### 2013-06-03 Article/Article20130603/tewi-paper-template.tex
Article - latex sources

% vim:encoding=utf8 ft=tex sts=2 sw=2 et:
% Copyright (c) 2009 Jaroslaw Koszuk
%
% $Id$

\documentclass{tewiart}

\usepackage[utf8]{inputenc}
\usepackage[T1]{fontenc}
\usepackage{graphicx}
\usepackage{amsthm}
\usepackage{txfonts}
\usepackage{epstopdf}

\usepackage{polski}
\usepackage[utf8]{inputenc}
\usepackage[table]{xcolor}
\usepackage{array}
\usepackage{subcaption}

\newtheorem{definition}{Definition}
\newtheorem{theorem}[definition]{Theorem}
\newtheorem{corollary}[definition]{Corollary}
\newtheorem{proposition}[definition]{Proposition}
\newtheorem{example}[definition]{Example}

\title{Magnitude of simple rules in investment strategies of algorithmic trading}
\headtitle{Magnitude of simple rules in investment strategies of algorithmic trading\dots}
\author{Antoni Wiliński\inst{1}, Piotr Błaszyński\inst{1}, Aneta Bera\inst{1}, \\ Wojciech Nowicki\inst{1}, Katarzyna Buda\inst{1}}
\headauthor{A. One, A. Two}
\affiliation{%
  \inst{1}West Pomeranian University of Technology\\
  Faculty of Computer Science\\
  ul.Żolnierska 49, 71-210 Szczecin Poland\\
  {awilinski,pblaszynski}@wi.ps.pl, @wi.ps.pl
}
\keywords{algorithmic trading, forecasting, financial markets, simple rules, computational intelligence, investment strategies}

\begin{document}

\begin{figure}
\centering
\includegraphics[width=\textwidth]{logotewi.png}
\end{figure}

\maketitle

\begin{abstract}
In article are shown studies of the possibly simplest investment strategy of algo trading. The authors' intention was to prove the thesis that in the greedy algorithmic trading directed to the appropriate response, not to forecast, there are almost always opportunities to achieve profit. This paper presents the results of tests for over twenty core markets - currency pairs, indices and commodities. Introduced the original concept of quadrant of openings on each bar. In principle, the strategy is not relevant investment (studies were conducted without transaction costs), only cognitive in order to develop
\end{abstract}

\section{Introduction}
\indent For centuries predicting future events was a great challenge for many fields of science. Probably next to the meteorology, most important is the prediction of changes in the financial markets. It's a big still unresolved task that intrigues and motivates the continuing search. Modern computing capabilities allow to change researcher relationship to predictive challenge. If the aim is to be effective investment, not the successful prediction, research target should be changed. Many scientific papers was devoted to the problem of investment efficiency, also including the best quality papers, as well as work of at least several Nobel Prize winners. Among the many highly sophisticated research methods, for years was examined the ability of simple patterns classification in the time series. Trying to take advantage of this simple patterns (classification rules) in investment strategies.\\
\indent The aim of papper is to verify thesis about effectiveness of such simple rules of opening and closing position on trading markets. High frequency open positions algo trading are considering here. The strategy is based on the basic concept - should be as simple as possible, impossible to achieve by human not assisted with machine, should reject the idea of "predictions" of the future and be based on idea of responding to market behaviour. Such strategies are being tested for at least several decades and rather has not good reviews. Most studies cover intersections of moving averages as premise of classifier opening positions rule or remaining idle. Usually these conditions turn out to be too easy to achieve satisfactory transaction efficiency.\\
\indent Close terms in such investment strategies are also very simple. They are mostly based on similar terms, resulting from mean values or number of bars that elapsed since open.
Similar concept will be considered in this study. This concept belongs simple rules group, extracted from repeated patterns in the time series of financial instruments. Most commonly, these rules include a group or sequence of conditions besides using moving averages also uses differences in average, first derivative, standard deviation (Bollinger Bands) or pivot points. Friesen, Weller i Dunham \cite{friesen09} say that these methods were for many years rather neglected by the academic community, despite frequent, or perhaps because of, use by trade practitioners on the stock exchange. This opinion is not completely correct, because even Eugene Fama, creator of the efficient markets theory \cite{fama91}, admitted later that  there is little evidence of of simple rules efficiency \cite{fama98}. Cai and Keasey \cite{cai05} noted both predictive and investing efficiency of simplest rules based on differences in derivatives averages and levels of price direction changes. Tian, Wan and Guo \cite{tian02} reported the effectiveness of certain rules for some markets and total unsuitable on other. This opinion has become an inspiration for the authors to consider a number of markets. They distinguish growing and mature markets. A wealth of simple rules ideas is work of Krutsinger \cite{krutsinger99}, collection of interviews with the most prominent modern practices – american market experts. Experts, which Phillip Ball \cite{ball07} writes, that deserves to be published, because they achieve financial success, so uncommon in academic.
It is easy to see that the majority of these excellent traders succeed within a certain period of time, and today the implementation of their methods gives poor results. This contradicts the general philosophy of these practitioners (but not all of them), that exists mysterious patterns or rules, that are characteristic for specific markets, which provide success.
\section{Strategy characteristics}
\indent The essence of the concept is the idea of simultaneous open long and short positions based on various signals, in this case the intersection graph (values of exchange rate  and stock index) and average of the last m closing of this price.
Let C be considering constantly changing prices of value, and Ci closing price of I OHLC bar (Open, High, Low, Close). Denote Cmi as average of m last close
\begin{equation} \label{label-of-equation-1}
  C_{mi} = (C_{i-m} + C_{i-m+1} + … + C_{i} ) / m; 
\end{equation}

At the moment of I bar closing, value can be compared with the Cmi average. Depending on the investor's beliefs about the existence of a particular trend are thus four possible decision-making situations:
1. If Ci  > Cmi  long position will be open
2. If Ci  > Cmi  short position will be open
3. If Ci  < Cmi  long position will be open
4. If Ci  < Cmi  short position will be open
Fig. 1. Quadrant of four possible open position.

\section{The test results}
The study of strategy was carried out on the following markets:
currency pairs: EURUSD...
stock indexes: 
commodities:

\begin{table}[!t]
\caption{Profits for all strategy quadrants} 
 \begin{center} 
 \begin{tabular}{|l|l|l|l|l|} 
 \hline \textbf{strategy} & \textbf{profit} & \textbf{bestCalmar} & \textbf{bestMALength} & \textbf{la} \\ \hline  
S1a & -3.148 & -0.9218155 & 43 & 168\\ \hline 
S1b & -2.34 & -0.5721271 & 53 & 158\\ \hline 
S1c & -46.021 & -0.99206708 & 8 & 1788\\ \hline 
S1d & -62.466 & -0.99572799 & 9 & 1877\\ \hline 
S1s & -111.077 & -0.99744078 & NaN & 4946\\ 
\hline \end{tabular} 
 \end{center} 
 \end{table}

\begin{figure}[h]
\centering
\begin{minipage}{.40\linewidth}
\centering \includegraphics[width=0.9\textwidth]{S1a.eps}
\subcaption{Profit - S1a}
\label{jedno}
\end{minipage}
\begin{minipage}{.40\linewidth}
\centering \includegraphics[width=0.9\textwidth]{S1b.eps}
\subcaption{Profit - S1b}
\label{dwu}
\end{minipage}
\\
\begin{minipage}{.40\linewidth}
\centering \includegraphics[width=0.9\textwidth]{S1c.eps}
\subcaption{Profit- S1c}
\label{cztero}
\end{minipage}
\begin{minipage}{.40\linewidth}
\centering 
\includegraphics[width=0.9\textwidth]{S1d.eps}
\subcaption{Profit - S1d}
\label{mansard}
\end{minipage}
\begin{minipage}{.8\linewidth}
\centering 
\includegraphics[width=0.9\textwidth]{S1s.eps}
\label{mansard}
\end{minipage}
\caption{EURJPY market results}
\end{figure}

\begin{figure}[h]
\centering
\begin{minipage}{.40\linewidth}
\centering \includegraphics[width=0.9\textwidth]{rysunek2a.png}
\subcaption{Version a}
\label{jedno}
\end{minipage}
\begin{minipage}{.40\linewidth}
\centering \includegraphics[width=0.9\textwidth]{rysunek2b.png}
\subcaption{Version b}
\label{dwu}
\end{minipage}
\\
\begin{minipage}{.40\linewidth}
\centering \includegraphics[width=0.9\textwidth]{rysunek2c.png}
\subcaption{Version c}
\label{cztero}
\end{minipage}
\begin{minipage}{.40\linewidth}
\centering 
\includegraphics[width=0.9\textwidth]{rysunek2d.png}
\subcaption{Version d}
\label{mansard}
\end{minipage}
\begin{minipage}{.8\linewidth}
\centering 
\includegraphics[width=0.9\textwidth]{rysunek1pp.png}
\label{mansard}
\end{minipage}
\caption{All versions}
\end{figure}

\section{Conclusions}
Ut purus. Nullam facilisis porttitor enim. Vestibulum nulla massa, ultricies
sed, molestie luctus, imperdiet eget, mi. \\
\indent Integer commodo ipsum vitae enim. Morbi mollis nunc suscipit nisl.
Class aptent taciti sociosqu ad litora torquent per conubia nostra, per
inceptos himenaeos. Nam urna lacus, placerat posuere, dapibus eget, gravida
at, lorem. Aliquam nec justo eu dui semper fringilla. Aliquam vitae urna.
Morbi mattis consectetur ante. Ut ante massa, vestibulum ut, accumsan ac,
convallis quis, orci. Pellentesque at ipsum vitae quam laoreet tristique. Cras
vel nunc. Nulla facilisi.\\
\indent Pellentesque fringilla nulla vitae metus varius faucibus. Fusce aliquet
vehicula risus. Donec pulvinar viverra lectus. Nam tristique. Nulla malesuada
metus nec purus. Ut aliquam diam. Phasellus eu dui vel ipsum aliquet
vestibulum. Quisque ullamcorper, ligula in placerat imperdiet, risus risus
malesuada dolor, ut scelerisque ipsum nisi eu urna. Mauris bibendum tortor
condimentum mauris.

\subsection{Some notes on references}\label{bib}
Examples of citing: \cite{wilinski09}, \cite{wilinski09,
tian02, satchwell05}.

%%%%%%%%%% USE ____BIBTEX____ TO GENERATE YOUR REFERENCES 
%%%%%%%%%%% PLEASE UNCOMMENT THE TWO FOLLOWING LINES

\bibliography{references-tewi}
\bibliographystyle{aiaa-tewi}

\end{document}

### 2013-06-03 Article/Article20130603/tewi-paper-template.tex
Dodane: rysunek symbolicznego kwadrantu reakcji na ruch rynku, FloatBarrier-y dodane po figurach - wymuszają połozenie rysunku Zmieniona szerokość rysunków Zmiana w rysunku rysunke1pp.png - dodane linie poziome
Fig. order
- zmiana wysokości wykresów - połozenie wykresów i tabeli na jednej stronie

@@
 \usepackage{epstopdf}
+\usepackage{placeins}
 
@@
 
+\begin{figure}[h]
+ \centering
+ \includegraphics[width=\textwidth]{Rysunek0_all2.png}
+ \caption{Symbolic quadrant of response (second line) for market movement (first line)}
+\end{figure}
+\FloatBarrier
+
+\begin{figure}[h]
+\centering
+\centering 
+\includegraphics[width=\textwidth]{rysunek1pp.png}
+\caption{All versions}
+\end{figure}
+\FloatBarrier
+
+\begin{figure}[h]
+\centering
+\begin{minipage}{.49\linewidth}
+\centering \includegraphics[width=\textwidth]{rysunek2a.png}
+\subcaption{Version a}
+\label{jedno}
+\end{minipage}
+\begin{minipage}{.49\linewidth}
+\centering \includegraphics[width=\textwidth]{rysunek2b.png}
+\subcaption{Version b}
+\label{dwu}
+\end{minipage}
+\\
+\begin{minipage}{.49\linewidth}
+\centering \includegraphics[width=\textwidth]{rysunek2c.png}
+\subcaption{Version c}
+\label{cztero}
+\end{minipage}
+\begin{minipage}{.49\linewidth}
+\centering 
+\includegraphics[width=\textwidth]{rysunek2d.png}
+\subcaption{Version d}
+\label{mansard}
+\end{minipage}
+\caption{Separate strategies}
+\end{figure}
+\FloatBarrier
+
 \section{The test results}
@@
  \hline \textbf{strategy} & \textbf{profit} & \textbf{bestCalmar} & \textbf{bestMALength} & \textbf{la} \\ \hline  
-S1a & -3.148 & -0.9218155 & 43 & 168\\ \hline 
-S1b & -2.34 & -0.5721271 & 53 & 158\\ \hline 
-S1c & -46.021 & -0.99206708 & 8 & 1788\\ \hline 
-S1d & -62.466 & -0.99572799 & 9 & 1877\\ \hline 
-S1s & -111.077 & -0.99744078 & NaN & 4946\\ 
+S1a & 26.177 & 5.5909868 & 24 & 2764\\ \hline 
+S1b & -19.002 & -0.74976326 & 31 & 2801\\ \hline 
+S1c & 12.025 & 2.6645247 & 31 & 2167\\ \hline 
+S1d & -4.57 & -0.47001954 & 21 & 2226\\ \hline 
+S1s & 14.33 & 2.957078 & NaN & 4968\\ 
 \hline \end{tabular} 
@@
  \end{table}
+\FloatBarrier
 
@@
 \centering
-\begin{minipage}{.40\linewidth}
-\centering \includegraphics[width=0.9\textwidth]{S1a.eps}
+\begin{minipage}{.49\linewidth}
+\centering 
+\includegraphics[width=0.9\textwidth]{S1a.eps}
 \subcaption{Profit - S1a}
@@
 \end{minipage}
-\begin{minipage}{.40\linewidth}
-\centering \includegraphics[width=0.9\textwidth]{S1b.eps}
+\begin{minipage}{.49\linewidth}
+\centering 
+\includegraphics[width=0.9\textwidth]{S1b.eps}
 \subcaption{Profit - S1b}
@@
 \\
-\begin{minipage}{.40\linewidth}
-\centering \includegraphics[width=0.9\textwidth]{S1c.eps}
+\begin{minipage}{.49\linewidth}
+\centering 
+\includegraphics[width=0.9\textwidth]{S1c.eps}
 \subcaption{Profit- S1c}
@@
 \end{minipage}
-\begin{minipage}{.40\linewidth}
+\begin{minipage}{.49\linewidth}
 \centering 
@@
 \end{minipage}
-\begin{minipage}{.8\linewidth}
+\begin{minipage}{\linewidth}
 \centering 
-\includegraphics[width=0.9\textwidth]{S1s.eps}
+\includegraphics[width=0.6\textwidth]{S1s.eps}
 \label{mansard}
+\subcaption{Profit - S1s}
 \end{minipage}
@@
 \end{figure}
-
-\begin{figure}[h]
-\centering
-\begin{minipage}{.40\linewidth}
-\centering \includegraphics[width=0.9\textwidth]{rysunek2a.png}
-\subcaption{Version a}
-\label{jedno}
-\end{minipage}
-\begin{minipage}{.40\linewidth}
-\centering \includegraphics[width=0.9\textwidth]{rysunek2b.png}
-\subcaption{Version b}
-\label{dwu}
-\end{minipage}
-\\
-\begin{minipage}{.40\linewidth}
-\centering \includegraphics[width=0.9\textwidth]{rysunek2c.png}
-\subcaption{Version c}
-\label{cztero}
-\end{minipage}
-\begin{minipage}{.40\linewidth}
-\centering 
-\includegraphics[width=0.9\textwidth]{rysunek2d.png}
-\subcaption{Version d}
-\label{mansard}
-\end{minipage}
-\begin{minipage}{.8\linewidth}
-\centering 
-\includegraphics[width=0.9\textwidth]{rysunek1pp.png}
-\label{mansard}
-\end{minipage}
-\caption{All versions}
-\end{figure}
+\FloatBarrier
 

### 2013-06-03 Article/Article20130603/tewi-paper-template.tex
Fig. size
poprawka podpisów osi w epsach na angielskim zmiana języka artykułu na angielski
literówka w adresie uczelni "Żolnierska" - > "Żołnierska"

@@
 \usepackage{placeins}
-
-\usepackage{polski}
+\usepackage[english]{babel}
 \usepackage[utf8]{inputenc}
@@
   Faculty of Computer Science\\
-  ul.Żolnierska 49, 71-210 Szczecin Poland\\
+  ul.Żołnierska 49, 71-210 Szczecin Poland\\
   {awilinski,pblaszynski}@wi.ps.pl, @wi.ps.pl
@@
 \centering 
-\includegraphics[width=0.9\textwidth]{S1a.eps}
+\includegraphics[width=0.82\textwidth]{S1a.eps}
 \subcaption{Profit - S1a}
@@
 \centering 
-\includegraphics[width=0.9\textwidth]{S1b.eps}
+\includegraphics[width=0.82\textwidth]{S1b.eps}
 \subcaption{Profit - S1b}
@@
 \centering 
-\includegraphics[width=0.9\textwidth]{S1c.eps}
+\includegraphics[width=0.82\textwidth]{S1c.eps}
 \subcaption{Profit- S1c}
@@
 \centering 
-\includegraphics[width=0.9\textwidth]{S1d.eps}
+\includegraphics[width=0.82\textwidth]{S1d.eps}
 \subcaption{Profit - S1d}

### 2013-06-03 Article/Article20130603/tewi-paper-template.tex
zmieniony format plików graficznych na eps
references cleanup

@@
   ul.Żołnierska 49, 71-210 Szczecin Poland\\
-  {awilinski,pblaszynski}@wi.ps.pl, @wi.ps.pl
+  \{awilinski, pblaszynski, abera, wnowicki, kbuda\}@wi.ps.pl
 }
@@
 \section{Introduction}
-\indent For centuries predicting future events was a great challenge for many fields of science.
-Probably next to the meteorology, most important is the prediction of changes in the financial markets.
-It's a big still unresolved task that intrigues and motivates the continuing search.
+\indent For centuries predicting future events was a great challenge for many fields of science \cite{ball07, wu12}.
+Probably next to the meteorology, most important is the prediction of changes in the financial markets \cite{krutsinger99, satchwell05, schwager02}.
+It's a big still unresolved task that intrigues and motivates the continuing search \cite{fama91, fama98}.
 Modern computing capabilities allow to change researcher relationship to predictive challenge.
@@
 Many scientific papers was devoted to the problem of investment efficiency, also including the best quality papers, as well as work of at least several Nobel Prize winners.
-Among the many highly sophisticated research methods, for years was examined the ability of simple patterns classification in the time series.
+Among the many highly sophisticated research methods \cite{fujimoto03, kompa08, pawlak02, pedrycz97, rua09, raghuraj09, wilinski09} , for years was examined the ability of simple patterns classification in the time series \cite{brock92, cai05, gencay99, lebaron99, satchwell05}.
 Trying to take advantage of this simple patterns (classification rules) in investment strategies.\\
 \indent The aim of papper is to verify thesis about effectiveness of such simple rules of opening and closing position on trading markets.
-High frequency open positions algo trading are considering here.
+High frequency open positions algo trading are considering here \cite{muriel04}.
 The strategy is based on the basic concept - should be as simple as possible, impossible to achieve by human not assisted with machine, should reject the idea of "predictions" of the future and be based on idea of responding to market behaviour.
@@
 \section{Strategy characteristics}
-\indent The essence of the concept is the idea of simultaneous open long and short positions based on various signals, in this case the intersection graph (values of exchange rate  and stock index) and average of the last m closing of this price.
+\indent The essence of the concept is the idea of simultaneous open long and short positions based on various signals, in this case the intersection graph (values of exchange rate  and stock index) and average of the last m closing of this price.\\
+Equally simple is the closing rule of each opened position. It's closed at the close of (i+1) bar (fig. 1).
 Let C be considering constantly changing prices of value, and Ci closing price of I OHLC bar (Open, High, Low, Close). Denote Cmi as average of m last close
@@
 4. If Ci  < Cmi  short position will be open
-Fig. 1. Quadrant of four possible open position.
+
+Each of these decisions is usually attributed to reasons arising from the conviction of the investor why and what happens in a moment.
+Should be noted that each of the above decisions is taken basing on average of different number of last close bar prices.
+Therefore, in the general case at the close moment close of I bar when it should make decision of open (short or long) it could happen that may occur up to four different levels of the average value calculated for the last m bars (different for each contractual quadrant).\\
+These situations are shown in Figure 1
 
@@
  \centering
- \includegraphics[width=\textwidth]{Rysunek0_all2.png}
+ \includegraphics[width=\textwidth]{Rysunek0_all2.eps}
  \caption{Symbolic quadrant of response (second line) for market movement (first line)}
@@
 \centering 
-\includegraphics[width=\textwidth]{rysunek1pp.png}
+\includegraphics[width=\textwidth]{rysunek1pp.eps}
 \caption{All versions}
@@
 \begin{minipage}{.49\linewidth}
-\centering \includegraphics[width=\textwidth]{rysunek2a.png}
+\centering \includegraphics[width=\textwidth]{rysunek2a.eps}
 \subcaption{Version a}
@@
 \begin{minipage}{.49\linewidth}
-\centering \includegraphics[width=\textwidth]{rysunek2b.png}
+\centering \includegraphics[width=\textwidth]{rysunek2b.eps}
 \subcaption{Version b}
@@
 \begin{minipage}{.49\linewidth}
-\centering \includegraphics[width=\textwidth]{rysunek2c.png}
+\centering \includegraphics[width=\textwidth]{rysunek2c.eps}
 \subcaption{Version c}
@@
 \centering 
-\includegraphics[width=\textwidth]{rysunek2d.png}
+\includegraphics[width=\textwidth]{rysunek2d.eps}
 \subcaption{Version d}
@@
 
-\subsection{Some notes on references}\label{bib}
-Examples of citing: \cite{wilinski09}, \cite{wilinski09,
-tian02, satchwell05}.
-
 %%%%%%%%%% USE ____BIBTEX____ TO GENERATE YOUR REFERENCES 

### 2013-06-04 Article/Article20130603/tewi-paper-template.tex
Zmiana w wypisaniu wzoru, indeksy poprawione. Dodane enumerate do sytuacji.

@@
 \begin{equation} \label{label-of-equation-1}
-  C_{mi} = (C_{i-m} + C_{i-m+1} + … + C_{i} ) / m; 
+  C_{m_{i}} = \frac{C_{i-m} + C_{i-m+1} + … + C_{i}}{m}; 
 \end{equation}
 
-At the moment of I bar closing, value can be compared with the Cmi average.
+At the moment of I bar closing, value can be compared with the $C_{m_{i}}$ average.
 Depending on the investor's beliefs about the existence of a particular trend are thus four possible decision-making situations:
-1. If Ci  > Cmi  long position will be open
-2. If Ci  > Cmi  short position will be open
-3. If Ci  < Cmi  long position will be open
-4. If Ci  < Cmi  short position will be open
+\begin{enumerate}
+\item If $C_i  > C_{m_{i}}$  long position will be open,
+\item If $C_i  > C_{m_{i}}$  short position will be open,
+\item If $C_i  < C_{m_{i}}$  long position will be open,
+\item If $C_i  < C_{m_{i}}$  short position will be open.
+\end{enumerate}
 
@@
 
-\begin{figure}[h]
+\begin{figure}[h!]
  \centering

### 2013-06-04 ForexTester/ForexTester/Candle.cs
Forex tester dir

@@ -1,0 +1,13 @@
+﻿namespace ForexTester
+{
+    public class Candle
+    {
+        public string Date;
+        public string Time;
+        public double Open;
+        public double Close;
+        public double Low;
+        public double High;
+        public double Volume;
+    }
+}

### 2013-06-04 ForexTester/ForexTester/ChartDrawing.cs

@@ -1,0 +1,56 @@
+﻿using System.Collections.Generic;
+using System.Windows.Forms.DataVisualization.Charting;
+
+namespace ForexTester
+{
+    class ChartDrawing
+    {
+        private readonly Chart m_chart;
+
+        public ChartDrawing(Chart chart)
+        {
+            m_chart = chart;
+        }
+
+        public void Draw(List<Candle> candles)
+        {
+            m_chart.Series.Clear();
+            var candlesSeries = m_chart.Series.Add("candles");
+            candlesSeries.ChartType = SeriesChartType.Candlestick;
+            var upperLinesSeries = m_chart.Series.Add("upperLines");
+            upperLinesSeries.ChartType = SeriesChartType.Line;
+            var midLinesSeries = m_chart.Series.Add("midLines");
+            midLinesSeries.ChartType = SeriesChartType.Line;
+            var lowerLinesSeries = m_chart.Series.Add("lowerLines");
+            lowerLinesSeries.ChartType = SeriesChartType.Line;
+            var x = 0;
+            var startSeries = m_chart.Series.Count;
+            var channels = startSeries;
+            const double delta = 0.001;
+            foreach (var candle in candles)
+            {
+                candlesSeries.Points.Add(new DataPoint(x, new[] { candle.Low, candle.High, candle.Close, candle.Open }));
+                if (x % 10 == 0)
+                {
+                    var channel = m_chart.Series.Add("channel" + channels);
+                    channel.ChartType = SeriesChartType.Line;
+                    channel.Points.Add(new DataPoint(x, candle.Close));
+                    channels++;
+                    if (channels > startSeries + 4)
+                    {
+                        var oldChannel = m_chart.Series[channels - 4];
+                        oldChannel.Points.Add(new DataPoint(x, candle.Close));
+                    }
+
+                    //upperLinesSeries.Points.Add(new DataPoint(x, candle.Close + delta * candle.Close));
+                    //midLinesSeries.Points.Add(new DataPoint(x, candle.Close));
+                    //lowerLinesSeries.Points.Add(new DataPoint(x, candle.Close-delta*candle.Close));
+                }
+                x++;
+                if (x > 50)
+                    break;
+            }
+
+        }
+    }
+}

### 2013-06-04 ForexTester/ForexTester/Program.cs

@@ -1,0 +1,21 @@
+﻿using System;
+using System.Collections.Generic;
+using System.Linq;
+using System.Windows.Forms;
+
+namespace ForexTester
+{
+    static class Program
+    {
+        /// <summary>
+        /// The main entry point for the application.
+        /// </summary>
+        [STAThread]
+        static void Main()
+        {
+            Application.EnableVisualStyles();
+            Application.SetCompatibleTextRenderingDefault(false);
+            Application.Run(new Tester());
+        }
+    }
+}

### 2013-06-04 ForexTester/ForexTester/Properties/AssemblyInfo.cs

@@ -1,0 +1,36 @@
+﻿using System.Reflection;
+using System.Runtime.CompilerServices;
+using System.Runtime.InteropServices;
+
+// General Information about an assembly is controlled through the following 
+// set of attributes. Change these attribute values to modify the information
+// associated with an assembly.
+[assembly: AssemblyTitle("WindowsFormsApplication1")]
+[assembly: AssemblyDescription("")]
+[assembly: AssemblyConfiguration("")]
+[assembly: AssemblyCompany("")]
+[assembly: AssemblyProduct("WindowsFormsApplication1")]
+[assembly: AssemblyCopyright("Copyright ©  2012")]
+[assembly: AssemblyTrademark("")]
+[assembly: AssemblyCulture("")]
+
+// Setting ComVisible to false makes the types in this assembly not visible 
+// to COM components.  If you need to access a type in this assembly from 
+// COM, set the ComVisible attribute to true on that type.
+[assembly: ComVisible(false)]
+
+// The following GUID is for the ID of the typelib if this project is exposed to COM
+[assembly: Guid("c893cef1-f12e-4f84-b61b-580c1fdd4164")]
+
+// Version information for an assembly consists of the following four values:
+//
+//      Major Version
+//      Minor Version 
+//      Build Number
+//      Revision
+//
+// You can specify all the values or you can default the Build and Revision Numbers 
+// by using the '*' as shown below:
+// [assembly: AssemblyVersion("1.0.*")]
+[assembly: AssemblyVersion("1.0.0.0")]
+[assembly: AssemblyFileVersion("1.0.0.0")]

### 2013-06-04 ForexTester/ForexTester/Properties/Resources.Designer.cs

@@ -1,0 +1,63 @@
+﻿//------------------------------------------------------------------------------
+// <auto-generated>
+//     This code was generated by a tool.
+//     Runtime Version:4.0.30319.18034
+//
+//     Changes to this file may cause incorrect behavior and will be lost if
+//     the code is regenerated.
+// </auto-generated>
+//------------------------------------------------------------------------------
+
+namespace ForexTester.Properties {
+    using System;
+    
+    
+    /// <summary>
+    ///   A strongly-typed resource class, for looking up localized strings, etc.
+    /// </summary>
+    // This class was auto-generated by the StronglyTypedResourceBuilder
+    // class via a tool like ResGen or Visual Studio.
+    // To add or remove a member, edit your .ResX file then rerun ResGen
+    // with the /str option, or rebuild your VS project.
+    [global::System.CodeDom.Compiler.GeneratedCodeAttribute("System.Resources.Tools.StronglyTypedResourceBuilder", "4.0.0.0")]
+    [global::System.Diagnostics.DebuggerNonUserCodeAttribute()]
+    [global::System.Runtime.CompilerServices.CompilerGeneratedAttribute()]
+    internal class Resources {
+        
+        private static global::System.Resources.ResourceManager resourceMan;
+        
+        private static global::System.Globalization.CultureInfo resourceCulture;
+        
+        [global::System.Diagnostics.CodeAnalysis.SuppressMessageAttribute("Microsoft.Performance", "CA1811:AvoidUncalledPrivateCode")]
+        internal Resources() {
+        }
+        
+        /// <summary>
+        ///   Returns the cached ResourceManager instance used by this class.
+        /// </summary>
+        [global::System.ComponentModel.EditorBrowsableAttribute(global::System.ComponentModel.EditorBrowsableState.Advanced)]
+        internal static global::System.Resources.ResourceManager ResourceManager {
+            get {
+                if (object.ReferenceEquals(resourceMan, null)) {
+                    global::System.Resources.ResourceManager temp = new global::System.Resources.ResourceManager("ForexTester.Properties.Resources", typeof(Resources).Assembly);
+                    resourceMan = temp;
+                }
+                return resourceMan;
+            }
+        }
+        
+        /// <summary>
+        ///   Overrides the current thread's CurrentUICulture property for all
+        ///   resource lookups using this strongly typed resource class.
+        /// </summary>
[…]

### 2013-06-04 ForexTester/ForexTester/Properties/Settings.Designer.cs

@@ -1,0 +1,26 @@
+﻿//------------------------------------------------------------------------------
+// <auto-generated>
+//     This code was generated by a tool.
+//     Runtime Version:4.0.30319.18034
+//
+//     Changes to this file may cause incorrect behavior and will be lost if
+//     the code is regenerated.
+// </auto-generated>
+//------------------------------------------------------------------------------
+
+namespace ForexTester.Properties {
+    
+    
+    [global::System.Runtime.CompilerServices.CompilerGeneratedAttribute()]
+    [global::System.CodeDom.Compiler.GeneratedCodeAttribute("Microsoft.VisualStudio.Editors.SettingsDesigner.SettingsSingleFileGenerator", "10.0.0.0")]
+    internal sealed partial class Settings : global::System.Configuration.ApplicationSettingsBase {
+        
+        private static Settings defaultInstance = ((Settings)(global::System.Configuration.ApplicationSettingsBase.Synchronized(new Settings())));
+        
+        public static Settings Default {
+            get {
+                return defaultInstance;
+            }
+        }
+    }
+}

### 2013-06-04 ForexTester/ForexTester/Strategies/BaseStrategy.cs

@@ -1,0 +1,27 @@
+﻿using System;
+using System.Collections.Generic;
+using System.Globalization;
+
+namespace ForexTester.Strategies
+{
+    public class BaseStrategy
+    {
+        protected List<Candle> Candles;
+        protected const string ResultFileExtension = "result";
+        public BaseStrategy(List<Candle> candles)
+        {
+            Candles = candles;
+        }
+
+        protected IEnumerable<Candle> GetCandlesRange(int i, int length)
+        {
+            return Candles.GetRange(i - Math.Min(i - 1, length), Math.Min(i, length) + 1);
+        }
+
+
+        protected string GetDouble(double value)
+        {
+            return value.ToString("0.00000", CultureInfo.InvariantCulture);
+        }
+    }   
+}

### 2013-06-04 ForexTester/ForexTester/Strategies/S1AParallel.cs

@@ -1,0 +1,27 @@
+﻿using System.Collections.Generic;
+using System.IO;
+using System.Linq;
+using System.Threading.Tasks;
+
+namespace ForexTester.Strategies
+{
+    class S1AParallel : S1Parallel
+    {
+        public S1AParallel(List<Candle> candles)
+            : base(candles)
+        {
+        }
+
+        protected override bool ComputePredicate(double mean, double close)
+        {
+            return mean < close;
+        }
+
+        protected override double ComputeProfit(int i)
+        {
+            return Candles[i + 1].Close - Candles[i + 1].Open;
+        }
+
+        protected override string ResultFilename{get { return "texRa.txt"; }}
+    }
+}

### 2013-06-04 ForexTester/ForexTester/Strategies/S1BParallel.cs

@@ -1,0 +1,27 @@
+﻿using System.Collections.Generic;
+using System.IO;
+using System.Linq;
+using System.Threading.Tasks;
+
+namespace ForexTester.Strategies
+{
+    class S1BParallel : S1Parallel
+    {
+        public S1BParallel(List<Candle> candles)
+            : base(candles)
+        {
+        }
+
+        protected override bool ComputePredicate(double mean, double close)
+        {
+            return mean < close;
+        }
+
+        protected override double ComputeProfit(int i)
+        {
+            return -Candles[i + 1].Close + Candles[i + 1].Open;
+        }
+
+        protected override string ResultFilename{get { return "texRb.txt"; }}
+    }
+}

### 2013-06-04 ForexTester/ForexTester/Strategies/S1CParallel.cs

@@ -1,0 +1,27 @@
+﻿using System.Collections.Generic;
+using System.IO;
+using System.Linq;
+using System.Threading.Tasks;
+
+namespace ForexTester.Strategies
+{
+    class S1CParallel : S1Parallel
+    {
+        public S1CParallel(List<Candle> candles)
+            : base(candles)
+        {
+        }
+
+        protected override bool ComputePredicate(double mean, double close)
+        {
+            return mean > close;
+        }
+
+        protected override double ComputeProfit(int i)
+        {
+            return Candles[i + 1].Close - Candles[i + 1].Open;
+        }
+
+        protected override string ResultFilename{get { return "texRc.txt"; }}
+    }
+}

### 2013-06-04 ForexTester/ForexTester/Strategies/S1DParallel.cs

@@ -1,0 +1,27 @@
+﻿using System.Collections.Generic;
+using System.IO;
+using System.Linq;
+using System.Threading.Tasks;
+
+namespace ForexTester.Strategies
+{
+    class S1DParallel : S1Parallel
+    {
+        public S1DParallel(List<Candle> candles)
+            : base(candles)
+        {
+        }
+
+        protected override bool ComputePredicate(double mean, double close)
+        {
+            return mean > close;
+        }
+
+        protected override double ComputeProfit(int i)
+        {
+            return - Candles[i + 1].Close + Candles[i + 1].Open;
+        }
+
+        protected override string ResultFilename{get { return "texRd.txt"; }}
+    }
+}

### 2013-06-04 ForexTester/ForexTester/Strategies/S1Parallel.cs

@@ -1,0 +1,111 @@
+﻿using System.Collections.Generic;
+using System.IO;
+using System.Linq;
+using System.Threading.Tasks;
+
+namespace ForexTester.Strategies
+{
+    class S1Parallel : BaseStrategy
+    {
+        public S1Parallel(List<Candle> candles)
+            : base(candles)
+        {
+        }
+        
+        protected virtual bool ComputePredicate(double mean, double close)
+        {
+            return true;
+        }
+        
+        protected virtual double ComputeProfit(int i)
+        {
+            return 0;
+        }
+        protected virtual string ResultFilename { get { return "texR.txt"; } }
+
+        public void ComputeStrategy(object selectedItem)
+        {
+            string filename = selectedItem + "." + ResultFileExtension;
+            var bestReturn = -120.0;
+            var candlesCount = Candles.Count;
+            var bestCalmar = 0.0;
+            var bestMa = 0;
+            var bestLa = 0;
+            using (var writer = new StreamWriter(filename, false))
+            {
+                writer.WriteLine("results");
+            }
+            Parallel.For(5, 100, paramALength =>
+            {
+                var localparamALength = paramALength;
+                var means = new List<double>(candlesCount) { Candles.First().Close };
+                var kon = candlesCount - 1;
+                for (var i = 1; i < kon; i++)
+                    means.Add(GetCandlesRange(i, localparamALength).Average(candle => candle.Close));
+                //CreateStatus("paramALength: {0}", paramALength);
+                //AppendStatus("  paramAVolLength: {0}\r\n", paramAVolLength);
+                var sumRa = new List<double>(candlesCount);
+                var returnValues = new List<double>(candlesCount);
+                var drawdowns = new List<double>(candlesCount);
+                var candlesBegin = localparamALength + 1;
+                var positionCount = 0; //liczba otwieranych pozycji
+                //var stopLossCount = 0; //liczba stop lossów
+                var lastCandle = kon;
+                for (int i = 0; i < candlesBegin; i++)
+                {
+                    sumRa.Add(0);
+                    returnValues.Add(0);
+                }
+                for (int i = candlesBegin; i < lastCandle; i++)
+                {
+                    returnValues.Add(0);
+                    if (ComputePredicate(means[i],  Candles[i].Close))
+                    {
+                        returnValues[i] = ComputeProfit(i);
+                        //zysk z i-tej pozycji long zamykanej na zamknięciu po 1 kroku
[…]

### 2013-06-04 ForexTester/ForexTester/Strategies/S1a.cs

@@ -1,0 +1,97 @@
+﻿using System.Collections.Generic;
+using System.IO;
+using System.Linq;
+
+namespace ForexTester.Strategies
+{
+    class S1A : BaseStrategy
+    {
+        public S1A(List<Candle> candles)
+            : base(candles)
+        {
+        }
+
+        public void ComputeStrategy(object selectedItem)
+        {
+            string filename = selectedItem + "." + ResultFileExtension;
+            var bestReturn = -120.0;
+            var candlesCount = Candles.Count;
+            var bestCalmar = 0.0;
+            var bestMa = 0;
+            using (var writer = new StreamWriter(filename, false))
+            {
+                writer.WriteLine("results");
+            }
+            //paramALength: 9 paramAVolLength: 26 paramABuffer: -0.00416 paramAVolThreshold: 100 paramADuration: 16 paramASL: 0.00576 Calmar: 2.6312
+            //const int paramALength=24;
+            for (var paramALength = 10; paramALength <= 1000; paramALength += 1)//liczba swiec wstecz do obliczenia maksimum
+            {
+                var means = new List<double>(candlesCount) { Candles.First().Close };
+                var kon = candlesCount - 1;
+                for (var i = 1; i < kon; i++)
+                    means.Add(GetCandlesRange(i, paramALength).Average(candle => candle.Close));
+                //CreateStatus("paramALength: {0}", paramALength);
+                //AppendStatus("  paramAVolLength: {0}\r\n", paramAVolLength);
+                var sumRa = new List<double>(candlesCount);
+                var returnValues = new List<double>(candlesCount);
+                var drawdowns = new List<double>(candlesCount);
+                var candlesBegin = paramALength + 1;
+                var positionCount = 0; //liczba otwieranych pozycji
+                //var stopLossCount = 0; //liczba stop lossów
+                var lastCandle = kon;
+                for (int i = 0; i < candlesBegin; i++)
+                {
+                    sumRa.Add(0);
+                    returnValues.Add(0);
+                }
+                for (int i = candlesBegin; i < lastCandle; i++)
+                {
+                    returnValues.Add(0);
+                    if (means[i] < Candles[i].Close)
+                    {
+                        returnValues[i] = Candles[i + 1].Close - Candles[i + 1].Open;
+                        //zysk z i-tej pozycji long zamykanej na zamknięciu po 1 kroku
+                        positionCount++;
+                    }
[…]

### 2013-06-04 ForexTester/ForexTester/Strategies/S4.cs

@@ -1,0 +1,150 @@
+﻿using System;
+using System.Collections.Generic;
+using System.IO;
+using System.Linq;
+
+namespace ForexTester.Strategies
+{
+    class S4:BaseStrategy
+    {
+        public S4(List<Candle> candles) : base(candles)
+        {
+        }
+
+        public void ComputeStrategy(object selectedItem)
+        {
+            string filename = selectedItem + "." + ResultFileExtension;
+            var bestReturn = -120.0;
+            var candlesCount = Candles.Count;
+            //var bestCalmar = 0.0;
+            //var bestMa = 0;
+            //var bestparamAVolLength = 0;
+            //var bestparamADuration = 0;
+            //var bestparamABuffer = 0.0;
+            //var bestparamAVolThreshold = 0.0;
+            //var bestparamAsl = 0.0;
+            const double spread = 0.00016;
+            using (var writer = new StreamWriter(filename, false))
+            {
+                writer.WriteLine("results");
+            }
+            //paramALength: 9 paramAVolLength: 26 paramABuffer: -0.00416 paramAVolThreshold: 100 paramADuration: 16 paramASL: 0.00576 Calmar: 2.6312
+            //const int paramALength=9;
+            for (var paramALength = 9; paramALength <= 19; paramALength += 1)//liczba swiec wstecz do obliczenia maksimum
+            {
+                var maxes = new List<double>(candlesCount) { Candles.First().Close };
+                var kon = candlesCount - 1;
+                for (var i = 1; i < kon; i++)
+                    maxes.Add(GetCandlesRange(i, paramALength).Max(candle => candle.Close));//TODO: Change to High
+                const int paramAVolLength = 26;
+                //for (int paramAVolLength = 26; paramAVolLength <= 26/*38*/; paramAVolLength++)
+                {
+                    //CreateStatus("paramALength: {0}", paramALength);
+                    //AppendStatus("  paramAVolLength: {0}\r\n", paramAVolLength);
+                    var volAverages = new List<double>(candlesCount) { 0 };
+                    for (var i = 1; i < kon; i++)
+                        volAverages.Add(GetCandlesRange(i, paramALength).Average(candle => candle.Volume) - Candles[i].Volume);
+                    //const int paramADuration = 16;
+                    for (var paramADuration = 6; paramADuration <= 16; paramADuration++)//liczba kroków wprzód do zamkniecia pozycji
+                    {
[…]

### 2013-06-04 ForexTester/ForexTester/Strategies/S4Parallel.cs

@@ -1,0 +1,175 @@
+﻿using System;
+using System.Collections.Generic;
+using System.IO;
+using System.Linq;
+using System.Text;
+using System.Threading.Tasks;
+
+namespace ForexTester.Strategies
+{
+    class S4Parallel : BaseStrategy
+    {
+        public S4Parallel(List<Candle> candles)
+            : base(candles)
+        {
+        }
+
+        public void ComputeStrategy2(object selectedItem)
+        {
+            var candlesCount = Candles.Count;
+            double[] maxes100 = new double[101];
+            Parallel.For(1, 100, paramALength =>
+                {
+                    var maxes = new List<double>(candlesCount) { Candles.First().Close };
+                    var kon = candlesCount - 1;
+                    var localparamALength = paramALength;
+                    for (var i = 1; i < kon; i++)
+                        maxes.Add(GetCandlesRange(i, localparamALength).Min(candle => candle.Close));//TODO: Change to High
+                    maxes100[localparamALength] = maxes[1000];
+
+                });
+            maxes100[0] = 1;
+
+        }
+
+        public void ComputeStrategy(object selectedItem)
+        {
+            var filename = selectedItem + "." + ResultFileExtension;
+            var bestReturn = -120.0;
+            var candlesCount = Candles.Count;
+            //var bestCalmar = 0.0;
+            //var bestMa = 0;
+            //var bestparamAVolLength = 0;
+            //var bestparamADuration = 0;
+            //var bestparamABuffer = 0.0;
+            //var bestparamAVolThreshold = 0.0;
+            //var bestparamAsl = 0.0;
+            const double spread = 0.00016;
+            using (var writer = new StreamWriter(filename, false))
+            {
+                writer.WriteLine("results");
+            }
+            //paramALength: 9 paramAVolLength: 26 paramABuffer: -0.00416 paramAVolThreshold: 100 paramADuration: 16 paramASL: 0.00576 Calmar: 2.6312
+            //const int paramALength=9;
+            Parallel.For(9, 19, paramALength =>
+            {
+            //for (var paramALength = 9; paramALength <= 19; paramALength += 10)//liczba swiec wstecz do obliczenia maksimum
+            //{
+                var localparamALength = paramALength;
+                var maxes = new List<double>(candlesCount) { Candles.First().Close };
+                var kon = candlesCount - 1;
+                for (var i = 1; i < kon; i++)
[…]

### 2013-06-04 ForexTester/ForexTester/Tester.Designer.cs

@@ -1,0 +1,146 @@
+﻿using System;
+using System.Collections.Generic;
+using System.IO;
+using System.Linq;
+
+namespace ForexTester
+{
+    partial class Tester
+    {
+        /// <summary>
+        /// Required designer variable.
+        /// </summary>
+        private System.ComponentModel.IContainer components = null;
+
+        /// <summary>
+        /// Clean up any resources being used.
+        /// </summary>
+        /// <param name="disposing">true if managed resources should be disposed; otherwise, false.</param>
+        protected override void Dispose(bool disposing)
+        {
+            if (disposing && (components != null))
+            {
+                components.Dispose();
+            }
+            base.Dispose(disposing);
+        }
+
+        #region Windows Form Designer generated code
+
+        /// <summary>
+        /// Required method for Designer support - do not modify
+        /// the contents of this method with the code editor.
+        /// </summary>
+        private void InitializeComponent()
+        {
+            System.Windows.Forms.DataVisualization.Charting.ChartArea chartArea1 = new System.Windows.Forms.DataVisualization.Charting.ChartArea();
+            this.btnLoadFile = new System.Windows.Forms.Button();
+            this.chart1 = new System.Windows.Forms.DataVisualization.Charting.Chart();
+            this.lblStatus = new System.Windows.Forms.Label();
+            this.chkMatlab = new System.Windows.Forms.CheckBox();
+            this.cmbFiles = new System.Windows.Forms.ComboBox();
+            this.label1 = new System.Windows.Forms.Label();
+            this.txtStatus = new System.Windows.Forms.TextBox();
+            ((System.ComponentModel.ISupportInitialize)(this.chart1)).BeginInit();
+            this.SuspendLayout();
+            // 
+            // btnLoadFile
+            // 
+            this.btnLoadFile.Location = new System.Drawing.Point(53, 59);
+            this.btnLoadFile.Name = "btnLoadFile";
+            this.btnLoadFile.Size = new System.Drawing.Size(75, 23);
+            this.btnLoadFile.TabIndex = 0;
+            this.btnLoadFile.Text = "Load file";
+            this.btnLoadFile.UseVisualStyleBackColor = true;
+            this.btnLoadFile.Click += new System.EventHandler(this.Button1Click);
+            // 
+            // chart1
+            // 
[…]

### 2013-06-04 ForexTester/ForexTester/Tester.cs

@@ -1,0 +1,159 @@
+﻿using System;
+using System.Collections.Generic;
+using System.Diagnostics;
+using System.Globalization;
+using System.IO;
+using System.Linq;
+using System.Threading.Tasks;
+using System.Windows.Forms;
+using System.Windows.Forms.DataVisualization.Charting;
+using ForexTester.Strategies;
+
+namespace ForexTester
+{
+    public partial class Tester : Form
+    {
+        const string m_ValuesFileExtension = "csv";
+        const string m_MatlabFileExtension = "m";
+        public Tester()
+        {
+            InitializeComponent();
+        }
+
+        private void Form1Load(object sender, EventArgs e)
+        {
+            LoadFilesToCombo();
+        }
+
+        private void LoadFilesToCombo()
+        {
+            foreach (var fullFilename in Directory.GetFiles(".", "*." + m_ValuesFileExtension, SearchOption.TopDirectoryOnly))
+            {
+                var fileName = Path.GetFileNameWithoutExtension(fullFilename);
+                if (fileName != null) cmbFiles.Items.Add(fileName);
+            }
+            if (cmbFiles.Items.Count>0)
+                cmbFiles.SelectedItem = cmbFiles.Items[0];
+        }
+
+        private void Button1Click(object sender, EventArgs e)
+        {
+            LoadData();
+            ComputeLines();
+            var chartDrawing = new ChartDrawing(chart1);
+            chartDrawing.Draw(m_candles);
+        }
+
+        private void LoadData()
+        {
+            //var data = File.ReadAllLines("EURUSD1." + m_ValuesFileExtension );
+            //var data = File.ReadAllLines("EURUSD60." + m_ValuesFileExtension);
+            var data = File.ReadAllLines(cmbFiles.SelectedItem + "." + m_ValuesFileExtension);
+
+            m_candles = new List<Candle>(data.Select(s => s.Split(',')).Select(values => new Candle
+                {
+                    Date = values[0],
+                    Time = values[1],
+                    Open = Convert.ToDouble(values[2].Replace(".", ",")),
+                    High = Convert.ToDouble(values[3].Replace(".", ",")),
+                    Low = Convert.ToDouble(values[4].Replace(".", ",")),
+                    Close = Convert.ToDouble(values[5].Replace(".", ",")),
+                    Volume = Convert.ToDouble(values[6].Replace(".", ","))
+                }).ToList());
+            ComputeAverages();
+            if (chkMatlab.Checked)
[…]

### 2013-06-04 ForexTester/ForexTester/ThreePointLine.cs

@@ -1,0 +1,12 @@
+﻿namespace ForexTester
+{
+    public class ThreePointLine
+    {
+        public int X0;
+        public double Y0;
+        public int X1;
+        public double Y1;
+        public int X2;
+        public double Y2;
+    }
+}

### 2013-06-04 Article/Article20130603/tewi-paper-template.tex
Conclusion

@@
 \section{Conclusions}
-Ut purus. Nullam facilisis porttitor enim. Vestibulum nulla massa, ultricies
-sed, molestie luctus, imperdiet eget, mi. \\
-\indent Integer commodo ipsum vitae enim. Morbi mollis nunc suscipit nisl.
-Class aptent taciti sociosqu ad litora torquent per conubia nostra, per
-inceptos himenaeos. Nam urna lacus, placerat posuere, dapibus eget, gravida
-at, lorem. Aliquam nec justo eu dui semper fringilla. Aliquam vitae urna.
-Morbi mattis consectetur ante. Ut ante massa, vestibulum ut, accumsan ac,
-convallis quis, orci. Pellentesque at ipsum vitae quam laoreet tristique. Cras
-vel nunc. Nulla facilisi.\\
-\indent Pellentesque fringilla nulla vitae metus varius faucibus. Fusce aliquet
-vehicula risus. Donec pulvinar viverra lectus. Nam tristique. Nulla malesuada
-metus nec purus. Ut aliquam diam. Phasellus eu dui vel ipsum aliquet
-vestibulum. Quisque ullamcorper, ligula in placerat imperdiet, risus risus
-malesuada dolor, ut scelerisque ipsum nisi eu urna. Mauris bibendum tortor
-condimentum mauris.
+\indent Suggested simple strategy is suitable only for algorithmic trading, even in absolute simplest form it seems to be interesting.
+As it’s been written in the introduction, more from cognitive point of view, than for the transaction value.\\
+\indent This strategy can be modified in many ways.
+Eg.
+in case of suggestions of simultaneous opening long and short positions better is to abandon work than opening both positions (due to transaction costs).
+The opening of another position in the same direction, eg.
+long position after closing the previous long position is senseless, it’s better to continue already opened position.
+These are two simplest ways to improve strategy.
+There are probably many ways to filter openings that allow to preserve only the most valuable due to profit events.
+Purpose of this paper was to prove the thesis, that even the simplest strategy has some potential profit, whose using is fascinating challenge.\\
+\indent The authors believe, due to observing results of experiments, that the thesis of this dormant potential has been acknowledged.
 

### 2013-06-04 ForexTester/ForexTester/Strategies/S1DParallel.cs
Unused usings

@@ -1,7 +1,4 @@
 ﻿using System.Collections.Generic;
-using System.IO;
-using System.Linq;
-using System.Threading.Tasks;
 
 namespace ForexTester.Strategies
 {

### 2013-06-04 ForexTester/ForexTester/Strategies/S4Parallel.cs

@@ -2,7 +2,6 @@
 using System.Collections.Generic;
 using System.IO;
 using System.Linq;
-using System.Text;
 using System.Threading.Tasks;
 
 namespace ForexTester.Strategies

### 2013-06-04 ForexTester/ForexTester/Tester.cs

@@ -4,9 +4,7 @@ using System.Diagnostics;
 using System.Globalization;
 using System.IO;
 using System.Linq;
-using System.Threading.Tasks;
 using System.Windows.Forms;
-using System.Windows.Forms.DataVisualization.Charting;
 using ForexTester.Strategies;
 
 namespace ForexTester

### 2013-06-04 ForexTester/ForexTester/Tester.cs
Cut files before 09.07.2012

@@ -47,7 +47,7 @@ namespace ForexTester
             //var data = File.ReadAllLines("EURUSD1." + m_ValuesFileExtension );
             //var data = File.ReadAllLines("EURUSD60." + m_ValuesFileExtension);
             var data = File.ReadAllLines(cmbFiles.SelectedItem + "." + m_ValuesFileExtension);
-
+            var compareDate = new DateTime(2012, 07, 09, 8, 0, 0);
             m_candles = new List<Candle>(data.Select(s => s.Split(',')).Select(values => new Candle
                 {
                     Date = values[0],
@@ -57,7 +57,7 @@ namespace ForexTester
                     Low = Convert.ToDouble(values[4].Replace(".", ",")),
                     Close = Convert.ToDouble(values[5].Replace(".", ",")),
                     Volume = Convert.ToDouble(values[6].Replace(".", ","))
-                }).ToList());
+                }).Where(v => Convert.ToDateTime( v.Date + " " + v.Time)> compareDate).ToList());
             ComputeAverages();
             if (chkMatlab.Checked)
                 GenerateToMatlab();

### 2013-06-04 ForexTester/ForexTester/Program.cs
Unused using

@@ -1,6 +1,4 @@
 ﻿using System;
-using System.Collections.Generic;
-using System.Linq;
 using System.Windows.Forms;
 
 namespace ForexTester

### 2013-06-04 ForexTester/ForexTester/Tester.Designer.cs
chkMatlab checked

@@ -77,6 +77,8 @@ namespace ForexTester
             // chkMatlab
             // 
             this.chkMatlab.AutoSize = true;
+            this.chkMatlab.Checked = true;
+            this.chkMatlab.CheckState = System.Windows.Forms.CheckState.Checked;
             this.chkMatlab.Location = new System.Drawing.Point(53, 36);
             this.chkMatlab.Name = "chkMatlab";
             this.chkMatlab.Size = new System.Drawing.Size(110, 17);

### 2013-06-04 Matlabs/S1_article/EURJPY.m
Pliki ze strategiami do artykułu. Plik startowy -> starter.m

@@ -1,0 +1,5000 @@
+C = [97.953,98.015,97.850,97.903,1182
+97.900,97.908,97.733,97.760,970
+97.765,97.810,97.673,97.783,774
+97.778,97.998,97.700,97.848,835
+97.850,97.875,97.768,97.780,660
+97.788,97.948,97.773,97.845,885
+97.840,97.883,97.768,97.823,1020
+97.818,97.905,97.745,97.900,1114
+97.905,98.023,97.878,97.953,929
+97.955,98.120,97.915,98.033,666
+98.028,98.088,98.015,98.015,657
+98.018,98.060,97.923,97.955,727
+97.950,98.030,97.925,97.983,652
+97.988,98.040,97.940,97.945,844
+97.950,98.040,97.935,97.965,2235
+97.960,98.005,97.940,97.990,1353
+97.980,98.055,97.965,97.995,629
+98.000,98.015,97.753,97.775,797
+97.768,97.878,97.760,97.830,679
+97.840,97.888,97.693,97.698,753
+97.700,97.770,97.630,97.633,754
+97.630,97.690,97.630,97.673,810
+97.680,97.710,97.643,97.698,658
+97.703,97.758,97.540,97.683,960
+97.680,97.688,97.298,97.400,1100
+97.393,97.738,97.323,97.613,1122
+97.615,97.905,97.605,97.825,819
+97.818,97.890,97.760,97.765,707
+97.775,97.845,97.728,97.735,586
+97.723,97.725,97.338,97.465,1005
+97.473,97.623,97.430,97.478,905
+97.480,97.515,97.305,97.378,1121
+97.375,97.383,97.218,97.338,805
+97.335,97.398,97.303,97.388,264
+97.383,97.425,97.328,97.348,337
+97.353,97.378,97.268,97.283,479
+97.280,97.363,97.230,97.273,407
+97.275,97.310,97.240,97.285,574
+97.290,97.325,97.225,97.280,1904
+97.270,97.295,97.235,97.268,915
+97.270,97.290,97.205,97.245,635
+97.235,97.243,97.085,97.155,756
+97.158,97.298,97.095,97.248,667
+97.245,97.370,97.228,97.295,619
+97.290,97.290,97.170,97.178,649
+97.195,97.258,97.168,97.198,685
+97.203,97.335,97.200,97.320,676
+97.313,97.350,97.183,97.260,749
+97.270,97.413,97.213,97.288,912
[…]

### 2013-06-04 Matlabs/S1_article/S1a.m

@@ -1,0 +1,76 @@
+function [] = S1a (C,ma,rynek)
+%(C) Antoni Wiliñski 2013
+%skrypt strategii S1 w projekcie TEWI
+%S1a - pierwszy kwadrant - oznaczajacy za³o¿enie, ze trend jest rosnacy i
+%nale¿y otwierac pozycje d³ugie wg zasady Buy Stop
+
+candlesCount = size(C,1);
+bestSumRa = -Inf;
+bestCalmara = -Inf;
+
+for ma=ma%10:50
+    means=zeros(1, candlesCount);
+    kon=candlesCount-1;
+    for i=2:kon
+        means(i) = mean(C(i-min(i-1,ma):i,4));
+    end
+    sumRa=zeros(1,6000);
+    Ra=zeros(1,6000);
+    pocz=ma+1;
+    if size(C,1)<5000
+        kon = 2047;
+    else
+        kon=5000-1;
+    end
+    la=0; %liczba otwieranych pozycji
+
+    for i=pocz:kon
+        if means(i)<C(i,4)
+       % if mean(C(i-ma:i,4))<C(i,4) && mean(C(i-ma:i,4))>C(i-1,4)
+            Ra(i)=C(i+1,4)-C(i+1,1); %zysk z i-tej pozycji long zamykanej po jednym kroku (na koñcu swiecy, w której nastapi³o otwarcie)
+            la=la+1;
+        end
+        sumRa(i)=sum(Ra(pocz:i));  %krzywa narastania kapita³u
+    end
+    
+    %obliczenie wspó³czynnika Calmara (stosunku zysku koñcowego do najwiekszego
+    %obsuniecia)
+    
+    recZ=0;  %rekord zysku
+    recO=0;  %rekord obsuniecia
+    
+    for j=1:kon
+        if sumRa(j)>recZ
+            recZ=sumRa(j);
+        end
+        dZ(j)=sumRa(j)-recZ; %róznica pomiedzy bie¿¹c¹ wartoscia kapita³u skumulowanego a dotychczasowym rekordem
+        if dZ(j)<recO
+            recO=dZ(j);  %obsuniecie maksymalne
+        end 
+    end
+    %wyniki koñcowe
+    Calmar=-sumRa(kon)/recO;  %wskaznik Calmara
+    if sumRa(kon)>bestSumRa
+        bestSumRa = sumRa(kon);
+        bestSumAll = sumRa;
+        bestCalmara = Calmar;
[…]

### 2013-06-04 Matlabs/S1_article/S1b.m

@@ -1,0 +1,76 @@
+function [] = S1b (C,mb,rynek)
+%(C) Antoni Wiliñski 2013
+%skrypt strategii S1 w projekcie TEWI
+%S1b - drugikwadrant kwadrant - oznaczajacy za³o¿enie, ze trend jest horyzontalny i
+%nale¿y otwierac pozycje krótkie wg zasady Sell Limit
+
+candlesCount = size(C,1);
+bestSumRb = -Inf;
+bestCalmarb = -Inf;
+
+for mb=mb%10:50
+    means=zeros(1, candlesCount);
+    kon=candlesCount-1;
+    for i=2:kon
+        means(i) = mean(C(i-min(i-1,mb):i,4));
+    end
+    sumRb=zeros(1,6000);
+    Rb=zeros(1,6000);
+    pocz=mb+1;
+    if size(C,1)<5000
+        kon = 2047;
+    else
+        kon=5000-1;
+    end
+    lb=0; %liczba otwieranych pozycji
+    
+    for i=pocz:kon
+        if means(i)<C(i,4)
+            Rb(i)=-C(i+1,4)+C(i+1,1); %zysk z i-tej pozycji short zamykanej po jednym kroku (na koñcu swiecy, w której nastapi³o otwarcie)
+            lb=lb+1;
+        end
+        sumRb(i)=sum(Rb(pocz:i));  %krzywa narastania kapita³u
+    end
+    
+    %obliczenie wspó³czynnika Calmara (stosunku zysku koñcowego do najwiekszego
+    %obsuniecia)
+    
+    recZ=0;  %rekord zysku
+    recO=0;  %rekord obsuniecia
+    
+    for j=1:kon
+        if sumRb(j)>recZ
+            recZ=sumRb(j);
+        end
+        dZ(j)=sumRb(j)-recZ; %róznica pomiedzy bie¿¹c¹ wartoscia kapita³u skumulowanego a dotychczasowym rekordem
+        if dZ(j)<recO
+            recO=dZ(j);  %obsuniecie maksymalne
+        end
+    end
+    %wyniki koñcowe
+    Calmar=-sumRb(kon)/recO;  %wskaznik Calmara
+    if sumRb(kon)>bestSumRb
+        bestSumRb = sumRb(kon);
+        bestSumAll = sumRb;
+        bestCalmarb = Calmar;
+        bestLb = lb;  %liczba otwartych pozycji
[…]

### 2013-06-04 Matlabs/S1_article/S1c.m

@@ -1,0 +1,76 @@
+function [] = S1c (C,mc,rynek)
+%(C) Antoni Wiliñski 2013
+%skrypt strategii S1 w projekcie TEWI
+%S1c - trzeci kwadrant - oznaczajacy za³o¿enie, ze trend jest horyzontalny i
+%nale¿y otwierac pozycje d³ugie wg zasady Buy Limit
+
+candlesCount = size(C,1);
+bestSumRc = -Inf;
+bestCalmarc = -Inf;
+
+
+for mc=mc%10:50%8:70
+    means=zeros(1, candlesCount);
+    kon=candlesCount-1;
+    for i=2:kon
+        means(i) = mean(C(i-min(i-1,mc):i,4));
+    end
+    sumRc=zeros(1,6000);
+    Rc=zeros(1,6000);
+    pocz=mc+1;
+    if size(C,1)<5000
+        kon = 2047;
+    else
+        kon=5000-1;
+    end
+    lc=0; %liczba otwieranych pozycji
+
+    for i=pocz:kon
+        if means(i)>C(i,4)
+            Rc(i)=C(i+1,4)-C(i+1,1); %zysk z i-tej pozycji long zamykanej po jednym kroku (na koñcu swiecy, w której nastapi³o otwarcie)
+            lc=lc+1;
+        end
+        sumRc(i)=sum(Rc(pocz:i));  %krzywa narastania kapita³u
+    end
+    
+    %obliczenie wspó³czynnika Calmara (stosunku zysku koñcowego do najwiekszego
+    %obsuniecia)
+    
+    recZ=0;  %rekord zysku
+    recO=0;  %rekord obsuniecia
+    
+    for j=1:kon
+        if sumRc(j)>recZ
+            recZ=sumRc(j);
+        end
+        dZ(j)=sumRc(j)-recZ; %róznica pomiedzy bie¿¹c¹ wartoscia kapita³u skumulowanego a dotychczasowym rekordem
+        if dZ(j)<recO
+            recO=dZ(j);  %obsuniecie maksymalne
+        end
+    end
+    %wyniki koñcowe
+    Calmar=-sumRc(kon)/recO;  %wskaznik Calmara
+    if sumRc(kon)>bestSumRc
+        bestSumRc = sumRc(kon);
+        bestSumAll = sumRc;
+        bestCalmarc = Calmar;
+        bestLc = lc;  %liczba otwartych pozycji
[…]

### 2013-06-04 Matlabs/S1_article/S1d.m

@@ -1,0 +1,78 @@
+function [] = S1d (C,md,rynek)
+%(C) Antoni Wiliñski 2013
+%skrypt strategii S1 w projekcie TEWI
+%S1d - czwarty kwadrant - oznaczajacy za³o¿enie, ze trend jest spadkowy i
+%nale¿y otwierac pozycje krótkie
+
+
+candlesCount = size(C,1);
+bestSumRd = -Inf;
+bestCalmard = -Inf;
+
+for md=md%10:50
+    means=zeros(1, candlesCount);
+    kon=candlesCount-1;
+    for i=2:kon
+        means(i) = mean(C(i-min(i-1,md):i-1,4));
+    end
+    sumRd=zeros(1,6000);
+    wykr=zeros(1,6000);
+    Rd=zeros(1,6000);
+    pocz=md+1;
+    if size(C,1)<5000
+        kon = 2047;
+    else
+        kon=5000-1;
+    end
+    ld=0; %liczba otwieranych pozycji
+    
+    for i=pocz:kon
+        if means(i)>C(i,4)
+            Rd(i)=-C(i+1,4)+C(i+1,1);%short zamykana po jednym kroku (na koñcu swiecy, w której nastapi³o otwarcie)
+            ld=ld+1;
+        end
+        sumRd(i)=sum(Rd(pocz:i));
+    end
+    
+    %obliczenie wspó³czynnika Calmara (stosunku zysku koñcowego do najwiekszego
+    %obsuniecia)
+    
+    recZ=0;  %rekord zysku
+    recO=0;  %rekord obsuniecia
+    
+    for j=1:kon
+        if sumRd(j)>recZ
+            recZ=sumRd(j);
+        end
+        dZ(j)=sumRd(j)-recZ; %róznica pomiedzy bie¿¹c¹ wartoscia kapita³u skumulowanego a dotychczasowym rekordem
+        if dZ(j)<recO
+            recO=dZ(j);  %obsuniecie maksymalne
+        end 
+    end
+    
+    %wyniki koñcowe
+    Calmar=-sumRd(kon)/recO;  %wskaznik Calmara
+    if sumRd(kon)>bestSumRd
+        bestSumRd = sumRd(kon);
+        bestSumAll = sumRd;
+        bestCalmard = Calmar;
+        bestLd = ld;  %liczba otwartych pozycji
+        bestLdp=ld/(kon-pocz);
+        bestMd = md;
[…]

### 2013-06-04 Matlabs/S1_article/S1s.m

@@ -1,0 +1,83 @@
+function [] = S1s (C,ma,mb,mc,md,rynek)
+%(C) Antoni Wiliñski 2013
+%skrypt strategii S1 w projekcie TEWI
+%S1a - pierwszy kwadrant - oznaczajacy za³o¿enie, ze trend jest rosnacy i
+
+%nale¿y otwierac pozycje d³ugie wg zasady Buy Stop
+
+
+sumRs=zeros(1,6000);
+Ra=zeros(1,6000);
+Rb=zeros(1,6000);
+Rc=zeros(1,6000);
+Rd=zeros(1,6000);
+Rs=zeros(1,6000);
+pocz=max([ma, mb, mc, md])+1;
+if size(C,1)<5000
+    kon = 2047;
+else
+    kon=5000-1;
+end
+ls=0; %liczba otwieranych pozycji
+
+
+for i=pocz:kon
+    if mean(C(i-ma:i,4))<C(i,4)
+        Ra(i)=C(i+1,4)-C(i+1,1); %zysk z i-tej pozycji long zamykanej po jednym kroku (na koñcu swiecy, w której nastapi³o otwarcie)
+    end
+    if mean(C(i-mb:i,4))<C(i,4)
+        Rb(i)=-C(i+1,4)+C(i+1,1);
+    end
+    if mean(C(i-mc:i,4))>C(i,4) 
+        Rc(i)=C(i+1,4)-C(i+1,1);
+    end
+    if mean(C(i-md:i,4))>C(i,4) 
+        Rd(i)=-C(i+1,4)+C(i+1,1);
+    end
+    Rs(i) = Ra(i) + Rb(i) + Rc(i) + Rd(i);
+    ls=ls+1;
+    sumRs(i)=sum(Rs(pocz:i));  %krzywa narastania kapita³u
+    sumRa(i)=sum(Ra(pocz:i));
+    sumRb(i)=sum(Rb(pocz:i));
+    sumRc(i)=sum(Rc(pocz:i));
+    sumRd(i)=sum(Rd(pocz:i));
+end
+
+%obliczenie wspó³czynnika Calmara (stosunku zysku koñcowego do najwiekszego
+%obsuniecia)
+
+recZ=0;  %rekord zysku
+recO=0;  %rekord obsuniecia
+
+for j=1:kon
+    if sumRs(j)>recZ
+        recZ=sumRs(j);
+    end
[…]

### 2013-06-04 Matlabs/S1_article/starter.m

@@ -1,0 +1,20 @@
+clc
+close
+clear
+
+ma=24;
+mb=6;
+mc=6;
+md=21;
+
+EURJPY;
+rynek = 'eurjpy';
+
+
+S1a(C,ma,rynek)
+S1b(C,mb,rynek)
+S1c(C,mc,rynek)
+S1d(C,md,rynek)
+S1s(C,ma,mb,mc,md,rynek)
+
+table_to_latex(rynek)

### 2013-06-04 Matlabs/S1_article/table_to_latex.m

@@ -1,0 +1,37 @@
+function [] = table_to_tex(rynek)
+%%%%%%%%%%%%% LATEX %%%%%%%%%%%%%%%%
+pocz_table = '\\begin{table} \n \\begin{center} \n \\begin{tabular}{|l|l|l|l|l|} \n \\hline \\textbf{strategy} & \\textbf{profit} & \\textbf{bestCalmar} & \\textbf{bestMALength} & \\textbf{la} \\\\ \\hline  \n';
+kon_table = '\\hline \\end{tabular} \n \\end{center} \n \\end{table}';
+
+A = load(['texRa_' rynek '.txt']);
+temp = num2str(A);
+midda_table = ['S1a & ' regexprep(temp,'( )+',' & ') '\\\\ \\hline \n'];
+
+B = load(['texRb_' rynek '.txt']);
+temp = num2str(B);
+middb_table = ['S1b & ' regexprep(temp,'( )+',' & ') '\\\\ \\hline \n'];
+
+C = load(['texRc_' rynek '.txt']);
+temp = num2str(C);
+middc_table = ['S1c & ' regexprep(temp,'( )+',' & ') '\\\\ \\hline \n'];
+
+
+D = load(['texRd_' rynek '.txt']);
+temp = num2str(D);
+middd_table = ['S1d & ' regexprep(temp,'( )+',' & ') '\\\\ \\hline \n'];
+
+S = load(['texRs_' rynek '.txt']);
+temp = num2str(S);
+midds_table = ['S1s & ' regexprep(temp,'( )+',' & ') '\\\\ \n'];
+
+
+
+fileID = fopen(['table_tex_' rynek '.txt'],'w');
+fprintf(fileID,pocz_table);
+fprintf(fileID,midda_table);
+fprintf(fileID,middb_table);
+fprintf(fileID,middc_table);
+fprintf(fileID,middd_table);
+fprintf(fileID,midds_table);
+fprintf(fileID,kon_table);
+fclose(fileID);

### 2013-06-04 Article/Article20130603/tewi-paper-template.tex
Emails
Strategy description

@@
 \author{Antoni Wiliński\inst{1}, Piotr Błaszyński\inst{1}, Aneta Bera\inst{1}, \\ Wojciech Nowicki\inst{1}, Katarzyna Buda\inst{1}}
-\headauthor{A. One, A. Two}
+\headauthor{Antoni Wiliński, Piotr Błaszyński}
 \affiliation{%
@@
   ul.Żołnierska 49, 71-210 Szczecin Poland\\
-  \{awilinski, pblaszynski, abera, wnowicki, kbuda\}@wi.ps.pl
+  \{awilinski, pblaszynski, abera, wnowicki, kbuda\}@wi.zut.edu.pl
 }
@@
 
+The situation described by a set of investment decisions (2) - (5) can be presented in the form of a contractual quadrant - Figure 1
+
 \begin{figure}[h!]
@@
 \FloatBarrier
+
+In this quadrant in quarters a) and b) we have situations (2) and (3) - ie, the closing value of the i bar Ci is greater than the average of the last m bars.
+The first line in those quarters is addressed to top - market is on the rise.
+In the quarter, a) reaction to the growth of the market is open a long position (2).
+The investor behaves as if he was convinced of the existence of a growing trend.
+In the quarter b) investors react on market growth is short position open.
+The investor behaves as if he predicted horizontal trend.
+
+Conversely in quarters, c) and d) the first movement of the market is declining and investor reaction is recorded appropriately in decisions (4) and (5).
+In quarter c) investor behaves as if he predicted horizontal trend and opens long position (4) and in quarter d) in believe of drowdown trend he opens short position (5).
+\\
+These situations are both shown in Figure 2\\
+\indent Figure 2 shows the situation at the close of (i-1) bar marked as Ci-1.
+The investor is following the situation in the I bar and at the moment of its close may immediately calculate each of the four average (1).
+Depending on the direction in which market has changed (upwards or downwards) we are dealing with quarters a and b of quadrant (If there is a price rise of the observed asset) or quarters c and d if there is a decrease.
+Because, at the moment of end of the i bar it can be calculated  value of each of the four average it can also be checked, if some of opening conditions (2)-(5) are passed.
+These four situations extracted from Figure 2 are shown in Figure 3, where in turn are explained  decision-making situations for the four quarters quadrant (Fig.
+1)\\
+\indent The following sketches from a) to d) shows the change in the market against a particular average from Cdmi to Cami.\\
+\indent Each of these averages is counted step by step (bar) separately for each of the four situations, and of course the condition to open a position associated with a particular situation may occur or not.
+For example, if the closing value of the I bar in the situation a) will be below Cami this not open long position.\\
+\indent Extremely important in this strategy is the one and only parameter - number of last bar closures for average calculation.
+In each quarter of quadrant, in the general case the number is different.
+It is determined for a dedicated n number of bars, acting learner section of the time series so that for example for quarter a) :\\
+\begin{equation}
+	m_a = argmax (sum (y_i ) ) (6)
+\end{equation}
+where
+yi = Ci+1 - Ci dla i=1, ..., n, for and complying  condition (2)
+So ma is the parameter learned on a particular section of a time series.
+This m  value,for which achieves a maximum gain of opened positions (for quarter a) long).
+On another length of time series, by (6) it could have different value.
+Similarly, for the parameters ,b, mc and md.\\
+Use of this strategy makes the investor no longer think about the market in the traditional way trying to recognize what kind of a trend at the moment there is or whether this trend has just changed.
+Machine that is learned the optimal value of m for each quarter of quadrant takes over this role and makes decisions in every of four possible investment situations.
+Take these decisions only when each of four calculated optimal moving averages condition is satisfied to open specific position.
+These strategy has been tested on the following markets as simple as possible.
+When was satisfied, one or more of the opening conditions (2) – (5) then position has been opened and closed at the close of the (i +1) bar.
 

### 2013-06-04 Matlabs/S1_article/S1a.m
poprawione pliki

@@ -5,10 +5,11 @@ function [] = S1a (C,ma,rynek)
 %nale¿y otwierac pozycje d³ugie wg zasady Buy Stop
 
 candlesCount = size(C,1);
+candlesCount(1)=5000;
 bestSumRa = -Inf;
 bestCalmara = -Inf;
 
-for ma=ma%10:50
+for ma=ma
     means=zeros(1, candlesCount);
     kon=candlesCount-1;
     for i=2:kon
@@ -73,4 +74,4 @@ plot(bestSumAll);
 xlabel('Candles');
 ylabel('Profit');
 set(hFig, 'PaperPositionMode','auto') ;  %# WYSIWYG
-print(hFig,'-depsc', '-r0',mfilename);
+print(hFig,'-depsc', '-r0',[mfilename '_' rynek]);

### 2013-06-04 Matlabs/S1_article/S1b.m

@@ -5,10 +5,11 @@ function [] = S1b (C,mb,rynek)
 %nale¿y otwierac pozycje krótkie wg zasady Sell Limit
 
 candlesCount = size(C,1);
+candlesCount(1)=5000;
 bestSumRb = -Inf;
 bestCalmarb = -Inf;
 
-for mb=mb%10:50
+for mb=mb
     means=zeros(1, candlesCount);
     kon=candlesCount-1;
     for i=2:kon
@@ -73,4 +74,4 @@ plot(bestSumAll);
 xlabel('Candles');
 ylabel('Profit');
 set(hFig, 'PaperPositionMode','auto');   %# WYSIWYG
-print(hFig,'-depsc', '-r0',mfilename);
+print(hFig,'-depsc', '-r0',[mfilename '_' rynek]);

### 2013-06-04 Matlabs/S1_article/S1c.m

@@ -5,11 +5,12 @@ function [] = S1c (C,mc,rynek)
 %nale¿y otwierac pozycje d³ugie wg zasady Buy Limit
 
 candlesCount = size(C,1);
+candlesCount(1)=5000;
 bestSumRc = -Inf;
 bestCalmarc = -Inf;
 
 
-for mc=mc%10:50%8:70
+for mc=mc
     means=zeros(1, candlesCount);
     kon=candlesCount-1;
     for i=2:kon
@@ -73,4 +74,4 @@ plot(bestSumAll)
 xlabel('Candles');
 ylabel('Profit');
 set(hFig, 'PaperPositionMode','auto')   %# WYSIWYG
-print(hFig,'-depsc', '-r0',mfilename)
+print(hFig,'-depsc', '-r0',[mfilename '_' rynek])

### 2013-06-04 Matlabs/S1_article/S1d.m

@@ -6,10 +6,11 @@ function [] = S1d (C,md,rynek)
 
 
 candlesCount = size(C,1);
+candlesCount(1)=5000;
 bestSumRd = -Inf;
 bestCalmard = -Inf;
 
-for md=md%10:50
+for md=md
     means=zeros(1, candlesCount);
     kon=candlesCount-1;
     for i=2:kon
@@ -75,4 +76,4 @@ plot(bestSumAll)
 xlabel('Candles');
 ylabel('Profit');
 set(hFig, 'PaperPositionMode','auto')   %# WYSIWYG
-print(hFig,'-depsc', '-r0',mfilename)
+print(hFig,'-depsc', '-r0',[mfilename '_' rynek])

### 2013-06-04 Matlabs/S1_article/S1s.m

@@ -80,4 +80,4 @@ plot(bestSumAll)
 xlabel('Candles');
 ylabel('Profit');
 set(hFig, 'PaperPositionMode','auto')   %# WYSIWYG
-print(hFig,'-depsc', '-r0',mfilename)
+print(hFig,'-depsc', '-r0',[mfilename '_' rynek])

### 2013-06-04 Matlabs/S1_article/starter.m

@@ -7,7 +7,7 @@ mb=6;
 mc=6;
 md=21;
 
-EURJPY;
+EURJPY60;
 rynek = 'eurjpy';
 
 

### 2013-06-04 Article/Article20130603/tewi-paper-template.tex
sum -> sigma

@@
 \begin{equation}
-	m_a = argmax (sum (y_i ) ) (6)
+	m_a = argmax (\sum y_i  )
 \end{equation}
 where
-yi = Ci+1 - Ci dla i=1, ..., n, for and complying  condition (2)
+$yi = C_{i+1} - C_{i}$ dla i=1, ..., n, for and complying  condition (2)
 So ma is the parameter learned on a particular section of a time series.

### 2013-06-04 Article/Article20130603/tewi-paper-template.tex
katalog na rysunki

@@
 S1a & 26.177 & 5.5909868 & 24 & 2764\\ \hline 
-S1b & -19.002 & -0.74976326 & 31 & 2801\\ \hline 
-S1c & 12.025 & 2.6645247 & 31 & 2167\\ \hline 
+S1b & -14.774 & -0.67029627 & 6 & 2660\\ \hline 
+S1c & 15.736 & 2.4898734 & 6 & 2332\\ \hline 
 S1d & -4.57 & -0.47001954 & 21 & 2226\\ \hline 
-S1s & 14.33 & 2.957078 & NaN & 4968\\ 
+S1s & 22.54 & 3.2459677 & NaN & 4975\\ 
 \hline \end{tabular} 
@@
 \centering 
-\includegraphics[width=0.82\textwidth]{S1a.eps}
+\includegraphics[width=0.82\textwidth]{images/S1a_eurjpy.eps}
 \subcaption{Profit - S1a}
@@
 \centering 
-\includegraphics[width=0.82\textwidth]{S1b.eps}
+\includegraphics[width=0.82\textwidth]{images/S1b_eurjpy.eps}
 \subcaption{Profit - S1b}
@@
 \centering 
-\includegraphics[width=0.82\textwidth]{S1c.eps}
+\includegraphics[width=0.82\textwidth]{images/S1c_eurjpy.eps}
 \subcaption{Profit- S1c}
@@
 \centering 
-\includegraphics[width=0.82\textwidth]{S1d.eps}
+\includegraphics[width=0.82\textwidth]{images/S1d_eurjpy.eps}
 \subcaption{Profit - S1d}
@@
 \centering 
-\includegraphics[width=0.6\textwidth]{S1s.eps}
+\includegraphics[width=0.6\textwidth]{images/S1s_eurjpy.eps}
 \label{mansard}

### 2013-06-04 Article/Article20130603/tewi-paper-template.tex
dodane wykresy i wyniki dla pozostałych rynków. poprawki w tekście

@@
 
-\title{Magnitude of simple rules in investment strategies of algorithmic trading}
-\headtitle{Magnitude of simple rules in investment strategies of algorithmic trading\dots}
+\title{Meaning of simple rules in investment strategies of algorithmic trading}
+\headtitle{Meaning of simple rules in investment strategies of algorithmic trading\dots}
 \author{Antoni Wiliński\inst{1}, Piotr Błaszyński\inst{1}, Aneta Bera\inst{1}, \\ Wojciech Nowicki\inst{1}, Katarzyna Buda\inst{1}}
@@
 \indent The essence of the concept is the idea of simultaneous open long and short positions based on various signals, in this case the intersection graph (values of exchange rate  and stock index) and average of the last m closing of this price.\\
-Equally simple is the closing rule of each opened position. It's closed at the close of (i+1) bar (fig. 1).
-Let C be considering constantly changing prices of value, and Ci closing price of I OHLC bar (Open, High, Low, Close). Denote Cmi as average of m last close
+Equally simple is the closing rule of each opened position. It's closed at the close of (i+1)th bar (Fig. 1).
+Let C be considering constantly changing prices of value, and $C_i$ closing price of i-th OHLC bar (Open, High, Low, Close). Denote $C_{m_{i}}$ as average of m last close
 \begin{equation} \label{label-of-equation-1}
-  C_{m_{i}} = \frac{C_{i-m} + C_{i-m+1} + … + C_{i}}{m}; 
+  C_{m_{i}} = \frac{C_{i-m} + C_{i-m+1} + … + C_{i}}{m+1}; \hspace{1em}m>0; 
 \end{equation}
 
-At the moment of I bar closing, value can be compared with the $C_{m_{i}}$ average.
+At the moment of i-th bar closing, value can be compared with the $C_{m_{i}}$ average.
 Depending on the investor's beliefs about the existence of a particular trend are thus four possible decision-making situations:
-\begin{enumerate}
-\item If $C_i  > C_{m_{i}}$  long position will be open,
-\item If $C_i  > C_{m_{i}}$  short position will be open,
-\item If $C_i  < C_{m_{i}}$  long position will be open,
-\item If $C_i  < C_{m_{i}}$  short position will be open.
-\end{enumerate}
+\begin{equation} If\ C_i  > C_{m_{i}}\   long\ position\ will\ be\ open;\ m=m_b. \end{equation}
+\begin{equation} If\ C_i  > C_{m_{i}}\   short\ position\ will\ be\ open;\ m=m_b. \end{equation}
+\begin{equation} If\ C_i  < C_{m_{i}}\   long\ position\ will\ be\ open;\ m=m_c. \end{equation}
+\begin{equation} If\ C_i  < C_{m_{i}}\   short\ position\ will\ be\ open;\ m=m_d. \end{equation}
 
@@
 Should be noted that each of the above decisions is taken basing on average of different number of last close bar prices.
-Therefore, in the general case at the close moment close of I bar when it should make decision of open (short or long) it could happen that may occur up to four different levels of the average value calculated for the last m bars (different for each contractual quadrant).\\
+Therefore, in the general case at the close moment close of i-th bar when it should make decision of open (short or long) it could happen that may occur up to four different levels of the average value calculated for the last m bars (different for each contractual quadrant).\\
 These situations are shown in Figure 1
@@
 
-\begin{figure}[h]
-\centering
-\centering 
-\includegraphics[width=\textwidth]{rysunek1pp.eps}
-\caption{All versions}
-\end{figure}
-\FloatBarrier
-
-In this quadrant in quarters a) and b) we have situations (2) and (3) - ie, the closing value of the i bar Ci is greater than the average of the last m bars.
+In this quadrant in quarters a) and b) we have situations (2) and (3) - ie, the closing value of the i bar $C_i$ is greater than the average of the last m bars.
 The first line in those quarters is addressed to top - market is on the rise.
@@
 These situations are both shown in Figure 2\\
-\indent Figure 2 shows the situation at the close of (i-1) bar marked as Ci-1.
-The investor is following the situation in the I bar and at the moment of its close may immediately calculate each of the four average (1).
+\begin{figure}[h]
+\centering
+\centering 
+\includegraphics[width=\textwidth]{rysunek1pp.eps}
+\caption{All possible situations for four different moving averages}
+\end{figure}
+\FloatBarrier
+\indent Figure 2 shows the situation at the close of (i-1) bar marked as $C_{i-1}$.
+The investor is following the situation in the i-th bar and at the moment of its close may immediately calculate each of the four average (1).
 Depending on the direction in which market has changed (upwards or downwards) we are dealing with quarters a and b of quadrant (If there is a price rise of the observed asset) or quarters c and d if there is a decrease.
@@
 1)\\
-\indent The following sketches from a) to d) shows the change in the market against a particular average from Cdmi to Cami.\\
-\indent Each of these averages is counted step by step (bar) separately for each of the four situations, and of course the condition to open a position associated with a particular situation may occur or not.
-For example, if the closing value of the I bar in the situation a) will be below Cami this not open long position.\\
-\indent Extremely important in this strategy is the one and only parameter - number of last bar closures for average calculation.
-In each quarter of quadrant, in the general case the number is different.
-It is determined for a dedicated n number of bars, acting learner section of the time series so that for example for quarter a) :\\
-\begin{equation}
-	m_a = argmax (\sum y_i  )
-\end{equation}
-where
-$yi = C_{i+1} - C_{i}$ dla i=1, ..., n, for and complying  condition (2)
-So ma is the parameter learned on a particular section of a time series.
-This m  value,for which achieves a maximum gain of opened positions (for quarter a) long).
-On another length of time series, by (6) it could have different value.
-Similarly, for the parameters ,b, mc and md.\\
-Use of this strategy makes the investor no longer think about the market in the traditional way trying to recognize what kind of a trend at the moment there is or whether this trend has just changed.
-Machine that is learned the optimal value of m for each quarter of quadrant takes over this role and makes decisions in every of four possible investment situations.
-Take these decisions only when each of four calculated optimal moving averages condition is satisfied to open specific position.
-These strategy has been tested on the following markets as simple as possible.
-When was satisfied, one or more of the opening conditions (2) – (5) then position has been opened and closed at the close of the (i +1) bar.
-
 \begin{figure}[h]
@@
 \FloatBarrier
+\indent The following sketches from a) to d) shows the change in the market against a particular average from $C^d_{m_{i}}$ to $C^a_{m_{i}}$.\\
+\indent Each of these averages is counted step by step (bar) separately for each of the four situations, and of course the condition to open a position associated with a particular situation may occur or not.
+For example, if the closing value of the i-th bar in the situation a) will be below Cami this not open long position.\\
+\indent Extremely important in this strategy is the one and only parameter - number of last bar closures for average calculation.
+In each quarter of quadrant, in the general case the number is different.
+It is determined for a dedicated n number of bars, acting learner section of the time series so that for example for quarter a) :\\
+\begin{equation}
+	m_a = argmax (\sum y_i  )
+\end{equation}
+where:\\
+$yi = C_{i+1} - C_{i}$ dla i=1, ..., n, for and complying  condition (2).\\
+So ma is the parameter learned on a particular section of a time series.
+This m  value,for which achieves a maximum gain of opened positions (for quarter a) long).
+On another length of time series, by (6) it could have different value.
+Similarly, for the parameters ,b, mc and md.\\
+Use of this strategy makes the investor no longer think about the market in the traditional way trying to recognize what kind of a trend at the moment there is or whether this trend has just changed.
+Machine that is learned the optimal value of m for each quarter of quadrant takes over this role and makes decisions in every of four possible investment situations.
+Take these decisions only when each of four calculated optimal moving averages condition is satisfied to open specific position.
+These strategy has been tested on the following markets as simple as possible.
+When was satisfied, one or more of the opening conditions (2) – (5) then position has been opened and closed at the close of the (i +1) bar.
 
@@
 The study of strategy was carried out on the following markets:
-currency pairs: EURUSD...
-stock indexes: 
-commodities:
-
+\begin{itemize}
+\item currency pairs: EURUSD, EURJPY, USDJPY, GBPUSD,
+\item indexes: FUS500, BOSSAPLN,
+\item commodities: FGOLD. FSILVER.
+\end{itemize}
+BOSSAPLN is currency index that represents ratio of PLN to four other currencies. Every currency pair used to calculate index has other weight USDPLN (40\%), EURPLN (50\%), GBPPLN (5\%), CHFPLN (5\%).
+\newpage
 \begin{table}[!t]
-\caption{Profits for all strategy quadrants} 
+\caption{Profits for all strategy quadrants for EURJPY} 
  \begin{center} 
@@
 S1d & -4.57 & -0.47001954 & 21 & 2226\\ \hline 
-S1s & 22.54 & 3.2459677 & NaN & 4975\\ 
+S1s & 22.54 & 3.2459677 & Group of MA & 4975\\ 
 \hline \end{tabular} 
@@
 
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+\newpage
+\begin{table}[!t]
+\caption{Profits for all strategy quadrants for FSILVER} 
+ \begin{center} 
+ \begin{tabular}{|l|l|l|l|l|} 
+ \hline \textbf{strategy} & \textbf{profit} & \textbf{bestCalmar} & \textbf{bestMALength} & \textbf{la} \\ \hline  
+S1a & -5.31 & -0.64520049 & 81 & 2582\\ \hline 
+S1b & 17.22 & 5.8571429 & 10 & 2508\\ \hline 
+S1c & 4.17 & 0.55525965 & 10 & 2473\\ \hline 
+S1d & 6.95 & 1.3314176 & 81 & 2336\\ \hline 
+S1s & 21.96 & 5.5454545 & Group of MA & 4918\\ 
+\hline \end{tabular} 
+ \end{center} 
+ \end{table}
+\FloatBarrier
+
+\begin{figure}[h]
+\centering
+\begin{minipage}{.49\linewidth}
+\centering 
+\includegraphics[width=0.82\textwidth]{images/S1a_silver.eps}
+\subcaption{Profit - S1a}
+\label{jedno}
+\end{minipage}
+\begin{minipage}{.49\linewidth}
+\centering 
+\includegraphics[width=0.82\textwidth]{images/S1b_silver.eps}
+\subcaption{Profit - S1b}
+\label{dwu}
+\end{minipage}
+\\
+\begin{minipage}{.49\linewidth}
+\centering 
+\includegraphics[width=0.82\textwidth]{images/S1c_silver.eps}
+\subcaption{Profit- S1c}
+\label{cztero}
+\end{minipage}
+\begin{minipage}{.49\linewidth}
+\centering 
+\includegraphics[width=0.82\textwidth]{images/S1d_silver.eps}
+\subcaption{Profit - S1d}
+\label{mansard}
+\end{minipage}
+\begin{minipage}{\linewidth}
+\centering 
+\includegraphics[width=0.6\textwidth]{images/S1s_silver.eps}
+\label{mansard}
+\subcaption{Profit - S1s}
+\end{minipage}
+\caption{FSILVER market results}
+\end{figure}
+\FloatBarrier
+
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+\newpage
+\begin{table}[!t]
+\caption{Profits for all strategy quadrants for BOSSAPLN} 
+ \begin{center} 
+ \begin{tabular}{|l|l|l|l|l|} 
+ \hline \textbf{strategy} & \textbf{profit} & \textbf{bestCalmar} & \textbf{bestMALength} & \textbf{la} \\ \hline  
+S1a & 5.87 & 1.9898305 & 21 & 2474\\ \hline 
+S1b & 2.86 & 0.6059322 & 5 & 2416\\ \hline 
+S1c & 10.91 & 4.3293651 & 5 & 2547\\ \hline 
+S1d & -2.23 & -0.4247619 & 21 & 2502\\ \hline 
+S1s & 17.91 & 4.3470874 & Group of MA & 4978\\ 
+\hline \end{tabular} 
+ \end{center} 
+ \end{table}
+\FloatBarrier
+
+\begin{figure}[h]
+\centering
+\begin{minipage}{.49\linewidth}
+\centering 
+\includegraphics[width=0.82\textwidth]{images/S1a_bossa.eps}
+\subcaption{Profit - S1a}
+\label{jedno}
+\end{minipage}
+\begin{minipage}{.49\linewidth}
+\centering 
+\includegraphics[width=0.82\textwidth]{images/S1b_bossa.eps}
+\subcaption{Profit - S1b}
+\label{dwu}
+\end{minipage}
+\\
+\begin{minipage}{.49\linewidth}
+\centering 
+\includegraphics[width=0.82\textwidth]{images/S1c_bossa.eps}
+\subcaption{Profit- S1c}
+\label{cztero}
+\end{minipage}
+\begin{minipage}{.49\linewidth}
+\centering 
+\includegraphics[width=0.82\textwidth]{images/S1d_bossa.eps}
+\subcaption{Profit - S1d}
+\label{mansard}
+\end{minipage}
+\begin{minipage}{\linewidth}
+\centering 
+\includegraphics[width=0.6\textwidth]{images/S1s_bossa.eps}
+\label{mansard}
+\subcaption{Profit - S1s}
+\end{minipage}
+\caption{BOSSAPLN market results}
+\end{figure}
+\FloatBarrier
+
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+\newpage
+\begin{table}[!t]
+\caption{Profits for all strategy quadrants for FUS500} 
+ \begin{center} 
+ \begin{tabular}{|l|l|l|l|l|} 
+ \hline \textbf{strategy} & \textbf{profit} & \textbf{bestCalmar} & \textbf{bestMALength} & \textbf{la} \\ \hline  
+S1a & 274.89 & 5.4433663 & 83 & 3200\\ \hline 
+S1b & -70.94 & -0.47328041 & 15 & 2798\\ \hline 
+S1c & 291.62 & 4.2584696 & 15 & 2186\\ \hline 
+S1d & -106.67 & -0.73237212 & 82 & 1723\\ \hline 
+S1s & 344.29 & 2.0821893 & Group of MA & 4916\\ 
+\hline \end{tabular} 
+ \end{center} 
+ \end{table}
+\FloatBarrier
+
+\begin{figure}[h]
+\centering
+\begin{minipage}{.49\linewidth}
+\centering 
+\includegraphics[width=0.82\textwidth]{images/S1a_fus.eps}
+\subcaption{Profit - S1a}
+\label{jedno}
+\end{minipage}
+\begin{minipage}{.49\linewidth}
+\centering 
+\includegraphics[width=0.82\textwidth]{images/S1b_fus.eps}
+\subcaption{Profit - S1b}
+\label{dwu}
+\end{minipage}
+\\
+\begin{minipage}{.49\linewidth}
+\centering 
+\includegraphics[width=0.82\textwidth]{images/S1c_fus.eps}
+\subcaption{Profit- S1c}
+\label{cztero}
+\end{minipage}
+\begin{minipage}{.49\linewidth}
+\centering 
+\includegraphics[width=0.82\textwidth]{images/S1d_fus.eps}
+\subcaption{Profit - S1d}
+\label{mansard}
+\end{minipage}
+\begin{minipage}{\linewidth}
+\centering 
+\includegraphics[width=0.6\textwidth]{images/S1s_fus.eps}
+\label{mansard}
+\subcaption{Profit - S1s}
+\end{minipage}
+\caption{FUS500 market results}
+\end{figure}
+\FloatBarrier
+
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+\newpage
+\begin{table}[!t]
+\caption{Profits for all strategy quadrants for FGOLD} 
+ \begin{center} 
+ \begin{tabular}{|l|l|l|l|l|} 
+ \hline \textbf{strategy} & \textbf{profit} & \textbf{bestCalmar} & \textbf{bestMALength} & \textbf{la} \\ \hline  
+S1a & 61.16 & 0.58503922 & 51 & 2578\\ \hline 
+S1b & 227.58 & 2.8169328 & 5 & 2519\\ \hline 
+S1c & 30.38 & 0.12023588 & 5 & 2470\\ \hline 
+S1d & 248.21 & 1.5167125 & 51 & 2370\\ \hline 
+S1s & 599.88 & 4.6027776 & Group of MA & 4948\\ 
+\hline \end{tabular} 
+ \end{center} 
+ \end{table}
+\FloatBarrier
+
+\begin{figure}[h]
+\centering
+\begin{minipage}{.49\linewidth}
+\centering 
+\includegraphics[width=0.82\textwidth]{images/S1a_gold.eps}
+\subcaption{Profit - S1a}
+\label{jedno}
+\end{minipage}
+\begin{minipage}{.49\linewidth}
+\centering 
+\includegraphics[width=0.82\textwidth]{images/S1b_gold.eps}
+\subcaption{Profit - S1b}
+\label{dwu}
+\end{minipage}
+\\
+\begin{minipage}{.49\linewidth}
+\centering 
+\includegraphics[width=0.82\textwidth]{images/S1c_gold.eps}
+\subcaption{Profit- S1c}
+\label{cztero}
+\end{minipage}
+\begin{minipage}{.49\linewidth}
+\centering 
+\includegraphics[width=0.82\textwidth]{images/S1d_gold.eps}
+\subcaption{Profit - S1d}
+\label{mansard}
+\end{minipage}
+\begin{minipage}{\linewidth}
+\centering 
+\includegraphics[width=0.6\textwidth]{images/S1s_gold.eps}
+\label{mansard}
+\subcaption{Profit - S1s}
+\end{minipage}
+\caption{FGOLD market results}
+\end{figure}
+\FloatBarrier
+
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+\newpage
+\begin{table}[!t]
+\caption{Profits for all strategy quadrants for GBPUSD} 
+ \begin{center} 
+ \begin{tabular}{|l|l|l|l|l|} 
+ \hline \textbf{strategy} & \textbf{profit} & \textbf{bestCalmar} & \textbf{bestMALength} & \textbf{la} \\ \hline  
+S1a & 0.05736 & 1.061436 & 92 & 2588\\ \hline 
+S1b & 0.12055 & 3.4101839 & 5 & 2513\\ \hline 
+S1c & 0.15356 & 3.1116515 & 5 & 2475\\ \hline 
+S1d & 0.01724 & 0.31254532 & 92 & 2319\\ \hline 
+S1s & 0.36007 & 6.892611 & Group of MA & 4907\\ 
+\hline \end{tabular} 
+ \end{center} 
+ \end{table}
+\FloatBarrier
+
+\begin{figure}[h]
+\centering
+\begin{minipage}{.49\linewidth}
+\centering 
+\includegraphics[width=0.82\textwidth]{images/S1a_gbpusd.eps}
+\subcaption{Profit - S1a}
+\label{jedno}
+\end{minipage}
+\begin{minipage}{.49\linewidth}
+\centering 
+\includegraphics[width=0.82\textwidth]{images/S1b_gbpusd.eps}
+\subcaption{Profit - S1b}
+\label{dwu}
+\end{minipage}
+\\
+\begin{minipage}{.49\linewidth}
+\centering 
+\includegraphics[width=0.82\textwidth]{images/S1c_gbpusd.eps}
+\subcaption{Profit- S1c}
+\label{cztero}
+\end{minipage}
+\begin{minipage}{.49\linewidth}
+\centering 
+\includegraphics[width=0.82\textwidth]{images/S1d_gbpusd.eps}
+\subcaption{Profit - S1d}
+\label{mansard}
+\end{minipage}
+\begin{minipage}{\linewidth}
+\centering 
+\includegraphics[width=0.6\textwidth]{images/S1s_gbpusd.eps}
+\label{mansard}
+\subcaption{Profit - S1s}
+\end{minipage}
+\caption{GBPUSD market results}
+\end{figure}
+\FloatBarrier
+
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+\newpage
+\begin{table}[!t]
+\caption{Profits for all strategy quadrants for USDJPY} 
+ \begin{center} 
+ \begin{tabular}{|l|l|l|l|l|} 
+ \hline \textbf{strategy} & \textbf{profit} & \textbf{bestCalmar} & \textbf{bestMALength} & \textbf{la} \\ \hline  
+S1a & 17.189 & 8.2362242 & 18 & 2693\\ \hline 
+S1b & -9.802 & -0.73511324 & 54 & 2665\\ \hline 
+S1c & 5.65 & 2.0582878 & 54 & 2280\\ \hline 
+S1d & 1.867 & 0.60715447 & 18 & 2287\\ \hline 
+S1s & 14.854 & 5.682479 & Group of MA & 4945\\ 
+\hline \end{tabular} 
+ \end{center} 
+ \end{table}
+\FloatBarrier
+
+\begin{figure}[h]
+\centering
+\begin{minipage}{.49\linewidth}
+\centering 
+\includegraphics[width=0.82\textwidth]{images/S1a_usdjpy.eps}
+\subcaption{Profit - S1a}
+\label{jedno}
+\end{minipage}
+\begin{minipage}{.49\linewidth}
+\centering 
+\includegraphics[width=0.82\textwidth]{images/S1b_usdjpy.eps}
+\subcaption{Profit - S1b}
+\label{dwu}
+\end{minipage}
+\\
+\begin{minipage}{.49\linewidth}
+\centering 
+\includegraphics[width=0.82\textwidth]{images/S1c_usdjpy.eps}
+\subcaption{Profit- S1c}
+\label{cztero}
+\end{minipage}
+\begin{minipage}{.49\linewidth}
+\centering 
+\includegraphics[width=0.82\textwidth]{images/S1d_usdjpy.eps}
+\subcaption{Profit - S1d}
+\label{mansard}
+\end{minipage}
+\begin{minipage}{\linewidth}
+\centering 
+\includegraphics[width=0.6\textwidth]{images/S1s_usdjpy.eps}
+\label{mansard}
+\subcaption{Profit - S1s}
+\end{minipage}
+\caption{USDJPY market results}
+\end{figure}
+\FloatBarrier
+
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
 \section{Conclusions}
@@
 Purpose of this paper was to prove the thesis, that even the simplest strategy has some potential profit, whose using is fascinating challenge.\\
-\indent The authors believe, due to observing results of experiments, that the thesis of this dormant potential has been acknowledged.
+\indent The authors believe, due to observing results of experiments, that the thesis of this dormant potential has been acknowledged. \\
+The results show that depending on the current market characteristics, it was possible to temporarily disable some quarters from trade to get better profits.
+Of course, they should still be calculated in the background, to be able include in trade if market characteristic will change.
 

### 2013-06-04 Article/Article20130603/tewi-paper-template.tex
poprawki - angielski

@@
 In article are shown studies of the possibly simplest investment strategy of algo trading.
-The authors' intention was to prove the thesis that in the greedy algorithmic trading directed to the appropriate response, not to forecast, there are almost always opportunities to achieve profit.
+The authors' intention was to prove the thesis that in the greedy algorithmic trading directed to the proper response, not to forecast, there are almost always opportunities to achieve profit.
 This paper presents the results of tests for over twenty core markets - currency pairs, indices and commodities.
 Introduced the original concept of quadrant of openings on each bar.
-In principle, the strategy is not relevant investment (studies were conducted without transaction costs), only cognitive in order to develop
+In principle, the strategy is not relevant investment (studies were conducted without transaction costs), only cognitive in order to develop.
 \end{abstract}
@@
 Modern computing capabilities allow to change researcher relationship to predictive challenge.
-If the aim is to be effective investment, not the successful prediction, research target should be changed.
+If the purpose of this research is to be effective investment, not the successful prediction, research target should be changed.
 Many scientific papers was devoted to the problem of investment efficiency, also including the best quality papers, as well as work of at least several Nobel Prize winners.
@@
 Trying to take advantage of this simple patterns (classification rules) in investment strategies.\\
-\indent The aim of papper is to verify thesis about effectiveness of such simple rules of opening and closing position on trading markets.
+\indent The purpose of this papper is to verify thesis about effectiveness of such simple rules of opening and closing position on trading markets.
 High frequency open positions algo trading are considering here \cite{muriel04}.
@@
 Usually these conditions turn out to be too easy to achieve satisfactory transaction efficiency.\\
-\indent Close terms in such investment strategies are also very simple. They are mostly based on similar terms, resulting from mean values or number of bars that elapsed since open.
-Similar concept will be considered in this study.
-This concept belongs simple rules group, extracted from repeated patterns in the time series of financial instruments.
+\indent Close terms in such investment strategies are also very simple.
+They are mostly based on similar terms, resulting from mean values or number of bars that elapsed since open.Other popular methods of closing such positions are Stop Loss and Take Profit.
+Similar concept will be considered in this paper.
+This concept belongs to group of simple rules, extracted from repeated patterns in the time series of financial instruments.
 Most commonly, these rules include a group or sequence of conditions besides using moving averages also uses differences in average, first derivative, standard deviation (Bollinger Bands) or pivot points.

### 2013-06-04 Article/Article20130603/tewi-paper-template.tex
zmieniona dokładność w tablekach do dwóch miejsc po przecinku

@@
  \hline \textbf{strategy} & \textbf{profit} & \textbf{bestCalmar} & \textbf{bestMALength} & \textbf{la} \\ \hline  
-S1a & 26.177 & 5.5909868 & 24 & 2764\\ \hline 
-S1b & -14.774 & -0.67029627 & 6 & 2660\\ \hline 
-S1c & 15.736 & 2.4898734 & 6 & 2332\\ \hline 
-S1d & -4.57 & -0.47001954 & 21 & 2226\\ \hline 
-S1s & 22.54 & 3.2459677 & Group of MA & 4975\\ 
+S1a & 26.18 & 5.59 & 24 & 2764\\ \hline 
+S1b & -14.77 & -0.67 & 6 & 2660\\ \hline 
+S1c & 15.74 & 2.49 & 6 & 2332\\ \hline 
+S1d & -4.57 & -0.47 & 21 & 2226\\ \hline 
+S1s & 22.54 & 3.25 & Group of MA & 4975\\ 
 \hline \end{tabular} 
@@
  \hline \textbf{strategy} & \textbf{profit} & \textbf{bestCalmar} & \textbf{bestMALength} & \textbf{la} \\ \hline  
-S1a & -5.31 & -0.64520049 & 81 & 2582\\ \hline 
-S1b & 17.22 & 5.8571429 & 10 & 2508\\ \hline 
-S1c & 4.17 & 0.55525965 & 10 & 2473\\ \hline 
-S1d & 6.95 & 1.3314176 & 81 & 2336\\ \hline 
-S1s & 21.96 & 5.5454545 & Group of MA & 4918\\ 
+S1a & -5.31 & -0.65 & 81 & 2582\\ \hline 
+S1b & 17.22 & 5.86 & 10 & 2508\\ \hline 
+S1c & 4.17 & 0.56 & 10 & 2473\\ \hline 
+S1d & 6.95 & 1.33 & 81 & 2336\\ \hline 
+S1s & 21.96 & 5.55 & Group of MA & 4918\\ 
 \hline \end{tabular} 
@@
  \hline \textbf{strategy} & \textbf{profit} & \textbf{bestCalmar} & \textbf{bestMALength} & \textbf{la} \\ \hline  
-S1a & 5.87 & 1.9898305 & 21 & 2474\\ \hline 
-S1b & 2.86 & 0.6059322 & 5 & 2416\\ \hline 
-S1c & 10.91 & 4.3293651 & 5 & 2547\\ \hline 
-S1d & -2.23 & -0.4247619 & 21 & 2502\\ \hline 
-S1s & 17.91 & 4.3470874 & Group of MA & 4978\\ 
+S1a & 5.87 & 1.99 & 21 & 2474\\ \hline 
+S1b & 2.86 & 0.61 & 5 & 2416\\ \hline 
+S1c & 10.91 & 4.33 & 5 & 2547\\ \hline 
+S1d & -2.23 & -0.42 & 21 & 2502\\ \hline 
+S1s & 17.91 & 4.35 & Group of MA & 4978\\ 
 \hline \end{tabular} 
@@
  \hline \textbf{strategy} & \textbf{profit} & \textbf{bestCalmar} & \textbf{bestMALength} & \textbf{la} \\ \hline  
-S1a & 274.89 & 5.4433663 & 83 & 3200\\ \hline 
-S1b & -70.94 & -0.47328041 & 15 & 2798\\ \hline 
-S1c & 291.62 & 4.2584696 & 15 & 2186\\ \hline 
-S1d & -106.67 & -0.73237212 & 82 & 1723\\ \hline 
-S1s & 344.29 & 2.0821893 & Group of MA & 4916\\ 
+S1a & 274.89 & 5.44 & 83 & 3200\\ \hline 
+S1b & -70.94 & -0.47 & 15 & 2798\\ \hline 
+S1c & 291.62 & 4.26 & 15 & 2186\\ \hline 
+S1d & -106.67 & -0.73 & 82 & 1723\\ \hline 
+S1s & 344.29 & 2.08 & Group of MA & 4916\\ 
 \hline \end{tabular} 
@@
  \hline \textbf{strategy} & \textbf{profit} & \textbf{bestCalmar} & \textbf{bestMALength} & \textbf{la} \\ \hline  
-S1a & 61.16 & 0.58503922 & 51 & 2578\\ \hline 
-S1b & 227.58 & 2.8169328 & 5 & 2519\\ \hline 
-S1c & 30.38 & 0.12023588 & 5 & 2470\\ \hline 
-S1d & 248.21 & 1.5167125 & 51 & 2370\\ \hline 
-S1s & 599.88 & 4.6027776 & Group of MA & 4948\\ 
+S1a & 61.16 & 0.59 & 51 & 2578\\ \hline 
+S1b & 227.58 & 2.82 & 5 & 2519\\ \hline 
+S1c & 30.38 & 0.12 & 5 & 2470\\ \hline 
+S1d & 248.21 & 1.52 & 51 & 2370\\ \hline 
+S1s & 599.88 & 4.60 & Group of MA & 4948\\ 
 \hline \end{tabular} 
@@
  \hline \textbf{strategy} & \textbf{profit} & \textbf{bestCalmar} & \textbf{bestMALength} & \textbf{la} \\ \hline  
-S1a & 0.05736 & 1.061436 & 92 & 2588\\ \hline 
-S1b & 0.12055 & 3.4101839 & 5 & 2513\\ \hline 
-S1c & 0.15356 & 3.1116515 & 5 & 2475\\ \hline 
-S1d & 0.01724 & 0.31254532 & 92 & 2319\\ \hline 
-S1s & 0.36007 & 6.892611 & Group of MA & 4907\\ 
+S1a & 0.06 & 1.06 & 92 & 2588\\ \hline 
+S1b & 0.12 & 3.41 & 5 & 2513\\ \hline 
+S1c & 0.15 & 3.11 & 5 & 2475\\ \hline 
+S1d & 0.02 & 0.31 & 92 & 2319\\ \hline 
+S1s & 0.36 & 6.89 & Group of MA & 4907\\ 
 \hline \end{tabular} 
@@
  \hline \textbf{strategy} & \textbf{profit} & \textbf{bestCalmar} & \textbf{bestMALength} & \textbf{la} \\ \hline  
-S1a & 17.189 & 8.2362242 & 18 & 2693\\ \hline 
-S1b & -9.802 & -0.73511324 & 54 & 2665\\ \hline 
-S1c & 5.65 & 2.0582878 & 54 & 2280\\ \hline 
-S1d & 1.867 & 0.60715447 & 18 & 2287\\ \hline 
-S1s & 14.854 & 5.682479 & Group of MA & 4945\\ 
+S1a & 17.19 & 8.24 & 18 & 2693\\ \hline 
+S1b & -9.80 & -0.74 & 54 & 2665\\ \hline 
+S1c & 5.65 & 2.06 & 54 & 2280\\ \hline 
+S1d & 1.87 & 0.61 & 18 & 2287\\ \hline 
+S1s & 14.85 & 5.68 & Group of MA & 4945\\ 
 \hline \end{tabular} 

### 2013-06-04 Article/Article20130603/tewi-paper-template.tex
zmiana kolejnosci wykresów/tabeli w wynikach testów na taką jaka jest wczesniej opisana poprawki związane z angielskim

@@
 \indent Close terms in such investment strategies are also very simple.
-They are mostly based on similar terms, resulting from mean values or number of bars that elapsed since open.Other popular methods of closing such positions are Stop Loss and Take Profit.
+They are mostly based on similar terms, resulting from mean values or number of bars that elapsed since open.
+Other popular methods of closing such positions are Stop Loss and Take Profit.
 Similar concept will be considered in this paper.
@@
 Friesen, Weller i Dunham \cite{friesen09} say that these methods were for many years rather neglected by the academic community, despite frequent, or perhaps because of, use by trade practitioners on the stock exchange.
-This opinion is not completely correct, because even Eugene Fama, creator of the efficient markets theory \cite{fama91}, admitted later that  there is little evidence of of simple rules efficiency \cite{fama98}.
+This opinion is not completely correct, because even Eugene Fama, creator of the efficient markets theory \cite{fama91}, admitted later that  there is little evidence of simple rules efficiency \cite{fama98}.
 Cai and Keasey \cite{cai05} noted both predictive and investing efficiency of simplest rules based on differences in derivatives averages and levels of price direction changes.
@@
 Depending on the investor's beliefs about the existence of a particular trend are thus four possible decision-making situations:
-\begin{equation} If\ C_i  > C_{m_{i}}\   long\ position\ will\ be\ open;\ m=m_b. \end{equation}
+\begin{equation} If\ C_i  > C_{m_{i}}\   long\ position\ will\ be\ open;\ m=m_a. \end{equation}
 \begin{equation} If\ C_i  > C_{m_{i}}\   short\ position\ will\ be\ open;\ m=m_b. \end{equation}
@@
 \FloatBarrier
-
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
@@
 \begin{table}[!t]
-\caption{Profits for all strategy quadrants for FSILVER} 
+\caption{Profits for all strategy quadrants for USDJPY} 
  \begin{center} 
@@
  \hline \textbf{strategy} & \textbf{profit} & \textbf{bestCalmar} & \textbf{bestMALength} & \textbf{la} \\ \hline  
-S1a & -5.31 & -0.65 & 81 & 2582\\ \hline 
-S1b & 17.22 & 5.86 & 10 & 2508\\ \hline 
-S1c & 4.17 & 0.56 & 10 & 2473\\ \hline 
-S1d & 6.95 & 1.33 & 81 & 2336\\ \hline 
-S1s & 21.96 & 5.55 & Group of MA & 4918\\ 
+S1a & 17.19 & 8.24 & 18 & 2693\\ \hline 
+S1b & -9.80 & -0.74 & 54 & 2665\\ \hline 
+S1c & 5.65 & 2.06 & 54 & 2280\\ \hline 
+S1d & 1.87 & 0.61 & 18 & 2287\\ \hline 
+S1s & 14.85 & 5.68 & Group of MA & 4945\\ 
 \hline \end{tabular} 
@@
 \centering 
-\includegraphics[width=0.82\textwidth]{images/S1a_silver.eps}
+\includegraphics[width=0.82\textwidth]{images/S1a_usdjpy.eps}
 \subcaption{Profit - S1a}
@@
 \centering 
-\includegraphics[width=0.82\textwidth]{images/S1b_silver.eps}
+\includegraphics[width=0.82\textwidth]{images/S1b_usdjpy.eps}
 \subcaption{Profit - S1b}
@@
 \centering 
-\includegraphics[width=0.82\textwidth]{images/S1c_silver.eps}
+\includegraphics[width=0.82\textwidth]{images/S1c_usdjpy.eps}
 \subcaption{Profit- S1c}
@@
 \centering 
-\includegraphics[width=0.82\textwidth]{images/S1d_silver.eps}
+\includegraphics[width=0.82\textwidth]{images/S1d_usdjpy.eps}
 \subcaption{Profit - S1d}
@@
 \centering 
-\includegraphics[width=0.6\textwidth]{images/S1s_silver.eps}
+\includegraphics[width=0.6\textwidth]{images/S1s_usdjpy.eps}
 \label{mansard}
@@
 \end{minipage}
-\caption{FSILVER market results}
+\caption{USDJPY market results}
+\end{figure}
+\FloatBarrier
+
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+\newpage
+\begin{table}[!t]
+\caption{Profits for all strategy quadrants for GBPUSD} 
+ \begin{center} 
+ \begin{tabular}{|l|l|l|l|l|} 
+ \hline \textbf{strategy} & \textbf{profit} & \textbf{bestCalmar} & \textbf{bestMALength} & \textbf{la} \\ \hline  
+S1a & 0.06 & 1.06 & 92 & 2588\\ \hline 
+S1b & 0.12 & 3.41 & 5 & 2513\\ \hline 
+S1c & 0.15 & 3.11 & 5 & 2475\\ \hline 
+S1d & 0.02 & 0.31 & 92 & 2319\\ \hline 
+S1s & 0.36 & 6.89 & Group of MA & 4907\\ 
+\hline \end{tabular} 
+ \end{center} 
+ \end{table}
+\FloatBarrier
+
+\begin{figure}[h]
+\centering
+\begin{minipage}{.49\linewidth}
+\centering 
+\includegraphics[width=0.82\textwidth]{images/S1a_gbpusd.eps}
+\subcaption{Profit - S1a}
+\label{jedno}
+\end{minipage}
+\begin{minipage}{.49\linewidth}
+\centering 
+\includegraphics[width=0.82\textwidth]{images/S1b_gbpusd.eps}
+\subcaption{Profit - S1b}
+\label{dwu}
+\end{minipage}
+\\
+\begin{minipage}{.49\linewidth}
+\centering 
+\includegraphics[width=0.82\textwidth]{images/S1c_gbpusd.eps}
+\subcaption{Profit- S1c}
+\label{cztero}
+\end{minipage}
+\begin{minipage}{.49\linewidth}
+\centering 
+\includegraphics[width=0.82\textwidth]{images/S1d_gbpusd.eps}
+\subcaption{Profit - S1d}
+\label{mansard}
+\end{minipage}
+\begin{minipage}{\linewidth}
+\centering 
+\includegraphics[width=0.6\textwidth]{images/S1s_gbpusd.eps}
+\label{mansard}
+\subcaption{Profit - S1s}
+\end{minipage}
+\caption{GBPUSD market results}
+\end{figure}
+\FloatBarrier
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+\newpage
+\begin{table}[!t]
+\caption{Profits for all strategy quadrants for FUS500} 
+ \begin{center} 
+ \begin{tabular}{|l|l|l|l|l|} 
+ \hline \textbf{strategy} & \textbf{profit} & \textbf{bestCalmar} & \textbf{bestMALength} & \textbf{la} \\ \hline  
+S1a & 274.89 & 5.44 & 83 & 3200\\ \hline 
+S1b & -70.94 & -0.47 & 15 & 2798\\ \hline 
+S1c & 291.62 & 4.26 & 15 & 2186\\ \hline 
+S1d & -106.67 & -0.73 & 82 & 1723\\ \hline 
+S1s & 344.29 & 2.08 & Group of MA & 4916\\ 
+\hline \end{tabular} 
+ \end{center} 
+ \end{table}
+\FloatBarrier
+
+\begin{figure}[h]
+\centering
+\begin{minipage}{.49\linewidth}
+\centering 
+\includegraphics[width=0.82\textwidth]{images/S1a_fus.eps}
+\subcaption{Profit - S1a}
+\label{jedno}
+\end{minipage}
+\begin{minipage}{.49\linewidth}
+\centering 
+\includegraphics[width=0.82\textwidth]{images/S1b_fus.eps}
+\subcaption{Profit - S1b}
+\label{dwu}
+\end{minipage}
+\\
+\begin{minipage}{.49\linewidth}
+\centering 
+\includegraphics[width=0.82\textwidth]{images/S1c_fus.eps}
+\subcaption{Profit- S1c}
+\label{cztero}
+\end{minipage}
+\begin{minipage}{.49\linewidth}
+\centering 
+\includegraphics[width=0.82\textwidth]{images/S1d_fus.eps}
+\subcaption{Profit - S1d}
+\label{mansard}
+\end{minipage}
+\begin{minipage}{\linewidth}
+\centering 
+\includegraphics[width=0.6\textwidth]{images/S1s_fus.eps}
+\label{mansard}
+\subcaption{Profit - S1s}
+\end{minipage}
+\caption{FUS500 market results}
 \end{figure}
@@
 \begin{table}[!t]
-\caption{Profits for all strategy quadrants for FUS500} 
- \begin{center} 
- \begin{tabular}{|l|l|l|l|l|} 
- \hline \textbf{strategy} & \textbf{profit} & \textbf{bestCalmar} & \textbf{bestMALength} & \textbf{la} \\ \hline  
-S1a & 274.89 & 5.44 & 83 & 3200\\ \hline 
-S1b & -70.94 & -0.47 & 15 & 2798\\ \hline 
-S1c & 291.62 & 4.26 & 15 & 2186\\ \hline 
-S1d & -106.67 & -0.73 & 82 & 1723\\ \hline 
-S1s & 344.29 & 2.08 & Group of MA & 4916\\ 
-\hline \end{tabular} 
- \end{center} 
- \end{table}
-\FloatBarrier
-
-\begin{figure}[h]
-\centering
-\begin{minipage}{.49\linewidth}
-\centering 
-\includegraphics[width=0.82\textwidth]{images/S1a_fus.eps}
-\subcaption{Profit - S1a}
-\label{jedno}
-\end{minipage}
-\begin{minipage}{.49\linewidth}
-\centering 
-\includegraphics[width=0.82\textwidth]{images/S1b_fus.eps}
-\subcaption{Profit - S1b}
-\label{dwu}
-\end{minipage}
-\\
-\begin{minipage}{.49\linewidth}
-\centering 
-\includegraphics[width=0.82\textwidth]{images/S1c_fus.eps}
-\subcaption{Profit- S1c}
-\label{cztero}
-\end{minipage}
-\begin{minipage}{.49\linewidth}
-\centering 
-\includegraphics[width=0.82\textwidth]{images/S1d_fus.eps}
-\subcaption{Profit - S1d}
-\label{mansard}
-\end{minipage}
-\begin{minipage}{\linewidth}
-\centering 
-\includegraphics[width=0.6\textwidth]{images/S1s_fus.eps}
-\label{mansard}
-\subcaption{Profit - S1s}
-\end{minipage}
-\caption{FUS500 market results}
-\end{figure}
-\FloatBarrier
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\newpage
-\begin{table}[!t]
 \caption{Profits for all strategy quadrants for FGOLD} 
@@
 \begin{table}[!t]
-\caption{Profits for all strategy quadrants for GBPUSD} 
+\caption{Profits for all strategy quadrants for FSILVER} 
  \begin{center} 
@@
  \hline \textbf{strategy} & \textbf{profit} & \textbf{bestCalmar} & \textbf{bestMALength} & \textbf{la} \\ \hline  
-S1a & 0.06 & 1.06 & 92 & 2588\\ \hline 
-S1b & 0.12 & 3.41 & 5 & 2513\\ \hline 
-S1c & 0.15 & 3.11 & 5 & 2475\\ \hline 
-S1d & 0.02 & 0.31 & 92 & 2319\\ \hline 
-S1s & 0.36 & 6.89 & Group of MA & 4907\\ 
+S1a & -5.31 & -0.65 & 81 & 2582\\ \hline 
+S1b & 17.22 & 5.86 & 10 & 2508\\ \hline 
+S1c & 4.17 & 0.56 & 10 & 2473\\ \hline 
+S1d & 6.95 & 1.33 & 81 & 2336\\ \hline 
+S1s & 21.96 & 5.55 & Group of MA & 4918\\ 
 \hline \end{tabular} 
@@
 \centering 
-\includegraphics[width=0.82\textwidth]{images/S1a_gbpusd.eps}
+\includegraphics[width=0.82\textwidth]{images/S1a_silver.eps}
 \subcaption{Profit - S1a}
@@
 \centering 
-\includegraphics[width=0.82\textwidth]{images/S1b_gbpusd.eps}
+\includegraphics[width=0.82\textwidth]{images/S1b_silver.eps}
 \subcaption{Profit - S1b}
@@
 \centering 
-\includegraphics[width=0.82\textwidth]{images/S1c_gbpusd.eps}
+\includegraphics[width=0.82\textwidth]{images/S1c_silver.eps}
 \subcaption{Profit- S1c}
@@
 \centering 
-\includegraphics[width=0.82\textwidth]{images/S1d_gbpusd.eps}
+\includegraphics[width=0.82\textwidth]{images/S1d_silver.eps}
 \subcaption{Profit - S1d}
@@
 \centering 
-\includegraphics[width=0.6\textwidth]{images/S1s_gbpusd.eps}
+\includegraphics[width=0.6\textwidth]{images/S1s_silver.eps}
 \label{mansard}
@@
 \end{minipage}
-\caption{GBPUSD market results}
-\end{figure}
-\FloatBarrier
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\newpage
-\begin{table}[!t]
-\caption{Profits for all strategy quadrants for USDJPY} 
- \begin{center} 
- \begin{tabular}{|l|l|l|l|l|} 
- \hline \textbf{strategy} & \textbf{profit} & \textbf{bestCalmar} & \textbf{bestMALength} & \textbf{la} \\ \hline  
-S1a & 17.19 & 8.24 & 18 & 2693\\ \hline 
-S1b & -9.80 & -0.74 & 54 & 2665\\ \hline 
-S1c & 5.65 & 2.06 & 54 & 2280\\ \hline 
-S1d & 1.87 & 0.61 & 18 & 2287\\ \hline 
-S1s & 14.85 & 5.68 & Group of MA & 4945\\ 
-\hline \end{tabular} 
- \end{center} 
- \end{table}
-\FloatBarrier
-
-\begin{figure}[h]
-\centering
-\begin{minipage}{.49\linewidth}
-\centering 
-\includegraphics[width=0.82\textwidth]{images/S1a_usdjpy.eps}
-\subcaption{Profit - S1a}
-\label{jedno}
-\end{minipage}
-\begin{minipage}{.49\linewidth}
-\centering 
-\includegraphics[width=0.82\textwidth]{images/S1b_usdjpy.eps}
-\subcaption{Profit - S1b}
-\label{dwu}
-\end{minipage}
-\\
-\begin{minipage}{.49\linewidth}
-\centering 
-\includegraphics[width=0.82\textwidth]{images/S1c_usdjpy.eps}
-\subcaption{Profit- S1c}
-\label{cztero}
-\end{minipage}
-\begin{minipage}{.49\linewidth}
-\centering 
-\includegraphics[width=0.82\textwidth]{images/S1d_usdjpy.eps}
-\subcaption{Profit - S1d}
-\label{mansard}
-\end{minipage}
-\begin{minipage}{\linewidth}
-\centering 
-\includegraphics[width=0.6\textwidth]{images/S1s_usdjpy.eps}
-\label{mansard}
-\subcaption{Profit - S1s}
-\end{minipage}
-\caption{USDJPY market results}
+\caption{FSILVER market results}
 \end{figure}

### 2013-06-04 Article/Article20130603/tewi-paper-template.tex
literówki

@@
 \indent The essence of the concept is the idea of simultaneous open long and short positions based on various signals, in this case the intersection graph (values of exchange rate  and stock index) and average of the last m closing of this price.\\
-Equally simple is the closing rule of each opened position. It's closed at the close of (i+1)th bar (Fig. 1).
-Let C be considering constantly changing prices of value, and $C_i$ closing price of i-th OHLC bar (Open, High, Low, Close). Denote $C_{m_{i}}$ as average of m last close
+Equally simple is the closing rule of each opened position. It's closed at the close of $(i+1)$th bar (Fig. 1).
+Let $C$ be considering constantly changing prices of value, and $C_i$ closing price of i-th OHLC bar (Open, High, Low, Close). Denote $C_{m_{i}}$ as average of m last close
 \begin{equation} \label{label-of-equation-1}
-  C_{m_{i}} = \frac{C_{i-m} + C_{i-m+1} + … + C_{i}}{m+1}; \hspace{1em}m>0; 
+  C_{m_{i}} = \frac{C_{i-m} + C_{i-m+1} + … + C_{i}}{m+1}; \hspace{1em}m>0. 
 \end{equation}
@@
 Depending on the investor's beliefs about the existence of a particular trend are thus four possible decision-making situations:
-\begin{equation} If\ C_i  > C_{m_{i}}\   long\ position\ will\ be\ open;\ m=m_a. \end{equation}
-\begin{equation} If\ C_i  > C_{m_{i}}\   short\ position\ will\ be\ open;\ m=m_b. \end{equation}
-\begin{equation} If\ C_i  < C_{m_{i}}\   long\ position\ will\ be\ open;\ m=m_c. \end{equation}
+\begin{equation} If\ C_i  > C_{m_{i}}\   long\ position\ will\ be\ open;\ m=m_a; \end{equation}
+\begin{equation} If\ C_i  > C_{m_{i}}\   short\ position\ will\ be\ open;\ m=m_b; \end{equation}
+\begin{equation} If\ C_i  < C_{m_{i}}\   long\ position\ will\ be\ open;\ m=m_c; \end{equation}
 \begin{equation} If\ C_i  < C_{m_{i}}\   short\ position\ will\ be\ open;\ m=m_d. \end{equation}
@@
 Each of these decisions is usually attributed to reasons arising from the conviction of the investor why and what happens in a moment.
-Should be noted that each of the above decisions is taken basing on average of different number of last close bar prices.
+It should be noted that each of the above decisions is taken basing on average of different number of last close bar prices.
 Therefore, in the general case at the close moment close of i-th bar when it should make decision of open (short or long) it could happen that may occur up to four different levels of the average value calculated for the last m bars (different for each contractual quadrant).\\
@@
 The investor is following the situation in the i-th bar and at the moment of its close may immediately calculate each of the four average (1).
-Depending on the direction in which market has changed (upwards or downwards) we are dealing with quarters a and b of quadrant (If there is a price rise of the observed asset) or quarters c and d if there is a decrease.
+Depending on the direction in which market has changed (upwards or downwards) we are dealing with quarters $a$ and $b$ of quadrant (If there is a price rise of the observed asset) or quarters $c$ and $d$ if there is a decrease.
 Because, at the moment of end of the i bar it can be calculated  value of each of the four average it can also be checked, if some of opening conditions (2)-(5) are passed.
@@
 \indent Each of these averages is counted step by step (bar) separately for each of the four situations, and of course the condition to open a position associated with a particular situation may occur or not.
-For example, if the closing value of the i-th bar in the situation a) will be below Cami this not open long position.\\
+For example, if the closing value of the i-th bar in the situation a) will be below $C^a_{m_{i}}$ this not open long position.\\
 \indent Extremely important in this strategy is the one and only parameter - number of last bar closures for average calculation.

### 2013-06-04 Article/Article20130603/tewi-paper-template.tex
et al.

@@
 \author{Antoni Wiliński\inst{1}, Piotr Błaszyński\inst{1}, Aneta Bera\inst{1}, \\ Wojciech Nowicki\inst{1}, Katarzyna Buda\inst{1}}
-\headauthor{Antoni Wiliński, Piotr Błaszyński}
+\headauthor{Antoni Wiliński, Piotr Błaszyński et al.}
 \affiliation{%
@@
 It should be noted that each of the above decisions is taken basing on average of different number of last close bar prices.
-Therefore, in the general case at the close moment close of i-th bar when it should make decision of open (short or long) it could happen that may occur up to four different levels of the average value calculated for the last m bars (different for each contractual quadrant).\\
-These situations are shown in Figure 1
+Therefore, in the general case at the close moment close of i-th bar when it should make decision of open (short or long) it could happen that may occur up to four different levels of the average value calculated for the last m bars (different for each contractual quadrant).
+These situations are shown in Figure 1.
 
@@
 
-In this quadrant in quarters a) and b) we have situations (2) and (3) - ie, the closing value of the i bar $C_i$ is greater than the average of the last m bars.
+In this quadrant in quarters a) and b) we have situations (2) and (3) - ie., the closing value of the i bar $C_i$ is greater than the average of the last m bars.
 The first line in those quarters is addressed to top - market is on the rise.
@@
 The investor is following the situation in the i-th bar and at the moment of its close may immediately calculate each of the four average (1).
-Depending on the direction in which market has changed (upwards or downwards) we are dealing with quarters $a$ and $b$ of quadrant (If there is a price rise of the observed asset) or quarters $c$ and $d$ if there is a decrease.
-Because, at the moment of end of the i bar it can be calculated  value of each of the four average it can also be checked, if some of opening conditions (2)-(5) are passed.
+Depending on the direction in which market has changed (upwards or downwards) we are dealing with quarters $a$ and $b$ of quadrant (if there is a price rise of the observed asset) or quarters $c$ and $d$ if there is a decrease.
+Because, at the moment of end of the i-th bar it can be calculated  value of each of the four average it can also be checked, if some of opening conditions (2)-(5) are passed.
 These four situations extracted from Figure 2 are shown in Figure 3, where in turn are explained  decision-making situations for the four quarters quadrant (Fig.
@@
 So ma is the parameter learned on a particular section of a time series.
-This m  value,for which achieves a maximum gain of opened positions (for quarter a) long).
+This m  value, for which achieves a maximum gain of opened positions (for quarter a) long).
 On another length of time series, by (6) it could have different value.
-Similarly, for the parameters ,b, mc and md.\\
+Similarly, for the parameters, b, mc and md.\\
 Use of this strategy makes the investor no longer think about the market in the traditional way trying to recognize what kind of a trend at the moment there is or whether this trend has just changed.

### 2013-06-04 Article/Article20130603/tewi-paper-template.tex
literówki 2
Suprising results ;)

@@
 As it’s been written in the introduction, more from cognitive point of view, than for the transaction value.\\
+Surprisingly strategy S1s is a fast and very simple way of receiving really good results, because it is sort of adding each quadrant in one file.
+In this case results show how surplus grows bigger than loss.
 \indent This strategy can be modified in many ways.

### 2013-06-04 Article/Article20130603/tewi-paper-template.tex
Tests description

@@
 \section{The test results}
+\indent The charts below shows the curves of capital accumulation for each quater of quadrant.
+Each graph represents one decision-making situation with the best parameter, number of last closures to calculate moving average.
+Fifth diagram shows the (S1s) cumulative strategy value.
+Which is the sum of profit of all open positions at this moment.
+Of course all component strategies are calculated for the best parameter for each of them.\\
 The study of strategy was carried out on the following markets:

### 2013-06-04 Article/Article20130603/tewi-paper-template.tex
tables description

@@
 It should be noted that each of the above decisions is taken basing on average of different number of last close bar prices.
-Therefore, in the general case at the close moment close of i-th bar when it should make decision of open (short or long) it could happen that may occur up to four different levels of the average value calculated for the last m bars (different for each contractual quadrant).
-These situations are shown in Figure 1.
+Therefore, in the general case at the close moment close of i-th bar when it should make decision of open (short or long) it could happen that may occur up to four different levels of the average value calculated for the last m bars (different for each contractual quadrant).\\
+These situations are shown in Figure 1
 
@@
 
-In this quadrant in quarters a) and b) we have situations (2) and (3) - ie., the closing value of the i bar $C_i$ is greater than the average of the last m bars.
+In this quadrant in quarters a) and b) we have situations (2) and (3) - ie, the closing value of the i bar $C_i$ is greater than the average of the last m bars.
 The first line in those quarters is addressed to top - market is on the rise.
@@
 The investor is following the situation in the i-th bar and at the moment of its close may immediately calculate each of the four average (1).
-Depending on the direction in which market has changed (upwards or downwards) we are dealing with quarters $a$ and $b$ of quadrant (if there is a price rise of the observed asset) or quarters $c$ and $d$ if there is a decrease.
-Because, at the moment of end of the i-th bar it can be calculated  value of each of the four average it can also be checked, if some of opening conditions (2)-(5) are passed.
+Depending on the direction in which market has changed (upwards or downwards) we are dealing with quarters $a$ and $b$ of quadrant (If there is a price rise of the observed asset) or quarters $c$ and $d$ if there is a decrease.
+Because, at the moment of end of the i bar it can be calculated  value of each of the four average it can also be checked, if some of opening conditions (2)-(5) are passed.
 These four situations extracted from Figure 2 are shown in Figure 3, where in turn are explained  decision-making situations for the four quarters quadrant (Fig.
@@
 So ma is the parameter learned on a particular section of a time series.
-This m  value, for which achieves a maximum gain of opened positions (for quarter a) long).
+This m  value,for which achieves a maximum gain of opened positions (for quarter a) long).
 On another length of time series, by (6) it could have different value.
-Similarly, for the parameters, b, mc and md.\\
+Similarly, for the parameters ,b, mc and md.\\
 Use of this strategy makes the investor no longer think about the market in the traditional way trying to recognize what kind of a trend at the moment there is or whether this trend has just changed.
@@
 Of course all component strategies are calculated for the best parameter for each of them.\\
+\indent Following tables present the results of conducted simulations aimed at finding the best number of bars required to calculate means (bestMALength).
+Column "strategy" specifies which strategy was used, "profit" - the cumulative sum of the profit.
+Third column, "bestCalmar", represents Calmar Ratio which describes profit---to---maximum drawdown ratio.
+Low Calmar Ratio indicates poor investment performance on a risk-adjusted basis during certain time span.
+Last column "la" presents the number of open positions.
 The study of strategy was carried out on the following markets:

### 2013-06-04 Article/Article20130603/tewi-paper-template.tex
usunieto zbędne pliki + literówki
eurusd results

@@
 \FloatBarrier
+
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+\newpage
+\begin{table}[!t]
+\caption{Profits for all strategy quadrants for EURUSD} 
+ \begin{center} 
+ \begin{tabular}{|l|l|l|l|l|} 
+ \hline \textbf{strategy} & \textbf{profit} & \textbf{bestCalmar} & \textbf{bestMALength} & \textbf{la} \\ \hline  
+S1a & 0.09 & 1.84 & 33 & 2635\\ \hline 
+S1b & 0.01 & 0.16 & 5 & 2587\\ \hline 
+S1c & 0.12 & 3.45 & 5 & 2406\\ \hline 
+S1d & -0.02 & -0.49 & 33 & 2331\\ \hline 
+S1s & 0.21 & 3.31 & Group of MA & 4966\\ 
+\hline \end{tabular} 
+ \end{center} 
+ \end{table}
+\FloatBarrier
+
+\begin{figure}[h]
+\centering
+\begin{minipage}{.49\linewidth}
+\centering 
+\includegraphics[width=0.82\textwidth]{images/S1a_eurusd.eps}
+\subcaption{Profit - S1a}
+\label{jedno}
+\end{minipage}
+\begin{minipage}{.49\linewidth}
+\centering 
+\includegraphics[width=0.82\textwidth]{images/S1b_eurusd.eps}
+\subcaption{Profit - S1b}
+\label{dwu}
+\end{minipage}
+\\
+\begin{minipage}{.49\linewidth}
+\centering 
+\includegraphics[width=0.82\textwidth]{images/S1c_eurusd.eps}
+\subcaption{Profit- S1c}
+\label{cztero}
+\end{minipage}
+\begin{minipage}{.49\linewidth}
+\centering 
+\includegraphics[width=0.82\textwidth]{images/S1d_eurusd.eps}
+\subcaption{Profit - S1d}
+\label{mansard}
+\end{minipage}
+\begin{minipage}{\linewidth}
+\centering 
+\includegraphics[width=0.6\textwidth]{images/S1s_eurusd.eps}
+\label{mansard}
+\subcaption{Profit - S1s}
+\end{minipage}
+\caption{EURUSD market results}
+\end{figure}
+\FloatBarrier
+
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

### 2013-06-04 Article/Article20130603/tewi-paper-template.tex
literowki + kolejnosc

@@
 \FloatBarrier
-\indent Figure 2 shows the situation at the close of (i-1) bar marked as $C_{i-1}$.
+\indent Figure 2 shows the situation at the close of $(i-1)$th bar marked as $C_{i-1}$.
 The investor is following the situation in the i-th bar and at the moment of its close may immediately calculate each of the four average (1).
@@
 These strategy has been tested on the following markets as simple as possible.
-When was satisfied, one or more of the opening conditions (2) – (5) then position has been opened and closed at the close of the (i +1) bar.
+When was satisfied, one or more of the opening conditions (2) – (5) then position has been opened and closed at the close of the $(i +1)$th bar.
 
@@
 Column "strategy" specifies which strategy was used, "profit" - the cumulative sum of the profit.
-Third column, "bestCalmar", represents Calmar Ratio which describes profit---to---maximum drawdown ratio.
+Third column, "bestCalmar", represents Calmar Ratio which describes profit-to-maximum drawdown ratio.
 Low Calmar Ratio indicates poor investment performance on a risk-adjusted basis during certain time span.
@@
 \begin{itemize}
-\item currency pairs: EURUSD, EURJPY, USDJPY, GBPUSD,
+\item currency pairs: EURJPY, USDJPY, GBPUSD, EURUSD,
 \item indexes: FUS500, BOSSAPLN,

### 2013-06-04 Article/Article20130603/tewi-paper-template.tex
literówka

@@
 If the purpose of this research is to be effective investment, not the successful prediction, research target should be changed.
-Many scientific papers was devoted to the problem of investment efficiency, also including the best quality papers, as well as work of at least several Nobel Prize winners.
+Many scientific papers were devoted to the problem of investment efficiency, also including the best quality papers, as well as work of at least several Nobel Prize winners.
 Among the many highly sophisticated research methods \cite{fujimoto03, kompa08, pawlak02, pedrycz97, rua09, raghuraj09, wilinski09} , for years was examined the ability of simple patterns classification in the time series \cite{brock92, cai05, gencay99, lebaron99, satchwell05}.

### 2013-06-04 Article/Article20130603/tewi-paper-template.tex
kolejne literówki

@@
 Trying to take advantage of this simple patterns (classification rules) in investment strategies.\\
-\indent The purpose of this papper is to verify thesis about effectiveness of such simple rules of opening and closing position on trading markets.
+\indent The purpose of this paper is to verify thesis about effectiveness of such simple rules of opening and closing position on trading markets.
 High frequency open positions algo trading are considering here \cite{muriel04}.
@@
 \section{The test results}
-\indent The charts below shows the curves of capital accumulation for each quater of quadrant.
+\indent The charts below show the curves of capital accumulation for each quarter of quadrant.
 Each graph represents one decision-making situation with the best parameter, number of last closures to calculate moving average.

### 2013-06-04 Article/Article20130603/tewi-paper-template.tex
usunięte resztki języka polskiego

@@
 where:\\
-$yi = C_{i+1} - C_{i}$ dla i=1, ..., n, for and complying  condition (2).\\
+$yi = C_{i+1} - C_{i}$ for i=1, ..., n and complying  condition (2).\\
 So ma is the parameter learned on a particular section of a time series.

### 2013-06-04 Article/Article20130603/tewi-paper-template.tex
indexes -> indices
conclusion

@@
 \item currency pairs: EURJPY, USDJPY, GBPUSD, EURUSD,
-\item indexes: FUS500, BOSSAPLN,
+\item indices: FUS500, BOSSAPLN,
 \item commodities: FGOLD. FSILVER.
@@
 As it’s been written in the introduction, more from cognitive point of view, than for the transaction value.\\
-Surprisingly strategy S1s is a fast and very simple way of receiving really good results, because it is sort of adding each quadrant in one file.
+\indent Surprisingly strategy S1s is a fast and very simple way of receiving really good results, because it is sort of adding each quadrant in one file.
 In this case results show how surplus grows bigger than loss.
@@
 \indent The authors believe, due to observing results of experiments, that the thesis of this dormant potential has been acknowledged. \\
-The results show that depending on the current market characteristics, it was possible to temporarily disable some quarters from trade to get better profits.
-Of course, they should still be calculated in the background, to be able include in trade if market characteristic will change.
+\indent Moreover the results proves that depending on the current market characteristics, it is possible to temporary disable some quarters from trade in order to getting better profits.
+Certainly parameters still should be calculated in the background, to be included in trade if market characteristic changes.
 

### 2013-06-04 Article/Article20130603/tewi-paper-template.tex
proves -> prove

@@
 \indent The authors believe, due to observing results of experiments, that the thesis of this dormant potential has been acknowledged. \\
-\indent Moreover the results proves that depending on the current market characteristics, it is possible to temporary disable some quarters from trade in order to getting better profits.
+\indent Moreover the results prove that depending on the current market characteristics, it is possible to temporary disable some quarters from trade in order to getting better profits.
 Certainly parameters still should be calculated in the background, to be included in trade if market characteristic changes.

### 2013-06-04 Article/Article20130603/tewi-paper-template.tex
temporary -> temporarily

@@
 \indent The authors believe, due to observing results of experiments, that the thesis of this dormant potential has been acknowledged. \\
-\indent Moreover the results prove that depending on the current market characteristics, it is possible to temporary disable some quarters from trade in order to getting better profits.
+\indent Moreover the results prove that depending on the current market characteristics, it is possible to temporarily disable some quarters from trade in order to getting better profits.
 Certainly parameters still should be calculated in the background, to be included in trade if market characteristic changes.

### 2013-06-04 Article/Article20130603/tewi-paper-template.tex
Trade moment

@@
 It should be noted that each of the above decisions is taken basing on average of different number of last close bar prices.
-Therefore, in the general case at the close moment close of i-th bar when it should make decision of open (short or long) it could happen that may occur up to four different levels of the average value calculated for the last m bars (different for each contractual quadrant).\\
+Therefore, it can be that the general case in exact moment, right after closing i-th bar, where decision should be made (short or long position) it could be that even 4 different levels of  the average value calculated for the last m bars (dfferent for each contractual quadrant).\\
 These situations are shown in Figure 1

### 2013-06-04 Article/Article20130603/tewi-paper-template.tex
These four situations are shown in Figure 1.

--- 2013-06-04 Article/Article20130603/tewi-paper-template.tex
@@
 It should be noted that each of the above decisions is taken basing on average of different number of last close bar prices.
-Therefore, in the general case at the close moment close of i-th bar when it should make decision of open (short or long) it could happen that may occur up to four different levels of the average value calculated for the last m bars (different for each contractual quadrant).\\
-These situations are shown in Figure 1
+Therefore, it can be that the general case in exact moment, right after closing i-th bar, where decision should be made (short or long position) it could be that even 4 different levels of  the average value calculated for the last m bars (dfferent for each contractual quadrant).
+These four situations are shown in Figure 1.
 

### 2013-06-04 Article/Article20130603/tewi-paper-template.tex
Conclusions - new line
widow killer

@@
 \end{equation}
-where:\\
-$yi = C_{i+1} - C_{i}$ for i=1, ..., n and complying  condition (2).\\
-So ma is the parameter learned on a particular section of a time series.
+where: $yi = C_{i+1} - C_{i}$ for i=1, ..., n and complying  condition (2).\\
+\indent So ma is the parameter learned on a particular section of a time series.
 This m  value,for which achieves a maximum gain of opened positions (for quarter a) long).
@@
 In this case results show how surplus grows bigger than loss.
+\\
 \indent This strategy can be modified in many ways.

### 2013-06-04 Article/Article20130603/tewi-paper-template.tex
of course -> Obviously
dfferent -> different

@@
 It should be noted that each of the above decisions is taken basing on average of different number of last close bar prices.
-Therefore, it can be that the general case in exact moment, right after closing i-th bar, where decision should be made (short or long position) it could be that even 4 different levels of  the average value calculated for the last m bars (dfferent for each contractual quadrant).
+Therefore, it can be that the general case in exact moment, right after closing i-th bar, where decision should be made (short or long position) it could be that even 4 different levels of  the average value calculated for the last m bars (different for each contractual quadrant).
 These four situations are shown in Figure 1.
@@
 Which is the sum of profit of all open positions at this moment.
-Of course all component strategies are calculated for the best parameter for each of them.\\
+Obviously all component strategies are calculated for the best parameter for each of them.\\
 \indent Following tables present the results of conducted simulations aimed at finding the best number of bars required to calculate means (bestMALength).

### 2013-06-05 Article/Article20130603/tewi-paper-template.tex
-th, index

@@
 \indent The essence of the concept is the idea of simultaneous open long and short positions based on various signals, in this case the intersection graph (values of exchange rate  and stock index) and average of the last m closing of this price.\\
-Equally simple is the closing rule of each opened position. It's closed at the close of $(i+1)$th bar (Fig. 1).
+Equally simple is the closing rule of each opened position. It's closed at the close of $(i+1)$-th bar (Fig. 1).
 Let $C$ be considering constantly changing prices of value, and $C_i$ closing price of i-th OHLC bar (Open, High, Low, Close). Denote $C_{m_{i}}$ as average of m last close
@@
 where: $yi = C_{i+1} - C_{i}$ for i=1, ..., n and complying  condition (2).\\
-\indent So ma is the parameter learned on a particular section of a time series.
+\indent So $m_{a}$ is the parameter learned on a particular section of a time series.
 This m value,for which achieves a maximum gain of opened positions (for quarter a) long).
 On another length of time series, by (6) it could have different value.
-Similarly, for the parameters ,b, mc and md.\\
+Similarly, for the parameters $m_{b}$, $m_{c}$ and $m_{d}$.\\
 Use of this strategy makes the investor no longer think about the market in the traditional way trying to recognize what kind of a trend at the moment there is or whether this trend has just changed.

### 2013-06-05 Article/Article20130603/tewi-paper-template.tex
8 results included
considered

@@
 The authors' intention was to prove the thesis that in the greedy algorithmic trading directed to the proper response, not to forecast, there are almost always opportunities to achieve profit.
-This paper presents the results of tests for over twenty core markets - currency pairs, indices and commodities.
+This paper presents the results of tests for over twenty core markets - currency pairs, indices and commodities (8 results included).
 Introduced the original concept of quadrant of openings on each bar.
@@
 \indent The purpose of this paper is to verify thesis about effectiveness of such simple rules of opening and closing position on trading markets.
-High frequency open positions algo trading are considering here \cite{muriel04}.
+High frequency open positions algo trading are considered here \cite{muriel04}.
 The strategy is based on the basic concept - should be as simple as possible, impossible to achieve by human not assisted with machine, should reject the idea of "predictions" of the future and be based on idea of responding to market behaviour.

### 2013-06-05 Article/Article20130603/tewi-paper-template.tex
is to open a long position
market growth with opening the short position

@@
 The first line in those quarters is addressed to top - market is on the rise.
-In the quarter, a) reaction to the growth of the market is open a long position (2).
+In the quarter, a) reaction to the growth of the market is to open a long position (2).
 The investor behaves as if he was convinced of the existence of a growing trend.
-In the quarter b) investors react on market growth is short position open.
+In the quarter b) investors react on market growth with opening the short position.
 The investor behaves as if he predicted horizontal trend.

### 2013-06-05 Article/Article20130603/tewi-paper-template.tex
predicts

@@
 In the quarter b) investors react on market growth with opening the short position.
-The investor behaves as if he predicted horizontal trend.
+The investor behaves as if he predicts horizontal trend.
 
 Conversely in quarters, c) and d) the first movement of the market is declining and investor reaction is recorded appropriately in decisions (4) and (5).
-In quarter c) investor behaves as if he predicted horizontal trend and opens long position (4) and in quarter d) in believe of drowdown trend he opens short position (5).
+In quarter c) investor behaves as if he predicts horizontal trend and opens long position (4) and in quarter d) in believe of drowdown trend he opens short position (5).
 \\

### 2013-06-05 Article/Article20130603/tewi-paper-template.tex
beliving of drawdown trend

@@
 Conversely in quarters, c) and d) the first movement of the market is declining and investor reaction is recorded appropriately in decisions (4) and (5).
-In quarter c) investor behaves as if he predicts horizontal trend and opens long position (4) and in quarter d) in believe of drowdown trend he opens short position (5).
+In quarter c) investor behaves as if he predicts horizontal trend and opens long position (4) and in quarter d) beliving of drawdown trend he opens short position (5).
 \\

### 2013-06-05 Article/Article20130603/tewi-paper-template.tex
four averages

@@
 Depending on the direction in which market has changed (upwards or downwards) we are dealing with quarters $a$ and $b$ of quadrant (If there is a price rise of the observed asset) or quarters $c$ and $d$ if there is a decrease.
-Because, at the moment of end of the i bar it can be calculated  value of each of the four average it can also be checked, if some of opening conditions (2)-(5) are passed.
+Because, at the moment of end of the i bar it can be calculated  value of each of the four averages it can also be checked, if some of opening conditions (2)-(5) are passed.
 These four situations extracted from Figure 2 are shown in Figure 3, where in turn are explained  decision-making situations for the four quarters quadrant (Fig.

### 2013-06-05 Article/Article20130603/tewi-paper-template.tex
price growth

@@
 The investor is following the situation in the i-th bar and at the moment of its close may immediately calculate each of the four average (1).
-Depending on the direction in which market has changed (upwards or downwards) we are dealing with quarters $a$ and $b$ of quadrant (If there is a price rise of the observed asset) or quarters $c$ and $d$ if there is a decrease.
+Depending on the direction in which market has changed (upwards or downwards) we are dealing with quarters $a$ and $b$ of quadrant (If there is a price growth of the observed asset) or quarters $c$ and $d$ if there is a decrease.
 Because, at the moment of end of the i bar it can be calculated  value of each of the four averages it can also be checked, if some of opening conditions (2)-(5) are passed.

### 2013-06-05 Article/Article20130603/tewi-paper-template.tex
then opening long position won't occur
\indent

@@
 \indent Each of these averages is counted step by step (bar) separately for each of the four situations, and of course the condition to open a position associated with a particular situation may occur or not.
-For example, if the closing value of the i-th bar in the situation a) will be below $C^a_{m_{i}}$ this not open long position.\\
+For example, if the closing value of the i-th bar in the situation a) will be below $C^a_{m_{i}}$ then opening long position won't occur.\\
 \indent Extremely important in this strategy is the one and only parameter - number of last bar closures for average calculation.
@@
 Similarly, for the parameters $m_{b}$, $m_{c}$ and $m_{d}$.\\
-Use of this strategy makes the investor no longer think about the market in the traditional way trying to recognize what kind of a trend at the moment there is or whether this trend has just changed.
+\indent Use of this strategy makes the investor no longer think about the market in the traditional way trying to recognize what kind of a trend at the moment there is or whether this trend has just changed.
 Machine that is learned the optimal value of m for each quarter of quadrant takes over this role and makes decisions in every of four possible investment situations.

### 2013-06-05 Article/Article20130603/tewi-paper-template.tex
for each one
del space

@@
 Many scientific papers were devoted to the problem of investment efficiency, also including the best quality papers, as well as work of at least several Nobel Prize winners.
-Among the many highly sophisticated research methods \cite{fujimoto03, kompa08, pawlak02, pedrycz97, rua09, raghuraj09, wilinski09} , for years was examined the ability of simple patterns classification in the time series \cite{brock92, cai05, gencay99, lebaron99, satchwell05}.
+Among the many highly sophisticated research methods \cite{fujimoto03, kompa08, pawlak02, pedrycz97, rua09, raghuraj09, wilinski09}, for years was examined the ability of simple patterns classification in the time series \cite{brock92, cai05, gencay99, lebaron99, satchwell05}.
 Trying to take advantage of this simple patterns (classification rules) in investment strategies.\\
@@
 Which is the sum of profit of all open positions at this moment.
-Obviously all component strategies are calculated for the best parameter for each of them.\\
+Obviously all component strategies are calculated for the best parameter for each one of them.\\
 \indent Following tables present the results of conducted simulations aimed at finding the best number of bars required to calculate means (bestMALength).

### 2013-06-05 Article/Article20130603/tewi-paper-template.tex
even four different

@@
 It should be noted that each of the above decisions is taken basing on average of different number of last close bar prices.
-Therefore, it can be that the general case in exact moment, right after closing i-th bar, where decision should be made (short or long position) it could be that even 4 different levels of  the average value calculated for the last m bars (different for each contractual quadrant).
+Therefore, it can be that the general case in exact moment, right after closing i-th bar, where decision should be made (short or long position) it could be that even four different levels of  the average value calculated for the last m bars (different for each contractual quadrant).
 These four situations are shown in Figure 1.

### 2013-06-05 Article/Article20130603/tewi-paper-template.tex
(eight results included)
at the close of $(i-1)$-th

@@
 The authors' intention was to prove the thesis that in the greedy algorithmic trading directed to the proper response, not to forecast, there are almost always opportunities to achieve profit.
-This paper presents the results of tests for over twenty core markets - currency pairs, indices and commodities (8 results included).
+This paper presents the results of tests for over twenty core markets - currency pairs, indices and commodities (eight results included).
 Introduced the original concept of quadrant of openings on each bar.
@@
 \FloatBarrier
-\indent Figure 2 shows the situation at the close of $(i-1)$th bar marked as $C_{i-1}$.
+\indent Figure 2 shows the situation at the close of $(i-1)$-th bar marked as $C_{i-1}$.
 The investor is following the situation in the i-th bar and at the moment of its close may immediately calculate each of the four average (1).

### 2013-06-05 Article/Article20130603/tewi-paper-template.tex
ul. Żołnierska
rather have

@@
   Faculty of Computer Science\\
-  ul.Żołnierska 49, 71-210 Szczecin Poland\\
+  ul. Żołnierska 49, 71-210 Szczecin Poland\\
   \{awilinski, pblaszynski, abera, wnowicki, kbuda\}@wi.zut.edu.pl
@@
 The strategy is based on the basic concept - should be as simple as possible, impossible to achieve by human not assisted with machine, should reject the idea of "predictions" of the future and be based on idea of responding to market behaviour.
-Such strategies are being tested for at least several decades and rather has not good reviews.
+Such strategies are being tested for at least several decades and rather have not good reviews.
 Most studies cover intersections of moving averages as premise of classifier opening positions rule or remaining idle.

### 2013-06-05 Article/Article20130603/tewi-paper-template.tex
since opening
that deserve

@@
 \indent Close terms in such investment strategies are also very simple.
-They are mostly based on similar terms, resulting from mean values or number of bars that elapsed since open.
+They are mostly based on similar terms, resulting from mean values or number of bars that elapsed since opening.
 Other popular methods of closing such positions are Stop Loss and Take Profit.
@@
 A wealth of simple rules ideas is work of Krutsinger \cite{krutsinger99}, collection of interviews with the most prominent modern practices – american market experts.
-Experts, which Phillip Ball \cite{ball07} writes, that deserves to be published, because they achieve financial success, so uncommon in academic.
+Experts, which Phillip Ball \cite{ball07} writes, that deserve to be published, because they achieve financial success, so uncommon in academic.
 It is easy to see that the majority of these excellent traders succeed within a certain period of time, and today the implementation of their methods gives poor results.

### 2013-06-05 Article/Article20130603/tewi-paper-template.tex
that there exists

@@
 It is easy to see that the majority of these excellent traders succeed within a certain period of time, and today the implementation of their methods gives poor results.
-This contradicts the general philosophy of these practitioners (but not all of them), that exists mysterious patterns or rules, that are characteristic for specific markets, which provide success.
+This contradicts the general philosophy of these practitioners (but not all of them), that there exists mysterious patterns or rules, that are characteristic for specific markets, which provide success.
 \section{Strategy characteristics}

### 2013-06-05 Article/Article20130603/tewi-paper-template.tex
calculated for the last $m$ bars

@@
 It should be noted that each of the above decisions is taken basing on average of different number of last close bar prices.
-Therefore, it can be that the general case in exact moment, right after closing i-th bar, where decision should be made (short or long position) it could be that even four different levels of  the average value calculated for the last m bars (different for each contractual quadrant).
+Therefore, it can be that the general case in exact moment, right after closing i-th bar, where decision should be made (short or long position) it could be that even four different levels of  the average value calculated for the last $m$ bars (different for each contractual quadrant).
 These four situations are shown in Figure 1.

### 2013-06-05 Article/Article20130603/tewi-paper-template.tex
The following sketches from a) to d) show
This $m$ value

@@
 \FloatBarrier
-\indent The following sketches from a) to d) shows the change in the market against a particular average from $C^d_{m_{i}}$ to $C^a_{m_{i}}$.\\
+\indent The following sketches from a) to d) show the change in the market against a particular average from $C^d_{m_{i}}$ to $C^a_{m_{i}}$.\\
 \indent Each of these averages is counted step by step (bar) separately for each of the four situations, and of course the condition to open a position associated with a particular situation may occur or not.
@@
 \indent So $m_{a}$ is the parameter learned on a particular section of a time series.
-This m value,for which achieves a maximum gain of opened positions (for quarter a) long).
+This $m$ value,for which achieves a maximum gain of opened positions (for quarter a) long).
 On another length of time series, by (6) it could have different value.

### 2013-06-05 Article/Article20130603/tewi-paper-template.tex
optimal value of $m$

@@
 \indent Use of this strategy makes the investor no longer think about the market in the traditional way trying to recognize what kind of a trend at the moment there is or whether this trend has just changed.
-Machine that is learned the optimal value of m for each quarter of quadrant takes over this role and makes decisions in every of four possible investment situations.
+Machine that is learned the optimal value of $m$ for each quarter of quadrant takes over this role and makes decisions in every of four possible investment situations.
 Take these decisions only when each of four calculated optimal moving averages condition is satisfied to open specific position.

### 2013-06-15 Matlabs/ZAD4/Sa.m
ZAD4
- Brak zapisywania wyników
- Błąd przywywoływaniu funkcji dla testowania...

@@ -1,0 +1,45 @@
+function [ sumReturn,Calmar ] = Sa(C,spread,paramALength,paramAVolLength,...
+    paramADuration,paramAVolThreshold,paramABuffer,paramASL, maxes, volAverages, pocz, ilosc)
+
+cSizes = size(C);
+candlesCount = cSizes(1);
+sumRa=zeros(1,candlesCount);
+Ra=zeros(1,candlesCount);
+dZ=zeros(1,candlesCount);
+la=0; %liczba otwieranych pozycji
+ls = 0;
+recordReturn=0;  %rekord zysku
+recordDrawdown=0;  %rekord obsuniecia
+pocz = pocz + 1;
+lastCandle = pocz + ilosc - 2;
+
+for i=pocz:lastCandle
+    
+    if maxes(i) + paramABuffer <C(i,4) && volAverages(i)<paramAVolThreshold
+        Ra(i)=C(i+paramADuration,4)-C(i+1,1)-spread; %zysk z i-tej pozycji long zamykanej na zamkniÍciu po paramADuration kroku
+        L=min(C(i+1:i+paramADuration,3));
+        
+        if (-C(i+1,1)+L)<-paramASL
+            Ra(i)=-paramASL;
+            ls=ls+1;
+        end
+        
+        la=la+1;
+    end
+    sumRa(i)=sumRa(i-1) + Ra(i);  %krzywa narastania kapita≥u
+    
+    if sumRa(i)>recordReturn
+        recordReturn=sumRa(i);
+    end
+    
+    dZ(i)=sumRa(i)-recordReturn; %rÛznica pomiedzy bieøπcπ wartoscia kapita≥u skumulowanego a dotychczasowym rekordem
+    
+    if dZ(i)<recordDrawdown
+        recordDrawdown=dZ(i);  %obsuniecie maksymalne
+    end
+end
+sumReturn=sumRa(lastCandle);
+Calmar=-sumReturn/recordDrawdown;  %wskaznik Calmara
+
+end
+

### 2013-06-15 Matlabs/ZAD4/Sd.m

@@ -1,0 +1,45 @@
+function [ sumReturn,Calmar ] = Sd(C,spread,paramDLength,paramDVolLength,...
+    paramDDuration,paramDVolThreshold,paramDBuffer,paramDSL, maxes, volAverages, pocz, ilosc)
+
+cSizes = size(C);
+candlesCount = cSizes(1);
+sumRd=zeros(1,candlesCount);
+Rd=zeros(1,candlesCount);
+dZ=zeros(1,candlesCount);
+ld=0; %liczba otwieranych pozycji
+ls = 0;
+recordReturn=0;  %rekord zysku
+recordDrawdown=0;  %rekord obsuniecia
+pocz = pocz + 1;
+lastCandle = pocz + ilosc - 2;
+
+for i=pocz:lastCandle
+    
+    if maxes(i) - paramDBuffer >C(i,4) && volAverages(i)<paramDVolThreshold
+        Rd(i)=-C(i+paramDDuration,4)+C(i+1,1)-spread; %zysk z i-tej pozycji long zamykanej na zamkniÍciu po paramADuration kroku
+        H=max(C(i+1:i+paramDDuration,2));
+        
+        if (C(i+1,1)-H)<-paramDSL
+            Rd(i)=-paramDSL;
+            ls=ls+1;
+        end
+        
+        ld=ld+1;
+    end
+    sumRd(i)=sumRd(i-1) + Rd(i);  %krzywa narastania kapita≥u
+    
+    if sumRd(i)>recordReturn
+        recordReturn=sumRd(i);
+    end
+    
+    dZ(i)=sumRd(i)-recordReturn; %rÛznica pomiedzy bieøπcπ wartoscia kapita≥u skumulowanego a dotychczasowym rekordem
+    
+    if dZ(i)<recordDrawdown
+        recordDrawdown=dZ(i);  %obsuniecie maksymalne
+    end
+end
+sumReturn=sumRd(lastCandle);
+Calmar=-sumReturn/recordDrawdown;  %wskaznik Calmara
+
+end
+

### 2013-06-15 Matlabs/ZAD4/zad4.m

@@ -1,0 +1,127 @@
+%(C) Antoni Wiliński 2013
+%skrypt strategii S4 w projekcie TEWI
+% Zadanie 4 - testowanie długości zbiorów uczących i testujących
+% Wersja by WNowicki, ABera, KBuda
+clc
+clear all
+close all
+tStart=tic;
+
+%%%%%%%%%%%%%%%%%%%%%%
+% Ustawienia:
+load ('gbpusd60');
+pip = 0.0001; % wielkosc pipsa na danym rynku
+spread = 2.8 * pip; % spread dla rynku
+
+% Parametry podstawowe
+VparamALength = [5:4:30]; % liczba swiec dla obliczenia sredniej
+VparamAVolLength = [5:4:30]; % liczba sweic wstecz dla obliczenia sredniego wolumenu
+VparamADuration = [5:2:30]; % dlugosc trwania otwartej pozycji
+VparamAVolThreshold = 0;%[10:-10:-10]; % prog dla volumenu
+VparamABuffer =  [-2*pip:-4*pip:-10*pip]; % wielkosc bufora
+VparamASL = 8*spread;%[8*spread:3*spread:20*spread]; % wartosc stop loss
+
+% Parametry dla zadania 4
+VparamASectionLearn = [100 500 1000 2000]; % dlugosc
+VparamASectionTest = [50 100 200 400]; % dlugosc
+ 
+%%%%%%%%%%%%%%%%%%%%%%
+
+bestReturn=-10000;
+cSizes = size(C);
+candlesCount = cSizes(1);
+bestCalmar = 0;
+bestMa = 0;
+bestparamAVolLength = 0;
+bestparamADuration = 0;
+bestparamABuffer = 0;
+bestparamAVolThreshold = 0;
+bestparamASL = 0;
+lastCandle = 0 ;
+bigPoint = 0;
+vvo = floor(candlesCount / 500) - 3;
+iterTotal = length(VparamALength)*length(VparamAVolLength)*length(VparamADuration)*length(VparamAVolThreshold)*length(VparamABuffer)*length(VparamASL)*(vvo+1);
+iterCounter = 0;
+disp(['# Rozmiar badania: ', num2str(iterTotal), ' iteracji.']);
+
+% ZAD4
+sectionResult = zeros(1,length(VparamASectionTest));
+
+for vo = 0:vvo
+	paramASectionLearn = 1000;
[…]

### 2013-06-15 Matlabs/ZAD4/zad4.m
ZAD4 - Poprawki
Poprawione błędy

@@ -14,9 +14,9 @@ pip = 0.0001; % wielkosc pipsa na danym rynku
 spread = 2.8 * pip; % spread dla rynku
 
 % Parametry podstawowe
-VparamALength = [5:4:30]; % liczba swiec dla obliczenia sredniej
-VparamAVolLength = [5:4:30]; % liczba sweic wstecz dla obliczenia sredniego wolumenu
-VparamADuration = [5:2:30]; % dlugosc trwania otwartej pozycji
+VparamALength = [5:3:30]; % liczba swiec dla obliczenia sredniej
+VparamAVolLength = [5:3:30]; % liczba sweic wstecz dla obliczenia sredniego wolumenu
+VparamADuration = [5:3:30]; % dlugosc trwania otwartej pozycji
 VparamAVolThreshold = 0;%[10:-10:-10]; % prog dla volumenu
 VparamABuffer =  [-2*pip:-4*pip:-10*pip]; % wielkosc bufora
 VparamASL = 8*spread;%[8*spread:3*spread:20*spread]; % wartosc stop loss
@@ -59,8 +59,10 @@ for vo = 0:vvo
 	
 		maxes=zeros(1, paramASectionLearn);
 		kon=(sectionLearnStart+paramASectionLearn)-1;
-		for i=2:kon
-			maxes(i) = max(C(i-min(i-1,paramALength):i,4));
+		ii=1;
+		for i=sectionLearnStart:kon
+			maxes(ii) = max(C(i-min(i-1,paramALength):i,4));
+			ii=ii+1;
 		end
 	
 		for vj = 1:length(VparamAVolLength)
@@ -69,8 +71,10 @@ for vo = 0:vvo
 		disp(['# Postep: ', num2str(round(iterCounter/iterTotal*100)), '%   Czas: ', num2str(toc(tStart))]);
 
 			volAverages=zeros(1, paramASectionLearn);
-			for i=2:kon
-				volAverages(i) = mean(C(i-min(i-1,paramAVolLength):i,5))-C(i,5);
+			ii=1;
+			for i=sectionLearnStart:kon
+				volAverages(ii) = mean(C(i-min(i-1,paramAVolLength):i,5))-C(i,5);
+				ii=ii+1;
 			end
 
 			for vk = 1:length(VparamADuration)
@@ -106,14 +110,14 @@ for vo = 0:vvo
 		end
 	end
[…]

### 2013-06-16 Matlabs/ZAD4/zad4.m
ZAD4 - zapisywanie
dodane zapisywanie parametrów dla badań cząstkowych by ABera

@@ -25,6 +25,11 @@ VparamASL = 8*spread;%[8*spread:3*spread:20*spread]; % wartosc stop loss
 VparamASectionLearn = [100 500 1000 2000]; % dlugosc
 VparamASectionTest = [50 100 200 400]; % dlugosc
  
+% Przygotowanie pliku do zapisu
+fileID =fopen([mfilename '.txt'],'w');
+formatSpec = 'bigPoint\tReturn\tCalmar\tparamALength\tparamAVolLength\tparamADuration\tparamAVolThreshold\tparamABuffer\tparamASL\n';
+fprintf(fileID,formatSpec);         
+
 %%%%%%%%%%%%%%%%%%%%%%
 
 bestReturn=-10000;
@@ -108,7 +113,13 @@ for vo = 0:vvo
 				end
 			end
 		end
-	end
+    end
+    
+    paramy=[bigPoint; sumReturn; Calmar; bestparamALength; bestparamAVolLength; ...
+        bestparamADuration;  bestparamAVolThreshold; bestparamABuffer; bestparamASL];
+    param_str = '%4.2f\t%4.2f\t%4.2f\t%4.2f\t%4.2f\t%4.2f\t%4.2f\t%4.2f\t%4.2f\n';
+    fprintf(fileID, param_str, paramy);
+    
 	maxes=zeros(1, max(VparamASectionTest)+max(bestparamALength,bestparamAVolLength) + bestparamADuration);
 	volAverages=zeros(1, max(VparamASectionTest)+max(bestparamALength,bestparamAVolLength) + bestparamADuration);
 	poczDanychTest = bigPoint+paramASectionLearn-max(bestparamALength,bestparamAVolLength);
@@ -124,8 +135,10 @@ for vo = 0:vvo
 		paramASectionTest = VparamASectionTest(vp);
 		[ sumReturn,Calmar ] = Sa (C(poczDanychTest:kon,:),spread,bestparamALength, bestparamAVolLength, bestparamADuration, bestparamAVolThreshold, bestparamABuffer, bestparamASL, maxes, volAverages,max(bestparamALength,bestparamAVolLength),paramASectionTest);
 		sectionResult(vp) = sectionResult(vp) + sumReturn;
-	end
+    end
+
 end
-sectionResult
+sectionResult;
 nazwa=[mfilename,'.','csv'];
 csvwrite(nazwa,sectionResult);
+fclose(fileID);

### 2013-06-16 Matlabs/ZAD4/zad4.m
ZAD4 - mała poprawka

@@ -96,7 +96,7 @@ for vo = 0:vvo
 							[ sumReturn,Calmar ] = Sa (C(bigPoint:bigPoint+paramASectionLearn+paramADuration,:),spread,paramALength, paramAVolLength, paramADuration, paramAVolThreshold, paramABuffer, paramASL, maxes, volAverages,1, paramASectionLearn);
 							if bestReturn<sumReturn
 								bestReturn=sumReturn;
-								%bestCalmar=Calmar;
+								bestCalmar=Calmar;
 								bestparamALength = paramALength;
 								bestparamAVolLength = paramAVolLength ;
 								bestparamADuration = paramADuration;
@@ -115,7 +115,7 @@ for vo = 0:vvo
 		end
     end
     
-    paramy=[bigPoint; sumReturn; Calmar; bestparamALength; bestparamAVolLength; ...
+    paramy=[bigPoint; bestReturn; bestCalmar; bestparamALength; bestparamAVolLength; ...
         bestparamADuration;  bestparamAVolThreshold; bestparamABuffer; bestparamASL];
     param_str = '%4.2f\t%4.2f\t%4.2f\t%4.2f\t%4.2f\t%4.2f\t%4.2f\t%4.2f\t%4.2f\n';
     fprintf(fileID, param_str, paramy);

### 2013-09-28 Article/Article20130912/TewiMiC/MatrixToLatex.m
changed: MatrixToLatex - added more columns. added: differnt types of figures generating (black-white).

@@ -1,7 +1,7 @@
 function [ ] = MatrixToLatex( file_name, Matrix )
 
 %%%%%%%%%%%%% LATEX %%%%%%%%%%%%%%%%
-pocz_table = '\\begin{table} \n \\begin{tabular}{|l|l|l|} \n \\hline test size & profit & Calmar\\\\ \\hline  \n';
+pocz_table = '\\begin{table} \n \\begin{tabular}{|l|l|l|l|l|l|} \n \\hline test size & profit & profit per canlde & Calmar & Open positions & Percentage [\\%%]\\\\ \\hline  \n';
 kon_table = '\\hline \\end{tabular} \n \\end{table}';
 
 mid_table = [];

### 2013-09-28 Article/Article20130912/TewiMiC/TewiMiCAllPeriods.m

@@ -9,6 +9,7 @@ for personInitials ={'AB'};%,'KB','MZ'}
     returns3d = zeros((scanPeriodCount + 3)* 100,testSize, scanPeriodCount);
     returns2d = zeros((scanPeriodCount + 3)* 100,testSize);
     calmars3d = zeros(testSize,testSize, scanPeriodCount);
+    open_pos = zeros(402,1);
     for i =1:scanPeriodCount
         C=textscan(personalFileHandle, '%d;%f;%f;%d;%d;%d;%f;%f;%d;%d;%d;%d;%f;%f\n');
         pocz = cell2mat(C(1));
@@ -26,8 +27,9 @@ for personInitials ={'AB'};%,'KB','MZ'}
         ll3 = cell2mat(C(12));
         bawe = cell2mat(C(13));
         bcawe = cell2mat(C(14));
-        returns= TewiMiCOnePeriodOneParamSet(pocz, kon, b, wstp, wstk, lkr, SL, TP, op, bvol, vwst, ll3, bawe, bcawe);
+        [returns, openings]= TewiMiCOnePeriodOneParamSet(pocz, kon, b, wstp, wstk, lkr, SL, TP, op, bvol, vwst, ll3, bawe, bcawe);
         returns3d(1:kon,:,i)= returns;
+        open_pos = open_pos + openings;
         %calmars3d do wyliczenia; 
         %tu powinniœmy zwróciæ macierz
         %return dla poszczególnych okresów testowych - 400 kolumn x 400
@@ -75,50 +77,53 @@ for personInitials ={'AB'};%,'KB','MZ'}
 %         calmars(x,actualStart)=actualCalmar;%interesuje nas tylko calmars(i,i)
 %     end
 
-    Tab =[];
-    for i=[10:10:150 150:50:400]
-        Calmar = obliczCalmara( cumulativeReturns(:,i) );
-        [cumulativeReturns(end,i) Calmar];
-        Tab(end+1,:) = [i,cumulativeReturns(end,i),Calmar];
-    end
-    MatrixToLatex( 'Wyniki_MiC.txt', Tab )
-    
-    hFig = figure(personNumber);
-    mesh(cumulativeReturns);
-    xlabel('length of test period');
-    ylabel('candles count');
-    zlabel('cumulative return');
-    SaveGraph( hFig, 'mic' )
-    
-    personNumber = personNumber + 1;
-    hFig = figure(personNumber);
-    mesh(cumulativeReturnsPerCandle);
[…]

### 2013-09-28 Article/Article20130912/TewiMiC/TewiMiCOnePeriodOneParamSet.m

@@ -1,4 +1,4 @@
-function[returns]=TewiMiCOnePeriodOneParamSet(pocz, kon, b, wstp, wstk, lkr, SL, TP, op, bvol, vwst, ll3, bawe, bcawe, returns3d, Calmars3d, actualTestIndex)
+function[returns, openings]=TewiMiCOnePeriodOneParamSet(pocz, kon, b, wstp, wstk, lkr, SL, TP, op, bvol, vwst, ll3, bawe, bcawe, returns3d, Calmars3d, actualTestIndex)
 
 %(C) Antoni Wilinski
 %skrypt inspirowany pomys³em Richarda Seidenberga z Joe Krutsingera s. 120, z
@@ -76,6 +76,7 @@ lll=0;
 
 pawe=1;
 cawe=1;
+openings = [];
 
 
 
@@ -124,6 +125,7 @@ for i=pocz:kon %40000:pocz+16000  %pêtla g³ówna, ka¿dy i-ty krok po pocz, to chw
         otw(ll)=2;
     end
     
+    openings(end+1,:) = [ll];
     
     sumcurr(i)=0;
     
@@ -327,7 +329,7 @@ for i=pocz:kon %40000:pocz+16000  %pêtla g³ówna, ka¿dy i-ty krok po pocz, to chw
 end %i
 
 
-zyl=sum(zz)
+zyl=sum(zz);
 %sharpe=zyl/std(zz)
 
 recZ=0;
@@ -343,7 +345,7 @@ for j=1:kon
         recO=dZ(j);  %obsuniecie maksymalne
     end
 end
-Calmar=-(zyl)/recO
+Calmar=-(zyl)/recO;
 
 
 z1=sum(zl1);

### 2013-09-28 Article/Article20130912/TewiMiD/TewiMiDAllPeriods.m

@@ -12,24 +12,28 @@ for personInitials =osoby
     returns3d = zeros((scanPeriodCount + 3)* 100,testSize, scanPeriodCount);
     returns2d = zeros((scanPeriodCount + 3)* 100,testSize);
     calmars3d = zeros(testSize,testSize, scanPeriodCount);
+	open_pos = zeros(402,1);
     for i =1:scanPeriodCount
         C=textscan(personalFileHandle, '%d;%f;%f;%d;%d;%d;%f;%f;%d;%d;%d;%d;%f;%f\n');
-        pocz = cell2mat(C(1));
-        kon = pocz + testSize;
-        zyl = cell2mat(C(2));
-        b = cell2mat(C(3));
-        wstp = cell2mat(C(4));
-        wstk = cell2mat(C(5));
-        lkr = cell2mat(C(6));
-        SL = cell2mat(C(7));
-        TP = cell2mat(C(8));
-        bvol = cell2mat(C(9));
-        vwst = cell2mat(C(10));
-        ll3 = cell2mat(C(11));
-        bawe = cell2mat(C(12));
-        bcawe = cell2mat(C(13));
-        returns= TewiMiDOnePeriodOneParamSet(pocz, kon, b, wstp, wstk, lkr, SL, TP, bvol, vwst, ll3, bawe, bcawe);
-        returns3d(1:kon,:,i)= returns;
+%         if i>=8 && i<=9
+            pocz = cell2mat(C(1));
+            kon = pocz + testSize;
+            zyl = cell2mat(C(2));
+            b = cell2mat(C(3));
+            wstp = cell2mat(C(4));
+            wstk = cell2mat(C(5));
+            lkr = cell2mat(C(6));
+            SL = cell2mat(C(7));
+            TP = cell2mat(C(8));
+            bvol = cell2mat(C(9));
+            vwst = cell2mat(C(10));
+            ll3 = cell2mat(C(11));
+            bawe = cell2mat(C(12));
+            bcawe = cell2mat(C(13));
+            [returns, openings]= TewiMiDOnePeriodOneParamSet(pocz, kon, b, wstp, wstk, lkr, SL, TP, bvol, vwst, ll3, bawe, bcawe);
+            returns3d(1:kon,:,i)= returns;
+            open_pos = open_pos + openings;
+%         end
         %calmars3d do wyliczenia;
         %tu powinniœmy zwróciæ macierz
[…]

### 2013-09-28 Article/Article20130912/TewiMiD/TewiMiDOnePeriodOneParamSet.m

@@ -1,4 +1,4 @@
-function[returns]=TewiMiDOnePeriodOneParamSet(pocz, kon, b, wstp, wstk, lkr, SL, TP, bvol, vwst, ll3, bawe, bcawe, returns3d, Calmars3d, actualTestIndex)
+function[returns, openings]=TewiMiDOnePeriodOneParamSet(pocz, kon, b, wstp, wstk, lkr, SL, TP, bvol, vwst, ll3, bawe, bcawe, returns3d, Calmars3d, actualTestIndex)
 
 %(C) Antoni Wilinski
 %skrypt inspirowany pomys³em Richarda Seidenberga z Joe Krutsingera s. 120, z
@@ -71,7 +71,7 @@ lll=0;
 
 pawe=1;
 cawe=1;
-
+openings = [];
 
 
 for i=pocz:kon%20:pocz+6100 %40000:pocz+16000  %pêtla g³ówna, ka¿dy i-ty krok po pocz, to chwila bie¿¹ca, nie dysponuje siê informacj¹ od i+1 wprzód; dopisane 1000 œwiec to swiece z przysz³osci
@@ -123,7 +123,7 @@ for i=pocz:kon%20:pocz+6100 %40000:pocz+16000  %pêtla g³ówna, ka¿dy i-ty krok po
         otw(ll)=2;
     end
     
-    
+    openings(end+1,:) = [ll];
     sumcurr(i)=0;
     
     
@@ -363,6 +363,10 @@ Calmar=-(zyl)/recO;
 l_open = lo1+lo2;
 
 [zyl Calmar]
+
+% disp(['Otwarcia: ' num2str(lo1) ' ' num2str(lo2)]);
+% disp(['Zamkniecia: 1)' num2str(l1) ' 2)' num2str(l2) ' 3)' num2str(l3)...
+%     ' 4)' num2str(l4) ' 5)' num2str(l5) ' 6)' num2str(l6) ' 7)' num2str(l7)]);
 
 end
 

### 2013-09-28 Article/Article20130912/different_figures/blackFig.m

@@ -1,0 +1,17 @@
+load wynikiD.mat
+step1 = 20;
+step2 = 50;
+A = cumulativeReturnsPerCandle(1020:step2:end,10:step1:end);
+h = mesh(A,'EdgeColor','black');
+set(h,'XData',get(h,'XData')*step1);
+set(h,'YData',get(h,'YData')*step2);
+set(h,'YData',get(h,'YData')+1000);
+% 
+xlabel('length of test period');
+ylabel('candles count');
+zlabel('cumulative return');
+view(33, 52)
+
+set(gcf, 'Position', [200 200 640 480])
+set(gcf, 'PaperPositionMode','auto')
+print(gcf,'-dpng', '-r0','cumulativeReturnsPerCandleD')

### 2013-09-28 Article/Article20130912/LatexArt/tewi-paper-template.tex
Article template in Latex

% vim:encoding=utf8 ft=tex sts=2 sw=2 et:
% Copyright (c) 2009 Jaroslaw Koszuk
%
% $Id$

\documentclass{tewiart}

\usepackage[utf8]{inputenc}
\usepackage[T1]{fontenc}
\usepackage{graphicx}
\usepackage{amsthm}
\usepackage{txfonts}
\usepackage{epstopdf}
\usepackage{placeins}
\usepackage[english]{babel}
\usepackage[utf8]{inputenc}
\usepackage[table]{xcolor}
\usepackage{array}
\usepackage{subcaption}

\newtheorem{definition}{Definition}
\newtheorem{theorem}[definition]{Theorem}
\newtheorem{corollary}[definition]{Corollary}
\newtheorem{proposition}[definition]{Proposition}
\newtheorem{example}[definition]{Example}

\title{Study on the effectiveness of the investment strategy based on a classifier with rules adapted by machine learning}
\headtitle{Study on the effectiveness of the investment strategy based on a classifier with rules adapted by machine learning\dots}
\author{Wiliński A.\inst{1}, Bera A.\inst{1}, Nowicki W.\inst{1}, Błaszyński P.\inst{1}}
\headauthor{Wiliński A., Bera A. et al.}
\affiliation{%
  \inst{1}West Pomeranian University of Technology,Szczecin, Poland\\
  \{awilinski, abera, wnowicki, pblaszynski\}@wi.zut.edu.pl
}
\keywords{machine learning,  cross validation, pattern recognition, classification, investment strategy, algotrading, forecasting, time series}

\begin{document}

\maketitle

\begin{abstract}
In this paper authors examine two transactional strategies based on the classifier which opens positions using some rules and closes them using different rules. A rule set contains time-varying parameters that when matched allow to make an investment decision. Researches contain the study of variability of these parameters and the relationship between learning period and testing (using the learned parameters). The strategies are evaluated based on the time series of cumulative profit achieved in the test periods. The study was conducted on the most popular currency pair EURUSD sampled with interval of 1 hour.
\end{abstract}

\section{Introduction}
INTRO

\bibliography{references-tewi}
\bibliographystyle{aiaa-tewi}

\end{document}

### 2013-09-28 Article/Article20130912/LatexArt/tewi-paper-template.tex
added 1 and 2 chapter

@@
 \usepackage{amsthm}
+\usepackage{amsmath}
 \usepackage{txfonts}
@@
 \title{Study on the effectiveness of the investment strategy based on a classifier with rules adapted by machine learning}
-\headtitle{Study on the effectiveness of the investment strategy based on a classifier with rules adapted by machine learning\dots}
+\headtitle{}
 \author{Wiliński A.\inst{1}, Bera A.\inst{1}, Nowicki W.\inst{1}, Błaszyński P.\inst{1}}
@@
 \section{Introduction}
-INTRO
+The aim of this work is to verify the hypothesis of the possibility of extracting patterns from time series, that would be classifiable as those that provide more accurate and better statistic prognosis.
+Another important objective is to confirm the assumption, that the time series of financial markets have a "memory" about the effectiveness of the learned pattern in a period after the learning one.
+This approach is consistent with the classic aim of machine learning shown by K.Murphy’ego [1], especially to financial markets described by Satchwell [2].
+Authors also intend to follow the principle of reproducibility of studies by other researchers, as well as by themselves, in other data environments, to make sense of the use of computational intelligence in its reasonable reproducibility [3, 4], in extracting of the regularity from chaos [5,6].
+\\
+
+The authors build an investment strategy with a relatively high complexity (measured by the number of factors included in the model), derived from a strategies group called strategy of simple rules (simple rules).
+In the literature those strategies are considered to be mainly strategies based on moving averages - their intersections and derivatives shown for example by Brock et al.
+[7], Cai et al.
+[8] and many other authors [9,10,11].
+Of course, the world of algorithms as well as prediction methods using a completely different nature, such as regression [12], multiple regression [13, 14], Fourier and wavelet transforms, and many others [16, 17] is plenteous.
+The authors use these methods as a basis for comparison, however they focus on mentioned simple rules.\\
+
+Authors propose strategy, that differs by suggesting different behaviors than the ones proposed when using Bollinger's Band, which has its foundation in a band built in an unusual way.
+According to the strategy based on that band, generally it can be assumed that the trend is horizontal and it is recommended to open position to the center of the band, after its cross by the price from the inside.
+In proposed strategies, authors use another band that is based on maxima of the maxima and minima of the minima of last several candles.\\
+
+In considered strategies authors move away from the principle of opening positions to the center of the band.
+In one modification, hereinafter referred to as sub strategy, position opens into the center of the band, whereas in another one, position opens on the outside.
+By treating the two considered sub strategies as an entirety and as strategies that are mutually retrieving (although a more appropriate word would be complementary) authors assume, that in the selected trading section, opening positions in opposite directions, of course not at the same time, can be done intentionally and effectively.
+During the trading, nature of the market (trend, volatility) may change.
+The market may be in some periods horizontal, in other trended.
+It is appropriate to seek all opportunities for profit.
+A similar philosophy is applied by several Krutsinger correspondents [18], , who belong to most prominent traders in US, who advocate unfounded reversal of the direction of opening the positions in case of series of failures.\\
+
+Returning to the issue of the complexity of the strategy, there are often opinions that the growing complexity of the prediction model is not indicated, because in learning section it  leads to overfitting [1,8,14] resulting in a greater error in the test sections.
+The problem of selecting the proper ratio between learning and testing phase is still unsolved for the non-stationary time series [5,19].
+In this situation the right approach seems to be the use of the idea of computational intelligence [4,6] by which the empirical justification hypothesis entitles to use the model.\\
+
+Therefore authors use two rather complex strategies (described below), achieving results that are in their assessment rewarding.
+They draw attention to the fact that the satisfaction problem belongs to the other sciences and depends on the trader's individual perception of the relationship between profit and risk, greed and fear [20].
+However, the issue of emotions in the trade is not considered here, but only noticed.\\
+
+The tests were deliberately performed in a fragment of the time series of a heavily diversified course, which contains both rising and downward trends as well as horizontal elements (Fig.
+\ref{timeSeries}).
+It is the time series, consisting of 4734 1-hour candles, of the most important and the most fluent currency pair EURUSD from 22.10.2012.
+\begin{figure}[h!]
+\begin{center}
+\includegraphics[width = 0.6\textwidth]{pictures/eurusd221012.png}
+\end{center}
+\caption{Time series EURUSD 1h}
+\label{timeSeries}
+\end{figure}
+\FloatBarrier
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+\section{Characteristics of investment strategies}
+The objective of the two considered strategies is to make investment decisions about buying or selling - opening long or short position in the studied market - the currency pair EURUSD.
+Decision is based on intersection of the current price and one of two barriers of additional indicator, called the ribbon.
+The band is made of two values calculated at the opening of each candle on the basis of historical data of the market.
+During the candle values of the band do not change, therefore barriers are creating step functions.
+In case, when the current price exceeds any of the barrier values (goes out of the band), a decision to buy or sell is made - the type of decision depends on the variant of the considered strategy - decision for sub strategy TewiMiC is different than in case of TewiMiD.
+Names of the strategies are derived from the name of the project, in which the research was carried out.
+
+\subsection{Definition of the band}
+The value of barriers forming a band is calculated using the maximum and minimum values of the last candle (OHLC).
+In the case of the upper band, it is the maximum of the maximal values of the n last candles, whereas in the case of the bottom band, it is the minimum of the minimal values of m last candles.
+
+\begin{equation}
+topBorder = \max{(H_{i-n},...,H_{i-1})}
+\end{equation}
+\begin{equation}
+bottomBorder = \min{(L_{i-m},...,L_{i-1})}
+\end{equation}
+
+As mentioned earlier, strategy comes in two versions that differ in terms of opening the positions when crossing the band.
+These differences result from different investor assumption about currently prevailing market trend.
+In the first case it is believed that the trend has just started and positions need to be opened in accordance with it.
+In the second case, the play is against the trend.
+The two considered variants, TewiMiC and TewiMiD, are based on excesses of the lower limit of the band.
+TewiMiD implies existence of a downward trend, for which when crossing (down) the lower limit of the band, a short position (assuming the price drop) is opened.
+This is known it literature and in trading as Sell Stop model.
+\\
+
+TewiMiC assumes the opposite case, therefore it is needed to open a long position (assuming the price increase).  This is Buy Limit model.
+
+\subsection{Strategy parameters}
+Considered strategies are based on a objects classification (events that meet the conditions contained in the set of rules which depend on the  value of certain parameters).
+Object - the event - is another candle.
+Rules are logical sentences like "if the price is greater than the upper barrier of the band", parameter is for example the upper barrier, which is a variable value.
+\\
+
+These parameters will determine whether the strategy will earn or lose.
+Appropriate selection of parameter values is therefore a key optimization issue in the use of the strategy.
+Considered strategies have 11 parameters, which are subject of optimization.
+\begin{itemize}
+\item p1 --- the number of candles, based on which the calculation of the current value of the band barrier is made; for researched time series, value of p1 generally ranges from 10 to 30;
+\item p2 --- number of steps forward, after which the position is closed in case none other close condition was met before; this value belongs to range from 3 to 40;
+\item p3 --– StopLoss condition; usually it remained in range from 0.002 to 0.017 expressed in values of EURUSD, which in researched period stayed in range from 1.2 to 1.4, as can be seen in \ref{timeSeries};
+\item p4 --– TakeProfit condition; generally ranged from 0.0015 to 0.009;
+\item p5 --- band buffer, offset from the barrier of the band defining the actual level of the expected crossing of the  price; ranged from -0.002 to 0.003;
+\item p6 --- maximum number of open positions at the same time; ranged from 3 to 20;
+\item p7 --- number of candles that determines average volume value; generally ranged from 2 to 10;
+\item p8 --- maximum value of the difference between the current value of the volume and the average value calculated on the basis of p7 candles back; ranged from 150 to 500;
+\item p9 --- number of candles on the cumulative profit curve, based on which current drawdown is calculated; ranged from 5 to 25;
+\item p10 --- highest acceptable drawdown on the cumulative yield curve; generally ranged from 0.0021 to 0.008;
+\item p11 --- acceptable amount of the cumulative loss for all currently open positions; ranged from 0.0005 to 0.003;
+\end{itemize}
+
+\subsection{Conditions of opening}
+As mentioned before, the signal to open the position is the intersection of the current price of the observed value and some barrier (that results from the calculated band).
+Special parameter called the buffer (p5) has been added, causing the offset of barrier from its actual value.
+Thus, the condition for opening TewiMIC strategy is:
+\begin{equation}
+\begin{split}
+if[(price < bottomBorder(p1) - buffor(p5)) \\ 
+and (current p6 < p6) and (Vol - meanVol(p7) < p8)] \\
+then open position long
+\end{split}
+\end{equation}
+where:\\
+\textit{price} – current value for EURUSD;\\
+\textit{bottomBorder(p1)} – value of lower band barrier for parameter p1; here minimum of last p1 minima; \\
+\textit{buffor(p5)} – value of buffer that moves said barrier;\\
+\textit{current p6} – number of currently opened positions;\\
+\textit{Vol} – current value of volume (in the candle);\\
+\textit{meanVol(p7)} – mean of volume of last p7 candles;\\
+
+\noindent and the opening condition for TewiMiD is:
+\begin{equation}
+\begin{split}
+if[(price < bottomBorder(p1) - buffor(p5)) \\ 
+and (current p6 < p6) and (Vol - meanVol(p7) > p8)] \\
+then open position short
+\end{split}
+\end{equation}
+
+As a result of these conditions, long positions, in sub strategy TewiMIC, are opened when three conditions are met simultaneously: crossing the bottom barrier reduced by buffer by the current price, the number of open positions is lesser than the limit (which is the optimized parameter p6) and the difference between the current volume and the average of the volume of the last p7 candle is less than the parameter p8.\\
+
+For TewiMiD strategy, similar, with significant differences - short positions will be opened and it is advisable that current volume should be greater  than the average.
+As the result of conducted research, authors concluded that volume (number of price changes in observed time frame – here during one hour) was the most important and most sensitive factor of decision model.\\
+
+These conditions can be met in two cases during the period of the current considered candle.
+They can be met immediately at the opening of the candle i.e.
+the opening value of the current candle is smaller than the barrier bottomBorder reduced by parameter p5.
+That condition can be met within the candle, when the current value of the price break through the lower barrier.
+\\
+
+The result of that is that we have two distinctly different opening conditions.
+
+\subsection{Conditions of closing}
+In both sub strategies there are 7 cases of closing the open positions, which results in their complexity - both in terms of logic and calculation.
+This complexity, however, exhausts all the possible surprises and does not  leave any opportunity for the unexpected market behavior.
+Of course, depending on the values of the parameters, frequency occurrences of closure cases can be very different.\\
+
+Firstly the terms for closing the long positions that were opened by conditions for TewiMiC will be presented.
+\begin{enumerate}
+\item Opened long position will be closed, if at the close of the candle \textit{(i + p2)} the position remained open, where \textit{i} - number of candle, which was opened;
+
+\item Position will be closed if at the opening of the next (i + k)-th - the candle after i-th candle, in which the position was opened, following condition is met: 
+\begin{equation}
+PriceO(i+k)-Price(i) <-SL
+\end{equation} 
+where \textit{ProceO(i+k)} is the opening value for (i+k)-th candle;\\
+Then the profit (in this case loss) will be calculated as:
+\begin{equation}
+Profit =PriceO (i+k)-Price(i);
+\end{equation}
+
+\item Position will be closed if inside the opening of the next (i + k)-th - the candle after i-th candle, in which the position was opened, following condition is met: 
+\begin{equation}
+(PriceO(i+k)-Price(i) )>-SL and (LowPrice(i+k)-Price(i))<-SL
+\end{equation} 
+Then the profit (in this case loss) will be calculated as:
+\begin{equation}
+Profit =-SL;
+\end{equation}
+
+\item Position will be closed if at the opening of the next (i + k)-th - the candle after i-th candle, in which the position was opened, following condition is met: 
+\begin{equation}
+PriceO(i+k)-Price(i)>TP
+\end{equation} 
+Then the profit will be calculated as:
+\begin{equation}
+Profit =PriceO (i+k)-Price(i);
+\end{equation}
+
+\item Position will be closed if inside the opening of the next (i + k)-th - the candle after i-th candle, in which the position was opened, following condition is met: 
+\begin{equation}
+(PriceO(i+k)-Price(i) )<TP and (HighPrice(i+k)-Price(i))>TP
+\end{equation} 
+Then the profit will be calculated as:
+\begin{equation}
+Profit =TP;
+\end{equation}
+where \textit{HighPrice(i+k)} is the maximum value for (i+k) candle;
+
+\item Position will be closed if at the opening of the next (i + k)-th - the candle after i-th candle, in which the position was opened, following condition is met: 
+\begin{equation}
+PriceO(i+k) >topBorder(i+k)
+\end{equation} 
+Then the profit will be calculated as:
+\begin{equation}
+Profit =PriceO (i+k) -  Price(i) ;
+\end{equation}
+
+\item Position will be closed if inside the opening of the next (i + k)-th - the candle after i-th candle, in which the position was opened, following condition is met: 
+\begin{equation}
+Price(i+k) >topBorder(i+k)
+\end{equation} 
+Then the profit will be calculated as:
+\begin{equation}
+Profit =topBorder (i+k) -  Price(i) ;
+\end{equation}
+
+\end{enumerate}
+
+In sub strategy TewiMiD conditions will look slightly different.
+\begin{enumerate}
+\item Opened short position will be closed if at the close of the candle (i + p2)-th the position remained open;\\
+Position will be closed if at the opening of the next (i + k)-th - the candle after i-th candle, in which the position was opened, following condition is met:
+\begin{equation}
+Price(i)-PriceO(i+k)<-SL
+\end{equation}                                      
+Then the profit (in this case loss) will be calculated as:
+\begin{equation}
+Profit =-PriceO (i+k) +  Price(i) ;
+\end{equation}
+
+\item Position will be closed if inside the opening of the next (i + k)-th - the candle after i-th candle, in which the position was opened, following condition is met:
+\begin{equation}
+(-PriceO (i+k)+price(i) )>-SL and (-HighPrice(i+k)+Price(i))<-SL
+\end{equation}                          
+Then the profit (in this case loss) will be calculated as:
+\begin{equation}
+Profit =-SL; 
+\end{equation}
+
+\item Position will be closed if at the opening of the next (i + k)-th - the candle after i-th candle, in which the position was opened, following condition is met:
+\begin{equation}
+Price(i)-PriceO(i+k>TP
+\end{equation}                                           
+Then the profit will be calculated as:
+\begin{equation}
+Profit =-PriceO (i+k)  + Price(i) ;
+\end{equation}
+
+\item Position will be closed if inside the opening of the next (i + k)-th - the candle after i-th candle, in which the position was opened, following condition is met: 
+\begin{equation}
+(-PriceO(i+k)+price(i) )<TP and (-LowPrice(i+k)+Price(i))>TP
+\end{equation}
+Then the profit will be calculated as:
+\begin{equation}
+Profit =TP; 
+\end{equation}
+
+\item Position will be closed if at the opening of the next (i + k)-th - the candle after i-th candle, in which the position was opened, following condition is met: 
+\begin{equation}
+PriceO(i+k) >bottomBorder(i+k)
+\end{equation}                          
+Then the profit will be calculated as:
+\begin{equation}
+Profit =-PriceO (i+k)  + Price(i) ;
+\end{equation}
+
+\item Position will be closed when inside the opening of the next (i + k)-th - the candle after i-th candle, in which the position was opened, following condition is met:
+\begin{equation}
+Price(i+k) >bottomBorder(i+k)
+\end{equation}                           
+Then the profit (in this case loss) will be calculated as:
+\begin{equation}
+Profit =-bottomBorder (i+k) +  Price(i) ;
+\end{equation}
+
+\end{enumerate}
+Additional conditions that are checked with each closing are the rules containing parameters p9, p10, p11.
+These parameters are found in the rules limiting the risk of an unacceptable failure.
+Moreover, the principle stating that in the case when the opening took place at the beginning of the candle, it is permissible to keep it open until following candle is opened was used.
+Because of that,  it was possible to avoid ambiguity involving the unpredictable sequence of the SL and TP.
+
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+\section{Badanie strategii}
+\begin{figure}[h!]
+\begin{center}
+\includegraphics[width=0.6\textwidth]{pictures/metodyka_badan.png}
+\caption{Metodyka przeprowadzonych badań dla przypadku zmiennego okna testowego}
+\label{metodyka}
+\end{center}
+\end{figure}
+\FloatBarrier
+
+\begin{figure}[h!]
+\begin{center}
+\includegraphics[width=0.7\textwidth]{pictures/mic_100.png}
+\caption{PODPIS}
+\label{MiC100}
+\end{center}
+\end{figure}
+\FloatBarrier
+
+\begin{figure}[h!]
+\begin{center}
+\includegraphics[width=0.7\textwidth]{pictures/mid_100.png}
+\caption{PODPIS}
+\label{MiD100}
+\end{center}
+\end{figure}
+\FloatBarrier
+
+\begin{figure}[h!]
+\begin{center}
+\includegraphics[width=0.7\textwidth]{pictures/cumulativeReturnsC.png}
+\caption{PODPIS}
+\label{Cum3DMiC}
+\end{center}
+\end{figure}
+\FloatBarrier
+
+\begin{figure}[h!]
+\begin{center}
+\includegraphics[width=0.7\textwidth]{pictures/mic_end.png}
+\caption{PODPIS}
+\label{Cum3DMiCend}
+\end{center}
+\end{figure}
+\FloatBarrier
+
+\begin{figure}[h!]
+\begin{center}
+\includegraphics[width=0.7\textwidth]{pictures/cumulativeReturnsPerCandleC.png}
+\caption{PODPIS}
+\label{Cum3DPerCMiC}
+\end{center}
+\end{figure}
+\FloatBarrier
+
+\begin{figure}[h!]
+\begin{center}
+\includegraphics[width=0.7\textwidth]{pictures/mic_percandle_end.png}
+\caption{PODPIS}
+\label{Cum3DPerCMiCend}
+\end{center}
+\end{figure}
+\FloatBarrier
+
+\begin{table} 
+\caption{TABLE 1}
+\label{table1}
+ \begin{tabular}{|l|l|l|l|l|l|} 
+ \hline size & profit & profit per canlde & Calmar & Open positions & Percentage [\%]\\ \hline  
+10 & -0.0192 & -0.0019 & -0.728 & 34 & 10.97 \\ 
+ 20 & 0.0415 & 0.0021 & 2.1594 & 66 & 10.65 \\ 
+ 30 & 0.0812 & 0.0027 & 2.4182 & 93 & 10 \\ 
+ 40 & 0.0768 & 0.0019 & 1.4048 & 120 & 9.68 \\ 
+ 50 & 0.1176 & 0.0024 & 2.4069 & 134 & 8.65 \\ 
+ 60 & 0.2318 & 0.0039 & 5.3914 & 153 & 8.23 \\ 
+ 70 & 0.2211 & 0.0032 & 4.7859 & 176 & 8.11 \\ 
+ 80 & 0.2359 & 0.0029 & 5.1063 & 196 & 7.9 \\ 
+ 90 & 0.3005 & 0.0033 & 8.6589 & 221 & 7.92 \\ 
+ 100 & 0.3548 & 0.0035 & 10.221 & 245 & 7.9 \\ 
+ 110 & 0.3294 & 0.003 & 9.4905 & 262 & 7.68 \\ 
+ 120 & 0.3172 & 0.0026 & 8.6479 & 283 & 7.61 \\ 
+ 130 & 0.2854 & 0.0022 & 4.5295 & 304 & 7.54 \\ 
+ 140 & 0.2512 & 0.0018 & 4.3911 & 335 & 7.72 \\ 
+ 150 & 0.2648 & 0.0018 & 4.6295 & 345 & 7.42 \\ 
+ 200 & 0.2194 & 0.0011 & 2.8244 & 482 & 7.77 \\ 
+ 250 & 0.2091 & 0.0008 & 2.2352 & 574 & 7.41 \\ 
+ 300 & 0.1684 & 0.0006 & 1.5345 & 720 & 7.74 \\ 
+ 350 & 0.1399 & 0.0004 & 1.0402 & 804 & 7.41 \\ 
+ 400 & 0.073 & 0.0002 & 0.5074 & 914 & 7.37 \\ 
+ \hline \end{tabular} 
+ \end{table}
+
+%%%%%%%%%
+\begin{figure}[h!]
+\begin{center}
+\includegraphics[width=0.7\textwidth]{pictures/cumulativeReturnsD.png}
+\caption{PODPIS}
+\label{Cum3DMiD}
+\end{center}
+\end{figure}
+\FloatBarrier
+
+\begin{figure}[h!]
+\begin{center}
+\includegraphics[width=0.7\textwidth]{pictures/mid_end.png}
+\caption{PODPIS}
+\label{Cum3DMiDend}
+\end{center}
+\end{figure}
+\FloatBarrier
+
+\begin{figure}[h!]
+\begin{center}
+\includegraphics[width=0.7\textwidth]{pictures/cumulativeReturnsPerCandleD.png}
+\caption{PODPIS}
+\label{Cum3DPerCMiD}
+\end{center}
+\end{figure}
+\FloatBarrier
+
+\begin{figure}[h!]
+\begin{center}
+\includegraphics[width=0.7\textwidth]{pictures/mid_percandle_end.png}
+\caption{PODPIS}
+\label{Cum3DPerCMiDend}
+\end{center}
+\end{figure}
+\FloatBarrier
+
+\begin{table} 
+\caption{TABLE 2}
+\label{table2}
+ \begin{tabular}{|l|l|l|l|l|l|} 
+ \hline size & profit & profit per canlde & Calmar & Open positions & Percentage [\%]\\ \hline  
+10 & 0.0108 & 0.0011 & 2.3305 & 11 & 3.55 \\ 
+ 20 & 0.0135 & 0.0007 & 2.4981 & 20 & 3.23 \\ 
+ 30 & 0.0249 & 0.0008 & 4.2953 & 47 & 5.05 \\ 
+ 40 & 0.0401 & 0.001 & 8.012 & 60 & 4.84 \\ 
+ 50 & 0.0443 & 0.0009 & 8.868 & 66 & 4.26 \\ 
+ 60 & 0.0636 & 0.0011 & 13.25 & 83 & 4.46 \\ 
+ 70 & 0.0771 & 0.0011 & 16.0687 & 95 & 4.38 \\ 
+ 80 & 0.0914 & 0.0011 & 19.0396 & 118 & 4.76 \\ 
+ 90 & 0.0899 & 0.001 & 10.5222 & 130 & 4.66 \\ 
+ 100 & 0.0935 & 0.0009 & 12.7934 & 141 & 4.55 \\ 
+ 110 & 0.0921 & 0.0008 & 12.6559 & 150 & 4.4 \\ 
+ 120 & 0.0949 & 0.0008 & 13.0337 & 159 & 4.27 \\ 
+ 130 & 0.0955 & 0.0007 & 13.1243 & 178 & 4.42 \\ 
+ 140 & 0.0998 & 0.0007 & 11.5503 & 188 & 4.33 \\ 
+ 150 & 0.0974 & 0.0006 & 9.6789 & 194 & 4.17 \\ 
+ 200 & 0.1011 & 0.0005 & 9.464 & 263 & 4.24 \\ 
+ 250 & 0.0965 & 0.0004 & 9.0392 & 328 & 4.23 \\ 
+ 300 & 0.1008 & 0.0003 & 9.3983 & 410 & 4.41 \\ 
+ 350 & 0.0924 & 0.0003 & 7.2935 & 467 & 4.3 \\ 
+ 400 & 0.1105 & 0.0003 & 8.1655 & 558 & 4.5 \\ 
+ \hline \end{tabular} 
+ \end{table}
 

### 2013-09-28 Article/Article20130912/LatexArt/tewi-paper-template.tex
fixed: equations

@@
 and (current p6 < p6) and (Vol - meanVol(p7) < p8)] \\
-then open position long
+\text{then open position long}
 \end{split}
@@
 and (current p6 < p6) and (Vol - meanVol(p7) > p8)] \\
-then open position short
+\text{then open position short}
 \end{split}
@@
 \begin{equation}
-(PriceO(i+k)-Price(i) )>-SL and (LowPrice(i+k)-Price(i))<-SL
+(PriceO(i+k)-Price(i) )>-SL \text{ and } (LowPrice(i+k)-Price(i))<-SL
 \end{equation} 
@@
 \begin{equation}
-(PriceO(i+k)-Price(i) )<TP and (HighPrice(i+k)-Price(i))>TP
+(PriceO(i+k)-Price(i) )<TP \text{ and } (HighPrice(i+k)-Price(i))>TP
 \end{equation} 
@@
 \begin{equation}
-(-PriceO (i+k)+price(i) )>-SL and (-HighPrice(i+k)+Price(i))<-SL
+(-PriceO (i+k)+price(i) )>-SL \text{ and } (-HighPrice(i+k)+Price(i))<-SL
 \end{equation}                          
@@
 \begin{equation}
-(-PriceO(i+k)+price(i) )<TP and (-LowPrice(i+k)+Price(i))>TP
+(-PriceO(i+k)+price(i) )<TP \text{ and } (-LowPrice(i+k)+Price(i))>TP
 \end{equation}

### 2013-09-28 Article/Article20130912/LatexArt/tewi-paper-template.tex
added: bibliography fixed: equations

@@
 \usepackage{subcaption}
+\usepackage{hyperref}
 
@@
 Another important objective is to confirm the assumption, that the time series of financial markets have a "memory" about the effectiveness of the learned pattern in a period after the learning one.
-This approach is consistent with the classic aim of machine learning shown by K.Murphy’ego [1], especially to financial markets described by Satchwell [2].
-Authors also intend to follow the principle of reproducibility of studies by other researchers, as well as by themselves, in other data environments, to make sense of the use of computational intelligence in its reasonable reproducibility [3, 4], in extracting of the regularity from chaos [5,6].
+This approach is consistent with the classic aim of machine learning shown by K.Murphy’ego \cite{Murphy}, especially to financial markets described by Satchwell \cite{Satchwell}.
+Authors also intend to follow the principle of reproducibility of studies by other researchers, as well as by themselves, in other data environments, to make sense of the use of computational intelligence in its reasonable reproducibility \cite{Polya, Donoho}, in extracting of the regularity from chaos \cite{Ball, Pedrycz}.
 \\
@@
 In the literature those strategies are considered to be mainly strategies based on moving averages - their intersections and derivatives shown for example by Brock et al.
-[7], Cai et al.
-[8] and many other authors [9,10,11].
-Of course, the world of algorithms as well as prediction methods using a completely different nature, such as regression [12], multiple regression [13, 14], Fourier and wavelet transforms, and many others [16, 17] is plenteous.
+\cite{Brock}, Cai et al.
+\cite{Cai} and many other authors \cite{Gencay, LeBaron, Tian}.
+Of course, the world of algorithms as well as prediction methods using a completely different nature, such as regression \cite{Muriel}, multiple regression \cite{Wilinski, Fujimoto}, Fourier and wavelet transforms, and many others \cite{Raghuraj, KleskWilinski} is plenteous.
 The authors use these methods as a basis for comparison, however they focus on mentioned simple rules.\\
@@
 It is appropriate to seek all opportunities for profit.
-A similar philosophy is applied by several Krutsinger correspondents [18], , who belong to most prominent traders in US, who advocate unfounded reversal of the direction of opening the positions in case of series of failures.\\
+A similar philosophy is applied by several Krutsinger correspondents \cite{Krutsinger}, , who belong to most prominent traders in US, who advocate unfounded reversal of the direction of opening the positions in case of series of failures.\\
 
-Returning to the issue of the complexity of the strategy, there are often opinions that the growing complexity of the prediction model is not indicated, because in learning section it  leads to overfitting [1,8,14] resulting in a greater error in the test sections.
-The problem of selecting the proper ratio between learning and testing phase is still unsolved for the non-stationary time series [5,19].
-In this situation the right approach seems to be the use of the idea of computational intelligence [4,6] by which the empirical justification hypothesis entitles to use the model.\\
+Returning to the issue of the complexity of the strategy, there are often opinions that the growing complexity of the prediction model is not indicated, because in learning section it  leads to overfitting \cite{Murphy, Cai, Fujimoto}  resulting in a greater error in the test sections.
+The problem of selecting the proper ratio between learning and testing phase is still unsolved for the non-stationary time series \cite{Ball, Ivakhnenko}.
+In this situation the right approach seems to be the use of the idea of computational intelligence \cite{Polya, Pedrycz} by which the empirical justification hypothesis entitles to use the model.\\
 
 Therefore authors use two rather complex strategies (described below), achieving results that are in their assessment rewarding.
-They draw attention to the fact that the satisfaction problem belongs to the other sciences and depends on the trader's individual perception of the relationship between profit and risk, greed and fear [20].
+They draw attention to the fact that the satisfaction problem belongs to the other sciences and depends on the trader's individual perception of the relationship between profit and risk, greed and fear \cite{Kahneman}.
 However, the issue of emotions in the trade is not considered here, but only noticed.\\
@@
 \item p2 --- number of steps forward, after which the position is closed in case none other close condition was met before; this value belongs to range from 3 to 40;
-\item p3 --– StopLoss condition; usually it remained in range from 0.002 to 0.017 expressed in values of EURUSD, which in researched period stayed in range from 1.2 to 1.4, as can be seen in \ref{timeSeries};
+\item p3 --– StopLoss condition; usually it remained in range from 0.002 to 0.017 expressed in values of EURUSD, which in researched period stayed in range from 1.2 to 1.4, as can be seen in Fig.
+\ref{timeSeries};
 \item p4 --– TakeProfit condition; generally ranged from 0.0015 to 0.009;
@@
 if[(price < bottomBorder(p1) - buffor(p5)) \\ 
-and (current p6 < p6) and (Vol - meanVol(p7) < p8)] \\
+\text{and } (current p6 < p6) \text{ and } (Vol - meanVol(p7) < p8)] \\
 \text{then open position long}
@@
 if[(price < bottomBorder(p1) - buffor(p5)) \\ 
-and (current p6 < p6) and (Vol - meanVol(p7) > p8)] \\
+\text{and } (current p6 < p6) \text{ and } (Vol - meanVol(p7) > p8)] \\
 \text{then open position short}
@@
 
-\begin{table} 
+\begin{table}[h!] 
 \caption{TABLE 1}
@@
  \end{table}
+ \FloatBarrier
 
@@
 
-\begin{table} 
+\begin{table}[h!]
 \caption{TABLE 2}
@@
  \end{table}
-
+ \FloatBarrier
 \bibliography{references-tewi}

### 2013-09-29 Article/Article20130912/LatexArt/tewi-paper-template.tex
Figures described

@@
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\section{Badanie strategii}
+\section{Strategy analysis}
+In both strategies a fixed period of learning are assumed (in the presented solution - 1000 one hour candles), followed by a testing period.
+Data from learning period were used to find a class of patterns which allowed to achieve maximum for the selected criterion (in this study Calmar ratio were selected).
+The same patterns were then searched during the test period and the test results were computed for previously unused data space.
+Of course, these results do not have to already be positive and acceptable and could negatively surprise investors.
+During the test as a measure of the effectiveness of the investment was considered the maximum rate of net profit (with transaction costs).
+The authors believe this two criteria in evaluation the quality of simulation results as legitimate.
+In the first phase of the validation, the training period is indicated for moderate and prudent risk management.
+In the test phase (in terms of actual trading) investor is mainly interested in profit.\\
+
+The main aim of the research was to obtain the most effective investment strategies by dynamic selection of test period duration.
+Later in this article were used concepts of learning period, a fixed-length 1000 candles but with different start in time.
+After this were test period, a variable-length immediately following a period of learning.
+The authors looks for the best (by the criteria described above) length of the test period in their research.
+This most preferred length of the learning period can be understood in two ways.
+This length can be changed after each learning period adjusted by additional current information feedback about profits or losses in the test period.
+It may also be the average length of the test window established on the basis of several recent validation.\\
+
+The process of finding the optimum parameters for both of the described strategy is divided into two stages.
+In the first step of the process pseudo-random strategy is used to find the boundaries of the parameter space in which may be the optimal solution.
+Calmar ratio value was used to assess the adequacy of randomly selected parameter combinations for a given period of learning.
+In the second stage PSO [Kennedy, Eberhart]  algorithm was used, searching for solutions within prescribed limits of the first stage.
+The objective function was the Calmar ratio maximizing as in the first step.
+The above tactics was used for each stage of the learning period, then checked "sustainability" of designated sets of parameters for test periods of different lengths - the basic rate of 100 candles and the other in the range of 10-400.\\
+
+Figure ~\ref{metodyka} on page ~\pageref{metodyka} shows how the research was conducted .
+Knowing the historical data recoiled by 1000 candles and they used the approach described above in order to find optimal parameters for a given period .
+After the appointment of tests performed on the current data.
+The strategy of the learned parameters should be used as long as it will bring satisfactory results on new data.
+When results are no longer good enough , the following parameters for the re-designation of historical data.
+Thus, the authors aim is to determine the point where it should be re- conversion parameters.
+Additionally, the authors set out to test a new standard of quality prediction.
+Now, extending the period of testing can produce better results, but more slowly or can not slip out of the local capital than some initial period, when the classic "remembers" the nature of the market .
+This new criterion is profit attributable to one candle variable of the test period.\\
+
 \begin{figure}[h!]
@@
 \includegraphics[width=0.6\textwidth]{pictures/metodyka_badan.png}
-\caption{Metodyka przeprowadzonych badań dla przypadku zmiennego okna testowego}
+\caption{Methods of testing carried out to test of the variable size window}
 \label{metodyka}
@@
 
+Figures ~\ref{MiC100} and 4 ~\ref{MiD100} on page ~\pageref{MiD100}show the cumulative profit for the test period equal to 100 for the two treatment strategies .
+
 \begin{figure}[h!]
@@
 \includegraphics[width=0.7\textwidth]{pictures/mic_100.png}
-\caption{PODPIS}
+\caption{Chart of the cumulative profit for the strategy for sustainable TewiMiC test period equal 100}
 \label{MiC100}
@@
 \includegraphics[width=0.7\textwidth]{pictures/mid_100.png}
-\caption{PODPIS}
+\caption{Chart of the cumulative profit for the strategy for sustainable TewiMiD test period equal 100}
 \label{MiD100}
@@
 
+It may be noted that the two policies , the test period of 100 , the products allow for systematic performance gain over the period with
+ only small landslides . Profit for the final strategy is TewiMiC 0355 , for TewiMiD profit is several times smaller and amounts to 0.094 . 
+Smaller decreases are for the second strategy. In addition, it confirms the higher the Calmar ratio - 12.79 , 
+when the first of these strategies is on 10.22 .
+According to the authors , these are excellent , achieved on sections of the test , not the learning episodes .
+ The latter , of course, achieved significantly better results matching classifier . It is also understood asymmetry results for the two strategies
+ - the first one is focused on horizontal trend , the other on a downward trend . The results depend on the nature of the market , 
+which is considered by learning strategies automatically. Perhaps at another time , for other data these results could be different.
+In addition to the basic performance of the length of the test period equal to 100 , a number of studies conducted on different lengths
+ of the period. There may be more favorable long test window than arbitrarily selected window above the 100 candles .\\
+
 \begin{figure}[h!]
@@
 \includegraphics[width=0.7\textwidth]{pictures/cumulativeReturnsC.png}
-\caption{PODPIS}
+\caption{Results for TewiMiC}
 \label{Cum3DMiC}
@@
 
+Below, we present four graphs showing the results of the strategy TewiMiC . The first of these shows the effect of test duration on the gain curve in time.
+
 \begin{figure}[h!]
@@
 \includegraphics[width=0.7\textwidth]{pictures/mic_end.png}
-\caption{PODPIS}
+\caption{Earnings accumulated over time , depending on the length of the test period for TewiMIC}
 \label{Cum3DMiCend}
@@
 \FloatBarrier
+To see more detail for how long the test period are achieved optimal results plotted showing 2D final profit for each of the three sizes.
+ From Figure 4 shows that the number of candles for achieving a high and satisfactory results are attributable to 80-120 .
+ The window 100 reflects quite well so desired test section.\\
 
@@
 \includegraphics[width=0.7\textwidth]{pictures/cumulativeReturnsPerCandleC.png}
-\caption{PODPIS}
+\caption{The final cumulative profit depending on the length of the trial for TewiMiC}
 \label{Cum3DPerCMiC}
@@
 
+Due to the different length of the test period studied , more reliable value required in the decision is said earnings per candle , 
+or how much strategy can earn in one hour. This is shown in Figures 7 and 8 On this basis , and Table 1 it can be concluded that the
+ most effective strategy is for the period 60-110 test .
+It can therefore be concluded that the average window of 100 candles well " remembers" the learned classifier parameters . 
+Many times in the classification of patterns , it is important whether there are frequent . 
+Part of the dilemma is equivalent to earnings per candle but also in this one. 22 presented a large opening in
+ the periods test items.\\
+
 \begin{figure}[h!]
@@
 \includegraphics[width=0.7\textwidth]{pictures/mic_percandle_end.png}
-\caption{PODPIS}
+\caption{Cumulative Profit for one candle in time depending on the length of the trial for TewiMiC}
 \label{Cum3DPerCMiCend}
@@
 \begin{table}[h!] 
-\caption{TABLE 1}
+\caption{Final profits and Calmar ratio for the selected length of the test period for TewiMiC}
 \label{table1}
@@
 %%%%%%%%%
+
+Figures ~\ref{Cum3DMiD} and 4 ~\ref{Cum3DMiDend} on page ~\pageref{Cum3DMiDend} show the effect of the length of the test period the profit curve.
+If TewiMiD strategy makes it difficult to determine the optimal interval length of the trial .
+
 \begin{figure}[h!]
@@
 \includegraphics[width=0.7\textwidth]{pictures/cumulativeReturnsD.png}
-\caption{PODPIS}
+\caption{Earnings accumulated over time , depending on the length of the test period for TewiMID}
 \label{Cum3DMiD}
@@
 \includegraphics[width=0.7\textwidth]{pictures/mid_end.png}
-\caption{PODPIS}
+\caption{The final cumulative profit depending on the length of the trial for TewiMiD}
 \label{Cum3DMiDend}
@@
 
+It is possible , however, due to graphs showing earnings per hour ( candle ), depending on the length of the period and a table listing the final results of the two studies .
+Similarly to the first strategy, this period falls on 60 - 90 candles.
+
 \begin{figure}[h!]
@@
 \includegraphics[width=0.7\textwidth]{pictures/cumulativeReturnsPerCandleD.png}
-\caption{PODPIS}
+\caption{Cumulative Profit for one candle in time depending on the length of the trial for TewiMiD}
 \label{Cum3DPerCMiD}
@@
 \includegraphics[width=0.7\textwidth]{pictures/mid_percandle_end.png}
-\caption{PODPIS}
+\caption{The final cumulative profit per candle , depending on the length of the test period for TewiMiD}
 \label{Cum3DPerCMiDend}
@@
 \begin{table}[h!]
-\caption{TABLE 2}
+\caption{Final profits and Calmar ratio for the selected length of the test period for TewiMiD}
 \label{table2}
@@
  \FloatBarrier
+
+Of course, the optimal convergence test window length , at least approximately , is a great convenience in machine design algotradingu .
+It should be noted that the authors assume that it is possible to test whether each strategy separately and it is not necessarily synchronous learning rolling .\\
+
+Following a review of various lengths were obtained dependence validation periods shown in Figures 6 and 10 It shows a fairly obvious that a good fit to the data parameters of the test will continue for some time after the end of the learner .
+This is due to the assumption that the prevailing trends in the market for a different direction , the nature of which is well explored during the learning process .
+The authors have found that the use of optimization methods derived from the area of artificial intelligence, including the PSO [21], given good and quickly reaches the optimum values of the rules of the classifier, and good results in the initial stages of the test.
+For longer test periods, it can be indeed get good results overall , however, the effectiveness of the strategy per unit time decreases significantly.
+In the applied learning scheme uses a learning period of fixed length .
+The test results obtained allow to conclude that the constant average length of the test window is more efficient and easier to manage than a strategy adaptively changing the length of the period.
+Discovered during the period of effective learning strategies properties for a short time - for test data period was a time of both strategies from about 50 to 120 hours at 1000 hours of learning time.
+\\
+The real market means that from 2 to 5 days, it can be assumed that the re- learning the parameters of the strategy should be carried out 1-2 times a week.
+This frequency is quite practical even for manual search of optimal parameters without fully automatic trading.
+The options trading strategies ( substrategia TewiMiC and TewiMiD ) are complementary, since for each variant can develop a set of other parameters.
+Separate sets of parameters are adapted better to the outdoor during optimization nature of the market, allowing for example, often contain long positions in the market with more frequent by growth trends.
+It should be noted that a further optimizations discovered trends are short-term and during one cycle of validation can occur several changes in these trends, and they can be of different lengths.
+Then there is the situation that one of the variants of the strategy takes into account the length of trends for deviating significantly from trends indicated by the second variant.
+The two variants substrategii are part of an investment strategy that allows you to combine the target until the time the four options trading strategies .
+It is a fact of this study add to the substrategie associated with opening long positions based on condition ( order ) Buy Stop and short positions in accordance with the model Sell Limit.
+Interestingly according to the authors , may also improve the combined strategies through the synthesis of recommendations such as combining four variants , some of which (eg 3 ) indicates the need for the purchase , and some ( such as 1 ) the need to conclude the sale of stock, it contains a number of transactions indications resulting from the sum of the different options ( in the above example - two requests) .
+This implies a lower cost ( for example, 2 times smaller ).
+Transaction costs for certain decisions [complete ] ( link to an article on the conference TEWI - you do not have ) so tests can be omitted , and the reduction significantly affects the efficiency improvement investment strategy.
+The studies take into account the transaction costs for the pessimistic (above average costs in popular brokers).
+In practical terms , the strategy is so big possibilities.
+With traditional software, e-commerce (such as Metatrader) does not have the possibility of converting a simple strategy parameters during operation.
+This implies the need for a hybrid solution , consisting for example of interprocess communication between the software and e-commerce program developed in universal high-level language (eg Matlab, C\#).
+Algotarding future will very likely be increasingly active domain for experts in algorithmization and programming and less and less economists and econometricians .
+
 \bibliography{references-tewi}

### 2013-09-29 Article/Article20130912/LatexArt/tewi-paper-template.tex
added: references changed: position of figures
Signed-off-by: Aneta Bera <bera.aneta@gmail.com>

@@
 It is appropriate to seek all opportunities for profit.
-A similar philosophy is applied by several Krutsinger correspondents \cite{Krutsinger}, , who belong to most prominent traders in US, who advocate unfounded reversal of the direction of opening the positions in case of series of failures.\\
+A similar philosophy is applied by several Krutsinger correspondents \cite{Krutsinger}, who belong to most prominent traders in US, who advocate unfounded reversal of the direction of opening the positions in case of series of failures.\\
 
@@
 
-Firstly the terms for closing the long positions that were opened by conditions for TewiMiC will be presented.
+\noindent Firstly the terms for closing the long positions that were opened by conditions for TewiMiC will be presented.
 \begin{enumerate}
-\item Opened long position will be closed, if at the close of the candle \textit{(i + p2)} the position remained open, where \textit{i} - number of candle, which was opened;
+\item Opened long position will be closed, if at the close of the candle (i + p2) the position remained open, where i - number of candle, which was opened;
 
@@
 
-\item Position will be closed if inside the opening of the next (i + k)-th - the candle after i-th candle, in which the position was opened, following condition is met: 
+\item Position will be closed if inside the next (i + k)-th - the candle after i-th candle, in which the position was opened, following condition is met: 
 \begin{equation}
@@
 \end{equation}
+where LowPrice(i+k) – is a minimum value of (i+k)-th candle;
 
@@
 
-In sub strategy TewiMiD conditions will look slightly different.
+\noindent In sub strategy TewiMiD conditions will look slightly different.
 \begin{enumerate}
 \item Opened short position will be closed if at the close of the candle (i + p2)-th the position remained open;\\
-Position will be closed if at the opening of the next (i + k)-th - the candle after i-th candle, in which the position was opened, following condition is met:
+
+\item Position will be closed if at the opening of the next (i + k)-th - the candle after i-th candle, in which the position was opened, following condition is met:
 \begin{equation}
@@
 
-\item Position will be closed if inside the opening of the next (i + k)-th - the candle after i-th candle, in which the position was opened, following condition is met:
+\item Position will be closed if inside the next (i + k)-th - the candle after i-th candle, in which the position was opened, following condition is met:
 \begin{equation}
@@
 Calmar ratio value was used to assess the adequacy of randomly selected parameter combinations for a given period of learning.
-In the second stage PSO [Kennedy, Eberhart]  algorithm was used, searching for solutions within prescribed limits of the first stage.
+In the second stage PSO \cite{Kennedy}  algorithm was used, searching for solutions within prescribed limits of the first stage.
 The objective function was the Calmar ratio maximizing as in the first step.
@@
 
-Figure ~\ref{metodyka} on page ~\pageref{metodyka} shows how the research was conducted .
-Knowing the historical data recoiled by 1000 candles and they used the approach described above in order to find optimal parameters for a given period .
+Figure ~\ref{metodyka} on page ~\pageref{metodyka} shows how the research was conducted.
+Knowing the historical data recoiled by 1000 candles and they used the approach described above in order to find optimal parameters for a given period.
 After the appointment of tests performed on the current data.
 The strategy of the learned parameters should be used as long as it will bring satisfactory results on new data.
-When results are no longer good enough , the following parameters for the re-designation of historical data.
+When results are no longer good enough, the following parameters for the re-designation of historical data.
 Thus, the authors aim is to determine the point where it should be re- conversion parameters.
 Additionally, the authors set out to test a new standard of quality prediction.
-Now, extending the period of testing can produce better results, but more slowly or can not slip out of the local capital than some initial period, when the classic "remembers" the nature of the market .
+Now, extending the period of testing can produce better results, but more slowly or can not slip out of the local capital than some initial period, when the classic "remembers" the nature of the market.
 This new criterion is profit attributable to one candle variable of the test period.\\
@@
 \begin{center}
-\includegraphics[width=0.6\textwidth]{pictures/metodyka_badan.png}
+\includegraphics[width=0.45\textwidth]{pictures/metodyka_badan.png}
 \caption{Methods of testing carried out to test of the variable size window}
@@
 
-Figures ~\ref{MiC100} and 4 ~\ref{MiD100} on page ~\pageref{MiD100}show the cumulative profit for the test period equal to 100 for the two treatment strategies .
+Figures ~\ref{MiC100} and ~\ref{MiD100} on page ~\pageref{MiD100} show the cumulative profit for the test period equal to 100 for the two treatment strategies.
 
@@
 \begin{center}
-\includegraphics[width=0.7\textwidth]{pictures/mic_100.png}
+\includegraphics[width=0.5\textwidth]{pictures/mic_100.png}
 \caption{Chart of the cumulative profit for the strategy for sustainable TewiMiC test period equal 100}
@@
 \begin{center}
-\includegraphics[width=0.7\textwidth]{pictures/mid_100.png}
+\includegraphics[width=0.5\textwidth]{pictures/mid_100.png}
 \caption{Chart of the cumulative profit for the strategy for sustainable TewiMiD test period equal 100}
@@
 
-It may be noted that the two policies , the test period of 100 , the products allow for systematic performance gain over the period with
- only small landslides . Profit for the final strategy is TewiMiC 0355 , for TewiMiD profit is several times smaller and amounts to 0.094 . 
-Smaller decreases are for the second strategy. In addition, it confirms the higher the Calmar ratio - 12.79 , 
-when the first of these strategies is on 10.22 .
-According to the authors , these are excellent , achieved on sections of the test , not the learning episodes .
- The latter , of course, achieved significantly better results matching classifier . It is also understood asymmetry results for the two strategies
- - the first one is focused on horizontal trend , the other on a downward trend . The results depend on the nature of the market , 
-which is considered by learning strategies automatically. Perhaps at another time , for other data these results could be different.
-In addition to the basic performance of the length of the test period equal to 100 , a number of studies conducted on different lengths
- of the period. There may be more favorable long test window than arbitrarily selected window above the 100 candles .\\
+It may be noted that the two policies, the test period of 100, the products allow for systematic performance gain over the period with
+ only small landslides. Profit for the final strategy is TewiMiC 0.355, for TewiMiD profit is several times smaller and amounts to 0.094. 
+Smaller decreases are for the second strategy. In addition, it confirms the higher the Calmar ratio - 12.79, 
+when the first of these strategies is on 10.22.
+According to the authors, these are excellent, achieved on sections of the test, not the learning episodes.
+ The latter, of course, achieved significantly better results matching classifier. It is also understood asymmetry results for the two strategies
+ - the first one is focused on horizontal trend, the other on a downward trend. The results depend on the nature of the market, 
+which is considered by learning strategies automatically. Perhaps at another time, for other data these results could be different.
+In addition to the basic performance of the length of the test period equal to 100, a number of studies conducted on different lengths
+ of the period. There may be more favorable long test window than arbitrarily selected window above the 100 candles.\\
 
+Below, we present four graphs showing the results of the strategy TewiMiC.
+The first of these (Figure \ref{Cum3DMiC} on page \pageref{Cum3DMiC}) shows the effect of test duration on the gain curve in time.\\
+To see more detail for how long the test period are achieved optimal results plotted showing 2D final profit for each of the three sizes.
+ From Figure \ref{Cum3DMiCend} on page \pageref{Cum3DMiCend} shows that the number of candles for achieving a high and satisfactory results are attributable to 80-120.
+ The window 100 reflects quite well so desired test section.\\
 \begin{figure}[h!]
 \begin{center}
-\includegraphics[width=0.7\textwidth]{pictures/cumulativeReturnsC.png}
+\includegraphics[width=0.5\textwidth]{pictures/cumulativeReturnsC.png}
 \caption{Results for TewiMiC}
@@
 
-Below, we present four graphs showing the results of the strategy TewiMiC . The first of these shows the effect of test duration on the gain curve in time.
-
 \begin{figure}[h!]
 \begin{center}
-\includegraphics[width=0.7\textwidth]{pictures/mic_end.png}
-\caption{Earnings accumulated over time , depending on the length of the test period for TewiMIC}
+\includegraphics[width=0.5\textwidth]{pictures/mic_end.png}
+\caption{Earnings accumulated over time, depending on the length of the test period for TewiMIC}
 \label{Cum3DMiCend}
@@
 \FloatBarrier
-To see more detail for how long the test period are achieved optimal results plotted showing 2D final profit for each of the three sizes.
- From Figure 4 shows that the number of candles for achieving a high and satisfactory results are attributable to 80-120 .
- The window 100 reflects quite well so desired test section.\\
+
+Due to the different length of the test period studied, more reliable value required in the decision is said earnings per candle, 
+or how much strategy can earn in one hour. This is shown in Figures \ref{Cum3DPerCMiC} and \ref{Cum3DPerCMiCend} On this basis, and Table \ref{table1} it can be concluded that the
+ most effective strategy is for the period 60-110 test.
+It can therefore be concluded that the average window of 100 candles well " remembers" the learned classifier parameters. 
+Many times in the classification of patterns, it is important whether there are frequent. 
+Part of the dilemma is equivalent to earnings per candle but also in this one. 22 presented a large opening in
+ the periods test items.\\
 
@@
 \begin{center}
-\includegraphics[width=0.7\textwidth]{pictures/cumulativeReturnsPerCandleC.png}
+\includegraphics[width=0.5\textwidth]{pictures/cumulativeReturnsPerCandleC.png}
 \caption{The final cumulative profit depending on the length of the trial for TewiMiC}
@@
 
-Due to the different length of the test period studied , more reliable value required in the decision is said earnings per candle , 
-or how much strategy can earn in one hour. This is shown in Figures 7 and 8 On this basis , and Table 1 it can be concluded that the
- most effective strategy is for the period 60-110 test .
-It can therefore be concluded that the average window of 100 candles well " remembers" the learned classifier parameters . 
-Many times in the classification of patterns , it is important whether there are frequent . 
-Part of the dilemma is equivalent to earnings per candle but also in this one. 22 presented a large opening in
- the periods test items.\\
-
 \begin{figure}[h!]
 \begin{center}
-\includegraphics[width=0.7\textwidth]{pictures/mic_percandle_end.png}
+\includegraphics[width=0.5\textwidth]{pictures/mic_percandle_end.png}
 \caption{Cumulative Profit for one candle in time depending on the length of the trial for TewiMiC}
@@
 \caption{Final profits and Calmar ratio for the selected length of the test period for TewiMiC}
+\scriptsize
 \label{table1}
+\begin{center}
 \begin{tabular}{|l|l|l|l|l|l|} 
@@
  \hline \end{tabular} 
+\end{center}
  \end{table}
@@
 
-Figures ~\ref{Cum3DMiD} and 4 ~\ref{Cum3DMiDend} on page ~\pageref{Cum3DMiDend} show the effect of the length of the test period the profit curve.
-If TewiMiD strategy makes it difficult to determine the optimal interval length of the trial .
+Figures ~\ref{Cum3DMiD} and ~\ref{Cum3DMiDend} on page ~\pageref{Cum3DMiDend} show the effect of the length of the test period the profit curve.
+If TewiMiD strategy makes it difficult to determine the optimal interval length of the trial.
 
@@
 \begin{center}
-\includegraphics[width=0.7\textwidth]{pictures/cumulativeReturnsD.png}
-\caption{Earnings accumulated over time , depending on the length of the test period for TewiMID}
+\includegraphics[width=0.442\textwidth]{pictures/cumulativeReturnsD.png}
+\caption{Earnings accumulated over time, depending on the length of the test period for TewiMID}
 \label{Cum3DMiD}
@@
 \begin{center}
-\includegraphics[width=0.7\textwidth]{pictures/mid_end.png}
+\includegraphics[width=0.42\textwidth]{pictures/mid_end.png}
 \caption{The final cumulative profit depending on the length of the trial for TewiMiD}
@@
 
-It is possible , however, due to graphs showing earnings per hour ( candle ), depending on the length of the period and a table listing the final results of the two studies .
+It is possible, however, due to graphs showing earnings per hour --- candle (Figures \ref{Cum3DPerCMiD} and \ref{Cum3DPerCMiDend}), depending on the length of the period and a Table \ref{table2} listing the final results of the two studies.
 Similarly to the first strategy, this period falls on 60 - 90 candles.
@@
 \begin{center}
-\includegraphics[width=0.7\textwidth]{pictures/cumulativeReturnsPerCandleD.png}
+\includegraphics[width=0.5\textwidth]{pictures/cumulativeReturnsPerCandleD.png}
 \caption{Cumulative Profit for one candle in time depending on the length of the trial for TewiMiD}
@@
 \begin{center}
-\includegraphics[width=0.7\textwidth]{pictures/mid_percandle_end.png}
-\caption{The final cumulative profit per candle , depending on the length of the test period for TewiMiD}
+\includegraphics[width=0.5\textwidth]{pictures/mid_percandle_end.png}
+\caption{The final cumulative profit per candle, depending on the length of the test period for TewiMiD}
 \label{Cum3DPerCMiDend}
@@
 \caption{Final profits and Calmar ratio for the selected length of the test period for TewiMiD}
+\scriptsize
 \label{table2}
+\begin{center}
  \begin{tabular}{|l|l|l|l|l|l|} 
@@
 
-Of course, the optimal convergence test window length , at least approximately , is a great convenience in machine design algotradingu .
-It should be noted that the authors assume that it is possible to test whether each strategy separately and it is not necessarily synchronous learning rolling .\\
+Of course, the optimal convergence test window length, at least approximately, is a great convenience in machine design algotradingu.
+It should be noted that the authors assume that it is possible to test whether each strategy separately and it is not necessarily synchronous learning rolling.\\
 
-Following a review of various lengths were obtained dependence validation periods shown in Figures 6 and 10 It shows a fairly obvious that a good fit to the data parameters of the test will continue for some time after the end of the learner .
-This is due to the assumption that the prevailing trends in the market for a different direction , the nature of which is well explored during the learning process .
-The authors have found that the use of optimization methods derived from the area of artificial intelligence, including the PSO [21], given good and quickly reaches the optimum values of the rules of the classifier, and good results in the initial stages of the test.
-For longer test periods, it can be indeed get good results overall , however, the effectiveness of the strategy per unit time decreases significantly.
-In the applied learning scheme uses a learning period of fixed length .
+\section{Conclusion}
+
+Following a review of various lengths were obtained dependence validation periods shown in Figures \ref{Cum3DMiDend} and \ref{Cum3DMiDend} It shows a fairly obvious that a good fit to the data parameters of the test will continue for some time after the end of the learner.
+This is due to the assumption that the prevailing trends in the market for a different direction, the nature of which is well explored during the learning process.
+The authors have found that the use of optimization methods derived from the area of artificial intelligence, including the PSO \cite{Kennedy}, given good and quickly reaches the optimum values of the rules of the classifier, and good results in the initial stages of the test.
+For longer test periods, it can be indeed get good results overall, however, the effectiveness of the strategy per unit time decreases significantly.
+In the applied learning scheme uses a learning period of fixed length.
 The test results obtained allow to conclude that the constant average length of the test window is more efficient and easier to manage than a strategy adaptively changing the length of the period.
@@
 Then there is the situation that one of the variants of the strategy takes into account the length of trends for deviating significantly from trends indicated by the second variant.
-The two variants substrategii are part of an investment strategy that allows you to combine the target until the time the four options trading strategies .
+The two variants substrategii are part of an investment strategy that allows you to combine the target until the time the four options trading strategies.
 It is a fact of this study add to the substrategie associated with opening long positions based on condition ( order ) Buy Stop and short positions in accordance with the model Sell Limit.
-Interestingly according to the authors , may also improve the combined strategies through the synthesis of recommendations such as combining four variants , some of which (eg 3 ) indicates the need for the purchase , and some ( such as 1 ) the need to conclude the sale of stock, it contains a number of transactions indications resulting from the sum of the different options ( in the above example - two requests) .
+Interestingly according to the authors, may also improve the combined strategies through the synthesis of recommendations such as combining four variants, some of which (eg 3 ) indicates the need for the purchase, and some ( such as 1 ) the need to conclude the sale of stock, it contains a number of transactions indications resulting from the sum of the different options ( in the above example - two requests).
 This implies a lower cost ( for example, 2 times smaller ).
-Transaction costs for certain decisions [complete ] ( link to an article on the conference TEWI - you do not have ) so tests can be omitted , and the reduction significantly affects the efficiency improvement investment strategy.
+Transaction costs for certain decisions [complete ] ( link to an article on the conference TEWI - you do not have ) so tests can be omitted, and the reduction significantly affects the efficiency improvement investment strategy.
 The studies take into account the transaction costs for the pessimistic (above average costs in popular brokers).
-In practical terms , the strategy is so big possibilities.
+In practical terms, the strategy is so big possibilities.
 With traditional software, e-commerce (such as Metatrader) does not have the possibility of converting a simple strategy parameters during operation.
-This implies the need for a hybrid solution , consisting for example of interprocess communication between the software and e-commerce program developed in universal high-level language (eg Matlab, C\#).
-Algotarding future will very likely be increasingly active domain for experts in algorithmization and programming and less and less economists and econometricians .
+This implies the need for a hybrid solution, consisting for example of interprocess communication between the software and e-commerce program developed in universal high-level language (eg Matlab, C\#).
+Algotarding future will very likely be increasingly active domain for experts in algorithmization and programming and less and less economists and econometricians.
 

### 2013-09-29 Article/Article20130912/LatexArt/tewi-paper-template.tex
method description

@@
 The objective function was the Calmar ratio maximizing as in the first step.
-The above tactics was used for each stage of the learning period, then checked "sustainability" of designated sets of parameters for test periods of different lengths - the basic rate of 100 candles and the other in the range of 10-400.\\
+The above tactics were used for each stage of the learning period, after this "sustainabilities" of designated sets of parameters for test periods of different lengths were determined - for the basic rate of 100 candles and the other in the range of 10-400.\\
 

### 2013-09-29 Article/Article20130912/LatexArt/tewi-paper-template_minipages.tex
two versions: minipages, added acknowledgement

--- 2013-09-29 Article/Article20130912/LatexArt/tewi-paper-template.tex
@@
 \affiliation{%
-  \inst{1}West Pomeranian University of Technology,Szczecin, Poland\\
+  \inst{1}West Pomeranian University of Technology, Szczecin, Poland\\
   \{awilinski, abera, wnowicki, pblaszynski\}@wi.zut.edu.pl
@@
 
-Figure ~\ref{metodyka} on page ~\pageref{metodyka} shows how the research was conducted.
+Figure ~\ref{research_methods} on page ~\pageref{research_methods} shows how the research was conducted.
 Knowing the historical data recoiled by 1000 candles and they used the approach described above in order to find optimal parameters for a given period.
@@
 \caption{Methods of testing carried out to test of the variable size window}
-\label{metodyka}
+\label{research_methods}
 \end{center}
@@
 \begin{figure}[h!]
+\begin{minipage}{.49\linewidth}
 \begin{center}
-\includegraphics[width=0.5\textwidth]{pictures/mic_100.png}
-\caption{Chart of the cumulative profit for the strategy for sustainable TewiMiC test period equal 100}
+\includegraphics[width=\textwidth]{pictures/mic_100.png}
+\subcaption{Sub strategy TewiMiC}
 \label{MiC100}
 \end{center}
-\end{figure}
-\FloatBarrier
-
-\begin{figure}[h!]
+\end{minipage}
+\begin{minipage}{.49\linewidth}
 \begin{center}
-\includegraphics[width=0.5\textwidth]{pictures/mid_100.png}
-\caption{Chart of the cumulative profit for the strategy for sustainable TewiMiD test period equal 100}
+\includegraphics[width=\textwidth]{pictures/mid_100.png}
+\subcaption{Sub strategy TewiMiD}
 \label{MiD100}
 \end{center}
+\end{minipage}
+
+\caption{Chart of the cumulative profit for the strategy for test period equal 100}
 \end{figure}
@@
 Below, we present four graphs showing the results of the strategy TewiMiC.
-The first of these (Figure \ref{Cum3DMiC} on page \pageref{Cum3DMiC}) shows the effect of test duration on the gain curve in time.\\
+The first of these (Figure \ref{Cum3DMiC} on page \pageref{Cum3DMiC}) shows the effect of test duration on the gain curve in time.
 To see more detail for how long the test period are achieved optimal results plotted showing 2D final profit for each of the three sizes.
  From Figure \ref{Cum3DMiCend} on page \pageref{Cum3DMiCend} shows that the number of candles for achieving a high and satisfactory results are attributable to 80-120.
- The window 100 reflects quite well so desired test section.\\
+ The window 100 reflects quite well so desired test section.
 \begin{figure}[h!]
+\begin{minipage}{.45\linewidth}
 \begin{center}
-\includegraphics[width=0.5\textwidth]{pictures/cumulativeReturnsC.png}
-\caption{Results for TewiMiC}
+\includegraphics[width=\textwidth]{pictures/cumulativeReturnsC.png}
+\subcaption{Results in 3D}
 \label{Cum3DMiC}
 \end{center}
-\end{figure}
-\FloatBarrier
-
-\begin{figure}[h!]
+\end{minipage}
+\begin{minipage}{.45\linewidth}
 \begin{center}
-\includegraphics[width=0.5\textwidth]{pictures/mic_end.png}
-\caption{Earnings accumulated over time, depending on the length of the test period for TewiMIC}
+\includegraphics[width=\textwidth]{pictures/mic_end.png}
+\subcaption{Final results}
 \label{Cum3DMiCend}
 \end{center}
+\end{minipage}
+\caption{Earnings accumulated over time, depending on the length of the test period for TewiMIC}
 \end{figure}
@@
 \begin{figure}[h!]
+\centering
+\begin{minipage}{.45\linewidth}
 \begin{center}
-\includegraphics[width=0.5\textwidth]{pictures/cumulativeReturnsPerCandleC.png}
-\caption{The final cumulative profit depending on the length of the trial for TewiMiC}
+\includegraphics[width=\textwidth]{pictures/cumulativeReturnsPerCandleC.png}
+\subcaption{Results in 3D}
 \label{Cum3DPerCMiC}
 \end{center}
-\end{figure}
-\FloatBarrier
-
-\begin{figure}[h!]
+\end{minipage}
+\begin{minipage}{.45\linewidth}
 \begin{center}
-\includegraphics[width=0.5\textwidth]{pictures/mic_percandle_end.png}
-\caption{Cumulative Profit for one candle in time depending on the length of the trial for TewiMiC}
+\includegraphics[width=\textwidth]{pictures/mic_percandle_end.png}
+\subcaption{Final results}
 \label{Cum3DPerCMiCend}
 \end{center}
+\end{minipage}
+\caption{Cumulative Profit for one candle in time depending on the length of the trial for TewiMiC}
 \end{figure}
@@
 \begin{figure}[h!]
+\begin{minipage}{.45\linewidth}
 \begin{center}
-\includegraphics[width=0.442\textwidth]{pictures/cumulativeReturnsD.png}
-\caption{Earnings accumulated over time, depending on the length of the test period for TewiMID}
+\includegraphics[width=\textwidth]{pictures/cumulativeReturnsD.png}
+\subcaption{Results in 3D}
 \label{Cum3DMiD}
 \end{center}
-\end{figure}
-\FloatBarrier
-
-\begin{figure}[h!]
+\end{minipage}
+\begin{minipage}{.45\linewidth}
 \begin{center}
-\includegraphics[width=0.42\textwidth]{pictures/mid_end.png}
-\caption{The final cumulative profit depending on the length of the trial for TewiMiD}
+\includegraphics[width=\textwidth]{pictures/mid_end.png}
+\subcaption{Final results}
 \label{Cum3DMiDend}
 \end{center}
+\end{minipage}
+\caption{Earnings accumulated over time, depending on the length of the test period for TewiMID}
 \end{figure}
@@
 \begin{figure}[h!]
+\centering
+\begin{minipage}{.45\linewidth}
 \begin{center}
-\includegraphics[width=0.5\textwidth]{pictures/cumulativeReturnsPerCandleD.png}
-\caption{Cumulative Profit for one candle in time depending on the length of the trial for TewiMiD}
+\includegraphics[width=\textwidth]{pictures/cumulativeReturnsPerCandleD.png}
+\subcaption{Results in 3D}
 \label{Cum3DPerCMiD}
 \end{center}
-\end{figure}
-\FloatBarrier
-
-\begin{figure}[h!]
+\end{minipage}
+\begin{minipage}{.45\linewidth}
 \begin{center}
-\includegraphics[width=0.5\textwidth]{pictures/mid_percandle_end.png}
-\caption{The final cumulative profit per candle, depending on the length of the test period for TewiMiD}
+\includegraphics[width=\textwidth]{pictures/mid_percandle_end.png}
+\subcaption{Final results}
 \label{Cum3DPerCMiDend}
 \end{center}
+\end{minipage}
+\caption{Cumulative Profit for one candle in time depending on the length of the trial for TewiMiD}
 \end{figure}
@@
  \FloatBarrier
-
 Of course, the optimal convergence test window length, at least approximately, is a great convenience in machine design algotradingu.
@@
 This implies the need for a hybrid solution, consisting for example of interprocess communication between the software and e-commerce program developed in universal high-level language (eg Matlab, C\#).
-Algotarding future will very likely be increasingly active domain for experts in algorithmization and programming and less and less economists and econometricians.
+Algotarding future will very likely be increasingly active domain for experts in algorithmization and programming and less and less economists and econometricians.\\
+
+\noindent Acknowledgment: Work done within the project TEWI financed from the Operational Programme of Innovative Economy in years 2012-2013.
 

### 2013-09-29 Article/Article20130912/LatexArt/tewi-paper-template.tex
two versions, added acknowledgement

@@
 This approach is consistent with the classic aim of machine learning shown by K.Murphy’ego \cite{Murphy}, especially to financial markets described by Satchwell \cite{Satchwell}.
-Authors also intend to follow the principle of reproducibility of studies by other researchers, as well as by themselves, in other data environments, to make sense of the use of computational intelligence in its reasonable reproducibility \cite{Polya, Donoho}, in extracting of the regularity from chaos \cite{Ball, Pedrycz}.
-\\
+Authors also intend to follow the principle of reproducibility of studies by other researchers, as well as by themselves, in other data environments, to make sense of the use of computational intelligence in its reasonable reproducibility \cite{Polya, Donoho}, in extracting of the regularity from chaos \cite{Ball, Pedrycz}.\\
 
@@
 The objective function was the Calmar ratio maximizing as in the first step.
-The above tactics were used for each stage of the learning period, after this "sustainabilities" of designated sets of parameters for test periods of different lengths were determined - for the basic rate of 100 candles and the other in the range of 10-400.\\
+The above tactics was used for each stage of the learning period, then checked "sustainability" of designated sets of parameters for test periods of different lengths - the basic rate of 100 candles and the other in the range of 10-400.\\
 

### 2013-09-29 Article/Article20130912/LatexArt/tewi-paper-template_minipages.tex
research procedure

@@
 Figure ~\ref{research_methods} on page ~\pageref{research_methods} shows how the research was conducted.
-Knowing the historical data recoiled by 1000 candles and they used the approach described above in order to find optimal parameters for a given period.
-After the appointment of tests performed on the current data.
-The strategy of the learned parameters should be used as long as it will bring satisfactory results on new data.
-When results are no longer good enough, the following parameters for the re-designation of historical data.
-Thus, the authors aim is to determine the point where it should be re- conversion parameters.
+Knowing the historical data 1000 candles were used and approach described above in order to find optimal parameters for a given period was used for this dataset.
+After the parameters search, tests were performed on the current data.
+The strategy for the learned parameters should be used as long as it will bring satisfactory results on new data.
+When results were no longer good enough, the next parameters search were performed on next piece of historical data.
+Thus, the authors aim is to determine the point where it should parameters be recalculated.
 Additionally, the authors set out to test a new standard of quality prediction.
-Now, extending the period of testing can produce better results, but more slowly or can not slip out of the local capital than some initial period, when the classic "remembers" the nature of the market.
-This new criterion is profit attributable to one candle variable of the test period.\\
+Now, extending the period of testing can produce better results, but more slowly or with local drawndown in comparision to first period, when the classifier "remembers" the nature of the market.
+This new criteria is profit attributable to one candle of the testing period.\\
 

### 2013-09-29 Article/Article20130912/LatexArt/tewi-paper-template_minipages.tex
results description

@@
 \includegraphics[width=0.45\textwidth]{pictures/metodyka_badan.png}
-\caption{Methods of testing carried out to test of the variable size window}
+\caption{Methods of testing carried out to test the variable size window}
 \label{research_methods}
@@
 
-Figures ~\ref{MiC100} and ~\ref{MiD100} on page ~\pageref{MiD100} show the cumulative profit for the test period equal to 100 for the two treatment strategies.
+Figures ~\ref{MiC100} and ~\ref{MiD100} on page ~\pageref{MiD100} shows the cumulative profit for the test period equal to 100 candles (hours) for the two examined strategies.
 
@@
 
-\caption{Chart of the cumulative profit for the strategy for test period equal 100}
+\caption{Chart of the profit for the strategy with fixed test period size - 100 candles}
 \end{figure}
@@
 
-It may be noted that the two policies, the test period of 100, the products allow for systematic performance gain over the period with
- only small landslides. Profit for the final strategy is TewiMiC 0.355, for TewiMiD profit is several times smaller and amounts to 0.094. 
-Smaller decreases are for the second strategy. In addition, it confirms the higher the Calmar ratio - 12.79, 
-when the first of these strategies is on 10.22.
-According to the authors, these are excellent, achieved on sections of the test, not the learning episodes.
- The latter, of course, achieved significantly better results matching classifier. It is also understood asymmetry results for the two strategies
- - the first one is focused on horizontal trend, the other on a downward trend. The results depend on the nature of the market, 
-which is considered by learning strategies automatically. Perhaps at another time, for other data these results could be different.
-In addition to the basic performance of the length of the test period equal to 100, a number of studies conducted on different lengths
- of the period. There may be more favorable long test window than arbitrarily selected window above the 100 candles.\\
+It may be noted that the two policies, for the test period of 100, allow for systematic profit in examined period with only for small drawndowns.
+Profit for the strategy TewiMiC 0.355, for TewiMiD profit is several times smaller and amounts to 0.094.
+But second strategy has smaller drawndowns.
+In addition, it is confirmed with the higher Calmar ratio - 12.79, where the result for first of these strategies is 10.22.
+According to the authors, results are excellent, achieved on testing sections, not on the learning periods.
+On learning periods, of course, significantly better results were achieved with classifier matching.
+It is also clear that asymmetry results for the two strategies arise from different approaches - the first one is focused on horizontal trend, the other on a downward trend.
+The results depend on the nature of the market, which is automatically founded by learning strategies.
+Perhaps at another period of time, for other data these results could be different.
+In addition to the basic performance of the length of the test period equal to 100, a number of studies were conducted on different lengths of the testing period.
+There may be more favorable length of test window than arbitrarily selected window length of 100 candles.\\
 
 Below, we present four graphs showing the results of the strategy TewiMiC.
-The first of these (Figure \ref{Cum3DMiC} on page \pageref{Cum3DMiC}) shows the effect of test duration on the gain curve in time.
+The first of these (Figure \ref{Cum3DMiC} on page \pageref{Cum3DMiC}) shows the effect of test duration on the profit curve in time.
 To see more detail for how long the test period are achieved optimal results plotted showing 2D final profit for each of the three sizes.

### 2013-09-29 Article/Article20130912/LatexArt/tewi-paper-template_minipages.tex
TewiMiC results

@@
 
+Results for TewiMiC
 Below, we present four graphs showing the results of the strategy TewiMiC.
 The first of these (Figure \ref{Cum3DMiC} on page \pageref{Cum3DMiC}) shows the effect of test duration on the profit curve in time.
-To see more detail for how long the test period are achieved optimal results plotted showing 2D final profit for each of the three sizes.
- From Figure \ref{Cum3DMiCend} on page \pageref{Cum3DMiCend} shows that the number of candles for achieving a high and satisfactory results are attributable to 80-120.
- The window 100 reflects quite well so desired test section.
+To show how long in the test period optimal results are achieved we plotted 2D chart of final profit for each of the examined sizes.
+Figure \ref{Cum3DMiCend} on page \pageref{Cum3DMiCend} shows that the number of candles for achieving a high and satisfactory results are attributable to 80-120.
+The window size 100 reflects quite well expected test section.
+
 \begin{figure}[h!]
@@
 
-Due to the different length of the test period studied, more reliable value required in the decision is said earnings per candle, 
-or how much strategy can earn in one hour. This is shown in Figures \ref{Cum3DPerCMiC} and \ref{Cum3DPerCMiCend} On this basis, and Table \ref{table1} it can be concluded that the
- most effective strategy is for the period 60-110 test.
-It can therefore be concluded that the average window of 100 candles well " remembers" the learned classifier parameters. 
-Many times in the classification of patterns, it is important whether there are frequent. 
-Part of the dilemma is equivalent to earnings per candle but also in this one. 22 presented a large opening in
- the periods test items.\\
+Due to the different length of the test period studied, more reliable value required in the decision is earnings per candle, what means how much strategy can earn in one hour.
+This is shown in Figures \ref{Cum3DPerCMiC} and \ref{Cum3DPerCMiCend}.
+On this basis, and Table 1 it can be concluded that the strategy is most effective for the testing period length beetween 60 and 110 hours.
+It can therefore be concluded that the average window of 100 candles well "remembers" the learned classifier parameters.
+Many times in the classification of patterns, it is important whether patterns are frequent.
+Part of the dilemma is solved by introducing earnings per candle but also in Table.
+\ref{table1} a count of opened market positions in the testing periods are presented.\\
 
@@
 \end{minipage}
-\caption{Cumulative Profit for one candle in time depending on the length of the trial for TewiMiC}
+\caption{Cumulative profit for one candle in time depending on the length of the testing period for TewiMiC}
 \end{figure}
@@
 %%%%%%%%%
+
+Results for TewiMiD
 

### 2013-09-29 Article/Article20130912/LatexArt/tewi-paper-template_minipages.tex
TewiMiD results

@@
 
-Figures ~\ref{Cum3DMiD} and ~\ref{Cum3DMiDend} on page ~\pageref{Cum3DMiDend} show the effect of the length of the test period the profit curve.
-If TewiMiD strategy makes it difficult to determine the optimal interval length of the trial.
+Figures ~\ref{Cum3DMiD} and ~\ref{Cum3DMiDend} on page ~\pageref{Cum3DMiDend} shows the effect of the length of the test period on the profit curve.
+In case of TewiMiD strategy it is difficult to determine the optimal interval length of the testing period.
 
@@
 
-It is possible, however, due to graphs showing earnings per hour --- candle (Figures \ref{Cum3DPerCMiD} and \ref{Cum3DPerCMiDend}), depending on the length of the period and a Table \ref{table2} listing the final results of the two studies.
-Similarly to the first strategy, this period falls on 60 - 90 candles.
+It is possible, however, due to graphs showing earnings per hour (candle) (Figures \ref{Cum3DPerCMiD} and \ref{Cum3DPerCMiDend}), depending on the length of the period and a Table \ref{table2} listing the final results of the two studies.
+Similarly to the first strategy, length of this period is beetween 60  and 90 candles.
 
@@
 \end{minipage}
-\caption{Cumulative Profit for one candle in time depending on the length of the trial for TewiMiD}
+\caption{Cumulative profit for one candle in time depending on the length of the testing period for TewiMiD}
 \end{figure}
@@
  \FloatBarrier
-Of course, the optimal convergence test window length, at least approximately, is a great convenience in machine design algotradingu.
-It should be noted that the authors assume that it is possible to test whether each strategy separately and it is not necessarily synchronous learning rolling.\\
+Of course, the optimal convergence test window length, at least approximately, is a great convenience in design of automatic strategy for algotrading.
+It should be noted that the authors assume that it is possible to test each strategy separately and it is not required to synchronize.\\
 
@@
 This implies a lower cost ( for example, 2 times smaller ).
-Transaction costs for certain decisions [complete ] ( link to an article on the conference TEWI - you do not have ) so tests can be omitted, and the reduction significantly affects the efficiency improvement investment strategy.
+Transaction costs for certain decisions so tests can be omitted, and the reduction significantly affects the efficiency improvement investment strategy.
 The studies take into account the transaction costs for the pessimistic (above average costs in popular brokers).

### 2013-09-29 Article/Article20130912/LatexArt/tewi-paper-template_minipages.tex
Conclusions 1

@@
 
-Following a review of various lengths were obtained dependence validation periods shown in Figures \ref{Cum3DMiDend} and \ref{Cum3DMiDend} It shows a fairly obvious that a good fit to the data parameters of the test will continue for some time after the end of the learner.
-This is due to the assumption that the prevailing trends in the market for a different direction, the nature of which is well explored during the learning process.
-The authors have found that the use of optimization methods derived from the area of artificial intelligence, including the PSO \cite{Kennedy}, given good and quickly reaches the optimum values of the rules of the classifier, and good results in the initial stages of the test.
-For longer test periods, it can be indeed get good results overall, however, the effectiveness of the strategy per unit time decreases significantly.
-In the applied learning scheme uses a learning period of fixed length.
-The test results obtained allow to conclude that the constant average length of the test window is more efficient and easier to manage than a strategy adaptively changing the length of the period.
-Discovered during the period of effective learning strategies properties for a short time - for test data period was a time of both strategies from about 50 to 120 hours at 1000 hours of learning time.
+Following a review of various lengths dependence validation periods shown in Figures \ref{Cum3DMiDend} and \ref{Cum3DMiDend} were obtained.
+It shows a fairly obvious that a good fit of the parameters of the test period will continue for some time after the end of the learning.
+This is due to the assumption that there are trends in the market in different direction.
+The nature of trends is well explored during the learning process.
+The authors have found that the use of optimization methods derived from the area of artificial intelligence, including the PSO \cite{Kennedy}, given good and quickly reached the optimum values of the rules of the classifier, and good results in the initial stages of the test period.
+For longer test periods, it can be indeed get good results overall, however, the effectiveness of the strategy per hour decreases significantly.
+Obtained results allow to conclude that the constant average length of the test window is more efficient and easier to manage than a strategy adaptively changing the length of the period.
+Strategies properties discovered during the learning period are effective for a short time - for test data period - good lengths for both strategies are about 50 to 120 hours at 1000 hours of learning time.
 \\

### 2013-09-29 Article/Article20130912/LatexArt/tewi-paper-template_minipages.tex
new figure and table position

@@
 The objective function was the Calmar ratio maximizing as in the first step.
-The above tactics was used for each stage of the learning period, then checked "sustainability" of designated sets of parameters for test periods of different lengths - the basic rate of 100 candles and the other in the range of 10-400.\\
-
+The above tactics was used for each stage of the learning period, then checked "sustainability" of designated sets of parameters for test periods of different lengths - the basic rate of 100 candles and the other in the range of 10-400.
 Figure ~\ref{research_methods} on page ~\pageref{research_methods} shows how the research was conducted.
@@
 \begin{center}
-\includegraphics[width=0.45\textwidth]{pictures/metodyka_badan.png}
+\includegraphics[width=0.4\textwidth]{pictures/metodyka_badan.png}
 \caption{Methods of testing carried out to test the variable size window}
@@
 \begin{center}
-\includegraphics[width=\textwidth]{pictures/mic_100.png}
+\includegraphics[width=0.9\textwidth]{pictures/mic_100.png}
 \subcaption{Sub strategy TewiMiC}
@@
 \begin{center}
-\includegraphics[width=\textwidth]{pictures/mid_100.png}
+\includegraphics[width=0.9\textwidth]{pictures/mid_100.png}
 \subcaption{Sub strategy TewiMiD}
@@
 
-Results for TewiMiC
+\textbf{Results for TewiMiC}\\
 Below, we present four graphs showing the results of the strategy TewiMiC.
@@
 \begin{figure}[h!]
-\begin{minipage}{.45\linewidth}
+\begin{minipage}{.49\linewidth}
 \begin{center}
-\includegraphics[width=\textwidth]{pictures/cumulativeReturnsC.png}
+\includegraphics[width=0.82\textwidth]{pictures/cumulativeReturnsC.png}
 \subcaption{Results in 3D}
@@
 \end{minipage}
-\begin{minipage}{.45\linewidth}
+\begin{minipage}{.49\linewidth}
 \begin{center}
-\includegraphics[width=\textwidth]{pictures/mic_end.png}
+\includegraphics[width=0.82\textwidth]{pictures/mic_end.png}
 \subcaption{Final results}
@@
 \centering
-\begin{minipage}{.45\linewidth}
+\begin{minipage}{.49\linewidth}
 \begin{center}
-\includegraphics[width=\textwidth]{pictures/cumulativeReturnsPerCandleC.png}
+\includegraphics[width=0.82\textwidth]{pictures/cumulativeReturnsPerCandleC.png}
 \subcaption{Results in 3D}
@@
 \end{minipage}
-\begin{minipage}{.45\linewidth}
+\begin{minipage}{.49\linewidth}
 \begin{center}
-\includegraphics[width=\textwidth]{pictures/mic_percandle_end.png}
+\includegraphics[width=0.82\textwidth]{pictures/mic_percandle_end.png}
 \subcaption{Final results}
@@
 \caption{Final profits and Calmar ratio for the selected length of the test period for TewiMiC}
-\scriptsize
+\tiny
 \label{table1}
@@
  \hline size & profit & profit per canlde & Calmar & Open positions & Percentage [\%]\\ \hline  
-10 & -0.0192 & -0.0019 & -0.728 & 34 & 10.97 \\ 
- 20 & 0.0415 & 0.0021 & 2.1594 & 66 & 10.65 \\ 
+%10 & -0.0192 & -0.0019 & -0.728 & 34 & 10.97 \\ 
+ %20 & 0.0415 & 0.0021 & 2.1594 & 66 & 10.65 \\ 
  30 & 0.0812 & 0.0027 & 2.4182 & 93 & 10 \\ 
@@
  120 & 0.3172 & 0.0026 & 8.6479 & 283 & 7.61 \\ 
- 130 & 0.2854 & 0.0022 & 4.5295 & 304 & 7.54 \\ 
- 140 & 0.2512 & 0.0018 & 4.3911 & 335 & 7.72 \\ 
  150 & 0.2648 & 0.0018 & 4.6295 & 345 & 7.42 \\ 
@@
 
-Results for TewiMiD
-
+\textbf{Results for TewiMiD }\\
 Figures ~\ref{Cum3DMiD} and ~\ref{Cum3DMiDend} on page ~\pageref{Cum3DMiDend} shows the effect of the length of the test period on the profit curve.
@@
 \begin{figure}[h!]
-\begin{minipage}{.45\linewidth}
+\begin{minipage}{.459\linewidth}
 \begin{center}
-\includegraphics[width=\textwidth]{pictures/cumulativeReturnsD.png}
+\includegraphics[width=0.82\textwidth]{pictures/cumulativeReturnsD.png}
 \subcaption{Results in 3D}
@@
 \end{minipage}
-\begin{minipage}{.45\linewidth}
+\begin{minipage}{.49\linewidth}
 \begin{center}
-\includegraphics[width=\textwidth]{pictures/mid_end.png}
+\includegraphics[width=0.82\textwidth]{pictures/mid_end.png}
 \subcaption{Final results}
@@
 \centering
-\begin{minipage}{.45\linewidth}
+\begin{minipage}{.49\linewidth}
 \begin{center}
-\includegraphics[width=\textwidth]{pictures/cumulativeReturnsPerCandleD.png}
+\includegraphics[width=0.82\textwidth]{pictures/cumulativeReturnsPerCandleD.png}
 \subcaption{Results in 3D}
@@
 \end{minipage}
-\begin{minipage}{.45\linewidth}
+\begin{minipage}{.49\linewidth}
 \begin{center}
-\includegraphics[width=\textwidth]{pictures/mid_percandle_end.png}
+\includegraphics[width=0.82\textwidth]{pictures/mid_percandle_end.png}
 \subcaption{Final results}
@@
 \caption{Final profits and Calmar ratio for the selected length of the test period for TewiMiD}
-\scriptsize
+\tiny
 \label{table2}
@@
  \hline size & profit & profit per canlde & Calmar & Open positions & Percentage [\%]\\ \hline  
-10 & 0.0108 & 0.0011 & 2.3305 & 11 & 3.55 \\ 
- 20 & 0.0135 & 0.0007 & 2.4981 & 20 & 3.23 \\ 
+%10 & 0.0108 & 0.0011 & 2.3305 & 11 & 3.55 \\ 
+% 20 & 0.0135 & 0.0007 & 2.4981 & 20 & 3.23 \\ 
  30 & 0.0249 & 0.0008 & 4.2953 & 47 & 5.05 \\ 
@@
  130 & 0.0955 & 0.0007 & 13.1243 & 178 & 4.42 \\ 
- 140 & 0.0998 & 0.0007 & 11.5503 & 188 & 4.33 \\ 
- 150 & 0.0974 & 0.0006 & 9.6789 & 194 & 4.17 \\ 
+% 140 & 0.0998 & 0.0007 & 11.5503 & 188 & 4.33 \\ 
+ %150 & 0.0974 & 0.0006 & 9.6789 & 194 & 4.17 \\ 
  200 & 0.1011 & 0.0005 & 9.464 & 263 & 4.24 \\ 
@@
  \end{table}
- \FloatBarrier
+
 Of course, the optimal convergence test window length, at least approximately, is a great convenience in design of automatic strategy for algotrading.

### 2013-09-29 Article/Article20130912/LatexArt/tewi-paper-template_minipages.tex
Conclusion 2

@@
 Strategies properties discovered during the learning period are effective for a short time - for test data period - good lengths for both strategies are about 50 to 120 hours at 1000 hours of learning time.
-\\
-The real market means that from 2 to 5 days, it can be assumed that the re- learning the parameters of the strategy should be carried out 1-2 times a week.
-This frequency is quite practical even for manual search of optimal parameters without fully automatic trading.
-The options trading strategies ( substrategia TewiMiC and TewiMiD ) are complementary, since for each variant can develop a set of other parameters.
-Separate sets of parameters are adapted better to the outdoor during optimization nature of the market, allowing for example, often contain long positions in the market with more frequent by growth trends.
-It should be noted that a further optimizations discovered trends are short-term and during one cycle of validation can occur several changes in these trends, and they can be of different lengths.
+In the real market means that from 2 to 5 days, it can be assumed that the re- learning the parameters of the strategy should be carried out 1-2 times a week.
+This frequency is quite practical even for manual search of optimal parameters without fully automatic trading.\\
+
+Presented trading strategies (substrategy TewiMiC and TewiMiD) are complementary, since each variant can develop a set of different parameters.
+Separate sets of parameters are adapted better to the nature of the market during optimization.
+It allows for example to trade long positions in the markets with more frequent upward trends.
+It should be noted that a further optimizations discovered trends are short-term and during one cycle of validation several changes in these trends can occur.
+These changes could be of different lengths.
 Then there is the situation that one of the variants of the strategy takes into account the length of trends for deviating significantly from trends indicated by the second variant.
-The two variants substrategii are part of an investment strategy that allows you to combine the target until the time the four options trading strategies.
-It is a fact of this study add to the substrategie associated with opening long positions based on condition ( order ) Buy Stop and short positions in accordance with the model Sell Limit.
-Interestingly according to the authors, may also improve the combined strategies through the synthesis of recommendations such as combining four variants, some of which (eg 3 ) indicates the need for the purchase, and some ( such as 1 ) the need to conclude the sale of stock, it contains a number of transactions indications resulting from the sum of the different options ( in the above example - two requests).
-This implies a lower cost ( for example, 2 times smaller ).
-Transaction costs for certain decisions so tests can be omitted, and the reduction significantly affects the efficiency improvement investment strategy.
+The two strategy variants are part of an investment strategy that allows you to combine the four options of trading strategies.
+You can join the strategies presented with the strategies associated with the opening of long positions based on condition (order) Buy Stop and short positions in accordance with the model Sell Limit.
+It is a fact of this study add to the strategies associated with opening long positions based on condition for Buy Stop order and short positions in accordance with the Sell Limit model.
+Interesting, according to the authors, may also be improving the combined strategies through the synthesis of recommendations such as combining four variants, some of which (eg 3) indicates the need for the purchase, and some (such as 1) the need to conclude the sale of stock, it contains a number of transactions indications resulting from the sum of the different options (in the above example - two requests).
+This implies a lower cost (for example, 2 times smaller).
+Transaction costs for certain decisions tests can be omitted, and this reduction significantly affects the efficiency improvement investment strategy.
 The studies take into account the transaction costs for the pessimistic (above average costs in popular brokers).
 In practical terms, the strategy is so big possibilities.
-With traditional software, e-commerce (such as Metatrader) does not have the possibility of converting a simple strategy parameters during operation.
-This implies the need for a hybrid solution, consisting for example of interprocess communication between the software and e-commerce program developed in universal high-level language (eg Matlab, C\#).
-Algotarding future will very likely be increasingly active domain for experts in algorithmization and programming and less and less economists and econometricians.\\
+With traditional software, trading programs (such as Metatrader) does not have the possibility of converting a simple strategy parameters during operation.
+This implies the need for a hybrid solution, consisting for example of interprocess communication between the trading software and program developed in universal high-level language (eg Matlab, C\#).
+Algotarding future will very likely be increasingly active domain for experts in algorithmization and programming and less and less for economists and econometricians.\\
 

### 2013-09-29 Article/Article20130912/LatexArt/tewi-paper-template_minipages.tex
Fixes in text

@@
 The main aim of the research was to obtain the most effective investment strategies by dynamic selection of test period duration.
-Later in this article were used concepts of learning period, a fixed-length 1000 candles but with different start in time.
-After this were test period, a variable-length immediately following a period of learning.
-The authors looks for the best (by the criteria described above) length of the test period in their research.
+Later in this article concepts of learning period, a fixed-length 1000 candles but with diffeerent start in
+time were used.
+Immediately after period of learing there was a variable-length test period.
+The authors look for the best (by the criteria described above) length of the test period in their research.
 This most preferred length of the learning period can be understood in two ways.
@@
 Figure ~\ref{research_methods} on page ~\pageref{research_methods} shows how the research was conducted.
-Knowing the historical data 1000 candles were used and approach described above in order to find optimal parameters for a given period was used for this dataset.
+Having historical data for 1000 candles, optimal parameters, for said data, have been found using approach described above.
 After the parameters search, tests were performed on the current data.
@@
 When results were no longer good enough, the next parameters search were performed on next piece of historical data.
-Thus, the authors aim is to determine the point where it should parameters be recalculated.
+Thus, the authors aim is to determine the point where those parameters should be recalculated.
 Additionally, the authors set out to test a new standard of quality prediction.
@@
 
-Figures ~\ref{MiC100} and ~\ref{MiD100} on page ~\pageref{MiD100} shows the cumulative profit for the test period equal to 100 candles (hours) for the two examined strategies.
+Figures ~\ref{MiC100} and ~\ref{MiD100} on page ~\pageref{MiD100} show the cumulative profit for the test period equal to 100 candles (hours) for the two examined strategies.
 
@@
 
-\caption{Chart of the profit for the strategy with fixed test period size - 100 candles}
+\caption{Charts of the profit for both strategies with fixed test period size - 100 candles}
 \end{figure}
@@
 
-It may be noted that the two policies, for the test period of 100, allow for systematic profit in examined period with only for small drawndowns.
+It may be noted that the two policies, for the test period of 100, allow for systematic profit in examined period with only small drawndowns.
 Profit for the strategy TewiMiC 0.355, for TewiMiD profit is several times smaller and amounts to 0.094.
@@
 Below, we present four graphs showing the results of the strategy TewiMiC.
-The first of these (Figure \ref{Cum3DMiC} on page \pageref{Cum3DMiC}) shows the effect of test duration on the profit curve in time.
+First (Figure \ref{Cum3DMiC} on page \pageref{Cum3DMiC}) shows the effect of test duration on the profit curve in time.
 To show how long in the test period optimal results are achieved we plotted 2D chart of final profit for each of the examined sizes.
@@
 
-Due to the different length of the test period studied, more reliable value required in the decision is earnings per candle, what means how much strategy can earn in one hour.
+Due to the different lengths of studied test periods, more reliable value required in the decision is earnings per candle, what means how much strategy can earn in one hour.
 This is shown in Figures \ref{Cum3DPerCMiC} and \ref{Cum3DPerCMiCend}.
@@
 Many times in the classification of patterns, it is important whether patterns are frequent.
-Part of the dilemma is solved by introducing earnings per candle but also in Table.
-\ref{table1} a count of opened market positions in the testing periods are presented.\\
+Part of the dilemma is solved by introducing earnings per candle but also in Table \ref{table1} a count of opened market positions in the testing periods are presented.\\
 
@@
 \textbf{Results for TewiMiD }\\
-Figures ~\ref{Cum3DMiD} and ~\ref{Cum3DMiDend} on page ~\pageref{Cum3DMiDend} shows the effect of the length of the test period on the profit curve.
+Figures ~\ref{Cum3DMiD} and ~\ref{Cum3DMiDend} on page ~\pageref{Cum3DMiDend} show impact of the length of the test period on the profit curve.
 In case of TewiMiD strategy it is difficult to determine the optimal interval length of the testing period.

### 2013-09-29 Article/Article20130912/LatexArt/tewi-paper-template_minipages.tex
Fixes in text - conclusion

@@
 
-Following a review of various lengths dependence validation periods shown in Figures \ref{Cum3DMiDend} and \ref{Cum3DMiDend} were obtained.
+Following a review of various lengths dependence validation periods shown in Figures \ref{Cum3DMiCend} and \ref{Cum3DMiDend} were obtained.
 It shows a fairly obvious that a good fit of the parameters of the test period will continue for some time after the end of the learning.
@@
 The authors have found that the use of optimization methods derived from the area of artificial intelligence, including the PSO \cite{Kennedy}, given good and quickly reached the optimum values of the rules of the classifier, and good results in the initial stages of the test period.
-For longer test periods, it can be indeed get good results overall, however, the effectiveness of the strategy per hour decreases significantly.
+For longer test periods, it can indeed get good results, however, the effectiveness of the strategy per hour decreases significantly.
 Obtained results allow to conclude that the constant average length of the test window is more efficient and easier to manage than a strategy adaptively changing the length of the period.
@@
 It allows for example to trade long positions in the markets with more frequent upward trends.
-It should be noted that a further optimizations discovered trends are short-term and during one cycle of validation several changes in these trends can occur.
+It should be noted that a further optimizations discovered trends that are short-term and during one cycle of validation several changes in these trends can occur.
 These changes could be of different lengths.
@@
 The studies take into account the transaction costs for the pessimistic (above average costs in popular brokers).
-In practical terms, the strategy is so big possibilities.
+In practical terms, the strategy has big potential.
 With traditional software, trading programs (such as Metatrader) does not have the possibility of converting a simple strategy parameters during operation.

### 2013-09-29 Article/Article20130912/LatexArt/tewi-paper-template_minipages.tex
fixed acknowledgement
changed - wrong line brake

@@
 \ref{timeSeries}).
-It is the time series, consisting of 4734 1-hour candles, of the most important and the most fluent currency pair EURUSD from 22.10.2012.
+It is the time series, consisting of 4734  \mbox{1-hour } candles, of the most important and the most fluent currency pair EURUSD from 22.10.2012.
 \begin{figure}[h!]
@@
 
-\noindent Acknowledgment: Work done within the project TEWI financed from the Operational Programme of Innovative Economy in years 2012-2013.
+\noindent Acknowledgment: Work done within the project TEWI financed from the Innovative Economy Programme in years 2012-2013.
 

### 2013-09-29 Matlabs/Indicators/AB/ROC_AB.tex
Indicator: tex version

\documentclass[12pt,a4paper]{article}
\usepackage{polski}
\usepackage[utf8]{inputenc}
\usepackage{amsmath}
\usepackage{amssymb}
\usepackage{amsfonts}
\usepackage{graphicx}
\usepackage{placeins}
\usepackage{listings}
\usepackage[svgnames]{xcolor}
 \lstset{literate={ą}{{\k{a}}}1 {ć}{{\'c}}1 {ę}{{\k{e}}}1 {ł}{{\l{}}}1 {ń}{{\'n}}1 {ó}{{\'o}}1 {ś}{{\'s}}1 {ż}{{\.z}}1 {ź}{{\'z}}1 {Ą}{{\k{A}}}1 {Ć}{{\'C}}1 {Ę}{{\k{E}}}1 {Ł}{{\L{}}}1 {Ń}{{\'N}}1 {Ó}{{\'O}}1 {Ś}{{\'S}}1 {Ż}{{\.Z}}1 {Ź}{{\'Z}}1 }
 \lstset{breaklines=true}
\lstset{language=Matlab,
  keywords={break,case,catch,continue,else,elseif,end,for,function,
     global,if,otherwise,persistent,return,switch,try,while},
  basicstyle=\ttfamily,
  keywordstyle=\color{blue},
  commentstyle=\color{DarkGreen},
  stringstyle=\color{dkgreen},
  numbers=left,
  numberstyle=\tiny\color{gray},
  stepnumber=1,
  numbersep=10pt,
  backgroundcolor=\color{white},
  tabsize=4,
  showspaces=false,
  showstringspaces=false}

\begin {document}
\begin{center}
\begin{large}
ROC --- opis wskaźnika Rate Of Change\\
\end{large}
Aneta Bera
\end{center}
%\baselineskip=22pt

Rate Of Change, nazywany po polsku wskaźnikiem zmian, jest to wskaźnikiem który
mierzy procentową zmianę pomiędzy najnowszą ceną
zamknięcia a ceną $k$ okresów wcześniej. Sposób wyliczenia wartości wskaźnika ROC dla danego punktu w czasie przedstawiają wzory \ref{wzor_1} oraz \ref{wzor_2}.
\begin{equation}
ROC(\text{dziś}) = \frac{\text{Cena zamknięcia dziś} - \text{Cena zamknięcia } k \text{ okresów temu}}{\text{Cena zamknięcia } k \text{ okresów temu}}\\
\label{wzor_1}
\end{equation}
\begin{equation}
ROC(i) = \frac{C(i,4) - C(i-k,4)}{C(i-k,4)}
\label{wzor_2}
\end{equation}

\noindent Do podstawowych własności krzywej ROC należą:
\begin{itemize}
\item obrazuje ona jak zmieniała się cena obserwowanego rynku w danym okresie,
\item jeśli wartość oscylatora znajduje się poniżej zera, to obecna cena jest wyższa od tej sprzed $k$-godzin temu, analogicznie gdy oscylator znajduje się powyżej zera, oznacza to, że obecna cena jest niższa od tej sprzed $k$-godzin temu,
\item wzrastająca linia wskaźnika pokazuje, że różnice między
obecnym poziomem ceny a tym $k$ -czas temu się
zwiększają, malejąca mówi natomiast, że różnica ta się zmniejsza,
\item jeśli ceny akcji będą rosły to można oczekiwać, że linia
oscylatora będzie zachowywać się analogicznie, jeśli ceny będą natomiast malały to linia oscylatora powinna maleć.
\end{itemize}
Najważniejszą własnością opisywanego wskaźnika, stosowaną przy implementacjach strategii, jest fakt wskazywania momentów w których powinny zostać zawarte transakcje. Gdy wartość wskaźnika przetnie od dołu poziom zero to zakłada się, że jest to dobry moment kupna, jeśli przetnie poziom zera od góry to sprzedaży. Zostało to przedstawione na rysunku \ref{kupsprz}. \\
\begin{figure}[h!]
\centering
\includegraphics[width = \textwidth]{BuySell.png}
\caption{Fragment przykładowej krzywej ROC wraz z sygnałami kupna --- zielone strzałki oraz sygnałami sprzedaży --- czerwone strzałki}
\label{kupsprz}
\end{figure}
\FloatBarrier

\noindent Poniższy listing przedstawia zaimplementowaną strategię w środowisku MATLAB.
\begin{scriptsize}
\begin{lstlisting}
pocz = k+2;	
kon = size(C,1)-1;
iL = 0; % przekroczenie 0 w górę - kupno (L)
iS = 0; % przekroczenie 0 w dół - sprzedaż (S)
sumR = zeros(1,size(C,1));
R = zeros(1,size(C,1));
ROC_vec = zeros(1,kon-k+1);
ROC_vec(pocz-1) = ((C(pocz-1,4) - C(pocz-1-k,4))/C(pocz-1-k,4))*100;

recordReturn = 0;  % rekord zysku
recordDrawdown = 0;  % rekord obsuniecia
LastPos = 0;    % zmienna do przechowywania wartości na otwarciu ostatniej pozycji

for i=pocz:kon
    ROC_vec(i) = ((C(i,4) - C(i-k,4))/C(i-k,4))*100;  % obliczenie punktu krzywej ROC
    if ROC_vec(i)*ROC_vec(i-1)<=0   % przecięcie krzywej ROC z zerem
        if ROC_vec(i-1)<ROC_vec(i)  % warunek kupna
            if iL+iS>0
                R(i) = -C(i+1,4)+LastPos-spread;   % zamknięcie S
            end
            LastPos = C(i+1,1);   % otworzenie L
            iL = iL + 1;
        elseif ROC_vec(i-1)>ROC_vec(i)  % warunek sprzedaży
            if iL+iS>0
                R(i) = C(i+1,4)-LastPos-spread;  % zamknięcie L
            end
            LastPos = C(i+1,1);   % otworzenie S
            iS = iS + 1;
        end
    end
    sumR(i) = sum(R(pocz:i));

    if sumR(i)>recordReturn
        recordReturn=sumR(i);
    end

    if sumR(i)-recordReturn<recordDrawdown
        recordDrawdown=sumR(i)-recordReturn;  
    end

end

Calmar=-sumR(kon)/recordDrawdown;
profit = sumR(kon);

end
\end{lstlisting}
\end{scriptsize}

Na podstawie zebranych informacji dotyczących wskaźnika $ROC$ utworzono prostą strategię inwestycyjną bazującą na regule: jeśli linia $ROC$ przetnie się z poziomem zera od dołu, to otwierana jest pozycja długa ($L$), a zamykana pozycja krótka ($S$), która została wcześniej otwarta. Gdy natomiast nastąpi przecięcie linii $ROC$ z poziomem zera od góry to otwarta zostanie pozycja krótka, a zamknięta długa. Badania zostały przeprowadzone na parze walutowej $EURJPY$ (szereg czasowy przedstawiony na rysunku \ref{rysunek2}). \\
\begin{figure}[h!]
\centering
\includegraphics[width = \textwidth]{podzialDanych.png}
\caption{Badany szereg czasowy z podziałem na część uczącą i testową}
\label{rysunek2}
\end{figure}
\FloatBarrier
Cały zbiór danych (świec) podzielony został na dwie części: uczącą ($60\%$ całości) oraz testową ($40\%$ całości). W przeprowadzonych badaniach poszukiwano optymalnej wartości parametru $k$ na okresie uczącym, następnie weryfikowano otrzymane wyniki na okresie testowym. Wybór optymalnej wartości parametru $k$ determinowano na dwa sposoby:
\begin{itemize}
\item otrzymanego zysku skumulowanego,
\item wskaźnika Calamara.
\end{itemize}

\noindent \textbf{I Wyniki badań przy maksymalizacji po zysku.}\\
\begin{figure}[h!]
\centering
\includegraphics[width = 0.6\textwidth]{ROC_EURJPY_LS_SearchBestK_zysk.png}
\caption{Zysk skumulowany EURJPY na okresie testowym przy maksymalizacji według zysku}
\end{figure}
\FloatBarrier
\begin{verbatim}
OKRES UCZĄCY
Długość cyklu: 	89
Zysk skumulowany: 	16.81
Calmar: 	2.66
Liczba otwartych pozycji długich: 	100
Liczba otwartych pozycji krótkich: 	100

OKRES WALIDUJĄCY
Długość cyklu: 	89
Zysk skumulowany: 	11.87
Calmar: 	1.00
Liczba otwartych pozycji długich: 	61
Liczba otwartych pozycji krótkich: 	61
\end{verbatim}
\newpage
\textbf{II Wyniki badań przy maksymalizacji po wskaźniku Calmara.}\\
\begin{figure}[h!]
\centering
\includegraphics[width = 0.6\textwidth]{ROC_EURJPY_LS_SearchBestKCalmar_zysk.png}
\caption{Zysk skumulowany EURJPY na okresie testowym przy maksymalizacji według Calmara}
\end{figure}
\FloatBarrier
\begin{verbatim}
OKRES UCZĄCY
Długość cyklu: 	230
Zysk skumulowany: 	12.82
Calmar: 	3.83
Liczba otwartych pozycji długich: 	52
Liczba otwartych pozycji krótkich: 	51

OKRES TESTUJĄCY
Długość cyklu: 	230
Zysk skumulowany: 	20.64
Calmar: 	5.08
Liczba otwartych pozycji długich: 	28
Liczba otwartych pozycji krótkich: 	29
\end{verbatim}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\end {document}

### 2013-10-01 Matlabs/PSO/start.m
Particle Swarm Optimization for TewiMiD (easily can be changed to MiA, MiB or MiC (you must add one more parameter - mic)

@@ -1,0 +1,54 @@
+function [] = start(nr_testu)
+
+
+% nr_testu = 33;
+
+eurusd221012;
+file_name = ['tewiMiCD' num2str(nr_testu) 'ab'];
+spread = 0.0002;
+
+pocz=(nr_testu-1)*100;
+kon=pocz+1000;
+poczt=pocz+1000;
+kon1=poczt+100;
+kon2=poczt+200;
+kon5=poczt+500;
+
+
+opcje = PSODefaultOptions(spread);
+timeout = 1;
+% definicje funkcji
+if(timeout)
+    opcje.best_position_timeout = 100;
+end
+
+
+% PSO
+[roj, ~, l_op, zysk] = PSO(opcje,C,pocz,kon,spread);
+
+temp_p = roj.best_position;
+
+% zapis optymalnych parametrów
+fileID =fopen([file_name 'opt_param.txt'],'w');
+fprintf(fileID, '%i\t %i-%i', nr_testu, pocz, kon);
+fprintf(fileID, '\t%0.5f\t%0.2f\t%0.2f\t%0.2f', temp_p(1), temp_p(2),temp_p(3),temp_p(4));
+fprintf(fileID, '\t%0.5f\t%0.5f\t%0.2f', temp_p(5), temp_p(6),temp_p(7));
+fprintf(fileID, '\t%0.2f\t%0.2f\t%0.5f\t%0.5f', temp_p(8), temp_p(9),temp_p(10),temp_p(11));
+fclose(fileID);
+
+[zysk roj.best_position_value]
+
+[ zysk100, Ca100, l100] = tewiMiD( C, spread, poczt, kon1, ...
+    temp_p(1), temp_p(2), temp_p(3), temp_p(4), temp_p(5),...
+    temp_p(6), temp_p(7), temp_p(8), temp_p(9), temp_p(10),...
+    temp_p(11));
+
+
+[zysk100]
+
+% zapis do pliku
+fileID =fopen([file_name '.txt'],'w');
+fprintf(fileID, '%i\t %i-%i', nr_testu, pocz, kon);
+fprintf(fileID, '\t%0.4f\t%0.4f', zysk, roj.best_position_value);
+fprintf(fileID, '\t%i\t%0.4f', l_op, zysk100); 
+fclose(fileID);

### 2013-10-03 Matlabs/Indicators/MZ/MZ_TEX/Indicators_MZ.tex
MZ - charakterystyka wskaźników w LaTeX

\documentclass[12pt,a4paper]{article}
\usepackage[MeX]{polski}
\usepackage[utf8]{inputenc}
\usepackage{amsmath}
\usepackage{amssymb}
\usepackage{amsfonts}
\usepackage{graphicx}
\usepackage{placeins}
\usepackage{listings}
\usepackage[svgnames]{xcolor}
 \lstset{literate={ą}{{\k{a}}}1 {ć}{{\'c}}1 {ę}{{\k{e}}}1 {ł}{{\l{}}}1 {ń}{{\'n}}1 {ó}{{\'o}}1 {ś}{{\'s}}1 {ż}{{\.z}}1 {ź}{{\'z}}1 {Ą}{{\k{A}}}1 {Ć}{{\'C}}1 {Ę}{{\k{E}}}1 {Ł}{{\L{}}}1 {Ń}{{\'N}}1 {Ó}{{\'O}}1 {Ś}{{\'S}}1 {Ż}{{\.Z}}1 {Ź}{{\'Z}}1 }
 \lstset{breaklines=true}
\lstset{language=Matlab,
  keywords={break,case,catch,continue,else,elseif,end,for,function,
     global,if,otherwise,persistent,return,switch,try,while},
  basicstyle=\ttfamily,
  keywordstyle=\color{blue},
  commentstyle=\color{DarkGreen},
  stringstyle=\color{dkgreen},
  numbers=left,
  numberstyle=\tiny\color{gray},
  stepnumber=1,
  numbersep=10pt,
  backgroundcolor=\color{white},
  tabsize=4,
  showspaces=false,
  showstringspaces=false}

\begin {document}
\begin{center}
\begin{large}
Stochastic Slow - oscylator stochastyczny wolny : opis wskaźnika\\
\end{large}
Michał Zabłocki
\end{center}
%\baselineskip=22pt

Stochastic Slow jest wolniejszą wersja podstawowego oscylatora stochastycznego. Składa się z dwóch linii oscylacyjnych: głównej linii oscylatora tzw. \%K oraz pomocniczej wygładzonej postaci tej linii tzw. \%D. Obie linie osiągają wartości z przedziału 0 - 100.  Sposób wyliczenia kolejnych wartości obu linii dla danego punktu w czasie przedstawiają wzory \ref{wzor_1} oraz \ref{wzor_2}.
\begin{equation}
\%K = \left[\begin{array}{c} \frac{ \sum_{j=0}^{2} (C_j - min(L_j, n))}{ \sum_{j=0}^{2} (max(H_j, n) - min(L_j, n))}\end{array}\right]\\
\label{wzor_1}
\end{equation}
\begin{equation}
\%D = SMA(\%K, 3)
\label{wzor_2}
\end{equation}

\noindent Dodatkowo mogą być poszukiwane dywergencje względem wykresu cenowego. Możliwe jest też poszukiwanie tzw. odwróconych dywergencji. W tej wersji wskaźnik może być używany jako miernik wykupienia / wyprzedania rynku. Wadą wskaźnika jest to, że w mocnych ruchach trendowych skrajne stany rynku mogą być sygnalizowane przedwcześnie.
Przy interpretacji wskaźnika najważniejszy jednak jest fakt, że wskazuje on momenty w których mogą być zawierane transakcje. Podstawowa zasada zakłada przyjęcie jako sygnału kupna sytuację gdy występują przecięcia linii \%D przez linię \%K od dołu. Natomiast, gdy linia \%D jest przecinana przez linię \%K od góry, to przyjmuje się taką sytuację za sygnał sprzedaży. Zostało to przedstawione na rysunku \ref{zasada}. \\
\begin{figure}[h!]
\centering
\includegraphics[width = \textwidth]{ss.png}
\caption{Fragment przebiegu kursu akcji (górny wykres) oraz odpowiadające jemu linie \%K i \%D wraz z sygnałami kupna --- błękitne strzałki oraz sygnałami sprzedaży --- pomarańczowe strzałki (dolny wykres)}
\label{zasada}
\end{figure}
\FloatBarrier

\noindent Poniższy listing przedstawia zaimplementowaną w środowisku MATLAB strategię wykorzystującą opisywany wskaźnik.
\begin{scriptsize}
\begin{lstlisting}
maxes=zeros(candlesCount,1);
mins=zeros(candlesCount,1);
K=zeros(candlesCount,1);
D=zeros(candlesCount,1);
kon=candlesCount-1;
for i=4:kon
    maxes(i) = max(verificationC(i-min(i-1,paramMALength):i-1,2));
    mins(i) = min(verificationC(i-min(i-1,paramMALength):i-1,3));
    K(i) = 100 * (sum(verificationC(i-min(i-1,3):i-1,4)-mins(i-min(i-1,2):i)) / sum(maxes(i-min(i-1,2):i)-mins(i-min(i-1,2):i)));
    D(i) = sum(K(i-min(i-1,2):i)) / min(i-1,3);
end

sumR=zeros(1,candlesCount);
R=zeros(1,candlesCount);
pocz=max(paramMALength, 10)+3;
iL=0; %liczba otwieranych pozycji kupna
iS=0; %liczba otwieranych pozycji sprzedarzy
lastCandle = kon-paramMALength;
recordReturn=0;  %rekord zysku
recordDrawdown=0;  %rekord obsuniecia
LastPos = 0; % zmienna do prz echowywa nia warto ś ci na otwarciu ostatniej pozycji
for i=pocz:lastCandle

    if K(i-1) < D(i-1) && K(i) >= D(i) % warunek kupna
        R(i)= - C(i+1,4)+LastPos-spread; % zamknięcie S
        LastPos = C(i+1,1); % otwarcie L
        iL=iL+1;
    elseif K(i-1) > D(i-1) && K(i) <= D(i) % warunek sprzedaż y
        R(i)=C(i+1,4)-LastPos-spread; % zamknięcie L
        LastPos = C(i+1,1); % otwarcie S
        iS=iS+1;
    end
    sumR(i)= sum(R(pocz:i));  %krzywa narastania kapitału

    if sumR(i)>recordReturn
        recordReturn=sumR(i);
    end

    if sumR(i)-recordReturn<recordDrawdown
        recordDrawdown=sumR(i)-recordReturn;  %obsuniecie maksymalne
    end
end

%wyniki końcowe
sumReturn=sumR(lastCandle);
Calmar=-sumReturn/recordDrawdown;  %wskaznik Calmara
\end{lstlisting}
\end{scriptsize}

Na podstawie zebranych informacji dotyczących wskaźnika $Stochastic Slow$ utworzono prostą strategię inwestycyjną bazującą na regule: jeśli linia $\%D$ jest przecinana przez  linię $\%K$ od dołu, to otwierana jest pozycja długa ($L$), a zamykana pozycja krótka ($S$), która została wcześniej otwarta. Natomiast gdy linia \%D jest przecinana przez linię \%K od góry, to otwarta zostanie pozycja krótka, a zamknięta długa. Badania zostały przeprowadzone na parze walutowej $CADCHF$ (szereg czasowy przedstawiony na rysunku \ref{rys2}). \\
\begin{figure}[h!]
\centering
\includegraphics[width = \textwidth]{szereg.png}
\caption{Badany szereg czasowy z podziałem na część uczącą i testową}
\label{rys2}
\end{figure}
\FloatBarrier
Cały zbiór danych (świec) podzielony został na dwie części: uczącą ($60\%$ całości) oraz testową ($40\%$ całości). W przeprowadzonych badaniach poszukiwano optymalnej wartości parametru $n$ na okresie uczącym, następnie weryfikowano otrzymane wyniki na okresie testowym. Wybór optymalnej wartości parametru $n$ determinowano na dwa sposoby:
\begin{itemize}
\item otrzymanego zysku skumulowanego,
\item wskaźnika Calamara.
\end{itemize}

\noindent \textbf{I Wyniki badań przy maksymalizacji po zysku.}\\
\begin{figure}[h!]
\centering
\includegraphics[width = 0.6\textwidth]{SS_CADCHF_S4LS_zysk.png}
\caption{Zysk skumulowany CADCHF na okresie testowym przy maksymalizacji według zysku}
\end{figure}
\FloatBarrier
\begin{verbatim}
OKRES UCZĄCY
Zysk skumulowany:     0.2917
Calmar:     0.4538
Liczba otwartych pozycji długich:     400
Liczba otwartych pozycji krótkich:     405

OKRES WALIDUJĄCY
Zysk skumulowany:     -1.3244
Calmar:     -1
Liczba otwartych pozycji długich:     244
Liczba otwartych pozycji krótkich:     245
\end{verbatim}
\newpage
\textbf{II Wyniki badań przy maksymalizacji po wskaźniku Calmara.}\\
\begin{figure}[h!]
\centering
\includegraphics[width = 0.6\textwidth]{SS_CADCHF_S4LS_calmar.png}
\caption{Zysk skumulowany EURJPY na okresie testowym przy maksymalizacji według Calmara}
\end{figure}
\FloatBarrier
\begin{verbatim}
OKRES UCZĄCY
Zysk skumulowany:     0.2917
Calmar:     0.4538
Liczba otwartych pozycji długich:     400
Liczba otwartych pozycji krótkich:     405

OKRES WALIDUJĄCY
Zysk skumulowany:     -1.3244
Calmar:     -1
Liczba otwartych pozycji długich:     244
Liczba otwartych pozycji krótkich:     245
\end{verbatim}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\newpage
\begin{center}
\begin{large}
Mass Index - indeks masy : opis wskaźnika\\
\end{large}
\end{center}
%\baselineskip=22pt

Mass Index wskaźnik jest pomocny w identyfikacji punktów zwrotnych, poprzez mierzenie odległości pomiędzy cenami maksymalnymi a minimalnymi. Według autora zmiana kierunku trendu następuje w momencie zaobserwowania tzw. wybrzuszenia zwrotnego, czyli wejścia wskaźnika ponad poziom 27 i następnie spadku poniżej 26,5. Wskaźnik nie identyfikuje jednak kierunku trendu, ustala jedynie punkt zwrotny. Sposób wyliczenia kolejnych wartości wskaźnika dla danego punktu w czasie przedstawia wzór \ref{wzor_3}.
\begin{equation}
Mass Index = \sum_{0}^{24} \left[\begin{array}{c} \frac{ EMA(H - L, 9)}{ EMA(EMA(H-L, 9), 9)}\end{array}\right]\\
\label{wzor_3}
\end{equation}

\noindent Sama interpretacja wskaźnika nie pozwala na wskazanie momentów w których mogą być zawierane konkretne transakcje (kopno/sprzedarz). W określeniu czy jest to sygnał kupna czy sprzedaży autor zaleca stosowanie 9- dniowej ekspotencjalnej średniej na wykresie notowań. Dlatego przyjeliśmy zasadę, która zakłada, że po wystąpieniu wybrzuszenia zwrotnego przyjmujemy jako sygnał kupna sytuację gdy wartość ceny zamknięcia przewyższa wartość 9- dniowej ekspotencjalnej średniej. Natomiast, gdy wartość ceny zamknięcia jest mniejsza od wartość 9- dniowej ekspotencjalnej średniej, to przyjmuje się taką sytuację za sygnał sprzedaży. Zostało to przedstawione na rysunku \ref{kupsprz2}. \\
\begin{figure}[h!]
\centering
\includegraphics[width = \textwidth]{mi2.png}
\caption{Fragment przebiegu kursu akcji z naniesioną  9- dniową ekspotencjalną średnią (górny wykres) oraz odpowiadające jemu wartości wskaźnika indeksu masy wraz z sygnałami kupna --- zielone strzałki oraz sygnałami sprzedaży --- czerwone strzałki (dolny wykres)}
\label{kupsprz2}
\end{figure}
\FloatBarrier

\noindent Poniższy listing przedstawia zaimplementowaną w środowisku MATLAB strategię wykorzystującą opisywany wskaźnik.
\begin{scriptsize}
\begin{lstlisting}
bestiL = 0;
bestiS = 0;
HL = C(:,2) - C(:,3); % różnica H - L
kon=candlesCount-1;
MI = zeros(candlesCount,1);
HLaverage = ema(HL,9);
EMA2 = HLaverage(9:end) ./ ema(HLaverage(9:end),9);
for i = 41:kon-16
    MI(i) = sum(EMA2(i-24:i));
end
Caverages = ema(C(:,4),9);

sumR=zeros(1,candlesCount);
R=zeros(1,candlesCount);
pocz=50;
iL=0; %liczba otwieranych pozycji kupna
iS=0; %liczba otwieranych pozycji sprzedarzy
lastCandle = kon-16;
recordReturn=0;  %rekord zysku
recordDrawdown=0;  %rekord obsuniecia
LastPos = 0;
pic1 = false;

for i=pocz:lastCandle

    if pic1 == false && MI(i) > 27 % warunek wystąpienia wybrzuszenia zwrotnego
        pic1 = true;
    end
    if pic1 == true && MI(i) < 26.5 % warunek zawarcia transakcji
        if C(i,4) > Caverages(i) % warunek kupna
            R(i)= -C(i+1,4)-LastPos-spread; % zamknięcie S
            LastPos = C(i+1,1); % otwarcie L
            iL=iL+1;
        elseif C(i,4) < Caverages(i) % warunek sprzedaży
            R(i)=C(i+1,4)-LastPos-spread; % zamknięcie L
            LastPos = C(i+1,1); % otwarcie S
            iS=iS+1;
        end
        pic1 = false;
    end
    sumR(i)= sum(R(pocz:i));  %krzywa narastania kapitału

    if sumR(i)>recordReturn
        recordReturn=sumR(i);
    end

    if sumR(i)-recordReturn<recordDrawdown
        recordDrawdown=sumR(i)-recordReturn;  %obsuniecie maksymalne
    end
end

%wyniki końcowe
sumReturn=sumR(lastCandle);
Calmar=-sumReturn/recordDrawdown;  %wskaznik Calmara
\end{lstlisting}
\end{scriptsize}

Na podstawie zebranych informacji dotyczących wskaźnika $Mass Index$ utworzono prostą strategię inwestycyjną bazującą na regule: jeśli wystąpi wybrzuszenie zwrotne oraz wartość ceny zamknięcia przewyższy wartość 9- dniowej ekspotencjalnej średniej, to otwierana jest pozycja długa ($L$), a zamknięta pozycja krótka ($S$), która została wcześniej otwarta . Natomiast, gdy wartość ceny zamknięcia będzie mniejsza od wartość 9- dniowej ekspotencjalnej średniej, to otwarta zostanie pozycja krótka ($S$), a zamknięta długa. Badania zostały przeprowadzone na parze walutowej $CADCHF$ (szereg czasowy przedstawiony na rysunku \ref{rys2}). \\

Ze względu na to iż wszystkie parametry wzoru są arbitralnie ustawione, to zbiór danych (świec) nie został podzielony na dwie części: uczącą i testującą ($40\%$ całości). Na całym zbiorze danych weryfikowano skuteczność strategii. \\

\newpage
\noindent \textbf{I Wyniki badań.}\\
\begin{figure}[h!]
\centering
\includegraphics[width = 0.6\textwidth]{MI_CADCHF_S4LS.png}
\caption{Zysk skumulowany CADCHF na okresie testowym przy maksymalizacji według zysku}
\end{figure}
\FloatBarrier
\begin{verbatim}
OKRES WALIDUJĄCY
Zysk skumulowany:     -8.3942
Calmar:     -1
Liczba otwartych pozycji długich:     5
Liczba otwartych pozycji krótkich:     3
\end{verbatim}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\end {document}

### 2013-10-06 Matlabs/Indicators/PB/SimpleStochasticMCC/StochasticA.m
Stochastic with MCC

@@ -1,0 +1,257 @@
+%(C) Piotr B³aszyñski 2013
+%skrypt strategii Stochastic Fast w projekcie TEWI - z dopasowaniem parametrów dla po³owy danych
+
+%parametry:
+% paramALength= 5;%2;
+% paramAEmaLength=4;%10; %liczba swiec wstecz do obliczenia sredniego wolumenu
+% paramABuffer=0.00021;%0.0007;
+% paramAVolThreshold=110;%950; %próg dla sredniego wolumenu
+% paramADuration=8; %liczba kroków wprzód do zamkniecia pozycji
+% paramASL=0.0023;  %Stop Loss
+%paramALength: 127 %
+%paramAEmaLength: 17 paramABuffer: 0 
+%paramAVolThreshold: 100 paramADuration: 30 paramASL: 0.01456 Calmar: 2.0615
+%Dane:
+
+tStart=tic;
+
+confusionMatrix.TP=0;
+confusionMatrix.FP=0;
+confusionMatrix.FN=0;
+confusionMatrix.TN=0;
+
+eurusd;
+bestReturn=-100;verificationC=C(4500:end,:); C=C(1:4500,:);
+cSizes = size(C);
+candlesCount = cSizes(1);
+bestCalmar = 0;
+bestMa = 0;
+bestparamAEmaLength = 0;
+bestparamADuration = 0;
+bestparamABuffer = 0;
+bestparamAVolThreshold = 0;
+bestparamASL = 0;
+
+spread = 0.00016;
+lastCandle = 0 ;
+
+
+for paramALength=127%105:2:145%liczba swiec wstecz do obliczenia maksimum
+    kValues=zeros(1, candlesCount);
+    kon=candlesCount-1;
+    for i=2:kon %O-1, H-2, L-3, C-4
+        maxValue = max(C(i-min(i-1,paramALength)+1:i,2));
+        minValue = min(C(i-min(i-1,paramALength)+1:i,3));
+        kValues(i)= 100*((C(i,4)-minValue)/(maxValue-minValue));
+    end
+    for paramAEmaLength=17%15:2:60%liczba swiec do wyg³adzania œredniej
+        dValues = ema(kValues, paramAEmaLength);
+        disp(['paramALength ', num2str(paramALength), '  paramAEmaLength ', num2str(paramAEmaLength)]);
+        for paramADuration=6:2:30; %liczba kroków wprzód do zamkniecia pozycji
+            for paramAVolThreshold=100%-100:100:100; %próg dla sredniego wolumenu
[…]

### 2013-10-06 Matlabs/Indicators/PB/SimpleStochasticMCC/calculateMCC.m

@@ -1,0 +1,10 @@
+function [ CM, MCC, P, R ] = calculateMCC( M )
+%calculates MCC Matthews Correlation Coefficient
+%  easy to interpret predictor classification (+1 - perfect predictor, 0 - random, -1 perfectly perverse predictor)
+% CM - confusion matrix,  MCC - Matthews Correlation Coefficient, P - precision, R
+CM = [M.TP M.FP; M.FN M.TN];
+MCC = (M.TP*M.TN-M.FP*M.FN)/sqrt((M.TP+M.FP)*(M.TP+M.FN)*(M.TN+M.FP)*(M.TN+M.FN));
+P=M.TP/(M.TP+M.FP);
+R=M.TP/(M.TP+M.FN);
+end
+

### 2013-10-14 Matlabs/Indicators/PB/StochasticPSO/Long/PSO.m
Stochatic w PSO, Long (A) version

@@ -1,0 +1,113 @@
+function [ swarm, iterNum, best_l_op,best_zysk ] = PSO( options,C,pocz,kon,spread)
+%UNTITLED2 Summary of this function goes here
+%   Detailed explanation goes here
+
+swarm = initSwarm(options);
+iterNum = 0;
+timeOutCounter = 0;
+
+best_l_op = [];
+best_zysk = [];
+SL= 8*spread:spread:48*spread;
+
+%main loop
+while (iterNum < options.max_iter_num) && timeOutCounter < (options.best_position_timeout)
+    disp([num2str(iterNum*100/options.max_iter_num) ' proc']);
+    changed = 0;
+    for c=1:length(swarm.particles)
+        %rP = unifrnd(0,1,[1 size(options.data_limits,1)])';
+        %rS = unifrnd(0,1,[1 size(options.data_limits,1)])';
+        
+        rP = rand(1, size(options.data_limits,1))';
+        rS = rand(1, size(options.data_limits,1))';
+        
+        swarm.particles(c).velocity = swarm.omega .* swarm.particles(c).velocity +...
+            swarm.phi_particle .* rP .* (swarm.particles(c).best_position - swarm.particles(c).position) +...
+            swarm.phi_swarm .* rS .* (swarm.best_position - swarm.particles(c).position);
+        swarm.particles(c).position = swarm.particles(c).position + ...
+            swarm.particles(c).velocity;
+        
+        %insert bounds-control here
+        for i = 1:size(options.data_limits,1)
+            tmp = swarm.particles(c).position(i);
+            test = tmp < options.data_limits(i,1) || tmp > options.data_limits(i,2);
+            if(test)
+                min = options.data_limits(i,1);
+                max = options.data_limits(i,2);
+                pos = min + (max-min).*rand(1,1);
+                swarm.particles(c).position(i) = pos;
+            end
+        end
+        swarm.particles(c).position([1,2,3]) =...
+            round(swarm.particles(c).position([1,2,3]));
+        %swarm.particles(c).position([5,6]) = SL([round(rand(1,2)*40+ones(1,2))]);
+        temp_p = swarm.particles(c).position;
+        [ zysk, Calmar, l_open] = StochasticOneParamSet( C, spread, pocz, kon, ...
+            temp_p(1), temp_p(2), temp_p(3), temp_p(4));
+        
+        if(zysk > swarm.particles(c).best_position_value)
+            swarm.particles(c).best_position = swarm.particles(c).position;
[…]

### 2013-10-14 Matlabs/Indicators/PB/StochasticPSO/Long/PSODefaultOptions.m

@@ -1,0 +1,18 @@
+function [ options ] = PSODefaultOptions(spread)
+    pip = spread/2;
+    field1 = 'omega' ; value1 = 0.75;
+    field2 = 'phi_swarm' ; value2 = 0.65;
+    field3 = 'phi_particle' ; value3 = 0.55;
+    field4 = 'data_limits' ; value4 = [5 300;
+        5 300;
+        5 100;
+        8*spread 78*spread];
+    field5 = 'num_of_particles' ; value5 = 250;
+    field6 = 'velocity_limits' ; value6 = [0.1 0.9; 0.1 0.9;0.1 0.9;0.1 0.9];
+    field8 = 'max_iter_num'; value8 = 200;
+    field9 = 'best_position_timeout'; value9 = Inf;
+
+    options = struct(field1, value1, field2, value2, field3, ...
+        value3, field4, value4, field5, value5, field6, value6,...
+        field8, value8, field9, value9);
+end

### 2013-10-14 Matlabs/Indicators/KB/Stochastic Fast.tex
opisy wskaznikow
plus latex i wykresy potrzebne

\documentclass[12pt,a4paper]{article}
\usepackage{polski}
\usepackage[utf8]{inputenc}
\usepackage{amsmath}
\usepackage{amssymb}
\usepackage{amsfonts}
\usepackage{graphicx}
\usepackage{placeins}
\usepackage{listings}
\usepackage[svgnames]{xcolor}
 \lstset{literate={ą}{{\k{a}}}1 {ć}{{\'c}}1 {ę}{{\k{e}}}1 {ł}{{\l{}}}1 {ń}{{\'n}}1 {ó}{{\'o}}1 {ś}{{\'s}}1 {ż}{{\.z}}1 {ź}{{\'z}}1 {Ą}{{\k{A}}}1 {Ć}{{\'C}}1 {Ę}{{\k{E}}}1 {Ł}{{\L{}}}1 {Ń}{{\'N}}1 {Ó}{{\'O}}1 {Ś}{{\'S}}1 {Ż}{{\.Z}}1 {Ź}{{\'Z}}1 }
 \lstset{breaklines=true}
\lstset{language=Matlab,
  keywords={break,case,catch,continue,else,elseif,end,for,function,
     global,if,otherwise,persistent,return,switch,try,while},
  basicstyle=\ttfamily,
  keywordstyle=\color{blue},
  commentstyle=\color{DarkGreen},
  stringstyle=\color{dkgreen},
  numbers=left,
  numberstyle=\tiny\color{gray},
  stepnumber=1,
  numbersep=10pt,
  backgroundcolor=\color{white},
  tabsize=4,
  showspaces=false,
  showstringspaces=false}

\begin {document}
\begin{center}
\begin{large}
Stochastic Fast --- opis wskaźnika Stochastic Fast\\
\end{large}
Katarzyna Buda
\end{center}
%\baselineskip=22pt

Stochastic Fast - wskaxnik stochastyczny szybki, zaproponowany w latach 50-tych przez George C. Lane. Sposób wyliczenia wartości wskaźnika uwzględniając wartości O,H,C,L, polega na wyliczeniu dwóch linii. \ref{wzor_1} oraz \ref{wzor_2}.
\begin{equation}
ValK=100*[ \frac{C-Min(L;n)}{max(H;n - min(L;n)}]
\label{wzor_1}
\end{equation}
\begin{equation}
ValD=EMA(ValK;3)
\label{wzor_2}
\end{equation}
gdzie:
\begin{itemize}
\newline
\item ValD - jest wygładzoną linią ValK
\item n - ilość dni
\item EMA - Wykładnicza średnia krocząca(Exponential Moving Average)
\end{itemize}

\noindent Do podstawowych własności wskaźnika należą:
\begin{itemize}
\item opokazuje poziom dzisiejszego zamknięcia w stosunku do najniższego oraz najwyższego punktu w badanym okresie
\item porusza się w przedziale od 0-100
\item obliczamy 2 linie oscylatora ValK i ValD (Value K i Value D) uwzględniając, że ValK jest główną linią oscylatora natomiast ValD jest wygładzoną postacią ValK
\end{itemize}
Najważniejszą własnością opisywanego wskaźnika, stosowaną przy implementacjach strategii, jest fakt wskazywania momentów w których powinny zostać zawarte transakcje. 
\begin{itemize}
\item sygnałem kupna jest przecięcie linii ValK ponad ValD
\item sygnałem sprzedaży jest przecięcie linii ValK poniżej ValD.

\end{itemize}
\noindent Poniższy listing przedstawia zaimplementowaną strategię w środowisku MATLAB.
\begin{scriptsize}
\begin{lstlisting}
[a b]=size(C);
roz=(60*a)/100;
roz=round(roz);
paramSectionLearn = C(1:roz,:);

[m,n]=size(paramSectionLearn);

O=paramSectionLearn(:,1);
L=paramSectionLearn(:,3);
H=paramSectionLearn(:,2);
C=paramSectionLearn(:,4);

%Parametry 
spread=0.00016;
bestReturn = -100;
bestMa = 0;
%Część ucząca

countCandleLearn=m;
lastCandleLearn=0;
krok=1;
%Część valid

paramALengthT=0;
countCandleTest=m1;
lastCandleTest=0;
tmp=countCandleLearn-1;
ValK=zeros(1, countCandleLearn);
paramZakrespocz=0;
chwi=1;
for paramALengthL=40 %liczba świec wstecz ( do max)
        chwi=chwi;
        chwi
    paramZakrespocz(chwi)=paramALengthL;
   for i=2:tmp
       max3=max(H(max(i-paramALengthL, 1):i));
       min3=min(L(max(i-paramALengthL, 1):i));
      ValK(i)=100*(C(i)-min3)/(max3-min3);
   end
    ValD=ema(ValK,3);
    sumRa=zeros(1,tmp);
    Ra=zeros(1,tmp);
   lastCandleLearn=tmp;

%-------------obliczanie zysków
    WinReturn=0;
    DownReturn=0;
    CalmarLearn=0;
    BestCalLearn=0;

    for j=2:lastCandleLearn

        if ValK(j)>ValD(j) && ValK(j-1)<=ValD(j)
            Ra(j)=C(j+krok)-O(j+1)-spread ;% zysk z j-tej pozycji long zamykanej na zamknięciu po 1 kroku 
          else if ValK(j)<ValD(j) && ValK(j-1)>=ValD(j) 
            Ra(j)=-C(j+krok)+O(j+1)+spread; 
               end
        end
        sumRa(j)=sumRa(j-1)+Ra(j); %krzywa narastania kapitału

        if sumRa(j)>WinReturn
            WinReturn=sumRa(j);
        end

        DownReturnTmp=sumRa(j)-WinReturn;
        if  DownReturnTmp<DownReturn
            DownReturn= DownReturnTmp;
        end

    end
    chwi=chwi+1;   
sumFinal=sumRa(lastCandleLearn);
CalmarLearn=-sumFinal/DownReturn;

if bestReturn < sumFinal
    bestMa=paramALengthL;
end
end

sumFinal=sumRa(lastCandleLearn);
CalmarLearn=-sumFinal/DownReturn;
\end{lstlisting}
\end{scriptsize}

Na podstawie zebranych informacji dotyczących wskaźnika Stochastic Fast, stworzono powyższy program uwzględniając pozycje sprzedaży i kupna przy określonych przecięciach. Badania przeprowadzono na rynku usdjpy.
\begin{itemize}
\item sygnałem kupna jest przecięcie linii ValK ponad ValD
\item sygnałem sprzedaży jest przecięcie linii ValK poniżej ValD.
\end{itemize}
Podczas badania wskaźnika cały zbiór danych (świec) podzielony został na dwie części: uczącą ($60\%$ całości) oraz testową ($40\%$ całości). W przeprowadzonych badaniach poszukiwano optymalnej wartości parametru $k$ na okresie uczącym, następnie weryfikowano otrzymane wyniki na okresie testowym. Wybór optymalnej wartości parametru (dla czystego wskaźnika Ma) polegał na wyszukaniu najlepszego zysku. \\
\newpage
\noindent \textbf{\\Wyniki badań przy maksymalizacji po zysku.}\\
\begin{figure}[h!]
\centering
\includegraphics[scale=0.6]{SF_zysk_us.png}\\
\caption{Zysk}
\end{figure}
\FloatBarrier
\noindent \textbf{Wycinek ValK i ValD}\\
\begin{figure}[h!]
\centering
\includegraphics[scale=0.4]{ValD_ValK_us.png}
\caption{ValD - kolor niebieski, ValK - kolor czerowny }
\end{figure}
\FloatBarrier
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\end {document}

### 2013-10-14 Matlabs/Indicators/KB/SF.m

@@ -1,171 +1,0 @@
-% Katarzyna Buda 
-% Stochastic Fast
-clc; close all; clear all;
-load('usdjpy60');
-paramSectionLearn = C(1:5400,:);
-paramSectionTest = C(5401:end,:);
-
-[m,n]=size(paramSectionLearn);
-[m1 n1]=size(paramSectionTest);
-
-O=paramSectionLearn(:,1);
-L=paramSectionLearn(:,3);
-H=paramSectionLearn(:,2);
-C=paramSectionLearn(:,4);
-
-%Parametry 
-pip = 0.01; % wielkosc pipsa na danym rynku
-spread = 1.8 * pip; % spread dla rynku
-pip =1; % wielkosc pipsa na danym rynku
-
-bestReturn = -1000;
-bestMa = 0;
-%Czêœæ ucz¹ca
-
-countCandleLearn=m;
-lastCandleLearn=0;
-krok=1;
-%Czêœæ valid
-
-paramALengthT=0;
-countCandleTest=m1;
-lastCandleTest=0;
-tmp=countCandleLearn-1;
-ValK=zeros(1, countCandleLearn);
-paramZakrespocz=0;
-chwi=1;
-for paramALengthL=10:100 %liczba œwiec wstecz ( do max)
-    chwi=chwi;
-    paramZakrespocz(chwi)=paramALengthL;
-   for i=2:tmp
-       max3=max(H(max(i-paramALengthL, 1):i));
-       min3=min(L(max(i-paramALengthL, 1):i));
-      ValK(i)=100*(C(i)-min3)/(max3-min3);
-   end
-    ValD=ema(ValK,3);
-    sumRa=zeros(1,tmp);
-    Ra=zeros(1,tmp);
-   lastCandleLearn=tmp;
-       
-    %-------------obliczanie zysków
-    WinReturn=0;
-    DownReturn=0;
-    CalmarLearn=0;
-    BestCalLEarn=0;
-    
-    for j=2:lastCandleLearn
-        
-        if ValK(j)>ValD(j) || ValK(j)<=ValD(j)
-            Ra(j)=C(j+krok)-O(j+1)-spread ;% zysk z j-tej pozycji long zamykanej na zamkniêciu po 1 kroku 
-        end
-
-        sumRa(j)=sumRa(j-1)+Ra(j); %krzywa narastania kapita³u
-        
-        if sumRa(j)>WinReturn
-            WinReturn=sumRa(j);
-        end
-        
[…]

### 2013-10-14 Matlabs/Indicators/KB/PivotPoint.m
Skrypty do Indykatorów

@@ -1,0 +1,185 @@
+clc; close all; clear all;
+load('usdjpy60');
+paramSectionLearn = C(1:5400,:);
+paramSectionTest = C(5401:end,:);
+
+[m,n]=size(paramSectionLearn);
+[m1 n1]=size(paramSectionTest);
+
+O=paramSectionLearn(:,1);
+L=paramSectionLearn(:,3);
+H=paramSectionLearn(:,2);
+C=paramSectionLearn(:,4);
+
+%Parametry 
+pip = 0.01; % wielkosc pipsa na danym rynku
+spread = 1.8 * pip; % spread dla rynku
+% pip =1; % wielkosc pipsa na danym rynku
+
+bestReturn = -100;
+bestMa = 0;
+%Czêœæ ucz¹ca
+
+countCandleLearn=m;
+lastCandleLearn=0;
+krok=1;
+%Czêœæ valid
+
+paramALengthT=0;
+countCandleTest=m1;
+lastCandleTest=0;
+chwi=1;
+tmp=countCandleLearn-1;
+
+P = (H + L + C) / 3;
+R1 = 2*P - L;
+S1 = 2*P - H;
+
+sumRa=zeros(1,tmp);
+Ra=zeros(1,tmp);
+lastCandleLearn=tmp;
+   
+WinReturn=0;
+DownReturn=0;
+CalmarLearn=0;
+BestCalLearn=0;
+for paramALengthL=10:100 %liczba œwiec wstecz ( do max)
+    chwi=chwi;
+
+paramZakrespocz(chwi)=paramALengthL;
+       
+    %-------------obliczanie zysków
+
+    
+    for j=2:lastCandleLearn
+        
+        if R1(j)>C(j) && R1(j)<=C(j-1)
+            Ra(j)=C(j+krok)-O(j+1)-spread ;% zysk z j-tej pozycji long zamykanej na zamkniêciu po 1 kroku 
+        else if S1(j)<C(j) && S1(j)>=C(j-1)
+             Ra(j)=-C(j+krok)+O(j+1)+spread   ; 
+            end
+        end
+
+        sumRa(j)=sumRa(j-1)+Ra(j); %krzywa narastania kapita³u
+        
+        if sumRa(j)>WinReturn
+            WinReturn=sumRa(j);
+        end
+        
+        DownReturnTmp=sumRa(j)-WinReturn;
+        if  DownReturnTmp<DownReturn
[…]

### 2013-10-14 Matlabs/Indicators/KB/Stochastic_Fast.m

@@ -1,0 +1,190 @@
+% Katarzyna Buda 
+% Stochastic Fast
+clc; close all; clear all;
+load('usdjpy60');
+paramSectionLearn = C(1:5400,:);
+paramSectionTest = C(5401:end,:);
+
+[m,n]=size(paramSectionLearn);
+[m1 n1]=size(paramSectionTest);
+
+O=paramSectionLearn(:,1);
+L=paramSectionLearn(:,3);
+H=paramSectionLearn(:,2);
+C=paramSectionLearn(:,4);
+
+%Parametry 
+pip = 0.01; % wielkosc pipsa na danym rynku
+spread = 1.8 * pip; % spread dla rynku
+% pip =1; % wielkosc pipsa na danym rynku
+
+bestReturn = -100;
+bestMa = 0;
+%Czêœæ ucz¹ca
+
+countCandleLearn=m;
+lastCandleLearn=0;
+krok=1;
+%Czêœæ valid
+
+paramALengthT=0;
+countCandleTest=m1;
+lastCandleTest=0;
+tmp=countCandleLearn-1;
+ValK=zeros(1, countCandleLearn);
+paramZakrespocz=0;
+chwi=1;
+for paramALengthL=10:100 %liczba œwiec wstecz ( do max)
+    chwi=chwi;
+    paramZakrespocz(chwi)=paramALengthL;
+   for i=2:tmp
+       max3=max(H(max(i-paramALengthL, 1):i));
+       min3=min(L(max(i-paramALengthL, 1):i));
+      ValK(i)=100*(C(i)-min3)/(max3-min3);
+   end
+    ValD=ema(ValK,3);
+    sumRa=zeros(1,tmp);
+    Ra=zeros(1,tmp);
+   lastCandleLearn=tmp;
+       
+    %-------------obliczanie zysków
+    WinReturn=0;
+    DownReturn=0;
+    CalmarLearn=0;
+    BestCalLearn=0;
+    
+    for j=2:lastCandleLearn
+        
+        if ValK(j)>ValD(j) && ValK(j-1)<=ValD(j)
+            Ra(j)=C(j+krok)-O(j+1)-spread ;% zysk z j-tej pozycji long zamykanej na zamkniêciu po 1 kroku 
+          else if ValK(j)<ValD(j) && ValK(j-1)>=ValD(j) 
+            Ra(j)=-C(j+krok)+O(j+1)+spread; 
+               end
+        end
[…]

### 2013-10-23 Matlabs/PSO/zlacz_pliki.m
added: łącznie plików wynikowych w jeden

@@ -1,0 +1,32 @@
+clc
+close
+clear
+
+% skrypt do ³¹czenia wyników
+id = fopen('wyniki_laczne.txt','w');
+
+for i=4:33
+    plik = sprintf('tewiROC%iab.txt',i);
+    id_t = fopen(plik);
+    tresc = fscanf(id_t,'%c');
+    fprintf(id,tresc);
+    fprintf(id,'\n');
+    fclose(id_t);
+end
+
+fclose(id);
+
+
+% skrypt do ³¹czenia wyników
+id = fopen('wyniki_laczne_opt.txt','w');
+
+for i=4:33
+    plik = sprintf('tewiROC%iabopt_param.txt',i);
+    id_t = fopen(plik);
+    tresc = fscanf(id_t,'%c');
+    fprintf(id,tresc);
+    fprintf(id,'\n');
+    fclose(id_t);
+end
+
+fclose(id);

### 2013-10-25 Matlabs/Indicators/MZ/S4halved - MassIndex/S4ABCD.m
Strategia dla wskaźników oparta na 4 kwadrantach

@@ -1,0 +1,460 @@
+%(C) Micha³ Zab³ocki 2013
+%skrypt strategii S4 w projekcie TEWI
+%S4L - sygna³ kupna - przeciêcia linii, %K ponad %D
+
+%parametry:
+% paramAVolLength -
+% paramADuration - liczba kroków wprzód do zamkniecia pozycji
+% paramASL - Stop Loss
+
+%Dane:
+tStart=tic;
+verificationC=C(5400:end,:); learningC=C(1:5399,:);
+
+confusionMatrix.TP=zeros(1,4);
+confusionMatrix.FP=zeros(1,4);
+confusionMatrix.FN=zeros(1,4);
+confusionMatrix.TN=zeros(1,4);
+
+% bests(1:11) - najlepsze parametry pêtli, bests(12) - bestSumR,
+%                      bests(13) - bestCalmar, bests(14) - bestLa
+bests = cell(4,14);
+bests(1:4,12) = {-1000};
+
+paramAVolLength_min = 5;
+paramAVolLength_step = 5;
+paramAVolLength_max = 30;
+
+hlAverageLength1_min = 2;
+hlAverageLength1_step = 1;
+hlAverageLength1_max = 50;
+
+ema2Length_min = 2;
+ema2Length_step = 1;
+ema2Length_max = 50;
+
+hlAverageLength2_min = 2;
+hlAverageLength2_step = 1;
+hlAverageLength2_max = 50;
+
+sumLength_min = 2;
+sumLength_step = 2;
+sumLength_max = 50;
+
+cAveragesLength_min = 2;
+cAveragesLength_step = 2;
+cAveragesLength_max = 50;
+
+openBorder_min = 0;
+openBorder_step = 0.1;
+% openBorder_max = 50;
+
+closeBorder_min = 0;
+closeBorder_step = 0.1;
+% closeBorder_max = 50;
+
+paramADuration_min = 2;
+paramADuration_step = 1;
+paramADuration_max = 50;
+
+paramAVolThreshold_min = 100;
+paramAVolThreshold_step = -10;
+paramAVolThreshold_max = 10;
+
+paramASL_min = 8*spread;
+paramASL_step = 3*spread;
+paramASL_max = 30*spread;
+
+paramAVolLength_Vector = paramAVolLength_min : paramAVolLength_step : paramAVolLength_max;
+hlAverageLength1_Vector = hlAverageLength1_min : hlAverageLength1_step : hlAverageLength1_max;
[…]

### 2013-10-25 Matlabs/Indicators/MZ/S4halved - MassIndex/S4LS_clear.m

@@ -1,0 +1,97 @@
+%(C) Micha³ Zab³ocki 2013
+%skrypt strategii S4 w projekcie TEWI
+%S4L - sygna³ kupna - przeciêcia linii, %K ponad %D
+
+%Dane:
+tStart=tic;
+
+true_positive = 0;
+false_positive = 0;
+false_negative = 0;
+true_negative = 0;
+
+cSizes = size(C);
+candlesCount = cSizes(1);
+bestiL = 0;
+bestiS = 0;
+HL = C(:,2) - C(:,3);
+
+kon=candlesCount-1;
+MI = zeros(candlesCount,1);
+HLaverage = ema(HL,9);
+EMA2 = HLaverage(9:end) ./ ema(HLaverage(9:end),9);
+for i = 41:kon-16
+    MI(i) = sum(EMA2(i-24:i));
+end
+Caverages = ema(C(:,4),9);
+
+sumR=zeros(1,candlesCount);
+R=zeros(1,candlesCount);
+pocz=50;
+iL=0; %liczba otwieranych pozycji kupna
+iS=0; %liczba otwieranych pozycji sprzedarzy
+lastCandle = kon-16;
+recordReturn=0;  %rekord zysku
+recordDrawdown=0;  %rekord obsuniecia
+LastPos = 0;
+pic1 = false;
+
+for i=pocz:lastCandle
+    
+    if pic1 == false && MI(i) > 27
+        pic1 = true;
+    end
+    if pic1 == true && MI(i) < 26.5
+        if C(i,4) > Caverages(i) % warunek kupna
+            R(i)= -C(i+1,4)-LastPos-spread; % zamkniêcie S
+            LastPos = C(i+1,1); % otwarcie L
+            iL=iL+1;
+        elseif C(i,4) < Caverages(i) % warunek sprzeda¿y
+            R(i)=C(i+1,4)-LastPos-spread; % zamkniêcie L
+            LastPos = C(i+1,1); % otwarcie S
+            iS=iS+1;
+        end
+        pic1 = false;
+    end
+    sumR(i)= sum(R(pocz:i));  %krzywa narastania kapita³u
+    
+    if sumR(i)>recordReturn
+        recordReturn=sumR(i);
+    end
+    
+    if sumR(i)-recordReturn<recordDrawdown
+        recordDrawdown=sumR(i)-recordReturn;  %obsuniecie maksymalne
+    end
+end
+
[…]

### 2013-10-25 Matlabs/Indicators/MZ/S4halved - MassIndex/run_abcd.m

@@ -1,0 +1,23 @@
+close all
+loopEnd=800;
+
+load ('cadchf60');
+pip = 0.0001; % wielkosc pipsa na danym rynku
+spread = 8 * pip; % spread dla rynku
+file_name = 'cadchf60';
+disp(['BADANIE RYNKU ', file_name, ' strategia S4{A,B, C, D} >>']);
+S4ABCD
+
+load ('nzdjpy60');
+pip = 0.01; % wielkosc pipsa na danym rynku
+spread = 6 * pip; % spread dla rynku
+file_name = 'nzdjpy60';
+disp(['BADANIE RYNKU ', file_name, ' strategia S4{A,B, C, D} >>']);
+S4ABCD
+
+load ('usdcad60');
+pip = 0.0001; % wielkosc pipsa na danym rynku
+spread = 4 * pip; % spread dla rynku
+file_name = 'usdcad60';
+disp(['BADANIE RYNKU ', file_name, ' strategia S4{A,B, C, D} >>']);
+S4ABCD

### 2013-10-25 Matlabs/Indicators/MZ/S4halved - StatisticSlow/S4ABCD.m

@@ -1,0 +1,429 @@
+%(C) Micha³ Zab³ocki 2013
+%skrypt strategii S4 w projekcie TEWI
+%S4L - sygna³ kupna - przeciêcia linii, %K ponad %D
+
+%parametry:
+% paramAVolLength -
+% paramADuration - liczba kroków wprzód do zamkniecia pozycji
+% paramASL - Stop Loss
+
+%Dane:
+tStart=tic;
+verificationC=C(5400:end,:); learningC=C(1:5399,:);
+
+confusionMatrix.TP=zeros(1,4);
+confusionMatrix.FP=zeros(1,4);
+confusionMatrix.FN=zeros(1,4);
+confusionMatrix.TN=zeros(1,4);
+
+% bests(1:10) - najlepsze parametry pêtli, bests(11) - bestSumR,
+%                      bests(12) - bestCalmar, bests(13) - bestLa
+bests = cell(4,13);
+bests(1:4,11) = {-1000};
+
+paramAVolLength_min = 5;
+paramAVolLength_step = 10;
+paramAVolLength_max = 30;
+
+minLength1_min = 2;
+minLength1_step = 2;
+minLength1_max = 30;
+
+minLength2_min = 2;
+minLength2_step = 2;
+minLength2_max = 30;
+
+maxLength_min = 2;
+maxLength_step = 2;
+maxLength_max = 30;
+
+sumLength1_min = 2;
+sumLength1_step = 2;
+sumLength1_max = 30;
+
+sumLength2_min = 2;
+sumLength2_step = 2;
+sumLength2_max = 30;
+
+dMALength_min = 2;
+dMALength_step = 2;
+dMALength_max = 30;
+
+paramADuration_min = 5;
+paramADuration_step = 10;
+paramADuration_max = 30;
+
+paramAVolThreshold_min = 100;
+paramAVolThreshold_step = -10;
+paramAVolThreshold_max = 10;
+
+paramASL_min = 8*spread;
+paramASL_step = 3*spread;
+paramASL_max = 20*spread;
+
+paramAVolLength_Vector = paramAVolLength_min : paramAVolLength_step : paramAVolLength_max;
+minLength1_Vector = minLength1_min : minLength1_step : minLength1_max;
+minLength2_Vector = minLength2_min : minLength2_step : minLength2_max;
+maxLength_Vector = maxLength_min : maxLength_step : maxLength_max;
[…]

### 2013-10-25 Matlabs/Indicators/MZ/S4halved - StatisticSlow/S4LS_clear_calmar.m

@@ -1,0 +1,172 @@
+%(C) Micha³ Zab³ocki 2013
+%skrypt strategii S4 w projekcie TEWI
+%S4L - sygna³ kupna - przeciêcia linii, %K ponad %D
+
+%parametry:
+% paramMALength - MA length
+
+%Dane:
+tStart=tic;
+verificationC=C(5400:end,:); C=C(1:5399,:);
+
+cSizes = size(C);
+candlesCount = cSizes(1);
+bestCalmar = -1000;
+bestMa = 0;
+bestReturn = -1000;
+bestiL = 0;
+bestiS = 0;
+lastCandle = 0 ;
+
+for paramMALength=1000:-20:2 %MA length
+    disp(['# Postep: ', 'paramMALength ', num2str(paramMALength), '   Czas: ', num2str(toc(tStart))]);
+    maxes=zeros(candlesCount,1);
+    mins=zeros(candlesCount,1);
+    K=zeros(candlesCount,1);
+    D=zeros(candlesCount,1);
+    kon=candlesCount-1;
+    for i=4:kon
+        maxes(i) = max(C(i-min(i-1,paramMALength):i-1,2));
+        mins(i) = min(C(i-min(i-1,paramMALength):i-1,3));
+        K(i) = 100 * (sum(C(i-min(i-1,3):i-1,4)-mins(i-min(i-1,2):i)) / sum(maxes(i-min(i-1,2):i)-mins(i-min(i-1,2):i)));
+        D(i) = sum(K(i-min(i-1,2):i)) / min(i-1,3);
+    end
+    
+    sumR=zeros(1,candlesCount);
+    R=zeros(1,candlesCount);
+    pocz=max(paramMALength, 10)+3;
+    iL=0; %liczba otwieranych pozycji kupna
+    iS=0; %liczba otwieranych pozycji sprzedarzy
+    lastCandle = kon-paramMALength;
+    recordReturn=0;  %rekord zysku
+    recordDrawdown=0;  %rekord obsuniecia
+    LastPos = 0;
+    for i=pocz:lastCandle
+        
+        if K(i-1) < D(i-1) && K(i) >= D(i)
+            R(i)= - C(i+1,4)+LastPos-spread; % zamkniêcie S
+            LastPos = C(i+1,1); % otwarcie L
+            iL=iL+1;
+        elseif K(i-1) > D(i-1) && K(i) <= D(i)
+            R(i)=C(i+1,4)-LastPos-spread; % zamkniêcie L
[…]

### 2013-10-25 Matlabs/Indicators/MZ/S4halved - StatisticSlow/S4LS_clear_zysk.m

@@ -1,0 +1,171 @@
+%(C) Micha³ Zab³ocki 2013
+%skrypt strategii S4 w projekcie TEWI
+%S4L - sygna³ kupna - przeciêcia linii, %K ponad %D
+
+%parametry:
+% paramMALength - MA length
+
+%Dane:
+tStart=tic;
+verificationC=C(5400:end,:); C=C(1:5399,:);
+
+cSizes = size(C);
+candlesCount = cSizes(1);
+bestCalmar = 0;
+bestMa = 0;
+bestReturn = -1000;
+bestiL = 0;
+bestiS = 0;
+
+for paramMALength=1000:-20:2 %MA length
+    disp(['# Postep: ', 'paramMALength ', num2str(paramMALength), '   Czas: ', num2str(toc(tStart))]);
+    maxes=zeros(candlesCount,1);
+    mins=zeros(candlesCount,1);
+    K=zeros(candlesCount,1);
+    D=zeros(candlesCount,1);
+    kon=candlesCount-1;
+    for i=4:kon
+        maxes(i) = max(C(i-min(i-1,paramMALength):i-1,2));
+        mins(i) = min(C(i-min(i-1,paramMALength):i-1,3));
+        K(i) = 100 * (sum(C(i-min(i-1,3):i-1,4)-mins(i-min(i-1,2):i)) / sum(maxes(i-min(i-1,2):i)-mins(i-min(i-1,2):i)));
+        D(i) = sum(K(i-min(i-1,2):i)) / min(i-1,3);
+    end
+    
+    sumR=zeros(1,candlesCount);
+    R=zeros(1,candlesCount);
+    pocz=max(paramMALength, 10)+3;
+    iL=0; %liczba otwieranych pozycji kupna
+    iS=0; %liczba otwieranych pozycji sprzedarzy
+    lastCandle = kon-paramMALength;
+    recordReturn=0;  %rekord zysku
+    recordDrawdown=0;  %rekord obsuniecia
+    LastPos = 0;
+    for i=pocz:lastCandle
+        
+        if K(i-1) < D(i-1) && K(i) >= D(i)
+            R(i)= - C(i+1,4)+LastPos-spread; % zamkniêcie S
+            LastPos = C(i+1,1); % otwarcie L
+            iL=iL+1;
+        elseif K(i-1) > D(i-1) && K(i) <= D(i)
+            R(i)=C(i+1,4)-LastPos-spread; % zamkniêcie L
[…]

### 2013-10-25 Matlabs/Indicators/MZ/S4halved - StatisticSlow/calculateMCC.m

@@ -1,0 +1,17 @@
+function [ CM, MCC, P, R ] = calculateMCC( M, S )
+%calculates MCC Matthews Correlation Coefficient
+%  easy to interpret predictor classification (+1 - perfect predictor, 0 - random, -1 perfectly perverse predictor)
+% CM - confusion matrix,  MCC - Matthews Correlation Coefficient, P - precision, R
+
+CM=cell(1,S);
+MCC=zeros(1,S);
+P=zeros(1,S);
+R=zeros(1,S);
+for i = 1:S
+    CM(i) = {[M.TP(i) M.FP(i); M.FN(i) M.TN(i)]};
+    MCC(i) = (M.TP(i)*M.TN(i)-M.FP(i)*M.FN(i))/sqrt((M.TP(i)+M.FP(i))*(M.TP(i)+M.FN(i))*(M.TN(i)+M.FP(i))*(M.TN(i)+M.FN(i)));
+    P(i)=M.TP(i)/(M.TP(i)+M.FP(i));
+    R(i)=M.TP(i)/(M.TP(i)+M.FN(i));
+end
+end
+

### 2013-10-25 Matlabs/Indicators/MZ/S4halved - StatisticSlow/run_abcd.m

@@ -1,0 +1,23 @@
+clear all
+loopEnd=1;
+
+load ('cadchf60');
+pip = 0.0001; % wielkosc pipsa na danym rynku
+spread = 8 * pip; % spread dla rynku
+file_name = 'cadchf60';
+disp(['BADANIE RYNKU ', file_name, ' strategia S4{A,B, C, D} >>']);
+S4ABCD
+
+load ('nzdjpy60');
+pip = 0.01; % wielkosc pipsa na danym rynku
+spread = 6 * pip; % spread dla rynku
+file_name = 'nzdjpy60';
+disp(['BADANIE RYNKU ', file_name, ' strategia S4{A,B, C, D} >>']);
+S4ABCD
+
+load ('usdcad60');
+pip = 0.0001; % wielkosc pipsa na danym rynku
+spread = 4 * pip; % spread dla rynku
+file_name = 'usdcad60';
+disp(['BADANIE RYNKU ', file_name, ' strategia S4{A,B, C, D} >>']);
+S4ABCD

### 2013-10-25 Matlabs/Indicators/KB/Pivot.tex

--- 2013-10-14 Matlabs/Indicators/KB/Stochastic Fast.tex
@@
 \begin{large}
-Stochastic Fast --- opis wskaźnika Stochastic Fast\\
+Pivot Point--- opis wskaźnika Pivot Point\\
 \end{large}
@@
 
-Stochastic Fast - wskaxnik stochastyczny szybki, zaproponowany w latach 50-tych przez George C.
-Lane.
-Sposób wyliczenia wartości wskaźnika uwzględniając wartości O,H,C,L, polega na wyliczeniu dwóch linii.
-\ref{wzor_1} oraz \ref{wzor_2}.
+Pivot Point - Jest to matematyczna formuła wyznaczania poziomów wsparć i oporu weryfikując maksima oraz minima występujące w danym okresie.
+Jest to wzór określający potencjalny zasięg ruchu notowań w danej jednostce czasu.
+Opiera się na obliczeniu danych za pomocą następujących wzorów: 1, 2, 3, 4 oraz 5}.
 \begin{equation}
-ValK=100*[ \frac{C-Min(L;n)}{max(H;n - min(L;n)}]
+P(Pivot point) = \franc{(H + L + C)}{3}
 \label{wzor_1}
@@
 \begin{equation}
-ValD=EMA(ValK;3)
+R1(Pierwszy opór) = 2*P - L
 \label{wzor_2}
 \end{equation}
-gdzie:
-\begin{itemize}
-\newline
-\item ValD - jest wygładzoną linią ValK
-\item n - ilość dni
-\item EMA - Wykładnicza średnia krocząca(Exponential Moving Average)
-\end{itemize}
+\begin{equation}
+S1 (Pierwsze wsparcie) = 2P - H
+\label{wzor_3}
+\end{equation}
+\begin{equation}
+R2 (Drugi opór) = P + (R1 - S1)
+\label{wzor_4}
+\end{equation}
+\begin{equation}
+S2 (Drugie wsparcie) = P - (R1 - S1)
+\label{wzor_5}
+\end{equation}
 
@@
 \begin{itemize}
-\item opokazuje poziom dzisiejszego zamknięcia w stosunku do najniższego oraz najwyższego punktu w badanym okresie
-\item porusza się w przedziale od 0-100
-\item obliczamy 2 linie oscylatora ValK i ValD (Value K i Value D) uwzględniając, że ValK jest główną linią oscylatora natomiast ValD jest wygładzoną postacią ValK
+\item służą do wyznaczania punktów wsparcia i oporu na rynkach
+\item określenie punktu zawarcia transakcji poprzez odpowiednie przecięcia linii
+\item ustalenie poziomu oporu branego pod uwagę (pierwszy lub drugi)
 \end{itemize}
+\newline
+
 Najważniejszą własnością opisywanego wskaźnika, stosowaną przy implementacjach strategii, jest fakt wskazywania momentów w których powinny zostać zawarte transakcje.
+W wypadku Pivot Point należy określić punkt zawarcia transakcji.
+Na potrzeby programu trzymano się strategii gdzie:
 \begin{itemize}
-\item sygnałem kupna jest przecięcie linii ValK ponad ValD
-\item sygnałem sprzedaży jest przecięcie linii ValK poniżej ValD.
-
+\item sygnałem kupna jest przecięcie linii R1
+\item sygnałem sprzedaży jest przecięcie linii S1
+\newline
 \end{itemize}
@@
 \begin{lstlisting}
-[a b]=size(C);
-roz=(60*a)/100;
-roz=round(roz);
-paramSectionLearn = C(1:roz,:);
+paramSectionLearn = C(1:5400,:);
+paramSectionTest = C(5401:end,:);
 
@@
 %Parametry 
-spread=0.00016;
+pip = 0.01; % wielkosc pipsa na danym rynku
+spread = 1.8 * pip; % spread dla rynku
+% pip =1; % wielkosc pipsa na danym rynku
+
 bestReturn = -100;
@@
 lastCandleTest=0;
+chwi=1;
 tmp=countCandleLearn-1;
-ValK=zeros(1, countCandleLearn);
-paramZakrespocz=0;
-chwi=1;
-for paramALengthL=40 %liczba świec wstecz ( do max)
-        chwi=chwi;
-        chwi
-    paramZakrespocz(chwi)=paramALengthL;
-   for i=2:tmp
-       max3=max(H(max(i-paramALengthL, 1):i));
-       min3=min(L(max(i-paramALengthL, 1):i));
-      ValK(i)=100*(C(i)-min3)/(max3-min3);
-   end
-    ValD=ema(ValK,3);
+
+P = (H + L + C) / 3;
+R1 = 2*P - L;
+S1 = 2*P - H;
+
 sumRa=zeros(1,tmp);
@@
 
-%-------------obliczanie zysków
 WinReturn=0;
@@
 BestCalLearn=0;
+for paramALengthL=10:100 %liczba świec wstecz ( do max)
+    chwi=chwi;
+
+paramZakrespocz(chwi)=paramALengthL;
+
+    %-------------obliczanie zysków
 
@@
 
-        if ValK(j)>ValD(j) && ValK(j-1)<=ValD(j)
+        if R1(j)>C(j) && R1(j)<=C(j-1)
             Ra(j)=C(j+krok)-O(j+1)-spread ;% zysk z j-tej pozycji long zamykanej na zamknięciu po 1 kroku 
-          else if ValK(j)<ValD(j) && ValK(j-1)>=ValD(j) 
-            Ra(j)=-C(j+krok)+O(j+1)+spread; 
+        else if S1(j)<C(j) && S1(j)>=C(j-1)
+             Ra(j)=-C(j+krok)+O(j+1)+spread   ; 
             end
         end
+
         sumRa(j)=sumRa(j-1)+Ra(j); %krzywa narastania kapitału
@@
  sumFinal=sumRa(lastCandleLearn);   
-CalmarLearn=-sumFinal/DownReturn;
-
     if bestReturn < sumFinal
@@
 
-sumFinal=sumRa(lastCandleLearn);
 CalmarLearn=-sumFinal/DownReturn;
@@
 
-Na podstawie zebranych informacji dotyczących wskaźnika Stochastic Fast, stworzono powyższy program uwzględniając pozycje sprzedaży i kupna przy określonych przecięciach.
+Na podstawie zebranych informacji dotyczących wskaźnika Pivot Point, stworzono powyższy program uwzględniając pozycje sprzedaży i kupna przy określonych przecięciach.
 Badania przeprowadzono na rynku usdjpy.
 \begin{itemize}
-\item sygnałem kupna jest przecięcie linii ValK ponad ValD
-\item sygnałem sprzedaży jest przecięcie linii ValK poniżej ValD.
+\item sygnałem kupna jest przecięcie linii R1
+\item sygnałem sprzedaży jest przecięcie linii S1
+\newline
 \end{itemize}
@@
 \\
-\newpage
+
 \noindent \textbf{\\Wyniki badań przy maksymalizacji po zysku.}\\
@@
 \centering
-\includegraphics[scale=0.6]{SF_zysk_us.png}\\
+\includegraphics[scale=0.4]{pp_zysk_us.png}
 \caption{Zysk}
+
 \end{figure}
 \FloatBarrier
-\noindent \textbf{Wycinek ValK i ValD}\\
+
+\newpage
+\noindent \textbf{Wycinek R1 i S1}\\
 \begin{figure}[h!]
 \centering
-\includegraphics[scale=0.4]{ValD_ValK_us.png}
-\caption{ValD - kolor niebieski, ValK - kolor czerowny }
+\includegraphics[scale=0.4]{pp_rs_us.png}
+\caption{Trend rynku - kolor niebieskim, R1 - kolor czerwony oraz S1 - kolor zielony }
 \end{figure}

### 2013-10-29 Article/book/generator/generator/generator/ChartGenerator.cs
book & book generator

@@ -1,0 +1,69 @@
+﻿using System.Collections;
+using System.Collections.Generic;
+using System.Diagnostics;
+using System.IO;
+using System.Linq;
+
+namespace generator
+{
+    class ChartGenerator
+    {
+        private readonly string outputFolder;
+        private readonly string authorInitials;
+        public ChartGenerator(string outputFolder, string authorInitials)
+        {
+            this.outputFolder = outputFolder;
+            this.authorInitials = authorInitials;
+        }
+
+        public string Generate(string filenameFormat, string marketName)
+        {
+            var imagesFolder = Path.Combine(outputFolder, "images");
+            var variantNamePlace = filenameFormat.IndexOf("{0}", System.StringComparison.InvariantCulture)+1;
+            Debug.Assert(variantNamePlace > 0, "variantNamePlace>0");
+            var labels = new List<string>(){"jedno", "dwu", "cztero", "mansard", "mansard"};
+            var texFilePath = Path.Combine(outputFolder, authorInitials + marketName + ".tex");
+            using (TextWriter writer = new StreamWriter(texFilePath))
+            {
+                writer.WriteLine(@"%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%");
+                writer.WriteLine(@"\newpage");
+                writer.WriteLine(@"\begin{table}[!t]");
+                writer.WriteLine(@"\caption{Profits for all strategy quadrants for " + marketName + "}");
+                writer.WriteLine(@" \begin{center}");
+                writer.WriteLine(@" \begin{tabular}{|l|l|l|l|l|}");
+                writer.WriteLine(@" \hline \textbf{strategy} & \textbf{profit} & \textbf{bestCalmar} & \textbf{bestMALength} & \textbf{la} \\ \hline");
+                writer.WriteLine(@"S1a & 17.19 & 8.24 & 18 & 2693\\ \hline");
+                writer.WriteLine(@"S1b & -9.80 & -0.74 & 54 & 2665\\ \hline");
+                writer.WriteLine(@"S1c & 5.65 & 2.06 & 54 & 2280\\ \hline");
+                writer.WriteLine(@"S1d & 1.87 & 0.61 & 18 & 2287\\ \hline");
+                writer.WriteLine(@"S1s & 14.85 & 5.68 & Group of MA & 4945\\"); 
+                writer.WriteLine(@"\hline \end{tabular}");
+                writer.WriteLine(@" \end{center}");
[…]

### 2013-10-29 Article/book/generator/generator/generator/Form1.cs

@@ -1,0 +1,31 @@
+﻿using System;
+using System.Windows.Forms;
+using System.IO;
+using generator.Properties;
+
+namespace generator
+{
+    public partial class Form1 : Form
+    {
+        public Form1()
+        {
+            InitializeComponent();
+        }
+
+        private void BtnGenerateClick(object sender, System.EventArgs e)
+        {
+            var outputFolder = "output" + DateTime.Now.ToString("yyyyMMdd_hhmmss");
+            System.IO.Directory.CreateDirectory(outputFolder);
+            System.IO.Directory.CreateDirectory(Path.Combine(outputFolder, "images"));
+            var oneChartGeneratorMz = new ChartGenerator(outputFolder, "MZ");
+            var s = new System.Text.StringBuilder(); 
+            s.Append(oneChartGeneratorMz.Generate("cadchfS1{0}", "CADCHF"));
+            s.Append(oneChartGeneratorMz.Generate("fcopperS1{0}", "FCOPPER"));
+            s.Append(oneChartGeneratorMz.Generate("fcornS1{0}", "FCORN"));
+            s.Append(oneChartGeneratorMz.Generate("nzdjpyS1{0}", "NZDJPY"));
+            s.Append(oneChartGeneratorMz.Generate("usdcadS1{0}", "USDCAD"));
+            File.WriteAllText(Path.Combine(outputFolder, "MZ.tex"), s.ToString());
+            toolStripStatusLabel1.Text = Resources.btnGenerateClickGenerated;
+        }
+    }
+}

### 2013-10-29 Article/book/generator/generator/generator/Properties/AssemblyInfo.cs

@@ -1,0 +1,36 @@
+﻿using System.Reflection;
+using System.Runtime.CompilerServices;
+using System.Runtime.InteropServices;
+
+// General Information about an assembly is controlled through the following 
+// set of attributes. Change these attribute values to modify the information
+// associated with an assembly.
+[assembly: AssemblyTitle("generator")]
+[assembly: AssemblyDescription("")]
+[assembly: AssemblyConfiguration("")]
+[assembly: AssemblyCompany("")]
+[assembly: AssemblyProduct("generator")]
+[assembly: AssemblyCopyright("Copyright ©  2013")]
+[assembly: AssemblyTrademark("")]
+[assembly: AssemblyCulture("")]
+
+// Setting ComVisible to false makes the types in this assembly not visible 
+// to COM components.  If you need to access a type in this assembly from 
+// COM, set the ComVisible attribute to true on that type.
+[assembly: ComVisible(false)]
+
+// The following GUID is for the ID of the typelib if this project is exposed to COM
+[assembly: Guid("878fbfbb-66d1-4569-af0f-b58cf6b38711")]
+
+// Version information for an assembly consists of the following four values:
+//
+//      Major Version
+//      Minor Version 
+//      Build Number
+//      Revision
+//
+// You can specify all the values or you can default the Build and Revision Numbers 
+// by using the '*' as shown below:
+// [assembly: AssemblyVersion("1.0.*")]
+[assembly: AssemblyVersion("1.0.0.0")]
+[assembly: AssemblyFileVersion("1.0.0.0")]

### 2013-10-29 Article/book/generator/generator/generator/Properties/Settings.Designer.cs

@@ -1,0 +1,30 @@
+﻿//------------------------------------------------------------------------------
+// <auto-generated>
+//     This code was generated by a tool.
+//     Runtime Version:4.0.30319.18051
+//
+//     Changes to this file may cause incorrect behavior and will be lost if
+//     the code is regenerated.
+// </auto-generated>
+//------------------------------------------------------------------------------
+
+namespace generator.Properties
+{
+
+
+    [global::System.Runtime.CompilerServices.CompilerGeneratedAttribute()]
+    [global::System.CodeDom.Compiler.GeneratedCodeAttribute("Microsoft.VisualStudio.Editors.SettingsDesigner.SettingsSingleFileGenerator", "11.0.0.0")]
+    internal sealed partial class Settings : global::System.Configuration.ApplicationSettingsBase
+    {
+
+        private static Settings defaultInstance = ((Settings)(global::System.Configuration.ApplicationSettingsBase.Synchronized(new Settings())));
+
+        public static Settings Default
+        {
+            get
+            {
+                return defaultInstance;
+            }
+        }
+    }
+}

### 2013-10-29 Article/book/FormatProposal/tewi-paper-template.tex
book format proposal - work in progress ;)

--- 2013-06-05 Article/Article20130603/tewi-paper-template.tex
@@
 Each graph represents one decision-making situation with the best parameter, number of last closures to calculate moving average.
-Fifth diagram shows the (S1s) cumulative strategy value.
-Which is the sum of profit of all open positions at this moment.
+Fifth diagram shows the (S1s) cumulative strategy value, which is the sum of profit of all open positions at this moment.
 Obviously all component strategies are calculated for the best parameter for each one of them.\\
@@
 
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+\newpage
+\begin{table}[!t]
+\caption{Profits for all strategy quadrants for CHFJPY}
+ \begin{center}
+ \begin{tabular}{|l|l|l|l|l|}
+ \hline \textbf{strategy} & \textbf{profit} & \textbf{bestCalmar} & \textbf{bestMALength} & \textbf{la} \\ \hline
+S1a & 17.19 & 8.24 & 18 & 2693\\ \hline
+S1b & -9.80 & -0.74 & 54 & 2665\\ \hline
+S1c & 5.65 & 2.06 & 54 & 2280\\ \hline
+S1d & 1.87 & 0.61 & 18 & 2287\\ \hline
+S1s & 14.85 & 5.68 & Group of MA & 4945\\
+\hline \end{tabular}
+ \end{center}
+ \end{table}
+\FloatBarrier
+\begin{figure}[h]
+\centering
+\begin{minipage}{\linewidth}
+\centering
+\includegraphics[width=0.6\textwidth]{images/chfjpyA.png}
+\subcaption{Profit - pyA}
+\label{jedno}
+\end{minipage}
+\begin{minipage}{\linewidth}
+\centering
+\includegraphics[width=0.6\textwidth]{images/chfjpyB.png}
+\subcaption{Profit - pyB}
+\label{dwu}
+\end{minipage}
+\\
+\begin{minipage}{\linewidth}
+\centering
+\includegraphics[width=0.6\textwidth]{images/chfjpyC.png}
+\subcaption{Profit - pyC}
+\label{cztero}
+\end{minipage}
+\begin{minipage}{\linewidth}
+\centering
+\includegraphics[width=0.6\textwidth]{images/chfjpyD.png}
+\subcaption{Profit - pyD}
+\label{mansard}
+\end{minipage}
+\caption{CHFJPY market results}
+\end{figure}
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+\newpage
+\begin{table}[!t]
+\caption{Profits for all strategy quadrants for EURJPY}
+ \begin{center}
+ \begin{tabular}{|l|l|l|l|l|}
+ \hline \textbf{strategy} & \textbf{profit} & \textbf{bestCalmar} & \textbf{bestMALength} & \textbf{la} \\ \hline
+S1a & 17.19 & 8.24 & 18 & 2693\\ \hline
+S1b & -9.80 & -0.74 & 54 & 2665\\ \hline
+S1c & 5.65 & 2.06 & 54 & 2280\\ \hline
+S1d & 1.87 & 0.61 & 18 & 2287\\ \hline
+S1s & 14.85 & 5.68 & Group of MA & 4945\\
+\hline \end{tabular}
+ \end{center}
+ \end{table}
+\FloatBarrier
+\begin{figure}[h]
+\centering
+\begin{minipage}{\linewidth}
+\centering
+\includegraphics[width=0.6\textwidth]{images/eurjpyA.png}
+\subcaption{Profit - pyA}
+\label{jedno}
+\end{minipage}
+\begin{minipage}{\linewidth}
+\centering
+\includegraphics[width=0.6\textwidth]{images/eurjpyB.png}
+\subcaption{Profit - pyB}
+\label{dwu}
+\end{minipage}
+\\
+\begin{minipage}{\linewidth}
+\centering
+\includegraphics[width=0.6\textwidth]{images/eurjpyC.png}
+\subcaption{Profit - pyC}
+\label{cztero}
+\end{minipage}
+\begin{minipage}{\linewidth}
+\centering
+\includegraphics[width=0.6\textwidth]{images/eurjpyD.png}
+\subcaption{Profit - pyD}
+\label{mansard}
+\end{minipage}
+\caption{EURJPY market results}
+\end{figure}
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+\newpage
+\begin{table}[!t]
+\caption{Profits for all strategy quadrants for FUS500}
+ \begin{center}
+ \begin{tabular}{|l|l|l|l|l|}
+ \hline \textbf{strategy} & \textbf{profit} & \textbf{bestCalmar} & \textbf{bestMALength} & \textbf{la} \\ \hline
+S1a & 17.19 & 8.24 & 18 & 2693\\ \hline
+S1b & -9.80 & -0.74 & 54 & 2665\\ \hline
+S1c & 5.65 & 2.06 & 54 & 2280\\ \hline
+S1d & 1.87 & 0.61 & 18 & 2287\\ \hline
+S1s & 14.85 & 5.68 & Group of MA & 4945\\
+\hline \end{tabular}
+ \end{center}
+ \end{table}
+\FloatBarrier
+\begin{figure}[h]
+\centering
+\begin{minipage}{\linewidth}
+\centering
+\includegraphics[width=0.6\textwidth]{images/fus500A.png}
+\subcaption{Profit - 00A}
+\label{jedno}
+\end{minipage}
+\begin{minipage}{\linewidth}
+\centering
+\includegraphics[width=0.6\textwidth]{images/fus500B.png}
+\subcaption{Profit - 00B}
+\label{dwu}
+\end{minipage}
+\\
+\begin{minipage}{\linewidth}
+\centering
+\includegraphics[width=0.6\textwidth]{images/fus500C.png}
+\subcaption{Profit - 00C}
+\label{cztero}
+\end{minipage}
+\begin{minipage}{\linewidth}
+\centering
+\includegraphics[width=0.6\textwidth]{images/fus500D.png}
+\subcaption{Profit - 00D}
+\label{mansard}
+\end{minipage}
+\caption{FUS500 market results}
+\end{figure}
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+\newpage
+\begin{table}[!t]
+\caption{Profits for all strategy quadrants for GBPCHF}
+ \begin{center}
+ \begin{tabular}{|l|l|l|l|l|}
+ \hline \textbf{strategy} & \textbf{profit} & \textbf{bestCalmar} & \textbf{bestMALength} & \textbf{la} \\ \hline
+S1a & 17.19 & 8.24 & 18 & 2693\\ \hline
+S1b & -9.80 & -0.74 & 54 & 2665\\ \hline
+S1c & 5.65 & 2.06 & 54 & 2280\\ \hline
+S1d & 1.87 & 0.61 & 18 & 2287\\ \hline
+S1s & 14.85 & 5.68 & Group of MA & 4945\\
+\hline \end{tabular}
+ \end{center}
+ \end{table}
+\FloatBarrier
+\begin{figure}[h]
+\centering
+\begin{minipage}{\linewidth}
+\centering
+\includegraphics[width=0.6\textwidth]{images/gbpchfA.png}
+\subcaption{Profit - hfA}
+\label{jedno}
+\end{minipage}
+\begin{minipage}{\linewidth}
+\centering
+\includegraphics[width=0.6\textwidth]{images/gbpchfB.png}
+\subcaption{Profit - hfB}
+\label{dwu}
+\end{minipage}
+\\
+\begin{minipage}{\linewidth}
+\centering
+\includegraphics[width=0.6\textwidth]{images/gbpchfC.png}
+\subcaption{Profit - hfC}
+\label{cztero}
+\end{minipage}
+\begin{minipage}{\linewidth}
+\centering
+\includegraphics[width=0.6\textwidth]{images/gbpchfD.png}
+\subcaption{Profit - hfD}
+\label{mansard}
+\end{minipage}
+\caption{GBPCHF market results}
+\end{figure}
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+\newpage
+\begin{table}[!t]
+\caption{Profits for all strategy quadrants for SILVER}
+ \begin{center}
+ \begin{tabular}{|l|l|l|l|l|}
+ \hline \textbf{strategy} & \textbf{profit} & \textbf{bestCalmar} & \textbf{bestMALength} & \textbf{la} \\ \hline
+S1a & 17.19 & 8.24 & 18 & 2693\\ \hline
+S1b & -9.80 & -0.74 & 54 & 2665\\ \hline
+S1c & 5.65 & 2.06 & 54 & 2280\\ \hline
+S1d & 1.87 & 0.61 & 18 & 2287\\ \hline
+S1s & 14.85 & 5.68 & Group of MA & 4945\\
+\hline \end{tabular}
+ \end{center}
+ \end{table}
+\FloatBarrier
+\begin{figure}[h]
+\centering
+\begin{minipage}{\linewidth}
+\centering
+\includegraphics[width=0.6\textwidth]{images/silverA.png}
+\subcaption{Profit - erA}
+\label{jedno}
+\end{minipage}
+\begin{minipage}{\linewidth}
+\centering
+\includegraphics[width=0.6\textwidth]{images/silverB.png}
+\subcaption{Profit - erB}
+\label{dwu}
+\end{minipage}
+\\
+\begin{minipage}{\linewidth}
+\centering
+\includegraphics[width=0.6\textwidth]{images/silverC.png}
+\subcaption{Profit - erC}
+\label{cztero}
+\end{minipage}
+\begin{minipage}{\linewidth}
+\centering
+\includegraphics[width=0.6\textwidth]{images/silverD.png}
+\subcaption{Profit - erD}
+\label{mansard}
+\end{minipage}
+\caption{SILVER market results}
+\end{figure}
+
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+\newpage
+\begin{table}[!t]
+\caption{Profits for all strategy quadrants for CADCHF}
+ \begin{center}
+ \begin{tabular}{|l|l|l|l|l|}
+ \hline \textbf{strategy} & \textbf{profit} & \textbf{bestCalmar} & \textbf{bestMALength} & \textbf{la} \\ \hline
+S1a & 17.19 & 8.24 & 18 & 2693\\ \hline
+S1b & -9.80 & -0.74 & 54 & 2665\\ \hline
+S1c & 5.65 & 2.06 & 54 & 2280\\ \hline
+S1d & 1.87 & 0.61 & 18 & 2287\\ \hline
+S1s & 14.85 & 5.68 & Group of MA & 4945\\
+\hline \end{tabular}
+ \end{center}
+ \end{table}
+\FloatBarrier
+\begin{figure}[h]
+\centering
+\begin{minipage}{\linewidth}
+\centering
+\includegraphics[width=0.6\textwidth]{images/cadchfS1a.png}
+\subcaption{Profit - S1a}
+\label{jedno}
+\end{minipage}
+\begin{minipage}{\linewidth}
+\centering
+\includegraphics[width=0.6\textwidth]{images/cadchfS1b.png}
+\subcaption{Profit - S1b}
+\label{dwu}
+\end{minipage}
+\\
+\begin{minipage}{\linewidth}
+\centering
+\includegraphics[width=0.6\textwidth]{images/cadchfS1c.png}
+\subcaption{Profit - S1c}
+\label{cztero}
+\end{minipage}
+\begin{minipage}{\linewidth}
+\centering
+\includegraphics[width=0.6\textwidth]{images/cadchfS1d.png}
+\subcaption{Profit - S1d}
+\label{mansard}
+\end{minipage}
+\begin{minipage}{.49\linewidth}
+\centering
+\includegraphics[width=0.82\textwidth]{images/cadchfS1s.png}
+\subcaption{Profit - S1s}
+\label{mansard}
+\end{minipage}
+\caption{CADCHF market results}
+\end{figure}
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+\newpage
+\begin{table}[!t]
+\caption{Profits for all strategy quadrants for FCOPPER}
+ \begin{center}
+ \begin{tabular}{|l|l|l|l|l|}
+ \hline \textbf{strategy} & \textbf{profit} & \textbf{bestCalmar} & \textbf{bestMALength} & \textbf{la} \\ \hline
+S1a & 17.19 & 8.24 & 18 & 2693\\ \hline
+S1b & -9.80 & -0.74 & 54 & 2665\\ \hline
+S1c & 5.65 & 2.06 & 54 & 2280\\ \hline
+S1d & 1.87 & 0.61 & 18 & 2287\\ \hline
+S1s & 14.85 & 5.68 & Group of MA & 4945\\
+\hline \end{tabular}
+ \end{center}
+ \end{table}
+\FloatBarrier
+\begin{figure}[h]
+\centering
+\begin{minipage}{\linewidth}
+\centering
+\includegraphics[width=0.6\textwidth]{images/fcopperS1a.png}
+\subcaption{Profit - S1a}
+\label{jedno}
+\end{minipage}
+\begin{minipage}{\linewidth}
+\centering
+\includegraphics[width=0.6\textwidth]{images/fcopperS1b.png}
+\subcaption{Profit - S1b}
+\label{dwu}
+\end{minipage}
+\\
+\begin{minipage}{\linewidth}
+\centering
+\includegraphics[width=0.6\textwidth]{images/fcopperS1c.png}
+\subcaption{Profit - S1c}
+\label{cztero}
+\end{minipage}
+\begin{minipage}{\linewidth}
+\centering
+\includegraphics[width=0.6\textwidth]{images/fcopperS1d.png}
+\subcaption{Profit - S1d}
+\label{mansard}
+\end{minipage}
+\begin{minipage}{.49\linewidth}
+\centering
+\includegraphics[width=0.82\textwidth]{images/fcopperS1s.png}
+\subcaption{Profit - S1s}
+\label{mansard}
+\end{minipage}
+\caption{FCOPPER market results}
+\end{figure}
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+\newpage
+\begin{table}[!t]
+\caption{Profits for all strategy quadrants for FCORN}
+ \begin{center}
+ \begin{tabular}{|l|l|l|l|l|}
+ \hline \textbf{strategy} & \textbf{profit} & \textbf{bestCalmar} & \textbf{bestMALength} & \textbf{la} \\ \hline
+S1a & 17.19 & 8.24 & 18 & 2693\\ \hline
+S1b & -9.80 & -0.74 & 54 & 2665\\ \hline
+S1c & 5.65 & 2.06 & 54 & 2280\\ \hline
+S1d & 1.87 & 0.61 & 18 & 2287\\ \hline
+S1s & 14.85 & 5.68 & Group of MA & 4945\\
+\hline \end{tabular}
+ \end{center}
+ \end{table}
+\FloatBarrier
+\begin{figure}[h]
+\centering
+\begin{minipage}{\linewidth}
+\centering
+\includegraphics[width=0.6\textwidth]{images/fcornS1a.png}
+\subcaption{Profit - S1a}
+\label{jedno}
+\end{minipage}
+\begin{minipage}{\linewidth}
+\centering
+\includegraphics[width=0.6\textwidth]{images/fcornS1b.png}
+\subcaption{Profit - S1b}
+\label{dwu}
+\end{minipage}
+\\
+\begin{minipage}{\linewidth}
+\centering
+\includegraphics[width=0.6\textwidth]{images/fcornS1c.png}
+\subcaption{Profit - S1c}
+\label{cztero}
+\end{minipage}
+\begin{minipage}{\linewidth}
+\centering
+\includegraphics[width=0.6\textwidth]{images/fcornS1d.png}
+\subcaption{Profit - S1d}
+\label{mansard}
+\end{minipage}
+\begin{minipage}{.49\linewidth}
+\centering
+\includegraphics[width=0.82\textwidth]{images/fcornS1s.png}
+\subcaption{Profit - S1s}
+\label{mansard}
+\end{minipage}
+\caption{FCORN market results}
+\end{figure}
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+\newpage
+\begin{table}[!t]
+\caption{Profits for all strategy quadrants for NZDJPY}
+ \begin{center}
+ \begin{tabular}{|l|l|l|l|l|}
+ \hline \textbf{strategy} & \textbf{profit} & \textbf{bestCalmar} & \textbf{bestMALength} & \textbf{la} \\ \hline
+S1a & 17.19 & 8.24 & 18 & 2693\\ \hline
+S1b & -9.80 & -0.74 & 54 & 2665\\ \hline
+S1c & 5.65 & 2.06 & 54 & 2280\\ \hline
+S1d & 1.87 & 0.61 & 18 & 2287\\ \hline
+S1s & 14.85 & 5.68 & Group of MA & 4945\\
+\hline \end{tabular}
+ \end{center}
+ \end{table}
+\FloatBarrier
+\begin{figure}[h]
+\centering
+\begin{minipage}{\linewidth}
+\centering
+\includegraphics[width=0.6\textwidth]{images/nzdjpyS1a.png}
+\subcaption{Profit - S1a}
+\label{jedno}
+\end{minipage}
+\begin{minipage}{\linewidth}
+\centering
+\includegraphics[width=0.6\textwidth]{images/nzdjpyS1b.png}
+\subcaption{Profit - S1b}
+\label{dwu}
+\end{minipage}
+\\
+\begin{minipage}{\linewidth}
+\centering
+\includegraphics[width=0.6\textwidth]{images/nzdjpyS1c.png}
+\subcaption{Profit - S1c}
+\label{cztero}
+\end{minipage}
+\begin{minipage}{\linewidth}
+\centering
+\includegraphics[width=0.6\textwidth]{images/nzdjpyS1d.png}
+\subcaption{Profit - S1d}
+\label{mansard}
+\end{minipage}
+\begin{minipage}{.49\linewidth}
+\centering
+\includegraphics[width=0.82\textwidth]{images/nzdjpyS1s.png}
+\subcaption{Profit - S1s}
+\label{mansard}
+\end{minipage}
+\caption{NZDJPY market results}
+\end{figure}
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+\newpage
+\begin{table}[!t]
+\caption{Profits for all strategy quadrants for USDCAD}
+ \begin{center}
+ \begin{tabular}{|l|l|l|l|l|}
+ \hline \textbf{strategy} & \textbf{profit} & \textbf{bestCalmar} & \textbf{bestMALength} & \textbf{la} \\ \hline
+S1a & 17.19 & 8.24 & 18 & 2693\\ \hline
+S1b & -9.80 & -0.74 & 54 & 2665\\ \hline
+S1c & 5.65 & 2.06 & 54 & 2280\\ \hline
+S1d & 1.87 & 0.61 & 18 & 2287\\ \hline
+S1s & 14.85 & 5.68 & Group of MA & 4945\\
+\hline \end{tabular}
+ \end{center}
+ \end{table}
+\FloatBarrier
+\begin{figure}[h]
+\centering
+\begin{minipage}{\linewidth}
+\centering
+\includegraphics[width=0.6\textwidth]{images/usdcadS1a.png}
+\subcaption{Profit - S1a}
+\label{jedno}
+\end{minipage}
+\begin{minipage}{\linewidth}
+\centering
+\includegraphics[width=0.6\textwidth]{images/usdcadS1b.png}
+\subcaption{Profit - S1b}
+\label{dwu}
+\end{minipage}
+\\
+\begin{minipage}{\linewidth}
+\centering
+\includegraphics[width=0.6\textwidth]{images/usdcadS1c.png}
+\subcaption{Profit - S1c}
+\label{cztero}
+\end{minipage}
+\begin{minipage}{\linewidth}
+\centering
+\includegraphics[width=0.6\textwidth]{images/usdcadS1d.png}
+\subcaption{Profit - S1d}
+\label{mansard}
+\end{minipage}
+\begin{minipage}{.49\linewidth}
+\centering
+\includegraphics[width=0.82\textwidth]{images/usdcadS1s.png}
+\subcaption{Profit - S1s}
+\label{mansard}
+\end{minipage}
+\caption{USDCAD market results}
+\end{figure}
+
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

### 2013-10-29 Article/book/generator/generator/generator/Form1.cs

@@ -18,13 +18,21 @@ namespace generator
             System.IO.Directory.CreateDirectory(outputFolder);
             System.IO.Directory.CreateDirectory(Path.Combine(outputFolder, "images"));
             var oneChartGeneratorMz = new ChartGenerator(outputFolder, "MZ");
-            var s = new System.Text.StringBuilder(); 
-            s.Append(oneChartGeneratorMz.Generate("cadchfS1{0}", "CADCHF"));
-            s.Append(oneChartGeneratorMz.Generate("fcopperS1{0}", "FCOPPER"));
-            s.Append(oneChartGeneratorMz.Generate("fcornS1{0}", "FCORN"));
-            s.Append(oneChartGeneratorMz.Generate("nzdjpyS1{0}", "NZDJPY"));
-            s.Append(oneChartGeneratorMz.Generate("usdcadS1{0}", "USDCAD"));
-            File.WriteAllText(Path.Combine(outputFolder, "MZ.tex"), s.ToString());
+            var builderMz = new System.Text.StringBuilder();
+            builderMz.Append(oneChartGeneratorMz.Generate("cadchfS1{0}", "CADCHF"));
+            builderMz.Append(oneChartGeneratorMz.Generate("fcopperS1{0}", "FCOPPER"));
+            builderMz.Append(oneChartGeneratorMz.Generate("fcornS1{0}", "FCORN"));
+            builderMz.Append(oneChartGeneratorMz.Generate("nzdjpyS1{0}", "NZDJPY"));
+            builderMz.Append(oneChartGeneratorMz.Generate("usdcadS1{0}", "USDCAD"));
+            File.WriteAllText(Path.Combine(outputFolder, "MZ.tex"), builderMz.ToString());
+            var oneChartGeneratorAb = new ChartGenerator(outputFolder, "AB");
+            var builderAb = new System.Text.StringBuilder();
+            builderAb.Append(oneChartGeneratorAb.Generate("chfjpy{0}", "CHFJPY"));
+            builderAb.Append(oneChartGeneratorAb.Generate("eurjpy{0}", "EURJPY"));
+            builderAb.Append(oneChartGeneratorAb.Generate("fus500{0}", "FUS500"));
+            builderAb.Append(oneChartGeneratorAb.Generate("gbpchf{0}", "GBPCHF"));
+            builderAb.Append(oneChartGeneratorAb.Generate("silver{0}", "SILVER"));
[…]

### 2013-10-29 Article/book/FormatProposal/tewi-paper-template.tex
book format proposal - latex tests

--- 2013-06-05 Article/Article20130603/tewi-paper-template.tex
@@
 
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+\newpage
+\begin{table}[!t]
+\caption{Profits for all strategy quadrants for CHFJPY}
+ \begin{center}
+ \begin{tabular}{|l|l|l|l|l|}
+ \hline \textbf{strategy} & \textbf{profit} & \textbf{bestCalmar} & \textbf{bestMALength} & \textbf{la} \\ \hline
+S1a & 17.19 & 8.24 & 18 & 2693\\ \hline
+S1b & -9.80 & -0.74 & 54 & 2665\\ \hline
+S1c & 5.65 & 2.06 & 54 & 2280\\ \hline
+S1d & 1.87 & 0.61 & 18 & 2287\\ \hline
+S1s & 14.85 & 5.68 & Group of MA & 4945\\
+\hline \end{tabular}
+ \end{center}
+ \end{table}
+\FloatBarrier
+\begin{figure}[h]
+\centering
+\begin{minipage}{\linewidth}
+\centering
+\includegraphics[width=0.49\textwidth]{images/chfjpyA.eps}
+\subcaption{Profit - pyA}
+\label{jedno}
+\end{minipage}
+\begin{minipage}{\linewidth}
+\centering
+\includegraphics[width=0.49\textwidth]{images/chfjpyB.eps}
+\subcaption{Profit - pyB}
+\label{dwu}
+\end{minipage}
+\\
+\begin{minipage}{\linewidth}
+\centering
+\includegraphics[width=0.49\textwidth]{images/chfjpyC.eps}
+\subcaption{Profit - pyC}
+\label{cztero}
+\end{minipage}
+\begin{minipage}{\linewidth}
+\centering
+\includegraphics[width=0.49\textwidth]{images/chfjpyD.eps}
+\subcaption{Profit - pyD}
+\label{mansard}
+\end{minipage}
+\begin{minipage}{\linewidth}
+\centering 
+\includegraphics[width=0.6\textwidth]{images/chfjpyD.eps}
+\label{mansard}
+\subcaption{Profit - S1s}
+\end{minipage}
+\caption{CHFJPY market results}
+\end{figure}
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+\newpage
+\begin{table}[!t]
+\caption{Profits for all strategy quadrants for EURJPY}
+ \begin{center}
+ \begin{tabular}{|l|l|l|l|l|}
+ \hline \textbf{strategy} & \textbf{profit} & \textbf{bestCalmar} & \textbf{bestMALength} & \textbf{la} \\ \hline
+S1a & 17.19 & 8.24 & 18 & 2693\\ \hline
+S1b & -9.80 & -0.74 & 54 & 2665\\ \hline
+S1c & 5.65 & 2.06 & 54 & 2280\\ \hline
+S1d & 1.87 & 0.61 & 18 & 2287\\ \hline
+S1s & 14.85 & 5.68 & Group of MA & 4945\\
+\hline \end{tabular}
+ \end{center}
+ \end{table}
+\FloatBarrier
+\begin{figure}[h]
+\centering
+\begin{minipage}{\linewidth}
+\centering
+\includegraphics[width=0.49\textwidth]{images/eurjpyA.eps}
+\subcaption{Profit - pyA}
+\label{jedno}
+\end{minipage}
+\begin{minipage}{\linewidth}
+\centering
+\includegraphics[width=0.49\textwidth]{images/eurjpyB.eps}
+\subcaption{Profit - pyB}
+\label{dwu}
+\end{minipage}
+\\
+\begin{minipage}{\linewidth}
+\centering
+\includegraphics[width=0.49\textwidth]{images/eurjpyC.eps}
+\subcaption{Profit - pyC}
+\label{cztero}
+\end{minipage}
+\begin{minipage}{\linewidth}
+\centering
+\includegraphics[width=0.49\textwidth]{images/eurjpyD.eps}
+\subcaption{Profit - pyD}
+\label{mansard}
+\end{minipage}
+\begin{minipage}{\linewidth}
+\centering
+\includegraphics[width=0.6\textwidth]{images/eurjpyD.eps}
+\subcaption{Profit - pyD}
+\label{mansard}
+\end{minipage}
+\caption{EURJPY market results}
+\end{figure}
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+\newpage
+\begin{table}[!t]
+\caption{Profits for all strategy quadrants for FUS500}
+ \begin{center}
+ \begin{tabular}{|l|l|l|l|l|}
+ \hline \textbf{strategy} & \textbf{profit} & \textbf{bestCalmar} & \textbf{bestMALength} & \textbf{la} \\ \hline
+S1a & 17.19 & 8.24 & 18 & 2693\\ \hline
+S1b & -9.80 & -0.74 & 54 & 2665\\ \hline
+S1c & 5.65 & 2.06 & 54 & 2280\\ \hline
+S1d & 1.87 & 0.61 & 18 & 2287\\ \hline
+S1s & 14.85 & 5.68 & Group of MA & 4945\\
+\hline \end{tabular}
+ \end{center}
+ \end{table}
+\FloatBarrier
+\begin{figure}[h]
+\centering
+\begin{minipage}{\linewidth}
+\centering
+\includegraphics[width=0.6\textwidth]{images/fus500A.eps}
+\subcaption{Profit - 00A}
+\label{jedno}
+\end{minipage}
+\begin{minipage}{\linewidth}
+\centering
+\includegraphics[width=0.6\textwidth]{images/fus500B.eps}
+\subcaption{Profit - 00B}
+\label{dwu}
+\end{minipage}
+\\
+\begin{minipage}{\linewidth}
+\centering
+\includegraphics[width=0.6\textwidth]{images/fus500C.eps}
+\subcaption{Profit - 00C}
+\label{cztero}
+\end{minipage}
+\begin{minipage}{\linewidth}
+\centering
+\includegraphics[width=0.6\textwidth]{images/fus500D.eps}
+\subcaption{Profit - 00D}
+\label{mansard}
+\end{minipage}
+\caption{FUS500 market results}
+\end{figure}
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+\newpage
+\begin{table}[!t]
+\caption{Profits for all strategy quadrants for GBPCHF}
+ \begin{center}
+ \begin{tabular}{|l|l|l|l|l|}
+ \hline \textbf{strategy} & \textbf{profit} & \textbf{bestCalmar} & \textbf{bestMALength} & \textbf{la} \\ \hline
+S1a & 17.19 & 8.24 & 18 & 2693\\ \hline
+S1b & -9.80 & -0.74 & 54 & 2665\\ \hline
+S1c & 5.65 & 2.06 & 54 & 2280\\ \hline
+S1d & 1.87 & 0.61 & 18 & 2287\\ \hline
+S1s & 14.85 & 5.68 & Group of MA & 4945\\
+\hline \end{tabular}
+ \end{center}
+ \end{table}
+\FloatBarrier
+\begin{figure}[h]
+\centering
+\begin{minipage}{\linewidth}
+\centering
+\includegraphics[width=0.6\textwidth]{images/gbpchfA.eps}
+\subcaption{Profit - hfA}
+\label{jedno}
+\end{minipage}
+\begin{minipage}{\linewidth}
+\centering
+\includegraphics[width=0.6\textwidth]{images/gbpchfB.eps}
+\subcaption{Profit - hfB}
+\label{dwu}
+\end{minipage}
+\\
+\begin{minipage}{\linewidth}
+\centering
+\includegraphics[width=0.6\textwidth]{images/gbpchfC.eps}
+\subcaption{Profit - hfC}
+\label{cztero}
+\end{minipage}
+\begin{minipage}{\linewidth}
+\centering
+\includegraphics[width=0.6\textwidth]{images/gbpchfD.eps}
+\subcaption{Profit - hfD}
+\label{mansard}
+\end{minipage}
+\caption{GBPCHF market results}
+\end{figure}
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+\newpage
+\begin{table}[!t]
+\caption{Profits for all strategy quadrants for SILVER}
+ \begin{center}
+ \begin{tabular}{|l|l|l|l|l|}
+ \hline \textbf{strategy} & \textbf{profit} & \textbf{bestCalmar} & \textbf{bestMALength} & \textbf{la} \\ \hline
+S1a & 17.19 & 8.24 & 18 & 2693\\ \hline
+S1b & -9.80 & -0.74 & 54 & 2665\\ \hline
+S1c & 5.65 & 2.06 & 54 & 2280\\ \hline
+S1d & 1.87 & 0.61 & 18 & 2287\\ \hline
+S1s & 14.85 & 5.68 & Group of MA & 4945\\
+\hline \end{tabular}
+ \end{center}
+ \end{table}
+\FloatBarrier
+\begin{figure}[h]
+\centering
+\begin{minipage}{\linewidth}
+\centering
+\includegraphics[width=0.6\textwidth]{images/silverA.eps}
+\subcaption{Profit - erA}
+\label{jedno}
+\end{minipage}
+\begin{minipage}{\linewidth}
+\centering
+\includegraphics[width=0.6\textwidth]{images/silverB.eps}
+\subcaption{Profit - erB}
+\label{dwu}
+\end{minipage}
+\\
+\begin{minipage}{\linewidth}
+\centering
+\includegraphics[width=0.6\textwidth]{images/silverC.eps}
+\subcaption{Profit - erC}
+\label{cztero}
+\end{minipage}
+\begin{minipage}{\linewidth}
+\centering
+\includegraphics[width=0.6\textwidth]{images/silverD.eps}
+\subcaption{Profit - erD}
+\label{mansard}
+\end{minipage}
+\caption{SILVER market results}
+\end{figure}
+
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+\newpage
+\begin{table}[!t]
+\caption{Profits for all strategy quadrants for CADCHF}
+ \begin{center}
+ \begin{tabular}{|l|l|l|l|l|}
+ \hline \textbf{strategy} & \textbf{profit} & \textbf{bestCalmar} & \textbf{bestMALength} & \textbf{la} \\ \hline
+S1a & 17.19 & 8.24 & 18 & 2693\\ \hline
+S1b & -9.80 & -0.74 & 54 & 2665\\ \hline
+S1c & 5.65 & 2.06 & 54 & 2280\\ \hline
+S1d & 1.87 & 0.61 & 18 & 2287\\ \hline
+S1s & 14.85 & 5.68 & Group of MA & 4945\\
+\hline \end{tabular}
+ \end{center}
+ \end{table}
+\FloatBarrier
+\begin{figure}[h]
+\centering
+\begin{minipage}{\linewidth}
+\centering
+\includegraphics[width=0.6\textwidth]{images/cadchfS1a.eps}
+\subcaption{Profit - S1a}
+\label{jedno}
+\end{minipage}
+\begin{minipage}{\linewidth}
+\centering
+\includegraphics[width=0.6\textwidth]{images/cadchfS1b.eps}
+\subcaption{Profit - S1b}
+\label{dwu}
+\end{minipage}
+\\
+\begin{minipage}{\linewidth}
+\centering
+\includegraphics[width=0.6\textwidth]{images/cadchfS1c.eps}
+\subcaption{Profit - S1c}
+\label{cztero}
+\end{minipage}
+\begin{minipage}{\linewidth}
+\centering
+\includegraphics[width=0.6\textwidth]{images/cadchfS1d.eps}
+\subcaption{Profit - S1d}
+\label{mansard}
+\end{minipage}
+\begin{minipage}{.49\linewidth}
+\centering
+\includegraphics[width=0.82\textwidth]{images/cadchfS1s.eps}
+\subcaption{Profit - S1s}
+\label{mansard}
+\end{minipage}
+\caption{CADCHF market results}
+\end{figure}
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+\newpage
+\begin{table}[!t]
+\caption{Profits for all strategy quadrants for FCOPPER}
+ \begin{center}
+ \begin{tabular}{|l|l|l|l|l|}
+ \hline \textbf{strategy} & \textbf{profit} & \textbf{bestCalmar} & \textbf{bestMALength} & \textbf{la} \\ \hline
+S1a & 17.19 & 8.24 & 18 & 2693\\ \hline
+S1b & -9.80 & -0.74 & 54 & 2665\\ \hline
+S1c & 5.65 & 2.06 & 54 & 2280\\ \hline
+S1d & 1.87 & 0.61 & 18 & 2287\\ \hline
+S1s & 14.85 & 5.68 & Group of MA & 4945\\
+\hline \end{tabular}
+ \end{center}
+ \end{table}
+\FloatBarrier
+\begin{figure}[h]
+\centering
+\begin{minipage}{\linewidth}
+\centering
+\includegraphics[width=0.6\textwidth]{images/fcopperS1a.eps}
+\subcaption{Profit - S1a}
+\label{jedno}
+\end{minipage}
+\begin{minipage}{\linewidth}
+\centering
+\includegraphics[width=0.6\textwidth]{images/fcopperS1b.eps}
+\subcaption{Profit - S1b}
+\label{dwu}
+\end{minipage}
+\\
+\begin{minipage}{\linewidth}
+\centering
+\includegraphics[width=0.6\textwidth]{images/fcopperS1c.eps}
+\subcaption{Profit - S1c}
+\label{cztero}
+\end{minipage}
+\begin{minipage}{\linewidth}
+\centering
+\includegraphics[width=0.6\textwidth]{images/fcopperS1d.eps}
+\subcaption{Profit - S1d}
+\label{mansard}
+\end{minipage}
+\begin{minipage}{.49\linewidth}
+\centering
+\includegraphics[width=0.82\textwidth]{images/fcopperS1s.eps}
+\subcaption{Profit - S1s}
+\label{mansard}
+\end{minipage}
+\caption{FCOPPER market results}
+\end{figure}
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+\newpage
+\begin{table}[!t]
+\caption{Profits for all strategy quadrants for FCORN}
+ \begin{center}
+ \begin{tabular}{|l|l|l|l|l|}
+ \hline \textbf{strategy} & \textbf{profit} & \textbf{bestCalmar} & \textbf{bestMALength} & \textbf{la} \\ \hline
+S1a & 17.19 & 8.24 & 18 & 2693\\ \hline
+S1b & -9.80 & -0.74 & 54 & 2665\\ \hline
+S1c & 5.65 & 2.06 & 54 & 2280\\ \hline
+S1d & 1.87 & 0.61 & 18 & 2287\\ \hline
+S1s & 14.85 & 5.68 & Group of MA & 4945\\
+\hline \end{tabular}
+ \end{center}
+ \end{table}
+\FloatBarrier
+\begin{figure}[h]
+\centering
+\begin{minipage}{\linewidth}
+\centering
+\includegraphics[width=0.6\textwidth]{images/fcornS1a.eps}
+\subcaption{Profit - S1a}
+\label{jedno}
+\end{minipage}
+\begin{minipage}{\linewidth}
+\centering
+\includegraphics[width=0.6\textwidth]{images/fcornS1b.eps}
+\subcaption{Profit - S1b}
+\label{dwu}
+\end{minipage}
+\\
+\begin{minipage}{\linewidth}
+\centering
+\includegraphics[width=0.6\textwidth]{images/fcornS1c.eps}
+\subcaption{Profit - S1c}
+\label{cztero}
+\end{minipage}
+\begin{minipage}{\linewidth}
+\centering
+\includegraphics[width=0.6\textwidth]{images/fcornS1d.eps}
+\subcaption{Profit - S1d}
+\label{mansard}
+\end{minipage}
+\begin{minipage}{.49\linewidth}
+\centering
+\includegraphics[width=0.82\textwidth]{images/fcornS1s.eps}
+\subcaption{Profit - S1s}
+\label{mansard}
+\end{minipage}
+\caption{FCORN market results}
+\end{figure}
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+\newpage
+\begin{table}[!t]
+\caption{Profits for all strategy quadrants for NZDJPY}
+ \begin{center}
+ \begin{tabular}{|l|l|l|l|l|}
+ \hline \textbf{strategy} & \textbf{profit} & \textbf{bestCalmar} & \textbf{bestMALength} & \textbf{la} \\ \hline
+S1a & 17.19 & 8.24 & 18 & 2693\\ \hline
+S1b & -9.80 & -0.74 & 54 & 2665\\ \hline
+S1c & 5.65 & 2.06 & 54 & 2280\\ \hline
+S1d & 1.87 & 0.61 & 18 & 2287\\ \hline
+S1s & 14.85 & 5.68 & Group of MA & 4945\\
+\hline \end{tabular}
+ \end{center}
+ \end{table}
+\FloatBarrier
+\begin{figure}[h]
+\centering
+\begin{minipage}{\linewidth}
+\centering
+\includegraphics[width=0.6\textwidth]{images/nzdjpyS1a.eps}
+\subcaption{Profit - S1a}
+\label{jedno}
+\end{minipage}
+\begin{minipage}{\linewidth}
+\centering
+\includegraphics[width=0.6\textwidth]{images/nzdjpyS1b.eps}
+\subcaption{Profit - S1b}
+\label{dwu}
+\end{minipage}
+\\
+\begin{minipage}{\linewidth}
+\centering
+\includegraphics[width=0.6\textwidth]{images/nzdjpyS1c.eps}
+\subcaption{Profit - S1c}
+\label{cztero}
+\end{minipage}
+\begin{minipage}{\linewidth}
+\centering
+\includegraphics[width=0.6\textwidth]{images/nzdjpyS1d.eps}
+\subcaption{Profit - S1d}
+\label{mansard}
+\end{minipage}
+\begin{minipage}{.49\linewidth}
+\centering
+\includegraphics[width=0.82\textwidth]{images/nzdjpyS1s.eps}
+\subcaption{Profit - S1s}
+\label{mansard}
+\end{minipage}
+\caption{NZDJPY market results}
+\end{figure}
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+\newpage
+\begin{table}[!t]
+\caption{Profits for all strategy quadrants for USDCAD}
+ \begin{center}
+ \begin{tabular}{|l|l|l|l|l|}
+ \hline \textbf{strategy} & \textbf{profit} & \textbf{bestCalmar} & \textbf{bestMALength} & \textbf{la} \\ \hline
+S1a & 17.19 & 8.24 & 18 & 2693\\ \hline
+S1b & -9.80 & -0.74 & 54 & 2665\\ \hline
+S1c & 5.65 & 2.06 & 54 & 2280\\ \hline
+S1d & 1.87 & 0.61 & 18 & 2287\\ \hline
+S1s & 14.85 & 5.68 & Group of MA & 4945\\
+\hline \end{tabular}
+ \end{center}
+ \end{table}
+\FloatBarrier
+\begin{figure}[h]
+\centering
+\begin{minipage}{\linewidth}
+\centering
+\includegraphics[width=0.6\textwidth]{images/usdcadS1a.eps}
+\subcaption{Profit - S1a}
+\label{jedno}
+\end{minipage}
+\begin{minipage}{\linewidth}
+\centering
+\includegraphics[width=0.6\textwidth]{images/usdcadS1b.eps}
+\subcaption{Profit - S1b}
+\label{dwu}
+\end{minipage}
+\\
+\begin{minipage}{\linewidth}
+\centering
+\includegraphics[width=0.6\textwidth]{images/usdcadS1c.eps}
+\subcaption{Profit - S1c}
+\label{cztero}
+\end{minipage}
+\begin{minipage}{\linewidth}
+\centering
+\includegraphics[width=0.6\textwidth]{images/usdcadS1d.eps}
+\subcaption{Profit - S1d}
+\label{mansard}
+\end{minipage}
+\begin{minipage}{.49\linewidth}
+\centering
+\includegraphics[width=0.82\textwidth]{images/usdcadS1s.eps}
+\subcaption{Profit - S1s}
+\label{mansard}
+\end{minipage}
+\caption{USDCAD market results}
+\end{figure}
+
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

### 2013-10-29 Article/book/generator/generator/generator/Form1.cs
book generator - one main file

@@ -1,4 +1,5 @@
 ﻿using System;
+using System.Text;
 using System.Windows.Forms;
 using System.IO;
 using generator.Properties;
@@ -33,6 +34,10 @@ namespace generator
             builderAb.Append(oneChartGeneratorAb.Generate("gbpchf{0}", "GBPCHF"));
             builderAb.Append(oneChartGeneratorAb.Generate("silver{0}", "SILVER"));
             File.WriteAllText(Path.Combine(outputFolder, "AB.tex"), builderAb.ToString());
+            StringBuilder allContent = new StringBuilder();
+            allContent.Append(File.ReadAllText("MZ.txt"));
+            allContent.Append(File.ReadAllText("AB.txt"));
+            File.WriteAllText(Path.Combine(outputFolder, "MAIN.tex"), allContent.ToString());
             toolStripStatusLabel1.Text = Resources.btnGenerateClickGenerated;
         }
     }

### 2013-10-29 Article/book/generator/generator/generator/Form1.cs
book generator - one main file - extracted

@@ -34,11 +34,18 @@ namespace generator
             builderAb.Append(oneChartGeneratorAb.Generate("gbpchf{0}", "GBPCHF"));
             builderAb.Append(oneChartGeneratorAb.Generate("silver{0}", "SILVER"));
             File.WriteAllText(Path.Combine(outputFolder, "AB.tex"), builderAb.ToString());
-            StringBuilder allContent = new StringBuilder();
-            allContent.Append(File.ReadAllText("MZ.txt"));
-            allContent.Append(File.ReadAllText("AB.txt"));
-            File.WriteAllText(Path.Combine(outputFolder, "MAIN.tex"), allContent.ToString());
+            WriteMainFile(outputFolder, "MZ;AB");
             toolStripStatusLabel1.Text = Resources.btnGenerateClickGenerated;
+        }
+
+        private static void WriteMainFile(string outputFolder, string initials )
+        {
+            StringBuilder allContent = new StringBuilder();
+            foreach (var initial in initials.Split(new char[] {';'}))
+            {
+                allContent.Append(File.ReadAllText(Path.Combine(outputFolder, initial + ".tex")));
+            }
+            File.WriteAllText(Path.Combine(outputFolder, "MAIN.tex"), allContent.ToString());
         }
     }
 }

### 2013-10-29 Article/book/generator/generator/generator/ChartGenerator.cs
book generator - pictures format

@@ -44,13 +44,13 @@ namespace generator
                 writer.WriteLine(@"\begin{figure}[h]");
                 writer.WriteLine(@"\centering");
                 var loopIndex = 0;
-                foreach (var pictureFile in Directory.GetFiles(authorInitials, string.Format(filenameFormat + ".png", "*")))
+                foreach (var pictureFile in Directory.GetFiles(authorInitials, string.Format(filenameFormat + ".eps", "*")))
                 {
                     writer.WriteLine(loopIndex == 4
-                                         ? @"\begin{minipage}{.49\linewidth}"
-                                         : @"\begin{minipage}{\linewidth}");
+                                         ? @"\begin{minipage}{\linewidth}"
+                                         : @"\begin{minipage}{.49\linewidth}");
                     writer.WriteLine(@"\centering");
-                    var widthValue = (loopIndex == 4) ? "0.82" : "0.6";
+                    var widthValue = (loopIndex == 4) ? "0.6" : "0.82";
                     writer.WriteLine(@"\includegraphics[width=" + widthValue + @"\textwidth]{images/" + Path.GetFileName(pictureFile) + "}");
                     writer.WriteLine(@"\subcaption{Profit - " + pictureFile.Substring(variantNamePlace, 3) + "}");
                     writer.WriteLine(@"\label{" + labels[loopIndex]  + "}");
@@ -62,6 +62,7 @@ namespace generator
                 }
                 writer.WriteLine(@"\caption{" + marketName  + " market results}");
                 writer.WriteLine(@"\end{figure}");
+                writer.WriteLine(@"\FloatBarrier");
             }
             return File.ReadAllText(texFilePath);
         }

### 2013-10-29 Article/book/FormatProposal/tewi-paper-template.tex
book format proposal - latex tests

--- 2013-06-05 Article/Article20130603/tewi-paper-template.tex
@@
 
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+\newpage
+\begin{table}[!t]
+\caption{Profits for all strategy quadrants for CADCHF}
+ \begin{center}
+ \begin{tabular}{|l|l|l|l|l|}
+ \hline \textbf{strategy} & \textbf{profit} & \textbf{bestCalmar} & \textbf{bestMALength} & \textbf{la} \\ \hline
+S1a & 17.19 & 8.24 & 18 & 2693\\ \hline
+S1b & -9.80 & -0.74 & 54 & 2665\\ \hline
+S1c & 5.65 & 2.06 & 54 & 2280\\ \hline
+S1d & 1.87 & 0.61 & 18 & 2287\\ \hline
+S1s & 14.85 & 5.68 & Group of MA & 4945\\
+\hline \end{tabular}
+ \end{center}
+ \end{table}
+\FloatBarrier
+
+\begin{figure}[h]
+\centering
+\begin{minipage}{.49\linewidth}
+\centering
+\includegraphics[width=0.82\textwidth]{images/cadchfS1a.eps}
+\subcaption{Profit - S1a}
+\label{jedno}
+\end{minipage}
+\begin{minipage}{.49\linewidth}
+\centering
+\includegraphics[width=0.82\textwidth]{images/cadchfS1b.eps}
+\subcaption{Profit - S1b}
+\label{dwu}
+\end{minipage}
+\\
+\begin{minipage}{.49\linewidth}
+\centering
+\includegraphics[width=0.82\textwidth]{images/cadchfS1c.eps}
+\subcaption{Profit - S1c}
+\label{cztero}
+\end{minipage}
+\begin{minipage}{.49\linewidth}
+\centering
+\includegraphics[width=0.82\textwidth]{images/cadchfS1d.eps}
+\subcaption{Profit - S1d}
+\label{mansard}
+\end{minipage}
+\begin{minipage}{\linewidth}
+\centering
+\includegraphics[width=0.6\textwidth]{images/cadchfS1s.eps}
+\label{mansard}
+\subcaption{Profit - S1s}
+\end{minipage}
+\caption{CADCHF market results}
+\end{figure}
+\FloatBarrier
+
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+\newpage
+\begin{table}[!t]
+\caption{Profits for all strategy quadrants for FCOPPER}
+ \begin{center}
+ \begin{tabular}{|l|l|l|l|l|}
+ \hline \textbf{strategy} & \textbf{profit} & \textbf{bestCalmar} & \textbf{bestMALength} & \textbf{la} \\ \hline
+S1a & 17.19 & 8.24 & 18 & 2693\\ \hline
+S1b & -9.80 & -0.74 & 54 & 2665\\ \hline
+S1c & 5.65 & 2.06 & 54 & 2280\\ \hline
+S1d & 1.87 & 0.61 & 18 & 2287\\ \hline
+S1s & 14.85 & 5.68 & Group of MA & 4945\\
+\hline \end{tabular}
+ \end{center}
+ \end{table}
+\FloatBarrier
+\begin{figure}[h]
+\centering
+\begin{minipage}{.49\linewidth}
+\centering
+\includegraphics[width=0.82\textwidth]{images/fcopperS1a.eps}
+\subcaption{Profit - S1a}
+\label{jedno}
+\end{minipage}
+\begin{minipage}{.49\linewidth}
+\centering
+\includegraphics[width=0.82\textwidth]{images/fcopperS1b.eps}
+\subcaption{Profit - S1b}
+\label{dwu}
+\end{minipage}
+\\
+\begin{minipage}{.49\linewidth}
+\centering
+\includegraphics[width=0.82\textwidth]{images/fcopperS1c.eps}
+\subcaption{Profit - S1c}
+\label{cztero}
+\end{minipage}
+\begin{minipage}{.49\linewidth}
+\centering
+\includegraphics[width=0.82\textwidth]{images/fcopperS1d.eps}
+\subcaption{Profit - S1d}
+\label{mansard}
+\end{minipage}
+\begin{minipage}{\linewidth}
+\centering
+\includegraphics[width=0.6\textwidth]{images/fcopperS1s.eps}
+\subcaption{Profit - S1s}
+\label{mansard}
+\end{minipage}
+\caption{FCOPPER market results}
+\end{figure}
+\FloatBarrier
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+\newpage
+\begin{table}[!t]
+\caption{Profits for all strategy quadrants for FCORN}
+ \begin{center}
+ \begin{tabular}{|l|l|l|l|l|}
+ \hline \textbf{strategy} & \textbf{profit} & \textbf{bestCalmar} & \textbf{bestMALength} & \textbf{la} \\ \hline
+S1a & 17.19 & 8.24 & 18 & 2693\\ \hline
+S1b & -9.80 & -0.74 & 54 & 2665\\ \hline
+S1c & 5.65 & 2.06 & 54 & 2280\\ \hline
+S1d & 1.87 & 0.61 & 18 & 2287\\ \hline
+S1s & 14.85 & 5.68 & Group of MA & 4945\\
+\hline \end{tabular}
+ \end{center}
+ \end{table}
+\FloatBarrier
+\begin{figure}[h]
+\centering
+\begin{minipage}{.49\linewidth}
+\centering
+\includegraphics[width=0.82\textwidth]{images/fcornS1a.eps}
+\subcaption{Profit - S1a}
+\label{jedno}
+\end{minipage}
+\begin{minipage}{.49\linewidth}
+\centering
+\includegraphics[width=0.82\textwidth]{images/fcornS1b.eps}
+\subcaption{Profit - S1b}
+\label{dwu}
+\end{minipage}
+\\
+\begin{minipage}{.49\linewidth}
+\centering
+\includegraphics[width=0.82\textwidth]{images/fcornS1c.eps}
+\subcaption{Profit - S1c}
+\label{cztero}
+\end{minipage}
+\begin{minipage}{.49\linewidth}
+\centering
+\includegraphics[width=0.82\textwidth]{images/fcornS1d.eps}
+\subcaption{Profit - S1d}
+\label{mansard}
+\end{minipage}
+\begin{minipage}{\linewidth}
+\centering
+\includegraphics[width=0.6\textwidth]{images/fcornS1s.eps}
+\subcaption{Profit - S1s}
+\label{mansard}
+\end{minipage}
+\caption{FCORN market results}
+\end{figure}
+\FloatBarrier
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+\newpage
+\begin{table}[!t]
+\caption{Profits for all strategy quadrants for NZDJPY}
+ \begin{center}
+ \begin{tabular}{|l|l|l|l|l|}
+ \hline \textbf{strategy} & \textbf{profit} & \textbf{bestCalmar} & \textbf{bestMALength} & \textbf{la} \\ \hline
+S1a & 17.19 & 8.24 & 18 & 2693\\ \hline
+S1b & -9.80 & -0.74 & 54 & 2665\\ \hline
+S1c & 5.65 & 2.06 & 54 & 2280\\ \hline
+S1d & 1.87 & 0.61 & 18 & 2287\\ \hline
+S1s & 14.85 & 5.68 & Group of MA & 4945\\
+\hline \end{tabular}
+ \end{center}
+ \end{table}
+\FloatBarrier
+\begin{figure}[h]
+\centering
+\begin{minipage}{.49\linewidth}
+\centering
+\includegraphics[width=0.82\textwidth]{images/nzdjpyS1a.eps}
+\subcaption{Profit - S1a}
+\label{jedno}
+\end{minipage}
+\begin{minipage}{.49\linewidth}
+\centering
+\includegraphics[width=0.82\textwidth]{images/nzdjpyS1b.eps}
+\subcaption{Profit - S1b}
+\label{dwu}
+\end{minipage}
+\\
+\begin{minipage}{.49\linewidth}
+\centering
+\includegraphics[width=0.82\textwidth]{images/nzdjpyS1c.eps}
+\subcaption{Profit - S1c}
+\label{cztero}
+\end{minipage}
+\begin{minipage}{.49\linewidth}
+\centering
+\includegraphics[width=0.82\textwidth]{images/nzdjpyS1d.eps}
+\subcaption{Profit - S1d}
+\label{mansard}
+\end{minipage}
+\begin{minipage}{\linewidth}
+\centering
+\includegraphics[width=0.6\textwidth]{images/nzdjpyS1s.eps}
+\subcaption{Profit - S1s}
+\label{mansard}
+\end{minipage}
+\caption{NZDJPY market results}
+\end{figure}
+\FloatBarrier
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+\newpage
+\begin{table}[!t]
+\caption{Profits for all strategy quadrants for USDCAD}
+ \begin{center}
+ \begin{tabular}{|l|l|l|l|l|}
+ \hline \textbf{strategy} & \textbf{profit} & \textbf{bestCalmar} & \textbf{bestMALength} & \textbf{la} \\ \hline
+S1a & 17.19 & 8.24 & 18 & 2693\\ \hline
+S1b & -9.80 & -0.74 & 54 & 2665\\ \hline
+S1c & 5.65 & 2.06 & 54 & 2280\\ \hline
+S1d & 1.87 & 0.61 & 18 & 2287\\ \hline
+S1s & 14.85 & 5.68 & Group of MA & 4945\\
+\hline \end{tabular}
+ \end{center}
+ \end{table}
+\FloatBarrier
+\begin{figure}[h]
+\centering
+\begin{minipage}{.49\linewidth}
+\centering
+\includegraphics[width=0.82\textwidth]{images/usdcadS1a.eps}
+\subcaption{Profit - S1a}
+\label{jedno}
+\end{minipage}
+\begin{minipage}{.49\linewidth}
+\centering
+\includegraphics[width=0.82\textwidth]{images/usdcadS1b.eps}
+\subcaption{Profit - S1b}
+\label{dwu}
+\end{minipage}
+\\
+\begin{minipage}{.49\linewidth}
+\centering
+\includegraphics[width=0.82\textwidth]{images/usdcadS1c.eps}
+\subcaption{Profit - S1c}
+\label{cztero}
+\end{minipage}
+\begin{minipage}{.49\linewidth}
+\centering
+\includegraphics[width=0.82\textwidth]{images/usdcadS1d.eps}
+\subcaption{Profit - S1d}
+\label{mansard}
+\end{minipage}
+\begin{minipage}{\linewidth}
+\centering
+\includegraphics[width=0.6\textwidth]{images/usdcadS1s.eps}
+\subcaption{Profit - S1s}
+\label{mansard}
+\end{minipage}
+\caption{USDCAD market results}
+\end{figure}
+\FloatBarrier
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+\newpage
+\begin{table}[!t]
+\caption{Profits for all strategy quadrants for CHFJPY}
+ \begin{center}
+ \begin{tabular}{|l|l|l|l|l|}
+ \hline \textbf{strategy} & \textbf{profit} & \textbf{bestCalmar} & \textbf{bestMALength} & \textbf{la} \\ \hline
+S1a & 17.19 & 8.24 & 18 & 2693\\ \hline
+S1b & -9.80 & -0.74 & 54 & 2665\\ \hline
+S1c & 5.65 & 2.06 & 54 & 2280\\ \hline
+S1d & 1.87 & 0.61 & 18 & 2287\\ \hline
+S1s & 14.85 & 5.68 & Group of MA & 4945\\
+\hline \end{tabular}
+ \end{center}
+ \end{table}
+\FloatBarrier
+\begin{figure}[h]
+\centering
+\begin{minipage}{.49\linewidth}
+\centering
+\includegraphics[width=0.82\textwidth]{images/chfjpyA.eps}
+\subcaption{Profit - pyA}
+\label{jedno}
+\end{minipage}
+\begin{minipage}{.49\linewidth}
+\centering
+\includegraphics[width=0.82\textwidth]{images/chfjpyB.eps}
+\subcaption{Profit - pyB}
+\label{dwu}
+\end{minipage}
+\\
+\begin{minipage}{.49\linewidth}
+\centering
+\includegraphics[width=0.82\textwidth]{images/chfjpyC.eps}
+\subcaption{Profit - pyC}
+\label{cztero}
+\end{minipage}
+\begin{minipage}{.49\linewidth}
+\centering
+\includegraphics[width=0.82\textwidth]{images/chfjpyD.eps}
+\subcaption{Profit - pyD}
+\label{mansard}
+\end{minipage}
+\begin{minipage}{\linewidth}
+\centering
+\includegraphics[width=0.6\textwidth]{images/chfjpyS.eps}
+\subcaption{Profit - pyS}
+\label{mansard}
+\end{minipage}
+\caption{CHFJPY market results}
+\end{figure}
+\FloatBarrier
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+\newpage
+\begin{table}[!t]
+\caption{Profits for all strategy quadrants for EURJPY}
+ \begin{center}
+ \begin{tabular}{|l|l|l|l|l|}
+ \hline \textbf{strategy} & \textbf{profit} & \textbf{bestCalmar} & \textbf{bestMALength} & \textbf{la} \\ \hline
+S1a & 17.19 & 8.24 & 18 & 2693\\ \hline
+S1b & -9.80 & -0.74 & 54 & 2665\\ \hline
+S1c & 5.65 & 2.06 & 54 & 2280\\ \hline
+S1d & 1.87 & 0.61 & 18 & 2287\\ \hline
+S1s & 14.85 & 5.68 & Group of MA & 4945\\
+\hline \end{tabular}
+ \end{center}
+ \end{table}
+\FloatBarrier
+\begin{figure}[h]
+\centering
+\begin{minipage}{.49\linewidth}
+\centering
+\includegraphics[width=0.82\textwidth]{images/eurjpyA.eps}
+\subcaption{Profit - pyA}
+\label{jedno}
+\end{minipage}
+\begin{minipage}{.49\linewidth}
+\centering
+\includegraphics[width=0.82\textwidth]{images/eurjpyB.eps}
+\subcaption{Profit - pyB}
+\label{dwu}
+\end{minipage}
+\\
+\begin{minipage}{.49\linewidth}
+\centering
+\includegraphics[width=0.82\textwidth]{images/eurjpyC.eps}
+\subcaption{Profit - pyC}
+\label{cztero}
+\end{minipage}
+\begin{minipage}{.49\linewidth}
+\centering
+\includegraphics[width=0.82\textwidth]{images/eurjpyD.eps}
+\subcaption{Profit - pyD}
+\label{mansard}
+\end{minipage}
+\begin{minipage}{\linewidth}
+\centering
+\includegraphics[width=0.6\textwidth]{images/eurjpyS.eps}
+\subcaption{Profit - pyS}
+\label{mansard}
+\end{minipage}
+\caption{EURJPY market results}
+\end{figure}
+\FloatBarrier
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+\newpage
+\begin{table}[!t]
+\caption{Profits for all strategy quadrants for FUS500}
+ \begin{center}
+ \begin{tabular}{|l|l|l|l|l|}
+ \hline \textbf{strategy} & \textbf{profit} & \textbf{bestCalmar} & \textbf{bestMALength} & \textbf{la} \\ \hline
+S1a & 17.19 & 8.24 & 18 & 2693\\ \hline
+S1b & -9.80 & -0.74 & 54 & 2665\\ \hline
+S1c & 5.65 & 2.06 & 54 & 2280\\ \hline
+S1d & 1.87 & 0.61 & 18 & 2287\\ \hline
+S1s & 14.85 & 5.68 & Group of MA & 4945\\
+\hline \end{tabular}
+ \end{center}
+ \end{table}
+\FloatBarrier
+\begin{figure}[h]
+\centering
+\begin{minipage}{.49\linewidth}
+\centering
+\includegraphics[width=0.82\textwidth]{images/fus500A.eps}
+\subcaption{Profit - 00A}
+\label{jedno}
+\end{minipage}
+\begin{minipage}{.49\linewidth}
+\centering
+\includegraphics[width=0.82\textwidth]{images/fus500B.eps}
+\subcaption{Profit - 00B}
+\label{dwu}
+\end{minipage}
+\\
+\begin{minipage}{.49\linewidth}
+\centering
+\includegraphics[width=0.82\textwidth]{images/fus500C.eps}
+\subcaption{Profit - 00C}
+\label{cztero}
+\end{minipage}
+\begin{minipage}{.49\linewidth}
+\centering
+\includegraphics[width=0.82\textwidth]{images/fus500D.eps}
+\subcaption{Profit - 00D}
+\label{mansard}
+\end{minipage}
+\begin{minipage}{\linewidth}
+\centering
+\includegraphics[width=0.6\textwidth]{images/fus500S.eps}
+\subcaption{Profit - 00S}
+\label{mansard}
+\end{minipage}
+\caption{FUS500 market results}
+\end{figure}
+\FloatBarrier
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+\newpage
+\begin{table}[!t]
+\caption{Profits for all strategy quadrants for GBPCHF}
+ \begin{center}
+ \begin{tabular}{|l|l|l|l|l|}
+ \hline \textbf{strategy} & \textbf{profit} & \textbf{bestCalmar} & \textbf{bestMALength} & \textbf{la} \\ \hline
+S1a & 17.19 & 8.24 & 18 & 2693\\ \hline
+S1b & -9.80 & -0.74 & 54 & 2665\\ \hline
+S1c & 5.65 & 2.06 & 54 & 2280\\ \hline
+S1d & 1.87 & 0.61 & 18 & 2287\\ \hline
+S1s & 14.85 & 5.68 & Group of MA & 4945\\
+\hline \end{tabular}
+ \end{center}
+ \end{table}
+\FloatBarrier
+\begin{figure}[h]
+\centering
+\begin{minipage}{.49\linewidth}
+\centering
+\includegraphics[width=0.82\textwidth]{images/gbpchfA.eps}
+\subcaption{Profit - hfA}
+\label{jedno}
+\end{minipage}
+\begin{minipage}{.49\linewidth}
+\centering
+\includegraphics[width=0.82\textwidth]{images/gbpchfB.eps}
+\subcaption{Profit - hfB}
+\label{dwu}
+\end{minipage}
+\\
+\begin{minipage}{.49\linewidth}
+\centering
+\includegraphics[width=0.82\textwidth]{images/gbpchfC.eps}
+\subcaption{Profit - hfC}
+\label{cztero}
+\end{minipage}
+\begin{minipage}{.49\linewidth}
+\centering
+\includegraphics[width=0.82\textwidth]{images/gbpchfD.eps}
+\subcaption{Profit - hfD}
+\label{mansard}
+\end{minipage}
+\begin{minipage}{\linewidth}
+\centering
+\includegraphics[width=0.6\textwidth]{images/gbpchfS.eps}
+\subcaption{Profit - hfS}
+\label{mansard}
+\end{minipage}
+\caption{GBPCHF market results}
+\end{figure}
+\FloatBarrier
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+\newpage
+\begin{table}[!t]
+\caption{Profits for all strategy quadrants for SILVER}
+ \begin{center}
+ \begin{tabular}{|l|l|l|l|l|}
+ \hline \textbf{strategy} & \textbf{profit} & \textbf{bestCalmar} & \textbf{bestMALength} & \textbf{la} \\ \hline
+S1a & 17.19 & 8.24 & 18 & 2693\\ \hline
+S1b & -9.80 & -0.74 & 54 & 2665\\ \hline
+S1c & 5.65 & 2.06 & 54 & 2280\\ \hline
+S1d & 1.87 & 0.61 & 18 & 2287\\ \hline
+S1s & 14.85 & 5.68 & Group of MA & 4945\\
+\hline \end{tabular}
+ \end{center}
+ \end{table}
+\FloatBarrier
+\begin{figure}[h]
+\centering
+\begin{minipage}{.49\linewidth}
+\centering
+\includegraphics[width=0.82\textwidth]{images/silverA.eps}
+\subcaption{Profit - erA}
+\label{jedno}
+\end{minipage}
+\begin{minipage}{.49\linewidth}
+\centering
+\includegraphics[width=0.82\textwidth]{images/silverB.eps}
+\subcaption{Profit - erB}
+\label{dwu}
+\end{minipage}
+\\
+\begin{minipage}{.49\linewidth}
+\centering
+\includegraphics[width=0.82\textwidth]{images/silverC.eps}
+\subcaption{Profit - erC}
+\label{cztero}
+\end{minipage}
+\begin{minipage}{.49\linewidth}
+\centering
+\includegraphics[width=0.82\textwidth]{images/silverD.eps}
+\subcaption{Profit - erD}
+\label{mansard}
+\end{minipage}
+\begin{minipage}{\linewidth}
+\centering
+\includegraphics[width=0.6\textwidth]{images/silverS.eps}
+\subcaption{Profit - erS}
+\label{mansard}
+\end{minipage}
+\caption{SILVER market results}
+\end{figure}
+\FloatBarrier
+
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

### 2013-10-29 Matlabs/Indicators/AB/uczenie1000/ROC_A/PSODefaultOptions.m
added: testing for A and D (ROC)

@@ -1,0 +1,20 @@
+function [ options ] = PSODefaultOptions(spread)
+    pip = spread/2;
+    field1 = 'omega' ; value1 = 0.75;
+    field2 = 'phi_swarm' ; value2 = 0.65;
+    field3 = 'phi_particle' ; value3 = 0.55;
+    field4 = 'data_limits' ; value4 = [8 20;
+        -500 500;
+        6 20;
+        2*pip 20*pip;
+        8*spread 48*spread;
+        16 240];
+    field5 = 'num_of_particles' ; value5 = 200;
+    field6 = 'velocity_limits' ; value6 = [0.1 0.9; 0.1 0.9;0.1 0.9;0.1 0.9;0.1 0.9;0.1 0.9];
+    field8 = 'max_iter_num'; value8 = 65;
+    field9 = 'best_position_timeout'; value9 = Inf;
+
+    options = struct(field1, value1, field2, value2, field3, ...
+        value3, field4, value4, field5, value5, field6, value6,...
+        field8, value8, field9, value9); 
+end

### 2013-10-29 Matlabs/Indicators/AB/uczenie1000/ROC_A/ROCAllPeriods.m

@@ -1,0 +1,67 @@
+personNumber = 1;
+eurusd221012;
+spread = 0.0002;
+personalFileHandle = fopen('tewiROCaAB.csv', 'r');
+header = textscan(personalFileHandle, '%s;%s;%s;%s;%s;%s;%s;%s\n');
+testSize = 100;
+scanPeriodCount = 31;%tylko do 100 œwiec mo¿na testowaæ 34 okresy, do 200 - 33
+returns3d = zeros((scanPeriodCount + 3)* 100,testSize, scanPeriodCount);
+returns2d = zeros((scanPeriodCount + 3)* 100,testSize);
+WYN = [];
+wynKON = 0;
+for i =1:scanPeriodCount
+    Cc=textscan(personalFileHandle, '%d;%f;%d;%d;%d;%f;%f;%d\n');
+    pocz = cell2mat(Cc(1));
+    kon = pocz + testSize;
+    zyl = cell2mat(Cc(2));
+    dur = cell2mat(Cc(3));
+    vt = cell2mat(Cc(4));
+    vl = cell2mat(Cc(5));
+    bff = cell2mat(Cc(6));
+    SL = cell2mat(Cc(7));
+    op = cell2mat(Cc(8));
+    [ Sum, Calmar, iL, returns] = ROCa( C, pocz, kon, spread,...
+    dur,vt,vl,bff,SL,op);
+    wynKON(end+1) = wynKON(end) + Sum;
+	if i>1
+        returns = returns + WYN(end);
+    end
+    WYN = [WYN returns];
+end
+fclose(personalFileHandle);
+
+wynKON(end)
+[ Calmar ] = obliczCalmara( WYN )
+plot(wynKON)
+figure
+plot(WYN)
+
+% returns2d = sum (returns3d, 3);
+% for i=1:kon
+%     for j=1:testSize
+%         returns2d(i,j)= returns2d(i,j) / nnz(returns3d(i,j,:));
+%     end
+% end
+% returns2d(isnan(returns2d)) = 0;
+% cumulativeReturns = zeros((scanPeriodCount + 3)* 100,testSize);
+% for j=1:testSize
+%     cumulativeReturns(1,j)= returns2d(1,j);
+% end
+% for i=2:kon
+%     for j=1:testSize
+%         cumulativeReturns(i,j)= cumulativeReturns(i-1,j) + returns2d(i,j);
+%     end
+% end
+% cumulativeReturnsPerCandle = cumulativeReturns;
+% for i=1:kon
[…]

### 2013-10-29 Matlabs/Indicators/AB/uczenie1000/ROC_A/ROCa.m

@@ -1,0 +1,47 @@
+function [ Sum, Calmar, iL, sumR] = ROCa( C, pocz, kon, spread,...
+    Duration, VolThreshold, VolLength, Buffer, SL, CloseAgo)
+
+
+
+iL = 0; % przekroczenie 0 w górê - kupno (L)
+sumR = [];%zeros(1,size(C,1));
+R = zeros(1,size(C,1));
+recordReturn=0;  %rekord zysku
+recordDrawdown=0;  %rekord obsuniecia
+
+[ ROC_vec ] = CalculateROC(C,pocz, kon, CloseAgo);
+
+volAverages=zeros(1, kon);
+for i=2:kon
+    volAverages(i) = mean(C(i-min(i-1,VolLength):i,5))-C(i,5);
+end
+
+for i=pocz:kon
+    if ROC_vec(i)*ROC_vec(i-1)<=0   % przeciêcie krzywej ROC z zerem
+        if ROC_vec(i-1) + Buffer <ROC_vec(i)  && volAverages(i)<VolThreshold% warunek kupna
+            iL = iL + 1;
+            R(i) = C(i+Duration,4)-C(i+1,1)-spread;
+            
+            L=min(C(i+1:i+Duration,3));
+            
+            if (-C(i+1,1)+L) < -SL
+                R(i) = - SL;
+            end
+            
+        end
+    end
+    sumR(i) = sum(R(pocz:i));
+    
+    if sumR(i)>recordReturn
+        recordReturn=sumR(i);
+    end
+    
+    if sumR(i)-recordReturn<recordDrawdown
+        recordDrawdown=sumR(i)-recordReturn;  
+    end
+end
+
+Calmar=-sumR(kon)/recordDrawdown;
+Sum = sumR(kon);
+sumR = sumR(pocz:kon);
+end

### 2013-10-29 Matlabs/Indicators/AB/uczenie1000/ROC_D/PSODefaultOptions.m

@@ -1,0 +1,20 @@
+function [ options ] = PSODefaultOptions(spread)
+    pip = spread/2;
+    field1 = 'omega' ; value1 = 0.75;
+    field2 = 'phi_swarm' ; value2 = 0.65;
+    field3 = 'phi_particle' ; value3 = 0.55;
+    field4 = 'data_limits' ; value4 = [8 20;
+        -500 500;
+        6 20;
+        -20*pip -2*pip;
+        8*spread 48*spread;
+        16 240];
+    field5 = 'num_of_particles' ; value5 = 150;%200;
+    field6 = 'velocity_limits' ; value6 = [0.1 0.9; 0.1 0.9;0.1 0.9;0.1 0.9;0.1 0.9;0.1 0.9];
+    field8 = 'max_iter_num'; value8 = 40;%65;
+    field9 = 'best_position_timeout'; value9 = Inf;
+
+    options = struct(field1, value1, field2, value2, field3, ...
+        value3, field4, value4, field5, value5, field6, value6,...
+        field8, value8, field9, value9); 
+end

### 2013-10-29 Article/book/matlabs/S1a.m
added: matlabs for generating plots, results for eurjpy, chfjpy, gbpchf, fus500, silver

@@ -1,0 +1,78 @@
+function [] = S1a (C,ma,rynek)
+%(C) Antoni Wiliñski 2013
+%skrypt strategii S1 w projekcie TEWI
+%S1a - pierwszy kwadrant - oznaczajacy za³o¿enie, ze trend jest rosnacy i
+%nale¿y otwierac pozycje d³ugie wg zasady Buy Stop
+
+candlesCount = size(C,1);
+
+% candlesCount(1)=5000;
+bestSumRa = -Inf;
+bestCalmara = -Inf;
+
+for ma=ma
+    means=zeros(1, candlesCount);
+    kon=candlesCount-1;
+    for i=2:kon
+        means(i) = mean(C(i-min(i-1,ma):i,4));
+    end
+    sumRa=zeros(1,6000);
+    Ra=zeros(1,6000);
+    pocz=ma+1;
+    if size(C,1)<5000
+        kon = 2047;
+    else
+        kon=5000-1;
+    end
+    la=0; %liczba otwieranych pozycji
+
+    for i=pocz:kon
+        if means(i)<C(i,4)
+       % if mean(C(i-ma:i,4))<C(i,4) && mean(C(i-ma:i,4))>C(i-1,4)
+            Ra(i)=C(i+1,4)-C(i+1,1); %zysk z i-tej pozycji long zamykanej po jednym kroku (na koñcu swiecy, w której nastapi³o otwarcie)
+            la=la+1;
+        end
+        sumRa(i)=sum(Ra(pocz:i));  %krzywa narastania kapita³u
+    end
+    
+    %obliczenie wspó³czynnika Calmara (stosunku zysku koñcowego do najwiekszego
+    %obsuniecia)
+    
+    recZ=0;  %rekord zysku
+    recO=0;  %rekord obsuniecia
+    
+    for j=1:kon
+        if sumRa(j)>recZ
+            recZ=sumRa(j);
+        end
+        dZ(j)=sumRa(j)-recZ; %róznica pomiedzy bie¿¹c¹ wartoscia kapita³u skumulowanego a dotychczasowym rekordem
+        if dZ(j)<recO
+            recO=dZ(j);  %obsuniecie maksymalne
+        end 
+    end
+    %wyniki koñcowe
+    Calmar=-sumRa(kon)/recO;  %wskaznik Calmara
+    if sumRa(kon)>bestSumRa
+        bestSumRa = sumRa(kon);
+        bestSumAll = sumRa;
[…]

### 2013-10-29 Article/book/matlabs/S1c.m

@@ -1,0 +1,77 @@
+function [] = S1c (C,mc,rynek)
+%(C) Antoni Wiliñski 2013
+%skrypt strategii S1 w projekcie TEWI
+%S1c - trzeci kwadrant - oznaczajacy za³o¿enie, ze trend jest horyzontalny i
+%nale¿y otwierac pozycje d³ugie wg zasady Buy Limit
+
+candlesCount = size(C,1);
+%candlesCount(1)=5000;
+bestSumRc = -Inf;
+bestCalmarc = -Inf;
+
+
+for mc=mc
+    means=zeros(1, candlesCount);
+    kon=candlesCount-1;
+    for i=2:kon
+        means(i) = mean(C(i-min(i-1,mc):i,4));
+    end
+    sumRc=zeros(1,6000);
+    Rc=zeros(1,6000);
+    pocz=mc+1;
+    if size(C,1)<5000
+        kon = 2047;
+    else
+        kon=5000-1;
+    end
+    lc=0; %liczba otwieranych pozycji
+
+    for i=pocz:kon
+        if means(i)>C(i,4)
+            Rc(i)=C(i+1,4)-C(i+1,1); %zysk z i-tej pozycji long zamykanej po jednym kroku (na koñcu swiecy, w której nastapi³o otwarcie)
+            lc=lc+1;
+        end
+        sumRc(i)=sum(Rc(pocz:i));  %krzywa narastania kapita³u
+    end
+    
+    %obliczenie wspó³czynnika Calmara (stosunku zysku koñcowego do najwiekszego
+    %obsuniecia)
+    
+    recZ=0;  %rekord zysku
+    recO=0;  %rekord obsuniecia
+    
+    for j=1:kon
+        if sumRc(j)>recZ
+            recZ=sumRc(j);
+        end
+        dZ(j)=sumRc(j)-recZ; %róznica pomiedzy bie¿¹c¹ wartoscia kapita³u skumulowanego a dotychczasowym rekordem
+        if dZ(j)<recO
+            recO=dZ(j);  %obsuniecie maksymalne
+        end
+    end
+    %wyniki koñcowe
+    Calmar=-sumRc(kon)/recO;  %wskaznik Calmara
+    if sumRc(kon)>bestSumRc
+        bestSumRc = sumRc(kon);
+        bestSumAll = sumRc;
+        bestCalmarc = Calmar;
[…]

### 2013-10-29 Article/book/matlabs/S1d.m

@@ -1,0 +1,80 @@
+function [] = S1d (C,md,rynek)
+%(C) Antoni Wiliñski 2013
+%skrypt strategii S1 w projekcie TEWI
+%S1d - czwarty kwadrant - oznaczajacy za³o¿enie, ze trend jest spadkowy i
+%nale¿y otwierac pozycje krótkie
+
+
+candlesCount = size(C,1);
+%candlesCount(1)=5000;
+bestSumRd = -Inf;
+bestCalmard = -Inf;
+
+for md=md
+    means=zeros(1, candlesCount);
+    kon=candlesCount-1;
+    for i=2:kon
+        means(i) = mean(C(i-min(i-1,md):i-1,4));
+    end
+    sumRd=zeros(1,6000);
+    wykr=zeros(1,6000);
+    Rd=zeros(1,6000);
+    pocz=md+1;
+    if size(C,1)<5000
+        kon = 2047;
+    else
+        kon=5000-1;
+    end
+    ld=0; %liczba otwieranych pozycji
+    
+    for i=pocz:kon
+        if means(i)>C(i,4)
+            Rd(i)=-C(i+1,4)+C(i+1,1);%short zamykana po jednym kroku (na koñcu swiecy, w której nastapi³o otwarcie)
+            ld=ld+1;
+        end
+        sumRd(i)=sum(Rd(pocz:i));
+    end
+    
+    %obliczenie wspó³czynnika Calmara (stosunku zysku koñcowego do najwiekszego
+    %obsuniecia)
+    
+    recZ=0;  %rekord zysku
+    recO=0;  %rekord obsuniecia
+    
+    for j=1:kon
+        if sumRd(j)>recZ
+            recZ=sumRd(j);
+        end
+        dZ(j)=sumRd(j)-recZ; %róznica pomiedzy bie¿¹c¹ wartoscia kapita³u skumulowanego a dotychczasowym rekordem
+        if dZ(j)<recO
+            recO=dZ(j);  %obsuniecie maksymalne
+        end 
+    end
+    
+    %wyniki koñcowe
+    Calmar=-sumRd(kon)/recO;  %wskaznik Calmara
+    if sumRd(kon)>bestSumRd
+        bestSumRd = sumRd(kon);
+        bestSumAll = sumRd;
+        bestCalmard = Calmar;
+        bestLd = ld;  %liczba otwartych pozycji
+        bestLdp=ld/(kon-pocz);
[…]

### 2013-10-29 Article/book/matlabs/S1s.m

@@ -1,0 +1,83 @@
+function [] = S1s (C,ma,mb,mc,md,rynek)
+%(C) Antoni Wiliñski 2013
+%skrypt strategii S1 w projekcie TEWI
+%S1a - pierwszy kwadrant - oznaczajacy za³o¿enie, ze trend jest rosnacy i
+
+%nale¿y otwierac pozycje d³ugie wg zasady Buy Stop
+
+
+sumRs=zeros(1,6000);
+Ra=zeros(1,6000);
+Rb=zeros(1,6000);
+Rc=zeros(1,6000);
+Rd=zeros(1,6000);
+Rs=zeros(1,6000);
+pocz=max([ma, mb, mc, md])+1;
+if size(C,1)<5000
+    kon = 2047;
+else
+    kon=5000-1;
+end
+ls=0; %liczba otwieranych pozycji
+
+
+for i=pocz:kon
+    if mean(C(i-ma:i,4))<C(i,4)
+        Ra(i)=C(i+1,4)-C(i+1,1); %zysk z i-tej pozycji long zamykanej po jednym kroku (na koñcu swiecy, w której nastapi³o otwarcie)
+    end
+    if mean(C(i-mb:i,4))<C(i,4)
+        Rb(i)=-C(i+1,4)+C(i+1,1);
+    end
+    if mean(C(i-mc:i,4))>C(i,4) 
+        Rc(i)=C(i+1,4)-C(i+1,1);
+    end
+    if mean(C(i-md:i,4))>C(i,4) 
+        Rd(i)=-C(i+1,4)+C(i+1,1);
+    end
+    Rs(i) = Ra(i) + Rb(i) + Rc(i) + Rd(i);
+    ls=ls+1;
+    sumRs(i)=sum(Rs(pocz:i));  %krzywa narastania kapita³u
+    sumRa(i)=sum(Ra(pocz:i));
+    sumRb(i)=sum(Rb(pocz:i));
+    sumRc(i)=sum(Rc(pocz:i));
+    sumRd(i)=sum(Rd(pocz:i));
+end
+
+%obliczenie wspó³czynnika Calmara (stosunku zysku koñcowego do najwiekszego
+%obsuniecia)
+
+recZ=0;  %rekord zysku
+recO=0;  %rekord obsuniecia
+
+for j=1:kon
+    if sumRs(j)>recZ
+        recZ=sumRs(j);
+    end
[…]

### 2013-10-29 Article/book/matlabs/starter.m

@@ -1,0 +1,21 @@
+clc
+close
+clear
+
+ma=5;
+mb=1;
+mc=47;
+md=5;
+
+CHFJPY;
+C = C(size(C,1)-5000:end,:);
+rynek = 'chfjpy';
+
+
+S1a(C,ma,rynek)
+S1b(C,mb,rynek)
+S1c(C,mc,rynek)
+S1d(C,md,rynek)
+S1s(C,ma,mb,mc,md,rynek)
+
+table_to_latex(rynek)

### 2013-11-09 Article/book/BookSources/chapter3SimpleRules.tex
Book 1st version

--- 2013-10-29 Article/book/FormatProposal/tewi-paper-template.tex
@@
-% vim:encoding=utf8 ft=tex sts=2 sw=2 et:
-% Copyright (c) 2009 Jaroslaw Koszuk
-%
-% $Id$
-
-\documentclass{tewiart}
-
-\usepackage[utf8]{inputenc}
-\usepackage[T1]{fontenc}
-\usepackage{graphicx}
-\usepackage{amsthm}
-\usepackage{txfonts}
-\usepackage{epstopdf}
-\usepackage{placeins}
-\usepackage[english]{babel}
-\usepackage[utf8]{inputenc}
-\usepackage[table]{xcolor}
-\usepackage{array}
-\usepackage{subcaption}
-
-\newtheorem{definition}{Definition}
-\newtheorem{theorem}[definition]{Theorem}
-\newtheorem{corollary}[definition]{Corollary}
-\newtheorem{proposition}[definition]{Proposition}
-\newtheorem{example}[definition]{Example}
-
-\title{Meaning of simple rules in investment strategies of algorithmic trading}
-\headtitle{Meaning of simple rules in investment strategies of algorithmic trading\dots}
-\author{Antoni Wiliński\inst{1}, Piotr Błaszyński\inst{1}, Aneta Bera\inst{1}, \\ Wojciech Nowicki\inst{1}, Katarzyna Buda\inst{1}}
-\headauthor{Antoni Wiliński, Piotr Błaszyński et al.}
-\affiliation{%
-  \inst{1}West Pomeranian University of Technology\\
-  Faculty of Computer Science\\
-  ul. Żołnierska 49, 71-210 Szczecin Poland\\
-  \{awilinski, pblaszynski, abera, wnowicki, kbuda\}@wi.zut.edu.pl
-}
-\keywords{algorithmic trading, forecasting, financial markets, simple rules, computational intelligence, investment strategies}
-
-\begin{document}
-
-\begin{figure}
-\centering
-\includegraphics[width=\textwidth]{logotewi.png}
-\end{figure}
-
-\maketitle
-
-\begin{abstract}
+\chapter{Znaczenie prostych zasad w strategiach inwestycyjnych handlu algorytmicznego}
+\label{SimpleRules} % Always give a unique label
+% use \chaptermark{}
+% to alter or adjust the chapter heading in the running head
+\section{abstract}
+\label{sec:c3abstract}
+% Always give a unique label % and use \ref{<label>} for cross-references % and \cite{<label>} for bibliographic references % use \sectionmark{} to alter or adjust the section heading in the running head
 In article are shown studies of the possibly simplest investment strategy of algo trading.
@@
 In principle, the strategy is not relevant investment (studies were conducted without transaction costs), only cognitive in order to develop.
-\end{abstract}
 
 \section{Introduction}
+\label{sec:c3Introduction}
 \indent For centuries predicting future events was a great challenge for many fields of science \cite{ball07, wu12}.
@@
 \section{Strategy characteristics}
+\label{sec:c3StrategyCharacteristics}
 \indent The essence of the concept is the idea of simultaneous open long and short positions based on various signals, in this case the intersection graph (values of exchange rate  and stock index) and average of the last m closing of this price.\\
@@
 \section{The test results}
+\label{sec:c3TheTestResults}
 \indent The charts below show the curves of capital accumulation for each quarter of quadrant.
@@
 
+\input{resultsChapter3Fig1EURJPY}
+\input{resultsChapter3Fig2CHFJPY}
+\input{resultsChapter3Fig3GBPCHF}
+\input{resultsChapter3Fig4FUS500}
+\input{resultsChapter3Fig5SILVER}
+
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
 \section{Conclusions}
+\label{sec:c3Conclusions}
 \indent Suggested simple strategy is suitable only for algorithmic trading, even in absolute simplest form it seems to be interesting.
@@
 \bibliographystyle{aiaa-tewi}
-
-\end{document}

### 2013-11-10 Article/book/matlabs/S1d.m
changed: xlabel without Polish characters

@@ -74,7 +74,7 @@ set(hFig, 'Position', [200 200 840 400]);
 bestSumAll = bestSumAll(bestSumAll~=0);
 plot(bestSumAll);
 xlim([0 length(bestSumAll)]);
-xlabel('Candles');
-ylabel('Profit');
+xlabel('Swiece');
+ylabel('Skumulowany zysk');
 set(hFig, 'PaperPositionMode','auto') ;  %# WYSIWYG
 print(hFig,'-depsc', '-r0',[mfilename '_' rynek]);

### 2013-11-10 Article/Article20131011/sources/PivotPointsProste.m
update version

@@ -1,0 +1,76 @@
+%Tomasz Nyczaj 2013 substrategie A-D
+
+%Dane:
+eurusd1h020313;
+size(C)
+
+RA=zeros(1,6000);
+sumRA=zeros(1,6000);
+RB=zeros(1,6000);
+sumRB=zeros(1,6000);
+RC=zeros(1,6000);
+sumRC=zeros(1,6000);
+RD=zeros(1,6000);
+sumRD=zeros(1,6000);
+sumRS=zeros(1,6000);
+spread=0.0002;
+lA=0;
+lB=0;
+lC=0;
+lD=0;
+   
+for i=2:6000
+      
+    %Wyliczenie punktów pivota  
+    P(i)=(C(i-1,2)+C(i-1,3)+C(i-1,4))/3;  %pivot point
+    RR1(i)=2*P(i)-C(i-1,3);  %pierwszy opór
+    SS1(i)=2*P(i)-C(i-1,2);  %pierwsze wsparcie
+    RR2(i)=P(i)+(RR1(i)-SS1(i)); %drugi opór
+    SS2(i)=P(i)-(RR1(i)-SS1(i));  %drugie wsparcie 
+    
+    %Warunki otwarcia pozycji d³ugiej
+    if RR2(i)<C(i,1)
+        RA(i)=C(i,4)-C(i,1)-spread;
+	lA=lA+1;
+    end
+if RR2(i)>C(i,1) && C(i,1)>RR1(i)
+        RB(i)=C(i,1)-C(i,4)-spread;
+	lB=lB+1;
+    end
+if SS1(i)>C(i,1) && C(i,1)>SS2(i)
+        RC(i)=C(i,4)-C(i,1)-spread;
+	lC=lC+1;
+    end
+if SS2(i)>C(i,1)
+        RD(i)=C(i,1)-C(i,4)-spread;
+	lD=lD+1;
+    end
+   
+%Obliczanie zysku skumulowanego
+    sumRA(i)=sum(RA(2:i));
+    sumRB(i)=sum(RB(2:i));
+    sumRC(i)=sum(RC(2:i));
+    sumRD(i)=sum(RD(2:i));
+    sumS(i)=sumRA(i)+sumRB(i)+sumRC(i)+sumRD(i);
+end
+
+sumaA=sumRA(6000)
+lA
+sumaB=sumRB(6000)
+lB
+sumaC=sumRC(6000)
+lC
+sumaD=sumRD(6000)
[…]

### 2013-11-10 Article/book/BookSources/chapter3SimpleRules.tex
changed: figures potition

@@
 % to alter or adjust the chapter heading in the running head
-\section{abstract}
-\label{sec:c3abstract}
+
+%\label{sec:c3abstract}
 % Always give a unique label % and use \ref{<label>} for cross-references % and \cite{<label>} for bibliographic references % use \sectionmark{} to alter or adjust the section heading in the running head
@@
 \newpage
-\begin{table}[!t]
-\caption{Profits for all strategy quadrants for EURJPY} 
- \begin{center} 
- \begin{tabular}{|l|l|l|l|l|} 
- \hline \textbf{strategy} & \textbf{profit} & \textbf{bestCalmar} & \textbf{bestMALength} & \textbf{la} \\ \hline  
-S1a & 26.18 & 5.59 & 24 & 2764\\ \hline 
-S1b & -14.77 & -0.67 & 6 & 2660\\ \hline 
-S1c & 15.74 & 2.49 & 6 & 2332\\ \hline 
-S1d & -4.57 & -0.47 & 21 & 2226\\ \hline 
-S1s & 22.54 & 3.25 & Group of MA & 4975\\ 
-\hline \end{tabular} 
- \end{center} 
- \end{table}
-\FloatBarrier
-
-\begin{figure}[h]
-\centering
-\begin{minipage}{.49\linewidth}
-\centering 
-\includegraphics[width=0.82\textwidth]{images/S1a_eurjpy.eps}
-\subcaption{Profit - S1a}
-\label{jedno}
-\end{minipage}
-\begin{minipage}{.49\linewidth}
-\centering 
-\includegraphics[width=0.82\textwidth]{images/S1b_eurjpy.eps}
-\subcaption{Profit - S1b}
-\label{dwu}
-\end{minipage}
-\\
-\begin{minipage}{.49\linewidth}
-\centering 
-\includegraphics[width=0.82\textwidth]{images/S1c_eurjpy.eps}
-\subcaption{Profit- S1c}
-\label{cztero}
-\end{minipage}
-\begin{minipage}{.49\linewidth}
-\centering 
-\includegraphics[width=0.82\textwidth]{images/S1d_eurjpy.eps}
-\subcaption{Profit - S1d}
-\label{mansard}
-\end{minipage}
-\begin{minipage}{\linewidth}
-\centering 
-\includegraphics[width=0.6\textwidth]{images/S1s_eurjpy.eps}
-\label{mansard}
-\subcaption{Profit - S1s}
-\end{minipage}
-\caption{EURJPY market results}
-\end{figure}
-\FloatBarrier
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\newpage
-\begin{table}[!t]
-\caption{Profits for all strategy quadrants for USDJPY} 
- \begin{center} 
- \begin{tabular}{|l|l|l|l|l|} 
- \hline \textbf{strategy} & \textbf{profit} & \textbf{bestCalmar} & \textbf{bestMALength} & \textbf{la} \\ \hline  
-S1a & 17.19 & 8.24 & 18 & 2693\\ \hline 
-S1b & -9.80 & -0.74 & 54 & 2665\\ \hline 
-S1c & 5.65 & 2.06 & 54 & 2280\\ \hline 
-S1d & 1.87 & 0.61 & 18 & 2287\\ \hline 
-S1s & 14.85 & 5.68 & Group of MA & 4945\\ 
-\hline \end{tabular} 
- \end{center} 
- \end{table}
-\FloatBarrier
-
-\begin{figure}[h]
-\centering
-\begin{minipage}{.49\linewidth}
-\centering 
-\includegraphics[width=0.82\textwidth]{images/S1a_usdjpy.eps}
-\subcaption{Profit - S1a}
-\label{jedno}
-\end{minipage}
-\begin{minipage}{.49\linewidth}
-\centering 
-\includegraphics[width=0.82\textwidth]{images/S1b_usdjpy.eps}
-\subcaption{Profit - S1b}
-\label{dwu}
-\end{minipage}
-\\
-\begin{minipage}{.49\linewidth}
-\centering 
-\includegraphics[width=0.82\textwidth]{images/S1c_usdjpy.eps}
-\subcaption{Profit- S1c}
-\label{cztero}
-\end{minipage}
-\begin{minipage}{.49\linewidth}
-\centering 
-\includegraphics[width=0.82\textwidth]{images/S1d_usdjpy.eps}
-\subcaption{Profit - S1d}
-\label{mansard}
-\end{minipage}
-\begin{minipage}{\linewidth}
-\centering 
-\includegraphics[width=0.6\textwidth]{images/S1s_usdjpy.eps}
-\label{mansard}
-\subcaption{Profit - S1s}
-\end{minipage}
-\caption{USDJPY market results}
-\end{figure}
-\FloatBarrier
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\newpage
-\begin{table}[!t]
-\caption{Profits for all strategy quadrants for GBPUSD} 
- \begin{center} 
- \begin{tabular}{|l|l|l|l|l|} 
- \hline \textbf{strategy} & \textbf{profit} & \textbf{bestCalmar} & \textbf{bestMALength} & \textbf{la} \\ \hline  
-S1a & 0.06 & 1.06 & 92 & 2588\\ \hline 
-S1b & 0.12 & 3.41 & 5 & 2513\\ \hline 
-S1c & 0.15 & 3.11 & 5 & 2475\\ \hline 
-S1d & 0.02 & 0.31 & 92 & 2319\\ \hline 
-S1s & 0.36 & 6.89 & Group of MA & 4907\\ 
-\hline \end{tabular} 
- \end{center} 
- \end{table}
-\FloatBarrier
-
-\begin{figure}[h]
-\centering
-\begin{minipage}{.49\linewidth}
-\centering 
-\includegraphics[width=0.82\textwidth]{images/S1a_gbpusd.eps}
-\subcaption{Profit - S1a}
-\label{jedno}
-\end{minipage}
-\begin{minipage}{.49\linewidth}
-\centering 
-\includegraphics[width=0.82\textwidth]{images/S1b_gbpusd.eps}
-\subcaption{Profit - S1b}
-\label{dwu}
-\end{minipage}
-\\
-\begin{minipage}{.49\linewidth}
-\centering 
-\includegraphics[width=0.82\textwidth]{images/S1c_gbpusd.eps}
-\subcaption{Profit- S1c}
-\label{cztero}
-\end{minipage}
-\begin{minipage}{.49\linewidth}
-\centering 
-\includegraphics[width=0.82\textwidth]{images/S1d_gbpusd.eps}
-\subcaption{Profit - S1d}
-\label{mansard}
-\end{minipage}
-\begin{minipage}{\linewidth}
-\centering 
-\includegraphics[width=0.6\textwidth]{images/S1s_gbpusd.eps}
-\label{mansard}
-\subcaption{Profit - S1s}
-\end{minipage}
-\caption{GBPUSD market results}
-\end{figure}
-\FloatBarrier
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\newpage
-\begin{table}[!t]
-\caption{Profits for all strategy quadrants for EURUSD} 
- \begin{center} 
- \begin{tabular}{|l|l|l|l|l|} 
- \hline \textbf{strategy} & \textbf{profit} & \textbf{bestCalmar} & \textbf{bestMALength} & \textbf{la} \\ \hline  
-S1a & 0.09 & 1.84 & 33 & 2635\\ \hline 
-S1b & 0.01 & 0.16 & 5 & 2587\\ \hline 
-S1c & 0.12 & 3.45 & 5 & 2406\\ \hline 
-S1d & -0.02 & -0.49 & 33 & 2331\\ \hline 
-S1s & 0.21 & 3.31 & Group of MA & 4966\\ 
-\hline \end{tabular} 
- \end{center} 
- \end{table}
-\FloatBarrier
-
-\begin{figure}[h]
-\centering
-\begin{minipage}{.49\linewidth}
-\centering 
-\includegraphics[width=0.82\textwidth]{images/S1a_eurusd.eps}
-\subcaption{Profit - S1a}
-\label{jedno}
-\end{minipage}
-\begin{minipage}{.49\linewidth}
-\centering 
-\includegraphics[width=0.82\textwidth]{images/S1b_eurusd.eps}
-\subcaption{Profit - S1b}
-\label{dwu}
-\end{minipage}
-\\
-\begin{minipage}{.49\linewidth}
-\centering 
-\includegraphics[width=0.82\textwidth]{images/S1c_eurusd.eps}
-\subcaption{Profit- S1c}
-\label{cztero}
-\end{minipage}
-\begin{minipage}{.49\linewidth}
-\centering 
-\includegraphics[width=0.82\textwidth]{images/S1d_eurusd.eps}
-\subcaption{Profit - S1d}
-\label{mansard}
-\end{minipage}
-\begin{minipage}{\linewidth}
-\centering 
-\includegraphics[width=0.6\textwidth]{images/S1s_eurusd.eps}
-\label{mansard}
-\subcaption{Profit - S1s}
-\end{minipage}
-\caption{EURUSD market results}
-\end{figure}
-\FloatBarrier
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\newpage
-\begin{table}[!t]
-\caption{Profits for all strategy quadrants for FUS500} 
- \begin{center} 
- \begin{tabular}{|l|l|l|l|l|} 
- \hline \textbf{strategy} & \textbf{profit} & \textbf{bestCalmar} & \textbf{bestMALength} & \textbf{la} \\ \hline  
-S1a & 274.89 & 5.44 & 83 & 3200\\ \hline 
-S1b & -70.94 & -0.47 & 15 & 2798\\ \hline 
-S1c & 291.62 & 4.26 & 15 & 2186\\ \hline 
-S1d & -106.67 & -0.73 & 82 & 1723\\ \hline 
-S1s & 344.29 & 2.08 & Group of MA & 4916\\ 
-\hline \end{tabular} 
- \end{center} 
- \end{table}
-\FloatBarrier
-
-\begin{figure}[h]
-\centering
-\begin{minipage}{.49\linewidth}
-\centering 
-\includegraphics[width=0.82\textwidth]{images/S1a_fus.eps}
-\subcaption{Profit - S1a}
-\label{jedno}
-\end{minipage}
-\begin{minipage}{.49\linewidth}
-\centering 
-\includegraphics[width=0.82\textwidth]{images/S1b_fus.eps}
-\subcaption{Profit - S1b}
-\label{dwu}
-\end{minipage}
-\\
-\begin{minipage}{.49\linewidth}
-\centering 
-\includegraphics[width=0.82\textwidth]{images/S1c_fus.eps}
-\subcaption{Profit- S1c}
-\label{cztero}
-\end{minipage}
-\begin{minipage}{.49\linewidth}
-\centering 
-\includegraphics[width=0.82\textwidth]{images/S1d_fus.eps}
-\subcaption{Profit - S1d}
-\label{mansard}
-\end{minipage}
-\begin{minipage}{\linewidth}
-\centering 
-\includegraphics[width=0.6\textwidth]{images/S1s_fus.eps}
-\label{mansard}
-\subcaption{Profit - S1s}
-\end{minipage}
-\caption{FUS500 market results}
-\end{figure}
-\FloatBarrier
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\newpage
-\begin{table}[!t]
-\caption{Profits for all strategy quadrants for BOSSAPLN} 
- \begin{center} 
- \begin{tabular}{|l|l|l|l|l|} 
- \hline \textbf{strategy} & \textbf{profit} & \textbf{bestCalmar} & \textbf{bestMALength} & \textbf{la} \\ \hline  
-S1a & 5.87 & 1.99 & 21 & 2474\\ \hline 
-S1b & 2.86 & 0.61 & 5 & 2416\\ \hline 
-S1c & 10.91 & 4.33 & 5 & 2547\\ \hline 
-S1d & -2.23 & -0.42 & 21 & 2502\\ \hline 
-S1s & 17.91 & 4.35 & Group of MA & 4978\\ 
-\hline \end{tabular} 
- \end{center} 
- \end{table}
-\FloatBarrier
-
-\begin{figure}[h]
-\centering
-\begin{minipage}{.49\linewidth}
-\centering 
-\includegraphics[width=0.82\textwidth]{images/S1a_bossa.eps}
-\subcaption{Profit - S1a}
-\label{jedno}
-\end{minipage}
-\begin{minipage}{.49\linewidth}
-\centering 
-\includegraphics[width=0.82\textwidth]{images/S1b_bossa.eps}
-\subcaption{Profit - S1b}
-\label{dwu}
-\end{minipage}
-\\
-\begin{minipage}{.49\linewidth}
-\centering 
-\includegraphics[width=0.82\textwidth]{images/S1c_bossa.eps}
-\subcaption{Profit- S1c}
-\label{cztero}
-\end{minipage}
-\begin{minipage}{.49\linewidth}
-\centering 
-\includegraphics[width=0.82\textwidth]{images/S1d_bossa.eps}
-\subcaption{Profit - S1d}
-\label{mansard}
-\end{minipage}
-\begin{minipage}{\linewidth}
-\centering 
-\includegraphics[width=0.6\textwidth]{images/S1s_bossa.eps}
-\label{mansard}
-\subcaption{Profit - S1s}
-\end{minipage}
-\caption{BOSSAPLN market results}
-\end{figure}
-\FloatBarrier
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\newpage
-\begin{table}[!t]
-\caption{Profits for all strategy quadrants for FGOLD} 
- \begin{center} 
- \begin{tabular}{|l|l|l|l|l|} 
- \hline \textbf{strategy} & \textbf{profit} & \textbf{bestCalmar} & \textbf{bestMALength} & \textbf{la} \\ \hline  
-S1a & 61.16 & 0.59 & 51 & 2578\\ \hline 
-S1b & 227.58 & 2.82 & 5 & 2519\\ \hline 
-S1c & 30.38 & 0.12 & 5 & 2470\\ \hline 
-S1d & 248.21 & 1.52 & 51 & 2370\\ \hline 
-S1s & 599.88 & 4.60 & Group of MA & 4948\\ 
-\hline \end{tabular} 
- \end{center} 
- \end{table}
-\FloatBarrier
-
-\begin{figure}[h]
-\centering
-\begin{minipage}{.49\linewidth}
-\centering 
-\includegraphics[width=0.82\textwidth]{images/S1a_gold.eps}
-\subcaption{Profit - S1a}
-\label{jedno}
-\end{minipage}
-\begin{minipage}{.49\linewidth}
-\centering 
-\includegraphics[width=0.82\textwidth]{images/S1b_gold.eps}
-\subcaption{Profit - S1b}
-\label{dwu}
-\end{minipage}
-\\
-\begin{minipage}{.49\linewidth}
-\centering 
-\includegraphics[width=0.82\textwidth]{images/S1c_gold.eps}
-\subcaption{Profit- S1c}
-\label{cztero}
-\end{minipage}
-\begin{minipage}{.49\linewidth}
-\centering 
-\includegraphics[width=0.82\textwidth]{images/S1d_gold.eps}
-\subcaption{Profit - S1d}
-\label{mansard}
-\end{minipage}
-\begin{minipage}{\linewidth}
-\centering 
-\includegraphics[width=0.6\textwidth]{images/S1s_gold.eps}
-\label{mansard}
-\subcaption{Profit - S1s}
-\end{minipage}
-\caption{FGOLD market results}
-\end{figure}
-\FloatBarrier
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\newpage
-\begin{table}[!t]
-\caption{Profits for all strategy quadrants for FSILVER} 
-\begin{center}
- \begin{tabular}{|l|l|l|l|l|} 
- \hline \textbf{strategy} & \textbf{profit} & \textbf{bestCalmar} & \textbf{bestMALength} & \textbf{la} \\ \hline  
-S1a & -5.31 & -0.65 & 81 & 2582\\ \hline 
-S1b & 17.22 & 5.86 & 10 & 2508\\ \hline 
-S1c & 4.17 & 0.56 & 10 & 2473\\ \hline 
-S1d & 6.95 & 1.33 & 81 & 2336\\ \hline 
-S1s & 21.96 & 5.55 & Group of MA & 4918\\ 
-\hline \end{tabular} 
- \end{center} 
- \end{table}
-\FloatBarrier
-
-\begin{figure}[h]
-\centering
-\begin{minipage}{.49\linewidth}
-\centering 
-\includegraphics[width=0.82\textwidth]{images/S1a_silver.eps}
-\subcaption{Profit - S1a}
-\label{jedno}
-\end{minipage}
-\begin{minipage}{.49\linewidth}
-\centering 
-\includegraphics[width=0.82\textwidth]{images/S1b_silver.eps}
-\subcaption{Profit - S1b}
-\label{dwu}
-\end{minipage}
-\\
-\begin{minipage}{.49\linewidth}
-\centering 
-\includegraphics[width=0.82\textwidth]{images/S1c_silver.eps}
-\subcaption{Profit- S1c}
-\label{cztero}
-\end{minipage}
-\begin{minipage}{.49\linewidth}
-\centering 
-\includegraphics[width=0.82\textwidth]{images/S1d_silver.eps}
-\subcaption{Profit - S1d}
-\label{mansard}
-\end{minipage}
-\begin{minipage}{\linewidth}
-\centering 
-\includegraphics[width=0.6\textwidth]{images/S1s_silver.eps}
-\label{mansard}
-\subcaption{Profit - S1s}
-\end{minipage}
-\caption{FSILVER market results}
-\end{figure}
-\FloatBarrier
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\newpage
-\begin{table}[!t]
-\caption{Profits for all strategy quadrants for CADCHF}
- \begin{center}
- \begin{tabular}{|l|l|l|l|l|}
- \hline \textbf{strategy} & \textbf{profit} & \textbf{bestCalmar} & \textbf{bestMALength} & \textbf{la} \\ \hline
-S1a & 17.19 & 8.24 & 18 & 2693\\ \hline
-S1b & -9.80 & -0.74 & 54 & 2665\\ \hline
-S1c & 5.65 & 2.06 & 54 & 2280\\ \hline
-S1d & 1.87 & 0.61 & 18 & 2287\\ \hline
-S1s & 14.85 & 5.68 & Group of MA & 4945\\
-\hline \end{tabular}
- \end{center}
- \end{table}
-\FloatBarrier
-
-\begin{figure}[h]
-\centering
-\begin{minipage}{.49\linewidth}
-\centering
-\includegraphics[width=0.82\textwidth]{images/cadchfS1a.eps}
-\subcaption{Profit - S1a}
-\label{jedno}
-\end{minipage}
-\begin{minipage}{.49\linewidth}
-\centering
-\includegraphics[width=0.82\textwidth]{images/cadchfS1b.eps}
-\subcaption{Profit - S1b}
-\label{dwu}
-\end{minipage}
-\\
-\begin{minipage}{.49\linewidth}
-\centering
-\includegraphics[width=0.82\textwidth]{images/cadchfS1c.eps}
-\subcaption{Profit - S1c}
-\label{cztero}
-\end{minipage}
-\begin{minipage}{.49\linewidth}
-\centering
-\includegraphics[width=0.82\textwidth]{images/cadchfS1d.eps}
-\subcaption{Profit - S1d}
-\label{mansard}
-\end{minipage}
-\begin{minipage}{\linewidth}
-\centering
-\includegraphics[width=0.6\textwidth]{images/cadchfS1s.eps}
-\label{mansard}
-\subcaption{Profit - S1s}
-\end{minipage}
-\caption{CADCHF market results}
-\end{figure}
-\FloatBarrier
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\newpage
-\begin{table}[!t]
-\caption{Profits for all strategy quadrants for FCOPPER}
- \begin{center}
- \begin{tabular}{|l|l|l|l|l|}
- \hline \textbf{strategy} & \textbf{profit} & \textbf{bestCalmar} & \textbf{bestMALength} & \textbf{la} \\ \hline
-S1a & 17.19 & 8.24 & 18 & 2693\\ \hline
-S1b & -9.80 & -0.74 & 54 & 2665\\ \hline
-S1c & 5.65 & 2.06 & 54 & 2280\\ \hline
-S1d & 1.87 & 0.61 & 18 & 2287\\ \hline
-S1s & 14.85 & 5.68 & Group of MA & 4945\\
-\hline \end{tabular}
- \end{center}
- \end{table}
-\FloatBarrier
-\begin{figure}[h]
-\centering
-\begin{minipage}{.49\linewidth}
-\centering
-\includegraphics[width=0.82\textwidth]{images/fcopperS1a.eps}
-\subcaption{Profit - S1a}
-\label{jedno}
-\end{minipage}
-\begin{minipage}{.49\linewidth}
-\centering
-\includegraphics[width=0.82\textwidth]{images/fcopperS1b.eps}
-\subcaption{Profit - S1b}
-\label{dwu}
-\end{minipage}
-\\
-\begin{minipage}{.49\linewidth}
-\centering
-\includegraphics[width=0.82\textwidth]{images/fcopperS1c.eps}
-\subcaption{Profit - S1c}
-\label{cztero}
-\end{minipage}
-\begin{minipage}{.49\linewidth}
-\centering
-\includegraphics[width=0.82\textwidth]{images/fcopperS1d.eps}
-\subcaption{Profit - S1d}
-\label{mansard}
-\end{minipage}
-\begin{minipage}{\linewidth}
-\centering
-\includegraphics[width=0.6\textwidth]{images/fcopperS1s.eps}
-\subcaption{Profit - S1s}
-\label{mansard}
-\end{minipage}
-\caption{FCOPPER market results}
-\end{figure}
-\FloatBarrier
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\newpage
-\begin{table}[!t]
-\caption{Profits for all strategy quadrants for FCORN}
- \begin{center}
- \begin{tabular}{|l|l|l|l|l|}
- \hline \textbf{strategy} & \textbf{profit} & \textbf{bestCalmar} & \textbf{bestMALength} & \textbf{la} \\ \hline
-S1a & 17.19 & 8.24 & 18 & 2693\\ \hline
-S1b & -9.80 & -0.74 & 54 & 2665\\ \hline
-S1c & 5.65 & 2.06 & 54 & 2280\\ \hline
-S1d & 1.87 & 0.61 & 18 & 2287\\ \hline
-S1s & 14.85 & 5.68 & Group of MA & 4945\\
-\hline \end{tabular}
- \end{center}
- \end{table}
-\FloatBarrier
-\begin{figure}[h]
-\centering
-\begin{minipage}{.49\linewidth}
-\centering
-\includegraphics[width=0.82\textwidth]{images/fcornS1a.eps}
-\subcaption{Profit - S1a}
-\label{jedno}
-\end{minipage}
-\begin{minipage}{.49\linewidth}
-\centering
-\includegraphics[width=0.82\textwidth]{images/fcornS1b.eps}
-\subcaption{Profit - S1b}
-\label{dwu}
-\end{minipage}
-\\
-\begin{minipage}{.49\linewidth}
-\centering
-\includegraphics[width=0.82\textwidth]{images/fcornS1c.eps}
-\subcaption{Profit - S1c}
-\label{cztero}
-\end{minipage}
-\begin{minipage}{.49\linewidth}
-\centering
-\includegraphics[width=0.82\textwidth]{images/fcornS1d.eps}
-\subcaption{Profit - S1d}
-\label{mansard}
-\end{minipage}
-\begin{minipage}{\linewidth}
-\centering
-\includegraphics[width=0.6\textwidth]{images/fcornS1s.eps}
-\subcaption{Profit - S1s}
-\label{mansard}
-\end{minipage}
-\caption{FCORN market results}
-\end{figure}
-\FloatBarrier
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\newpage
-\begin{table}[!t]
-\caption{Profits for all strategy quadrants for NZDJPY}
- \begin{center}
- \begin{tabular}{|l|l|l|l|l|}
- \hline \textbf{strategy} & \textbf{profit} & \textbf{bestCalmar} & \textbf{bestMALength} & \textbf{la} \\ \hline
-S1a & 17.19 & 8.24 & 18 & 2693\\ \hline
-S1b & -9.80 & -0.74 & 54 & 2665\\ \hline
-S1c & 5.65 & 2.06 & 54 & 2280\\ \hline
-S1d & 1.87 & 0.61 & 18 & 2287\\ \hline
-S1s & 14.85 & 5.68 & Group of MA & 4945\\
-\hline \end{tabular}
- \end{center}
- \end{table}
-\FloatBarrier
-\begin{figure}[h]
-\centering
-\begin{minipage}{.49\linewidth}
-\centering
-\includegraphics[width=0.82\textwidth]{images/nzdjpyS1a.eps}
-\subcaption{Profit - S1a}
-\label{jedno}
-\end{minipage}
-\begin{minipage}{.49\linewidth}
-\centering
-\includegraphics[width=0.82\textwidth]{images/nzdjpyS1b.eps}
-\subcaption{Profit - S1b}
-\label{dwu}
-\end{minipage}
-\\
-\begin{minipage}{.49\linewidth}
-\centering
-\includegraphics[width=0.82\textwidth]{images/nzdjpyS1c.eps}
-\subcaption{Profit - S1c}
-\label{cztero}
-\end{minipage}
-\begin{minipage}{.49\linewidth}
-\centering
-\includegraphics[width=0.82\textwidth]{images/nzdjpyS1d.eps}
-\subcaption{Profit - S1d}
-\label{mansard}
-\end{minipage}
-\begin{minipage}{\linewidth}
-\centering
-\includegraphics[width=0.6\textwidth]{images/nzdjpyS1s.eps}
-\subcaption{Profit - S1s}
-\label{mansard}
-\end{minipage}
-\caption{NZDJPY market results}
-\end{figure}
-\FloatBarrier
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\newpage
-\begin{table}[!t]
-\caption{Profits for all strategy quadrants for USDCAD}
- \begin{center}
- \begin{tabular}{|l|l|l|l|l|}
- \hline \textbf{strategy} & \textbf{profit} & \textbf{bestCalmar} & \textbf{bestMALength} & \textbf{la} \\ \hline
-S1a & 17.19 & 8.24 & 18 & 2693\\ \hline
-S1b & -9.80 & -0.74 & 54 & 2665\\ \hline
-S1c & 5.65 & 2.06 & 54 & 2280\\ \hline
-S1d & 1.87 & 0.61 & 18 & 2287\\ \hline
-S1s & 14.85 & 5.68 & Group of MA & 4945\\
-\hline \end{tabular}
- \end{center}
- \end{table}
-\FloatBarrier
-\begin{figure}[h]
-\centering
-\begin{minipage}{.49\linewidth}
-\centering
-\includegraphics[width=0.82\textwidth]{images/usdcadS1a.eps}
-\subcaption{Profit - S1a}
-\label{jedno}
-\end{minipage}
-\begin{minipage}{.49\linewidth}
-\centering
-\includegraphics[width=0.82\textwidth]{images/usdcadS1b.eps}
-\subcaption{Profit - S1b}
-\label{dwu}
-\end{minipage}
-\\
-\begin{minipage}{.49\linewidth}
-\centering
-\includegraphics[width=0.82\textwidth]{images/usdcadS1c.eps}
-\subcaption{Profit - S1c}
-\label{cztero}
-\end{minipage}
-\begin{minipage}{.49\linewidth}
-\centering
-\includegraphics[width=0.82\textwidth]{images/usdcadS1d.eps}
-\subcaption{Profit - S1d}
-\label{mansard}
-\end{minipage}
-\begin{minipage}{\linewidth}
-\centering
-\includegraphics[width=0.6\textwidth]{images/usdcadS1s.eps}
-\subcaption{Profit - S1s}
-\label{mansard}
-\end{minipage}
-\caption{USDCAD market results}
-\end{figure}
-\FloatBarrier
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\newpage
-\begin{table}[!t]
-\caption{Profits for all strategy quadrants for CHFJPY}
- \begin{center}
- \begin{tabular}{|l|l|l|l|l|}
- \hline \textbf{strategy} & \textbf{profit} & \textbf{bestCalmar} & \textbf{bestMALength} & \textbf{la} \\ \hline
-S1a & 17.19 & 8.24 & 18 & 2693\\ \hline
-S1b & -9.80 & -0.74 & 54 & 2665\\ \hline
-S1c & 5.65 & 2.06 & 54 & 2280\\ \hline
-S1d & 1.87 & 0.61 & 18 & 2287\\ \hline
-S1s & 14.85 & 5.68 & Group of MA & 4945\\
-\hline \end{tabular}
- \end{center}
- \end{table}
-\FloatBarrier
-\begin{figure}[h]
-\centering
-\begin{minipage}{.49\linewidth}
-\centering
-\includegraphics[width=0.82\textwidth]{images/chfjpyA.eps}
-\subcaption{Profit - pyA}
-\label{jedno}
-\end{minipage}
-\begin{minipage}{.49\linewidth}
-\centering
-\includegraphics[width=0.82\textwidth]{images/chfjpyB.eps}
-\subcaption{Profit - pyB}
-\label{dwu}
-\end{minipage}
-\\
-\begin{minipage}{.49\linewidth}
-\centering
-\includegraphics[width=0.82\textwidth]{images/chfjpyC.eps}
-\subcaption{Profit - pyC}
-\label{cztero}
-\end{minipage}
-\begin{minipage}{.49\linewidth}
-\centering
-\includegraphics[width=0.82\textwidth]{images/chfjpyD.eps}
-\subcaption{Profit - pyD}
-\label{mansard}
-\end{minipage}
-\begin{minipage}{\linewidth}
-\centering
-\includegraphics[width=0.6\textwidth]{images/chfjpyS.eps}
-\subcaption{Profit - pyS}
-\label{mansard}
-\end{minipage}
-\caption{CHFJPY market results}
-\end{figure}
-\FloatBarrier
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\newpage
-\begin{table}[!t]
-\caption{Profits for all strategy quadrants for EURJPY}
- \begin{center}
- \begin{tabular}{|l|l|l|l|l|}
- \hline \textbf{strategy} & \textbf{profit} & \textbf{bestCalmar} & \textbf{bestMALength} & \textbf{la} \\ \hline
-S1a & 17.19 & 8.24 & 18 & 2693\\ \hline
-S1b & -9.80 & -0.74 & 54 & 2665\\ \hline
-S1c & 5.65 & 2.06 & 54 & 2280\\ \hline
-S1d & 1.87 & 0.61 & 18 & 2287\\ \hline
-S1s & 14.85 & 5.68 & Group of MA & 4945\\
-\hline \end{tabular}
- \end{center}
- \end{table}
-\FloatBarrier
-\begin{figure}[h]
-\centering
-\begin{minipage}{.49\linewidth}
-\centering
-\includegraphics[width=0.82\textwidth]{images/eurjpyA.eps}
-\subcaption{Profit - pyA}
-\label{jedno}
-\end{minipage}
-\begin{minipage}{.49\linewidth}
-\centering
-\includegraphics[width=0.82\textwidth]{images/eurjpyB.eps}
-\subcaption{Profit - pyB}
-\label{dwu}
-\end{minipage}
-\\
-\begin{minipage}{.49\linewidth}
-\centering
-\includegraphics[width=0.82\textwidth]{images/eurjpyC.eps}
-\subcaption{Profit - pyC}
-\label{cztero}
-\end{minipage}
-\begin{minipage}{.49\linewidth}
-\centering
-\includegraphics[width=0.82\textwidth]{images/eurjpyD.eps}
-\subcaption{Profit - pyD}
-\label{mansard}
-\end{minipage}
-\begin{minipage}{\linewidth}
-\centering
-\includegraphics[width=0.6\textwidth]{images/eurjpyS.eps}
-\subcaption{Profit - pyS}
-\label{mansard}
-\end{minipage}
-\caption{EURJPY market results}
-\end{figure}
-\FloatBarrier
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\newpage
-\begin{table}[!t]
-\caption{Profits for all strategy quadrants for FUS500}
- \begin{center}
- \begin{tabular}{|l|l|l|l|l|}
- \hline \textbf{strategy} & \textbf{profit} & \textbf{bestCalmar} & \textbf{bestMALength} & \textbf{la} \\ \hline
-S1a & 17.19 & 8.24 & 18 & 2693\\ \hline
-S1b & -9.80 & -0.74 & 54 & 2665\\ \hline
-S1c & 5.65 & 2.06 & 54 & 2280\\ \hline
-S1d & 1.87 & 0.61 & 18 & 2287\\ \hline
-S1s & 14.85 & 5.68 & Group of MA & 4945\\
-\hline \end{tabular}
- \end{center}
- \end{table}
-\FloatBarrier
-\begin{figure}[h]
-\centering
-\begin{minipage}{.49\linewidth}
-\centering
-\includegraphics[width=0.82\textwidth]{images/fus500A.eps}
-\subcaption{Profit - 00A}
-\label{jedno}
-\end{minipage}
-\begin{minipage}{.49\linewidth}
-\centering
-\includegraphics[width=0.82\textwidth]{images/fus500B.eps}
-\subcaption{Profit - 00B}
-\label{dwu}
-\end{minipage}
-\\
-\begin{minipage}{.49\linewidth}
-\centering
-\includegraphics[width=0.82\textwidth]{images/fus500C.eps}
-\subcaption{Profit - 00C}
-\label{cztero}
-\end{minipage}
-\begin{minipage}{.49\linewidth}
-\centering
-\includegraphics[width=0.82\textwidth]{images/fus500D.eps}
-\subcaption{Profit - 00D}
-\label{mansard}
-\end{minipage}
-\begin{minipage}{\linewidth}
-\centering
-\includegraphics[width=0.6\textwidth]{images/fus500S.eps}
-\subcaption{Profit - 00S}
-\label{mansard}
-\end{minipage}
-\caption{FUS500 market results}
-\end{figure}
-\FloatBarrier
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\newpage
-\begin{table}[!t]
-\caption{Profits for all strategy quadrants for GBPCHF}
- \begin{center}
- \begin{tabular}{|l|l|l|l|l|}
- \hline \textbf{strategy} & \textbf{profit} & \textbf{bestCalmar} & \textbf{bestMALength} & \textbf{la} \\ \hline
-S1a & 17.19 & 8.24 & 18 & 2693\\ \hline
-S1b & -9.80 & -0.74 & 54 & 2665\\ \hline
-S1c & 5.65 & 2.06 & 54 & 2280\\ \hline
-S1d & 1.87 & 0.61 & 18 & 2287\\ \hline
-S1s & 14.85 & 5.68 & Group of MA & 4945\\
-\hline \end{tabular}
- \end{center}
- \end{table}
-\FloatBarrier
-\begin{figure}[h]
-\centering
-\begin{minipage}{.49\linewidth}
-\centering
-\includegraphics[width=0.82\textwidth]{images/gbpchfA.eps}
-\subcaption{Profit - hfA}
-\label{jedno}
-\end{minipage}
-\begin{minipage}{.49\linewidth}
-\centering
-\includegraphics[width=0.82\textwidth]{images/gbpchfB.eps}
-\subcaption{Profit - hfB}
-\label{dwu}
-\end{minipage}
-\\
-\begin{minipage}{.49\linewidth}
-\centering
-\includegraphics[width=0.82\textwidth]{images/gbpchfC.eps}
-\subcaption{Profit - hfC}
-\label{cztero}
-\end{minipage}
-\begin{minipage}{.49\linewidth}
-\centering
-\includegraphics[width=0.82\textwidth]{images/gbpchfD.eps}
-\subcaption{Profit - hfD}
-\label{mansard}
-\end{minipage}
-\begin{minipage}{\linewidth}
-\centering
-\includegraphics[width=0.6\textwidth]{images/gbpchfS.eps}
-\subcaption{Profit - hfS}
-\label{mansard}
-\end{minipage}
-\caption{GBPCHF market results}
-\end{figure}
-\FloatBarrier
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\newpage
-\begin{table}[!t]
-\caption{Profits for all strategy quadrants for SILVER}
- \begin{center}
- \begin{tabular}{|l|l|l|l|l|}
- \hline \textbf{strategy} & \textbf{profit} & \textbf{bestCalmar} & \textbf{bestMALength} & \textbf{la} \\ \hline
-S1a & 17.19 & 8.24 & 18 & 2693\\ \hline
-S1b & -9.80 & -0.74 & 54 & 2665\\ \hline
-S1c & 5.65 & 2.06 & 54 & 2280\\ \hline
-S1d & 1.87 & 0.61 & 18 & 2287\\ \hline
-S1s & 14.85 & 5.68 & Group of MA & 4945\\
-\hline \end{tabular}
- \end{center}
- \end{table}
-\FloatBarrier
-\begin{figure}[h]
-\centering
-\begin{minipage}{.49\linewidth}
-\centering
-\includegraphics[width=0.82\textwidth]{images/silverA.eps}
-\subcaption{Profit - erA}
-\label{jedno}
-\end{minipage}
-\begin{minipage}{.49\linewidth}
-\centering
-\includegraphics[width=0.82\textwidth]{images/silverB.eps}
-\subcaption{Profit - erB}
-\label{dwu}
-\end{minipage}
-\\
-\begin{minipage}{.49\linewidth}
-\centering
-\includegraphics[width=0.82\textwidth]{images/silverC.eps}
-\subcaption{Profit - erC}
-\label{cztero}
-\end{minipage}
-\begin{minipage}{.49\linewidth}
-\centering
-\includegraphics[width=0.82\textwidth]{images/silverD.eps}
-\subcaption{Profit - erD}
-\label{mansard}
-\end{minipage}
-\begin{minipage}{\linewidth}
-\centering
-\includegraphics[width=0.6\textwidth]{images/silverS.eps}
-\subcaption{Profit - erS}
-\label{mansard}
-\end{minipage}
-\caption{SILVER market results}
-\end{figure}
-\FloatBarrier
+%\begin{table}[!t]
+%\caption{Profits for all strategy quadrants for EURJPY} 
+% \begin{center} 
+% \begin{tabular}{|l|l|l|l|l|} 
+% \hline \textbf{strategy} & \textbf{profit} & \textbf{bestCalmar} & \textbf{bestMALength} & \textbf{la} \\ \hline  
+%S1a & 26.18 & 5.59 & 24 & 2764\\ \hline 
+%S1b & -14.77 & -0.67 & 6 & 2660\\ \hline 
+%S1c & 15.74 & 2.49 & 6 & 2332\\ \hline 
+%S1d & -4.57 & -0.47 & 21 & 2226\\ \hline 
+%S1s & 22.54 & 3.25 & Group of MA & 4975\\ 
+%\hline \end{tabular} 
+% \end{center} 
+% \end{table}
+%\FloatBarrier
+%
+%\begin{figure}[h]
+%\centering
+%\begin{minipage}{.49\linewidth}
+%\centering 
+%\includegraphics[width=0.82\textwidth]{images/S1a_eurjpy.eps}
+%\subcaption{Profit - S1a}
+%\label{jedno}
+%\end{minipage}
+%\begin{minipage}{.49\linewidth}
+%\centering 
+%\includegraphics[width=0.82\textwidth]{images/S1b_eurjpy.eps}
+%\subcaption{Profit - S1b}
+%\label{dwu}
+%\end{minipage}
+%\\
+%\begin{minipage}{.49\linewidth}
+%\centering 
+%\includegraphics[width=0.82\textwidth]{images/S1c_eurjpy.eps}
+%\subcaption{Profit- S1c}
+%\label{cztero}
+%\end{minipage}
+%\begin{minipage}{.49\linewidth}
+%\centering 
+%\includegraphics[width=0.82\textwidth]{images/S1d_eurjpy.eps}
+%\subcaption{Profit - S1d}
+%\label{mansard}
+%\end{minipage}
+%\begin{minipage}{\linewidth}
+%\centering 
+%\includegraphics[width=0.6\textwidth]{images/S1s_eurjpy.eps}
+%\label{mansard}
+%\subcaption{Profit - S1s}
+%\end{minipage}
+%\caption{EURJPY market results}
+%\end{figure}
+%\FloatBarrier
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+%\newpage
+%\begin{table}[!t]
+%\caption{Profits for all strategy quadrants for USDJPY} 
+% \begin{center} 
+% \begin{tabular}{|l|l|l|l|l|} 
+% \hline \textbf{strategy} & \textbf{profit} & \textbf{bestCalmar} & \textbf{bestMALength} & \textbf{la} \\ \hline  
+%S1a & 17.19 & 8.24 & 18 & 2693\\ \hline 
+%S1b & -9.80 & -0.74 & 54 & 2665\\ \hline 
+%S1c & 5.65 & 2.06 & 54 & 2280\\ \hline 
+%S1d & 1.87 & 0.61 & 18 & 2287\\ \hline 
+%S1s & 14.85 & 5.68 & Group of MA & 4945\\ 
+%\hline \end{tabular} 
+% \end{center} 
+% \end{table}
+%\FloatBarrier
+%
+%\begin{figure}[h]
+%\centering
+%\begin{minipage}{.49\linewidth}
+%\centering 
+%\includegraphics[width=0.82\textwidth]{images/S1a_usdjpy.eps}
+%\subcaption{Profit - S1a}
+%\label{jedno}
+%\end{minipage}
+%\begin{minipage}{.49\linewidth}
+%\centering 
+%\includegraphics[width=0.82\textwidth]{images/S1b_usdjpy.eps}
+%\subcaption{Profit - S1b}
+%\label{dwu}
+%\end{minipage}
+%\\
+%\begin{minipage}{.49\linewidth}
+%\centering 
+%\includegraphics[width=0.82\textwidth]{images/S1c_usdjpy.eps}
+%\subcaption{Profit- S1c}
+%\label{cztero}
+%\end{minipage}
+%\begin{minipage}{.49\linewidth}
+%\centering 
+%\includegraphics[width=0.82\textwidth]{images/S1d_usdjpy.eps}
+%\subcaption{Profit - S1d}
+%\label{mansard}
+%\end{minipage}
+%\begin{minipage}{\linewidth}
+%\centering 
+%\includegraphics[width=0.6\textwidth]{images/S1s_usdjpy.eps}
+%\label{mansard}
+%\subcaption{Profit - S1s}
+%\end{minipage}
+%\caption{USDJPY market results}
+%\end{figure}
+%\FloatBarrier
+%
+%
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+%\newpage
+%\begin{table}[!t]
+%\caption{Profits for all strategy quadrants for GBPUSD} 
+% \begin{center} 
+% \begin{tabular}{|l|l|l|l|l|} 
+% \hline \textbf{strategy} & \textbf{profit} & \textbf{bestCalmar} & \textbf{bestMALength} & \textbf{la} \\ \hline  
+%S1a & 0.06 & 1.06 & 92 & 2588\\ \hline 
+%S1b & 0.12 & 3.41 & 5 & 2513\\ \hline 
+%S1c & 0.15 & 3.11 & 5 & 2475\\ \hline 
+%S1d & 0.02 & 0.31 & 92 & 2319\\ \hline 
+%S1s & 0.36 & 6.89 & Group of MA & 4907\\ 
+%\hline \end{tabular} 
+% \end{center} 
+% \end{table}
+%\FloatBarrier
+%
+%\begin{figure}[h]
+%\centering
+%\begin{minipage}{.49\linewidth}
+%\centering 
+%\includegraphics[width=0.82\textwidth]{images/S1a_gbpusd.eps}
+%\subcaption{Profit - S1a}
+%\label{jedno}
+%\end{minipage}
+%\begin{minipage}{.49\linewidth}
+%\centering 
+%\includegraphics[width=0.82\textwidth]{images/S1b_gbpusd.eps}
+%\subcaption{Profit - S1b}
+%\label{dwu}
+%\end{minipage}
+%\\
+%\begin{minipage}{.49\linewidth}
+%\centering 
+%\includegraphics[width=0.82\textwidth]{images/S1c_gbpusd.eps}
+%\subcaption{Profit- S1c}
+%\label{cztero}
+%\end{minipage}
+%\begin{minipage}{.49\linewidth}
+%\centering 
+%\includegraphics[width=0.82\textwidth]{images/S1d_gbpusd.eps}
+%\subcaption{Profit - S1d}
+%\label{mansard}
+%\end{minipage}
+%\begin{minipage}{\linewidth}
+%\centering 
+%\includegraphics[width=0.6\textwidth]{images/S1s_gbpusd.eps}
+%\label{mansard}
+%\subcaption{Profit - S1s}
+%\end{minipage}
+%\caption{GBPUSD market results}
+%\end{figure}
+%\FloatBarrier
+%
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+%\newpage
+%\begin{table}[!t]
+%\caption{Profits for all strategy quadrants for EURUSD} 
+% \begin{center} 
+% \begin{tabular}{|l|l|l|l|l|} 
+% \hline \textbf{strategy} & \textbf{profit} & \textbf{bestCalmar} & \textbf{bestMALength} & \textbf{la} \\ \hline  
+%S1a & 0.09 & 1.84 & 33 & 2635\\ \hline 
+%S1b & 0.01 & 0.16 & 5 & 2587\\ \hline 
+%S1c & 0.12 & 3.45 & 5 & 2406\\ \hline 
+%S1d & -0.02 & -0.49 & 33 & 2331\\ \hline 
+%S1s & 0.21 & 3.31 & Group of MA & 4966\\ 
+%\hline \end{tabular} 
+% \end{center} 
+% \end{table}
+%\FloatBarrier
+%
+%\begin{figure}[h]
+%\centering
+%\begin{minipage}{.49\linewidth}
+%\centering 
+%\includegraphics[width=0.82\textwidth]{images/S1a_eurusd.eps}
+%\subcaption{Profit - S1a}
+%\label{jedno}
+%\end{minipage}
+%\begin{minipage}{.49\linewidth}
+%\centering 
+%\includegraphics[width=0.82\textwidth]{images/S1b_eurusd.eps}
+%\subcaption{Profit - S1b}
+%\label{dwu}
+%\end{minipage}
+%\\
+%\begin{minipage}{.49\linewidth}
+%\centering 
+%\includegraphics[width=0.82\textwidth]{images/S1c_eurusd.eps}
+%\subcaption{Profit- S1c}
+%\label{cztero}
+%\end{minipage}
+%\begin{minipage}{.49\linewidth}
+%\centering 
+%\includegraphics[width=0.82\textwidth]{images/S1d_eurusd.eps}
+%\subcaption{Profit - S1d}
+%\label{mansard}
+%\end{minipage}
+%\begin{minipage}{\linewidth}
+%\centering 
+%\includegraphics[width=0.6\textwidth]{images/S1s_eurusd.eps}
+%\label{mansard}
+%\subcaption{Profit - S1s}
+%\end{minipage}
+%\caption{EURUSD market results}
+%\end{figure}
+%\FloatBarrier
+%
+%
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+%
+%
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+%\newpage
+%\begin{table}[!t]
+%\caption{Profits for all strategy quadrants for FUS500} 
+% \begin{center} 
+% \begin{tabular}{|l|l|l|l|l|} 
+% \hline \textbf{strategy} & \textbf{profit} & \textbf{bestCalmar} & \textbf{bestMALength} & \textbf{la} \\ \hline  
+%S1a & 274.89 & 5.44 & 83 & 3200\\ \hline 
+%S1b & -70.94 & -0.47 & 15 & 2798\\ \hline 
+%S1c & 291.62 & 4.26 & 15 & 2186\\ \hline 
+%S1d & -106.67 & -0.73 & 82 & 1723\\ \hline 
+%S1s & 344.29 & 2.08 & Group of MA & 4916\\ 
+%\hline \end{tabular} 
+% \end{center} 
+% \end{table}
+%\FloatBarrier
+%
+%\begin{figure}[h]
+%\centering
+%\begin{minipage}{.49\linewidth}
+%\centering 
+%\includegraphics[width=0.82\textwidth]{images/S1a_fus.eps}
+%\subcaption{Profit - S1a}
+%\label{jedno}
+%\end{minipage}
+%\begin{minipage}{.49\linewidth}
+%\centering 
+%\includegraphics[width=0.82\textwidth]{images/S1b_fus.eps}
+%\subcaption{Profit - S1b}
+%\label{dwu}
+%\end{minipage}
+%\\
+%\begin{minipage}{.49\linewidth}
+%\centering 
+%\includegraphics[width=0.82\textwidth]{images/S1c_fus.eps}
+%\subcaption{Profit- S1c}
+%\label{cztero}
+%\end{minipage}
+%\begin{minipage}{.49\linewidth}
+%\centering 
+%\includegraphics[width=0.82\textwidth]{images/S1d_fus.eps}
+%\subcaption{Profit - S1d}
+%\label{mansard}
+%\end{minipage}
+%\begin{minipage}{\linewidth}
+%\centering 
+%\includegraphics[width=0.6\textwidth]{images/S1s_fus.eps}
+%\label{mansard}
+%\subcaption{Profit - S1s}
+%\end{minipage}
+%\caption{FUS500 market results}
+%\end{figure}
+%\FloatBarrier
+%
+%
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+%\newpage
+%\begin{table}[!t]
+%\caption{Profits for all strategy quadrants for BOSSAPLN} 
+% \begin{center} 
+% \begin{tabular}{|l|l|l|l|l|} 
+% \hline \textbf{strategy} & \textbf{profit} & \textbf{bestCalmar} & \textbf{bestMALength} & \textbf{la} \\ \hline  
+%S1a & 5.87 & 1.99 & 21 & 2474\\ \hline 
+%S1b & 2.86 & 0.61 & 5 & 2416\\ \hline 
+%S1c & 10.91 & 4.33 & 5 & 2547\\ \hline 
+%S1d & -2.23 & -0.42 & 21 & 2502\\ \hline 
+%S1s & 17.91 & 4.35 & Group of MA & 4978\\ 
+%\hline \end{tabular} 
+% \end{center} 
+% \end{table}
+%\FloatBarrier
+%
+%\begin{figure}[h]
+%\centering
+%\begin{minipage}{.49\linewidth}
+%\centering 
+%\includegraphics[width=0.82\textwidth]{images/S1a_bossa.eps}
+%\subcaption{Profit - S1a}
+%\label{jedno}
+%\end{minipage}
+%\begin{minipage}{.49\linewidth}
+%\centering 
+%\includegraphics[width=0.82\textwidth]{images/S1b_bossa.eps}
+%\subcaption{Profit - S1b}
+%\label{dwu}
+%\end{minipage}
+%\\
+%\begin{minipage}{.49\linewidth}
+%\centering 
+%\includegraphics[width=0.82\textwidth]{images/S1c_bossa.eps}
+%\subcaption{Profit- S1c}
+%\label{cztero}
+%\end{minipage}
+%\begin{minipage}{.49\linewidth}
+%\centering 
+%\includegraphics[width=0.82\textwidth]{images/S1d_bossa.eps}
+%\subcaption{Profit - S1d}
+%\label{mansard}
+%\end{minipage}
+%\begin{minipage}{\linewidth}
+%\centering 
+%\includegraphics[width=0.6\textwidth]{images/S1s_bossa.eps}
+%\label{mansard}
+%\subcaption{Profit - S1s}
+%\end{minipage}
+%\caption{BOSSAPLN market results}
+%\end{figure}
+%\FloatBarrier
+%
+%
+%
+%
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+%\newpage
+%\begin{table}[!t]
+%\caption{Profits for all strategy quadrants for FGOLD} 
+% \begin{center} 
+% \begin{tabular}{|l|l|l|l|l|} 
+% \hline \textbf{strategy} & \textbf{profit} & \textbf{bestCalmar} & \textbf{bestMALength} & \textbf{la} \\ \hline  
+%S1a & 61.16 & 0.59 & 51 & 2578\\ \hline 
+%S1b & 227.58 & 2.82 & 5 & 2519\\ \hline 
+%S1c & 30.38 & 0.12 & 5 & 2470\\ \hline 
+%S1d & 248.21 & 1.52 & 51 & 2370\\ \hline 
+%S1s & 599.88 & 4.60 & Group of MA & 4948\\ 
+%\hline \end{tabular} 
+% \end{center} 
+% \end{table}
+%\FloatBarrier
+%
+%\begin{figure}[h]
+%\centering
+%\begin{minipage}{.49\linewidth}
+%\centering 
+%\includegraphics[width=0.82\textwidth]{images/S1a_gold.eps}
+%\subcaption{Profit - S1a}
+%\label{jedno}
+%\end{minipage}
+%\begin{minipage}{.49\linewidth}
+%\centering 
+%\includegraphics[width=0.82\textwidth]{images/S1b_gold.eps}
+%\subcaption{Profit - S1b}
+%\label{dwu}
+%\end{minipage}
+%\\
+%\begin{minipage}{.49\linewidth}
+%\centering 
+%\includegraphics[width=0.82\textwidth]{images/S1c_gold.eps}
+%\subcaption{Profit- S1c}
+%\label{cztero}
+%\end{minipage}
+%\begin{minipage}{.49\linewidth}
+%\centering 
+%\includegraphics[width=0.82\textwidth]{images/S1d_gold.eps}
+%\subcaption{Profit - S1d}
+%\label{mansard}
+%\end{minipage}
+%\begin{minipage}{\linewidth}
+%\centering 
+%\includegraphics[width=0.6\textwidth]{images/S1s_gold.eps}
+%\label{mansard}
+%\subcaption{Profit - S1s}
+%\end{minipage}
+%\caption{FGOLD market results}
+%\end{figure}
+%\FloatBarrier
+%
+%
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+%\newpage
+%\begin{table}[!t]
+%\caption{Profits for all strategy quadrants for FSILVER} 
+%\begin{center}
+% \begin{tabular}{|l|l|l|l|l|} 
+% \hline \textbf{strategy} & \textbf{profit} & \textbf{bestCalmar} & \textbf{bestMALength} & \textbf{la} \\ \hline  
+%S1a & -5.31 & -0.65 & 81 & 2582\\ \hline 
+%S1b & 17.22 & 5.86 & 10 & 2508\\ \hline 
+%S1c & 4.17 & 0.56 & 10 & 2473\\ \hline 
+%S1d & 6.95 & 1.33 & 81 & 2336\\ \hline 
+%S1s & 21.96 & 5.55 & Group of MA & 4918\\ 
+%\hline \end{tabular} 
+% \end{center} 
+% \end{table}
+%\FloatBarrier
+%
+%\begin{figure}[h]
+%\centering
+%\begin{minipage}{.49\linewidth}
+%\centering 
+%\includegraphics[width=0.82\textwidth]{images/S1a_silver.eps}
+%\subcaption{Profit - S1a}
+%\label{jedno}
+%\end{minipage}
+%\begin{minipage}{.49\linewidth}
+%\centering 
+%\includegraphics[width=0.82\textwidth]{images/S1b_silver.eps}
+%\subcaption{Profit - S1b}
+%\label{dwu}
+%\end{minipage}
+%\\
+%\begin{minipage}{.49\linewidth}
+%\centering 
+%\includegraphics[width=0.82\textwidth]{images/S1c_silver.eps}
+%\subcaption{Profit- S1c}
+%\label{cztero}
+%\end{minipage}
+%\begin{minipage}{.49\linewidth}
+%\centering 
+%\includegraphics[width=0.82\textwidth]{images/S1d_silver.eps}
+%\subcaption{Profit - S1d}
+%\label{mansard}
+%\end{minipage}
+%\begin{minipage}{\linewidth}
+%\centering 
+%\includegraphics[width=0.6\textwidth]{images/S1s_silver.eps}
+%\label{mansard}
+%\subcaption{Profit - S1s}
+%\end{minipage}
+%\caption{FSILVER market results}
+%\end{figure}
+%\FloatBarrier
+%
+%
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+%\newpage
+%\begin{table}[!t]
+%\caption{Profits for all strategy quadrants for CADCHF}
+% \begin{center}
+% \begin{tabular}{|l|l|l|l|l|}
+% \hline \textbf{strategy} & \textbf{profit} & \textbf{bestCalmar} & \textbf{bestMALength} & \textbf{la} \\ \hline
+%S1a & 17.19 & 8.24 & 18 & 2693\\ \hline
+%S1b & -9.80 & -0.74 & 54 & 2665\\ \hline
+%S1c & 5.65 & 2.06 & 54 & 2280\\ \hline
+%S1d & 1.87 & 0.61 & 18 & 2287\\ \hline
+%S1s & 14.85 & 5.68 & Group of MA & 4945\\
+%\hline \end{tabular}
+% \end{center}
+% \end{table}
+%\FloatBarrier
+%
+%\begin{figure}[h]
+%\centering
+%\begin{minipage}{.49\linewidth}
+%\centering
+%\includegraphics[width=0.82\textwidth]{images/cadchfS1a.eps}
+%\subcaption{Profit - S1a}
+%\label{jedno}
+%\end{minipage}
+%\begin{minipage}{.49\linewidth}
+%\centering
+%\includegraphics[width=0.82\textwidth]{images/cadchfS1b.eps}
+%\subcaption{Profit - S1b}
+%\label{dwu}
+%\end{minipage}
+%\\
+%\begin{minipage}{.49\linewidth}
+%\centering
+%\includegraphics[width=0.82\textwidth]{images/cadchfS1c.eps}
+%\subcaption{Profit - S1c}
+%\label{cztero}
+%\end{minipage}
+%\begin{minipage}{.49\linewidth}
+%\centering
+%\includegraphics[width=0.82\textwidth]{images/cadchfS1d.eps}
+%\subcaption{Profit - S1d}
+%\label{mansard}
+%\end{minipage}
+%\begin{minipage}{\linewidth}
+%\centering
+%\includegraphics[width=0.6\textwidth]{images/cadchfS1s.eps}
+%\label{mansard}
+%\subcaption{Profit - S1s}
+%\end{minipage}
+%\caption{CADCHF market results}
+%\end{figure}
+%\FloatBarrier
+%
+%
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+%\newpage
+%\begin{table}[!t]
+%\caption{Profits for all strategy quadrants for FCOPPER}
+% \begin{center}
+% \begin{tabular}{|l|l|l|l|l|}
+% \hline \textbf{strategy} & \textbf{profit} & \textbf{bestCalmar} & \textbf{bestMALength} & \textbf{la} \\ \hline
+%S1a & 17.19 & 8.24 & 18 & 2693\\ \hline
+%S1b & -9.80 & -0.74 & 54 & 2665\\ \hline
+%S1c & 5.65 & 2.06 & 54 & 2280\\ \hline
+%S1d & 1.87 & 0.61 & 18 & 2287\\ \hline
+%S1s & 14.85 & 5.68 & Group of MA & 4945\\
+%\hline \end{tabular}
+% \end{center}
+% \end{table}
+%\FloatBarrier
+%\begin{figure}[h]
+%\centering
+%\begin{minipage}{.49\linewidth}
+%\centering
+%\includegraphics[width=0.82\textwidth]{images/fcopperS1a.eps}
+%\subcaption{Profit - S1a}
+%\label{jedno}
+%\end{minipage}
+%\begin{minipage}{.49\linewidth}
+%\centering
+%\includegraphics[width=0.82\textwidth]{images/fcopperS1b.eps}
+%\subcaption{Profit - S1b}
+%\label{dwu}
+%\end{minipage}
+%\\
+%\begin{minipage}{.49\linewidth}
+%\centering
+%\includegraphics[width=0.82\textwidth]{images/fcopperS1c.eps}
+%\subcaption{Profit - S1c}
+%\label{cztero}
+%\end{minipage}
+%\begin{minipage}{.49\linewidth}
+%\centering
+%\includegraphics[width=0.82\textwidth]{images/fcopperS1d.eps}
+%\subcaption{Profit - S1d}
+%\label{mansard}
+%\end{minipage}
+%\begin{minipage}{\linewidth}
+%\centering
+%\includegraphics[width=0.6\textwidth]{images/fcopperS1s.eps}
+%\subcaption{Profit - S1s}
+%\label{mansard}
+%\end{minipage}
+%\caption{FCOPPER market results}
+%\end{figure}
+%\FloatBarrier
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+%\newpage
+%\begin{table}[!t]
+%\caption{Profits for all strategy quadrants for FCORN}
+% \begin{center}
+% \begin{tabular}{|l|l|l|l|l|}
+% \hline \textbf{strategy} & \textbf{profit} & \textbf{bestCalmar} & \textbf{bestMALength} & \textbf{la} \\ \hline
+%S1a & 17.19 & 8.24 & 18 & 2693\\ \hline
+%S1b & -9.80 & -0.74 & 54 & 2665\\ \hline
+%S1c & 5.65 & 2.06 & 54 & 2280\\ \hline
+%S1d & 1.87 & 0.61 & 18 & 2287\\ \hline
+%S1s & 14.85 & 5.68 & Group of MA & 4945\\
+%\hline \end{tabular}
+% \end{center}
+% \end{table}
+%\FloatBarrier
+%\begin{figure}[h]
+%\centering
+%\begin{minipage}{.49\linewidth}
+%\centering
+%\includegraphics[width=0.82\textwidth]{images/fcornS1a.eps}
+%\subcaption{Profit - S1a}
+%\label{jedno}
+%\end{minipage}
+%\begin{minipage}{.49\linewidth}
+%\centering
+%\includegraphics[width=0.82\textwidth]{images/fcornS1b.eps}
+%\subcaption{Profit - S1b}
+%\label{dwu}
+%\end{minipage}
+%\\
+%\begin{minipage}{.49\linewidth}
+%\centering
+%\includegraphics[width=0.82\textwidth]{images/fcornS1c.eps}
+%\subcaption{Profit - S1c}
+%\label{cztero}
+%\end{minipage}
+%\begin{minipage}{.49\linewidth}
+%\centering
+%\includegraphics[width=0.82\textwidth]{images/fcornS1d.eps}
+%\subcaption{Profit - S1d}
+%\label{mansard}
+%\end{minipage}
+%\begin{minipage}{\linewidth}
+%\centering
+%\includegraphics[width=0.6\textwidth]{images/fcornS1s.eps}
+%\subcaption{Profit - S1s}
+%\label{mansard}
+%\end{minipage}
+%\caption{FCORN market results}
+%\end{figure}
+%\FloatBarrier
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+%\newpage
+%\begin{table}[!t]
+%\caption{Profits for all strategy quadrants for NZDJPY}
+% \begin{center}
+% \begin{tabular}{|l|l|l|l|l|}
+% \hline \textbf{strategy} & \textbf{profit} & \textbf{bestCalmar} & \textbf{bestMALength} & \textbf{la} \\ \hline
+%S1a & 17.19 & 8.24 & 18 & 2693\\ \hline
+%S1b & -9.80 & -0.74 & 54 & 2665\\ \hline
+%S1c & 5.65 & 2.06 & 54 & 2280\\ \hline
+%S1d & 1.87 & 0.61 & 18 & 2287\\ \hline
+%S1s & 14.85 & 5.68 & Group of MA & 4945\\
+%\hline \end{tabular}
+% \end{center}
+% \end{table}
+%\FloatBarrier
+%\begin{figure}[h]
+%\centering
+%\begin{minipage}{.49\linewidth}
+%\centering
+%\includegraphics[width=0.82\textwidth]{images/nzdjpyS1a.eps}
+%\subcaption{Profit - S1a}
+%\label{jedno}
+%\end{minipage}
+%\begin{minipage}{.49\linewidth}
+%\centering
+%\includegraphics[width=0.82\textwidth]{images/nzdjpyS1b.eps}
+%\subcaption{Profit - S1b}
+%\label{dwu}
+%\end{minipage}
+%\\
+%\begin{minipage}{.49\linewidth}
+%\centering
+%\includegraphics[width=0.82\textwidth]{images/nzdjpyS1c.eps}
+%\subcaption{Profit - S1c}
+%\label{cztero}
+%\end{minipage}
+%\begin{minipage}{.49\linewidth}
+%\centering
+%\includegraphics[width=0.82\textwidth]{images/nzdjpyS1d.eps}
+%\subcaption{Profit - S1d}
+%\label{mansard}
+%\end{minipage}
+%\begin{minipage}{\linewidth}
+%\centering
+%\includegraphics[width=0.6\textwidth]{images/nzdjpyS1s.eps}
+%\subcaption{Profit - S1s}
+%\label{mansard}
+%\end{minipage}
+%\caption{NZDJPY market results}
+%\end{figure}
+%\FloatBarrier
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+%\newpage
+%\begin{table}[!t]
+%\caption{Profits for all strategy quadrants for USDCAD}
+% \begin{center}
+% \begin{tabular}{|l|l|l|l|l|}
+% \hline \textbf{strategy} & \textbf{profit} & \textbf{bestCalmar} & \textbf{bestMALength} & \textbf{la} \\ \hline
+%S1a & 17.19 & 8.24 & 18 & 2693\\ \hline
+%S1b & -9.80 & -0.74 & 54 & 2665\\ \hline
+%S1c & 5.65 & 2.06 & 54 & 2280\\ \hline
+%S1d & 1.87 & 0.61 & 18 & 2287\\ \hline
+%S1s & 14.85 & 5.68 & Group of MA & 4945\\
+%\hline \end{tabular}
+% \end{center}
+% \end{table}
+%\FloatBarrier
+%\begin{figure}[h]
+%\centering
+%\begin{minipage}{.49\linewidth}
+%\centering
+%\includegraphics[width=0.82\textwidth]{images/usdcadS1a.eps}
+%\subcaption{Profit - S1a}
+%\label{jedno}
+%\end{minipage}
+%\begin{minipage}{.49\linewidth}
+%\centering
+%\includegraphics[width=0.82\textwidth]{images/usdcadS1b.eps}
+%\subcaption{Profit - S1b}
+%\label{dwu}
+%\end{minipage}
+%\\
+%\begin{minipage}{.49\linewidth}
+%\centering
+%\includegraphics[width=0.82\textwidth]{images/usdcadS1c.eps}
+%\subcaption{Profit - S1c}
+%\label{cztero}
+%\end{minipage}
+%\begin{minipage}{.49\linewidth}
+%\centering
+%\includegraphics[width=0.82\textwidth]{images/usdcadS1d.eps}
+%\subcaption{Profit - S1d}
+%\label{mansard}
+%\end{minipage}
+%\begin{minipage}{\linewidth}
+%\centering
+%\includegraphics[width=0.6\textwidth]{images/usdcadS1s.eps}
+%\subcaption{Profit - S1s}
+%\label{mansard}
+%\end{minipage}
+%\caption{USDCAD market results}
+%\end{figure}
+%\FloatBarrier
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+%\newpage
+%\begin{table}[!t]
+%\caption{Profits for all strategy quadrants for CHFJPY}
+% \begin{center}
+% \begin{tabular}{|l|l|l|l|l|}
+% \hline \textbf{strategy} & \textbf{profit} & \textbf{bestCalmar} & \textbf{bestMALength} & \textbf{la} \\ \hline
+%S1a & 17.19 & 8.24 & 18 & 2693\\ \hline
+%S1b & -9.80 & -0.74 & 54 & 2665\\ \hline
+%S1c & 5.65 & 2.06 & 54 & 2280\\ \hline
+%S1d & 1.87 & 0.61 & 18 & 2287\\ \hline
+%S1s & 14.85 & 5.68 & Group of MA & 4945\\
+%\hline \end{tabular}
+% \end{center}
+% \end{table}
+%\FloatBarrier
+%\begin{figure}[h]
+%\centering
+%\begin{minipage}{.49\linewidth}
+%\centering
+%\includegraphics[width=0.82\textwidth]{images/chfjpyA.eps}
+%\subcaption{Profit - pyA}
+%\label{jedno}
+%\end{minipage}
+%\begin{minipage}{.49\linewidth}
+%\centering
+%\includegraphics[width=0.82\textwidth]{images/chfjpyB.eps}
+%\subcaption{Profit - pyB}
+%\label{dwu}
+%\end{minipage}
+%\\
+%\begin{minipage}{.49\linewidth}
+%\centering
+%\includegraphics[width=0.82\textwidth]{images/chfjpyC.eps}
+%\subcaption{Profit - pyC}
+%\label{cztero}
+%\end{minipage}
+%\begin{minipage}{.49\linewidth}
+%\centering
+%\includegraphics[width=0.82\textwidth]{images/chfjpyD.eps}
+%\subcaption{Profit - pyD}
+%\label{mansard}
+%\end{minipage}
+%\begin{minipage}{\linewidth}
+%\centering
+%\includegraphics[width=0.6\textwidth]{images/chfjpyS.eps}
+%\subcaption{Profit - pyS}
+%\label{mansard}
+%\end{minipage}
+%\caption{CHFJPY market results}
+%\end{figure}
+%\FloatBarrier
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+%\newpage
+%\begin{table}[!t]
+%\caption{Profits for all strategy quadrants for EURJPY}
+% \begin{center}
+% \begin{tabular}{|l|l|l|l|l|}
+% \hline \textbf{strategy} & \textbf{profit} & \textbf{bestCalmar} & \textbf{bestMALength} & \textbf{la} \\ \hline
+%S1a & 17.19 & 8.24 & 18 & 2693\\ \hline
+%S1b & -9.80 & -0.74 & 54 & 2665\\ \hline
+%S1c & 5.65 & 2.06 & 54 & 2280\\ \hline
+%S1d & 1.87 & 0.61 & 18 & 2287\\ \hline
+%S1s & 14.85 & 5.68 & Group of MA & 4945\\
+%\hline \end{tabular}
+% \end{center}
+% \end{table}
+%\FloatBarrier
+%\begin{figure}[h]
+%\centering
+%\begin{minipage}{.49\linewidth}
+%\centering
+%\includegraphics[width=0.82\textwidth]{images/eurjpyA.eps}
+%\subcaption{Profit - pyA}
+%\label{jedno}
+%\end{minipage}
+%\begin{minipage}{.49\linewidth}
+%\centering
+%\includegraphics[width=0.82\textwidth]{images/eurjpyB.eps}
+%\subcaption{Profit - pyB}
+%\label{dwu}
+%\end{minipage}
+%\\
+%\begin{minipage}{.49\linewidth}
+%\centering
+%\includegraphics[width=0.82\textwidth]{images/eurjpyC.eps}
+%\subcaption{Profit - pyC}
+%\label{cztero}
+%\end{minipage}
+%\begin{minipage}{.49\linewidth}
+%\centering
+%\includegraphics[width=0.82\textwidth]{images/eurjpyD.eps}
+%\subcaption{Profit - pyD}
+%\label{mansard}
+%\end{minipage}
+%\begin{minipage}{\linewidth}
+%\centering
+%\includegraphics[width=0.6\textwidth]{images/eurjpyS.eps}
+%\subcaption{Profit - pyS}
+%\label{mansard}
+%\end{minipage}
+%\caption{EURJPY market results}
+%\end{figure}
+%\FloatBarrier
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+%\newpage
+%\begin{table}[!t]
+%\caption{Profits for all strategy quadrants for FUS500}
+% \begin{center}
+% \begin{tabular}{|l|l|l|l|l|}
+% \hline \textbf{strategy} & \textbf{profit} & \textbf{bestCalmar} & \textbf{bestMALength} & \textbf{la} \\ \hline
+%S1a & 17.19 & 8.24 & 18 & 2693\\ \hline
+%S1b & -9.80 & -0.74 & 54 & 2665\\ \hline
+%S1c & 5.65 & 2.06 & 54 & 2280\\ \hline
+%S1d & 1.87 & 0.61 & 18 & 2287\\ \hline
+%S1s & 14.85 & 5.68 & Group of MA & 4945\\
+%\hline \end{tabular}
+% \end{center}
+% \end{table}
+%\FloatBarrier
+%\begin{figure}[h]
+%\centering
+%\begin{minipage}{.49\linewidth}
+%\centering
+%\includegraphics[width=0.82\textwidth]{images/fus500A.eps}
+%\subcaption{Profit - 00A}
+%\label{jedno}
+%\end{minipage}
+%\begin{minipage}{.49\linewidth}
+%\centering
+%\includegraphics[width=0.82\textwidth]{images/fus500B.eps}
+%\subcaption{Profit - 00B}
+%\label{dwu}
+%\end{minipage}
+%\\
+%\begin{minipage}{.49\linewidth}
+%\centering
+%\includegraphics[width=0.82\textwidth]{images/fus500C.eps}
+%\subcaption{Profit - 00C}
+%\label{cztero}
+%\end{minipage}
+%\begin{minipage}{.49\linewidth}
+%\centering
+%\includegraphics[width=0.82\textwidth]{images/fus500D.eps}
+%\subcaption{Profit - 00D}
+%\label{mansard}
+%\end{minipage}
+%\begin{minipage}{\linewidth}
+%\centering
+%\includegraphics[width=0.6\textwidth]{images/fus500S.eps}
+%\subcaption{Profit - 00S}
+%\label{mansard}
+%\end{minipage}
+%\caption{FUS500 market results}
+%\end{figure}
+%\FloatBarrier
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+%\newpage
+%\begin{table}[!t]
+%\caption{Profits for all strategy quadrants for GBPCHF}
+% \begin{center}
+% \begin{tabular}{|l|l|l|l|l|}
+% \hline \textbf{strategy} & \textbf{profit} & \textbf{bestCalmar} & \textbf{bestMALength} & \textbf{la} \\ \hline
+%S1a & 17.19 & 8.24 & 18 & 2693\\ \hline
+%S1b & -9.80 & -0.74 & 54 & 2665\\ \hline
+%S1c & 5.65 & 2.06 & 54 & 2280\\ \hline
+%S1d & 1.87 & 0.61 & 18 & 2287\\ \hline
+%S1s & 14.85 & 5.68 & Group of MA & 4945\\
+%\hline \end{tabular}
+% \end{center}
+% \end{table}
+%\FloatBarrier
+%\begin{figure}[h]
+%\centering
+%\begin{minipage}{.49\linewidth}
+%\centering
+%\includegraphics[width=0.82\textwidth]{images/gbpchfA.eps}
+%\subcaption{Profit - hfA}
+%\label{jedno}
+%\end{minipage}
+%\begin{minipage}{.49\linewidth}
+%\centering
+%\includegraphics[width=0.82\textwidth]{images/gbpchfB.eps}
+%\subcaption{Profit - hfB}
+%\label{dwu}
+%\end{minipage}
+%\\
+%\begin{minipage}{.49\linewidth}
+%\centering
+%\includegraphics[width=0.82\textwidth]{images/gbpchfC.eps}
+%\subcaption{Profit - hfC}
+%\label{cztero}
+%\end{minipage}
+%\begin{minipage}{.49\linewidth}
+%\centering
+%\includegraphics[width=0.82\textwidth]{images/gbpchfD.eps}
+%\subcaption{Profit - hfD}
+%\label{mansard}
+%\end{minipage}
+%\begin{minipage}{\linewidth}
+%\centering
+%\includegraphics[width=0.6\textwidth]{images/gbpchfS.eps}
+%\subcaption{Profit - hfS}
+%\label{mansard}
+%\end{minipage}
+%\caption{GBPCHF market results}
+%\end{figure}
+%\FloatBarrier
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+%\newpage
+%\begin{table}[!t]
+%\caption{Profits for all strategy quadrants for SILVER}
+% \begin{center}
+% \begin{tabular}{|l|l|l|l|l|}
+% \hline \textbf{strategy} & \textbf{profit} & \textbf{bestCalmar} & \textbf{bestMALength} & \textbf{la} \\ \hline
+%S1a & 17.19 & 8.24 & 18 & 2693\\ \hline
+%S1b & -9.80 & -0.74 & 54 & 2665\\ \hline
+%S1c & 5.65 & 2.06 & 54 & 2280\\ \hline
+%S1d & 1.87 & 0.61 & 18 & 2287\\ \hline
+%S1s & 14.85 & 5.68 & Group of MA & 4945\\
+%\hline \end{tabular}
+% \end{center}
+% \end{table}
+%\FloatBarrier
+%\begin{figure}[h]
+%\centering
+%\begin{minipage}{.49\linewidth}
+%\centering
+%\includegraphics[width=0.82\textwidth]{images/silverA.eps}
+%\subcaption{Profit - erA}
+%\label{jedno}
+%\end{minipage}
+%\begin{minipage}{.49\linewidth}
+%\centering
+%\includegraphics[width=0.82\textwidth]{images/silverB.eps}
+%\subcaption{Profit - erB}
+%\label{dwu}
+%\end{minipage}
+%\\
+%\begin{minipage}{.49\linewidth}
+%\centering
+%\includegraphics[width=0.82\textwidth]{images/silverC.eps}
+%\subcaption{Profit - erC}
+%\label{cztero}
+%\end{minipage}
+%\begin{minipage}{.49\linewidth}
+%\centering
+%\includegraphics[width=0.82\textwidth]{images/silverD.eps}
+%\subcaption{Profit - erD}
+%\label{mansard}
+%\end{minipage}
+%\begin{minipage}{\linewidth}
+%\centering
+%\includegraphics[width=0.6\textwidth]{images/silverS.eps}
+%\subcaption{Profit - erS}
+%\label{mansard}
+%\end{minipage}
+%\caption{SILVER market results}
+%\end{figure}
+%\FloatBarrier
 

### 2013-11-12 Article/Article20131011/sources/PP_Str_Podsumowanie.m
PP - v.6.

@@ -1,0 +1,347 @@
+%Tomasz Nyczaj 2013 Podsumowanie 4 substrategii
+
+%Dane:
+eurusd1h020313;
+size(C)
+
+%Inicjalizacja zmiennych, aby nie powiêkszaæ macierzy w pêtlach
+R1=zeros(1,6000);
+R1a=zeros(1,6000);
+R1b=zeros(1,6000);
+vol1=zeros(1,6000);
+v1=zeros(1,6000);
+R2=zeros(1,6000);
+R2a=zeros(1,6000);
+R2b=zeros(1,6000);
+vol2=zeros(1,6000);
+v2=zeros(1,6000);
+R3=zeros(1,6000);
+R3a=zeros(1,6000);
+R3b=zeros(1,6000);
+vol3=zeros(1,6000);
+v3=zeros(1,6000);
+R4=zeros(1,6000);
+R4a=zeros(1,6000);
+R4b=zeros(1,6000);
+vol4=zeros(1,6000);
+v4=zeros(1,6000);
+P=zeros(1,6000);
+RR1=zeros(1,6000);
+RR2=zeros(1,6000);
+SS1=zeros(1,6000);
+SS2=zeros(1,6000);
+sumR1=zeros(1,6000);
+sumR1a=zeros(1,6000);
+sumR2=zeros(1,6000);
+sumR2a=zeros(1,6000);
+sumR3=zeros(1,6000);
+sumR3a=zeros(1,6000);
+sumR4=zeros(1,6000);
+sumR4a=zeros(1,6000);
+suma=zeros(1,6000);
+spread=0.0002;
+
+lA=0;
+lB=0;
+lC=0;
+lD=0;
+TPA=0;
+TPB=0;
+TPC=0;
+TPD=0;
+FPA=0;
+FPB=0;
+FPC=0;
+FPD=0;
+TNA=0;
+TNB=0;
+TNC=0;
+TND=0;
+FNA=0;
+FNB=0;
+FNC=0;
+FND=0;
+
+k1=47;
+t1=22;
+l1=165;
+b1=0.0054;
+vp1=-52;
+
+k2=178;
+t2=139;
+l2=31;
+b2=0.0016;
+vp2=-246;
+
+k3=52;
+t3=23;
+l3=177;
+b3=0.0018;
+vp3=-129;
+
+k4=91;
+t4=2;
+l4=76;
+b4=0.0072;
+vp4=-190;
+
[…]

### 2013-11-12 Matlabs/Indicators/LB/ATR/ROC_AB.tex

\documentclass[12pt,a4paper]{article}
\usepackage{polski}
\usepackage[utf8]{inputenc}
\usepackage{amsmath}
\usepackage{amssymb}
\usepackage{amsfonts}
\usepackage{graphicx}
\usepackage{placeins}
\usepackage{listings}
\usepackage[svgnames]{xcolor}
 \lstset{literate={ą}{{\k{a}}}1 {ć}{{\'c}}1 {ę}{{\k{e}}}1 {ł}{{\l{}}}1 {ń}{{\'n}}1 {ó}{{\'o}}1 {ś}{{\'s}}1 {ż}{{\.z}}1 {ź}{{\'z}}1 {Ą}{{\k{A}}}1 {Ć}{{\'C}}1 {Ę}{{\k{E}}}1 {Ł}{{\L{}}}1 {Ń}{{\'N}}1 {Ó}{{\'O}}1 {Ś}{{\'S}}1 {Ż}{{\.Z}}1 {Ź}{{\'Z}}1 }
 \lstset{breaklines=true}
\lstset{language=Matlab,
  keywords={break,case,catch,continue,else,elseif,end,for,function,
     global,if,otherwise,persistent,return,switch,try,while},
  basicstyle=\ttfamily,
  keywordstyle=\color{blue},
  commentstyle=\color{DarkGreen},
  stringstyle=\color{dkgreen},
  numbers=left,
  numberstyle=\tiny\color{gray},
  stepnumber=1,
  numbersep=10pt,
  backgroundcolor=\color{white},
  tabsize=4,
  showspaces=false,
  showstringspaces=false}

\begin {document}
\begin{center}
\begin{large}
ATR --Average True Rang-  opis wskaźnika  \\
\end{large}
Łukasz Brzosko
\end{center}
%\baselineskip=22pt

Average True Range - średni zakres zmian. Jest to wskaźnik obliczający zmienność cen w ujęciu bezwględnym.  Wykorzystywany jest do wychwycenia zmienności kursu. Wskaźnik ATR oblicza się jako średnią z rzeczywistego zakresu zmian (TR - True Range), który jest największą wartością z następujących trzech wielkości : odległością pomiędzy poprzednią ceną zamknięcia (Close) a dzisiejszym minimum (Low),odległością pomiędzy dzisiejszym maksimum (High) a poprzednią ceną zamknięcia (Close),odległością pomiędzy dzisiejszym maksimum (High) i minimum (Low). Wskaźnik jest używany do przewidywania lokalnych szczytów i dołków - jego wartość jest często wysoka i osiąga szczyt przed lokalnym minimum lub maksimum kursu . Także wysoka wartość wskaźnika podczas gwałtownego spadku lub wzrostu może zapowiadać dłuższą zmianę trendu. Niskie wartości wskaźnika potwierdzają trend horyzontalny.

\noindent

\noindent Poniższy listing przedstawia zaimplementowaną strategię w MATLAB-ie.
\begin{scriptsize}
\begin{lstlisting}

%Dane:
tStart=tic;
cSizes = size(C);
candlesCount = cSizes(1);
kon=candlesCount-1;
sumRa=zeros(1,candlesCount);
Ra=zeros(1,candlesCount);
pocz=50;
la=0; %liczba otwieranych pozycji
lastCandle = kon-16;
recordReturn=0; %rekord zysku
recordDrawdown=0; %rekord obsuniecia
pic1 = false;
obv=C(pocz-1,5)
for i=pocz:lastCandle

       if(C(i,4)>C(i-1,4))
       obv_tab(i)=obv+C(i,5);
       obv=obv_tab(i);
       end
       if(C(i,4)<C(i-1,4))
       obv_tab(i)=obv-C(i,5);
       obv=obv_tab(i);
       end

end

for i=100:lastCandle
obv_max(i)=max([obv_tab(i-14) obv_tab(i-13) obv_tab(i-12) obv_tab(i-11) obv_tab(i-10) obv_tab(i-9) obv_tab(i-8) obv_tab(i-7) obv_tab(i-6) obv_tab(i-5) obv_tab(i-4) obv_tab(i-3) obv_tab(i-2) obv_tab(i-1)]);
end

for i=100:lastCandle

            if (obv_tab(i)>obv_max(i))
            Ra(i)=C(i+1,4)-C(i+1,1)-spread; %zysk z i-tej pozycji long zamykanej na zamknieciu po paramADuration kroku

            la=la+1;

            end
    sumRa(i)=sumRa(i-1) + Ra(i); %krzywa narastania kapita3u

    if sumRa(i)>recordReturn
        recordReturn=sumRa(i);
    end

    if sumRa(i)-recordReturn<recordDrawdown
        recordDrawdown=sumRa(i)-recordReturn; %obsuniecie maksymalne
    end
end

sumReturn=sumRa(lastCandle);

\end{lstlisting}
\end{scriptsize}

Na podstawie zebranych informacji dotyczących wskaźnika $ATR$ utworzono prostą strategię inwestycyjną bazującą na regule: Obliczono średnią ATR z 14 okresów i porównywano ją z wartością bezwględną z różnicy pomiędzy ceną otwarcia z aktualnej świecy, a ceną zaknięcia z poprzedzającej ceny. Jeżeli średnia była większa od wartości bezwględnej to zawierano transakcję kupna. Badania zostały przeprowadzone na parze walutowej $EURCZK$ (szereg czasowy przedstawiony na rysunku \ref{rysunek2}). \\
\begin{figure}[h!]
\centering
\includegraphics[width = \textwidth]{podzialDanych.png}
\caption{Badany szereg czasowy}
\label{rysunek2}
\end{figure}
\FloatBarrier
W przeprowadzonych badaniach przyjęto optymalną wartość parametru okresów do obliczenia wskaźnika ATR =14, następnie weryfikowano otrzymane wyniki na okresie testowym. 
\newpage
\noindent \textbf{I Wyniki badań .}\\
\begin{figure}[h!]
\centering
\includegraphics[width = 0.6\textwidth]{ROC_EURJPY_LS_SearchBestK_zysk.png}
\caption{Zysk skumulowany EURCZK na okresie testowym dla pozycji długich. }
\end{figure}
\FloatBarrier
\begin{verbatim}

Zysk skumulowany          18.4184
Calmar                     2.3641
liczba otwartych pozycji  8777

\end{verbatim}

\end {document}

### 2013-11-12 Matlabs/Indicators/LB/OBV/ROC_AB.tex

--- 2013-11-12 Matlabs/Indicators/LB/ATR/ROC_AB.tex
@@
 \begin{large}
-ATR --Average True Rang-  opis wskaźnika  \\
+OBV -- On Balance Volume-  opis wskaźnika  \\
 \end{large}
@@
 
-Average True Range - średni zakres zmian.
-Jest to wskaźnik obliczający zmienność cen w ujęciu bezwględnym.
-Wykorzystywany jest do wychwycenia zmienności kursu.
-Wskaźnik ATR oblicza się jako średnią z rzeczywistego zakresu zmian (TR - True Range), który jest największą wartością z następujących trzech wielkości : odległością pomiędzy poprzednią ceną zamknięcia (Close) a dzisiejszym minimum (Low),odległością pomiędzy dzisiejszym maksimum (High) a poprzednią ceną zamknięcia (Close),odległością pomiędzy dzisiejszym maksimum (High) i minimum (Low).
-Wskaźnik jest używany do przewidywania lokalnych szczytów i dołków - jego wartość jest często wysoka i osiąga szczyt przed lokalnym minimum lub maksimum kursu .
-Także wysoka wartość wskaźnika podczas gwałtownego spadku lub wzrostu może zapowiadać dłuższą zmianę trendu.
-Niskie wartości wskaźnika potwierdzają trend horyzontalny.
+On Balance Volume - równowaga wolumenu.
+Jest to wskaźnik opierający się na wolumenie.
+Sesjom wzrostowym towarzyszy wzrost wolumenu, natomiast sesjom zniżkowym spadek.
+Zmniejszanie obrotów przy wysokiem poziomie ceny instrumentu jest często interpretowane jako sygnał zmiany kierunku i zbliżających się sesjach spadkowych, a w przypadku spadków instrumentu i spadków obrotu, może to być sygnał, że jest to lokalny dołek i nastąpi zwrot ku górze.
+Istota wskaźnika polega na dodawaniu wolumenu przy sesjach wzrostowych wolumenu, a odejmowaniu wolumenu przy sesjach spadkowych.
+OBV jest liczone według następujących reguł   : C  większa od ceny C [-1] to OBV = OBV [-1] + V, Jeżeli C mniejsza od C [-1] to OBV = OBV [-1] - V, Jeżeli C równa się C [-1] to OBV = OBV [-1]
 
@@
 tStart=tic;
+
 cSizes = size(C);
@@
 kon=candlesCount-1;
+
 sumRa=zeros(1,candlesCount);
@@
 
-sumReturn=sumRa(lastCandle);
-
 \end{lstlisting}
@@
 
-Na podstawie zebranych informacji dotyczących wskaźnika $ATR$ utworzono prostą strategię inwestycyjną bazującą na regule: Obliczono średnią ATR z 14 okresów i porównywano ją z wartością bezwględną z różnicy pomiędzy ceną otwarcia z aktualnej świecy, a ceną zaknięcia z poprzedzającej ceny.
-Jeżeli średnia była większa od wartości bezwględnej to zawierano transakcję kupna.
+Na podstawie zebranych informacji dotyczących wskaźnika $OBV$ utworzono prostą strategię inwestycyjną bazującą na regule: Obliczono maksymalną wartość OBV z 14 okresów i porównywano ją z wartością bieżącą OBV.
+Jeżeli wartość bieżąca OBV była większa od wartości maksymalnej z 14 okresów, to zawierano transakcję kupna.
 Badania zostały przeprowadzone na parze walutowej $EURCZK$ (szereg czasowy przedstawiony na rysunku \ref{rysunek2}).
@@
 \FloatBarrier
-W przeprowadzonych badaniach przyjęto optymalną wartość parametru okresów do obliczenia wskaźnika ATR =14, następnie weryfikowano otrzymane wyniki na okresie testowym. 
+W przeprowadzonych badaniach przyjęto optymalną wartość parametru okresów do obliczenia wskaźnika OBV =14.
 \newpage
@@
 
-Zysk skumulowany          18.4184
-Calmar                     2.3641
-liczba otwartych pozycji  8777
+Zysk skumulowany          7.1888
+Calmar                    3.2053
+liczba otwartych pozycji    1139
 

### 2013-11-14 Article/book/BookSources/chapter1Indicators.tex
Book - first indicator - no error version

--- 2013-09-29 Matlabs/Indicators/AB/ROC_AB.tex
@@
-\documentclass[12pt,a4paper]{article}
-\usepackage{polski}
-\usepackage[utf8]{inputenc}
-\usepackage{amsmath}
-\usepackage{amssymb}
-\usepackage{amsfonts}
-\usepackage{graphicx}
-\usepackage{placeins}
-\usepackage{listings}
-\usepackage[svgnames]{xcolor}
- \lstset{literate={ą}{{\k{a}}}1 {ć}{{\'c}}1 {ę}{{\k{e}}}1 {ł}{{\l{}}}1 {ń}{{\'n}}1 {ó}{{\'o}}1 {ś}{{\'s}}1 {ż}{{\.z}}1 {ź}{{\'z}}1 {Ą}{{\k{A}}}1 {Ć}{{\'C}}1 {Ę}{{\k{E}}}1 {Ł}{{\L{}}}1 {Ń}{{\'N}}1 {Ó}{{\'O}}1 {Ś}{{\'S}}1 {Ż}{{\.Z}}1 {Ź}{{\'Z}}1 }
- \lstset{breaklines=true}
-\lstset{language=Matlab,
-  keywords={break,case,catch,continue,else,elseif,end,for,function,
-     global,if,otherwise,persistent,return,switch,try,while},
-  basicstyle=\ttfamily,
-  keywordstyle=\color{blue},
-  commentstyle=\color{DarkGreen},
-  stringstyle=\color{dkgreen},
-  numbers=left,
-  numberstyle=\tiny\color{gray},
-  stepnumber=1,
-  numbersep=10pt,
-  backgroundcolor=\color{white},
-  tabsize=4,
-  showspaces=false,
-  showstringspaces=false}
+%%%%%%%%%%%%%%%%%%%%% chapter.tex %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
 
-\begin {document}
-\begin{center}
-\begin{large}
-ROC --- opis wskaźnika Rate Of Change\\
-\end{large}
-Aneta Bera
-\end{center}
-%\baselineskip=22pt
+\chapter{Wskaźniki analizy technicznej}
+\label{Indicators} % Always give a unique label
+% use \chaptermark{}
+% to alter or adjust the chapter heading in the running head
 
+W poniższym rozdziale zaprezentowane zostaną wskaźniki analizy technicznej oraz ich zastosowanie do handlu na wybranych parach walutowych, indeksach giełdowych i kontraktach terminowych.
+
+\section{ROC --- wskaźnik Rate Of Change}
+\label{sec:1ROC}
 Rate Of Change, nazywany po polsku wskaźnikiem zmian, jest to wskaźnikiem który
@@
 \end{verbatim}
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\end {document}
+%

### 2013-12-12 Article/Article20130912/LatexArt/tewi-paper-template_minipages.tex
Full names should be shown for all abbreviations

@@
 The strategies are evaluated based on the time series of cumulative profit achieved in the test periods.
-The study was conducted on the most popular currency pair EURUSD sampled with interval of 1 hour.
+The study was conducted on the most popular currency pair EURUSD (Euro - Dollar) sampled with interval of 1 hour.
 \end{abstract}
@@
 It is appropriate to seek all opportunities for profit.
-A similar philosophy is applied by several Krutsinger correspondents \cite{Krutsinger}, who belong to most prominent traders in US, who advocate unfounded reversal of the direction of opening the positions in case of series of failures.\\
+A similar philosophy is applied by several Krutsinger correspondents \cite{Krutsinger}, who belong to most prominent traders in USA, who advocate unfounded reversal of the direction of opening the positions in case of series of failures.\\
 
@@
 \subsection{Definition of the band}
-The value of barriers forming a band is calculated using the maximum and minimum values of the last candle (OHLC).
+The value of barriers forming a band is calculated using the maximum and minimum values of the last candle (OHLC - Open, High, Low, Close prices).
 In the case of the upper band, it is the maximum of the maximal values of the n last candles, whereas in the case of the bottom band, it is the minimum of the minimal values of m last candles.
@@
 \end{equation} 
-where \textit{ProceO(i+k)} is the opening value for (i+k)-th candle;\\
+where \textit{PriceO(i+k)} is the opening value for (i+k)-th candle and \textit{SL} is Stop Loss (level of acceptable risk in one trade) in pips;\\
 Then the profit (in this case loss) will be calculated as:
@@
 \end{equation} 
+where \textit{TP} is Take Profit (maximum reward level in single trade) in pips;\\
 Then the profit will be calculated as:
@@
 Calmar ratio value was used to assess the adequacy of randomly selected parameter combinations for a given period of learning.
-In the second stage PSO \cite{Kennedy}  algorithm was used, searching for solutions within prescribed limits of the first stage.
+In the second stage PSO (Particle Swarm Optimization) \cite{Kennedy}  algorithm was used, searching for solutions within prescribed limits of the first stage.
 The objective function was the Calmar ratio maximizing as in the first step.
@@
 First (Figure \ref{Cum3DMiC} on page \pageref{Cum3DMiC}) shows the effect of test duration on the profit curve in time.
-To show how long in the test period optimal results are achieved we plotted 2D chart of final profit for each of the examined sizes.
+To show how long in the test period optimal results are achieved we plotted 2D (two-dimensional) chart of final profit for each of the examined sizes.
 Figure \ref{Cum3DMiCend} on page \pageref{Cum3DMiCend} shows that the number of candles for achieving a high and satisfactory results are attributable to 80-120.

### 2013-12-12 Article/Article20130912/LatexArt/tewi-paper-template_minipages.tex
It is mentioned in p.3 that “…However, the issue of emotions in the trade is not considered here, but only noticed. …” Why it is not considered? How it can be considered? More justifications should be provided on this issue.
editor 1: 6,7,11 - done editor 2: PSO done? editor 3: style in intro

@@
 This approach is consistent with the classic aim of machine learning shown by K.Murphy’ego \cite{Murphy}, especially to financial markets described by Satchwell \cite{Satchwell}.
-Authors also intend to follow the principle of reproducibility of studies by other researchers, as well as by themselves, in other data environments, to make sense of the use of computational intelligence in its reasonable reproducibility \cite{Polya, Donoho}, in extracting of the regularity from chaos \cite{Ball, Pedrycz}.\\
+The intention of this research was also to follow the principle of reproducibility of studies by other researchers, as well as by themselves, in other data environments, to make sense of the use of computational intelligence in its reasonable reproducibility \cite{Polya, Donoho}, in extracting of the regularity from chaos \cite{Ball, Pedrycz}.\\
 
-The authors build an investment strategy with a relatively high complexity (measured by the number of factors included in the model), derived from a strategies group called strategy of simple rules (simple rules).
+An investment strategy with a relatively high complexity (measured by the number of factors included in the model), derived from a strategies group called strategy of simple rules (simple rules) was built.
 In the literature those strategies are considered to be mainly strategies based on moving averages - their intersections and derivatives shown for example by Brock et al.
@@
 Of course, the world of algorithms as well as prediction methods using a completely different nature, such as regression \cite{Muriel}, multiple regression \cite{Wilinski, Fujimoto}, Fourier and wavelet transforms, and many others \cite{Raghuraj, KleskWilinski} is plenteous.
-The authors use these methods as a basis for comparison, however they focus on mentioned simple rules.\\
+This methods are used as a basis for comparison, however the main focus is on mentioned simple rules.\\
 
-Authors propose strategy, that differs by suggesting different behaviors than the ones proposed when using Bollinger's Band, which has its foundation in a band built in an unusual way.
+This paper proposes strategy, that differs by suggesting different behaviors than the ones proposed when using Bollinger's Band, which has its foundation in a band built in an unusual way.
 According to the strategy based on that band, generally it can be assumed that the trend is horizontal and it is recommended to open position to the center of the band, after its cross by the price from the inside.
-In proposed strategies, authors use another band that is based on maxima of the maxima and minima of the minima of last several candles.\\
+In proposed strategies, another band that is based on maxima of the maxima and minima of the minima of last several candles is used.\\
 
@@
 In one modification, hereinafter referred to as sub strategy, position opens into the center of the band, whereas in another one, position opens on the outside.
-By treating the two considered sub strategies as an entirety and as strategies that are mutually retrieving (although a more appropriate word would be complementary) authors assume, that in the selected trading section, opening positions in opposite directions, of course not at the same time, can be done intentionally and effectively.
+By treating the two considered sub strategies as an entirety and as strategies that are mutually retrieving (although a more appropriate word would be complementary) it is assumed, that in the selected trading section, opening positions in opposite directions, of course not at the same time, can be done intentionally and effectively.
 During the trading, nature of the market (trend, volatility) may change.
@@
 
-Therefore authors use two rather complex strategies (described below), achieving results that are in their assessment rewarding.
-They draw attention to the fact that the satisfaction problem belongs to the other sciences and depends on the trader's individual perception of the relationship between profit and risk, greed and fear \cite{Kahneman}.
-However, the issue of emotions in the trade is not considered here, but only noticed.\\
+Therefore in this paper two rather complex strategies (described below) are used, achieving results that are assesed as rewarding.
+Attention is drawn to the fact that the satisfaction problem belongs to the other sciences and depends on the trader's individual perception of the relationship between profit and risk, greed and fear \cite{Kahneman}.
+However, the issue of emotions in the trade is not considered here, but only noticed because there is the assumption that trading is done automatically.\\ % Myślę, że jest tutaj zaznaczone to o czym mowa w recenzji 1 punkt 5 - czy jest sens to rozwijać???
 
@@
 The main aim of the research was to obtain the most effective investment strategies by dynamic selection of test period duration.
-Later in this article concepts of learning period, a fixed-length 1000 candles but with diffeerent start in
+Later in this article concepts of learning period, a fixed-length 1000 candles but with different start in
 time were used.
@@
 
-The process of finding the optimum parameters for both of the described strategy is divided into two stages.
-In the first step of the process pseudo-random strategy is used to find the boundaries of the parameter space in which may be the optimal solution.
+Given that the search space is relatively broad and unknown (it is difficult to estimate how specific combination of parameters would influence strategy's effectiveness) it is necessary to define its boundaries and then to find a combination of parameters that would maximize strategy's efficiency.
+In the first step of the process, a pseudo-random strategy is used to find the boundaries of the parameter space in which may exist the optimal solution.
 Calmar ratio value was used to assess the adequacy of randomly selected parameter combinations for a given period of learning.
-In the second stage PSO (Particle Swarm Optimization) \cite{Kennedy}  algorithm was used, searching for solutions within prescribed limits of the first stage.
-The objective function was the Calmar ratio maximizing as in the first step.
-The above tactics was used for each stage of the learning period, then checked "sustainability" of designated sets of parameters for test periods of different lengths - the basic rate of 100 candles and the other in the range of 10-400.
+It would be possible to use an iterative method that would traverse the search space with certain step.
+However it would be extremely time consuming method given that the space is 11-dimensional.
+In the second stage PSO (Particle Swarm Optimization) \cite{Kennedy}  algorithm which already has been proved useful in finding optimal strategy parameters \cite{PSOtrading} was used, searching for solutions within prescribed limits of the first stage.
+The objective function was to maximizing the Calmar ratio, as it was in the first step.
+\\
+The above tactic was used for each stage of the learning period, then checked "sustainability" of designated sets of parameters for test periods of different lengths - the basic rate of 100 candles and the other in the range of 10-400.
 Figure ~\ref{research_methods} on page ~\pageref{research_methods} shows how the research was conducted.
@@
 Following a review of various lengths dependence validation periods shown in Figures \ref{Cum3DMiCend} and \ref{Cum3DMiDend} were obtained.
-It shows a fairly obvious that a good fit of the parameters of the test period will continue for some time after the end of the learning.
+It is fairly obvious that a good fit of the parameters of the test period will continue for some time after the end of the learning.
 This is due to the assumption that there are trends in the market in different direction.

### 2013-12-12 Article/Article20130912/LatexArt/tewi-paper-template_minipages.tex
work in progress

@@
 \section{Introduction}
-The aim of this work is to verify the hypothesis of the possibility of extracting patterns from time series, that would be classifiable as those that provide more accurate and better statistic prognosis.
-Another important objective is to confirm the assumption, that the time series of financial markets have a "memory" about the effectiveness of the learned pattern in a period after the learning one.
+The aim of this work is verification hypothesis of patterns extraction possibility from from time series, which could be classified as providing better statistic and more accurate prognosis.
+Another important objective is confirmation of assumption, that financial markets time series have a “memory” of pattern efficiency in a time period after the time which pattern was learn in.
 This approach is consistent with the classic aim of machine learning shown by K.Murphy’ego \cite{Murphy}, especially to financial markets described by Satchwell \cite{Satchwell}.
-The intention of this research was also to follow the principle of reproducibility of studies by other researchers, as well as by themselves, in other data environments, to make sense of the use of computational intelligence in its reasonable reproducibility \cite{Polya, Donoho}, in extracting of the regularity from chaos \cite{Ball, Pedrycz}.\\
+Research intention was also to follow reproducibility principle of other researchers studies, as well as by themselves, in other data environments, to make sense of the use of computational intelligence in its reasonable reproducibility \cite{Polya, Donoho}, in extracting of the regularity from chaos \cite{Ball, Pedrycz}.\\
 

### 2013-12-12 Article/Article20130912/LatexArt/tewi-paper-template_minipages.tex
Intorduction poprawione

@@
 
-An investment strategy with a relatively high complexity (measured by the number of factors included in the model), derived from a strategies group called strategy of simple rules (simple rules) was built.
+An investment strategy with a relatively high complexity (measured by the number of factors included in the model) was built, derived from a strategies group called strategy of simple rules (simple rules).
 In the literature those strategies are considered to be mainly strategies based on moving averages - their intersections and derivatives shown for example by Brock et al.
@@
 \cite{Cai} and many other authors \cite{Gencay, LeBaron, Tian}.
-Of course, the world of algorithms as well as prediction methods using a completely different nature, such as regression \cite{Muriel}, multiple regression \cite{Wilinski, Fujimoto}, Fourier and wavelet transforms, and many others \cite{Raghuraj, KleskWilinski} is plenteous.
+Of course, the world of algorithms as well as prediction methods is using a completely different nature, such as regression \cite{Muriel}, multiple regression \cite{Wilinski, Fujimoto}, Fourier and wavelet transforms, and many others \cite{Raghuraj, KleskWilinski} is plenteous.
 This methods are used as a basis for comparison, however the main focus is on mentioned simple rules.\\
 
-This paper proposes strategy, that differs by suggesting different behaviors than the ones proposed when using Bollinger's Band, which has its foundation in a band built in an unusual way.
+This paper proposes strategy, which differs by suggesting different behaviors than the ones proposed when using Bollinger's Band, which has its foundation in a band built in an unusual way.
 According to the strategy based on that band, generally it can be assumed that the trend is horizontal and it is recommended to open position to the center of the band, after its cross by the price from the inside.
@@
 
-In considered strategies authors move away from the principle of opening positions to the center of the band.
+Considered strategies move away from the principle of opening positions to the center of the band.
 In one modification, hereinafter referred to as sub strategy, position opens into the center of the band, whereas in another one, position opens on the outside.
@@
 
-Returning to the issue of the complexity of the strategy, there are often opinions that the growing complexity of the prediction model is not indicated, because in learning section it  leads to overfitting \cite{Murphy, Cai, Fujimoto}  resulting in a greater error in the test sections.
+Returning to the issue of complexity of strategy, there are often opinions that the growing complexity of the prediction model is not indicated, because in learning section it  leads to overfitting \cite{Murphy, Cai, Fujimoto}  resulting in a greater error in the test sections.
 The problem of selecting the proper ratio between learning and testing phase is still unsolved for the non-stationary time series \cite{Ball, Ivakhnenko}.

### 2013-12-12 Article/Article20130912/LatexArt/tewi-paper-template_minipages.tex
duplicate from

@@
 \section{Introduction}
-The aim of this work is verification hypothesis of patterns extraction possibility from from time series, which could be classified as providing better statistic and more accurate prognosis.
+The aim of this work is verification hypothesis of patterns extraction possibility from time series, which could be classified as providing better statistic and more accurate prognosis.
 Another important objective is confirmation of assumption, that financial markets time series have a “memory” of pattern efficiency in a time period after the time which pattern was learn in.

### 2013-12-13 Article/Article20130912/LatexArt/tewi-paper-template_minipages.tex
checked and corrected first 11 pages

@@
 \section{Introduction}
-The aim of this work is verification hypothesis of patterns extraction possibility from time series, which could be classified as providing better statistic and more accurate prognosis.
+The aim of this work is to verrify the hypothesis of patterns extraction possibility from time series, which could be classified as providing better statistic and more accurate prognosis.
 Another important objective is confirmation of assumption, that financial markets time series have a “memory” of pattern efficiency in a time period after the time which pattern was learn in.
@@
 
-Returning to the issue of complexity of strategy, there are often opinions that the growing complexity of the prediction model is not indicated, because in learning section it  leads to overfitting \cite{Murphy, Cai, Fujimoto}  resulting in a greater error in the test sections.
+Returning to the issue of complexity of strategy, there are often opinions that the growing complexity of the prediction model is not indicated, because in learning section it  leads to overfitting \cite{Murphy, Cai, Fujimoto}.
+This results in a greater error in the test sections.
 The problem of selecting the proper ratio between learning and testing phase is still unsolved for the non-stationary time series \cite{Ball, Ivakhnenko}.
@@
 \ref{timeSeries}).
-It is the time series, consisting of 4734  \mbox{1-hour } candles, of the most important and the most fluent currency pair EURUSD from 22.10.2012.
+This time series, consists of 4734  \mbox{1-hour } candles, of the most important and the most fluent currency pair EURUSD from 22.10.2012.
 \begin{figure}[h!]
@@
 \section{Characteristics of investment strategies}
-The objective of the two considered strategies is to make investment decisions about buying or selling - opening long or short position in the studied market - the currency pair EURUSD.
-Decision is based on intersection of the current price and one of two barriers of additional indicator, called the ribbon.
+The objective of the two strategies considered is to make investment decisions about buying or selling - opening long or short position in the market studied - the currency pair EURUSD.
+The decision is based on the intersection of the current price and one of two barriers of additional indicator, called the ribbon.
 The band is made of two values calculated at the opening of each candle on the basis of historical data of the market.
-During the candle values of the band do not change, therefore barriers are creating step functions.
-In case, when the current price exceeds any of the barrier values (goes out of the band), a decision to buy or sell is made - the type of decision depends on the variant of the considered strategy - decision for sub strategy TewiMiC is different than in case of TewiMiD.
+During the candle, values of the band do not change; therefore, barriers are creating step functions.
+In case when the current price exceeds any of the barrier values (goes out of the band), a decision to buy or sell is made - the type of decision depends on the variant of the considered strategy - decision for sub strategy TewiMiC is different than in case of TewiMiD.
 Names of the strategies are derived from the name of the project, in which the research was carried out.
@@
 \subsection{Definition of the band}
-The value of barriers forming a band is calculated using the maximum and minimum values of the last candle (OHLC - Open, High, Low, Close prices).
+The values of barriers forming a band are calculated using the maximum and minimum values of the last candle (OHLC - Open, High, Low, Close prices).
 In the case of the upper band, it is the maximum of the maximal values of the n last candles, whereas in the case of the bottom band, it is the minimum of the minimal values of m last candles.
@@
 Object - the event - is another candle.
-Rules are logical sentences like "if the price is greater than the upper barrier of the band", parameter is for example the upper barrier, which is a variable value.
+Rules are logical sentences like "if the price is greater than the upper barrier of the band" and the parameter is for example the upper barrier, which is a variable value.
 \\
@@
 
-For TewiMiD strategy, similar, with significant differences - short positions will be opened and it is advisable that current volume should be greater  than the average.
-As the result of conducted research, authors concluded that volume (number of price changes in observed time frame – here during one hour) was the most important and most sensitive factor of decision model.\\
+For TewiMiD strategy, analogously, with significant differences --- short positions will be opened and it is advisable that current volume should be greater  than the average.
+As the result of conducted research, authors concluded that volume (number of price changes in observed time frame --– here during one hour) was the most important and most sensitive factor of decision model.\\
 
@@
 \\
-
 The result of that is that we have two distinctly different opening conditions.
@@
 \subsection{Conditions of closing}
-In both sub strategies there are 7 cases of closing the open positions, which results in their complexity - both in terms of logic and calculation.
+In both sub strategies there are 7 cases of closing the open positions, which results in their complexity --- both in terms of logic and calculation.
 This complexity, however, exhausts all the possible surprises and does not  leave any opportunity for the unexpected market behavior.
@@
 During the test as a measure of the effectiveness of the investment was considered the maximum rate of net profit (with transaction costs).
-The authors believe this two criteria in evaluation the quality of simulation results as legitimate.
+The authors believe that these two criteria in evaluation the quality of simulation results are legitimate.
 In the first phase of the validation, the training period is indicated for moderate and prudent risk management.
@@
 Later in this article concepts of learning period, a fixed-length 1000 candles but with different start in
-time were used.
+time, were used.
 Immediately after period of learing there was a variable-length test period.

### 2013-12-13 Article/Article20130912/LatexArt/tewi-paper-template_minipages.tex
poprawki profesora

@@
 \begin{abstract}
-In this paper authors examine two transactional strategies based on the classifier which opens positions using some rules and closes them using different rules.
+This paper examined two transactional strategies based on the classifier which opens positions using some rules and closes them using different rules.
 A rule set contains time-varying parameters that when matched allow to make an investment decision.
@@
 The study was conducted on the most popular currency pair EURUSD (Euro - Dollar) sampled with interval of 1 hour.
+An important contribution to the theory of algotrading resulting from presented research is specification of the parameter space (quite large, consisting of 11 parameters) that achieves very good results using cross validation.
 \end{abstract}
@@
 
-An investment strategy with a relatively high complexity (measured by the number of factors included in the model) was built, derived from a strategies group called strategy of simple rules (simple rules).
+An investment strategy with a relatively high complexity (measured by the number of factors included in the model) was built, derived from a strategies group called strategy of simple rules.
 In the literature those strategies are considered to be mainly strategies based on moving averages - their intersections and derivatives shown for example by Brock et al.
@@
 \FloatBarrier
+A choice of parameters essential for defining the rules of opening and closing positions is crucial to the effectiveness of the strategy.
+Parametric space presented in this paper is a result of many trials prior to its final approval.
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
@@
 This implies the need for a hybrid solution, consisting for example of interprocess communication between the trading software and program developed in universal high-level language (eg Matlab, C\#).
-Algotarding future will very likely be increasingly active domain for experts in algorithmization and programming and less and less for economists and econometricians.\\
+Algotarding future will very likely be increasingly active domain for experts in algorithmization and programming and less and less for economists and econometricians.
+Presented results can be considered as particularly good and are reproducible by scrupulous reader.
+Alternative strategies can be compared with presented ones using the same criteria (i.e.
+Calmar ratio).
+For many years the authors have been improving following strategy and its implementation in the real market.\\
 

### 2013-12-13 Article/Article20130912/LatexArt/tewi-paper-template_minipages.tex
added: definition of Calmar ratio and part in conclusion

@@
 \usepackage[utf8]{inputenc}
-\usepackage[table]{xcolor}
+\usepackage[table,usenames,dvipsnames,svgnames]{xcolor}
 \usepackage{array}
@@
 In both strategies a fixed period of learning are assumed (in the presented solution - 1000 one hour candles), followed by a testing period.
-Data from learning period were used to find a class of patterns which allowed to achieve maximum for the selected criterion (in this study Calmar ratio were selected).
-The same patterns were then searched during the test period and the test results were computed for previously unused data space.
+Data from learning period were used to find a class of patterns which allowed to achieve maximum for the selected criterion, \textcolor{RedViolet}{in this study Calmar ratio (which is defined as a returned profit to maximum drawdown ratio) was selected.} The same patterns were then searched during the test period and the test results were computed for previously unused data space.
 Of course, these results do not have to already be positive and acceptable and could negatively surprise investors.
@@
 This implies the need for a hybrid solution, consisting for example of interprocess communication between the trading software and program developed in universal high-level language (eg Matlab, C\#).
-Algotarding future will very likely be increasingly active domain for experts in algorithmization and programming and less and less for economists and econometricians.
+Algotarding future will very likely be increasingly active domain for experts in algorithmization and programming and less and less for economists and econometricians.\\
+
+\textcolor{RedViolet}{Authors are aware of the fact that the parametric space is broad and choosing right ones is not a trivial task.
+It is not obvious that choosen and presented in this paper parameters are the best.
+There are no obvious sources that would suggest which parameters should be considered in investment strategies.
+To determine the parameters used in presented strategies an inductive method (??computional intelligence??) has been used --- after adding parameter the results were assessed and when they were acceptable the following parameter was added to the strategy.
+Even though selected parameters resulted in high efficiency, it does not mean that one should refrain from searching for better choice of parameters.}\\
+
 Presented results can be considered as particularly good and are reproducible by scrupulous reader.
@@
 Calmar ratio).
-For many years the authors have been improving following strategy and its implementation in the real market.\\
+For many years the authors have been improving following strategy and its implementation in the real market.
+\textcolor{RedViolet}{Current and future research aims to study the influence of the number of parameters --- expanding or limiting the parameter space --- and adding two additional sub strategies based on the same band as aforementioned.}\\
 

### 2013-12-13 Article/Article20130912/LatexArt/tewi-paper-template_minipages.tex
aded: about PSO

@@
 \begin{center}
-\includegraphics[width = 0.6\textwidth]{pictures/eurusd221012.png}
+\includegraphics[width = 0.55\textwidth]{pictures/eurusd221012.png}
 \end{center}
@@
 In both strategies a fixed period of learning are assumed (in the presented solution - 1000 one hour candles), followed by a testing period.
-Data from learning period were used to find a class of patterns which allowed to achieve maximum for the selected criterion, \textcolor{RedViolet}{in this study Calmar ratio (which is defined as a returned profit to maximum drawdown ratio) was selected.} The same patterns were then searched during the test period and the test results were computed for previously unused data space.
+Data from learning period were used to find a class of patterns which allowed to achieve maximum for the selected criterion, \textcolor{RedViolet}{in this study Calmar ratio (which is defined as a final profit to maximum drawdown ratio) was selected.} The same patterns were then searched during the test period and the test results were computed for previously unused data space.
 Of course, these results do not have to already be positive and acceptable and could negatively surprise investors.
@@
 However it would be extremely time consuming method given that the space is 11-dimensional.
-In the second stage PSO (Particle Swarm Optimization) \cite{Kennedy}  algorithm which already has been proved useful in finding optimal strategy parameters \cite{PSOtrading} was used, searching for solutions within prescribed limits of the first stage.
+In the second stage PSO (Particle Swarm Optimization) \cite{Kennedy}  algorithm, which already has been proved useful in finding optimal strategy parameters \cite{PSOtrading} and allows to find a satisfying combination of parameters values in relatively short time even in broad search spaces, was used.
+Search space for PSO algorithm has been define in previous step.
 The objective function was to maximizing the Calmar ratio, as it was in the first step.
@@
 \begin{center}
-\includegraphics[width=0.4\textwidth]{pictures/metodyka_badan.png}
+\includegraphics[width=0.6\textwidth]{pictures/metodyka_badan.png}
 \caption{Methods of testing carried out to test the variable size window}
@@
 \begin{figure}[h!]
-\begin{minipage}{.49\linewidth}
+\begin{minipage}{.45\linewidth}
 \begin{center}
@@
 \end{minipage}
-\begin{minipage}{.49\linewidth}
+\begin{minipage}{.45\linewidth}
 \begin{center}
@@
 \begin{figure}[h!]
-\begin{minipage}{.49\linewidth}
+\begin{minipage}{.45\linewidth}
 \begin{center}
-\includegraphics[width=0.82\textwidth]{pictures/cumulativeReturnsC.png}
+\includegraphics[width=0.80\textwidth]{pictures/cumulativeReturnsC.png}
 \subcaption{Results in 3D}
@@
 \end{minipage}
-\begin{minipage}{.49\linewidth}
+\begin{minipage}{.45\linewidth}
 \begin{center}
-\includegraphics[width=0.82\textwidth]{pictures/mic_end.png}
+\includegraphics[width=0.80\textwidth]{pictures/mic_end.png}
 \subcaption{Final results}
@@
 \centering
-\begin{minipage}{.49\linewidth}
+\begin{minipage}{.45\linewidth}
 \begin{center}
-\includegraphics[width=0.82\textwidth]{pictures/cumulativeReturnsPerCandleC.png}
+\includegraphics[width=0.80\textwidth]{pictures/cumulativeReturnsPerCandleC.png}
 \subcaption{Results in 3D}
@@
 \end{minipage}
-\begin{minipage}{.49\linewidth}
+\begin{minipage}{.45\linewidth}
 \begin{center}
-\includegraphics[width=0.82\textwidth]{pictures/mic_percandle_end.png}
+\includegraphics[width=0.80\textwidth]{pictures/mic_percandle_end.png}
 \subcaption{Final results}
@@
 There are no obvious sources that would suggest which parameters should be considered in investment strategies.
-To determine the parameters used in presented strategies an inductive method (??computional intelligence??) has been used --- after adding parameter the results were assessed and when they were acceptable the following parameter was added to the strategy.
+To determine the parameters utilized in presented strategies an iterative computation has been used --- after adding parameter the results were assessed and when they were acceptable the following parameter was added to the strategy.
 Even though selected parameters resulted in high efficiency, it does not mean that one should refrain from searching for better choice of parameters.}\\

### 2013-12-14 Article/Article20130912/LatexArt/tewi-paper-template_minipages.tex
bibs

@@
 \FloatBarrier
-
 \begin{table}[h!]
@@
 The authors have found that the use of optimization methods derived from the area of artificial intelligence, including the PSO \cite{Kennedy}, given good and quickly reached the optimum values of the rules of the classifier, and good results in the initial stages of the test period.
+Also PSO method was proven its effectiveness in similiar optimization problems\cite{Chau2007642}\cite{Zhang}.
 For longer test periods, it can indeed get good results, however, the effectiveness of the strategy per hour decreases significantly.
@@
 To determine the parameters utilized in presented strategies an iterative computation has been used --- after adding parameter the results were assessed and when they were acceptable the following parameter was added to the strategy.
-Even though selected parameters resulted in high efficiency, it does not mean that one should refrain from searching for better choice of parameters.}\\
-
-Presented results can be considered as particularly good and are reproducible by scrupulous reader.
+Even though selected parameters resulted in high efficiency, it does not mean that one should refrain from searching for better choice of parameters.} Presented results can be considered as particularly good and are reproducible by scrupulous reader.
 Alternative strategies can be compared with presented ones using the same criteria (i.e.

### 2013-12-14 Article/Article20130912/LatexArt/tewi-paper-template_minipages.tex
no color version

--- 2013-12-13 Article/Article20130912/LatexArt/tewi-paper-template_minipages.tex
@@
 Attention is drawn to the fact that the satisfaction problem belongs to the other sciences and depends on the trader's individual perception of the relationship between profit and risk, greed and fear \cite{Kahneman}.
-However, the issue of emotions in the trade is not considered here, but only noticed because there is the assumption that trading is done automatically.\\ % Myślę, że jest tutaj zaznaczone to o czym mowa w recenzji 1 punkt 5 - czy jest sens to rozwijać???
+However, the issue of emotions in the trade is not considered here, but only noticed because there is the assumption that trading is done automatically.\\
 
@@
 In both strategies a fixed period of learning are assumed (in the presented solution - 1000 one hour candles), followed by a testing period.
-Data from learning period were used to find a class of patterns which allowed to achieve maximum for the selected criterion, \textcolor{RedViolet}{in this study Calmar ratio (which is defined as a final profit to maximum drawdown ratio) was selected.} The same patterns were then searched during the test period and the test results were computed for previously unused data space.
+Data from learning period were used to find a class of patterns which allowed to achieve maximum for the selected criterion, in this study Calmar ratio (which is defined as a final profit to maximum drawdown ratio) was selected.
+The same patterns were then searched during the test period and the test results were computed for previously unused data space.
 Of course, these results do not have to already be positive and acceptable and could negatively surprise investors.
@@
 \begin{figure}[h!]
+\centering
 \begin{minipage}{.45\linewidth}
@@
 \begin{figure}[h!]
+\centering
 \begin{minipage}{.459\linewidth}
@@
 
-\textcolor{RedViolet}{Authors are aware of the fact that the parametric space is broad and choosing right ones is not a trivial task.
+Authors are aware of the fact that the parametric space is broad and choosing right ones is not a trivial task.
 It is not obvious that choosen and presented in this paper parameters are the best.
@@
 To determine the parameters utilized in presented strategies an iterative computation has been used --- after adding parameter the results were assessed and when they were acceptable the following parameter was added to the strategy.
-Even though selected parameters resulted in high efficiency, it does not mean that one should refrain from searching for better choice of parameters.}\\
-
+Even though selected parameters resulted in high efficiency, it does not mean that one should refrain from searching for better choice of parameters.
 Presented results can be considered as particularly good and are reproducible by scrupulous reader.
@@
 For many years the authors have been improving following strategy and its implementation in the real market.
-\textcolor{RedViolet}{Current and future research aims to study the influence of the number of parameters --- expanding or limiting the parameter space --- and adding two additional sub strategies based on the same band as aforementioned.}\\
+Current and future research aims to study the influence of the number of parameters --- expanding or limiting the parameter space --- and adding two additional sub strategies based on the same band as aforementioned.\\
 

### 2013-12-14 Article/Article20130912/LatexArt/tewi-paper-template_minipages.tex
update: bibliography + png -> eps
bibliography layout

@@
 \usepackage{graphicx}
+\usepackage{epstopdf}
 \usepackage{amsthm}
@@
 \usepackage{txfonts}
-\usepackage{epstopdf}
 \usepackage{placeins}
@@
 \begin{center}
-\includegraphics[width = 0.55\textwidth]{pictures/eurusd221012.png}
+\includegraphics[width = 0.55\textwidth]{pictures/eurusd221012.eps}
 \end{center}
@@
 TewiMiD implies existence of a downward trend, for which when crossing (down) the lower limit of the band, a short position (assuming the price drop) is opened.
-This is known it literature and in trading as Sell Stop model.
+This is known in literature and in trading as Sell Stop model.
 \\
@@
 \begin{center}
-\includegraphics[width=0.9\textwidth]{pictures/mic_100.png}
+\includegraphics[width=0.9\textwidth]{pictures/mic_100.eps}
 \subcaption{Sub strategy TewiMiC}
@@
 \begin{center}
-\includegraphics[width=0.9\textwidth]{pictures/mid_100.png}
+\includegraphics[width=0.9\textwidth]{pictures/mid_100.eps}
 \subcaption{Sub strategy TewiMiD}
@@
 \begin{center}
-\includegraphics[width=0.80\textwidth]{pictures/cumulativeReturnsC.png}
+\includegraphics[width=0.80\textwidth]{pictures/cumulativeReturnsC.eps}
 \subcaption{Results in 3D}
@@
 \begin{center}
-\includegraphics[width=0.80\textwidth]{pictures/mic_end.png}
+\includegraphics[width=0.80\textwidth]{pictures/mic_end.eps}
 \subcaption{Final results}
@@
 \begin{center}
-\includegraphics[width=0.80\textwidth]{pictures/cumulativeReturnsPerCandleC.png}
+\includegraphics[width=0.80\textwidth]{pictures/cumulativeReturnsPerCandleC.eps}
 \subcaption{Results in 3D}
@@
 \begin{center}
-\includegraphics[width=0.80\textwidth]{pictures/mic_percandle_end.png}
+\includegraphics[width=0.80\textwidth]{pictures/mic_percandle_end.eps}
 \subcaption{Final results}
@@
 \begin{center}
-\includegraphics[width=0.82\textwidth]{pictures/cumulativeReturnsD.png}
+\includegraphics[width=0.82\textwidth]{pictures/cumulativeReturnsD.eps}
 \subcaption{Results in 3D}
@@
 \begin{center}
-\includegraphics[width=0.82\textwidth]{pictures/mid_end.png}
+\includegraphics[width=0.82\textwidth]{pictures/mid_end.eps}
 \subcaption{Final results}
@@
 \begin{center}
-\includegraphics[width=0.82\textwidth]{pictures/cumulativeReturnsPerCandleD.png}
+\includegraphics[width=0.82\textwidth]{pictures/cumulativeReturnsPerCandleD.eps}
 \subcaption{Results in 3D}
@@
 \begin{center}
-\includegraphics[width=0.82\textwidth]{pictures/mid_percandle_end.png}
+\includegraphics[width=0.82\textwidth]{pictures/mid_percandle_end.eps}
 \subcaption{Final results}

### 2013-12-14 Article/Article20130912/LatexArt/tewi-paper-template_minipages.tex
corrected errors

@@
 \begin{abstract}
-This paper examined two transactional strategies based on the classifier which opens positions using some rules and closes them using different rules.
+This paper examines two transactional strategies based on the classifier which opens positions using some rules and closes them using different rules.
 A rule set contains time-varying parameters that when matched allow to make an investment decision.
@@
 \section{Introduction}
-The aim of this work is to verrify the hypothesis of patterns extraction possibility from time series, which could be classified as providing better statistic and more accurate prognosis.
+The aim of this work is to verify the hypothesis of patterns extraction possibility from time series, which could be classified as providing better statistic and more accurate prognosis.
 Another important objective is confirmation of assumption, that financial markets time series have a “memory” of pattern efficiency in a time period after the time which pattern was learn in.
-This approach is consistent with the classic aim of machine learning shown by K.Murphy’ego \cite{Murphy}, especially to financial markets described by Satchwell \cite{Satchwell}.
+This approach is consistent with the classic aim of machine learning shown by K.Murphy \cite{Murphy}, especially to financial markets described by Satchwell \cite{Satchwell}.
 Research intention was also to follow reproducibility principle of other researchers studies, as well as by themselves, in other data environments, to make sense of the use of computational intelligence in its reasonable reproducibility \cite{Polya, Donoho}, in extracting of the regularity from chaos \cite{Ball, Pedrycz}.\\
@@
 \begin{center}
-\includegraphics[width = 0.55\textwidth]{pictures/eurusd221012.eps}
+\includegraphics[width = 0.5\textwidth]{pictures/eurusd221012.eps}
 \end{center}
@@
 In the second stage PSO (Particle Swarm Optimization) \cite{Kennedy}  algorithm, which already has been proved useful in finding optimal strategy parameters \cite{PSOtrading} and allows to find a satisfying combination of parameters values in relatively short time even in broad search spaces, was used.
-Search space for PSO algorithm has been define in previous step.
+Search space for PSO algorithm has been defined in previous step.
 The objective function was to maximizing the Calmar ratio, as it was in the first step.
@@
 Additionally, the authors set out to test a new standard of quality prediction.
-Now, extending the period of testing can produce better results, but more slowly or with local drawndown in comparision to first period, when the classifier "remembers" the nature of the market.
+Now, extending the period of testing can produce better results, but more slowly or with local drawdown in comparision to first period, when the classifier "remembers" the nature of the market.
 This new criteria is profit attributable to one candle of the testing period.\\
@@
 
-It may be noted that the two policies, for the test period of 100, allow for systematic profit in examined period with only small drawndowns.
+It may be noted that the two policies, for the test period of 100, allow for systematic profit in examined period with only small drawdowns.
 Profit for the strategy TewiMiC 0.355, for TewiMiD profit is several times smaller and amounts to 0.094.
-But second strategy has smaller drawndowns.
+But second strategy has smaller drawdowns.
 In addition, it is confirmed with the higher Calmar ratio - 12.79, where the result for first of these strategies is 10.22.

### 2013-12-17 Article/book/BookSources/chapter1Indicators.tex
book planned layout
book - all inicators

@@
 
-\chapter{Wskaźniki analizy technicznej}
+\chapter{Technical analysis indicators}
 \label{Indicators} % Always give a unique label
@@
 
-\section{ROC --- wskaźnik Rate Of Change}
-\label{sec:1ROC}
-Rate Of Change, nazywany po polsku wskaźnikiem zmian, jest to wskaźnikiem który
-mierzy procentową zmianę pomiędzy najnowszą ceną
-zamknięcia a ceną $k$ okresów wcześniej. Sposób wyliczenia wartości wskaźnika ROC dla danego punktu w czasie przedstawiają wzory \ref{wzor_1} oraz \ref{wzor_2}.
-\begin{equation}
-ROC(\text{dziś}) = \frac{\text{Cena zamknięcia dziś} - \text{Cena zamknięcia } k \text{ okresów temu}}{\text{Cena zamknięcia } k \text{ okresów temu}}\\
-\label{wzor_1}
-\end{equation}
-\begin{equation}
-ROC(i) = \frac{C(i,4) - C(i-k,4)}{C(i-k,4)}
-\label{wzor_2}
-\end{equation}
-
-\noindent Do podstawowych własności krzywej ROC należą:
-\begin{itemize}
-\item obrazuje ona jak zmieniała się cena obserwowanego rynku w danym okresie,
-\item jeśli wartość oscylatora znajduje się poniżej zera, to obecna cena jest wyższa od tej sprzed $k$-godzin temu, analogicznie gdy oscylator znajduje się powyżej zera, oznacza to, że obecna cena jest niższa od tej sprzed $k$-godzin temu,
-\item wzrastająca linia wskaźnika pokazuje, że różnice między
-obecnym poziomem ceny a tym $k$ -czas temu się
-zwiększają, malejąca mówi natomiast, że różnica ta się zmniejsza,
-\item jeśli ceny akcji będą rosły to można oczekiwać, że linia
-oscylatora będzie zachowywać się analogicznie, jeśli ceny będą natomiast malały to linia oscylatora powinna maleć.
-\end{itemize}
-Najważniejszą własnością opisywanego wskaźnika, stosowaną przy implementacjach strategii, jest fakt wskazywania momentów w których powinny zostać zawarte transakcje.
-Gdy wartość wskaźnika przetnie od dołu poziom zero to zakłada się, że jest to dobry moment kupna, jeśli przetnie poziom zera od góry to sprzedaży.
-Zostało to przedstawione na rysunku \ref{kupsprz}.
-\\
-\begin{figure}[h!]
-\centering
-\includegraphics[width = \textwidth]{BuySell.png}
-\caption{Fragment przykładowej krzywej ROC wraz z sygnałami kupna --- zielone strzałki oraz sygnałami sprzedaży --- czerwone strzałki}
-\label{kupsprz}
-\end{figure}
-\FloatBarrier
-
-\noindent Poniższy listing przedstawia zaimplementowaną strategię w środowisku MATLAB.
-\begin{scriptsize}
-\begin{lstlisting}
-pocz = k+2;	
-kon = size(C,1)-1;
-iL = 0; % przekroczenie 0 w górę - kupno (L)
-iS = 0; % przekroczenie 0 w dół - sprzedaż (S)
-sumR = zeros(1,size(C,1));
-R = zeros(1,size(C,1));
-ROC_vec = zeros(1,kon-k+1);
-ROC_vec(pocz-1) = ((C(pocz-1,4) - C(pocz-1-k,4))/C(pocz-1-k,4))*100;
-
-recordReturn = 0;  % rekord zysku
-recordDrawdown = 0;  % rekord obsuniecia
-LastPos = 0;    % zmienna do przechowywania wartości na otwarciu ostatniej pozycji
-
-for i=pocz:kon
-    ROC_vec(i) = ((C(i,4) - C(i-k,4))/C(i-k,4))*100;  % obliczenie punktu krzywej ROC
-    if ROC_vec(i)*ROC_vec(i-1)<=0   % przecięcie krzywej ROC z zerem
-        if ROC_vec(i-1)<ROC_vec(i)  % warunek kupna
-            if iL+iS>0
-                R(i) = -C(i+1,4)+LastPos-spread;   % zamknięcie S
-            end
-            LastPos = C(i+1,1);   % otworzenie L
-            iL = iL + 1;
-        elseif ROC_vec(i-1)>ROC_vec(i)  % warunek sprzedaży
-            if iL+iS>0
-                R(i) = C(i+1,4)-LastPos-spread;  % zamknięcie L
-            end
-            LastPos = C(i+1,1);   % otworzenie S
-            iS = iS + 1;
-        end
-    end
-    sumR(i) = sum(R(pocz:i));
-
-    if sumR(i)>recordReturn
-        recordReturn=sumR(i);
-    end
-
-    if sumR(i)-recordReturn<recordDrawdown
-        recordDrawdown=sumR(i)-recordReturn;  
-    end
-
-end
-
-Calmar=-sumR(kon)/recordDrawdown;
-profit = sumR(kon);
-
-end
-\end{lstlisting}
-\end{scriptsize}
-
-Na podstawie zebranych informacji dotyczących wskaźnika $ROC$ utworzono prostą strategię inwestycyjną bazującą na regule: jeśli linia $ROC$ przetnie się z poziomem zera od dołu, to otwierana jest pozycja długa ($L$), a zamykana pozycja krótka ($S$), która została wcześniej otwarta.
-Gdy natomiast nastąpi przecięcie linii $ROC$ z poziomem zera od góry to otwarta zostanie pozycja krótka, a zamknięta długa.
-Badania zostały przeprowadzone na parze walutowej $EURJPY$ (szereg czasowy przedstawiony na rysunku \ref{rysunek2}).
-\\
-\begin{figure}[h!]
-\centering
-\includegraphics[width = \textwidth]{podzialDanych.png}
-\caption{Badany szereg czasowy z podziałem na część uczącą i testową}
-\label{rysunek2}
-\end{figure}
-\FloatBarrier
-Cały zbiór danych (świec) podzielony został na dwie części: uczącą ($60\%$ całości) oraz testową ($40\%$ całości).
-W przeprowadzonych badaniach poszukiwano optymalnej wartości parametru $k$ na okresie uczącym, następnie weryfikowano otrzymane wyniki na okresie testowym.
-Wybór optymalnej wartości parametru $k$ determinowano na dwa sposoby:
-\begin{itemize}
-\item otrzymanego zysku skumulowanego,
-\item wskaźnika Calamara.
-\end{itemize}
-
-\noindent \textbf{I Wyniki badań przy maksymalizacji po zysku.}\\
-\begin{figure}[h!]
-\centering
-\includegraphics[width = 0.6\textwidth]{ROC_EURJPY_LS_SearchBestK_zysk.png}
-\caption{Zysk skumulowany EURJPY na okresie testowym przy maksymalizacji według zysku}
-\end{figure}
-\FloatBarrier
-\begin{verbatim}
-OKRES UCZĄCY
-Długość cyklu: 	89
-Zysk skumulowany: 	16.81
-Calmar: 	2.66
-Liczba otwartych pozycji długich: 	100
-Liczba otwartych pozycji krótkich: 	100
-
-OKRES WALIDUJĄCY
-Długość cyklu: 	89
-Zysk skumulowany: 	11.87
-Calmar: 	1.00
-Liczba otwartych pozycji długich: 	61
-Liczba otwartych pozycji krótkich: 	61
-\end{verbatim}
-\newpage
-\textbf{II Wyniki badań przy maksymalizacji po wskaźniku Calmara.}\\
-\begin{figure}[h!]
-\centering
-\includegraphics[width = 0.6\textwidth]{ROC_EURJPY_LS_SearchBestKCalmar_zysk.png}
-\caption{Zysk skumulowany EURJPY na okresie testowym przy maksymalizacji według Calmara}
-\end{figure}
-\FloatBarrier
-\begin{verbatim}
-OKRES UCZĄCY
-Długość cyklu: 	230
-Zysk skumulowany: 	12.82
-Calmar: 	3.83
-Liczba otwartych pozycji długich: 	52
-Liczba otwartych pozycji krótkich: 	51
-
-OKRES TESTUJĄCY
-Długość cyklu: 	230
-Zysk skumulowany: 	20.64
-Calmar: 	5.08
-Liczba otwartych pozycji długich: 	28
-Liczba otwartych pozycji krótkich: 	29
-\end{verbatim}
-%
+\input{chapter1IndicatorsROC}
+\input{chapter1IndicatorsATR}
+\input{chapter1IndicatorsOBV}
+\input{chapter1IndicatorsSTF}
+\input{chapter1IndicatorsPPV}
+\input{chapter1IndicatorsMACD}
+\input{chapter1IndicatorsSTS}
+\input{chapter1IndicatorsMI}

### 2013-12-17 Article/book/BookSources/chapter1IndicatorsATR.tex
book - all inicators

--- 2013-11-12 Matlabs/Indicators/LB/ATR/ROC_AB.tex
@@
-\documentclass[12pt,a4paper]{article}
-\usepackage{polski}
-\usepackage[utf8]{inputenc}
-\usepackage{amsmath}
-\usepackage{amssymb}
-\usepackage{amsfonts}
-\usepackage{graphicx}
-\usepackage{placeins}
-\usepackage{listings}
-\usepackage[svgnames]{xcolor}
- \lstset{literate={ą}{{\k{a}}}1 {ć}{{\'c}}1 {ę}{{\k{e}}}1 {ł}{{\l{}}}1 {ń}{{\'n}}1 {ó}{{\'o}}1 {ś}{{\'s}}1 {ż}{{\.z}}1 {ź}{{\'z}}1 {Ą}{{\k{A}}}1 {Ć}{{\'C}}1 {Ę}{{\k{E}}}1 {Ł}{{\L{}}}1 {Ń}{{\'N}}1 {Ó}{{\'O}}1 {Ś}{{\'S}}1 {Ż}{{\.Z}}1 {Ź}{{\'Z}}1 }
- \lstset{breaklines=true}
-\lstset{language=Matlab,
-  keywords={break,case,catch,continue,else,elseif,end,for,function,
-     global,if,otherwise,persistent,return,switch,try,while},
-  basicstyle=\ttfamily,
-  keywordstyle=\color{blue},
-  commentstyle=\color{DarkGreen},
-  stringstyle=\color{dkgreen},
-  numbers=left,
-  numberstyle=\tiny\color{gray},
-  stepnumber=1,
-  numbersep=10pt,
-  backgroundcolor=\color{white},
-  tabsize=4,
-  showspaces=false,
-  showstringspaces=false}
-
-\begin {document}
-\begin{center}
-\begin{large}
-ATR --Average True Rang-  opis wskaźnika  \\
-\end{large}
-Łukasz Brzosko
-\end{center}
-%\baselineskip=22pt
+\section{ATR --- Average True Range}
+\label{sec:1ATR}
 
@@
 \end{verbatim}
-
-\end {document}
+%

### 2013-12-17 Article/book/BookSources/chapter1IndicatorsMI.tex
book - all inicators

--- 2013-10-03 Matlabs/Indicators/MZ/MZ_TEX/Indicators_MZ.tex
@@
-\documentclass[12pt,a4paper]{article}
-\usepackage[MeX]{polski}
-\usepackage[utf8]{inputenc}
-\usepackage{amsmath}
-\usepackage{amssymb}
-\usepackage{amsfonts}
-\usepackage{graphicx}
-\usepackage{placeins}
-\usepackage{listings}
-\usepackage[svgnames]{xcolor}
- \lstset{literate={ą}{{\k{a}}}1 {ć}{{\'c}}1 {ę}{{\k{e}}}1 {ł}{{\l{}}}1 {ń}{{\'n}}1 {ó}{{\'o}}1 {ś}{{\'s}}1 {ż}{{\.z}}1 {ź}{{\'z}}1 {Ą}{{\k{A}}}1 {Ć}{{\'C}}1 {Ę}{{\k{E}}}1 {Ł}{{\L{}}}1 {Ń}{{\'N}}1 {Ó}{{\'O}}1 {Ś}{{\'S}}1 {Ż}{{\.Z}}1 {Ź}{{\'Z}}1 }
- \lstset{breaklines=true}
-\lstset{language=Matlab,
-  keywords={break,case,catch,continue,else,elseif,end,for,function,
-     global,if,otherwise,persistent,return,switch,try,while},
-  basicstyle=\ttfamily,
-  keywordstyle=\color{blue},
-  commentstyle=\color{DarkGreen},
-  stringstyle=\color{dkgreen},
-  numbers=left,
-  numberstyle=\tiny\color{gray},
-  stepnumber=1,
-  numbersep=10pt,
-  backgroundcolor=\color{white},
-  tabsize=4,
-  showspaces=false,
-  showstringspaces=false}
-
-\begin {document}
-\begin{center}
-\begin{large}
-Stochastic Slow - oscylator stochastyczny wolny : opis wskaźnika\\
-\end{large}
-Michał Zabłocki
-\end{center}
-%\baselineskip=22pt
-
-Stochastic Slow jest wolniejszą wersja podstawowego oscylatora stochastycznego.
-Składa się z dwóch linii oscylacyjnych: głównej linii oscylatora tzw.
-\%K oraz pomocniczej wygładzonej postaci tej linii tzw.
-\%D.
-Obie linie osiągają wartości z przedziału 0 - 100.
-Sposób wyliczenia kolejnych wartości obu linii dla danego punktu w czasie przedstawiają wzory \ref{wzor_1} oraz \ref{wzor_2}.
-\begin{equation}
-\%K = \left[\begin{array}{c} \frac{ \sum_{j=0}^{2} (C_j - min(L_j, n))}{ \sum_{j=0}^{2} (max(H_j, n) - min(L_j, n))}\end{array}\right]\\
-\label{wzor_1}
-\end{equation}
-\begin{equation}
-\%D = SMA(\%K, 3)
-\label{wzor_2}
-\end{equation}
-
-\noindent Dodatkowo mogą być poszukiwane dywergencje względem wykresu cenowego.
-Możliwe jest też poszukiwanie tzw.
-odwróconych dywergencji.
-W tej wersji wskaźnik może być używany jako miernik wykupienia / wyprzedania rynku.
-Wadą wskaźnika jest to, że w mocnych ruchach trendowych skrajne stany rynku mogą być sygnalizowane przedwcześnie.
-Przy interpretacji wskaźnika najważniejszy jednak jest fakt, że wskazuje on momenty w których mogą być zawierane transakcje.
-Podstawowa zasada zakłada przyjęcie jako sygnału kupna sytuację gdy występują przecięcia linii \%D przez linię \%K od dołu.
-Natomiast, gdy linia \%D jest przecinana przez linię \%K od góry, to przyjmuje się taką sytuację za sygnał sprzedaży.
-Zostało to przedstawione na rysunku \ref{zasada}.
-\\
-\begin{figure}[h!]
-\centering
-\includegraphics[width = \textwidth]{ss.png}
-\caption{Fragment przebiegu kursu akcji (górny wykres) oraz odpowiadające jemu linie \%K i \%D wraz z sygnałami kupna --- błękitne strzałki oraz sygnałami sprzedaży --- pomarańczowe strzałki (dolny wykres)}
-\label{zasada}
-\end{figure}
-\FloatBarrier
-
-\noindent Poniższy listing przedstawia zaimplementowaną w środowisku MATLAB strategię wykorzystującą opisywany wskaźnik.
-\begin{scriptsize}
-\begin{lstlisting}
-maxes=zeros(candlesCount,1);
-mins=zeros(candlesCount,1);
-K=zeros(candlesCount,1);
-D=zeros(candlesCount,1);
-kon=candlesCount-1;
-for i=4:kon
-    maxes(i) = max(verificationC(i-min(i-1,paramMALength):i-1,2));
-    mins(i) = min(verificationC(i-min(i-1,paramMALength):i-1,3));
-    K(i) = 100 * (sum(verificationC(i-min(i-1,3):i-1,4)-mins(i-min(i-1,2):i)) / sum(maxes(i-min(i-1,2):i)-mins(i-min(i-1,2):i)));
-    D(i) = sum(K(i-min(i-1,2):i)) / min(i-1,3);
-end
-
-sumR=zeros(1,candlesCount);
-R=zeros(1,candlesCount);
-pocz=max(paramMALength, 10)+3;
-iL=0; %liczba otwieranych pozycji kupna
-iS=0; %liczba otwieranych pozycji sprzedarzy
-lastCandle = kon-paramMALength;
-recordReturn=0;  %rekord zysku
-recordDrawdown=0;  %rekord obsuniecia
-LastPos = 0; % zmienna do prz echowywa nia warto ś ci na otwarciu ostatniej pozycji
-for i=pocz:lastCandle
-
-    if K(i-1) < D(i-1) && K(i) >= D(i) % warunek kupna
-        R(i)= - C(i+1,4)+LastPos-spread; % zamknięcie S
-        LastPos = C(i+1,1); % otwarcie L
-        iL=iL+1;
-    elseif K(i-1) > D(i-1) && K(i) <= D(i) % warunek sprzedaż y
-        R(i)=C(i+1,4)-LastPos-spread; % zamknięcie L
-        LastPos = C(i+1,1); % otwarcie S
-        iS=iS+1;
-    end
-    sumR(i)= sum(R(pocz:i));  %krzywa narastania kapitału
-
-    if sumR(i)>recordReturn
-        recordReturn=sumR(i);
-    end
-
-    if sumR(i)-recordReturn<recordDrawdown
-        recordDrawdown=sumR(i)-recordReturn;  %obsuniecie maksymalne
-    end
-end
-
-%wyniki końcowe
-sumReturn=sumR(lastCandle);
-Calmar=-sumReturn/recordDrawdown;  %wskaznik Calmara
-\end{lstlisting}
-\end{scriptsize}
-
-Na podstawie zebranych informacji dotyczących wskaźnika $Stochastic Slow$ utworzono prostą strategię inwestycyjną bazującą na regule: jeśli linia $\%D$ jest przecinana przez  linię $\%K$ od dołu, to otwierana jest pozycja długa ($L$), a zamykana pozycja krótka ($S$), która została wcześniej otwarta.
-Natomiast gdy linia \%D jest przecinana przez linię \%K od góry, to otwarta zostanie pozycja krótka, a zamknięta długa.
-Badania zostały przeprowadzone na parze walutowej $CADCHF$ (szereg czasowy przedstawiony na rysunku \ref{rys2}).
-\\
-\begin{figure}[h!]
-\centering
-\includegraphics[width = \textwidth]{szereg.png}
-\caption{Badany szereg czasowy z podziałem na część uczącą i testową}
-\label{rys2}
-\end{figure}
-\FloatBarrier
-Cały zbiór danych (świec) podzielony został na dwie części: uczącą ($60\%$ całości) oraz testową ($40\%$ całości).
-W przeprowadzonych badaniach poszukiwano optymalnej wartości parametru $n$ na okresie uczącym, następnie weryfikowano otrzymane wyniki na okresie testowym.
-Wybór optymalnej wartości parametru $n$ determinowano na dwa sposoby:
-\begin{itemize}
-\item otrzymanego zysku skumulowanego,
-\item wskaźnika Calamara.
-\end{itemize}
-
-\noindent \textbf{I Wyniki badań przy maksymalizacji po zysku.}\\
-\begin{figure}[h!]
-\centering
-\includegraphics[width = 0.6\textwidth]{SS_CADCHF_S4LS_zysk.png}
-\caption{Zysk skumulowany CADCHF na okresie testowym przy maksymalizacji według zysku}
-\end{figure}
-\FloatBarrier
-\begin{verbatim}
-OKRES UCZĄCY
-Zysk skumulowany:     0.2917
-Calmar:     0.4538
-Liczba otwartych pozycji długich:     400
-Liczba otwartych pozycji krótkich:     405
-
-OKRES WALIDUJĄCY
-Zysk skumulowany:     -1.3244
-Calmar:     -1
-Liczba otwartych pozycji długich:     244
-Liczba otwartych pozycji krótkich:     245
-\end{verbatim}
-\newpage
-\textbf{II Wyniki badań przy maksymalizacji po wskaźniku Calmara.}\\
-\begin{figure}[h!]
-\centering
-\includegraphics[width = 0.6\textwidth]{SS_CADCHF_S4LS_calmar.png}
-\caption{Zysk skumulowany EURJPY na okresie testowym przy maksymalizacji według Calmara}
-\end{figure}
-\FloatBarrier
-\begin{verbatim}
-OKRES UCZĄCY
-Zysk skumulowany:     0.2917
-Calmar:     0.4538
-Liczba otwartych pozycji długich:     400
-Liczba otwartych pozycji krótkich:     405
-
-OKRES WALIDUJĄCY
-Zysk skumulowany:     -1.3244
-Calmar:     -1
-Liczba otwartych pozycji długich:     244
-Liczba otwartych pozycji krótkich:     245
-\end{verbatim}
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\newpage
-\begin{center}
-\begin{large}
-Mass Index - indeks masy : opis wskaźnika\\
-\end{large}
-\end{center}
-%\baselineskip=22pt
+\section{Mass Index}
+\label{sec:1ATR}
 
@@
 \end{verbatim}
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-
-\end {document}
+%

### 2013-12-17 Article/book/BookSources/chapter1IndicatorsOBV.tex
book - all inicators

--- 2013-11-12 Matlabs/Indicators/LB/OBV/ROC_AB.tex
@@
-\documentclass[12pt,a4paper]{article}
-\usepackage{polski}
-\usepackage[utf8]{inputenc}
-\usepackage{amsmath}
-\usepackage{amssymb}
-\usepackage{amsfonts}
-\usepackage{graphicx}
-\usepackage{placeins}
-\usepackage{listings}
-\usepackage[svgnames]{xcolor}
- \lstset{literate={ą}{{\k{a}}}1 {ć}{{\'c}}1 {ę}{{\k{e}}}1 {ł}{{\l{}}}1 {ń}{{\'n}}1 {ó}{{\'o}}1 {ś}{{\'s}}1 {ż}{{\.z}}1 {ź}{{\'z}}1 {Ą}{{\k{A}}}1 {Ć}{{\'C}}1 {Ę}{{\k{E}}}1 {Ł}{{\L{}}}1 {Ń}{{\'N}}1 {Ó}{{\'O}}1 {Ś}{{\'S}}1 {Ż}{{\.Z}}1 {Ź}{{\'Z}}1 }
- \lstset{breaklines=true}
-\lstset{language=Matlab,
-  keywords={break,case,catch,continue,else,elseif,end,for,function,
-     global,if,otherwise,persistent,return,switch,try,while},
-  basicstyle=\ttfamily,
-  keywordstyle=\color{blue},
-  commentstyle=\color{DarkGreen},
-  stringstyle=\color{dkgreen},
-  numbers=left,
-  numberstyle=\tiny\color{gray},
-  stepnumber=1,
-  numbersep=10pt,
-  backgroundcolor=\color{white},
-  tabsize=4,
-  showspaces=false,
-  showstringspaces=false}
-
-\begin {document}
-\begin{center}
-\begin{large}
-OBV -- On Balance Volume-  opis wskaźnika  \\
-\end{large}
-Łukasz Brzosko
-\end{center}
-%\baselineskip=22pt
+\section{OBV --- On Balance Volume}
+\label{sec:1OBV}
 

### 2013-12-17 Article/book/BookSources/chapter1IndicatorsPPV.tex
book - all inicators

--- 2013-10-25 Matlabs/Indicators/KB/Pivot.tex
@@
-\documentclass[12pt,a4paper]{article}
-\usepackage{polski}
-\usepackage[utf8]{inputenc}
-\usepackage{amsmath}
-\usepackage{amssymb}
-\usepackage{amsfonts}
-\usepackage{graphicx}
-\usepackage{placeins}
-\usepackage{listings}
-\usepackage[svgnames]{xcolor}
- \lstset{literate={ą}{{\k{a}}}1 {ć}{{\'c}}1 {ę}{{\k{e}}}1 {ł}{{\l{}}}1 {ń}{{\'n}}1 {ó}{{\'o}}1 {ś}{{\'s}}1 {ż}{{\.z}}1 {ź}{{\'z}}1 {Ą}{{\k{A}}}1 {Ć}{{\'C}}1 {Ę}{{\k{E}}}1 {Ł}{{\L{}}}1 {Ń}{{\'N}}1 {Ó}{{\'O}}1 {Ś}{{\'S}}1 {Ż}{{\.Z}}1 {Ź}{{\'Z}}1 }
- \lstset{breaklines=true}
-\lstset{language=Matlab,
-  keywords={break,case,catch,continue,else,elseif,end,for,function,
-     global,if,otherwise,persistent,return,switch,try,while},
-  basicstyle=\ttfamily,
-  keywordstyle=\color{blue},
-  commentstyle=\color{DarkGreen},
-  stringstyle=\color{dkgreen},
-  numbers=left,
-  numberstyle=\tiny\color{gray},
-  stepnumber=1,
-  numbersep=10pt,
-  backgroundcolor=\color{white},
-  tabsize=4,
-  showspaces=false,
-  showstringspaces=false}
-
-\begin {document}
-\begin{center}
-\begin{large}
-Pivot Point--- opis wskaźnika Pivot Point\\
-\end{large}
-Katarzyna Buda
-\end{center}
-%\baselineskip=22pt
+\section{Pivot Point}
+\label{sec:1PPV}
 
@@
 Jest to wzór określający potencjalny zasięg ruchu notowań w danej jednostce czasu.
-Opiera się na obliczeniu danych za pomocą następujących wzorów: 1, 2, 3, 4 oraz 5}.
+Opiera się na obliczeniu danych za pomocą następujących wzorów: 1, 2, 3, 4 oraz 5.
 \begin{equation}
-P(Pivot point) = \franc{(H + L + C)}{3}
+P(Pivot point) = \frac{(H + L + C)}{3}
 \label{wzor_1}
@@
 \end{itemize}
-\newline
 
@@
 \FloatBarrier
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\end {document}
+%

### 2013-12-17 Article/book/BookSources/chapter1IndicatorsROC.tex
book - all inicators

--- 2013-09-29 Matlabs/Indicators/AB/ROC_AB.tex
@@
-\documentclass[12pt,a4paper]{article}
-\usepackage{polski}
-\usepackage[utf8]{inputenc}
-\usepackage{amsmath}
-\usepackage{amssymb}
-\usepackage{amsfonts}
-\usepackage{graphicx}
-\usepackage{placeins}
-\usepackage{listings}
-\usepackage[svgnames]{xcolor}
- \lstset{literate={ą}{{\k{a}}}1 {ć}{{\'c}}1 {ę}{{\k{e}}}1 {ł}{{\l{}}}1 {ń}{{\'n}}1 {ó}{{\'o}}1 {ś}{{\'s}}1 {ż}{{\.z}}1 {ź}{{\'z}}1 {Ą}{{\k{A}}}1 {Ć}{{\'C}}1 {Ę}{{\k{E}}}1 {Ł}{{\L{}}}1 {Ń}{{\'N}}1 {Ó}{{\'O}}1 {Ś}{{\'S}}1 {Ż}{{\.Z}}1 {Ź}{{\'Z}}1 }
- \lstset{breaklines=true}
-\lstset{language=Matlab,
-  keywords={break,case,catch,continue,else,elseif,end,for,function,
-     global,if,otherwise,persistent,return,switch,try,while},
-  basicstyle=\ttfamily,
-  keywordstyle=\color{blue},
-  commentstyle=\color{DarkGreen},
-  stringstyle=\color{dkgreen},
-  numbers=left,
-  numberstyle=\tiny\color{gray},
-  stepnumber=1,
-  numbersep=10pt,
-  backgroundcolor=\color{white},
-  tabsize=4,
-  showspaces=false,
-  showstringspaces=false}
-
-\begin {document}
-\begin{center}
-\begin{large}
-ROC --- opis wskaźnika Rate Of Change\\
-\end{large}
-Aneta Bera
-\end{center}
-%\baselineskip=22pt
-
+\section{ROC --- Rate Of Change indicator}
+\label{sec:1ROC}
 Rate Of Change, nazywany po polsku wskaźnikiem zmian, jest to wskaźnikiem który

### 2013-12-17 Article/book/BookSources/chapter1IndicatorsSTF.tex
book - all inicators

--- 2013-10-14 Matlabs/Indicators/KB/Stochastic Fast.tex
@@
-\documentclass[12pt,a4paper]{article}
-\usepackage{polski}
-\usepackage[utf8]{inputenc}
-\usepackage{amsmath}
-\usepackage{amssymb}
-\usepackage{amsfonts}
-\usepackage{graphicx}
-\usepackage{placeins}
-\usepackage{listings}
-\usepackage[svgnames]{xcolor}
- \lstset{literate={ą}{{\k{a}}}1 {ć}{{\'c}}1 {ę}{{\k{e}}}1 {ł}{{\l{}}}1 {ń}{{\'n}}1 {ó}{{\'o}}1 {ś}{{\'s}}1 {ż}{{\.z}}1 {ź}{{\'z}}1 {Ą}{{\k{A}}}1 {Ć}{{\'C}}1 {Ę}{{\k{E}}}1 {Ł}{{\L{}}}1 {Ń}{{\'N}}1 {Ó}{{\'O}}1 {Ś}{{\'S}}1 {Ż}{{\.Z}}1 {Ź}{{\'Z}}1 }
- \lstset{breaklines=true}
-\lstset{language=Matlab,
-  keywords={break,case,catch,continue,else,elseif,end,for,function,
-     global,if,otherwise,persistent,return,switch,try,while},
-  basicstyle=\ttfamily,
-  keywordstyle=\color{blue},
-  commentstyle=\color{DarkGreen},
-  stringstyle=\color{dkgreen},
-  numbers=left,
-  numberstyle=\tiny\color{gray},
-  stepnumber=1,
-  numbersep=10pt,
-  backgroundcolor=\color{white},
-  tabsize=4,
-  showspaces=false,
-  showstringspaces=false}
+\section{Stochastic Fast}
+\label{sec:1STF}
 
-\begin {document}
-\begin{center}
-\begin{large}
-Stochastic Fast --- opis wskaźnika Stochastic Fast\\
-\end{large}
-Katarzyna Buda
-\end{center}
-%\baselineskip=22pt
-
-Stochastic Fast - wskaxnik stochastyczny szybki, zaproponowany w latach 50-tych przez George C.
+Stochastic Fast - wskaźnik stochastyczny szybki, zaproponowany w latach 50-tych przez George C.
 Lane.
@@
 \begin{itemize}
-\newline
 \item ValD - jest wygładzoną linią ValK

### 2013-12-17 Article/book/BookSources/chapter1IndicatorsSTS.tex
book - all inicators

--- 2013-10-03 Matlabs/Indicators/MZ/MZ_TEX/Indicators_MZ.tex
@@
-\documentclass[12pt,a4paper]{article}
-\usepackage[MeX]{polski}
-\usepackage[utf8]{inputenc}
-\usepackage{amsmath}
-\usepackage{amssymb}
-\usepackage{amsfonts}
-\usepackage{graphicx}
-\usepackage{placeins}
-\usepackage{listings}
-\usepackage[svgnames]{xcolor}
- \lstset{literate={ą}{{\k{a}}}1 {ć}{{\'c}}1 {ę}{{\k{e}}}1 {ł}{{\l{}}}1 {ń}{{\'n}}1 {ó}{{\'o}}1 {ś}{{\'s}}1 {ż}{{\.z}}1 {ź}{{\'z}}1 {Ą}{{\k{A}}}1 {Ć}{{\'C}}1 {Ę}{{\k{E}}}1 {Ł}{{\L{}}}1 {Ń}{{\'N}}1 {Ó}{{\'O}}1 {Ś}{{\'S}}1 {Ż}{{\.Z}}1 {Ź}{{\'Z}}1 }
- \lstset{breaklines=true}
-\lstset{language=Matlab,
-  keywords={break,case,catch,continue,else,elseif,end,for,function,
-     global,if,otherwise,persistent,return,switch,try,while},
-  basicstyle=\ttfamily,
-  keywordstyle=\color{blue},
-  commentstyle=\color{DarkGreen},
-  stringstyle=\color{dkgreen},
-  numbers=left,
-  numberstyle=\tiny\color{gray},
-  stepnumber=1,
-  numbersep=10pt,
-  backgroundcolor=\color{white},
-  tabsize=4,
-  showspaces=false,
-  showstringspaces=false}
-
-\begin {document}
-\begin{center}
-\begin{large}
-Stochastic Slow - oscylator stochastyczny wolny : opis wskaźnika\\
-\end{large}
-Michał Zabłocki
-\end{center}
-%\baselineskip=22pt
+\section{Stochastic Slow}
+\label{sec:1STS}
 
@@
 \end{verbatim}
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\newpage
-\begin{center}
-\begin{large}
-Mass Index - indeks masy : opis wskaźnika\\
-\end{large}
-\end{center}
-%\baselineskip=22pt
-
-Mass Index wskaźnik jest pomocny w identyfikacji punktów zwrotnych, poprzez mierzenie odległości pomiędzy cenami maksymalnymi a minimalnymi.
-Według autora zmiana kierunku trendu następuje w momencie zaobserwowania tzw.
-wybrzuszenia zwrotnego, czyli wejścia wskaźnika ponad poziom 27 i następnie spadku poniżej 26,5.
-Wskaźnik nie identyfikuje jednak kierunku trendu, ustala jedynie punkt zwrotny.
-Sposób wyliczenia kolejnych wartości wskaźnika dla danego punktu w czasie przedstawia wzór \ref{wzor_3}.
-\begin{equation}
-Mass Index = \sum_{0}^{24} \left[\begin{array}{c} \frac{ EMA(H - L, 9)}{ EMA(EMA(H-L, 9), 9)}\end{array}\right]\\
-\label{wzor_3}
-\end{equation}
-
-\noindent Sama interpretacja wskaźnika nie pozwala na wskazanie momentów w których mogą być zawierane konkretne transakcje (kopno/sprzedarz).
-W określeniu czy jest to sygnał kupna czy sprzedaży autor zaleca stosowanie 9- dniowej ekspotencjalnej średniej na wykresie notowań.
-Dlatego przyjeliśmy zasadę, która zakłada, że po wystąpieniu wybrzuszenia zwrotnego przyjmujemy jako sygnał kupna sytuację gdy wartość ceny zamknięcia przewyższa wartość 9- dniowej ekspotencjalnej średniej.
-Natomiast, gdy wartość ceny zamknięcia jest mniejsza od wartość 9- dniowej ekspotencjalnej średniej, to przyjmuje się taką sytuację za sygnał sprzedaży.
-Zostało to przedstawione na rysunku \ref{kupsprz2}.
-\\
-\begin{figure}[h!]
-\centering
-\includegraphics[width = \textwidth]{mi2.png}
-\caption{Fragment przebiegu kursu akcji z naniesioną  9- dniową ekspotencjalną średnią (górny wykres) oraz odpowiadające jemu wartości wskaźnika indeksu masy wraz z sygnałami kupna --- zielone strzałki oraz sygnałami sprzedaży --- czerwone strzałki (dolny wykres)}
-\label{kupsprz2}
-\end{figure}
-\FloatBarrier
-
-\noindent Poniższy listing przedstawia zaimplementowaną w środowisku MATLAB strategię wykorzystującą opisywany wskaźnik.
-\begin{scriptsize}
-\begin{lstlisting}
-bestiL = 0;
-bestiS = 0;
-HL = C(:,2) - C(:,3); % różnica H - L
-kon=candlesCount-1;
-MI = zeros(candlesCount,1);
-HLaverage = ema(HL,9);
-EMA2 = HLaverage(9:end) ./ ema(HLaverage(9:end),9);
-for i = 41:kon-16
-    MI(i) = sum(EMA2(i-24:i));
-end
-Caverages = ema(C(:,4),9);
-
-sumR=zeros(1,candlesCount);
-R=zeros(1,candlesCount);
-pocz=50;
-iL=0; %liczba otwieranych pozycji kupna
-iS=0; %liczba otwieranych pozycji sprzedarzy
-lastCandle = kon-16;
-recordReturn=0;  %rekord zysku
-recordDrawdown=0;  %rekord obsuniecia
-LastPos = 0;
-pic1 = false;
-
-for i=pocz:lastCandle
-
-    if pic1 == false && MI(i) > 27 % warunek wystąpienia wybrzuszenia zwrotnego
-        pic1 = true;
-    end
-    if pic1 == true && MI(i) < 26.5 % warunek zawarcia transakcji
-        if C(i,4) > Caverages(i) % warunek kupna
-            R(i)= -C(i+1,4)-LastPos-spread; % zamknięcie S
-            LastPos = C(i+1,1); % otwarcie L
-            iL=iL+1;
-        elseif C(i,4) < Caverages(i) % warunek sprzedaży
-            R(i)=C(i+1,4)-LastPos-spread; % zamknięcie L
-            LastPos = C(i+1,1); % otwarcie S
-            iS=iS+1;
-        end
-        pic1 = false;
-    end
-    sumR(i)= sum(R(pocz:i));  %krzywa narastania kapitału
-
-    if sumR(i)>recordReturn
-        recordReturn=sumR(i);
-    end
-
-    if sumR(i)-recordReturn<recordDrawdown
-        recordDrawdown=sumR(i)-recordReturn;  %obsuniecie maksymalne
-    end
-end
-
-%wyniki końcowe
-sumReturn=sumR(lastCandle);
-Calmar=-sumReturn/recordDrawdown;  %wskaznik Calmara
-\end{lstlisting}
-\end{scriptsize}
-
-Na podstawie zebranych informacji dotyczących wskaźnika $Mass Index$ utworzono prostą strategię inwestycyjną bazującą na regule: jeśli wystąpi wybrzuszenie zwrotne oraz wartość ceny zamknięcia przewyższy wartość 9- dniowej ekspotencjalnej średniej, to otwierana jest pozycja długa ($L$), a zamknięta pozycja krótka ($S$), która została wcześniej otwarta .
-Natomiast, gdy wartość ceny zamknięcia będzie mniejsza od wartość 9- dniowej ekspotencjalnej średniej, to otwarta zostanie pozycja krótka ($S$), a zamknięta długa.
-Badania zostały przeprowadzone na parze walutowej $CADCHF$ (szereg czasowy przedstawiony na rysunku \ref{rys2}).
-\\
-
-Ze względu na to iż wszystkie parametry wzoru są arbitralnie ustawione, to zbiór danych (świec) nie został podzielony na dwie części: uczącą i testującą ($40\%$ całości).
-Na całym zbiorze danych weryfikowano skuteczność strategii.
-\\
-
-\newpage
-\noindent \textbf{I Wyniki badań.}\\
-\begin{figure}[h!]
-\centering
-\includegraphics[width = 0.6\textwidth]{MI_CADCHF_S4LS.png}
-\caption{Zysk skumulowany CADCHF na okresie testowym przy maksymalizacji według zysku}
-\end{figure}
-\FloatBarrier
-\begin{verbatim}
-OKRES WALIDUJĄCY
-Zysk skumulowany:     -8.3942
-Calmar:     -1
-Liczba otwartych pozycji długich:     5
-Liczba otwartych pozycji krótkich:     3
-\end{verbatim}
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-
-\end {document}
+%

### 2013-12-21 Article/book/BookSources/chapter1IndicatorsROC.tex
AB - indicator (PL->ENG, PNG->EPS)

@@
 \label{sec:1ROC}
-Rate Of Change, nazywany po polsku wskaźnikiem zmian, jest to wskaźnikiem który
-mierzy procentową zmianę pomiędzy najnowszą ceną
-zamknięcia a ceną $k$ okresów wcześniej. Sposób wyliczenia wartości wskaźnika ROC dla danego punktu w czasie przedstawiają wzory \ref{wzor_1} oraz \ref{wzor_2}.
+Rate Of Change is an indicator which measures the percentage change between the latest price and closing price of $k$ periods before.
+The method of calculating the value of the ROC, for a given point in time, represent formulas \ref{wzorroc_1} and \ref{wzorroc_2}.
 \begin{equation}
-ROC(\text{dziś}) = \frac{\text{Cena zamknięcia dziś} - \text{Cena zamknięcia } k \text{ okresów temu}}{\text{Cena zamknięcia } k \text{ okresów temu}}\\
-\label{wzor_1}
+ROC(\text{now}) = \frac{\text{Current close price} - \text{Close price} k \text{ periods before}}{\text{Close price } k \text{ periods before}}\\
+\label{wzorroc_1}
 \end{equation}
@@
 ROC(i) = \frac{C(i,4) - C(i-k,4)}{C(i-k,4)}
-\label{wzor_2}
+\label{wzorroc_2}
 \end{equation}
 
-\noindent Do podstawowych własności krzywej ROC należą:
+\noindent The basic properties of the ROC curve are:
 \begin{itemize}
-\item obrazuje ona jak zmieniała się cena obserwowanego rynku w danym okresie,
-\item jeśli wartość oscylatora znajduje się poniżej zera, to obecna cena jest wyższa od tej sprzed $k$-godzin temu, analogicznie gdy oscylator znajduje się powyżej zera, oznacza to, że obecna cena jest niższa od tej sprzed $k$-godzin temu,
-\item wzrastająca linia wskaźnika pokazuje, że różnice między
-obecnym poziomem ceny a tym $k$ -czas temu się
-zwiększają, malejąca mówi natomiast, że różnica ta się zmniejsza,
-\item jeśli ceny akcji będą rosły to można oczekiwać, że linia
-oscylatora będzie zachowywać się analogicznie, jeśli ceny będą natomiast malały to linia oscylatora powinna maleć.
+\item it shows how the observed market price during the period changed,
+\item when the oscillator value is below zero, then the current price is higher than one from $k$-candles ago; analogically, when the oscillator is above zero, it means that the current price is lower than the price from $k$-candles ago,
+\item increasing indicator line shows that the differences between the current prices and ones from $k$-time ago are increasing, decreasing says, that this differences decrease,
+\item if the stock prices rise it can be expected that the oscillator line will behave in the same way; if the prices decrease the oscillator line should decrease.
 \end{itemize}
-Najważniejszą własnością opisywanego wskaźnika, stosowaną przy implementacjach strategii, jest fakt wskazywania momentów w których powinny zostać zawarte transakcje.
-Gdy wartość wskaźnika przetnie od dołu poziom zero to zakłada się, że jest to dobry moment kupna, jeśli przetnie poziom zera od góry to sprzedaży.
-Zostało to przedstawione na rysunku \ref{kupsprz}.
-\\
+The most important property of the described indicator, used while implementing  the strategy, is that it indicates the moments in which transactions should be made.
+When the value of the indicator crosses the zero level from below, it is assumed that this is a good time to buy, if it crosses the zero level from above, this is the good time to sale.
+This is shown in Figure \ref{kupsprzroc}.\\
 \begin{figure}[h!]
 \centering
-\includegraphics[width = \textwidth]{BuySell.png}
-\caption{Fragment przykładowej krzywej ROC wraz z sygnałami kupna --- zielone strzałki oraz sygnałami sprzedaży --- czerwone strzałki}
-\label{kupsprz}
+\includegraphics[width = \textwidth]{BuySell.eps}
+\caption{Part of the sample ROC curve with buying signals --- green arrows --- and selling signals --- red arrows}
+\label{kupsprzroc}
 \end{figure}
@@
 
-\noindent Poniższy listing przedstawia zaimplementowaną strategię w środowisku MATLAB.
+\noindent The following listing shows the strategy implemented in MATLAB.
 \begin{scriptsize}
@@
 kon = size(C,1)-1;
-iL = 0; % przekroczenie 0 w górę - kupno (L)
-iS = 0; % przekroczenie 0 w dół - sprzedaż (S)
+iL = 0; % exceeding 0 to top - buy(L)
+iS = 0; % exceeding 0 to bottom - sell(S)
 sumR = zeros(1,size(C,1));
@@
 
-recordReturn = 0;  % rekord zysku
-recordDrawdown = 0;  % rekord obsuniecia
-LastPos = 0;    % zmienna do przechowywania wartości na otwarciu ostatniej pozycji
+recordReturn = 0;  % record profit
+recordDrawdown = 0;  % record drawdown
+LastPos = 0;    % variable used to store the value of the opening of the last position
 
 for i=pocz:kon
-    ROC_vec(i) = ((C(i,4) - C(i-k,4))/C(i-k,4))*100;  % obliczenie punktu krzywej ROC
-    if ROC_vec(i)*ROC_vec(i-1)<=0   % przecięcie krzywej ROC z zerem
-        if ROC_vec(i-1)<ROC_vec(i)  % warunek kupna
+   ROC_vec(i) = ((C(i,4) - C(i-k,4))/C(i-k,4))*100;  % calculating the ROC curve
+   if ROC_vec(i)*ROC_vec(i-1)<=0   % the intersection of the ROC curve with zero
+       if ROC_vec(i-1)<ROC_vec(i)  % a condition of purchase
            if iL+iS>0
-                R(i) = -C(i+1,4)+LastPos-spread;   % zamknięcie S
+               R(i) = -C(i+1,4)+LastPos-spread;   % closing S
            end
-            LastPos = C(i+1,1);   % otworzenie L
+           LastPos = C(i+1,1);   % open L
            iL = iL + 1;
-        elseif ROC_vec(i-1)>ROC_vec(i)  % warunek sprzedaży
+       elseif ROC_vec(i-1)>ROC_vec(i)  % a condition of sale
            if iL+iS>0
-                R(i) = C(i+1,4)-LastPos-spread;  % zamknięcie L
+               R(i) = C(i+1,4)-LastPos-spread;  % closing L
            end
-            LastPos = C(i+1,1);   % otworzenie S
+           LastPos = C(i+1,1);   % open S
            iS = iS + 1;
@@
    sumR(i) = sum(R(pocz:i));
-
     if sumR(i)>recordReturn
@@
 
-Na podstawie zebranych informacji dotyczących wskaźnika $ROC$ utworzono prostą strategię inwestycyjną bazującą na regule: jeśli linia $ROC$ przetnie się z poziomem zera od dołu, to otwierana jest pozycja długa ($L$), a zamykana pozycja krótka ($S$), która została wcześniej otwarta.
-Gdy natomiast nastąpi przecięcie linii $ROC$ z poziomem zera od góry to otwarta zostanie pozycja krótka, a zamknięta długa.
-Badania zostały przeprowadzone na parze walutowej $EURJPY$ (szereg czasowy przedstawiony na rysunku \ref{rysunek2}).
-\\
+Based on collected information on the $ROC$ ratio a simple investment strategy, based on the rule: if the $ROC$ line intersects the zero level from below, it opens a long position ($L$) and closed a short position ($S$) which has been previously opened, was created.
+When $ROC$ line intersects zero level from above it will open a short position and close a long one.
+Tests were carried out on $EURJPY$ currency pair (time series shown in Figure \ref{rysunek2roc}).\\
+
 \begin{figure}[h!]
 \centering
-\includegraphics[width = \textwidth]{podzialDanych.png}
-\caption{Badany szereg czasowy z podziałem na część uczącą i testową}
-\label{rysunek2}
+\includegraphics[width = \textwidth]{podzialDanych.eps}
+\caption{Studied time series with the division into the learn and test part}
+\label{rysunek2roc}
 \end{figure}
 \FloatBarrier
-Cały zbiór danych (świec) podzielony został na dwie części: uczącą ($60\%$ całości) oraz testową ($40\%$ całości).
-W przeprowadzonych badaniach poszukiwano optymalnej wartości parametru $k$ na okresie uczącym, następnie weryfikowano otrzymane wyniki na okresie testowym.
-Wybór optymalnej wartości parametru $k$ determinowano na dwa sposoby:
+The entire data set (candles) is divided into two parts: the learn ($60 \%$ of the total) and test ($40\%$ of the total).
+During studies an optimal value for $k$ on a period of learning was searched, then verified obtained results for the test period.
+Selecting the optimal value of the parameter $ k $ was determined in two ways:
 \begin{itemize}
-\item otrzymanego zysku skumulowanego,
-\item wskaźnika Calamara.
+\item the resulting final profit,
+\item Calmar ratio.
 \end{itemize}
-
-\noindent \textbf{I Wyniki badań przy maksymalizacji po zysku.}\\
+\newpage
+\noindent \textbf{I The results of maximizing the profit.}\\
 \begin{figure}[h!]
 \centering
-\includegraphics[width = 0.6\textwidth]{ROC_EURJPY_LS_SearchBestK_zysk.png}
-\caption{Zysk skumulowany EURJPY na okresie testowym przy maksymalizacji według zysku}
+\includegraphics[width = 0.7\textwidth]{ROC_EURJPY_LS_SearchBestK_zysk.eps}
+\caption{Cumulative return for the test period of EURJPY  while maximizing the profit}
 \end{figure}
@@
 \begin{verbatim}
-OKRES UCZĄCY
-Długość cyklu: 	89
-Zysk skumulowany: 	16.81
-Calmar: 	2.66
-Liczba otwartych pozycji długich: 	100
-Liczba otwartych pozycji krótkich: 	100
+LEARN PERIOD
+The length of the cycle: 	89
+Cumulative return: 	16.81
+Calmar ratio: 	2.66
+The number of opened long positions: 	100
+The number of opened short positions:  	100
 
-OKRES WALIDUJĄCY
-Długość cyklu: 	89
-Zysk skumulowany: 	11.87
-Calmar: 	1.00
-Liczba otwartych pozycji długich: 	61
-Liczba otwartych pozycji krótkich: 	61
+TEST PERIOD
+The length of the cycle: 	89
+Cumulative return: 	11.87
+Calmar ratio: 	1.00
+The number of opened long positions: 	61
+The number of opened short positions: 	61
 \end{verbatim}
-\newpage
-\textbf{II Wyniki badań przy maksymalizacji po wskaźniku Calmara.}\\
+
+\noindent \textbf{II The results of maximizing the Calmar ratio.}\\
 \begin{figure}[h!]
 \centering
-\includegraphics[width = 0.6\textwidth]{ROC_EURJPY_LS_SearchBestKCalmar_zysk.png}
-\caption{Zysk skumulowany EURJPY na okresie testowym przy maksymalizacji według Calmara}
+\includegraphics[width = 0.7\textwidth]{ROC_EURJPY_LS_SearchBestKCalmar_zysk.eps}
+\caption{Cumulative return for the test period of EURJPY  while maximizing the Calmar ratio}
 \end{figure}
@@
 \begin{verbatim}
-OKRES UCZĄCY
-Długość cyklu: 	230
-Zysk skumulowany: 	12.82
-Calmar: 	3.83
-Liczba otwartych pozycji długich: 	52
-Liczba otwartych pozycji krótkich: 	51
+LEARN PERIOD
+The length of the cycle: 	230
+Cumulative return: 	12.82
+Calmar ratio: 3.83
+The number of opened long positions: 	52
+The number of opened short positions:  	51
 
-OKRES TESTUJĄCY
-Długość cyklu: 	230
-Zysk skumulowany: 	20.64
-Calmar: 	5.08
-Liczba otwartych pozycji długich: 	28
-Liczba otwartych pozycji krótkich: 	29
+TEST PERIOD
+The length of the cycle: 	230
+Cumulative return: 	20.64
+Calmar ratio: 	5.08
+The number of opened long positions: 	28
+The number of opened short positions: 	29
 \end{verbatim}
-%

### 2014-01-24 ForexTester/ForexTester/Strategies/EarthWorm.cs
Earthworm tests

@@ -27,21 +27,26 @@ namespace ForexTester.Strategies
             var bestReturn = -120.0;
             var candlesCount = Candles.Count;
             var bestCalmar = 0.0;
-            var bestMa = 0;
+            var bestParam1 = 0;
+            var bestParam2 = 0;
             var shortPositionOpen = 0;
             var longPositionOpen = 0;
             const double defaultSpread = 0.0002;
             using (var writer = new StreamWriter(filename, false))
             {
                 writer.WriteLine("results");
-                for (var param1 = 20; param1 <= 20; param1 += 1)
+                //const int param1 = 215;
+                for (var param1 = 10; param1 <= 80; param1 += 1)
                 {
-                    for (var param2 = 1; param2 <= 1; param2++)
+                   // const int param2 = 3;
+                    for (var param2 = 1; param2 <= 40; param2++)
+                        //for (var param2 = 1; param2 <= param1 / 2 + 1; param2++)
                     {
                         var transactionState = TransactionStates.None;
                         var candlesBegin = param1 + 1;
                         var kon = candlesCount - 1;
                         var lastCandle = kon;
+                        var isPosition = false;
                         sumRa = new List<double>(candlesCount);
                         var returnValues = new List<double>(candlesCount);
                         var drawdowns = new List<double>(candlesCount);
@@ -66,6 +71,7 @@ namespace ForexTester.Strategies
                                 shortPositionOpen++;
                                 positionReturn = Candles[i].Close - Candles[i + 1].Close - spread;
                                 transactionState = TransactionStates.Short;
+                                isPosition = true;
                                 writer.WriteLine("OTWARCIE Short: \t\t '{0} {1}'\t{2}\t{3}", Candles[i].Date, Candles[i].Time, GetDouble(positionReturn), GetDouble(Candles[i].Close));
 
                             }
@@ -75,12 +81,13 @@ namespace ForexTester.Strategies
                                 longPositionOpen++;
                                 positionReturn = -Candles[i].Close + Candles[i + 1].Close - spread;
                                 transactionState = TransactionStates.Long;
+                                isPosition = true;
                                 writer.WriteLine("OTWARCIE  LONG: \t\t '{0} {1}'\t{2}\t{3}", Candles[i].Date, Candles[i].Time, GetDouble(positionReturn), GetDouble(Candles[i].Close));
                             }
                             returnValues.Add(positionReturn);
[…]

### 2014-01-24 Article/Article20130912/LatexArt/tewi-paper-template_minipages.tex
Postal code
6. is added

@@
 \affiliation{%
-  \inst{1}West Pomeranian University of Technology, Szczecin, Poland\\
+  \inst{1}West Pomeranian University of Technology, Żołnierska 49, 71-210 Szczecin, Poland\\
   \{awilinski, abera, wnowicki, pblaszynski\}@wi.zut.edu.pl
@@
 \begin{itemize}
-\item p1 --- the number of candles, based on which the calculation of the current value of the band barrier is made; for researched time series, value of p1 generally ranges from 10 to 30;
-\item p2 --- number of steps forward, after which the position is closed in case none other close condition was met before; this value belongs to range from 3 to 40;
-\item p3 --– StopLoss condition; usually it remained in range from 0.002 to 0.017 expressed in values of EURUSD, which in researched period stayed in range from 1.2 to 1.4, as can be seen in Fig.
+\item p1 is the number of candles, based on which the calculation of the current value of the band barrier is made; for researched time series, value of p1 generally ranges from 10 to 30;
+\item p2 is number of steps forward, after which the position is closed in case none other close condition was met before; this value belongs to range from 3 to 40;
+\item p3 is StopLoss condition; usually it remained in range from 0.002 to 0.017 expressed in values of EURUSD, which in researched period stayed in range from 1.2 to 1.4, as can be seen in Fig.
 \ref{timeSeries};
-\item p4 --– TakeProfit condition; generally ranged from 0.0015 to 0.009;
-\item p5 --- band buffer, offset from the barrier of the band defining the actual level of the expected crossing of the  price; ranged from -0.002 to 0.003;
-\item p6 --- maximum number of open positions at the same time; ranged from 3 to 20;
-\item p7 --- number of candles that determines average volume value; generally ranged from 2 to 10;
-\item p8 --- maximum value of the difference between the current value of the volume and the average value calculated on the basis of p7 candles back; ranged from 150 to 500;
-\item p9 --- number of candles on the cumulative profit curve, based on which current drawdown is calculated; ranged from 5 to 25;
-\item p10 --- highest acceptable drawdown on the cumulative yield curve; generally ranged from 0.0021 to 0.008;
-\item p11 --- acceptable amount of the cumulative loss for all currently open positions; ranged from 0.0005 to 0.003;
+\item p4 is TakeProfit condition; generally ranged from 0.0015 to 0.009;
+\item p5 is band buffer, offset from the barrier of the band defining the actual level of the expected crossing of the  price; ranged from -0.002 to 0.003;
+\item p6 is maximum number of open positions at the same time; ranged from 3 to 20;
+\item p7 is the number of candles that determines average volume value; generally ranged from 2 to 10;
+\item p8 is maximum value of the difference between the current value of the volume and the average value calculated on the basis of p7 candles back; ranged from 150 to 500;
+\item p9 is the number of candles on the cumulative profit curve, based on which current drawdown is calculated; ranged from 5 to 25;
+\item p10 is highest acceptable drawdown on the cumulative yield curve; generally ranged from 0.0021 to 0.008;
+\item p11 is acceptable amount of the cumulative loss for all currently open positions; ranged from 0.0005 to 0.003;
 \end{itemize}
@@
 where:\\
-\textit{price} – current value for EURUSD;\\
-\textit{bottomBorder(p1)} – value of lower band barrier for parameter p1; here minimum of last p1 minima; \\
-\textit{buffor(p5)} – value of buffer that moves said barrier;\\
-\textit{current p6} – number of currently opened positions;\\
-\textit{Vol} – current value of volume (in the candle);\\
-\textit{meanVol(p7)} – mean of volume of last p7 candles;\\
+\textit{price} is current value for EURUSD;\\
+\textit{bottomBorder(p1)} is value of lower band barrier for parameter p1; here minimum of last p1 minima; \\
+\textit{buffor(p5)} is value of buffer that moves said barrier;\\
+\textit{current p6} is number of currently opened positions;\\
+\textit{Vol} is current value of volume (in the candle);\\
+\textit{meanVol(p7)} is mean of volume of last p7 candles;\\
 

### 2014-01-24 Article/Article20130912/LatexArt/tewi-paper-template_minipages.tex
7. TewiMiC, TewiMiD consistency

@@
 Special parameter called the buffer (p5) has been added, causing the offset of barrier from its actual value.
-Thus, the condition for opening TewiMIC strategy is:
+Thus, the condition for opening TewiMiC strategy is:
 \begin{equation}
@@
 
-As a result of these conditions, long positions, in sub strategy TewiMIC, are opened when three conditions are met simultaneously: crossing the bottom barrier reduced by buffer by the current price, the number of open positions is lesser than the limit (which is the optimized parameter p6) and the difference between the current volume and the average of the volume of the last p7 candle is less than the parameter p8.\\
+As a result of these conditions, long positions, in sub strategy TewiMiC, are opened when three conditions are met simultaneously: crossing the bottom barrier reduced by buffer by the current price, the number of open positions is lesser than the limit (which is the optimized parameter p6) and the difference between the current volume and the average of the volume of the last p7 candle is less than the parameter p8.\\
 
@@
 \end{minipage}
-\caption{Earnings accumulated over time, depending on the length of the test period for TewiMIC}
+\caption{Earnings accumulated over time, depending on the length of the test period for TewiMiC}
 \end{figure}
@@
 \end{minipage}
-\caption{Earnings accumulated over time, depending on the length of the test period for TewiMID}
+\caption{Earnings accumulated over time, depending on the length of the test period for TewiMiD}
 \end{figure}

### 2014-01-24 Article/Article20130912/LatexArt/tewi-paper-template_minipages.tex
8. Equation (20), ((1), (2) -> (1))
9. StopLoss, TakeProfit, ith, (k+i)th

@@
 \begin{equation}
-topBorder = \max{(H_{i-n},...,H_{i-1})}
-\end{equation}
-\begin{equation}
-bottomBorder = \min{(L_{i-m},...,L_{i-1})}
+\begin{split}
+topBorder = \max{(H_{i-n},...,H_{i-1})}, \\ 
+bottomBorder = \min{(L_{i-m},...,L_{i-1})}.
+\end{split}
 \end{equation}
@@
 \begin{enumerate}
-\item Opened long position will be closed, if at the close of the candle (i + p2) the position remained open, where i - number of candle, which was opened;
+\item Opened long position will be closed, if at the close of the candle (i + p2) the position remained open, where \textit{i} is number of candle, which was opened;
 
-\item Position will be closed if at the opening of the next (i + k)-th - the candle after i-th candle, in which the position was opened, following condition is met: 
+\item Position will be closed if at the opening of the next (i + k)th, the candle after \textit{i}th candle, in which the position was opened, following condition is met: 
 \begin{equation}
@@
 \end{equation} 
-where \textit{PriceO(i+k)} is the opening value for (i+k)-th candle and \textit{SL} is Stop Loss (level of acceptable risk in one trade) in pips;\\
+where \textit{PriceO(i+k)} is the opening value for \textit{(i+k)}th candle and \textit{SL} is StopLoss (level of acceptable risk in one trade) in pips;\\
 Then the profit (in this case loss) will be calculated as:
@@
 
-\item Position will be closed if inside the next (i + k)-th - the candle after i-th candle, in which the position was opened, following condition is met: 
+\item Position will be closed if inside the next \textit{(i + k)}th, the candle after \textit{i}th candle, in which the position was opened, following condition is met: 
 \begin{equation}
-(PriceO(i+k)-Price(i) )>-SL \text{ and } (LowPrice(i+k)-Price(i))<-SL
+\begin{split}
+(PriceO(i+k)-Price(i) )>-SL,\\
+(LowPrice(i+k)-Price(i))<-SL.
+\end{split}
 \end{equation} 
@@
 \end{equation}
-where LowPrice(i+k) – is a minimum value of (i+k)-th candle;
+where LowPrice(\textit{i+k}) is a minimum value of (\textit{i+k})th candle;
 
@@
 \end{equation} 
-where \textit{TP} is Take Profit (maximum reward level in single trade) in pips;\\
+where \textit{TP} is TakeProfit (maximum reward level in single trade) in pips;\\
 Then the profit will be calculated as:
@@
 
-\item Position will be closed if inside the next (i + k)-th - the candle after i-th candle, in which the position was opened, following condition is met: 
+\item Position will be closed if inside the next (\textit{i + k})th - the candle after \textit{i}th candle, in which the position was opened, following condition is met: 
 \begin{equation}
@@
 
-\item Position will be closed if at the opening of the next (i + k)-th - the candle after i-th candle, in which the position was opened, following condition is met: 
+\item Position will be closed if at the opening of the next (\textit{i + k})th - the candle after \textit{i}th candle, in which the position was opened, following condition is met: 
 \begin{equation}
@@
 \begin{enumerate}
-\item Opened short position will be closed if at the close of the candle (i + p2)-th the position remained open;\\
+\item Opened short position will be closed if at the close of the candle (\textit{i + p2})th the position remained open;\\
 
-\item Position will be closed if at the opening of the next (i + k)-th - the candle after i-th candle, in which the position was opened, following condition is met:
+\item Position will be closed if at the opening of the next (\textit{i + k})th - the candle after \textit{i}th candle, in which the position was opened, following condition is met:
 \begin{equation}
@@
 
-\item Position will be closed if inside the next (i + k)-th - the candle after i-th candle, in which the position was opened, following condition is met:
+\item Position will be closed if inside the next (\textit{i + k})th - the candle after \textit{i}th candle, in which the position was opened, following condition is met:
 \begin{equation}
@@
 
-\item Position will be closed if at the opening of the next (i + k)-th - the candle after i-th candle, in which the position was opened, following condition is met:
+\item Position will be closed if at the opening of the next (\textit{i + k})th - the candle after \textit{i}th candle, in which the position was opened, following condition is met:
 \begin{equation}
-Price(i)-PriceO(i+k>TP
+Price(i)-PriceO(i+k)>TP
 \end{equation}                                           
@@
 
-\item Position will be closed when inside the opening of the next (i + k)-th - the candle after i-th candle, in which the position was opened, following condition is met:
+\item Position will be closed when inside the opening of the next (\textit{i + k})th - the candle after \textit{i}th candle, in which the position was opened, following condition is met:
 \begin{equation}

### 2014-01-24 Article/Article20130912/LatexArt/tewi-paper-template_minipages.tex
[2],[4],[5],[10],[11],[12] and other highlights

@@
 The aim of this work is to verify the hypothesis of patterns extraction possibility from time series, which could be classified as providing better statistic and more accurate prognosis.
-Another important objective is confirmation of assumption, that financial markets time series have a “memory” of pattern efficiency in a time period after the time which pattern was learn in.
+Another important objective is confirmation of assumption, that financial markets time series have a “memory” of pattern efficiency in a time period following the time series that was used in learning period.
 This approach is consistent with the classic aim of machine learning shown by K.Murphy \cite{Murphy}, especially to financial markets described by Satchwell \cite{Satchwell}.
@@
 \cite{Cai} and many other authors \cite{Gencay, LeBaron, Tian}.
-Of course, the world of algorithms as well as prediction methods is using a completely different nature, such as regression \cite{Muriel}, multiple regression \cite{Wilinski, Fujimoto}, Fourier and wavelet transforms, and many others \cite{Raghuraj, KleskWilinski} is plenteous.
+Of course, the world of algorithms as well as prediction methods using a completely different nature, such as regression \cite{Muriel}, multiple regression \cite{Wilinski, Fujimoto}, Fourier and wavelet transforms, and many others \cite{Raghuraj, KleskWilinski} is plenteous.
 This methods are used as a basis for comparison, however the main focus is on mentioned simple rules.\\
@@
 \ref{timeSeries}).
-This time series, consists of 4734  \mbox{1-hour } candles, of the most important and the most fluent currency pair EURUSD from 22.10.2012.
+This time series, consists of 4734  \mbox{1-hour } candles, of the most important and the most fluent currency pair EURUSD from October 22, 2012.
 \begin{figure}[h!]
@@
 Of course, these results do not have to already be positive and acceptable and could negatively surprise investors.
-During the test as a measure of the effectiveness of the investment was considered the maximum rate of net profit (with transaction costs).
+During the test the maximum rate of net profit(with transaction costs) was considered as a measure of the effectiveness of the investment.
 The authors believe that these two criteria in evaluation the quality of simulation results are legitimate.
@@
 The above tactic was used for each stage of the learning period, then checked "sustainability" of designated sets of parameters for test periods of different lengths - the basic rate of 100 candles and the other in the range of 10-400.
-Figure ~\ref{research_methods} on page ~\pageref{research_methods} shows how the research was conducted.
+Figure ~\ref{research_methods} shows how the research was conducted.
 Having historical data for 1000 candles, optimal parameters, for said data, have been found using approach described above.
@@
 
-Figures ~\ref{MiC100} and ~\ref{MiD100} on page ~\pageref{MiD100} show the cumulative profit for the test period equal to 100 candles (hours) for the two examined strategies.
+Figures ~\ref{MiC100} and ~\ref{MiD100} show the cumulative profit for the test period equal to 100 candles (hours) for the two examined strategies.
 
@@
 But second strategy has smaller drawdowns.
-In addition, it is confirmed with the higher Calmar ratio - 12.79, where the result for first of these strategies is 10.22.
+In addition, it is confirmed with the higher Calmar ratio --- 12.79 --- where the result for first of these strategies is 10.22.
 According to the authors, results are excellent, achieved on testing sections, not on the learning periods.
@@
 Below, we present four graphs showing the results of the strategy TewiMiC.
-First (Figure \ref{Cum3DMiC} on page \pageref{Cum3DMiC}) shows the effect of test duration on the profit curve in time.
+First (Figure \ref{Cum3DMiC} shows the effect of test duration on the profit curve in time.
 To show how long in the test period optimal results are achieved we plotted 2D (two-dimensional) chart of final profit for each of the examined sizes.
-Figure \ref{Cum3DMiCend} on page \pageref{Cum3DMiCend} shows that the number of candles for achieving a high and satisfactory results are attributable to 80-120.
+Figure \ref{Cum3DMiCend} shows that the number of candles for achieving a high and satisfactory results are attributable to 80-120.
 The window size 100 reflects quite well expected test section.
@@
 
-Due to the different lengths of studied test periods, more reliable value required in the decision is earnings per candle, what means how much strategy can earn in one hour.
+Due to the different lengths of studied test periods, more reliable value used when making the decision is earnings per candle (that shows how much can strategy earn in one hour).
 This is shown in Figures \ref{Cum3DPerCMiC} and \ref{Cum3DPerCMiCend}.
@@
 \textbf{Results for TewiMiD }\\
-Figures ~\ref{Cum3DMiD} and ~\ref{Cum3DMiDend} on page ~\pageref{Cum3DMiDend} show impact of the length of the test period on the profit curve.
+Figures ~\ref{Cum3DMiD} and ~\ref{Cum3DMiDend} show impact of the length of the test period on the profit curve.
 In case of TewiMiD strategy it is difficult to determine the optimal interval length of the testing period.
@@
 Strategies properties discovered during the learning period are effective for a short time - for test data period - good lengths for both strategies are about 50 to 120 hours at 1000 hours of learning time.
-In the real market means that from 2 to 5 days, it can be assumed that the re- learning the parameters of the strategy should be carried out 1-2 times a week.
+In the real market it usually means from 2 to 5 days.
+It can be assumed that the re-learning of the parameters of the strategy should be carried out 1-2 times a week.
 This frequency is quite practical even for manual search of optimal parameters without fully automatic trading.\\

### 2014-01-24 Article/Article20130912/LatexArt/tewi-paper-template_minipages.tex
[3] changed

@@
 The problem of selecting the proper ratio between learning and testing phase is still unsolved for the non-stationary time series \cite{Ball, Ivakhnenko}.
-In this situation the right approach seems to be the use of the idea of computational intelligence \cite{Polya, Pedrycz} by which the empirical justification hypothesis entitles to use the model.\\
+In this situation the right approach seems to be the use of the idea of computational intelligence \cite{Polya, Pedrycz} which helps to compute adequate length of learning and testing periods.\\
 

### 2014-01-24 Article/Article20130912/LatexArt/tewi-paper-template_minipages.tex
other changes

@@
 The two strategy variants are part of an investment strategy that allows you to combine the four options of trading strategies.
-You can join the strategies presented with the strategies associated with the opening of long positions based on condition (order) Buy Stop and short positions in accordance with the model Sell Limit.
-It is a fact of this study add to the strategies associated with opening long positions based on condition for Buy Stop order and short positions in accordance with the Sell Limit model.
-Interesting, according to the authors, may also be improving the combined strategies through the synthesis of recommendations such as combining four variants, some of which (eg 3) indicates the need for the purchase, and some (such as 1) the need to conclude the sale of stock, it contains a number of transactions indications resulting from the sum of the different options (in the above example - two requests).
+You can join the strategies presented with the strategies associated with the opening of long positions based on condition (order) Buy Stop and short positions in accordance with the model Sell Limit.It is possible to add to the current strategies additional sub strategies associated with opening long positions (based on condition for Buy Stop order) and short positions (in accordance with the Sell Limit model).
+Interesting, according to the authors, may also be improving the combined strategies through the synthesis of recommendations.
+An example of such improvement may be combination of four variants, some of which (eg 3) indicate the need for the purchase, and some (such as 1) the need to conclude the sale of stock --- then the number of transactions that were made results from  accumulating all of the variants (in presented case -- 2 purchases).
 This implies a lower cost (for example, 2 times smaller).
@@
 
-\noindent Acknowledgment: Work done within the project TEWI financed from the Innovative Economy Programme in years 2012-2013.
+\noindent Acknowledgment: The work is done within the project TEWI financed from the Innovative Economy Programme in years 2012-2013.
 

### 2014-03-09 Article/Article20131011/jtacs_latex/jtacs_tewi.tex
article PP -> latex inkscape figures for granada update

\documentclass{jtacs}
\usepackage{placeins}

\begin{document}
\title{A study on the effectiveness of investment strategy based on the concept of pivot points levels using  Matthews criterion}
\markboth{A. Wilinski, T. Nyczaj, A. Bera, P. Blaszynski}{}
\maketitle

\xauthor{Antoni Wilinski$^1$, Tomasz Nyczaj$^1$, Aneta Bera$^1$, Piotr Blaszynski$^{1}$}
\xaffiliation{$^1$ Faculty of Computer Science and Information Technology, West Pomeranian University of Technology, Szczecin, Poland}
\xemail{\{awilinski, tnyczaj, abera, pblaszynski\}@wi.zut.edu.pl}

\begin{abstract}%
In this work, the possibility of assessing traditional investment strategy based on the pivot points for using with other than the commonly used criterion is examined. The authors attempted to apply the Matthews Correlation Coefficient (further reffered as MCC)  criterion based on a confusion matrix when assessing the strategy to include more factors than the traditional criteria (such as profit, profit vs. Risk, Sharpe ratio, Calmar ratio) and to express these factors by one number. The criterion based on a confusion matrix is, in authors beliefs, unique in this application and gives a fairly valuable estimation of trading strategy. An example of several strategies tested on EURUSD 1h time series in selected intervals in the years 2012-2013 is considered. Among these strategies there is a simple strategy based on the concept of pivot points levels and more complex derivative strategies, based on the vector of optimized values of certain parameters. These strategies are evaluated using both traditional criteria and modification of MCC proposed by the authors. 
\end{abstract}

\begin{keywords}%
algorithmic trading, machine learning, investment strategies, confusion matrix%
\end{keywords}

%
\section{Introduction}
Confusion matrix is a well-known criterion for assessing the quality of classification in machine learning, however, it does not give a clear answer which classifier is better\cite{provost} \cite{lewis} \cite{burke}. On its basis a number of additional measures of classification quality \cite{hay}, such as accuracy, precision, sensitivity, specificity, etc \cite{baldi} are built. One of additional measures derived from the confusion matrix is the Matthews criterion \cite{matthews}. It is so much more convenient than the original confusion matrix that is a number, not a matrix. Authors realize, however, that such a measure of the quality of the classification also has its drawbacks (like all the criteria or their sets used to evaluate the quality of investment strategies - Sharpe ratio, Calmar ratio or set of indicators). \\

	In the analysis of the confusion matrix a False Positive error that is a Type I error and the False Negative error that is a Type II error (Type II error \cite{burke}) are defined. If one considers the hypothesis that the test subject has cancer or that the observed passenger is a terrorist, a type I error causes less impact than the type II error (in common sense it is better to err in thinking that someone has cancer, than being wrong and believing that the patient is healthy; it is better to make a mistake by assessing that the observed passenger is a terrorist, than not recognizing one, when in fact he/she is). When considering the hypothesis that is needed to open long positions, because under certain conditions of close it will bring profit - type I error is more painful for the investor (as he/she lose) than type II error (no open positions). Therefore, you can define the following correct decisions and mistakes made by the investor, eg during strategy testing of open long positions only:
\begin{itemize}
\item True  Positive (TP) –-- when the investor believes that the market price of the observed asset will increase, and in fact it happens;
\item False Positive (FP)  --– when the investor believes that the market price will increase and in reality the price drops;
\item True Negative (TN) --– when the investor believes that the observed price will drop and does not open a position, and in fact he is right;
\item False Negative (FN) --– when the investor believes that the observed price will drop and does not open a position, while in reality, the price rose and a chance for another profit was lost.
\end{itemize}
A similar analysis can be performed for the cases of other strategy that opens only short positions - with reversed conclusions.\\
Taking into account the above definitions, Matthews has already developed several years ago a formula, in which the matrix of all the events and decisions is summed up using  MCC indicator:
\begin{equation}
MCC = \frac{TP \cdot TN - FP \cdot FN}{(TP+FP)(TP+FN)(TN+FP)(TN+FN)}
\end{equation}
In this index all the possible successes and failures as well as their frequency are taken into account simultaneously. In addition, this index is a number in the range $[-1, 1]$ giving a view of the inverse of the total predictability ($-1$), full of randomness ($0$) or full predictability of events ($1$).\\
Other quality prediction indicators, described below, such as Sharpe ratio or Calmar ratio have obvious drawbacks and thus many practitioners of investment process use multi-criteria evaluation method to find the effectiveness of the strategy. Such sets of indicators are referred in a popular investment platform Metatrader \cite{wang} and include, among others, factors such as average profit, the average loss, the number of consecutive successes and failures, the largest drawdown,  the number of successes to the number of failures, etc. Profit for long positions is calculated as difference between price of buy and price of sell including spread, similarly for short positions this is difference between sell and buy price with a negative sign. The loss on the position is when the profit is less than zero.\\
The authors of this publication referring to the market practice consider Calmar \cite{sinclare} as a very good synthetic indicator, which unfortunately also has an apparent drawback - with very long investment horizon it overstates investors optimistic who starts using a particular strategy.\\
The authors believe that the MCC indicator does not have this disadvantage. Regardless of the size of the time window in which a certain strategy would be considered and a MCC indicator would be applied there, it should give similar value (for a given strategy), as long as the strategy takes into account all the possible trends. The strategy considered here meets this challenge. Figure \ref{rys1} shows a fragment of the time series for EURUSD 1h showing both the downward trend, rising trend and fragments, which can be considered as cycles or horizontal trend. EURUSD is most popular currency pairs and has smallest spread value. One hour interval matches the frequency of the transaction and this pair has sufficient volatility at said interval to consider it for the algorithmic trading purposes. 
\begin{figure}[ht]
\centering
\includegraphics[width = 0.6\textwidth]{pictures/researched_data.png}
\caption{A fragment of the time series EURUSD 1h on which strategy was tested}
\label{rys1}
\end{figure}
\FloatBarrier

% % % % % % % % % % % % % % % % % % % % % % % % % %
\section{Research of the simple strategy based on pivot points}
Pivot points (further referred to as PP) are certain contractual levels considered in the candle (or in few further candles), calculated on the basis of data from the past. According to popular sources \cite{person} \cite{myers} there are many ways (algorithms) to calculate Pivot levels. The authors treat these formulas as suggestions (treated as an inspiration rather than as dogmas). It can be easily demonstrated, that strategies based on the idea of pivot points in the original form have low effectiveness. This low efficiency is demonstrated in the article. At the same time, the authors of this study demonstrate higher effectiveness of the strategies based on more complex investment algorithms coming from the same concept of Pivot levels.\\

The first strategy that the authors consider in this paper is a strategy, as simple as possible, based directly on the pivot points formulas that are suggested in many sources  \cite{person}\cite{myers}\cite{tian}. The second strategy is an extension of the first one, with several parameters, that are optimized in machine learning, added.\\

In the first approach, the PP is treated as a simple, consistent and repeatable operation. After the end of the next candle, pivot points \cite{person} and all derivative levels are calculated using traditional (optionally modified) formulas, and then immediately, depending on the situation, long or short positions are opened. This position is closed at the end of the candle in which it was opened.\\

The first simple type of strategy is as follows. \\
Usually there are 4 (rarely 6) defined pivot points levels \cite{person} \cite{myers}. The top two are called resistance levels (R1, R2), bottom two - support levels (S1, S2). There are different formulas, but the most popular \cite{person} are:
\begin{equation}
P= \frac{(H+L+C)}{3}
\end{equation}
\begin{equation}
R1=2 \cdot P-L
\end{equation}
\begin{equation}
S1=2 \cdot P-H
\end{equation}
\begin{equation}
R2=P+(R1-S1)
\end{equation}
\begin{equation}
S2=P-(R1-S1)
\end{equation}
For the portion of the surveyed data, curves described using aforementioned formulas may look like the ones in the Figure \ref{rys2}.
\begin{figure}[ht]
\centering
\includegraphics[width = 0.6\textwidth]{pictures/samplePP2.png}
\caption{Relative position of the PP levels and levels of resistance and support}
\label{rys2}
\end{figure}
\FloatBarrier
The graph shows how the level of PP oscillates between the respective levels of support and resistance and how periodically intersects them.\\

The strategy relies on stating four different hypotheses about the further course prices, depending on where the closing price is on the ,,scale'' levels calculated at the close of the candle. This is authored strategy, although not very original. In the literature one can find a lot of suggestions to behave that way \cite{murphy}\cite{krutsinger}\cite{elder}. Of course, there are also other possible hypotheses and strategies based on them \cite{wilinskir}.\\

Therefore, it is believed, that if the price upward or downward deviation on the opening of the following candle is considered very high (above R2 or below S2), one has to deal with the trend (increasing or declining) and should open position to the ,,outside''. If the price is located between levels R1 and R2, or S1 and S2, it should be presumed that the trend is horizontal and one has to open position to  the inside. If the price is quite neutral, between S1 and R1, no action is necessary.\\

Presented classification allows to define four decision situations --- four sub strategies, hereafter referred to as A ... D.
\begin{itemize}
\item A - Sub strategy triggered when current price deviates upward above the R2 level. Then investor (or machine) will open long position. Position will be closed at the close of the current candle --- after one candle interval. Similarly in next sub strategies.
\item B - Sub strategy triggered when current price is above R1 level and at the same time above R2 level. Then investor will open short position.
\item C - Sub strategy triggered when current price is above S2 level and at the same time below S1 level. Then investor will open long position.
\item D - Sub strategy triggered when current price is below S2 level. Then investor will open short position.
\end{itemize}
It is worth noting that due to the uncertainty, when the price is close to the PP, no position will be opened if the price is inside the band between S1 and R1 level. This simplest strategy gives the following results for the considered data set. \\

For sub strategy A, Figure \ref{rys3} presents how cumulative profit has changed during tested candles. 
\begin{figure}[ht]
\centering
\includegraphics[width = 0.5\textwidth]{pictures/PivotPointsAp.png}
\caption{Cumulative profit for simple sub strategy A}
\label{rys3}
\end{figure}
\FloatBarrier

For this strategy confusion matrix is is presented in Table \ref{tab1}
\begin{table}[ht]
\centering
\caption{Confusion matrix for simple sub strategy A}
\label{tab1}
\begin{tabular}{|l|l|l|}\hline
&	Actual = profit	& Actual = loss\\ \hline
Prediction = profit & $5$	& $6$ \\ \hline
Prediction = loss &	$2409$ &	$3579$ \\ \hline
\end{tabular}
\end{table}
\FloatBarrier
\noindent and Matthews correlation coefficient is $MCC=0.0046$.\\
\noindent The final results for this simple strategy A:
\begin{itemize}
\item Profit: $0.0069$
\item Calmar: $2.432$
\end{itemize}
Analyzing the course chart it can be seen that there are: a small number of opened positions, balance in the number of wins and losses, and the final profit. \\

Subsequently, studies were carried out for the next of these four strategies - simple sub strategy B. Confusion matrix - as presented below - was obtained by an even smaller number of events (only 5). For this strategy confusion matrix is as presented in Table \ref{tab2}
\begin{table}[ht]
\centering
\caption{Confusion matrix for simple sub strategy B}
\label{tab2}
\begin{tabular}{|l|l|l|}\hline
&	Actual = profit	& Actual = loss\\ \hline
Prediction = profit & $4$	& $1$ \\ \hline
Prediction = loss &	$2397$ &	$3597$ \\ \hline
\end{tabular}
\end{table}
\FloatBarrier
\noindent and Matthews correlation coefficient is $MCC=0.0236$.\\
Cumulative return curve is presented in the Figure \ref{rys4}.
\begin{figure}[ht]
\centering
\includegraphics[width = 0.5\textwidth]{pictures/PivotPointsBp.png}
\caption{Cumulative profit for simple sub strategy B}
\label{rys4}
\end{figure}
\FloatBarrier
\noindent Final result for sub strategy B:
\begin{itemize}
\item Profit: $0.0035$
\item Calmar: $7.80$
\end{itemize}
The value of Calmar ratio is impressive, but given that the number of items is small it is rather coincidence and can be treated just as an interesting fact.\\

Next studies were carried out for a simple sub strategy C which gave confusion matrix as in Table \ref{tab3}
\begin{table}[ht]
\centering
\caption{Confusion matrix for simple sub strategy C}
\label{tab3}
\begin{tabular}{|l|l|l|}\hline
&	Actual = profit	& Actual = loss\\ \hline
Prediction = profit & $9$	& $1$ \\ \hline
Prediction = loss &	$2405$ &	$3584$ \\ \hline
\end{tabular}
\end{table}
\FloatBarrier
\noindent and Matthews correlation coefficient is $MCC=0.0415$.\\
Cumulative return curve is presented in the Figure \ref{rys5}.
\begin{figure}[ht]
\centering
\includegraphics[width = 0.5\textwidth]{pictures/PivotPointsCp.png}
\caption{Cumulative profit for simple sub strategy C}
\label{rys5}
\end{figure}
\FloatBarrier
\noindent Final result for sub strategy C:
\begin{itemize}
\item Profit: $0.0022$
\item Calmar: $8.539$
\end{itemize}

Last tested strategy was sub strategy D. Obtained confusion matrix is presented in Table \ref{tab4}
\begin{table}[ht]
\centering
\caption{Confusion matrix for simple sub strategy D}
\label{tab4}
\begin{tabular}{|l|l|l|}\hline
&	Actual = profit	& Actual = loss\\ \hline
Prediction = profit & $1$	& $13$ \\ \hline
Prediction = loss &	$2400$ &	$3585$ \\ \hline
\end{tabular}
\end{table}
\FloatBarrier
\noindent and Matthews correlation coefficient is $MCC=-0.0325$.\\
Cumulative return curve is presented in the Figure \ref{rys6}.
\begin{figure}[ht]
\centering
\includegraphics[width = 0.5\textwidth]{pictures/PivotPointsDp.png}
\caption{Cumulative profit for simple sub strategy D}
\label{rys6}
\end{figure}
\FloatBarrier
\noindent Final result for sub strategy D:
\begin{itemize}
\item Profit: $-0.0081$
\item Calmar: $-1.00$
\end{itemize}

This is the only of the four strategies ending with loss, also with a small number of openings and not reliable end result.\\

Much more interesting conclusion may be a summary of all four sub strategies. After all, they can be run simultaneously, under the conditions provided in the PP. After adding all the results accumulated profit curve can be presented as in Figure \ref{rys7}. Obtained confusion matrix is presented in Table \ref{tab5}
\begin{table}[ht]
\centering
\caption{Confusion matrix for summary of all simple sub strategies}
\label{tab5}
\begin{tabular}{|l|l|l|}\hline
&	Actual = profit	& Actual = loss\\ \hline
Prediction = profit & $19$	& $21$ \\ \hline
Prediction = loss &	$9611$ &	$14345$ \\ \hline
\end{tabular}
\end{table}
\FloatBarrier
\noindent and Matthews correlation coefficient is $MCC=0.0061$.
\begin{figure}[ht]
\centering
\includegraphics[width = 0.5\textwidth]{pictures/PivotPointsSp.png}
\caption{Cumulative profit for simple strategy S}
\label{rys7}
\end{figure}
\FloatBarrier
\noindent Final result:
\begin{itemize}
\item Profit: $0.0045$
\item Calmar: $1.07$
\end{itemize}

In this ,,generalized'' strategy $40$ positions have been opened. However, the result is not very exciting. This confirms authors suppositions, that this simple strategy, despite incentives from many practitioners, is inefficient and fraught with huge risk.\\

Sub strategy A gave a positive final result with a profit higher than the profit from all four sub strategies. Even better results are obtained by using sub strategy B, which allows to achieve the criterion of $MCC = 0.236$.
The only clearly losing sub strategy is D - opening short positions in the conditions of the hypothesis of a downward trend (the observed exchange rate i.e. in  Figure 1 shows that these failures cannot be explained by such continual increase in the exchange rate).\\
Such disproportions in the results of individual sub strategies can suggest ideas for next strategies, i.e. based on combinatorial combining good sub strategies and excluding bad. They will not be considered here.  More complex strategies will be considered as an alternative for discussed low-frequency events.\\
The Table \ref{tab6} summarizes the results obtained in the studies. In addition, it presents the  number of open positions and a precision, which describes percentage of items that have been opened correctly (returned profit) for all open positions:
\begin{equation}
Precision = \frac{TP}{TP+FP} = \frac{TP}{\text{Positive situations}}
\end{equation}
\begin{table}[ht]
\centering
\caption{Summary results for simple sub strategies}
\label{tab6}
\begin{tabular}{|l|l|l|l|l|l|}\hline
&	Final profit &	Calmar	& Number of open positions	& Precision & 	MCC \\ \hline
A&	$0.0069$ &	$2.43$ &	$11$ &	$0.455$ &	$0.0046$ \\ \hline
B&	$0.0035$ &	$7.80$ &	$5$ &	$0.800$ &	$0.0236$ \\ \hline
C&	$0.0022$ &	$8.54$ &	$10$ &	$0.900$ &	$0.0415$ \\ \hline
D&	$-0.0081$ &	$-1.00$ &	$14$ &	$0.071$ &	$-0.0325$ \\ \hline
S&	$0.0045$ &	$1.07$ &	$40$ &	$0.475$ &	$0.0061$ \\ \hline
\end{tabular}
\end{table}
\FloatBarrier
As can be seen the precision for sub strategy B and C --- in which the positions are opened inside --- is high. It raises the concept of a different strategy, in which i.e. only B and C would be used with A and D excluded. However, the authors decided to test other concepts.

% % % % % % % % % % % % % % % % % % % % % % % % % %
\section{Tests of the authorial strategies based on the concept of pivot points}
The additional parameters are a completely authorial contribution to the article and have not appeared in any other publication as the same set. The parameters were obtained as a result of trials and experiments carried out in the data space. The strategies are rather signs of inventiveness than logic. Nevertheless, their usage to open and close positions is absolutely rational and highly logical. \\

Due to insignificant number of openings using the simple variants, the authors introduced additional parameters to each of the sub strategies.\\

\noindent There are five parameters:
\begin{itemize}
\item p1 –-- the number of steps forward for the position closing,
\item p2 --– the number of steps backward for calculating average volume, 
\item p3 –-- the number of steps backward in the cumulative profit curve for the position opening decision,
\item p4 --– the minimum drawdown determining  suspension of the position opening,
\item p5 --– the minimum volume determining a position opening.
\end{itemize}

Values of the parameters may vary depending on the market condition in order to maximize specific criterions (e.g. the Calmar ratio, the MCC) in a pre-defined time windows only.  It is suggested to use machine learning as a basic adaptive method of the parameters optimization. In the first step of the research a possibility of creating a strategy that uses the same values of the parameters during the entire time horizon and which results in a major rise of the profit, compared to the simple variants of the strategies based on the concept of pivot points is eximined. It is necessary to define a conditions for opening and closing positions using parameters: p1,p2,p3,p4,p5.
Each of the sub strategies has its own set of values of the parameters (p1 ... p5), which were optimized separately. For this reason the parameters below were named p1A, p1B etc.\\

\noindent \textbf{The position opening conditions}\\

The position opening condition of the A sub-strategy:
\begin{verbatim}
If	price>R2 and 
    (AverageVolume(p2A) - CurrentVolume)>p5A and 
    (CumulativeProfit(p1A+p3A) – CumulativeProfit(p1A))<p4A
Then 	Open Long
\end{verbatim}

\noindent where:
\begin{itemize}
\item price –-- the current EUR/USD exchange rate,
\item Average Volume(p2A) –-- the mean value of the last p2A volume values,
\item CumulativeProfit(p1A) --– the cumulative profit from before p1A candles,
\item CurrentVolume --– the current value of the volume,
\item CumulativeProfit(p1A+p3A) --– the cumulative profit from before (p1A+p3A) candles.
\end{itemize}

Making use of a similar notation it is possible to describe the position opening conditions of the remaining sub strategies.\\

The position opening condition of the B sub strategy:
\begin{verbatim}
If	price<R2 and 
    price>R1 and
    (AverageVolume(p2B) - CurrentVolume)>p5B and 
    (CumulativeProfit(p1B+p3B) – CumulativeProfit(p1B))<p4B
Then 	Open Short
\end{verbatim}

The position opening condition of the C sub strategy:
\begin{verbatim}
If	price<S1 and 
    price>S2 and
    (AverageVolume(p2C) - CurrentVolume)>p5C and
    (CumulativeProfit(p1C+p3C) – CumulativeProfit(p1C))<p4C
Then 	Open Long
\end{verbatim}

The position opening condition of the D sub strategy:
\begin{verbatim}
If	price<S1 andprice<S2 and  
    (AverageVolume(p2D) - CurrentVolume)>p5D and
    (CumulativeProfit(p1D+p3D) – CumulativeProfit(p1D))<p4D
Then 	Open Short
\end{verbatim}

\noindent \textbf{The position closing conditions}\\

In all of the sub strategies the position is closed after the optimal number of candles p1X as follows:
\begin{verbatim}
If	CandleCounter>p1X  
Then 	Close Short/Long
\end{verbatim}
\noindent where:
\begin{itemize}
\item CandleCounter --- the candle counter as from the position opening,
\item p1X --– the number of steps forward for the position closing of the sub-strategy (A, B, C or D).
\end{itemize}
\vspace{1em}
The Table \ref{tab7} shows the optimized values of the parameters of each of the sub strategies.
\begin{table}[ht]
\centering
\caption{Optimized values of the parameters for each of simple sub strategies}
\label{tab7}
\begin{tabular}{|l|l|l|l|l|l|}\hline
Sub-strategy/parameter&	p1&	p2	& p3 &	p4	& p5 \\ \hline
A	& $47$	& $22$	& $165$	& $0.0054$	& $-52$\\ \hline
B	& $178$	& $139$	& $31$	& $0.0016$	& $-246$\\ \hline
C	& $52$	& $23$	& $177$	& $0.0018$	& $-129$\\ \hline
D	& $91$	& $2$	& $76$	& $0.0072$	& $-190$\\ \hline
The sum of the sub strategies	& p1 group & 	p2 group	& p3 group	& p4 group	& p5 group\\ \hline
\end{tabular}
\end{table}
\FloatBarrier

The confusion matrix presenting the results of the A sub strategy simulations looks like in Table \ref{tab8}.
\begin{table}[ht]
\centering
\caption{Matrix for sub strategy A}
\label{tab8}
\begin{tabular}{|l|l|l|}\hline
&	Actual = profit	& Actual = loss\\ \hline
Prediction = profit & $102$	& $57$ \\ \hline
Prediction = loss &	$2677$ &	$2947$ \\ \hline
\end{tabular}
\end{table}
\FloatBarrier

\noindent The Matthews correlation coefficient is $0.0054.$\\
The results of the sub strategy presented in a conventional manner –-- with the cumulative profit curve --– look like in Figure \ref{rys8}.
\begin{figure}[ht]
\centering
\includegraphics[width = 0.5\textwidth]{pictures/PivotPointsA.png}
\caption{Cumulative profit for sub strategy A}
\label{rys8}
\end{figure}
\FloatBarrier
\noindent The final results of the A sub-strategy:
\begin{itemize}
\item Profit: $0.268$
\item The Calmar ratio: $1.703$
\end{itemize}
\vspace{1em}
\noindent Afterward similar tests of the B sub strategy were run.\\

The confusion matrix presenting the results of the B sub strategy simulations is presented in Table \ref{tab9}.
\begin{table}[ht]
\centering
\caption{Matrix for sub strategy B}
\label{tab9}
\begin{tabular}{|l|l|l|}\hline
&	Actual = profit	& Actual = loss\\ \hline
Prediction = profit & $83$	& $48$ \\ \hline
Prediction = loss &	$2602$ &	$3058$ \\ \hline
\end{tabular}
\end{table}
\FloatBarrier
\noindent The Matthews correlation coefficient is $0.052$.\\
The cumulative profit curve for sub strategy  B is presented in Figure \ref{rys9}.
\begin{figure}[ht]
\centering
\includegraphics[width = 0.5\textwidth]{pictures/PivotPointsB.png}
\caption{Cumulative profit for sub strategy B}
\label{rys9}
\end{figure}
\FloatBarrier
The final results of the B sub strategy:
\begin{itemize}
\item Profit: $0.633$
\item The Calmar ratio: $4.271$
\end{itemize}
\vspace{1em}
\noindent Afterward similar tests of the C sub-strategy were run.\\

The confusion matrix presenting the results of the C sub strategy simulations looks like in Table \ref{tab10}.
\begin{table}[ht]
\centering
\caption{Matrix for sub strategy C}
\label{tab10}
\begin{tabular}{|l|l|l|}\hline
&	Actual = profit	& Actual = loss\\ \hline
Prediction = profit & $102$	& $53$ \\ \hline
Prediction = loss &	$2743$ &	$2873$ \\ \hline
\end{tabular}
\end{table}
\FloatBarrier
\noindent The Matthews correlation coefficient is $0.055$.\\
The cumulative profit curve looks like in Figure \ref{rys10}.
\begin{figure}[ht]
\centering
\includegraphics[width = 0.5\textwidth]{pictures/PivotPointsC.png}
\caption{Cumulative profit for sub strategy C}
\label{rys10}
\end{figure}
\FloatBarrier
The final results of the C sub strategy:
\begin{itemize}
\item Profit: $0.478$
\item The Calmar ratio: $5.302$
\end{itemize}
\vspace{1em}
\noindent Afterward similar tests of the D sub-strategy were run.\\

The confusion matrix presenting the results of the D sub strategy simulations is presented in Table \ref{tab11}.
\begin{table}[ht]
\centering
\caption{Matrix for sub strategy D}
\label{tab11}
\begin{tabular}{|l|l|l|}\hline
&	Actual = profit	& Actual = loss\\ \hline
Prediction = profit & $79$	& $42$ \\ \hline
Prediction = loss &	$2649$ &	$3063$ \\ \hline
\end{tabular}
\end{table}
\FloatBarrier
\noindent The Matthews correlation coefficient is $0.054$.\\
The cumulative profit curve for sub strategy D is presented in Figure \ref{rys11}.
\begin{figure}[ht]
\centering
\includegraphics[width = 0.5\textwidth]{pictures/PivotPointsD.png}
\caption{Cumulative profit for sub strategy D}
\label{rys11}
\end{figure}
\FloatBarrier	
The final results of the D sub strategy:
\begin{itemize}
\item Profit: $0.385$
\item The Calmar ratio: $3.129$
\end{itemize}

% % % % % % % % % % % % % % % % % % % % % % % % % %
\section{The summary of the strategies effectiveness with the MCC}
The cumulative profit curve of the summarizing strategy composed of the four sub strategies is presented in Figure \ref{rys12}.
\begin{figure}[ht]
\centering
\includegraphics[width = 0.5\textwidth]{pictures/PivotPointsPodsumowanie.png}
\caption{Cumulative profit for sub strategy S}
\label{rys12}
\end{figure}
\FloatBarrier
The confusion matrix presenting the results of the summarizing strategy is presented in Table \ref{tab12}.
\begin{table}[ht]
\centering
\caption{Confusion matrix for summary of all sub strategies}
\label{tab12}
\begin{tabular}{|l|l|l|}\hline
&	Actual = profit	& Actual = loss\\ \hline
Prediction = profit & $366$	& $200$ \\ \hline
Prediction = loss &	$10671$ &	$11941$ \\ \hline
\end{tabular}
\end{table}
\FloatBarrier

\noindent The Matthews correlation coefficient is $0.054$.\\
The final results of the summarizing strategy:
\begin{itemize}
\item Profit: 1.7644
\item The Calmar ratio: 11.991
\end{itemize}
\vspace{1em}
The Table \ref{tab13} presents a summary of the tests results. The authors show also the number of the opened positions and the precision measure, which  is defined as the ratio of the true positives to both true positives and false positives. 
\begin{table}[ht]
\centering
\caption{Optimized values of the parameters for each sub strategy}
\label{tab13}
\begin{tabular}{|l|l|l|l|l|l|}\hline
&	Final profit &	Calmar	& Number of open positions	& Precision & 	MCC \\ \hline
A	& $0.268$	& $1.703$	& $159$	& $0.642$	& $0.054$\\ \hline
B	& $0.633$	& $4.271$	& $131$	& $0.634$	& $0.052$\\ \hline
C	& $0.478$	& $5.302$	& $155$	& $0.658$	& $0.055$\\ \hline
D	& $0.385$	& $3.129$	& $121$	& $0.653$	& $0.054$\\ \hline
S	& $1.764$	& $11.991$	& $566$	& $0.647$	& $0.054$\\ \hline
\end{tabular}
\end{table}
\FloatBarrier
As demonstrated in the table, the MCC values of all the sub strategies and the summarizing one are almost exact. The equality of the values is caused by the similar precision of the sub strategies. Obtained precision measures are supposed to be very high. It may be compared to a 60 percent chance of winning ,,an asymmetrical coin'' toss. It is important to remember that these results were gathered within the training data set. Though, deducing from the gained experience, the authors consider the finding to be remarkable. Since this manner of usage of the MCC is unique, an approximately five-percent value of the MCC was a completely new occurrence. It should be noted that the Calmar ratio achieved values within a significantly wider range.

% % % % % % % % % % % % % % % % % % % % % % % % % %
\section{Conclusions}

The research of the usefulness of the MCC to evaluate the quality of the strategy does not encourage  to use this indicator. It is clear especially in the last table, that comparable values of MCC values may give different values of Calmar ratio. Generally, however, in confusion matrix lies interesting information especially regarding precision of the strategy. The $TP /( TP + FP )$ ratio resembles the model of asymmetric coins, which  investor  ,,throws''. If the ratio is greater than 50\% than this strategy is promising. The test strategy achieved results far above 60\%. \\

An important result of this work is also paying attention to the low efficiency of the popularized strategies based on the concept of fixed pivot points levels. For authors, it is clear that without the introduction of additional parameters such strategies are useless --- these strategies generate small number of openings and their effectiveness is difficult to statistically prove.

\bibliography{jtacs_tewi}
\bibliographystyle{jtacs}

\end{document}

### 2014-04-06 Article/Article20140124/latex/article_main.tex
latex version 1.0

\documentclass[runningheads,a4paper]{llncs}

\usepackage{amssymb}
\setcounter{tocdepth}{3}
\usepackage{graphicx}
\usepackage{epstopdf}
\usepackage{amsmath}
\usepackage{placeins}

\usepackage{url}
\urldef{\mailsa}\path|{awilinski, abera, mjarlaczynski, pblaszynski}@wi.zut.edu.pl|    
\newcommand{\keywords}[1]{\par\addvspace\baselineskip
\noindent\keywordname\enspace\ignorespaces#1}

\begin{document}

\mainmatter  % start of an individual contribution

% first the title is needed
\title{The investment strategy based on behavior of artificial earthworm for use in algotrading}

% a short form should be given in case it is too long for the running head
\titlerunning{SHORT TITLE}

% the name(s) of the author(s) follow(s) next
%
% NB: Chinese authors should write their first names(s) in front of
% their surnames. This ensures that the names appear correctly in
% the running heads and the author index.
%
\author{Antoni Wilinski
\and Aneta Bera\and Maciej Jarlaczynski\and Piotr Blaszynski}
%
\authorrunning{A. Wilinski et al}
% (feature abused for this document to repeat the title also on left hand pages)

% the affiliations are given next; don't give your e-mail address
% unless you accept that it will be published
\institute{West Pomeranian University of Technology, Faculty of Computer Science,\\
Zolnierska 49, 71210 Szczecin, Poland\\
\mailsa\\
\url{http://wi.zut.edu.pl}}

%
% NB: a more complex sample for affiliations and the mapping to the
% corresponding authors can be found in the file "llncs.dem"
% (search for the string "\mainmatter" where a contribution starts).
% "llncs.dem" accompanies the document class "llncs.cls".
%

\toctitle{The investment strategy based on behavior of artificial earthworm for use in algotrading}
\tocauthor{Antoni Wilinski}
\maketitle

\begin{abstract}
This paper presents an innovative concept of investment strategy derived from the general ideas of artificial intelligence. The strategy has been tested in a number of simulations on historical data and on data outside learning periods. Tests were performed mainly in the selected currency markets, including the primary currency pair EURUSD. Presented approach opens long and short positions alternately during the closing of actual candles. Closing of position is based on recommendation which is deduced from changes in features of time series. The strategy has parameters that vary through time, and are adapted to the market changes. To present the strategy metaphor of an artificial earthworm, that feeds on a time series, was used. The goal was to implement presented strategy for trading platform to achieve the automatic trading effect. Implemented strategy allows to achieve interesting results.
\keywords{investment strategy, machine learning, forecasting, time series, algotrading}
\end{abstract}

\section{Introduction}

Algotrading is rapidly growing new form of trading on financial markets where investor (that makes decisions) is replaced with automaton (computer program) []. Such machine can perform operations (opening and closing positions, placing orders to open such positions that meet certain conditions) directly in an automated brokerage platform environment. It may also be a recommendation system that helps investor with making correct decisions.\\

Such computer applications (bots) require carefully prepared and tested software that most often needs to adapt to the changing situations on the observed markets. Modern trends, in the development of this software, include sophisticated methods of: artificial intelligence, pattern recognition, classification and machine learning. Those methods are interpenetrating and complementary and are also expanded with information based on fundamental analysis, for example, automatically extracted from the Internet[Schwager, Elder, … nasze hindawi].\\

Strategy presented in this paper is an example of a solution that can be used fully automated or with investor’s assistance, who makes the decision manually. To use this software, it is necessary to make sure that there are reasonable premises of achieving the success. These conditions can be achieved through inductive thinking, involving the assumption that multiple validation of decision on data from the past substantiates the correctness of the decision in the future. If a certain set of rules in the strategy used to seek the pattern, leads to the success then these rules are a pattern that is encouraged for repeated use. If repeated use of said pattern results in more successes than failures, then the basic premise to consider the use of the pattern is rational []. Unfortunately, changing market is causing the pattern to become outdated therefore it is necessary to constantly update it. Search in the historical patterns, that could be effective in the data space not used for their determination ( to identify these patterns ), is a major challenge also applied in machine learning which is used in this paper.
The article is organized as follows: at first authors describe an authored strategy based on an entirely innovative, according to the authors, concept of an artificial worm. Subsequently extensive studies of effectiveness of presented strategy in terms of prediction and the aspect of investment are carried out. At the end the conclusions resulting from the study are presented and also cited bibliographic sources are included.

\section{Strategy characteristics}
In presented strategy, a metaphorical procedure is often used to explain heuristic algorithms of artificial intelligence. Said procedure is a reference to an inspiration derived from the nature.\\

Let's consider an artificial worm, which behaves like its natural inspirer. Let this artificial worm have a length of p1 candles (vectors representing the knowledge about events occurring within the contractual part of the time series). Let her movement come down to the successive ,,eating'' one candle and simultaneous ,,discarding'' of one candle --- always having p1 candles. Thus the earthworm moves incrementally at length of time called the period of the candle. I-th candle is  defined as a row of data of values  Oi, Hi, Li, Ci (Open, High, Low and Close). These values represent (in order): the value at the beginning of this period, the maximum value within the period, the minimum and the closing values - at the end of the candle.\\
Let's assume that candle can have color (often in a number of brokerage platforms, this procedure is used). Therefore candles may be red (when the opening of the candle is higher than its closing $Oi>Ci$) and green (when the situation is opposite $Oi <Ci$).\\
Let's also assume --- it is a primary strategy rule - that when an artificial earthworm has a significant advantage of red candles, a short position is opened or continued. When earthworm has the significant advantage of green candles, a long position is opened or continued. Imprecise term ,,significant'' is defined by the use of the second parameter p2 according to the rules:
\begin{equation}
\text{If }  Lr > p1/2 -p2 \text{ then short;}
\end{equation}
opening of short position will be suggested;
\begin{equation}
\text{If }  Lg > p1/2 -p2 \text{ then long;}
\end{equation}
opening of long position will be suggested;
\begin{equation}
\text{If }  Lg < p1/2 -p2 \text{ and } Lr< p1/2-p2 \text{ then none;}
\label{eq:eq3}
\end{equation}
the continuation of state will be suggested (position or no opened position).\\

In the rules above Lr and Lg are the number of candles, respectively ,,red'' and ,,green'' in the worm of p1 length, wherein $p1 = Lr + Lg$.\\
When dominance determined by another parameter p2 is undecided, as in \ref{eq:eq3}, then worm takes the color white and the position will not be opened. When the worm continues to open position, investor does not incur costs. On many platforms, also in literature, symbolic marking of growing candles in white and decreasing in black is used. In this article, due to the occurrence of three values, green-red-white colors are used.\\

Earthworm is therefore supplied with artificial intelligence, which allows the accumulation of knowledge and decision-making:
\begin{itemize}
\item right after closing of the current candle, worm ,,swallows'' the candle and ,,knows'' what color is it;
\item earthworm knows how many candles it is composed with;
\item after absorbing and discarding one candle, worms knows how many candles inside it are red or green and how to determine its status --- red, green or white;
\item knowing its status, earthworm knows how to make a decision about opening or continuing position; the opening of a position (long or short) means the simultaneous closing of the current position (opposite) if such position is opened;
\item earthworm observes cumulative profit curve and if it  notices unacceptable drawdown, then opened position is changed to the opposite;
\item unacceptable drawdown is defined by two other parameters p3 and p4. p3 is the number of previous candles, which sets a reference point in time series, in which the value of the accumulated profit for i-p3 is checked for comparison with the current value of the accumulated profit. p4 is permissible decrease of cumulative profit. If it is exceeded, the SL (Stop Loss --- closes the currently open position) mechanism is activated;
\item worm also observes current course changes during  each next candle and reacts to unprofitable changes. If the current exchange rate causes a loss on the opened positions greater than p5 then the SL mechanism is triggered --- the position is closed and to the end of the candle worm remains in the state without an open position. p5 is therefore the fifth strategy parameter. 
\end{itemize}

These features of the worm's intelligence may be extended, however, for this work they were limited to the foregoing. \\

It is assumed that the time series is Si where $i = 1, 2, ...,$ and each word is a vector $Si = (Oi, Hi, Li, Ci)$ called candle consisting of  four values: Open, High, Low and Close of time between the time t and t +1. I is the final index of word which is the last word in time series that was taken under consideration.\\

Figure \ref{fig:fig1} presents, as described above, earthworm in three successive states. After ,,swallowing'' the next candle worm loses the last one. Candles inside the body of the worm have different colors (presented in the form of solid lines (green) and dashed (red)). 
\begin{figure}[ht]
\centering
\includegraphics[width = 0.4\textwidth]{figures/rys1.eps}
\caption{An example of changes in fixed-length p1 (number of candles) worm, which is traversing the time series.}
\label{fig:fig1}
\end{figure}
\FloatBarrier
Artificial worm executes the following algorithm.\\
The strategy is built on the principle of classical machine learning. Before starting to run the algorithm, on data located outside the environment that investor knows (like on the current market segments --- out-of-sample), it is necessary to ,,teach''  the values of parameters. Since we are dealing with time series,  the natural solution is that the period of learning preceding testing period.  This principle is presented in Figure \ref{fig:fig2}, which shows examples of learning periods and following them testing periods. Data from testing period was not used during learning. This figure shows also that in learning periods, the same data can be used several times by successively moving time frame by the number of steps corresponding to the length of the test window (of course only when  the length of the test period is shorter than the learning).\\
In both periods the same algorithm based on the intelligent behavior of worm is used. Of course, the typical problem of machine learning is the proper selection of the length of learning and testing period [], what will be a subject of further research.\\
\begin{figure}[ht]
\centering
\includegraphics[width = 0.6\textwidth]{figures/rys2.png}
\caption{An example of the arrangement of learning and testing periods of strategy parameters in time series.}
\label{fig:fig2}
\end{figure}
\FloatBarrier

This repeatable algorithm, located in both periods - learning and testing, has the following structure. In learning period the optimal value for five parameters p1, p2, ..., p5 was determined. In test period these designated values of parameters were used to perform the algorithm in the new environment. In each i-th step (candle) of time series following activities were performed:
\begin{itemize}
\item For each $i = p1, p1 +1, p1 +2, ..., I$ and for $j = 1, ..., p1$ check whether the candle located at a distance i-j backwards from the current candle is:\\
green when $Oi-j <Ci-j$, \\
red when $Oi-j> Ci-j$, \\
where p1 --- is the first parameter which is the length of the artificial worm - the number of candles of different colors that make up the ,,body'' of the worm; \\
$Oi-j$ --- is the opening value of (i-j)-th candle;\\ 
$Ci-j$ --- is the closing value of (i-j)-th candle; \\
$I$ --- is the length of the test window, after which it is necessary to change the parameters values to the new, learned in the machine learning phase;\\
\item In each i-th step, the loop j = 1, ..., p 1 is performed in which a number of green Lg, red Lr candles is calculated so the sum of  Lg and Lr is p1 (to avoid the situation when $Oi = Ci$, it is assigned arbitrarily to one of the candles sets, for example green);
\item A condition for the existence of a Rg recommendation to open a long position (or to continue it if it is open) is checked. This condition is arbitrarily adopted (one can of course consider different one): 
\begin{equation}
\text{If } lg> p1/2-p2 \text{ then } Rg=1
\end{equation}

\end{itemize}
If this condition is fulfilled, then depending on the current position status PositionState (where PositionState is a variable which takes values {long, short, 0}) at the opening of the next candle, a position is opened or continued as follows: 
\begin{equation}
\text{If } Rg=1 \text{ and } PositionState =long \text{ then PositionState =long;}
\end{equation}
(costless continuation of opened position);
\begin{equation}
\text{If } Rg=1 \text{ and } PositionState = short \text{ then PositionState=long;}
\end{equation}
\begin{equation}
\text{If } Rg=1 \text{ and } PositionState =0 \text{ then PositionState =long;}
\end{equation}

Similarly check the condition of recommendations Rr to open or continue short position:
\begin{equation}
\text{If } lr>p1/2 – p2 \text {then Rr=1.}
\end{equation}
If this condition is fulfilled, then depending on what the current position status PositionState is, at the opening of the next candle, position is opened or continued as follows: \\
\begin{equation}
\text{If } Rr=1 \text{ and } PositionState =long \text{ then PositionState =short;}
\end{equation}
\begin{equation}
\text{If } Rr==1 \text{ and } PositionState ==short \text{ then PositionState=short;}
\end{equation}
(costless continuing of opened position)
\begin{equation}
\text{If } Rr==1 \text{ and }  PositionState ==0 \text{ then  PositionState =short;}
\end{equation}

In formulas above there is a parameter p2. It is the second parameter of the strategy which is an arbitrarily separated part of the worm, which depending on size causes the direction of investment not to change. Large p2 causes long positions to change into short positions (or vice-versa) rarely. Small value of p2 leads to a higher frequency of these changes. The optimum value of p2 is chosen similarly like p1.
\begin{itemize}
\item 	When opening long position, profit after one candle (this does not mean that position was closed after a single candle) can be calculated as:
\begin{equation}
Zi = Ci +1 - Ci - spread;
\end{equation}
where the spread = 0, when opened long position is continued; \\
and spread = cost, when long position was opened after closing or opening a short position in case when there was no open position;\\
cost is a variable that depends on the particular brokerage platform that was used for testing the strategy; in this case, for the currency pair EURUSD $cost = 0.00016$ was assumed and for the currency pair GBPUSD $cost = 0.00028$.
\item When short position is opened, profit after one candle (it does not mean that position is closed) can be calculated as: 
\begin{equation}
Zi = Ci-Ci +1- spread;
\end{equation}
where the $spread = 0$, when opened short position is continued;\\ 
and $spread = cost$, when short position was opened after closing or opening a long position in case when there was no open position.
\end{itemize}
Figure \ref{fig:fig3} and \ref{fig:fig4} explain the definitions of profit within a single candle in case of opening (or the continuation of long and short position).
\begin{figure}[h!]
\centering
\includegraphics[width = 0.5\textwidth]{figures/rys3.png}
\caption{Method of calculating profit in the (i +1)-th candle, in which long position was opened.}
\label{fig:fig3}
\end{figure}
\FloatBarrier
\begin{figure}[h!]
\centering
\includegraphics[width = 0.5\textwidth]{figures/rys4.png}
\caption{Method of calculating profit in the (i +1)-th candle, in which short position was opened.}
\label{fig:fig4}
\end{figure}
\FloatBarrier

Both figures show symbolically the changes of course, combining simple value at the opening and closing of the candle, ignoring the oscillations inside the candle.
\begin{itemize}
\item If as the result of the test the number of red and green candles in the body of the worm had not obtained any advantage from the color that would recommend to open defined position (worm was white), it is assumed to continue the position, which is open, without any cost of the transaction (with the value of $spread = 0$). If at the beginning of the candle, at the time of checking the recommendation, there was no open position then it can be assumed to continue without any position.
\item Each of the profits calculated above is verified in terms of exceeding the allowable local position drawdown (within one candle). This additional risk management is widely used in automated trading and is called limiting losses --- Stop Loss (SL). In this algorithm, SL was introduced as the fifth parameter of the strategy --- p5.
\end{itemize}

\noindent Presented strategy was tested if:
\begin{itemize}
\item in the case of opening at the beginning of the i-th candle or continuation of a long position presented condition did not occur:\\
\begin{equation}
\text{If } Li-Oi<SL \text{ then } Zi=-SL
\end{equation}
where Li --– the lowest rate value in the i-th candle; SL --– absolute value Stop Loss appearing as p5 parameter;
\item in the case of opening at the beginning of the i-th candle or continuation of a short position presented condition did not occur:
\begin{equation}
\text{If } Oi-Hi<SL \text{ then } Zi=-SL
\end{equation}
where Hi --– the highest rate value in the i-th candle.
\end{itemize}
This way p5 parameter was used for securing in strategy the strong local changes in exchange rate within a single candle.\\
The meaning of p5 parameter to the behavior of the worm and the occurrence of the closing position is explained in Figure \ref{fig:fig5} and Figure \ref{fig:fig6}. This time, unlike in Figures \ref{fig:fig3} and \ref{fig:fig4}, changes in exchange are inside the candle.
\begin{figure}[h!]
\centering
\includegraphics[width = 0.5\textwidth]{figures/rys5.png}
\caption{Method of calculating the profit (here: loss) in the case of necessity to use p5 parameter actuating mechanism SL for long positions.}
\label{fig:fig5}
\end{figure}
\FloatBarrier
\begin{figure}[h!]
\centering
\includegraphics[width = 0.5\textwidth]{figures/rys6.png}
\caption{Method of calculating the profit (here: loss) in the case of necessity to use p5 parameter actuating mechanism SL for long positions.}
\label{fig:fig6}
\end{figure}
\FloatBarrier

\begin{itemize}
\item To determine the current quality of the strategy and risk management summation of current gains/losses (the accumulation) is performed
\begin{equation}
Zci = sum ( Zi ) \text{ from } i = 1 \text{ to the current i value;}
\end{equation}
\item There is a possible local subsidence Zci capital by introducing two additional parameters to manage the risk.\\
p3 --- the number of steps back on the curve of the cumulative profit for the determination of Zci --- p3 for comparison with the present value of Zci;
p4 --- maximum size of the capital subsidence (eg for the currency pair EURUSD measured in pips ) , which if exceeded will trigger the closure position:\\
\begin{equation}
\text{If } ( Zci - p3 - Zi ) <- p4 \text{ and } PositionState \neq 0 \text{ then } PositionState = 0
\end{equation} 
where PositionState --- is the type of open position (long or short) and PositionStates equal 0 means resignations from the opening position to the beginning of the next candle.
\end{itemize}
So, the above-described algorithm uses 5 parameters, as many as 3 of which are devoted to risk management strategy.\\

The complexity of the algorithm is illustrated in Figure \ref{fig:fig7}, which in the form of a decision tree shows the individual steps and decisions made in the iteration on a single candle. This iteration was carried out both in the search for optimal parameters p1, ..., p5 and in the process they use in the testing phase for data not used in learning.\\

The figure shows in a tree further decisions taken at the beginning of the candle and then reactions to any unacceptable change in course. The first examines the state of the position taken over from the closure of the previous candle. The next step is to work out decisions / recommendations as to the direction of the opening from the set {long, short, none}. After opening position is observed return of the open position. It can be positive or negative. If it is positive, it does not take up any additional decisions. If it is negative, it checks if it is not achieved the level of SL. In the case of a negative return of the items, except for testing, SL is not exceeded within a candle tested is also a condition resulting from the use of parameters (p3, p4). Tree is a state of complete items transmitted at the beginning of the next candle.

\begin{figure}[h!]
\centering
\includegraphics[width = \textwidth]{figures/rys7.png}
\caption{Decision tree for the states and decisions in one step (candle) in the learning phase and testing.}
\label{fig:fig7}
\end{figure}
\FloatBarrier

Described algorithm is implemented the in Matlab and using the platform Metatrader MQL4 language. The study was conducted both in the historical data (of course with the principles of machine learning --- testing was carried out using data not used in the learning phase) and a real ,,live'' market. Between the communities, there are also important differences that affect the diversity of simulation results.

\section{The study of strategy}
The study was conducted primarily on the basic EURUSD exchange rate at candlelight 1h. This market was chosen because of its popularity, a huge liquidity and also due to the possession by the authors many experiences in other machine learning strategy for this particular market such as []. These experiments suggested initially, carrying out many tests with a long learning period, about 1000 candles, then 500 candles and testing time windows of 50 to 200 candles. All these attempts have proven to be very effective and led to continuing losses. After months of trying in many markets noted that over long periods of learning, eg the order of 1000 candles strategy variability is very large. Therefore, the tests started with a decidedly shorter periods of learning and testing.\\

Finally, the authors decided to present the results for the two markets - currency pairs EURUSD and GBPUSD sampled at 1h in machine learning aspect ratios matched to the reduced scope of both the learning phase and testing.\\

Table \ref{tab:tab1} summarizes the results for different time periods. The study was conducted at approximately constant number of candles testing period, e.g. if the testing period was 10 candles, is to perform the test algorithm 1300 candles optimal parameters were calculated 130 times. If the testing period was 20 candles are the parameters were changed 65 times, etc., if it was available long test period is not used it.

\begin{table}[h!]
\centering
\caption{The test results of the algorithm for different configurations of learning and testing periods for a couple EUEUSD.}
\label{tab:tab1}
\begin{tabular}{|l|r|r|r|r|} \hline
Learning/Test &	8	 &	10 &		15	 &	20 \\ \hline
40 &		-0.0261 &		-0.0759	 &	-0.1424	 &	-0.0653 \\ \hline
60 &		0.0044 &		-0.0156 &		0.0275 &		0.1647 \\ \hline
80 &		-0.0234 &		0.0989 &		\textbf{0.2401} &		0.0618 \\ \hline
100	 &	0.0290 &		0.0529 &		-0.0104	 &	0.0018 \\ \hline
\end{tabular}
\end{table}
\FloatBarrier

The table shows that the best results were obtained for the ratio of the learning period to test period as 80/15. For this comparison periods was performed to study the market in EURUSD and shown in the Figure \ref{fig:fig8} For the 800-hour candles obtained result 0.2401 (2401 pips). Chart is definitely a growth course with a maximum of 600 pips from falling, which gives a very good, according to the authors, the criterion of Calmar (ratio of profit to capital najwiekzsego slips) about nearly 4.0.\\

\begin{figure}[h!]
\centering
\includegraphics[width = 0.6\textwidth]{figures/rys8.png}
\caption{Mileage accumulation of capital for 800 steps after 15 candles made of uses of the algorithm for the currency pair EURUSD 1h.}
\label{fig:fig8}
\end{figure}
\FloatBarrier

Tests were also made for another great importance and the currency pair GBPUSD 1h. The results are shown in Table \ref{tab:tab2} and in Figure \ref{fig:fig9}.

\begin{table}[h!]
\centering
\caption{The test results of the algorithm for different configurations of learning and testing periods for GBPUSD.}
\label{tab:tab2}
\begin{tabular}{|l|r|r|r|r|} \hline
Learning/Test &	8	 &	10	 &	15 &		20 \\ \hline
40	 &	-0.1706	 &	0.0084 &		-0.1566	 &	-0.0877 \\ \hline
60	 &	-0.1321	 &	-0.1668 &		-0.0070	 &	-0.0644 \\ \hline
80	 &	-0.0175	 &	-0.1375 &		\textbf{0.0870}	 &	-0.0983 \\ \hline
100	 &	-0.0744	 &	-0.0699	 &	-0.0174	 &	-0.1178 \\ \hline
\end{tabular}
\end{table}
\FloatBarrier

\begin{figure}[h!]
\centering
\includegraphics[width = 0.6\textwidth]{figures/rys9.png}
\caption{Mileage accumulation of capital for 400 steps after 15 candles made of uses of the algorithm for the currency pair GBPUSD 1h.}
\label{fig:fig9}
\end{figure}
\FloatBarrier

Results for the currency pair are worse than for EURUSD, however, reaffirm the overall efficiency of the algorithm.\\

It was also decided to test the effectiveness of the algorithm in terms of one candle 1h. The results are shown in Table 3\ref{tab:tab3} and Table \ref{tab:tab4}.

\begin{table}[h!]
\centering
\caption{PerCandle EURUSD.}
\label{tab:tab3}
\begin{tabular}{|l|r|r|r|r|} \hline
Learning/Test &	8	 &	10 &		15	 &	20\\ \hline
40 &		-2.207E-06 &		-6.443E-06 &		-1.219E-05 &		-5.641E-06\\ \hline
60 &		3.695E-07 &		-1.327E-06 &		2.358E-06 &		1.425E-05\\ \hline
80 &		-1.989E-06 &		8.427E-06	 &	\textbf{2.062E-05} &		5.3549E-06\\ \hline
100	 &	2.465E-06 &		4.517E-06 &		-8.981E-07 &		1.571E-07\\ \hline
\end{tabular}
\end{table}
\FloatBarrier

\begin{table}[h!]
\centering
\caption{PerCandle GBPUSD.}
\label{tab:tab4}
\begin{tabular}{|l|r|r|r|r|} \hline
Learning/Test &	8	 & 	10 &		15	 &	20\\ \hline
40	 & -2.949E-05 & 	1.457E-06 & 	-2.768E-05	 & -1.578E-05\\ \hline
60	 & -2.289E-05 & 	-2.912E-05 & 	-1.250E-06 & 	-1.162E-05\\ \hline
80	 & -3.043E-06 & 	-2.408E-05	 & \textbf{1.551E-05} & 	-1.780E-05\\ \hline
100	 & -1.299E-05 & 	-1.228E-05 & 	-3.110E-06	 & -2.143E-05\\ \hline
\end{tabular}
\end{table}
\FloatBarrier

The best results are obtained in both cases (for both markets) for the ratio test to the learning period as 80/15. Result for EURUSD this means achievement of profit over 100 pips per month (approximately 550 hours of trading). This result is in terms of risk at Calmar ratio around 4 should be considered as engaging. Not much is worse than the result obtained for the other test pairs - GBPUSD.\\

In addition, efficacy studies were carried out and optimized for different test periods. To these results can be compared with each other, has been carried out their link, and the results were divided by the length of the test period, expressed by the number of candles. 
Figure \ref{fig:fig10} and Figure \ref{fig:fig11} present the results.

\begin{figure}[h!]
\centering
\includegraphics[width = 0.6\textwidth]{figures/rys10.png}
\caption{EURUSD Results per candle.}
\label{fig:fig10}
\end{figure}
\FloatBarrier

\begin{figure}[h!]
\centering
\includegraphics[width = 0.6\textwidth]{figures/rys11.png}
\caption{GBPUSD Results per candle.}
\label{fig:fig11}
\end{figure}
\FloatBarrier

From these results it can be concluded that the strategy is working with a short shelf life characteristics. The best results are achieved in periods of about 10-20 candles, it is unlike any other strategy presented in [Hindawi] where the best results were achieved for the test periods with a length of 80-100 candles.\\
All the above presented results refer to simulations in Matlab.

\section{Strategy Verification Using Online Trading Platform}
From a conceptual point of view implementing automated trading strategies in Matlab environment is one of proper approaches. Matlab provides a number of features to rapidly prototype such algorithms, for e.g. built-in computation functions and charting tools. What is more, Matlab enables also intuitive operations on vectors and matrices as well as flexible insight into variables values that are produced by the algorithm which greatly facilitates computing process management.\\

However in such approach it is very important to make sure that an algorithm that has been developed in Matlab can be used also regarding to real market conditions, which means a number of rules, validations and limitations, which obviously are not natively implemented in Matlab as it is just an open computing environment.\\

To make sure that those market conditions are met in the algorithm, Matlab script was converted manually to MQL4 expert advisor for trading platform of MetaTrader 4, which platform is commonly used to perform the real market operations.\\

The main differences between the implementation of the artificial earthworm in Matlab and in MetaTrader are listed below:
\begin{itemize}
\item Matlab
\begin{itemize}
\item Calculation of balance and other standard market statistics is implemented manually, including also calculation of profit and loss related with opening / closing position;
\item SL handling is implemented manually, including trailing stop;
\item Lack of built-in market validations for opening / closing position;
\item Calculations are done using only 4 discrete price values for each candle;
\item Implementation approach from technical point of view is a matter of developer decisions;
\end{itemize}
\item MetaTrader
\begin{itemize}
\item Balance and other standard market statistics are calculated automatically, including also a strictly defined API for opening / closing position;
\item SL handling is a built-in feature, including trailing stop;
\item There are built-in market validations for opening / closing position;
\item Prices are changing smoothly for current candle (not only final fixed OHLC values);
\item Implementation approach from technical point of view is a not only a matter of developer decisions, but is also enforced by MetaTrader conventions (phases of initialization, candle execution, deinitialization etc.);
\end{itemize}
\end{itemize}

The elements listed above could cause some variations in the fragmentary as well as the final results of the algorithm execution.\\

In the article, implementation for MetaTrader4 has covered only the testing part of the algorithm, using fixed set of parameters that have been previously computed in Matlab in the learning part of execution for every test period. It is imporntat to note that implementing full algorithm, along with the learning part in MQL4, is obviously possible, however in that in the article the main objective was to confirm that the artificial worm can run on a real market with results similar to those achieved in Matlab.\\

Below are presented balance comparisons in Matlab and MetaTrader environments:
\begin{enumerate}
\item for GBPUSD currency pair using 1h candles values in time period of 2013.01.09 - 2013.12.30 in two different approches:
\begin{itemize}
\item with fixed parameters: p1=27, p2=4, p3=1, p4=-0.0060, p5=0.0060 (Figure \ref{fig:fig10} and Figure \ref{fig:fig11}). Optimal parameters in that case were computed in Matlab for the first testing period and then were used for all testing periods.
\item with dynamic parameters that were changed every testing period, regarding to their values computed in Matlab that were put to MetaTrader (Figure \ref{fig:fig12} and Figure \ref{fig:fig13})
\end{itemize}
In both approaches following assumptions were done:
\begin{itemize}
\item spread was 0.0028, 
\item initial deposit was 50000 EUR,
\item size of the opening positions was 1 lot,
\item each testing period lasted 15 candles.
\end{itemize}
\item for EURUSD currency pair using 1h candles values in time period of 2012.01.20 - 2013.01.01 in two different approches:
\begin{itemize}
\item with fixed parameters: p1=34, p2=4, p3=3, p4=-0.0060, p5=0.0060 (Figure \ref{fig:fig14} and Figure \ref{fig:fig15}) Optimal parameters in that case were computed in Matlab for the first testing period and then were used for all testing periods.
\item with dynamic parameters that were changed every testing period, regarding to their values computed in Matlab that were put to MetaTrader (Figure \ref{fig:fig16} and Figure \ref{fig:fig17})
\end{itemize}
In both approaches following assumptions were done:
\begin{itemize}
\item spread was 0.0016, 
\item initial deposit was 10000 EUR,
\item size of the opening positions was 1 lot,
\item each testing period lasted 15 candles.
\end{itemize}
\end{enumerate}

Results of the algorithm execution in both environments for both currency pairs are presented in Table \ref{tab:tab5}.
\begin{table}[h!]
\centering
\caption{Results of the algorithm execution in both environments for both currency pairs and various parameters values.}
\label{tab:tab5}
\begin{tabular}{|p{0.19\textwidth}|p{0.19\textwidth}|p{0.19\textwidth}|p{0.19\textwidth}|p{0.19\textwidth}|} \hline
 &  Total net profit in MetaTrader [EUR]	 &  Total net profit in Matlab 
[EUR]	 &  Difference [EUR]	 &  Difference [\%]\\ \hline
\multicolumn{5}{|c|}{GBPUSD in time period 2013.01.09 - 2013.12.30}\\ \hline
Fixed p1-p5	 & -8 823.76 & 	-7 987.00 & 	836.76 & 	10.48\\
Dynamic p1-p5	 & 6 057.82	 & 5 555.00	 & 502.82 & 	9.05\\ \hline
\multicolumn{5}{|c|}{EURUSD in time period 2012.01.20 - 2013.01.01}\\ \hline
Fixed p1-p5	 & 2 305,18 & 	2 695,00	 & 389,82	 & 14,46\\
Dynamic p1-p5 & 	13 669,40 & 	17 260,00 & 	3590,60	 & 20,80\\ \hline
\end{tabular}
\end{table}
\FloatBarrier

\begin{figure}[h!]
\centering
\includegraphics[width = 0.6\textwidth]{figures/rys12.png}
\caption{Balance (relative value) in Matlab for GBPUSD [1h] in period 2013.01.09 - 2013.12.30 with fixed parameters p1-p5.}
\label{fig:fig12}
\end{figure}
\FloatBarrier
\begin{figure}[h!]
\centering
\includegraphics[width = 0.6\textwidth]{figures/rys13.png}
\caption{Balance (absolute value) in MetaTrader for GBPUSD [1h] in period 2013.01.09 - 2013.12.30 with fixed parameters p1-p5.}
\label{fig:fig13}
\end{figure}
\FloatBarrier

When following charts are respectively compared:
\begin{itemize}
\item Figure \ref{fig:fig12} with Figure \ref{fig:fig13},
\item Figure \ref{fig:fig14} with Figure \ref{fig:fig15},
\item Figure \ref{fig:fig16} with Figure \ref{fig:fig17},
\item Figure \ref{fig:fig18} with Figure \ref{fig:fig19}.
\end{itemize}

It is important to note that every first chart from each pair above was done in Matlab and every second chart was done in MetaTrader. In Matlab chart context, every point of abscissa axis represents testing period, while on ordinate axis there is a result of testing period (relative value), so that it can be assumed that chart was done in time domain. On the other hand, every abscissa on MetaTrader chart represents each opening of position, which means that chart is not linear related with time (however in cases presented in the article it is really similar to time domain), so that chart begins with first position opening and it is denoised in comparison to Matlab chart as every line are determined by opening and closing position, no matter how long this position has lasted. Despite those differences, corellation between Matlab and MetaTrader charts for the artificial worm algorithm executions is indisputable.

\begin{figure}[h!]
\centering
\includegraphics[width = 0.6\textwidth]{figures/rys14.png}
\caption{Balance (relative value) in Matlab for GBPUSD [1h] in period 2013.01.09 - 2013.12.30 with dynamic p1-p5.}
\label{fig:fig14}
\end{figure}
\FloatBarrier
\begin{figure}[h!]
\centering
\includegraphics[width = 0.6\textwidth]{figures/rys15.png}
\caption{Balance (absolute value) in MetaTrader for GBPUSD [1h] in period 2013.01.09 - 2013.12.30 with dynamic p1-p5.}
\label{fig:fig15}
\end{figure}
\FloatBarrier

Differences in results for the algorithm for Matlab and MetaTrader presented in Table \ref{tab:tab2}. by level of 9-21\% are significant, but it is important to note they do not contest convergence in the algorithm execution in both environments. It is possible to do more detailed research on differences for balance accumulation for particular positions to align the algorithm execution. However for the article purposes conversion of scripts that has been done is sufficient and gives solid base to admit that the algorithm is applicable for market regarding its conceptual assumptions.

\begin{figure}[h!]
\centering
\includegraphics[width = 0.6\textwidth]{figures/rys16.png}
\caption{Balance (relative value) in Matlab for EURUSD [1h] in period 2012.01.20 - 2013.01.01 with fixed p1-p5.}
\label{fig:fig16}
\end{figure}
\FloatBarrier
\begin{figure}[h!]
\centering
\includegraphics[width = 0.6\textwidth]{figures/rys17.png}
\caption{Balance (absolute values) in MetaTrader for EURUSD [1h] in period 2012.01.20 - 2013.01.01 with fixed p1-p5.}
\label{fig:fig17}
\end{figure}
\FloatBarrier

\begin{figure}[h!]
\centering
\includegraphics[width = 0.6\textwidth]{figures/rys18.png}
\caption{Balance (relative values) in Matlab for EURUSD [1h] in period 2012.01.20 - 2013.01.01 with dynamic p1-p5.}
\label{fig:fig18}
\end{figure}
\FloatBarrier
\begin{figure}[h!]
\centering
\includegraphics[width = 0.6\textwidth]{figures/rys19.png}
\caption{19 Balance (absolute values) in MetaTrader for EURUSD [1h] in period 2012.01.20 - 2013.01.01 with dynamic p1-p5.}
\label{fig:fig19}
\end{figure}
\FloatBarrier

\section{Conclusions}

Presented in the paper the concept of an innovative investment strategy gave satisfactory results for a certain pair as the result of periods of machine learning. For example, in the studied data for two key market currency pairs sampled every hour , the best value is 80 hours of teaching and 15 hours of testing. One can assume that this relationship may change in a different environment (for other markets, for other periods) by becoming a sort of next parameter that optimal values should be sought. It should be emphasized that the study was conducted on data not used in the learning phase and for the basic principle of machine learning achieved results that would have satisfied many a practice. It should also be noted that outside research conducted in environment completely specified (for constant unchanging data stored in Matlab ) was also performed simulations in terms of actual brokerage platform. The results obtained in both environments are similar in the sense of direction changes and logic behavior caused by the user received by the algorithm implemented in the Matlab and Metatrader. Differences explained in this work .
The direction of further research will test the hypothesis that the variability periods to test the learner can improve the quality of prediction. This hypothesis seems to be interesting against the background of previous experiences and results, eg for different studied strategies, including [ Hindawi ] obtained surprisingly different optimal length of periods of learning and testing.

\begin{thebibliography}{4}
%
%\bibitem{jour} Smith, T.F., Waterman, M.S.: Identification of Common Molecular
%Subsequences. J. Mol. Biol. 147, 195--197 (1981)
%
%\bibitem{lncschap} May, P., Ehrlich, H.C., Steinke, T.: ZIB Structure Prediction Pipeline:
%Composing a Complex Biological Workflow through Web Services. In: Nagel,
%W.E., Walter, W.V., Lehner, W. (eds.) Euro-Par 2006. LNCS, vol. 4128,
%pp. 1148--1158. Springer, Heidelberg (2006)
%
%\bibitem{book} Foster, I., Kesselman, C.: The Grid: Blueprint for a New Computing
%Infrastructure. Morgan Kaufmann, San Francisco (1999)
%
%\bibitem{proceeding1} Czajkowski, K., Fitzgerald, S., Foster, I., Kesselman, C.: Grid
%Information Services for Distributed Resource Sharing. In: 10th IEEE
%International Symposium on High Performance Distributed Computing, pp.
%181--184. IEEE Press, New York (2001)
%
%\bibitem{proceeding2} Foster, I., Kesselman, C., Nick, J., Tuecke, S.: The Physiology of the
%Grid: an Open Grid Services Architecture for Distributed Systems
%Integration. Technical report, Global Grid Forum (2002)
%
%\bibitem{url} National Center for Biotechnology Information, \url{http://www.ncbi.nlm.nih.gov}

\end{thebibliography}

\end{document}

### 2014-04-06 Matlabs/Indicators/PB/ADX/PSO/Adx10fun.m
ADX - some changes

@@ -99,7 +99,7 @@ end
 lastPosState=posState;
 lastOpenPrice= openPrice;
 
-zysk = sumz(kon)%+zz(kon);
+zysk = sumz(kon);%+zz(kon);
 
 Calmar = obliczCalmara(sumz);
 

### 2014-04-06 Matlabs/Indicators/PB/ADX/PSO/startAdx.m

@@ -42,22 +42,20 @@ end
 % PSO
 [ swarm, iterNum, best_l_op,best_zysk, best_calmar, lastPosLearnState, lastOpenPrice] = PSO(opcje,C,pocz,kon,spread, firstPosLearnState, lastOpenPrice);
 bestParticles = getBestQuarterParticles(swarm);
-paropt = swarm.best_position;
 ldopt = best_l_op;
 zyskU = best_zysk;
 calmarU = best_calmar;
 
-%[ zyskU, calmarU, paropt, sumrec, ldopt] = Adx10opt( C, spread, pocz, kon, P1, P2, P3, P4);
-
-
 %testowanie
 for iParticle = 1:length(bestParticles)
+    paropt = bestParticles(iParticle).best_position;
+
     [ zyskT, CalmarT, sumzT, LongShortT, lastPosState, lastOpenPriceTest] = Adx10fun( C, spread, poczt, kont, paropt(1), paropt(2), paropt(3), paropt(4), paropt(5), firstPosState, lastOpenPriceTest );%, paropt(6), paropt(7));
     
     name = ['EURUSD4_bySum_' num2str(kk) '_particle_' num2str(iParticle)];
-    fileID = fopen([name '.txt'],'w');
-    fprintf(fileID, 'PoczU\t DataPocz\t KonU\t DataKon\t KonT\t DataKonT\t ZsykU\t CalmarU\t P1\t P2\t P3\t P4\t P5\t Long\t Short\t ZyskT\n');% fprintf(fileID, 'PoczU\t KonU\t KonT\t ZsykU\t CalmarU\t P1\t P2\t P3\t P4\t Long\t Short\t ZyskT\n');
-    fprintf(fileID, '%d\t %s\t %d\t %s\t %d\t %s\t %.4f\t %.4f\t %d\t %d\t %d\t %.4f\t %.4f\t %d\t %d\t %.4f\n\n', ...
+    fileID = fopen([name '.txt'], 'a');
+    %fprintf(fileID, 'PoczU\t DataPocz\t KonU\t DataKon\t KonT\t DataKonT\t ZsykU\t CalmarU\t P1\t P2\t P3\t P4\t P5\t Long\t Short\t ZyskT\n');% fprintf(fileID, 'PoczU\t KonU\t KonT\t ZsykU\t CalmarU\t P1\t P2\t P3\t P4\t Long\t Short\t ZyskT\n');
[…]

### 2014-04-06 Matlabs/Indicators/PB/ADX/PSO/start_opt.m

@@ -13,9 +13,9 @@ lastPosState = 0;
 lastPosLearnState = 0;
 lastOpenPrice=0;
 lastOpenPriceTest=0;
-for kk=[1:5]
+for kk=[1:51]
 %for kk=[1:26]
-    [returnTest, lastPosState, lastPosLearnState, lastOpenPrice, lastOpenPriceTest] = startAdx( C, Daty, kk, lastPosState, lastPosLearnState, lastOpenPrice, lastOpenPriceTest);
+    [returnTest, lastPosState, lastPosLearnState, lastOpenPrice, lastOpenPriceTest]     = startAdx( C, Daty, kk, lastPosState, lastPosLearnState, lastOpenPrice, lastOpenPriceTest);
     returns(kk)= returnTest;
     returnSum(kk) = sum(returns(1:kk));
 end

### 2014-04-06 Matlabs/Indicators/PB/ADX/PSO/wyniki/check.m

@@ -1,0 +1,11 @@
+fid = fopen('wyniki_Sum_particle8.txt');
+out2=textscan(fid, '%d%s%d%s%d%s%f%f%d%d%d%f%f%d%d%f\n', 'delimiter', ';');
+fclose(fid);
+out2{1,16};
+dataLength = length(out2{1,16});
+sumReturns = zeros(1, dataLength );
+sumReturns(1) = out2{1,16}(1);
+for i=2:dataLength 
+    sumReturns(i) = sumReturns(i-1) + out2{1,16}(i);
+end
+plot(sumReturns);

### 2014-04-06 Matlabs/Indicators/PB/ADX/PSO/zlacz_wyniki.m

@@ -1,16 +1,19 @@
     
-fileID = fopen('wyniki4_Sum.txt','w');
 
-for i = 1:51
-    tmpF = fopen(['EURUSD4_bySum_' num2str(i) '.txt']);
-    D = textscan(tmpF,'%s','delimiter','\n');
-    A = D{1};
-    if i==1
-        fprintf(fileID,'%s\n%s\n',A{1}, A{2});
-    else
-        fprintf(fileID,'%s\n',A{2});
+for iParticle = 1:20
+	fileID = fopen(['wyniki_Sum_particle' num2str(iParticle) '.txt'], 'w');
+	for i = 1:51%    name = ['EURUSD4_bySum_' num2str(kk) '_particle_' num2str(iParticle)];
+		tmpF = fopen(['EURUSD4_bySum_' num2str(i) '_particle_' num2str(iParticle) '.txt']);
+		D = textscan(tmpF,'%s','delimiter','\n');
+		A = D{1};
+% 		if i==1
+% 			fprintf(fileID,'%s\n%s\n',A{1}, A{2});
+% 		else
+% 			fprintf(fileID,'%s\n',A{2});
+% 		end
+        fprintf(fileID,'%s\n',A{1});
+		fclose(tmpF);
     end
-    fclose(tmpF);
+    fclose(fileID);
 end
 
-fclose(fileID);

### 2014-04-06 Article/Article20140406Granada/LatexArt/article_main.tex

--- 2014-04-06 Article/Article20140124/latex/article_main.tex
@@
 Modern trends, in the development of this software, include sophisticated methods of: artificial intelligence, pattern recognition, classification and machine learning.
-Those methods are interpenetrating and complementary and are also expanded with information based on fundamental analysis, for example, automatically extracted from the Internet[Schwager, Elder, … nasze hindawi].\\
+Those methods are interpenetrating and complementary and are also expanded with information based on fundamental analysis, for example, automatically extracted from the Internet \cite{elder} [Schwager, Elder, … nasze hindawi].\\
 
@@
 If a certain set of rules in the strategy used to seek the pattern, leads to the success then these rules are a pattern that is encouraged for repeated use.
-If repeated use of said pattern results in more successes than failures, then the basic premise to consider the use of the pattern is rational [].
+If repeated use of said pattern results in more successes than failures, then the basic premise to consider the use of the pattern is rational [] \cite{elder} \cite{burke} \cite{burke}.
 Unfortunately, changing market is causing the pattern to become outdated therefore it is necessary to constantly update it.
@@
 
-\begin{thebibliography}{4}
-%
+\bibliography{article_main}
+%\begin{thebibliography}{4}
+
 %\bibitem{jour} Smith, T.F., Waterman, M.S.: Identification of Common Molecular
@@
 
-\end{thebibliography}
+%\end{thebibliography}
 

### 2014-04-06 Article/Article20140406Granada/LatexArt/article_main.tex
external bib file

@@
 If a certain set of rules in the strategy used to seek the pattern, leads to the success then these rules are a pattern that is encouraged for repeated use.
-If repeated use of said pattern results in more successes than failures, then the basic premise to consider the use of the pattern is rational [] \cite{elder} \cite{burke} \cite{burke}.
+If repeated use of said pattern results in more successes than failures, then the basic premise to consider the use of the pattern is rational [].
 Unfortunately, changing market is causing the pattern to become outdated therefore it is necessary to constantly update it.
@@
 Thus the earthworm moves incrementally at length of time called the period of the candle.
-I-th candle is  defined as a row of data of values  Oi, Hi, Li, Ci (Open, High, Low and Close).
+I-th candle is  defined as a row of data of values  $Oi$, $Hi$, $Li$, $Ci$ (Open, High, Low and Close).
 These values represent (in order): the value at the beginning of this period, the maximum value within the period, the minimum and the closing values - at the end of the candle.\\
@@
 
-\bibliography{article_main}
-%\begin{thebibliography}{4}
-
-%\bibitem{jour} Smith, T.F., Waterman, M.S.: Identification of Common Molecular
-%Subsequences. J. Mol. Biol. 147, 195--197 (1981)
-%
-%\bibitem{lncschap} May, P., Ehrlich, H.C., Steinke, T.: ZIB Structure Prediction Pipeline:
-%Composing a Complex Biological Workflow through Web Services. In: Nagel,
-%W.E., Walter, W.V., Lehner, W. (eds.) Euro-Par 2006. LNCS, vol. 4128,
-%pp. 1148--1158. Springer, Heidelberg (2006)
-%
-%\bibitem{book} Foster, I., Kesselman, C.: The Grid: Blueprint for a New Computing
-%Infrastructure. Morgan Kaufmann, San Francisco (1999)
-%
-%\bibitem{proceeding1} Czajkowski, K., Fitzgerald, S., Foster, I., Kesselman, C.: Grid
-%Information Services for Distributed Resource Sharing. In: 10th IEEE
-%International Symposium on High Performance Distributed Computing, pp.
-%181--184. IEEE Press, New York (2001)
-%
-%\bibitem{proceeding2} Foster, I., Kesselman, C., Nick, J., Tuecke, S.: The Physiology of the
-%Grid: an Open Grid Services Architecture for Distributed Systems
-%Integration. Technical report, Global Grid Forum (2002)
-%
-%\bibitem{url} National Center for Biotechnology Information, \url{http://www.ncbi.nlm.nih.gov}
-
-%\end{thebibliography}
+\bibliography{bibliography}
+\bibliographystyle{splncs}
 

### 2014-04-08 Article/Article20140406Granada/LatexArt/article_main.tex
Bibliography 1st version

@@
 
-Algotrading is rapidly growing new form of trading on financial markets where investor (that makes decisions) is replaced with automaton (computer program) [].
+Algotrading is rapidly growing new form of trading on financial markets where investor (that makes decisions) is replaced with automaton (computer program) \cite{Leshik2011}.
 Such machine can perform operations (opening and closing positions, placing orders to open such positions that meet certain conditions) directly in an automated brokerage platform environment.
@@
 Modern trends, in the development of this software, include sophisticated methods of: artificial intelligence, pattern recognition, classification and machine learning.
-Those methods are interpenetrating and complementary and are also expanded with information based on fundamental analysis, for example, automatically extracted from the Internet \cite{elder} [Schwager, Elder, … nasze hindawi].\\
+Those methods are interpenetrating and complementary and are also expanded with information based on fundamental analysis, for example, automatically extracted from the Internet \cite{elder}\cite{Wilinski2014}\cite{Schwager1996}.\\
 
@@
 Let's assume that candle can have color (often in a number of brokerage platforms, this procedure is used).
-Therefore candles may be red (when the opening of the candle is higher than its closing $Oi>Ci$) and green (when the situation is opposite $Oi <Ci$).\\
+Therefore candles may be red (when the opening of the candle is higher than its closing $Oi>Ci$) and green (when the situation is opposite $Oi<Ci$).\\
 Let's also assume --- it is a primary strategy rule - that when an artificial earthworm has a significant advantage of red candles, a short position is opened or continued.
@@
 From these results it can be concluded that the strategy is working with a short shelf life characteristics.
-The best results are achieved in periods of about 10-20 candles, it is unlike any other strategy presented in [Hindawi] where the best results were achieved for the test periods with a length of 80-100 candles.\\
+The best results are achieved in periods of about 10-20 candles, it is unlike any other strategy presented in \cite{Wilinski2014} where the best results were achieved for the test periods with a length of 80-100 candles.\\
 All the above presented results refer to simulations in Matlab.
@@
 The direction of further research will test the hypothesis that the variability periods to test the learner can improve the quality of prediction.
-This hypothesis seems to be interesting against the background of previous experiences and results, eg for different studied strategies, including [ Hindawi ] obtained surprisingly different optimal length of periods of learning and testing.
+This hypothesis seems to be interesting against the background of previous experiences and results, eg for different studied strategies, including \cite{Wilinski2014} obtained surprisingly different optimal length of periods of learning and testing.
 

### 2014-04-13 Article/Article20140406Granada/LatexArt/article_main.tex
Spaces

@@
 Unfortunately, changing market is causing the pattern to become outdated therefore it is necessary to constantly update it.
-Search in the historical patterns, that could be effective in the data space not used for their determination ( to identify these patterns ), is a major challenge also applied in machine learning which is used in this paper.
+Search in the historical patterns, that could be effective in the data space not used for their determination (to identify these patterns), is a major challenge also applied in machine learning which is used in this paper.
 The article is organized as follows: at first authors describe an authored strategy based on an entirely innovative, according to the authors, concept of an artificial worm.
@@
 p3 --- the number of steps back on the curve of the cumulative profit for the determination of Zci --- p3 for comparison with the present value of Zci;
-p4 --- maximum size of the capital subsidence (eg for the currency pair EURUSD measured in pips ) , which if exceeded will trigger the closure position:\\
+p4 --- maximum size of the capital subsidence (eg for the currency pair EURUSD measured in pips), which if exceeded will trigger the closure position:\\
 \begin{equation}
@@
 So, the above-described algorithm uses 5 parameters, as many as 3 of which are devoted to risk management strategy.\\
-
+%%PBStart
 The complexity of the algorithm is illustrated in Figure \ref{fig:fig7}, which in the form of a decision tree shows the individual steps and decisions made in the iteration on a single candle.
@@
 \centering
-\caption{The test results of the algorithm for different configurations of learning and testing periods for a couple EUEUSD.}
+\caption{The test results of the algorithm for different configurations of learning and testing periods for a currency pair EURUSD.}
 \label{tab:tab1}
@@
 All the above presented results refer to simulations in Matlab.
+%%PBStop
 
@@
 Presented in the paper the concept of an innovative investment strategy gave satisfactory results for a certain pair as the result of periods of machine learning.
-For example, in the studied data for two key market currency pairs sampled every hour , the best value is 80 hours of teaching and 15 hours of testing.
+For example, in the studied data for two key market currency pairs sampled every hour, the best value is 80 hours of teaching and 15 hours of testing.
 One can assume that this relationship may change in a different environment (for other markets, for other periods) by becoming a sort of next parameter that optimal values should be sought.
 It should be emphasized that the study was conducted on data not used in the learning phase and for the basic principle of machine learning achieved results that would have satisfied many a practice.
-It should also be noted that outside research conducted in environment completely specified (for constant unchanging data stored in Matlab ) was also performed simulations in terms of actual brokerage platform.
+It should also be noted that outside research conducted in environment completely specified (for constant unchanging data stored in Matlab) was also performed simulations in terms of actual brokerage platform.
 The results obtained in both environments are similar in the sense of direction changes and logic behavior caused by the user received by the algorithm implemented in the Matlab and Metatrader.
-Differences explained in this work .
+Differences explained in this work.
 The direction of further research will test the hypothesis that the variability periods to test the learner can improve the quality of prediction.

### 2014-04-15 Article/Article20140406Granada/LatexArt/article_main.tex
effectiveness
titlerunning - The investment strategy based on behavior of artificial earthworm
in the Matlab

@@
 % a short form should be given in case it is too long for the running head
-\titlerunning{SHORT TITLE}
+\titlerunning{The investment strategy based on behavior of artificial earthworm}
 
@@
 
-Described algorithm is implemented the in Matlab and using the platform Metatrader MQL4 language.
+Described algorithm is implemented in the Matlab and using the MQL4 language of the Metatrader platform.
 The study was conducted both in the historical data (of course with the principles of machine learning --- testing was carried out using data not used in the learning phase) and a real ,,live'' market.
@@
 
-In addition, efficacy studies were carried out and optimized for different test periods.
+In addition, effectiveness studies were carried out and optimized for different test periods.
 To these results can be compared with each other, has been carried out their link, and the results were divided by the length of the test period, expressed by the number of candles.

### 2014-04-15 Article/Article20140406Granada/LatexArt/article_main.tex
which shows the individual steps

@@
 %%PBStart
-The complexity of the algorithm is illustrated in Figure \ref{fig:fig7}, which in the form of a decision tree shows the individual steps and decisions made in the iteration on a single candle.
+The complexity of the algorithm is illustrated in Figure \ref{fig:fig7}, which shows the individual steps and decisions made in the iteration on a single candle in the form of a decision tree.
 This iteration was carried out both in the search for optimal parameters p1, ..., p5 and in the process they use in the testing phase for data not used in learning.\\

### 2014-04-15 Article/Article20140406Granada/LatexArt/article_main.tex
used in learning period

@@
 The complexity of the algorithm is illustrated in Figure \ref{fig:fig7}, which shows the individual steps and decisions made in the iteration on a single candle in the form of a decision tree.
-This iteration was carried out both in the search for optimal parameters p1, ..., p5 and in the process they use in the testing phase for data not used in learning.\\
+This iteration was carried out both in the search for optimal parameters p1, ..., p5 and in the process they use in the testing phase for data not used in learning period.\\
 

### 2014-05-05 Article/Article20140406Granada/LatexArt/article_main.tex
tree form
All citations, preparation to pagecount optimization ;)

@@
 If a certain set of rules in the strategy used to seek the pattern, leads to the success then these rules are a pattern that is encouraged for repeated use.
-If repeated use of said pattern results in more successes than failures, then the basic premise to consider the use of the pattern is rational [].
+If repeated use of said pattern results in more successes than failures, then the basic premise to consider the use of the pattern is rational\cite{bishop2006pattern}.
 Unfortunately, changing market is causing the pattern to become outdated therefore it is necessary to constantly update it.
@@
 
-The figure shows in a tree further decisions taken at the beginning of the candle and then reactions to any unacceptable change in course.
+The figure shows in a tree form further decisions taken at the beginning of the candle and then reactions to any unacceptable change in course.
 The first examines the state of the position taken over from the closure of the previous candle.
@@
 This hypothesis seems to be interesting against the background of previous experiences and results, eg for different studied strategies, including \cite{Wilinski2014} obtained surprisingly different optimal length of periods of learning and testing.
+\cite{burke}\cite{hay}\cite{krutsinger}\cite{lewis}\cite{murphy}\cite{provost}\cite{wang}\cite{sinclare}\cite{person}\cite{myers}\cite{tian}
 

### 2014-05-05 Article/Article20140406Granada/LatexArt/article_main.tex
Minor fixes

@@
 \end{itemize}
-So, the above-described algorithm uses 5 parameters, as many as 3 of which are devoted to risk management strategy.\\
+So, the above-described algorithm uses 5 parameters, as many as 3 of which are devoted to risk management of the strategy.\\
 %%PBStart
@@
 The study was conducted primarily on the basic EURUSD exchange rate at candlelight 1h.
-This market was chosen because of its popularity, a huge liquidity and also due to the possession by the authors many experiences in other machine learning strategy for this particular market such as [].
+This market was chosen because of its popularity, a huge liquidity and also due to the possession by the authors many experiences in other machine learning strategy for this particular market such as \cite{Wilinski2014}.
 These experiments suggested initially, carrying out many tests with a long learning period, about 1000 candles, then 500 candles and testing time windows of 50 to 200 candles.
@@
 \begin{tabular}{|l|r|r|r|r|} \hline
-Learning/Test &	8	 &	10 &		15	 &	20 \\ \hline
+Learning\textbackslash Test &	8	 &	10 &		15	 &	20 \\ \hline
 40 &		-0.0261 &		-0.0759	 &	-0.1424	 &	-0.0653 \\ \hline
@@
 The table shows that the best results were obtained for the ratio of the learning period to test period as 80/15.
-For this comparison periods was performed to study the market in EURUSD and shown in the Figure \ref{fig:fig8} For the 800-hour candles obtained result 0.2401 (2401 pips).
+For this comparison periods was performed to study the market in EURUSD and shown in the Figure \ref{fig:fig8} For the 800 one hour candles obtained result 0.2401 (2401 pips).
 Chart is definitely a growth course with a maximum of 600 pips from falling, which gives a very good, according to the authors, the criterion of Calmar (ratio of profit to capital najwiekzsego slips) about nearly 4.0.\\
@@
 \begin{tabular}{|l|r|r|r|r|} \hline
-Learning/Test &	8	 &	10	 &	15 &		20 \\ \hline
+Learning\textbackslash Test &	8	 &	10	 &	15 &		20 \\ \hline
 40	 &	-0.1706	 &	0.0084 &		-0.1566	 &	-0.0877 \\ \hline
@@
 \begin{tabular}{|l|r|r|r|r|} \hline
-Learning/Test &	8	 &	10 &		15	 &	20\\ \hline
+Learning\textbackslash Test &	8	 &	10 &		15	 &	20\\ \hline
 40 &		-2.207E-06 &		-6.443E-06 &		-1.219E-05 &		-5.641E-06\\ \hline
@@
 \begin{tabular}{|l|r|r|r|r|} \hline
-Learning/Test &	8	 & 	10 &		15	 &	20\\ \hline
+Learning\textbackslash Test &	8	 & 	10 &		15	 &	20\\ \hline
 40	 & -2.949E-05 & 	1.457E-06 & 	-2.768E-05	 & -1.578E-05\\ \hline
@@
 \begin{itemize}
-\item spread was 0.0028, 
+\item spread was 0.00028, 
 \item initial deposit was 50000 EUR,
@@
 \begin{itemize}
-\item spread was 0.0016, 
+\item spread was 0.00016, 
 \item initial deposit was 10000 EUR,

### 2014-05-05 Article/Article20140406Granada/LatexArt/article_main.tex
edited abstract

@@
 Presented approach opens long and short positions alternately during the closing of actual candles.
-Closing of position is based on recommendation which is deduced from changes in features of time series.
+Closing of position is based on recommendation which is deduced from changes in characteristics of time series.
 The strategy has parameters that vary through time, and are adapted to the market changes.
-To present the strategy metaphor of an artificial earthworm, that feeds on a time series, was used.
+To present the strategy, a metaphor of an innovative artificial earthworm, that feeds on a time series, was used.
+The earthworm has its own artificial intelligence which allows it to analyse ,,consumed'' candles, change its preferences about movement direction or to stay in neutral state.
 The goal was to implement presented strategy for trading platform to achieve the automatic trading effect.
+The strategy was tested in two development environments --- MATLAB environment and trading platform MetaTrader after conversion of M-file into MQL4 file.
 Implemented strategy allows to achieve interesting results.

### 2014-05-05 Article/Article20140406Granada/LatexArt/article_main.tex
Size cutted to 17 pages

@@
 
-Figure \ref{fig:fig1} presents, as described above, earthworm in three successive states.
-After ,,swallowing'' the next candle worm loses the last one.
-Candles inside the body of the worm have different colors (presented in the form of solid lines (green) and dashed (red)).
-\begin{figure}[ht]
-\centering
-\includegraphics[width = 0.4\textwidth]{figures/rys1.eps}
-\caption{An example of changes in fixed-length p1 (number of candles) worm, which is traversing the time series.}
-\label{fig:fig1}
-\end{figure}
-\FloatBarrier
 Artificial worm executes the following algorithm.\\
@@
 This principle is presented in Figure \ref{fig:fig2}, which shows examples of learning periods and following them testing periods.
-Data from testing period was not used during learning.
-This figure shows also that in learning periods, the same data can be used several times by successively moving time frame by the number of steps corresponding to the length of the test window (of course only when  the length of the test period is shorter than the learning).\\
+Data from testing period was not used during learning.\\
 In both periods the same algorithm based on the intelligent behavior of worm is used.
-Of course, the typical problem of machine learning is the proper selection of the length of learning and testing period [], what will be a subject of further research.\\
+Of course, the typical problem of machine learning is the proper selection of the length of learning and testing period \cite{bishop2006pattern}, what will be a subject of further research.\\
 \begin{figure}[ht]
@@
 \end{itemize}
-Figure \ref{fig:fig3} and \ref{fig:fig4} explain the definitions of profit within a single candle in case of opening (or the continuation of long and short position).
-\begin{figure}[h!]
-\centering
-\includegraphics[width = 0.5\textwidth]{figures/rys3.png}
-\caption{Method of calculating profit in the (i +1)-th candle, in which long position was opened.}
-\label{fig:fig3}
-\end{figure}
-\FloatBarrier
-\begin{figure}[h!]
-\centering
-\includegraphics[width = 0.5\textwidth]{figures/rys4.png}
-\caption{Method of calculating profit in the (i +1)-th candle, in which short position was opened.}
-\label{fig:fig4}
-\end{figure}
-\FloatBarrier
 
-Both figures show symbolically the changes of course, combining simple value at the opening and closing of the candle, ignoring the oscillations inside the candle.
 \begin{itemize}
@@
 This way p5 parameter was used for securing in strategy the strong local changes in exchange rate within a single candle.\\
-The meaning of p5 parameter to the behavior of the worm and the occurrence of the closing position is explained in Figure \ref{fig:fig5} and Figure \ref{fig:fig6}.
-This time, unlike in Figures \ref{fig:fig3} and \ref{fig:fig4}, changes in exchange are inside the candle.
+The meaning of p5 parameter to the behavior of the worm and the occurrence of the closing position is explained in Figure \ref{fig:fig5}.
 \begin{figure}[h!]
@@
 \label{fig:fig5}
-\end{figure}
-\FloatBarrier
-\begin{figure}[h!]
-\centering
-\includegraphics[width = 0.5\textwidth]{figures/rys6.png}
-\caption{Method of calculating the profit (here: loss) in the case of necessity to use p5 parameter actuating mechanism SL for long positions.}
-\label{fig:fig6}
 \end{figure}
@@
 
-Tests were also made for another great importance and the currency pair GBPUSD 1h. The results are shown in Table \ref{tab:tab2} and in Figure \ref{fig:fig9}.
+Tests were also made for another great importance and the currency pair GBPUSD 1h. Results for the currency pair are worse than for EURUSD, however, reaffirm the overall efficiency of the algorithm.\\
 
-\begin{table}[h!]
-\centering
-\caption{The test results of the algorithm for different configurations of learning and testing periods for GBPUSD.}
-\label{tab:tab2}
-\begin{tabular}{|l|r|r|r|r|} \hline
-Learning\textbackslash Test &	8	 &	10	 &	15 &		20 \\ \hline
-40	 &	-0.1706	 &	0.0084 &		-0.1566	 &	-0.0877 \\ \hline
-60	 &	-0.1321	 &	-0.1668 &		-0.0070	 &	-0.0644 \\ \hline
-80	 &	-0.0175	 &	-0.1375 &		\textbf{0.0870}	 &	-0.0983 \\ \hline
-100	 &	-0.0744	 &	-0.0699	 &	-0.0174	 &	-0.1178 \\ \hline
-\end{tabular}
-\end{table}
-\FloatBarrier
-
-\begin{figure}[h!]
-\centering
-\includegraphics[width = 0.6\textwidth]{figures/rys9.png}
-\caption{Mileage accumulation of capital for 400 steps after 15 candles made of uses of the algorithm for the currency pair GBPUSD 1h.}
-\label{fig:fig9}
-\end{figure}
-\FloatBarrier
-
-Results for the currency pair are worse than for EURUSD, however, reaffirm the overall efficiency of the algorithm.\\
-
-It was also decided to test the effectiveness of the algorithm in terms of one candle 1h. The results are shown in Table 3\ref{tab:tab3} and Table \ref{tab:tab4}.
+It was also decided to test the effectiveness of the algorithm in terms of one candle 1h. The results are shown in Table \ref{tab:tab3} and Table \ref{tab:tab4}.
 
@@
 Result for EURUSD this means achievement of profit over 100 pips per month (approximately 550 hours of trading).
-This result is in terms of risk at Calmar ratio around 4 should be considered as engaging.
-Not much is worse than the result obtained for the other test pairs - GBPUSD.\\
+This result is in terms of risk at Calmar ratio around 4 should be considered as engaging.\\
 
@@
 \label{fig:fig10}
-\end{figure}
-\FloatBarrier
-
-\begin{figure}[h!]
-\centering
-\includegraphics[width = 0.6\textwidth]{figures/rys11.png}
-\caption{GBPUSD Results per candle.}
-\label{fig:fig11}
 \end{figure}
@@
 
-When following charts are respectively compared:
-\begin{itemize}
-\item Figure \ref{fig:fig12} with Figure \ref{fig:fig13},
-\item Figure \ref{fig:fig14} with Figure \ref{fig:fig15},
-\item Figure \ref{fig:fig16} with Figure \ref{fig:fig17},
-\item Figure \ref{fig:fig18} with Figure \ref{fig:fig19}.
-\end{itemize}
-
 It is important to note that every first chart from each pair above was done in Matlab and every second chart was done in MetaTrader.
@@
 
-Differences in results for the algorithm for Matlab and MetaTrader presented in Table \ref{tab:tab2}.
-by level of 9-21\% are significant, but it is important to note they do not contest convergence in the algorithm execution in both environments.
-It is possible to do more detailed research on differences for balance accumulation for particular positions to align the algorithm execution.
-However for the article purposes conversion of scripts that has been done is sufficient and gives solid base to admit that the algorithm is applicable for market regarding its conceptual assumptions.
-
-\begin{figure}[h!]
-\centering
-\includegraphics[width = 0.6\textwidth]{figures/rys16.png}
-\caption{Balance (relative value) in Matlab for EURUSD [1h] in period 2012.01.20 - 2013.01.01 with fixed p1-p5.}
-\label{fig:fig16}
-\end{figure}
-\FloatBarrier
-\begin{figure}[h!]
-\centering
-\includegraphics[width = 0.6\textwidth]{figures/rys17.png}
-\caption{Balance (absolute values) in MetaTrader for EURUSD [1h] in period 2012.01.20 - 2013.01.01 with fixed p1-p5.}
-\label{fig:fig17}
-\end{figure}
-\FloatBarrier
-
-\begin{figure}[h!]
-\centering
-\includegraphics[width = 0.6\textwidth]{figures/rys18.png}
-\caption{Balance (relative values) in Matlab for EURUSD [1h] in period 2012.01.20 - 2013.01.01 with dynamic p1-p5.}
-\label{fig:fig18}
-\end{figure}
-\FloatBarrier
-\begin{figure}[h!]
-\centering
-\includegraphics[width = 0.6\textwidth]{figures/rys19.png}
-\caption{19 Balance (absolute values) in MetaTrader for EURUSD [1h] in period 2012.01.20 - 2013.01.01 with dynamic p1-p5.}
-\label{fig:fig19}
-\end{figure}
-\FloatBarrier
-
 \section{Conclusions}
@@
 This hypothesis seems to be interesting against the background of previous experiences and results, eg for different studied strategies, including \cite{Wilinski2014} obtained surprisingly different optimal length of periods of learning and testing.
-\cite{burke}\cite{hay}\cite{krutsinger}\cite{lewis}\cite{murphy}\cite{provost}\cite{wang}\cite{sinclare}\cite{person}\cite{myers}\cite{tian}
+\cite{krutsinger}\cite{lewis}\cite{murphy}\cite{provost}\cite{wang}\cite{sinclare}\cite{person}\cite{tian}
 

### 2014-05-05 Article/Article20140406Granada/LatexArt/article_main.tex
minipages

@@
 \usepackage{placeins}
+\usepackage{subcaption}
+\captionsetup{compatibility=false}
 
@@
 \begin{figure}[h!]
+\begin{minipage}{0.49\textwidth}
 \centering
-\includegraphics[width = 0.6\textwidth]{figures/rys12.png}
-\caption{Balance (relative value) in Matlab for GBPUSD [1h] in period 2013.01.09 - 2013.12.30 with fixed parameters p1-p5.}
+\includegraphics[width = 0.9\textwidth]{figures/rys12.png}
+\subcaption{} % Balance (relative value) in Matlab for GBPUSD [1h] in period 2013.01.09 - 2013.12.30 with fixed parameters p1-p5.
 \label{fig:fig12}
-\end{figure}
-\FloatBarrier
-\begin{figure}[h!]
+\end{minipage}
+\begin{minipage}{0.49\textwidth}
 \centering
-\includegraphics[width = 0.6\textwidth]{figures/rys13.png}
-\caption{Balance (absolute value) in MetaTrader for GBPUSD [1h] in period 2013.01.09 - 2013.12.30 with fixed parameters p1-p5.}
+\includegraphics[width = \textwidth]{figures/rys13.png}
+\subcaption{} % Balance (absolute value) in MetaTrader for GBPUSD [1h] in period 2013.01.09 - 2013.12.30 with fixed parameters p1-p5.
 \label{fig:fig13}
+\end{minipage}
+\caption{CAPTION GOES HERE}
 \end{figure}
@@
 \begin{figure}[h!]
+\begin{minipage}{0.49\textwidth}
 \centering
-\includegraphics[width = 0.6\textwidth]{figures/rys14.png}
-\caption{Balance (relative value) in Matlab for GBPUSD [1h] in period 2013.01.09 - 2013.12.30 with dynamic p1-p5.}
+\includegraphics[width = 0.9\textwidth]{figures/rys14.png}
+\subcaption{} %Balance (relative value) in Matlab for GBPUSD [1h] in period 2013.01.09 - 2013.12.30 with dynamic p1-p5.
 \label{fig:fig14}
-\end{figure}
-\FloatBarrier
-\begin{figure}[h!]
+\end{minipage}
+\begin{minipage}{0.49\textwidth}
 \centering
-\includegraphics[width = 0.6\textwidth]{figures/rys15.png}
-\caption{Balance (absolute value) in MetaTrader for GBPUSD [1h] in period 2013.01.09 - 2013.12.30 with dynamic p1-p5.}
+\includegraphics[width = \textwidth]{figures/rys15.png}
+\subcaption{} %Balance (absolute value) in MetaTrader for GBPUSD [1h] in period 2013.01.09 - 2013.12.30 with dynamic p1-p5.
 \label{fig:fig15}
+\end{minipage}
+\caption{CAPTION GOES HERE}
 \end{figure}

### 2014-05-05 Article/Article20140406Granada/LatexArt/article_main.tex
Figures (6,7) captions

@@
 \includegraphics[width = 0.9\textwidth]{figures/rys12.png}
-\subcaption{} % Balance (relative value) in Matlab for GBPUSD [1h] in period 2013.01.09 - 2013.12.30 with fixed parameters p1-p5.
+\subcaption{Balance (relative value) in Matlab.}
 \label{fig:fig12}
@@
 \includegraphics[width = \textwidth]{figures/rys13.png}
-\subcaption{} % Balance (absolute value) in MetaTrader for GBPUSD [1h] in period 2013.01.09 - 2013.12.30 with fixed parameters p1-p5.
+\subcaption{Balance (absolute value) in MetaTrader.}
 \label{fig:fig13}
 \end{minipage}
-\caption{CAPTION GOES HERE}
+\caption{Balance for GBPUSD [1h] in period 2013.01.09 - 2013.12.30 with fixed parameters p1-p5.}
 \end{figure}
@@
 \includegraphics[width = 0.9\textwidth]{figures/rys14.png}
-\subcaption{} %Balance (relative value) in Matlab for GBPUSD [1h] in period 2013.01.09 - 2013.12.30 with dynamic p1-p5.
+\subcaption{Balance (relative value) in Matlab.}
 \label{fig:fig14}
@@
 \includegraphics[width = \textwidth]{figures/rys15.png}
-\subcaption{} %Balance (absolute value) in MetaTrader for GBPUSD [1h] in period 2013.01.09 - 2013.12.30 with dynamic p1-p5.
+\subcaption{Balance (absolute value) in MetaTrader.}
 \label{fig:fig15}
 \end{minipage}
-\caption{CAPTION GOES HERE}
+\caption{Balance for GBPUSD [1h] in period 2013.01.09 - 2013.12.30 with dynamic parameters p1-p5.}
 \end{figure}

### 2014-05-06 Article/Article20140406Granada/LatexArt/article_main.tex
Figure 7, Table 1 shift
variables in italic, subscripts

@@
 Let's consider an artificial worm, which behaves like its natural inspirer.
-Let this artificial worm have a length of p1 candles (vectors representing the knowledge about events occurring within the contractual part of the time series).
-Let her movement come down to the successive ,,eating'' one candle and simultaneous ,,discarding'' of one candle --- always having p1 candles.
+Let this artificial worm have a length of $p1$ candles (vectors representing the knowledge about events occurring within the contractual part of the time series).
+Let her movement come down to the successive ,,eating'' one candle and simultaneous ,,discarding'' of one candle --- always having $p1$ candles.
 Thus the earthworm moves incrementally at length of time called the period of the candle.
-I-th candle is  defined as a row of data of values  $Oi$, $Hi$, $Li$, $Ci$ (Open, High, Low and Close).
+I-th candle is  defined as a row of data of values  $O_i$, $H_i$, $L_i$, $C_i$ (Open, High, Low and Close).
 These values represent (in order): the value at the beginning of this period, the maximum value within the period, the minimum and the closing values - at the end of the candle.\\
 Let's assume that candle can have color (often in a number of brokerage platforms, this procedure is used).
-Therefore candles may be red (when the opening of the candle is higher than its closing $Oi>Ci$) and green (when the situation is opposite $Oi<Ci$).\\
+Therefore candles may be red (when the opening of the candle is higher than its closing $O_i>C_i$) and green (when the situation is opposite $O_i<C_i$).\\
 Let's also assume --- it is a primary strategy rule - that when an artificial earthworm has a significant advantage of red candles, a short position is opened or continued.
@@
 
-In the rules above Lr and Lg are the number of candles, respectively ,,red'' and ,,green'' in the worm of p1 length, wherein $p1 = Lr + Lg$.\\
+In the rules above Lr and Lg are the number of candles, respectively ,,red'' and ,,green'' in the worm of $p1$ length, wherein $p1 = Lr + Lg$.\\
 When dominance determined by another parameter p2 is undecided, as in \ref{eq:eq3}, then worm takes the color white and the position will not be opened.
@@
 
-It is assumed that the time series is Si where $i = 1, 2, ...,$ and each word is a vector $Si = (Oi, Hi, Li, Ci)$ called candle consisting of  four values: Open, High, Low and Close of time between the time t and t +1.
+It is assumed that the time series is Si where $i = 1, 2, ...,$ and each word is a vector $Si = (O_i, H_i, L_i, C_i)$ called candle consisting of  four values: Open, High, Low and Close of time between the time t and t +1.
 I is the final index of word which is the last word in time series that was taken under consideration.\\
@@
 This repeatable algorithm, located in both periods - learning and testing, has the following structure.
-In learning period the optimal value for five parameters p1, p2, ..., p5 was determined.
+In learning period the optimal value for five parameters $p1$, $p2$, ..., $p5$ was determined.
 In test period these designated values of parameters were used to perform the algorithm in the new environment.
@@
 \item For each $i = p1, p1 +1, p1 +2, ..., I$ and for $j = 1, ..., p1$ check whether the candle located at a distance i-j backwards from the current candle is:\\
-green when $Oi-j <Ci-j$, \\
-red when $Oi-j> Ci-j$, \\
-where p1 --- is the first parameter which is the length of the artificial worm - the number of candles of different colors that make up the ,,body'' of the worm; \\
-$Oi-j$ --- is the opening value of (i-j)-th candle;\\ 
-$Ci-j$ --- is the closing value of (i-j)-th candle; \\
+green when $O_{i-j} <C_{i-j}$, \\
+red when $O_{i-j}> C_{i-j}$, \\
+where $p1$ --- is the first parameter which is the length of the artificial worm - the number of candles of different colors that make up the ,,body'' of the worm; \\
+$O_{i-j}$ --- is the opening value of (i-j)-th candle;\\ 
+$C_{i-j}$ --- is the closing value of (i-j)-th candle; \\
 $I$ --- is the length of the test window, after which it is necessary to change the parameters values to the new, learned in the machine learning phase;\\
-\item In each i-th step, the loop j = 1, ..., p 1 is performed in which a number of green Lg, red Lr candles is calculated so the sum of  Lg and Lr is p1 (to avoid the situation when $Oi = Ci$, it is assigned arbitrarily to one of the candles sets, for example green);
+\item In each $i$-th step, the loop $j = 1, ..., p1$ is performed in which a number of green $Lg$, red $Lr$ candles is calculated so the sum of $Lg$ and $Lr$ is $p1$ (to avoid the situation when $O_i = C_i$, it is assigned arbitrarily to one of the candles sets, for example green);
 \item A condition for the existence of a Rg recommendation to open a long position (or to continue it if it is open) is checked.
@@
 
-In formulas above there is a parameter p2.
+In formulas above there is a parameter $p2$.
 It is the second parameter of the strategy which is an arbitrarily separated part of the worm, which depending on size causes the direction of investment not to change.
-Large p2 causes long positions to change into short positions (or vice-versa) rarely.
-Small value of p2 leads to a higher frequency of these changes.
-The optimum value of p2 is chosen similarly like p1.
+Large $p2$ causes long positions to change into short positions (or vice-versa) rarely.
+Small value of $p2$ leads to a higher frequency of these changes.
+The optimum value of $p2$ is chosen similarly like $p1$.
 \begin{itemize}
@@
 \begin{equation}
-Zi = Ci +1 - Ci - spread;
+Z_i = C_{i+1} - C_i - spread;
 \end{equation}
@@
 \begin{equation}
-Zi = Ci-Ci +1- spread;
+Z_i = C_i-C_{i+1}- spread;
 \end{equation}
@@
 This additional risk management is widely used in automated trading and is called limiting losses --- Stop Loss (SL).
-In this algorithm, SL was introduced as the fifth parameter of the strategy --- p5.
+In this algorithm, SL was introduced as the fifth parameter of the strategy --- $p5$.
 \end{itemize}
@@
 \begin{equation}
-\text{If } Li-Oi<SL \text{ then } Zi=-SL
+\text{If } L_i-O_i<SL \text{ then } Z_i=-SL
 \end{equation}
@@
 \begin{equation}
-\text{If } Oi-Hi<SL \text{ then } Zi=-SL
+\text{If } O_i-H_i<SL \text{ then } Z_i=-SL
 \end{equation}
@@
 \begin{equation}
-Zci = sum ( Zi ) \text{ from } i = 1 \text{ to the current i value;}
+Zci = sum ( Z_i ) \text{ from } i = 1 \text{ to the current i value;}
 \end{equation}
 \item There is a possible local subsidence Zci capital by introducing two additional parameters to manage the risk.\\
-p3 --- the number of steps back on the curve of the cumulative profit for the determination of Zci --- p3 for comparison with the present value of Zci;
-p4 --- maximum size of the capital subsidence (eg for the currency pair EURUSD measured in pips), which if exceeded will trigger the closure position:\\
+$p3$ --- the number of steps back on the curve of the cumulative profit for the determination of $Zc_i$ --- $p3$ for comparison with the present value of $Zc_i$;
+$p4$ --- maximum size of the capital subsidence (eg for the currency pair EURUSD measured in pips), which if exceeded will trigger the closure position:\\
 \begin{equation}
-\text{If } ( Zci - p3 - Zi ) <- p4 \text{ and } PositionState \neq 0 \text{ then } PositionState = 0
+\text{If } ( Zc_i - p3 - Z_i ) <- p4 \text{ and } PositionState \neq 0 \text{ then } PositionState = 0
 \end{equation} 
@@
 The complexity of the algorithm is illustrated in Figure \ref{fig:fig7}, which shows the individual steps and decisions made in the iteration on a single candle in the form of a decision tree.
-This iteration was carried out both in the search for optimal parameters p1, ..., p5 and in the process they use in the testing phase for data not used in learning period.\\
+This iteration was carried out both in the search for optimal parameters $p1, ..., p5$ and in the process they use in the testing phase for data not used in learning period.\\
+\begin{figure}[h!]
+\centering
+\includegraphics[width = \textwidth]{figures/rys7.png}
+\caption{Decision tree for the states and decisions in one step (candle) in the learning phase and testing.}
+\label{fig:fig7}
+\end{figure}
+\FloatBarrier
 
@@
 If it is negative, it checks if it is not achieved the level of SL.
-In the case of a negative return of the items, except for testing, SL is not exceeded within a candle tested is also a condition resulting from the use of parameters (p3, p4).
+In the case of a negative return of the items, except for testing, SL is not exceeded within a candle tested is also a condition resulting from the use of parameters ($p3$, $p4$).
 Tree is a state of complete items transmitted at the beginning of the next candle.
-
-\begin{figure}[h!]
-\centering
-\includegraphics[width = \textwidth]{figures/rys7.png}
-\caption{Decision tree for the states and decisions in one step (candle) in the learning phase and testing.}
-\label{fig:fig7}
-\end{figure}
-\FloatBarrier
 
@@
 
-Table \ref{tab:tab1} summarizes the results for different time periods.
-The study was conducted at approximately constant number of candles testing period, e.g.
-if the testing period was 10 candles, is to perform the test algorithm 1300 candles optimal parameters were calculated 130 times.
-If the testing period was 20 candles are the parameters were changed 65 times, etc., if it was available long test period is not used it.
-
 \begin{table}[h!]
@@
 \FloatBarrier
+Table \ref{tab:tab1} summarizes the results for different time periods.
+The study was conducted at approximately constant number of candles testing period, e.g.
+if the testing period was 10 candles, is to perform the test algorithm 1300 candles optimal parameters were calculated 130 times.
+If the testing period was 20 candles are the parameters were changed 65 times, etc., if it was available long test period is not used it.
 
@@
 \begin{itemize}
-\item with fixed parameters: p1=27, p2=4, p3=1, p4=-0.0060, p5=0.0060 (Figure \ref{fig:fig10} and Figure \ref{fig:fig11}).
+\item with fixed parameters: $p1$=27, $p2$=4, $p3$=1, $p4$=-0.0060, $p5$=0.0060 (Figure \ref{fig:fig10} and Figure \ref{fig:fig11}).
 Optimal parameters in that case were computed in Matlab for the first testing period and then were used for all testing periods.
@@
 \begin{itemize}
-\item with fixed parameters: p1=34, p2=4, p3=3, p4=-0.0060, p5=0.0060 (Figure \ref{fig:fig14} and Figure \ref{fig:fig15}) Optimal parameters in that case were computed in Matlab for the first testing period and then were used for all testing periods.
+\item with fixed parameters: $p1$=34, $p2$=4, $p3$=3, $p4$=-0.0060, $p5$=0.0060 (Figure \ref{fig:fig14} and Figure \ref{fig:fig15}) Optimal parameters in that case were computed in Matlab for the first testing period and then were used for all testing periods.
 \item with dynamic parameters that were changed every testing period, regarding to their values computed in Matlab that were put to MetaTrader (Figure \ref{fig:fig16} and Figure \ref{fig:fig17})
@@
 \multicolumn{5}{|c|}{GBPUSD in time period 2013.01.09 - 2013.12.30}\\ \hline
-Fixed p1-p5	 & -8 823.76 & 	-7 987.00 & 	836.76 & 	10.48\\
-Dynamic p1-p5	 & 6 057.82	 & 5 555.00	 & 502.82 & 	9.05\\ \hline
+Fixed $p1$-$p5$	 & -8 823.76 & 	-7 987.00 & 	836.76 & 	10.48\\
+Dynamic $p1$-$p5$	 & 6 057.82	 & 5 555.00	 & 502.82 & 	9.05\\ \hline
 \multicolumn{5}{|c|}{EURUSD in time period 2012.01.20 - 2013.01.01}\\ \hline
-Fixed p1-p5	 & 2 305,18 & 	2 695,00	 & 389,82	 & 14,46\\
-Dynamic p1-p5 & 	13 669,40 & 	17 260,00 & 	3590,60	 & 20,80\\ \hline
+Fixed $p1$-$p5$	 & 2 305,18 & 	2 695,00	 & 389,82	 & 14,46\\
+Dynamic $p1$-$p5$ & 	13 669,40 & 	17 260,00 & 	3590,60	 & 20,80\\ \hline
 \end{tabular}
@@
 \end{minipage}
-\caption{Balance for GBPUSD [1h] in period 2013.01.09 - 2013.12.30 with fixed parameters p1-p5.}
+\caption{Balance for GBPUSD [1h] in period 2013.01.09 - 2013.12.30 with fixed parameters $p1$-$p5$.}
 \end{figure}
@@
 \end{minipage}
-\caption{Balance for GBPUSD [1h] in period 2013.01.09 - 2013.12.30 with dynamic parameters p1-p5.}
+\caption{Balance for GBPUSD [1h] in period 2013.01.09 - 2013.12.30 with dynamic parameters $p1$-$p5$.}
 \end{figure}

### 2014-05-06 Article/Article20140406Granada/LatexArt/article_main.tex
variables in intalic

@@
 \begin{equation}
-\text{If }  Lr > p1/2 -p2 \text{ then short;}
+\text{If }  Lr > p1/2 -p2 \text{ then } short;
 \end{equation}
@@
 \begin{equation}
-\text{If }  Lg > p1/2 -p2 \text{ then long;}
+\text{If }  Lg > p1/2 -p2 \text{ then } long;
 \end{equation}
@@
 \begin{equation}
-\text{If }  Lg < p1/2 -p2 \text{ and } Lr< p1/2-p2 \text{ then none;}
+\text{If }  Lg < p1/2 -p2 \text{ and } Lr< p1/2-p2 \text{ then } none;
 \label{eq:eq3}
@@
 \item earthworm observes cumulative profit curve and if it  notices unacceptable drawdown, then opened position is changed to the opposite;
-\item unacceptable drawdown is defined by two other parameters p3 and p4.
-p3 is the number of previous candles, which sets a reference point in time series, in which the value of the accumulated profit for i-p3 is checked for comparison with the current value of the accumulated profit.
-p4 is permissible decrease of cumulative profit.
-If it is exceeded, the SL (Stop Loss --- closes the currently open position) mechanism is activated;
+\item unacceptable drawdown is defined by two other parameters $p3$ and $p4$.
+$p3$ is the number of previous candles, which sets a reference point in time series, in which the value of the accumulated profit for $i-p3$ is checked for comparison with the current value of the accumulated profit.
+$p4$ is permissible decrease of cumulative profit.
+If it is exceeded, the $SL$ (Stop Loss --- closes the currently open position) mechanism is activated;
 \item worm also observes current course changes during  each next candle and reacts to unprofitable changes.
-If the current exchange rate causes a loss on the opened positions greater than p5 then the SL mechanism is triggered --- the position is closed and to the end of the candle worm remains in the state without an open position.
-p5 is therefore the fifth strategy parameter.
+If the current exchange rate causes a loss on the opened positions greater than $p5$ then the $SL$ mechanism is triggered --- the position is closed and to the end of the candle worm remains in the state without an open position.
+$p5$ is therefore the fifth strategy parameter.
 \end{itemize}
@@
 
-It is assumed that the time series is Si where $i = 1, 2, ...,$ and each word is a vector $Si = (O_i, H_i, L_i, C_i)$ called candle consisting of  four values: Open, High, Low and Close of time between the time t and t +1.
+It is assumed that the time series is Si where $i = 1, 2, ...,$ and each word is a vector $S_i = (O_i, H_i, L_i, C_i)$ called candle consisting of  four values: Open, High, Low and Close of time between the time t and t +1.
 I is the final index of word which is the last word in time series that was taken under consideration.\\
@@
 \begin{equation}
-\text{If } lg> p1/2-p2 \text{ then } Rg=1
+\text{If } Lg> p1/2-p2 \text{ then } Rg=1
 \end{equation}
@@
 \begin{equation}
-\text{If } lr>p1/2 – p2 \text {then Rr=1.}
+\text{If } Lr>p1/2 – p2 \text {then Rr=1.}
 \end{equation}
@@
 \item Each of the profits calculated above is verified in terms of exceeding the allowable local position drawdown (within one candle).
-This additional risk management is widely used in automated trading and is called limiting losses --- Stop Loss (SL).
-In this algorithm, SL was introduced as the fifth parameter of the strategy --- $p5$.
+This additional risk management is widely used in automated trading and is called limiting losses --- Stop Loss ($SL$).
+In this algorithm, $SL$ was introduced as the fifth parameter of the strategy --- $p5$.
 \end{itemize}
@@
 \end{equation}
-where Li --– the lowest rate value in the i-th candle; SL --– absolute value Stop Loss appearing as p5 parameter;
+where Li --– the lowest rate value in the i-th candle; $SL$ --– absolute value Stop Loss appearing as $p5$ parameter;
 \item in the case of opening at the beginning of the i-th candle or continuation of a short position presented condition did not occur:
@@
 \end{itemize}
-This way p5 parameter was used for securing in strategy the strong local changes in exchange rate within a single candle.\\
-The meaning of p5 parameter to the behavior of the worm and the occurrence of the closing position is explained in Figure \ref{fig:fig5}.
+This way $p5$ parameter was used for securing in strategy the strong local changes in exchange rate within a single candle.\\
+The meaning of $p5$ parameter to the behavior of the worm and the occurrence of the closing position is explained in Figure \ref{fig:fig5}.
 \begin{figure}[h!]
@@
 \includegraphics[width = 0.5\textwidth]{figures/rys5.png}
-\caption{Method of calculating the profit (here: loss) in the case of necessity to use p5 parameter actuating mechanism SL for long positions.}
+\caption{Method of calculating the profit (here: loss) in the case of necessity to use $p5$ parameter actuating mechanism $SL$ for long positions.}
 \label{fig:fig5}
@@
 If it is positive, it does not take up any additional decisions.
-If it is negative, it checks if it is not achieved the level of SL.
-In the case of a negative return of the items, except for testing, SL is not exceeded within a candle tested is also a condition resulting from the use of parameters ($p3$, $p4$).
+If it is negative, it checks if it is not achieved the level of $SL$.
+In the case of a negative return of the items, except for testing, $SL$ is not exceeded within a candle tested is also a condition resulting from the use of parameters ($p3$, $p4$).
 Tree is a state of complete items transmitted at the beginning of the next candle.
@@
 \item Calculation of balance and other standard market statistics is implemented manually, including also calculation of profit and loss related with opening / closing position;
-\item SL handling is implemented manually, including trailing stop;
+\item $SL$ handling is implemented manually, including trailing stop;
 \item Lack of built-in market validations for opening / closing position;
@@
 \item Balance and other standard market statistics are calculated automatically, including also a strictly defined API for opening / closing position;
-\item SL handling is a built-in feature, including trailing stop;
+\item $SL$ handling is a built-in feature, including trailing stop;
 \item There are built-in market validations for opening / closing position;

### 2014-05-07 Article/Article20140406Granada/LatexArt/article_main.tex
word->element

@@
 
-It is assumed that the time series is Si where $i = 1, 2, ...,$ and each word is a vector $S_i = (O_i, H_i, L_i, C_i)$ called candle consisting of  four values: Open, High, Low and Close of time between the time t and t +1.
+It is assumed that the time series is Si where $i = 1, 2, ...,$ and each element is a vector $S_i = (O_i, H_i, L_i, C_i)$ called candle consisting of four values: Open, High, Low and Close of time between the time $t$ and $t+1$.
 I is the final index of word which is the last word in time series that was taken under consideration.\\

### 2014-05-07 Article/Article20140406Granada/LatexArt/article_main.tex
i-th in italic

@@
 Thus the earthworm moves incrementally at length of time called the period of the candle.
-I-th candle is  defined as a row of data of values  $O_i$, $H_i$, $L_i$, $C_i$ (Open, High, Low and Close).
+$I-th$ candle is  defined as a row of data of values  $O_i$, $H_i$, $L_i$, $C_i$ (Open, High, Low and Close).
 These values represent (in order): the value at the beginning of this period, the maximum value within the period, the minimum and the closing values - at the end of the candle.\\
@@
 In test period these designated values of parameters were used to perform the algorithm in the new environment.
-In each i-th step (candle) of time series following activities were performed:
+In each $i-th$ step (candle) of time series following activities were performed:
 \begin{itemize}
@@
 $I$ --- is the length of the test window, after which it is necessary to change the parameters values to the new, learned in the machine learning phase;\\
-\item In each $i$-th step, the loop $j = 1, ..., p1$ is performed in which a number of green $Lg$, red $Lr$ candles is calculated so the sum of $Lg$ and $Lr$ is $p1$ (to avoid the situation when $O_i = C_i$, it is assigned arbitrarily to one of the candles sets, for example green);
+\item In each $i-th$ step, the loop $j = 1, ..., p1$ is performed in which a number of green $Lg$, red $Lr$ candles is calculated so the sum of $Lg$ and $Lr$ is $p1$ (to avoid the situation when $O_i = C_i$, it is assigned arbitrarily to one of the candles sets, for example green);
 \item A condition for the existence of a Rg recommendation to open a long position (or to continue it if it is open) is checked.
@@
 \begin{itemize}
-\item in the case of opening at the beginning of the i-th candle or continuation of a long position presented condition did not occur:\\
+\item in the case of opening at the beginning of the $i-th$ candle or continuation of a long position presented condition did not occur:\\
 \begin{equation}
@@
 \end{equation}
-where Li --– the lowest rate value in the i-th candle; $SL$ --– absolute value Stop Loss appearing as $p5$ parameter;
-\item in the case of opening at the beginning of the i-th candle or continuation of a short position presented condition did not occur:
+where Li --– the lowest rate value in the $i-th$ candle; $SL$ --– absolute value Stop Loss appearing as $p5$ parameter;
+\item in the case of opening at the beginning of the $i-th$ candle or continuation of a short position presented condition did not occur:
 \begin{equation}
@@
 \end{equation}
-where Hi --– the highest rate value in the i-th candle.
+where Hi --– the highest rate value in the $i-th$ candle.
 \end{itemize}

### 2014-05-07 Article/Article20140406Granada/LatexArt/article_main.tex
zmniejszone odstępy po rysunkach

@@
 \FloatBarrier
-
+\vspace{-1em}
 This repeatable algorithm, located in both periods - learning and testing, has the following structure.
@@
 \FloatBarrier
-
+\vspace{-1em}
 The figure shows in a tree form further decisions taken at the beginning of the candle and then reactions to any unacceptable change in course.
@@
 \FloatBarrier
-
+\vspace{-1em}
 Tests were also made for another great importance and the currency pair GBPUSD 1h. Results for the currency pair are worse than for EURUSD, however, reaffirm the overall efficiency of the algorithm.\\
@@
 \FloatBarrier
+\vspace{-1em}
 
@@
 \FloatBarrier
-
 \begin{figure}[h!]
@@
 \FloatBarrier
-
+\vspace{-1em}
 It is important to note that every first chart from each pair above was done in Matlab and every second chart was done in MetaTrader.
@@
 Despite those differences, corellation between Matlab and MetaTrader charts for the artificial worm algorithm executions is indisputable.
-
 \begin{figure}[h!]

### 2014-05-07 Article/Article20140406Granada/LatexArt/article_main.tex
Zci -> Zc_i

@@
 \begin{equation}
-Zci = sum ( Z_i ) \text{ from } i = 1 \text{ to the current i value;}
+Zc_i = sum ( Z_i ) \text{ from } i = 1 \text{ to the current i value;}
 \end{equation}
-\item There is a possible local subsidence Zci capital by introducing two additional parameters to manage the risk.\\
+\item There is a possible local subsidence $Zc_i$ capital by introducing two additional parameters to manage the risk.\\
 $p3$ --- the number of steps back on the curve of the cumulative profit for the determination of $Zc_i$ --- $p3$ for comparison with the present value of $Zc_i$;

### 2014-05-08 Article/Article20140406Granada/LatexArt/article_main.tex
new keyword: mql4
bots -> bot

@@
 Implemented strategy allows to achieve interesting results.
-\keywords{investment strategy, machine learning, forecasting, time series, algotrading}
+\keywords{investment strategy, machine learning, forecasting, time series, algotrading, mql4}
 \end{abstract}
@@
 
-Such computer applications (bots) require carefully prepared and tested software that most often needs to adapt to the changing situations on the observed markets.
+Such computer applications (bot) require carefully prepared and tested software that most often needs to adapt to the changing situations on the observed markets.
 Modern trends, in the development of this software, include sophisticated methods of: artificial intelligence, pattern recognition, classification and machine learning.

### 2014-05-08 Article/Article20140406Granada/LatexArt/article_main.tex
cite{Wilinski2014}

--- 2014-05-07 Article/Article20140406Granada/LatexArt/article_main.tex
@@
 
-Algotrading is rapidly growing new form of trading on financial markets where investor (that makes decisions) is replaced with automaton (computer program) \cite{Leshik2011}.
+Algotrading is rapidly growing new form of trading on financial markets where investor (that makes decisions) is replaced with automaton (computer program) \cite{Leshik2011}\cite{Wilinski2014}.
 Such machine can perform operations (opening and closing positions, placing orders to open such positions that meet certain conditions) directly in an automated brokerage platform environment.
@@
 \centering
-\includegraphics[width = 0.6\textwidth]{figures/rys2.png}
+%\includegraphics[width = 0.6\textwidth]{figures/rys2.png}
 \caption{An example of the arrangement of learning and testing periods of strategy parameters in time series.}

### 2014-05-08 Article/Article20140406Granada/LatexArt/article_main.tex
citations at section 1

@@
 Such computer applications (bots) require carefully prepared and tested software that most often needs to adapt to the changing situations on the observed markets.
-Modern trends, in the development of this software, include sophisticated methods of: artificial intelligence, pattern recognition, classification and machine learning.
-Those methods are interpenetrating and complementary and are also expanded with information based on fundamental analysis, for example, automatically extracted from the Internet \cite{elder}\cite{Wilinski2014}\cite{Schwager1996}.\\
+Modern trends, in the development of this software, include sophisticated methods of: artificial intelligence, pattern recognition, classification and machine learning\cite{Leshik2011}\cite{Wilinski}\cite{wang}\cite{sinclare}.
+Those methods are interpenetrating and complementary and are also expanded with information based on fundamental analysis, for example, automatically extracted from the Internet \cite{elder}\cite{Wilinski2014}\cite{Schwager1996}.
+Many strategies are based on relatively simple rules.
+Efficiency of this rules is amplified by using of machine learning\cite{Wilinski}\cite{person}\cite{tian}\cite{krutsinger}\cite{lewis}\cite{murphy}.\\
 
@@
 To use this software, it is necessary to make sure that there are reasonable premises of achieving the success.
-These conditions can be achieved through inductive thinking, involving the assumption that multiple validation of decision on data from the past substantiates the correctness of the decision in the future.
+These conditions can be achieved through inductive thinking\cite{provost}\cite{KleskWilinski}, involving the assumption that multiple validation of decision on data from the past substantiates the correctness of the decision in the future.
 If a certain set of rules in the strategy used to seek the pattern, leads to the success then these rules are a pattern that is encouraged for repeated use.
-If repeated use of said pattern results in more successes than failures, then the basic premise to consider the use of the pattern is rational\cite{bishop2006pattern}.
+If repeated use of said pattern results in more successes than failures, then the basic premise to consider the use of the pattern is rational\cite{bishop2006pattern}\cite{KleskWilinski}.
 Unfortunately, changing market is causing the pattern to become outdated therefore it is necessary to constantly update it.

### 2014-05-09 Article/Article20140406Granada/LatexArt/article_main.tex
pl chars
worm -> earthworm
I-th -> i-th

@@
 \captionsetup{compatibility=false}
+\usepackage[T1]{fontenc}
+\usepackage[utf8x]{inputenc}
 
@@
 %
-\author{Antoni Wilinski
-\and Aneta Bera\and Maciej Jarlaczynski\and Piotr Blaszynski}
+\author{Antoni Wiliński
+\and Aneta Bera\and Maciej Jarlaczyński\and Piotr Błaszyński}
 %
@@
 
-Let's consider an artificial worm, which behaves like its natural inspirer.
+Let's consider an artificial earthworm, which behaves like its natural inspirer.
 Let this artificial worm have a length of $p1$ candles (vectors representing the knowledge about events occurring within the contractual part of the time series).
@@
 Thus the earthworm moves incrementally at length of time called the period of the candle.
-$I-th$ candle is  defined as a row of data of values  $O_i$, $H_i$, $L_i$, $C_i$ (Open, High, Low and Close).
+$i-th$ candle is  defined as a row of data of values  $O_i$, $H_i$, $L_i$, $C_i$ (Open, High, Low and Close).
 These values represent (in order): the value at the beginning of this period, the maximum value within the period, the minimum and the closing values - at the end of the candle.\\

### 2014-05-09 Article/Article20140406Granada/LatexArt/article_main.tex
procedure -> approach

@@
 These values represent (in order): the value at the beginning of this period, the maximum value within the period, the minimum and the closing values - at the end of the candle.\\
-Let's assume that candle can have color (often in a number of brokerage platforms, this procedure is used).
+Let's assume that candle can have color (often in a number of brokerage platforms, this approach is used).
 Therefore candles may be red (when the opening of the candle is higher than its closing $O_i>C_i$) and green (when the situation is opposite $O_i<C_i$).\\

### 2014-05-09 Article/Article20140406Granada/LatexArt/article_main.tex
italic, text deleted

@@
 When earthworm has the significant advantage of green candles, a long position is opened or continued.
-Imprecise term ,,significant'' is defined by the use of the second parameter p2 according to the rules:
+Imprecise term ,,significant'' is defined by the use of the second parameter $p2$ according to the rules:
 \begin{equation}
@@
 
-In the rules above Lr and Lg are the number of candles, respectively ,,red'' and ,,green'' in the worm of $p1$ length, wherein $p1 = Lr + Lg$.\\
-When dominance determined by another parameter p2 is undecided, as in \ref{eq:eq3}, then worm takes the color white and the position will not be opened.
+In the rules above $Lr$ and $Lg$ are the number of candles, respectively ,,red'' and ,,green'' in the worm of $p1$ length, wherein $p1 = Lr + Lg$.\\
+When dominance determined by another parameter $p2$ is undecided, as in (\ref{eq:eq3}), then worm takes the color white and the position will not be opened.
 When the worm continues to open position, investor does not incur costs.
@@
 
-It is assumed that the time series is Si where $i = 1, 2, ...,$ and each element is a vector $S_i = (O_i, H_i, L_i, C_i)$ called candle consisting of four values: Open, High, Low and Close of time between the time $t$ and $t+1$.
-I is the final index of word which is the last word in time series that was taken under consideration.\\
+It is assumed that the time series is $S_i$ where $i = 1, 2, ...,$ and each element is a vector $S_i = (O_i, H_i, L_i, C_i)$ called candle.\\
 
-Artificial worm executes the following algorithm.\\
+Artificial earthworm executes the following algorithm.\\
 The strategy is built on the principle of classical machine learning.
 Before starting to run the algorithm, on data located outside the environment that investor knows (like on the current market segments --- out-of-sample), it is necessary to ,,teach''  the values of parameters.
-Since we are dealing with time series,  the natural solution is that the period of learning preceding testing period.
 This principle is presented in Figure \ref{fig:fig2}, which shows examples of learning periods and following them testing periods.
 Data from testing period was not used during learning.\\
-In both periods the same algorithm based on the intelligent behavior of worm is used.
-Of course, the typical problem of machine learning is the proper selection of the length of learning and testing period \cite{bishop2006pattern}, what will be a subject of further research.\\
 \begin{figure}[ht]

### 2014-05-09 Article/Article20140406Granada/LatexArt/article_main.tex
italic

@@
 \item In each $i-th$ step, the loop $j = 1, ..., p1$ is performed in which a number of green $Lg$, red $Lr$ candles is calculated so the sum of $Lg$ and $Lr$ is $p1$ (to avoid the situation when $O_i = C_i$, it is assigned arbitrarily to one of the candles sets, for example green);
-\item A condition for the existence of a Rg recommendation to open a long position (or to continue it if it is open) is checked.
+\item A condition for the existence of a $Rg$ recommendation to open a long position (or to continue it if it is open) is checked.
 This condition is arbitrarily adopted (one can of course consider different one):
@@
 \end{itemize}
-If this condition is fulfilled, then depending on the current position status PositionState (where PositionState is a variable which takes values {long, short, 0}) at the opening of the next candle, a position is opened or continued as follows:
+If this condition is fulfilled, then depending on the current position status $PositionState$ (where $PositionState$ is a variable which takes values {long, short, 0}) at the opening of the next candle, a position is opened or continued as follows:
 \begin{equation}
-\text{If } Rg=1 \text{ and } PositionState =long \text{ then PositionState =long;}
+\text{If } Rg=1 \text{ and } PositionState =long \text{ then }PositionState =long;
 \end{equation}
@@
 \begin{equation}
-\text{If } Rg=1 \text{ and } PositionState = short \text{ then PositionState=long;}
+\text{If } Rg=1 \text{ and } PositionState = short \text{ then } PositionState=long;
 \end{equation}
 \begin{equation}
-\text{If } Rg=1 \text{ and } PositionState =0 \text{ then PositionState =long;}
+\text{If } Rg=1 \text{ and } PositionState =0 \text{ then } PositionState =long;
 \end{equation}
@@
 \begin{equation}
-\text{If } Rr=1 \text{ and } PositionState =long \text{ then PositionState =short;}
+\text{If } Rr=1 \text{ and } PositionState =long \text{ then } PositionState =short;
 \end{equation}
 \begin{equation}
-\text{If } Rr==1 \text{ and } PositionState ==short \text{ then PositionState=short;}
+\text{If } Rr==1 \text{ and } PositionState ==short \text{ then } PositionState=short;
 \end{equation}
@@
 \begin{equation}
-\text{If } Rr==1 \text{ and }  PositionState ==0 \text{ then  PositionState =short;}
+\text{If } Rr==1 \text{ and }  PositionState ==0 \text{ then }  PositionState =short;
 \end{equation}
@@
 \end{equation}
-where the spread = 0, when opened long position is continued; \\
-and spread = cost, when long position was opened after closing or opening a short position in case when there was no open position;\\
-cost is a variable that depends on the particular brokerage platform that was used for testing the strategy; in this case, for the currency pair EURUSD $cost = 0.00016$ was assumed and for the currency pair GBPUSD $cost = 0.00028$.
+where the $spread = 0$, when opened long position is continued; \\
+and $spread = cost$, when long position was opened after closing or opening a short position in case when there was no open position;\\
+$cost$ is a variable that depends on the particular brokerage platform that was used for testing the strategy; in this case, for the currency pair EURUSD $cost = 0.00016$ was assumed and for the currency pair GBPUSD $cost = 0.00028$.
 \item When short position is opened, profit after one candle (it does not mean that position is closed) can be calculated as: 
@@
 \end{equation}
-where Li --– the lowest rate value in the $i-th$ candle; $SL$ --– absolute value Stop Loss appearing as $p5$ parameter;
+where $L_i$ --– the lowest rate value in the $i-th$ candle; $SL$ --– absolute value Stop Loss appearing as $p5$ parameter;
 \item in the case of opening at the beginning of the $i-th$ candle or continuation of a short position presented condition did not occur:
@@
 $p3$ --- the number of steps back on the curve of the cumulative profit for the determination of $Zc_i$ --- $p3$ for comparison with the present value of $Zc_i$;
-$p4$ --- maximum size of the capital subsidence (eg for the currency pair EURUSD measured in pips), which if exceeded will trigger the closure position:\\
+$p4$ --- maximum value measured in pips of the capital drawdown (eg for the currency pair EURUSD), which if exceeded will trigger the closure position:\\
 \begin{equation}
@@
 \end{equation} 
-where PositionState --- is the type of open position (long or short) and PositionStates equal 0 means resignations from the opening position to the beginning of the next candle.
+where $PositionState$ --- is the type of open position (long or short) and $PositionState$ equal 0 means resignations from the opening position to the beginning of the next candle.
 \end{itemize}

### 2014-05-09 Article/Article20140406Granada/LatexArt/article_main.tex
communities -> environments
candlelight 1h -> 1h candles

@@
 The study was conducted both in the historical data (of course with the principles of machine learning --- testing was carried out using data not used in the learning phase) and a real ,,live'' market.
-Between the communities, there are also important differences that affect the diversity of simulation results.
+Between the environments, there are also important differences that affect the diversity of simulation results.
 
 \section{The study of strategy}
-The study was conducted primarily on the basic EURUSD exchange rate at candlelight 1h.
+The study was conducted primarily on the basic EURUSD exchange rate at 1h candles.
 This market was chosen because of its popularity, a huge liquidity and also due to the possession by the authors many experiences in other machine learning strategy for this particular market such as \cite{Wilinski2014}.

### 2014-05-09 Article/Article20140406Granada/LatexArt/article_main.tex
cite{Wilinski}

@@
 The study was conducted primarily on the basic EURUSD exchange rate at 1h candles.
-This market was chosen because of its popularity, a huge liquidity and also due to the possession by the authors many experiences in other machine learning strategy for this particular market such as \cite{Wilinski2014}.
+This market was chosen because of its popularity, a huge liquidity and also due to the possession by the authors many experiences in other machine learning strategy for this particular market such as \cite{Wilinski2014}\cite{Wilinski}.
 These experiments suggested initially, carrying out many tests with a long learning period, about 1000 candles, then 500 candles and testing time windows of 50 to 200 candles.

### 2014-05-09 Article/Article20140406Granada/LatexArt/article_main.tex
style

@@
 The table shows that the best results were obtained for the ratio of the learning period to test period as 80/15.
-For this comparison periods was performed to study the market in EURUSD and shown in the Figure \ref{fig:fig8} For the 800 one hour candles obtained result 0.2401 (2401 pips).
+For this comparison periods was performed to study the market in EURUSD and shown in the Figure \ref{fig:fig8} For the 800 one hour candles the result 0.2401 (2401 pips) is obtained.
 Chart is definitely a growth course with a maximum of 600 pips from falling, which gives a very good, according to the authors, the criterion of Calmar (ratio of profit to capital najwiekzsego slips) about nearly 4.0.\\

### 2014-05-09 Article/Article20140406Granada/LatexArt/article_main.tex
style fixes

@@
 For this comparison periods was performed to study the market in EURUSD and shown in the Figure \ref{fig:fig8} For the 800 one hour candles the result 0.2401 (2401 pips) is obtained.
-Chart is definitely a growth course with a maximum of 600 pips from falling, which gives a very good, according to the authors, the criterion of Calmar (ratio of profit to capital najwiekzsego slips) about nearly 4.0.\\
+Chart is definitely a growth course with a maximum of 600 pips from falling, which gives a very good, according to the authors, the criterion of Calmar (ratio of maximum profit to maximum drawdown) nearly about 4.0.\\
 

### 2014-05-09 Article/Article20140406Granada/LatexArt/article_main.tex
Matlab-Metatrader comparision, Figures

@@
 
-It was also decided to test the effectiveness of the algorithm in terms of one candle 1h. The results are shown in Table \ref{tab:tab3} and Table \ref{tab:tab4}.
-
-\begin{table}[h!]
-\centering
-\caption{PerCandle EURUSD.}
-\label{tab:tab3}
-\begin{tabular}{|l|r|r|r|r|} \hline
-Learning\textbackslash Test &	8	 &	10 &		15	 &	20\\ \hline
-40 &		-2.207E-06 &		-6.443E-06 &		-1.219E-05 &		-5.641E-06\\ \hline
-60 &		3.695E-07 &		-1.327E-06 &		2.358E-06 &		1.425E-05\\ \hline
-80 &		-1.989E-06 &		8.427E-06	 &	\textbf{2.062E-05} &		5.3549E-06\\ \hline
-100	 &	2.465E-06 &		4.517E-06 &		-8.981E-07 &		1.571E-07\\ \hline
-\end{tabular}
-\end{table}
-\FloatBarrier
-
-\begin{table}[h!]
-\centering
-\caption{PerCandle GBPUSD.}
-\label{tab:tab4}
-\begin{tabular}{|l|r|r|r|r|} \hline
-Learning\textbackslash Test &	8	 & 	10 &		15	 &	20\\ \hline
-40	 & -2.949E-05 & 	1.457E-06 & 	-2.768E-05	 & -1.578E-05\\ \hline
-60	 & -2.289E-05 & 	-2.912E-05 & 	-1.250E-06 & 	-1.162E-05\\ \hline
-80	 & -3.043E-06 & 	-2.408E-05	 & \textbf{1.551E-05} & 	-1.780E-05\\ \hline
-100	 & -1.299E-05 & 	-1.228E-05 & 	-3.110E-06	 & -2.143E-05\\ \hline
-\end{tabular}
-\end{table}
-\FloatBarrier
-
 The best results are obtained in both cases (for both markets) for the ratio test to the learning period as 80/15.
@@
 To these results can be compared with each other, has been carried out their link, and the results were divided by the length of the test period, expressed by the number of candles.
-Figure \ref{fig:fig10} and Figure \ref{fig:fig11} present the results.
+Figure \ref{fig:fig10} present the results for EURUSD currency pair.
 
@@
 \begin{enumerate}
+\item for EURUSD currency pair using 1h candles values in time period of 2012.01.20 - 2013.01.01 in two different approches:
+\begin{itemize}
+\item with fixed parameters: $p1$=34, $p2$=4, $p3$=3, $p4$=-0.0060, $p5$=0.0060.
+Optimal parameters in that case were computed in Matlab for the first testing period and then were used for all testing periods.
+\item with dynamic parameters that were changed every testing period, regarding to their values computed in Matlab that were put to MetaTrader 
+\end{itemize}
+In both approaches following assumptions were done:
+\begin{itemize}
+\item spread was 0.00016, 
+\item initial deposit was 10000 EUR,
+\item size of the opening positions was 1 lot,
+\item each testing period lasted 15 candles.
+\end{itemize}
 \item for GBPUSD currency pair using 1h candles values in time period of 2013.01.09 - 2013.12.30 in two different approches:
 \begin{itemize}
-\item with fixed parameters: $p1$=27, $p2$=4, $p3$=1, $p4$=-0.0060, $p5$=0.0060 (Figure \ref{fig:fig10} and Figure \ref{fig:fig11}).
+\item with fixed parameters: $p1$=27, $p2$=4, $p3$=1, $p4$=-0.0060, $p5$=0.0060 (Figure \ref{fig:fig12} and Figure \ref{fig:fig13}).
 Optimal parameters in that case were computed in Matlab for the first testing period and then were used for all testing periods.
-\item with dynamic parameters that were changed every testing period, regarding to their values computed in Matlab that were put to MetaTrader (Figure \ref{fig:fig12} and Figure \ref{fig:fig13})
+\item with dynamic parameters that were changed every testing period, regarding to their values computed in Matlab that were put to MetaTrader (Figure \ref{fig:fig14} and Figure \ref{fig:fig13})
 \end{itemize}
@@
 \item initial deposit was 50000 EUR,
-\item size of the opening positions was 1 lot,
-\item each testing period lasted 15 candles.
-\end{itemize}
-\item for EURUSD currency pair using 1h candles values in time period of 2012.01.20 - 2013.01.01 in two different approches:
-\begin{itemize}
-\item with fixed parameters: $p1$=34, $p2$=4, $p3$=3, $p4$=-0.0060, $p5$=0.0060 (Figure \ref{fig:fig14} and Figure \ref{fig:fig15}) Optimal parameters in that case were computed in Matlab for the first testing period and then were used for all testing periods.
-\item with dynamic parameters that were changed every testing period, regarding to their values computed in Matlab that were put to MetaTrader (Figure \ref{fig:fig16} and Figure \ref{fig:fig17})
-\end{itemize}
-In both approaches following assumptions were done:
-\begin{itemize}
-\item spread was 0.00016, 
-\item initial deposit was 10000 EUR,
 \item size of the opening positions was 1 lot,

### 2014-05-09 Article/Article20140406Granada/LatexArt/article_main.tex
cites

@@
 The direction of further research will test the hypothesis that the variability periods to test the learner can improve the quality of prediction.
-This hypothesis seems to be interesting against the background of previous experiences and results, eg for different studied strategies, including \cite{Wilinski2014} obtained surprisingly different optimal length of periods of learning and testing.
-\cite{krutsinger}\cite{lewis}\cite{murphy}\cite{provost}\cite{wang}\cite{sinclare}\cite{person}\cite{tian}
+This hypothesis seems to be interesting against the background of previous experiences and results, eg for different studied strategies, including \cite{Wilinski2014}\cite{Wilinski}\cite{sinclare}\cite{krutsinger} obtained surprisingly different optimal length of periods of learning and testing.
 

### 2014-05-09 Article/Article20140406Granada/LatexArt/article_main.tex
corrections, todo: missing figure

@@
+% !TeX spellcheck = en_US
 \documentclass[runningheads,a4paper]{llncs}
@@
 \usepackage[utf8x]{inputenc}
+\usepackage{todonotes}
 
@@
 
-Algotrading is rapidly growing new form of trading on financial markets where investor (that makes decisions) is replaced with automaton (computer program) \cite{Leshik2011}\cite{Wilinski2014}.
-Such machine can perform operations (opening and closing positions, placing orders to open such positions that meet certain conditions) directly in an automated brokerage platform environment.
+Algotrading is new, rapidly growing form of trading on financial markets where investor (that makes decisions) is replaced with automaton (computer program) \cite{Leshik2011,Wilinski2014}.
+Such machine can perform operations (opening and closing positions, placing orders to open positions that meet certain conditions) directly in an automated brokerage platform environment.
 It may also be a recommendation system that helps investor with making correct decisions.\\
@@
 Such computer applications (bots) require carefully prepared and tested software that most often needs to adapt to the changing situations on the observed markets.
-Modern trends, in the development of this software, include sophisticated methods of: artificial intelligence, pattern recognition, classification and machine learning\cite{Leshik2011}\cite{Wilinski}\cite{wang}\cite{sinclare}.
-Those methods are interpenetrating and complementary and are also expanded with information based on fundamental analysis, for example, automatically extracted from the Internet \cite{elder}\cite{Wilinski2014}\cite{Schwager1996}.
+Modern trends, in the development of this software, include sophisticated methods of: artificial intelligence, pattern recognition, classification and machine learning \cite{Leshik2011,Wilinski,wang,sinclare}.
+Those methods are interpenetrating and complementary and are also expanded with information based on fundamental analysis, for example, automatically extracted from the Internet \cite{elder,Wilinski2014,Schwager1996}.
 Many strategies are based on relatively simple rules.
-Efficiency of this rules is amplified by using of machine learning\cite{Wilinski}\cite{person}\cite{tian}\cite{krutsinger}\cite{lewis}\cite{murphy}.\\
+Efficiency of these rules is amplified by using of machine learning \cite{Wilinski,person,tian,krutsinger,lewis,murphy}.\\
 
@@
 To use this software, it is necessary to make sure that there are reasonable premises of achieving the success.
-These conditions can be achieved through inductive thinking\cite{provost}\cite{KleskWilinski}, involving the assumption that multiple validation of decision on data from the past substantiates the correctness of the decision in the future.
+These conditions can be achieved through inductive thinking \cite{provost,KleskWilinski}, involving the assumption that multiple validation of decision on data from the past substantiates the correctness of the decision in the future.
 If a certain set of rules in the strategy used to seek the pattern, leads to the success then these rules are a pattern that is encouraged for repeated use.
-If repeated use of said pattern results in more successes than failures, then the basic premise to consider the use of the pattern is rational\cite{bishop2006pattern}\cite{KleskWilinski}.
+If repeated use of said pattern results in more successes than failures, then the basic premise to consider the use of the pattern is rational \cite{bishop2006pattern,KleskWilinski}.
 Unfortunately, changing market is causing the pattern to become outdated therefore it is necessary to constantly update it.
@@
 Therefore candles may be red (when the opening of the candle is higher than its closing $O_i>C_i$) and green (when the situation is opposite $O_i<C_i$).\\
-Let's also assume --- it is a primary strategy rule - that when an artificial earthworm has a significant advantage of red candles, a short position is opened or continued.
-When earthworm has the significant advantage of green candles, a long position is opened or continued.
+Let's also assume --- it is a primary strategy rule - that when an artificial earthworm has a significant dominance of red candles, a short position is opened or continued.
+When earthworm has the significant dominance of green candles, a long position is opened or continued.
 Imprecise term ,,significant'' is defined by the use of the second parameter $p2$ according to the rules:
@@
 \item earthworm knows how many candles it is composed with;
-\item after absorbing and discarding one candle, worms knows how many candles inside it are red or green and how to determine its status --- red, green or white;
+\item after absorbing and discarding one candle, worm knows how many candles inside it are red or green and how to determine its status --- red, green or white;
 \item knowing its status, earthworm knows how to make a decision about opening or continuing position; the opening of a position (long or short) means the simultaneous closing of the current position (opposite) if such position is opened;
@@
 \item worm also observes current course changes during  each next candle and reacts to unprofitable changes.
-If the current exchange rate causes a loss on the opened positions greater than $p5$ then the $SL$ mechanism is triggered --- the position is closed and to the end of the candle worm remains in the state without an open position.
+If the current exchange rate causes a loss on the opened positions greater than $p5$ then the $SL$ mechanism is triggered --- the position is closed and till the end of the candle worm remains in the state without an open position.
 $p5$ is therefore the fifth strategy parameter.
@@
 Data from testing period was not used during learning.\\
+\todo{CZY TEN RYSUNEK MA TU BYĆ? BO JEST ZAKOMENTOWANY ALE JEST DO NIEGO ODNIESIENIE W TEKŚCIE ???} 
 \begin{figure}[ht]
@@
 red when $O_{i-j}> C_{i-j}$, \\
-where $p1$ --- is the first parameter which is the length of the artificial worm - the number of candles of different colors that make up the ,,body'' of the worm; \\
+where $p1$ --- is the first parameter which is the length of the artificial worm --- the number of candles of different colors that make up the ,,body'' of the worm; \\
 $O_{i-j}$ --- is the opening value of (i-j)-th candle;\\ 
@@
 \begin{equation}
-\text{If } Lr>p1/2 – p2 \text {then Rr=1.}
+\text{If } Lr>p1/2 - p2 \text { then Rr=1.}
 \end{equation}
@@
 \begin{itemize}
-\item If as the result of the test the number of red and green candles in the body of the worm had not obtained any advantage from the color that would recommend to open defined position (worm was white), it is assumed to continue the position, which is open, without any cost of the transaction (with the value of $spread = 0$).
+\item If as the result of the test the number of red and green candles in the body of the worm had not obtained any dominance from the color that would recommend to open defined position (worm was white), it is assumed to continue the position, which is open, without any cost of the transaction (with the value of $spread = 0$).
 If at the beginning of the candle, at the time of checking the recommendation, there was no open position then it can be assumed to continue without any position.
@@
 \end{itemize}
-So, the above-described algorithm uses 5 parameters, as many as 3 of which are devoted to risk management of the strategy.\\
+So, the above-described algorithm uses 5 parameters and 3 of them are devoted to risk management of the strategy.\\
 %%PBStart
 The complexity of the algorithm is illustrated in Figure \ref{fig:fig7}, which shows the individual steps and decisions made in the iteration on a single candle in the form of a decision tree.
-This iteration was carried out both in the search for optimal parameters $p1, ..., p5$ and in the process they use in the testing phase for data not used in learning period.\\
+This iteration was carried out both in the search for optimal parameters $p1, ..., p5$ and in the process of testing the parameters on data that was not used in the learning period.
 \begin{figure}[h!]
@@
 \includegraphics[width = \textwidth]{figures/rys7.png}
-\caption{Decision tree for the states and decisions in one step (candle) in the learning phase and testing.}
+\caption{Decision tree for the states and decisions in one step (candle) in the learning nd testing phase.}
 \label{fig:fig7}
@@
 \FloatBarrier
-\vspace{-1em}
+
 The figure shows in a tree form further decisions taken at the beginning of the candle and then reactions to any unacceptable change in course.
-The first examines the state of the position taken over from the closure of the previous candle.
-The next step is to work out decisions / recommendations as to the direction of the opening from the set {long, short, none}.
-After opening position is observed return of the open position.
-It can be positive or negative.
-If it is positive, it does not take up any additional decisions.
-If it is negative, it checks if it is not achieved the level of $SL$.
-In the case of a negative return of the items, except for testing, $SL$ is not exceeded within a candle tested is also a condition resulting from the use of parameters ($p3$, $p4$).
-Tree is a state of complete items transmitted at the beginning of the next candle.
+The first step is to examine the state of the position which is taken from the closing of the previous one.
+The next step is to make decisions / recommendations as to the direction of the opening from the set \{long, short, none\}.
+After opening position  the return of the open position is observed --- it can be positive or negative.
+If it is positive, no any additional decisions are necessary.
+In the case of a negative return from the position both the level of $SL$ and a condition resulting from the use of parameters ($p3$, $p4$) are checked.
+The state at the end of tree is a beginning of the next candle.
 
-Described algorithm is implemented in the Matlab and using the MQL4 language of the Metatrader platform.
+Described algorithm was implemented in MATLAB environment and in Metatrader platform using the MQL4 language.
 The study was conducted both in the historical data (of course with the principles of machine learning --- testing was carried out using data not used in the learning phase) and a real ,,live'' market.
-Between the environments, there are also important differences that affect the diversity of simulation results.
+Between the environments, there are important differences that affect the diversity of simulation results.
 
 \section{The study of strategy}
-The study was conducted primarily on the basic EURUSD exchange rate at 1h candles.
-This market was chosen because of its popularity, a huge liquidity and also due to the possession by the authors many experiences in other machine learning strategy for this particular market such as \cite{Wilinski2014}\cite{Wilinski}.
+The study was conducted primarily on the basic currency pair EURUSD at 1h candles.
+This market was chosen because of its popularity, a huge liquidity and also due to the fact that the authors posses many experiences in other machine learning strategies for this particular market such as in \cite{Wilinski2014,Wilinski}.
 These experiments suggested initially, carrying out many tests with a long learning period, about 1000 candles, then 500 candles and testing time windows of 50 to 200 candles.
-All these attempts have proven to be very effective and led to continuing losses.
-After months of trying in many markets noted that over long periods of learning, eg the order of 1000 candles strategy variability is very large.
+All these attempts have proven to be ineffective and led to continuing losses.
+After months of tests in many markets it was noted that over long periods of learning, e.g.
+the order of 1000 candles, variability in parameters was very large.
 Therefore, the tests started with a decidedly shorter periods of learning and testing.\\
 
-Finally, the authors decided to present the results for the two markets - currency pairs EURUSD and GBPUSD sampled at 1h in machine learning aspect ratios matched to the reduced scope of both the learning phase and testing.\\
+Finally, the authors decided to present the results for the two markets --- currency pairs EURUSD and GBPUSD sampled at 1h --- in machine learning with ratios adjusted to the reduced scope of both the learning and testing phase.\\
 
@@
 Table \ref{tab:tab1} summarizes the results for different time periods.
-The study was conducted at approximately constant number of candles testing period, e.g.
-if the testing period was 10 candles, is to perform the test algorithm 1300 candles optimal parameters were calculated 130 times.
-If the testing period was 20 candles are the parameters were changed 65 times, etc., if it was available long test period is not used it.
+The study was conducted at approximately constant number of candles in testing period, e.g.
+if the testing period was 10 candles long, to perform the test on 1300 candles, optimal parameters were calculated 130 times.
+If the testing period was 20 candles long the parameters were changed 65 times, etc..
 
-The table shows that the best results were obtained for the ratio of the learning period to test period as 80/15.
-For this comparison periods was performed to study the market in EURUSD and shown in the Figure \ref{fig:fig8} For the 800 one hour candles the result 0.2401 (2401 pips) is obtained.
-Chart is definitely a growth course with a maximum of 600 pips from falling, which gives a very good, according to the authors, the criterion of Calmar (ratio of maximum profit to maximum drawdown) nearly about 4.0.\\
+The table shows that the best results were obtained for the learning to testing period ratio of 80/15.
+For this ratio tests were performed on the EURUSD market and shown in the Figure \ref{fig:fig8}.
+For the 800 one hour candles the result 0.2401 (2401 pips) is obtained.
+Chart is showing a growing course with a maximum fall of 600 pips, which gives a very good, according to the authors, the criterion of Calmar (ratio of maximum profit to maximum drawdown) nearly about $4.0$.\\
 
@@
 \centering
-\includegraphics[width = 0.6\textwidth]{figures/rys8.png}
+\includegraphics[width = 0.5\textwidth]{figures/rys8.png}
 \caption{Mileage accumulation of capital for 800 steps after 15 candles made of uses of the algorithm for the currency pair EURUSD 1h.}
@@
 \vspace{-1em}
-Tests were also made for another great importance and the currency pair GBPUSD 1h. Results for the currency pair are worse than for EURUSD, however, reaffirm the overall efficiency of the algorithm.\\
+Tests were also made for another great important currency pair GBPUSD sampled every 1h.
+Results for this currency pair are worse than for EURUSD, however, they reaffirm the overall efficiency of the algorithm.\\
 
-The best results are obtained in both cases (for both markets) for the ratio test to the learning period as 80/15.
-Result for EURUSD this means achievement of profit over 100 pips per month (approximately 550 hours of trading).
-This result is in terms of risk at Calmar ratio around 4 should be considered as engaging.\\
+The best results are obtained in both cases (for both markets) for the learning to testing period ratio of 80/15.
+Result for EURUSD means that the profit higher than 100 pips per month (approximately 550 hours of trading) was achieved.
+This result in terms of risk with Calmar ratio around 4 should be considered as engaging.\\
 
 In addition, effectiveness studies were carried out and optimized for different test periods.
-To these results can be compared with each other, has been carried out their link, and the results were divided by the length of the test period, expressed by the number of candles.
-Figure \ref{fig:fig10} present the results for EURUSD currency pair.
+For the purpose of comparison, the results were combined.
+Achieved results were divided by the length of the testing period (number of candles).
+
+Figure \ref{fig:fig10} presents the results for EURUSD currency pair.
 
@@
 \centering
-\includegraphics[width = 0.6\textwidth]{figures/rys10.png}
+\includegraphics[width = 0.5\textwidth]{figures/rys10.png}
 \caption{EURUSD Results per candle.}
@@
 
-From these results it can be concluded that the strategy is working with a short shelf life characteristics.
-The best results are achieved in periods of about 10-20 candles, it is unlike any other strategy presented in \cite{Wilinski2014} where the best results were achieved for the test periods with a length of 80-100 candles.\\
-All the above presented results refer to simulations in Matlab.
+From these results it can be concluded that the strategy is working with a short term duration characteristics.
+The best results were achieved in periods containing 10-20 candles --- unlike in any other strategy presented in \cite{Wilinski2014}, where the best results were achieved for the test periods with a length of 80-100 candles.\\
+All the results presented above refer to simulations conducted in MATLAB.
 %%PBStop
@@
 \section{Strategy Verification Using Online Trading Platform}
-From a conceptual point of view implementing automated trading strategies in Matlab environment is one of proper approaches.
-Matlab provides a number of features to rapidly prototype such algorithms, for e.g.
+From a conceptual point of view, implementing automated trading strategies in MATLAB environment is one of proper approaches.
+MATLAB provides a number of features to rapidly prototype such algorithms, for e.g.
 built-in computation functions and charting tools.
-What is more, Matlab enables also intuitive operations on vectors and matrices as well as flexible insight into variables values that are produced by the algorithm which greatly facilitates computing process management.\\
+What is more, MATLAB enables also intuitive operations on vectors and matrices as well as flexible insight into variables values that are produced by the algorithm which greatly facilitates computing process management.\\
 
-However in such approach it is very important to make sure that an algorithm that has been developed in Matlab can be used also regarding to real market conditions, which means a number of rules, validations and limitations, which obviously are not natively implemented in Matlab as it is just an open computing environment.\\
+However, in such approach, it is very important to make sure that an algorithm, that has been developed in MATLAB, can be used also regarding to real market conditions, which means a number of rules, validations and limitations, which obviously are not natively implemented in MATLAB, as it is just an open computing environment.\\
 
-To make sure that those market conditions are met in the algorithm, Matlab script was converted manually to MQL4 expert advisor for trading platform of MetaTrader 4, which platform is commonly used to perform the real market operations.\\
+To make sure that those market conditions are met in the algorithm, MATLAB script was converted manually to MQL4 expert advisor for trading platform of MetaTrader 4, which is commonly used to perform the real market operations.\\
 
-The main differences between the implementation of the artificial earthworm in Matlab and in MetaTrader are listed below:
+The main differences between the implementation of the artificial earthworm in MATLAB and in MetaTrader are listed below:
 \begin{itemize}
-\item Matlab
+\item MATLAB
 \begin{itemize}
@@
 
-In the article, implementation for MetaTrader4 has covered only the testing part of the algorithm, using fixed set of parameters that have been previously computed in Matlab in the learning part of execution for every test period.
-It is imporntat to note that implementing full algorithm, along with the learning part in MQL4, is obviously possible, however in that in the article the main objective was to confirm that the artificial worm can run on a real market with results similar to those achieved in Matlab.\\
+In the article, implementation for MetaTrader4 has covered only the testing part of the algorithm, using fixed set of parameters that have been previously computed in MATLAB in the learning part of execution for every test period.
+It is important to note that implementing full algorithm, along with the learning part in MQL4, is obviously possible, however in the article the main objective was to confirm that the artificial worm can run on a real market with results similar to those achieved in MATLAB.\\
 
-Below are presented balance comparisons in Matlab and MetaTrader environments:
+Below are presented balance comparisons in MATLAB and MetaTrader environments:
 \begin{enumerate}
-\item for EURUSD currency pair using 1h candles values in time period of 2012.01.20 - 2013.01.01 in two different approches:
+\item for EURUSD currency pair using 1h candles values in time period of 2012.01.20 - 2013.01.01 in two different approaches:
 \begin{itemize}
 \item with fixed parameters: $p1$=34, $p2$=4, $p3$=3, $p4$=-0.0060, $p5$=0.0060.
-Optimal parameters in that case were computed in Matlab for the first testing period and then were used for all testing periods.
-\item with dynamic parameters that were changed every testing period, regarding to their values computed in Matlab that were put to MetaTrader 
+Optimal parameters in that case were computed in MATLAB for the first testing period and then were used for all testing periods.
+\item with dynamic parameters that were changed every testing period, regarding to their values computed in MATLAB that were put to MetaTrader 
 \end{itemize}
@@
 \item with fixed parameters: $p1$=27, $p2$=4, $p3$=1, $p4$=-0.0060, $p5$=0.0060 (Figure \ref{fig:fig12} and Figure \ref{fig:fig13}).
-Optimal parameters in that case were computed in Matlab for the first testing period and then were used for all testing periods.
-\item with dynamic parameters that were changed every testing period, regarding to their values computed in Matlab that were put to MetaTrader (Figure \ref{fig:fig14} and Figure \ref{fig:fig13})
+Optimal parameters in that case were computed in MATLAB for the first testing period and then were used for all testing periods.
+\item with dynamic parameters that were changed every testing period, regarding to their values computed in MATLAB that were put to MetaTrader (Figure \ref{fig:fig14} and Figure \ref{fig:fig13})
 \end{itemize}
@@
 \begin{tabular}{|p{0.19\textwidth}|p{0.19\textwidth}|p{0.19\textwidth}|p{0.19\textwidth}|p{0.19\textwidth}|} \hline
- &  Total net profit in MetaTrader [EUR]	 &  Total net profit in Matlab 
+ &  Total net profit in MetaTrader [EUR]	 &  Total net profit in MATLAB 
 [EUR]	 &  Difference [EUR]	 &  Difference [\%]\\ \hline
@@
 \includegraphics[width = 0.9\textwidth]{figures/rys12.png}
-\subcaption{Balance (relative value) in Matlab.}
+\subcaption{Balance (relative value) in MATLAB.}
 \label{fig:fig12}
@@
 \vspace{-1em}
-It is important to note that every first chart from each pair above was done in Matlab and every second chart was done in MetaTrader.
-In Matlab chart context, every point of abscissa axis represents testing period, while on ordinate axis there is a result of testing period (relative value), so that it can be assumed that chart was done in time domain.
-On the other hand, every abscissa on MetaTrader chart represents each opening of position, which means that chart is not linear related with time (however in cases presented in the article it is really similar to time domain), so that chart begins with first position opening and it is denoised in comparison to Matlab chart as every line are determined by opening and closing position, no matter how long this position has lasted.
-Despite those differences, corellation between Matlab and MetaTrader charts for the artificial worm algorithm executions is indisputable.
+It is important to note that every first chart from each pair above was done in MATLAB and every second chart was done in MetaTrader.
+In MATLAB chart context, every point of abscissa axis represents testing period, while on ordinate axis there is a result of testing period (relative value), so that it can be assumed that chart was done in time domain.
+On the other hand, every abscissa on MetaTrader chart represents each opening of position, which means that chart is not linear related with time (however in cases presented in the article it is really similar to time domain), so that chart begins with first position opening and it is denoised in comparison to MATLAB chart as every line are determined by opening and closing position, no matter how long this position has lasted.
+Despite those differences, correlation between MATLAB and MetaTrader charts for the artificial worm algorithm executions is indisputable.
 \begin{figure}[h!]
@@
 \includegraphics[width = 0.9\textwidth]{figures/rys14.png}
-\subcaption{Balance (relative value) in Matlab.}
+\subcaption{Balance (relative value) in MATLAB.}
 \label{fig:fig14}
@@
 It should be emphasized that the study was conducted on data not used in the learning phase and for the basic principle of machine learning achieved results that would have satisfied many a practice.
-It should also be noted that outside research conducted in environment completely specified (for constant unchanging data stored in Matlab) was also performed simulations in terms of actual brokerage platform.
-The results obtained in both environments are similar in the sense of direction changes and logic behavior caused by the user received by the algorithm implemented in the Matlab and Metatrader.
+It should also be noted that outside research conducted in environment completely specified (for constant unchanging data stored in MATLAB) was also performed simulations in terms of actual brokerage platform.
+The results obtained in both environments are similar in the sense of direction changes and logic behavior caused by the user received by the algorithm implemented in the MATLAB and MetaTrader.
 Differences explained in this work.

### 2014-05-09 Article/Article20140406Granada/LatexArt/article_main.tex
nd -> and
missing fig.

@@
 Data from testing period was not used during learning.\\
-\todo{CZY TEN RYSUNEK MA TU BYĆ? BO JEST ZAKOMENTOWANY ALE JEST DO NIEGO ODNIESIENIE W TEKŚCIE ???} 
 \begin{figure}[ht]
 \centering
-%\includegraphics[width = 0.6\textwidth]{figures/rys2.png}
+\includegraphics[width = 0.6\textwidth]{figures/rys2.png}
 \caption{An example of the arrangement of learning and testing periods of strategy parameters in time series.}
@@
 \includegraphics[width = \textwidth]{figures/rys7.png}
-\caption{Decision tree for the states and decisions in one step (candle) in the learning nd testing phase.}
+\caption{Decision tree for the states and decisions in one step (candle) in the learning and testing phase.}
 \label{fig:fig7}

### 2014-05-10 Article/Article20140406Granada/LatexArt/article_main.tex
(the last one)

@@
 Let this artificial worm have a length of $p1$ candles (vectors representing the knowledge about events occurring within the contractual part of the time series).
-Let her movement come down to the successive ,,eating'' one candle and simultaneous ,,discarding'' of one candle --- always having $p1$ candles.
+Let her movement come down to the successive ,,eating'' one candle and simultaneous ,,discarding'' of one candle (the last one) --- always having $p1$ candles.
 Thus the earthworm moves incrementally at length of time called the period of the candle.

### 2014-05-10 Article/Article20140406Granada/LatexArt/article_main.tex
intellect
i-j italic

@@
 
-Earthworm is therefore supplied with artificial intelligence, which allows the accumulation of knowledge and decision-making:
+Earthworm is therefore supplied with artificial intellect, which allows the accumulation of knowledge and decision-making:
 \begin{itemize}
@@
 \begin{itemize}
-\item For each $i = p1, p1 +1, p1 +2, ..., I$ and for $j = 1, ..., p1$ check whether the candle located at a distance i-j backwards from the current candle is:\\
+\item For each $i = p1, p1 +1, p1 +2, ..., I$ and for $j = 1, ..., p1$ check whether the candle located at a distance $i-j$ backwards from the current candle is:\\
 green when $O_{i-j} <C_{i-j}$, \\

### 2014-05-10 Article/Article20140406Granada/LatexArt/article_main.tex
PositionState ==none,   from \{$long, short, none$\}

@@
 \end{itemize}
-If this condition is fulfilled, then depending on the current position status $PositionState$ (where $PositionState$ is a variable which takes values {long, short, 0}) at the opening of the next candle, a position is opened or continued as follows:
+If this condition is fulfilled, then depending on the current position status $PositionState$ (where $PositionState$ is a variable which takes values from \{$long, short, none$\}) at the opening of the next candle, a position is opened or continued as follows:
 \begin{equation}
@@
 \begin{equation}
-\text{If } Rg=1 \text{ and } PositionState =0 \text{ then } PositionState =long;
+\text{If } Rg=1 \text{ and } PositionState =none \text{ then } PositionState =long;
 \end{equation}
@@
 \begin{equation}
-\text{If } Rr==1 \text{ and }  PositionState ==0 \text{ then }  PositionState =short;
+\text{If } Rr==1 \text{ and }  PositionState ==none \text{ then }  PositionState =short;
 \end{equation}

### 2014-05-10 Article/Article20140406Granada/LatexArt/article_main.tex
italic H_i
for the first of the currency pairs

@@
 \end{equation}
-where Hi --– the highest rate value in the $i-th$ candle.
+where $H_i$ --– the highest rate value in the $i-th$ candle.
 \end{itemize}
@@
 \begin{equation}
-Zc_i = sum ( Z_i ) \text{ from } i = 1 \text{ to the current i value;}
+Zc_i = sum ( Z_i ) \text{ from } i = 1 \text{ to the current } i \text{ value;}
 \end{equation}
@@
 \FloatBarrier
-Table \ref{tab:tab1} summarizes the results for different time periods.
+Table \ref{tab:tab1} summarizes the results for different time periods for the first of the currency pairs.
 The study was conducted at approximately constant number of candles in testing period, e.g.

### 2014-05-10 Article/Article20140406Granada/LatexArt/article_main.tex
long -> duration
deleted some text and 2 \vspace{-1em}

@@
 The study was conducted at approximately constant number of candles in testing period, e.g.
-if the testing period was 10 candles long, to perform the test on 1300 candles, optimal parameters were calculated 130 times.
+if the testing period was 10 candles duration, to perform the test on 1300 candles, optimal parameters were calculated 130 times.
 If the testing period was 20 candles long the parameters were changed 65 times, etc..
@@
 \FloatBarrier
-\vspace{-1em}
 Tests were also made for another great important currency pair GBPUSD sampled every 1h.
@@
 The best results are obtained in both cases (for both markets) for the learning to testing period ratio of 80/15.
-Result for EURUSD means that the profit higher than 100 pips per month (approximately 550 hours of trading) was achieved.
-This result in terms of risk with Calmar ratio around 4 should be considered as engaging.\\
+Result for EURUSD means that the profit higher than 100 pips per month (approximately 550 hours of trading) was achieved.\\
 
@@
 Figure \ref{fig:fig10} presents the results for EURUSD currency pair.
+
+From these results it can be concluded that the strategy is working with a short term duration characteristics.
+The best results were achieved in periods containing 10-20 candles --- unlike in any other strategy presented in \cite{Wilinski2014}, where the best results were achieved for the test periods with a length of 80-100 candles.\\
+All the results presented above refer to simulations conducted in MATLAB.
 
@@
 \FloatBarrier
-\vspace{-1em}
-
-From these results it can be concluded that the strategy is working with a short term duration characteristics.
-The best results were achieved in periods containing 10-20 candles --- unlike in any other strategy presented in \cite{Wilinski2014}, where the best results were achieved for the test periods with a length of 80-100 candles.\\
-All the results presented above refer to simulations conducted in MATLAB.
 %%PBStop

### 2014-05-10 Article/Article20140406Granada/LatexArt/article_main.tex
were
Mileage accumulation of capital for horizon of 800 steps for the currency pair EURUSD 1h. This horizon was divided into sections with

@@
 \includegraphics[width = 0.5\textwidth]{figures/rys8.png}
-\caption{Mileage accumulation of capital for 800 steps after 15 candles made of uses of the algorithm for the currency pair EURUSD 1h.}
+\caption{Mileage accumulation of capital for horizon of 800 steps for the currency pair EURUSD 1h.
+This horizon was divided into sections with constant parameter values.
+Test sections were preceded by learning sections with a length of 80 steps.}
 \label{fig:fig8}
@@
 The results obtained in both environments are similar in the sense of direction changes and logic behavior caused by the user received by the algorithm implemented in the MATLAB and MetaTrader.
-Differences explained in this work.
+Differences were explained in this work.
 The direction of further research will test the hypothesis that the variability periods to test the learner can improve the quality of prediction.

### 2014-05-11 Article/Article20140406Granada/LatexArt/article_main.tex
change figure position
mileage deleted
Abstract

@@
 \begin{abstract}
-This paper presents an innovative concept of investment strategy derived from the general ideas of artificial intelligence.
-The strategy has been tested in a number of simulations on historical data and on data outside learning periods.
-Tests were performed mainly in the selected currency markets, including the primary currency pair EURUSD.
-Presented approach opens long and short positions alternately during the closing of actual candles.
-Closing of position is based on recommendation which is deduced from changes in characteristics of time series.
-The strategy has parameters that vary through time, and are adapted to the market changes.
-To present the strategy, a metaphor of an innovative artificial earthworm, that feeds on a time series, was used.
-The earthworm has its own artificial intelligence which allows it to analyse ,,consumed'' candles, change its preferences about movement direction or to stay in neutral state.
+The paper presents an innovative concept of investment strategy derived from the general ideas of artificial intelligence.
+The strategy has been tested in a number of simulations on historical data as well as data outside learning periods.
+Tests were performed mainly in the selected currency markets, including the primary currency pair of EURUSD.
+Presented approach opens long and short positions alternately during candle closing events.
+Closing a position is based on recommendation which is deduced from changes in characteristics of time series.
+The strategy has parameters that vary through time and are adapted to a market changes.
+To present the strategy a metaphor of an innovative artificial earthworm that feeds on a time series was used.
+The earthworm has its own artificial intelligence which enables it to analyse ,,consumed'' candles, change its preferences about movement direction or to stay in neutral state.
 The goal was to implement presented strategy for trading platform to achieve the automatic trading effect.
 The strategy was tested in two development environments --- MATLAB environment and trading platform MetaTrader after conversion of M-file into MQL4 file.
-Implemented strategy allows to achieve interesting results.
+Implemented strategy enables to achieve interesting results.
 \keywords{investment strategy, machine learning, forecasting, time series, algotrading, mql4}
@@
 \includegraphics[width = 0.5\textwidth]{figures/rys8.png}
-\caption{Mileage accumulation of capital for horizon of 800 steps for the currency pair EURUSD 1h.
+\caption{Accumulation of capital for horizon of 800 steps for the currency pair EURUSD 1h.
 This horizon was divided into sections with constant parameter values.
@@
 Results for this currency pair are worse than for EURUSD, however, they reaffirm the overall efficiency of the algorithm.\\
+
+\begin{figure}[h!]
+\centering
+\includegraphics[width = 0.5\textwidth]{figures/rys10.png}
+\caption{EURUSD Results per candle.}
+\label{fig:fig10}
+\end{figure}
+\FloatBarrier
 
@@
 Figure \ref{fig:fig10} presents the results for EURUSD currency pair.
-
 From these results it can be concluded that the strategy is working with a short term duration characteristics.
@@
 
-\begin{figure}[h!]
-\centering
-\includegraphics[width = 0.5\textwidth]{figures/rys10.png}
-\caption{EURUSD Results per candle.}
-\label{fig:fig10}
-\end{figure}
-\FloatBarrier
 %%PBStop

### 2014-05-11 Article/Article20140406Granada/LatexArt/article_main.tex
Introduction

@@
 
-Algotrading is new, rapidly growing form of trading on financial markets where investor (that makes decisions) is replaced with automaton (computer program) \cite{Leshik2011,Wilinski2014}.
+Algotrading is a new rapidly growing form of trading on financial markets where investor (that makes decisions) is replaced with trading bot (computer program) \cite{Leshik2011,Wilinski2014}.
 Such machine can perform operations (opening and closing positions, placing orders to open positions that meet certain conditions) directly in an automated brokerage platform environment.
-It may also be a recommendation system that helps investor with making correct decisions.\\
+It may also occur as a recommendation system that helps investor with making correct decisions.\\
 
@@
 Modern trends, in the development of this software, include sophisticated methods of: artificial intelligence, pattern recognition, classification and machine learning \cite{Leshik2011,Wilinski,wang,sinclare}.
-Those methods are interpenetrating and complementary and are also expanded with information based on fundamental analysis, for example, automatically extracted from the Internet \cite{elder,Wilinski2014,Schwager1996}.
+Those methods are interpenetrating and complementary and are also expanded with information based on fundamental analysis e.g.
+automatically extracted from the Internet \cite{elder,Wilinski2014,Schwager1996}.
 Many strategies are based on relatively simple rules.
@@
 
-Strategy presented in this paper is an example of a solution that can be used fully automated or with investor’s assistance, who makes the decision manually.
-To use this software, it is necessary to make sure that there are reasonable premises of achieving the success.
+Strategy presented in this paper is an example of a solution that can be used fully automatically or with assistance of investor who makes the decision manually.
+Using such softwaremakes sense only if there are reasonable premises of achieving the success.
 These conditions can be achieved through inductive thinking \cite{provost,KleskWilinski}, involving the assumption that multiple validation of decision on data from the past substantiates the correctness of the decision in the future.
 If a certain set of rules in the strategy used to seek the pattern, leads to the success then these rules are a pattern that is encouraged for repeated use.
-If repeated use of said pattern results in more successes than failures, then the basic premise to consider the use of the pattern is rational \cite{bishop2006pattern,KleskWilinski}.
+If repeated use of mentioned pattern results in more successes than failures, then the basic premise to consider the use of the pattern is rational \cite{bishop2006pattern,KleskWilinski}.
 Unfortunately, changing market is causing the pattern to become outdated therefore it is necessary to constantly update it.
-Search in the historical patterns, that could be effective in the data space not used for their determination (to identify these patterns), is a major challenge also applied in machine learning which is used in this paper.
-The article is organized as follows: at first authors describe an authored strategy based on an entirely innovative, according to the authors, concept of an artificial worm.
+Finding historically effective patterns that could be also effective in a data space not used for their determination (to identify these patterns) is a major challenge for machine learning which is applied in the paper.
+The article is organized as follows: at first authors describe an authored strategy based on an entirely innovative concept of an artificial worm.
 Subsequently extensive studies of effectiveness of presented strategy in terms of prediction and the aspect of investment are carried out.

### 2014-05-11 Article/Article20140406Granada/LatexArt/article_main.tex
worm->earthworm

@@
 Finding historically effective patterns that could be also effective in a data space not used for their determination (to identify these patterns) is a major challenge for machine learning which is applied in the paper.
-The article is organized as follows: at first authors describe an authored strategy based on an entirely innovative concept of an artificial worm.
+The article is organized as follows: at first authors describe an authored strategy based on an entirely innovative concept of an artificial earthworm.
 Subsequently extensive studies of effectiveness of presented strategy in terms of prediction and the aspect of investment are carried out.
@@
 \section{Strategy characteristics}
-In presented strategy, a metaphorical procedure is often used to explain heuristic algorithms of artificial intelligence. Said procedure is a reference to an inspiration derived from the nature.\\
+In presented strategy, a metaphorical procedure is often used to explain heuristic algorithms of artificial intelligence. The procedure is a reference to an inspiration derived from the nature.\\
 
 Let's consider an artificial earthworm, which behaves like its natural inspirer.
-Let this artificial worm have a length of $p1$ candles (vectors representing the knowledge about events occurring within the contractual part of the time series).
-Let her movement come down to the successive ,,eating'' one candle and simultaneous ,,discarding'' of one candle (the last one) --- always having $p1$ candles.
+Let this artificial earthworm have a length of $p1$ candles (vectors representing the knowledge about events occurring within the contractual part of the time series).
+Let its movement come down to the successive ,,eating'' one candle and simultaneous ,,discarding'' of one candle (the last one) --- always having $p1$ candles.
 Thus the earthworm moves incrementally at length of time called the period of the candle.
@@
 These values represent (in order): the value at the beginning of this period, the maximum value within the period, the minimum and the closing values - at the end of the candle.\\
-Let's assume that candle can have color (often in a number of brokerage platforms, this approach is used).
+Let's assume that candle have a color (often in a number of brokerage platforms such approach is used).
 Therefore candles may be red (when the opening of the candle is higher than its closing $O_i>C_i$) and green (when the situation is opposite $O_i<C_i$).\\
-Let's also assume --- it is a primary strategy rule - that when an artificial earthworm has a significant dominance of red candles, a short position is opened or continued.
+Let's also assume --- it is a primary strategy rule - that when the artificial earthworm has a significant dominance of red candles, a short position is opened or continued.
 When earthworm has the significant dominance of green candles, a long position is opened or continued.
@@
 
-In the rules above $Lr$ and $Lg$ are the number of candles, respectively ,,red'' and ,,green'' in the worm of $p1$ length, wherein $p1 = Lr + Lg$.\\
-When dominance determined by another parameter $p2$ is undecided, as in (\ref{eq:eq3}), then worm takes the color white and the position will not be opened.
-When the worm continues to open position, investor does not incur costs.
+In the rules above $Lr$ and $Lg$ are the number of candles, respectively ,,red'' and ,,green'' in the earthworm of $p1$ length, wherein $p1 = Lr + Lg$.\\
+When dominance determined by another parameter $p2$ is undecided, as in (\ref{eq:eq3}), then earthworm takes the color white and the position will not be opened.
+When the earthworm continues to open position, investor does not incur costs.
 On many platforms, also in literature, symbolic marking of growing candles in white and decreasing in black is used.
@@
 \begin{itemize}
-\item right after closing of the current candle, worm ,,swallows'' the candle and ,,knows'' what color is it;
+\item right after closing of the current candle, earthworm ,,swallows'' the candle and ,,knows'' what color is it;
 \item earthworm knows how many candles it is composed with;
-\item after absorbing and discarding one candle, worm knows how many candles inside it are red or green and how to determine its status --- red, green or white;
+\item after absorbing and discarding one candle, earthworm knows how many candles inside it are red or green and how to determine its status --- red, green or white;
 \item knowing its status, earthworm knows how to make a decision about opening or continuing position; the opening of a position (long or short) means the simultaneous closing of the current position (opposite) if such position is opened;
@@
 If it is exceeded, the $SL$ (Stop Loss --- closes the currently open position) mechanism is activated;
-\item worm also observes current course changes during  each next candle and reacts to unprofitable changes.
-If the current exchange rate causes a loss on the opened positions greater than $p5$ then the $SL$ mechanism is triggered --- the position is closed and till the end of the candle worm remains in the state without an open position.
+\item earthworm also observes current course changes during  each next candle and reacts to unprofitable changes.
+If the current exchange rate causes a loss on the opened positions greater than $p5$ then the $SL$ mechanism is triggered --- the position is closed and till the end of the candle earthworm remains in the state without an open position.
 $p5$ is therefore the fifth strategy parameter.
@@
 
-These features of the worm's intelligence may be extended, however, for this work they were limited to the foregoing. \\
+These features of the earthworm's intelligence may be extended, however, for this work they were limited to the foregoing. \\
 
@@
 red when $O_{i-j}> C_{i-j}$, \\
-where $p1$ --- is the first parameter which is the length of the artificial worm --- the number of candles of different colors that make up the ,,body'' of the worm; \\
+where $p1$ --- is the first parameter which is the length of the artificial earthworm --- the number of candles of different colors that make up the ,,body'' of the earthworm; \\
 $O_{i-j}$ --- is the opening value of (i-j)-th candle;\\ 
@@
 In formulas above there is a parameter $p2$.
-It is the second parameter of the strategy which is an arbitrarily separated part of the worm, which depending on size causes the direction of investment not to change.
+It is the second parameter of the strategy which is an arbitrarily separated part of the earthworm, which depending on size causes the direction of investment not to change.
 Large $p2$ causes long positions to change into short positions (or vice-versa) rarely.
@@
 \begin{itemize}
-\item If as the result of the test the number of red and green candles in the body of the worm had not obtained any dominance from the color that would recommend to open defined position (worm was white), it is assumed to continue the position, which is open, without any cost of the transaction (with the value of $spread = 0$).
+\item If as the result of the test the number of red and green candles in the body of the earthworm had not obtained any dominance from the color that would recommend to open defined position (earthworm was white), it is assumed to continue the position, which is open, without any cost of the transaction (with the value of $spread = 0$).
 If at the beginning of the candle, at the time of checking the recommendation, there was no open position then it can be assumed to continue without any position.
@@
 This way $p5$ parameter was used for securing in strategy the strong local changes in exchange rate within a single candle.\\
-The meaning of $p5$ parameter to the behavior of the worm and the occurrence of the closing position is explained in Figure \ref{fig:fig5}.
+The meaning of $p5$ parameter to the behavior of the earthworm and the occurrence of the closing position is explained in Figure \ref{fig:fig5}.
 \begin{figure}[h!]
@@
 In the article, implementation for MetaTrader4 has covered only the testing part of the algorithm, using fixed set of parameters that have been previously computed in MATLAB in the learning part of execution for every test period.
-It is important to note that implementing full algorithm, along with the learning part in MQL4, is obviously possible, however in the article the main objective was to confirm that the artificial worm can run on a real market with results similar to those achieved in MATLAB.\\
+It is important to note that implementing full algorithm, along with the learning part in MQL4, is obviously possible, however in the article the main objective was to confirm that the artificial earthworm can run on a real market with results similar to those achieved in MATLAB.\\
 
@@
 On the other hand, every abscissa on MetaTrader chart represents each opening of position, which means that chart is not linear related with time (however in cases presented in the article it is really similar to time domain), so that chart begins with first position opening and it is denoised in comparison to MATLAB chart as every line are determined by opening and closing position, no matter how long this position has lasted.
-Despite those differences, correlation between MATLAB and MetaTrader charts for the artificial worm algorithm executions is indisputable.
+Despite those differences, correlation between MATLAB and MetaTrader charts for the artificial earthworm algorithm executions is indisputable.
 \begin{figure}[h!]

### 2014-05-12 Article/Article20140406Granada/LatexArt/article_main.tex
3rd & 4th section

@@
 
-Earthworm is therefore supplied with artificial intellect, which allows the accumulation of knowledge and decision-making:
+The earthworm is therefore supplied with artificial intellect which enables the accumulation of knowledge and decision-making:
 \begin{itemize}
@@
 The strategy is built on the principle of classical machine learning.
-Before starting to run the algorithm, on data located outside the environment that investor knows (like on the current market segments --- out-of-sample), it is necessary to ,,teach''  the values of parameters.
+Before starting to run the algorithm on data located outside the scope that investor knows (like on the current market segments --- out-of-sample), it is necessary to ,,teach''  the values of parameters.
 This principle is presented in Figure \ref{fig:fig2}, which shows examples of learning periods and following them testing periods.
@@
 \vspace{-1em}
-This repeatable algorithm, located in both periods - learning and testing, has the following structure.
-In learning period the optimal value for five parameters $p1$, $p2$, ..., $p5$ was determined.
-In test period these designated values of parameters were used to perform the algorithm in the new environment.
-In each $i-th$ step (candle) of time series following activities were performed:
+This repeatable algorithm located in both periods - learning and testing - has the following structure.
+In learning period the optimal value for five parameters $p1$, $p2$, ..., $p5$ is determined.
+In test period these designated values of parameters are used to perform the algorithm in the new environment.
+In each $i-th$ step (candle) of time series following activities are performed:
 \begin{itemize}
@@
 $I$ --- is the length of the test window, after which it is necessary to change the parameters values to the new, learned in the machine learning phase;\\
-\item In each $i-th$ step, the loop $j = 1, ..., p1$ is performed in which a number of green $Lg$, red $Lr$ candles is calculated so the sum of $Lg$ and $Lr$ is $p1$ (to avoid the situation when $O_i = C_i$, it is assigned arbitrarily to one of the candles sets, for example green);
+\item In each $i-th$ step, the loop $j = 1, ..., p1$ is performed in which a number of green $Lg$, red $Lr$ candles is calculated so the sum of $Lg$ and $Lr$ is $p1$ (to avoid the situation when $O_i = C_i$ is an arbitrary assignation to one of the candles sets e.g.
+green);
 \item A condition for the existence of a $Rg$ recommendation to open a long position (or to continue it if it is open) is checked.
@@
 
-\section{The study of strategy}
+\section{Strategy studies}
 The study was conducted primarily on the basic currency pair EURUSD at 1h candles.
@@
 
-\section{Strategy Verification Using Online Trading Platform}
-From a conceptual point of view, implementing automated trading strategies in MATLAB environment is one of proper approaches.
-MATLAB provides a number of features to rapidly prototype such algorithms, for e.g.
+\section{Strategy verification using online trading platform}
+From a conceptual point of view implementing automated trading strategies in MATLAB environment is one of proper approaches.
+MATLAB provides a number of features to rapidly prototype such algorithms, e.g.
 built-in computation functions and charting tools.
@@
 
-However, in such approach, it is very important to make sure that an algorithm, that has been developed in MATLAB, can be used also regarding to real market conditions, which means a number of rules, validations and limitations, which obviously are not natively implemented in MATLAB, as it is just an open computing environment.\\
+However in such approach it is very important to make sure that an algorithm that has been developed in MATLAB could be used also regarding to real market conditions which means a number of rules, validations and limitations which obviously are not natively implemented in MATLAB as it is just an generic computing environment.\\
 
-To make sure that those market conditions are met in the algorithm, MATLAB script was converted manually to MQL4 expert advisor for trading platform of MetaTrader 4, which is commonly used to perform the real market operations.\\
+To make sure that those market conditions are met in the algorithm MATLAB script was converted manually to MQL4 expert advisor for trading platform of MetaTrader 4 which is commonly used to perform the real market operations.\\
 
@@
 
-In the article, implementation for MetaTrader4 has covered only the testing part of the algorithm, using fixed set of parameters that have been previously computed in MATLAB in the learning part of execution for every test period.
+In the paper MetaTrader4, implementation for  has covered only the testing part of the algorithm using fixed set of parameters that have been previously computed in MATLAB in the learning part of execution for every test period.
 It is important to note that implementing full algorithm, along with the learning part in MQL4, is obviously possible, however in the article the main objective was to confirm that the artificial earthworm can run on a real market with results similar to those achieved in MATLAB.\\

### 2014-05-12 Article/Article20140406Granada/LatexArt/article_main.tex
Conclusion

@@
 
-Presented in the paper the concept of an innovative investment strategy gave satisfactory results for a certain pair as the result of periods of machine learning.
-For example, in the studied data for two key market currency pairs sampled every hour, the best value is 80 hours of teaching and 15 hours of testing.
+The concept of an innovative investment strategy gave satisfactory results for a certain pair as the result of periods of machine learning.
+E.g.
+in the studied data for two key market currency pairs sampled every hour, the best value is 80 hours of teaching and 15 hours of testing.
 One can assume that this relationship may change in a different environment (for other markets, for other periods) by becoming a sort of next parameter that optimal values should be sought.

### 2014-05-12 Article/Article20140406Granada/LatexArt/article_main.tex
Title

@@
 % first the title is needed
-\title{The investment strategy based on behavior of artificial earthworm for use in algotrading}
+\title{Investment Strategy Based on Artificial Earthworm Behavior for Algotrading Application}
 
 % a short form should be given in case it is too long for the running head
-\titlerunning{The investment strategy based on behavior of artificial earthworm}
+\titlerunning{Investment Strategy Based on Artificial Earthworm Behavior}
 

### 2014-05-12 Article/Article20140406Granada/LatexArt/article_main.tex
przeniesienia do nowych linii: and, or....

@@
 
-\mainmatter  % start of an individual contribution
+\mainmatter  % start of~an individual contribution
 
@@
 
-% the name(s) of the author(s) follow(s) next
+% the name(s) of~the author(s) follow(s) next
 %
@@
 % their surnames. This ensures that the names appear correctly in
-% the running heads and the author index.
+% the running heads and~the author index.
 %
@@
 % unless you accept that it will be published
-\institute{West Pomeranian University of Technology, Faculty of Computer Science,\\
+\institute{West Pomeranian University of~Technology, Faculty of~Computer Science,\\
 Zolnierska 49, 71210 Szczecin, Poland\\
@@
 %
-% NB: a more complex sample for affiliations and the mapping to the
+% NB: a more complex sample for affiliations and~the mapping to the
 % corresponding authors can be found in the file "llncs.dem"
@@
 
-\toctitle{The investment strategy based on behavior of artificial earthworm for use in algotrading}
+\toctitle{The investment strategy based on behavior of~artificial earthworm for use in algotrading}
 \tocauthor{Antoni Wilinski}
@@
 \begin{abstract}
-The paper presents an innovative concept of investment strategy derived from the general ideas of artificial intelligence.
-The strategy has been tested in a number of simulations on historical data as well as data outside learning periods.
-Tests were performed mainly in the selected currency markets, including the primary currency pair of EURUSD.
-Presented approach opens long and short positions alternately during candle closing events.
-Closing a position is based on recommendation which is deduced from changes in characteristics of time series.
-The strategy has parameters that vary through time and are adapted to a market changes.
-To present the strategy a metaphor of an innovative artificial earthworm that feeds on a time series was used.
-The earthworm has its own artificial intelligence which enables it to analyse ,,consumed'' candles, change its preferences about movement direction or to stay in neutral state.
-The goal was to implement presented strategy for trading platform to achieve the automatic trading effect.
-The strategy was tested in two development environments --- MATLAB environment and trading platform MetaTrader after conversion of M-file into MQL4 file.
+The paper presents an innovative concept of~investment strategy derived from the~general ideas of~artificial intelligence.
+The strategy has been tested in a~number of~simulations on historical data as well as data outside learning periods.
+Tests were performed mainly in the~selected currency markets, including the~primary currency pair of~EURUSD.
+Presented approach opens long and~short positions alternately during candle closing events.
+Closing a~position is based on recommendation which is deduced from changes in characteristics of~time series.
+The strategy has parameters that vary through time and~are adapted to a~market changes.
+To present the~strategy a~metaphor of~an innovative artificial earthworm that feeds on a~time series was used.
+The earthworm has its own artificial intelligence which enables it to analyse ,,consumed'' candles, change its preferences about movement direction or~to stay in neutral state.
+The goal was to implement presented strategy for trading platform to achieve the~automatic trading effect.
+The strategy was tested in two development environments --- MATLAB environment and~trading platform MetaTrader after conversion of~M-file into MQL4 file.
 Implemented strategy enables to achieve interesting results.
@@
 
-Algotrading is a new rapidly growing form of trading on financial markets where investor (that makes decisions) is replaced with trading bot (computer program) \cite{Leshik2011,Wilinski2014}.
-Such machine can perform operations (opening and closing positions, placing orders to open positions that meet certain conditions) directly in an automated brokerage platform environment.
-It may also occur as a recommendation system that helps investor with making correct decisions.\\
+Algotrading is a~new rapidly growing form of~trading on financial markets where investor (that makes decisions) is replaced with trading bot (computer program) \cite{Leshik2011,Wilinski2014}.
+Such machine can perform operations (opening and~closing positions, placing orders to open positions that meet certain conditions) directly in an automated brokerage platform environment.
+It may also occur as a~recommendation system that helps investor with making correct decisions.\\
 
-Such computer applications (bots) require carefully prepared and tested software that most often needs to adapt to the changing situations on the observed markets.
-Modern trends, in the development of this software, include sophisticated methods of: artificial intelligence, pattern recognition, classification and machine learning \cite{Leshik2011,Wilinski,wang,sinclare}.
-Those methods are interpenetrating and complementary and are also expanded with information based on fundamental analysis e.g.
-automatically extracted from the Internet \cite{elder,Wilinski2014,Schwager1996}.
+Such computer applications (bots) require carefully prepared and~tested software that most often needs to adapt to the~changing situations on the~observed markets.
+Modern trends, in the~development of~this software, include sophisticated methods of: artificial intelligence, pattern recognition, classification and~machine learning \cite{Leshik2011,Wilinski,wang,sinclare}.
+Those methods are interpenetrating and~complementary and~are also expanded with information based on fundamental analysis e.g.
+automatically extracted from the~Internet \cite{elder,Wilinski2014,Schwager1996}.
 Many strategies are based on relatively simple rules.
-Efficiency of these rules is amplified by using of machine learning \cite{Wilinski,person,tian,krutsinger,lewis,murphy}.\\
+Efficiency of~these rules is amplified by~using of~machine learning \cite{Wilinski,person,tian,krutsinger,lewis,murphy}.\\
 
-Strategy presented in this paper is an example of a solution that can be used fully automatically or with assistance of investor who makes the decision manually.
-Using such softwaremakes sense only if there are reasonable premises of achieving the success.
-These conditions can be achieved through inductive thinking \cite{provost,KleskWilinski}, involving the assumption that multiple validation of decision on data from the past substantiates the correctness of the decision in the future.
-If a certain set of rules in the strategy used to seek the pattern, leads to the success then these rules are a pattern that is encouraged for repeated use.
-If repeated use of mentioned pattern results in more successes than failures, then the basic premise to consider the use of the pattern is rational \cite{bishop2006pattern,KleskWilinski}.
-Unfortunately, changing market is causing the pattern to become outdated therefore it is necessary to constantly update it.
-Finding historically effective patterns that could be also effective in a data space not used for their determination (to identify these patterns) is a major challenge for machine learning which is applied in the paper.
-The article is organized as follows: at first authors describe an authored strategy based on an entirely innovative concept of an artificial earthworm.
-Subsequently extensive studies of effectiveness of presented strategy in terms of prediction and the aspect of investment are carried out.
-At the end the conclusions resulting from the study are presented and also cited bibliographic sources are included.
+Strategy presented in this paper is an example of~a~solution that can be used fully automatically or~with assistance of~investor who makes the~decision manually.
+Using such softwaremakes sense only if there are reasonable premises of~achieving the~success.
+These conditions can be achieved through inductive thinking \cite{provost,KleskWilinski}, involving the~assumption that multiple validation of~decision on data from the~past substantiates the~correctness of~the~decision in the~future.
+If a~certain set of~rules in the~strategy used to seek the~pattern, leads to the~success then these rules are a~pattern that is encouraged for repeated use.
+If repeated use of~mentioned pattern results in more successes than failures, then the~basic premise to consider the~use of~the~pattern is rational \cite{bishop2006pattern,KleskWilinski}.
+Unfortunately, changing market is causing the~pattern to become outdated therefore it is necessary to constantly update it.
+Finding historically effective patterns that could be also effective in a~data space not used for their determination (to identify these patterns) is a~major challenge for machine learning which is applied in the~paper.
+The article is organized as follows: at first authors describe an authored strategy based on an entirely innovative concept of~an artificial earthworm.
+Subsequently extensive studies of~effectiveness of~presented strategy in terms of~prediction and~the~aspect of~investment are carried out.
+At the~end the~conclusions resulting from the~study are presented and~also cited bibliographic sources are included.
 
 \section{Strategy characteristics}
-In presented strategy, a metaphorical procedure is often used to explain heuristic algorithms of artificial intelligence. The procedure is a reference to an inspiration derived from the nature.\\
+In presented strategy, a~metaphorical procedure is often used to explain heuristic algorithms of~artificial intelligence. The procedure is a~reference to an inspiration derived from the~nature.\\
 
 Let's consider an artificial earthworm, which behaves like its natural inspirer.
-Let this artificial earthworm have a length of $p1$ candles (vectors representing the knowledge about events occurring within the contractual part of the time series).
-Let its movement come down to the successive ,,eating'' one candle and simultaneous ,,discarding'' of one candle (the last one) --- always having $p1$ candles.
-Thus the earthworm moves incrementally at length of time called the period of the candle.
-$i-th$ candle is  defined as a row of data of values  $O_i$, $H_i$, $L_i$, $C_i$ (Open, High, Low and Close).
-These values represent (in order): the value at the beginning of this period, the maximum value within the period, the minimum and the closing values - at the end of the candle.\\
-Let's assume that candle have a color (often in a number of brokerage platforms such approach is used).
-Therefore candles may be red (when the opening of the candle is higher than its closing $O_i>C_i$) and green (when the situation is opposite $O_i<C_i$).\\
-Let's also assume --- it is a primary strategy rule - that when the artificial earthworm has a significant dominance of red candles, a short position is opened or continued.
-When earthworm has the significant dominance of green candles, a long position is opened or continued.
-Imprecise term ,,significant'' is defined by the use of the second parameter $p2$ according to the rules:
+Let this artificial earthworm have a~length of~$p1$ candles (vectors representing the~knowledge about events occurring within the~contractual part of~the~time series).
+Let its movement come down to the~successive ,,eating'' one candle and~simultaneous ,,discarding'' of~one candle (the last one) --- always having $p1$ candles.
+Thus the~earthworm moves incrementally at length of~time called the~period of~the~candle.
+$i-th$ candle is  defined as a~row of~data of~values  $O_i$, $H_i$, $L_i$, $C_i$ (Open, High, Low and~Close).
+These values represent (in order): the~value at the~beginning of~this period, the~maximum value within the~period, the~minimum and~the~closing values - at the~end of~the~candle.\\
+Let's assume that candle have a~color (often in a~number of~brokerage platforms such approach is used).
+Therefore candles may be red (when the~opening of~the~candle is higher than its closing $O_i>C_i$) and~green (when the~situation is opposite $O_i<C_i$).\\
+Let's also assume --- it is a~primary strategy rule - that when the~artificial earthworm has a~significant dominance of~red candles, a~short position is opened or~continued.
+When earthworm has the~significant dominance of~green candles, a~long position is opened or~continued.
+Imprecise term ,,significant'' is defined by~the~use of~the~second parameter $p2$ according to the~rules:
 \begin{equation}
@@
 \end{equation}
-opening of short position will be suggested;
+opening of~short position will be suggested;
 \begin{equation}
@@
 \end{equation}
-opening of long position will be suggested;
+opening of~long position will be suggested;
 \begin{equation}
-\text{If }  Lg < p1/2 -p2 \text{ and } Lr< p1/2-p2 \text{ then } none;
+\text{If }  Lg < p1/2 -p2 \text{ and~} Lr< p1/2-p2 \text{ then } none;
 \label{eq:eq3}
 \end{equation}
-the continuation of state will be suggested (position or no opened position).\\
+the continuation of~state will be suggested (position or~no opened position).\\
 
-In the rules above $Lr$ and $Lg$ are the number of candles, respectively ,,red'' and ,,green'' in the earthworm of $p1$ length, wherein $p1 = Lr + Lg$.\\
-When dominance determined by another parameter $p2$ is undecided, as in (\ref{eq:eq3}), then earthworm takes the color white and the position will not be opened.
-When the earthworm continues to open position, investor does not incur costs.
-On many platforms, also in literature, symbolic marking of growing candles in white and decreasing in black is used.
-In this article, due to the occurrence of three values, green-red-white colors are used.\\
+In the~rules above $Lr$ and~$Lg$ are the~number of~candles, respectively ,,red'' and~,,green'' in the~earthworm of~$p1$ length, wherein $p1 = Lr + Lg$.\\
+When dominance determined by~another parameter $p2$ is undecided, as in (\ref{eq:eq3}), then earthworm takes the~color white and~the~position will not be opened.
+When the~earthworm continues to open position, investor does not incur costs.
+On many platforms, also in literature, symbolic marking of~growing candles in white and~decreasing in black is used.
+In this article, due to the~occurrence of~three values, green-red-white colors are used.\\
 
-The earthworm is therefore supplied with artificial intellect which enables the accumulation of knowledge and decision-making:
+The earthworm is therefore supplied with artificial intellect which enables the~accumulation of~knowledge and~decision-making:
 \begin{itemize}
-\item right after closing of the current candle, earthworm ,,swallows'' the candle and ,,knows'' what color is it;
+\item right after closing of~the~current candle, earthworm ,,swallows'' the~candle and~,,knows'' what color is it;
 \item earthworm knows how many candles it is composed with;
-\item after absorbing and discarding one candle, earthworm knows how many candles inside it are red or green and how to determine its status --- red, green or white;
-\item knowing its status, earthworm knows how to make a decision about opening or continuing position; the opening of a position (long or short) means the simultaneous closing of the current position (opposite) if such position is opened;
-\item earthworm observes cumulative profit curve and if it  notices unacceptable drawdown, then opened position is changed to the opposite;
-\item unacceptable drawdown is defined by two other parameters $p3$ and $p4$.
-$p3$ is the number of previous candles, which sets a reference point in time series, in which the value of the accumulated profit for $i-p3$ is checked for comparison with the current value of the accumulated profit.
-$p4$ is permissible decrease of cumulative profit.
-If it is exceeded, the $SL$ (Stop Loss --- closes the currently open position) mechanism is activated;
-\item earthworm also observes current course changes during  each next candle and reacts to unprofitable changes.
-If the current exchange rate causes a loss on the opened positions greater than $p5$ then the $SL$ mechanism is triggered --- the position is closed and till the end of the candle earthworm remains in the state without an open position.
-$p5$ is therefore the fifth strategy parameter.
+\item after absorbing and~discarding one candle, earthworm knows how many candles inside it are red or~green and~how to determine its status --- red, green or~white;
+\item knowing its status, earthworm knows how to make a~decision about opening or~continuing position; the~opening of~a~position (long or~short) means the~simultaneous closing of~the~current position (opposite) if such position is opened;
+\item earthworm observes cumulative profit curve and~if it  notices unacceptable drawdown, then opened position is changed to the~opposite;
+\item unacceptable drawdown is defined by~two other parameters $p3$ and~$p4$.
+$p3$ is the~number of~previous candles, which sets a~reference point in time series, in which the~value of~the~accumulated profit for $i-p3$ is checked for comparison with the~current value of~the~accumulated profit.
+$p4$ is permissible decrease of~cumulative profit.
+If it is exceeded, the~$SL$ (Stop Loss --- closes the~currently open position) mechanism is activated;
+\item earthworm also observes current course changes during  each next candle and~reacts to unprofitable changes.
+If the~current exchange rate causes a~loss on the~opened positions greater than $p5$ then the~$SL$ mechanism is triggered --- the~position is closed and~till the~end of~the~candle earthworm remains in the~state without an open position.
+$p5$ is therefore the~fifth strategy parameter.
 \end{itemize}
 
-These features of the earthworm's intelligence may be extended, however, for this work they were limited to the foregoing. \\
+These features of~the~earthworm's intelligence may be extended, however, for this work they were limited to the~foregoing. \\
 
-It is assumed that the time series is $S_i$ where $i = 1, 2, ...,$ and each element is a vector $S_i = (O_i, H_i, L_i, C_i)$ called candle.\\
+It is assumed that the~time series is $S_i$ where $i = 1, 2, ...,$ and~each element is a~vector $S_i = (O_i, H_i, L_i, C_i)$ called candle.\\
 
-Artificial earthworm executes the following algorithm.\\
-The strategy is built on the principle of classical machine learning.
-Before starting to run the algorithm on data located outside the scope that investor knows (like on the current market segments --- out-of-sample), it is necessary to ,,teach''  the values of parameters.
-This principle is presented in Figure \ref{fig:fig2}, which shows examples of learning periods and following them testing periods.
+Artificial earthworm executes the~following algorithm.\\
+The strategy is built on the~principle of~classical machine learning.
+Before starting to run the~algorithm on data located outside the~scope that investor knows (like on the~current market segments --- out-of-sample), it is necessary to ,,teach''  the~values of~parameters.
+This principle is presented in Figure \ref{fig:fig2}, which shows examples of~learning periods and~following them testing periods.
 Data from testing period was not used during learning.\\
@@
 \includegraphics[width = 0.6\textwidth]{figures/rys2.png}
-\caption{An example of the arrangement of learning and testing periods of strategy parameters in time series.}
+\caption{An example of~the~arrangement of~learning and~testing periods of~strategy parameters in time series.}
 \label{fig:fig2}
@@
 \vspace{-1em}
-This repeatable algorithm located in both periods - learning and testing - has the following structure.
-In learning period the optimal value for five parameters $p1$, $p2$, ..., $p5$ is determined.
-In test period these designated values of parameters are used to perform the algorithm in the new environment.
-In each $i-th$ step (candle) of time series following activities are performed:
+This repeatable algorithm located in both periods - learning and~testing - has the~following structure.
+In learning period the~optimal value for five parameters $p1$, $p2$, ..., $p5$ is determined.
+In test period these designated values of~parameters are used to perform the~algorithm in the~new environment.
+In each $i-th$ step (candle) of~time series following activities are performed:
 \begin{itemize}
-\item For each $i = p1, p1 +1, p1 +2, ..., I$ and for $j = 1, ..., p1$ check whether the candle located at a distance $i-j$ backwards from the current candle is:\\
+\item For each $i = p1, p1 +1, p1 +2, ..., I$ and~for $j = 1, ..., p1$ check whether the~candle located at a~distance $i-j$ backwards from the~current candle is:\\
 green when $O_{i-j} <C_{i-j}$, \\
 red when $O_{i-j}> C_{i-j}$, \\
-where $p1$ --- is the first parameter which is the length of the artificial earthworm --- the number of candles of different colors that make up the ,,body'' of the earthworm; \\
-$O_{i-j}$ --- is the opening value of (i-j)-th candle;\\ 
-$C_{i-j}$ --- is the closing value of (i-j)-th candle; \\
-$I$ --- is the length of the test window, after which it is necessary to change the parameters values to the new, learned in the machine learning phase;\\
-\item In each $i-th$ step, the loop $j = 1, ..., p1$ is performed in which a number of green $Lg$, red $Lr$ candles is calculated so the sum of $Lg$ and $Lr$ is $p1$ (to avoid the situation when $O_i = C_i$ is an arbitrary assignation to one of the candles sets e.g.
+where $p1$ --- is the~first parameter which is the~length of~the~artificial earthworm --- the~number of~candles of~different colors that make up the~,,body'' of~the~earthworm; \\
+$O_{i-j}$ --- is the~opening value of~(i-j)-th candle;\\ 
+$C_{i-j}$ --- is the~closing value of~(i-j)-th candle; \\
+$I$ --- is the~length of~the~test window, after which it is necessary to change the~parameters values to the~new, learned in the~machine learning phase;\\
+\item In each $i-th$ step, the~loop $j = 1, ..., p1$ is performed in which a~number of~green $Lg$, red $Lr$ candles is calculated so the~sum of~$Lg$ and~$Lr$ is $p1$ (to avoid the~situation when $O_i = C_i$ is an arbitrary assignation to one of~the~candles sets e.g.
 green);
-\item A condition for the existence of a $Rg$ recommendation to open a long position (or to continue it if it is open) is checked.
-This condition is arbitrarily adopted (one can of course consider different one):
+\item A condition for the~existence of~a~$Rg$ recommendation to open a~long position (or to continue it if it is open) is checked.
+This condition is arbitrarily adopted (one can of~course consider different one):
 \begin{equation}
@@
 \end{itemize}
-If this condition is fulfilled, then depending on the current position status $PositionState$ (where $PositionState$ is a variable which takes values from \{$long, short, none$\}) at the opening of the next candle, a position is opened or continued as follows:
+If this condition is fulfilled, then depending on the~current position status $PositionState$ (where $PositionState$ is a~variable which takes values from \{$long, short, none$\}) at the~opening of~the~next candle, a~position is opened or~continued as follows:
 \begin{equation}
-\text{If } Rg=1 \text{ and } PositionState =long \text{ then }PositionState =long;
+\text{If } Rg=1 \text{ and~} PositionState =long \text{ then }PositionState =long;
 \end{equation}
-(costless continuation of opened position);
+(costless continuation of~opened position);
 \begin{equation}
-\text{If } Rg=1 \text{ and } PositionState = short \text{ then } PositionState=long;
+\text{If } Rg=1 \text{ and~} PositionState = short \text{ then } PositionState=long;
 \end{equation}
 \begin{equation}
-\text{If } Rg=1 \text{ and } PositionState =none \text{ then } PositionState =long;
+\text{If } Rg=1 \text{ and~} PositionState =none \text{ then } PositionState =long;
 \end{equation}
 
-Similarly check the condition of recommendations Rr to open or continue short position:
+Similarly check the~condition of~recommendations Rr to open or~continue short position:
 \begin{equation}
@@
 \end{equation}
-If this condition is fulfilled, then depending on what the current position status PositionState is, at the opening of the next candle, position is opened or continued as follows: \\
+If this condition is fulfilled, then depending on what the~current position status PositionState is, at the~opening of~the~next candle, position is opened or~continued as follows: \\
 \begin{equation}
-\text{If } Rr=1 \text{ and } PositionState =long \text{ then } PositionState =short;
+\text{If } Rr=1 \text{ and~} PositionState =long \text{ then } PositionState =short;
 \end{equation}
 \begin{equation}
-\text{If } Rr==1 \text{ and } PositionState ==short \text{ then } PositionState=short;
+\text{If } Rr==1 \text{ and~} PositionState ==short \text{ then } PositionState=short;
 \end{equation}
-(costless continuing of opened position)
+(costless continuing of~opened position)
 \begin{equation}
-\text{If } Rr==1 \text{ and }  PositionState ==none \text{ then }  PositionState =short;
+\text{If } Rr==1 \text{ and~}  PositionState ==none \text{ then }  PositionState =short;
 \end{equation}
 
-In formulas above there is a parameter $p2$.
-It is the second parameter of the strategy which is an arbitrarily separated part of the earthworm, which depending on size causes the direction of investment not to change.
+In formulas above there is a~parameter $p2$.
+It is the~second parameter of~the~strategy which is an arbitrarily separated part of~the~earthworm, which depending on size causes the~direction of~investment not to change.
 Large $p2$ causes long positions to change into short positions (or vice-versa) rarely.
-Small value of $p2$ leads to a higher frequency of these changes.
-The optimum value of $p2$ is chosen similarly like $p1$.
+Small value of~$p2$ leads to a~higher frequency of~these changes.
+The optimum value of~$p2$ is chosen similarly like $p1$.
 \begin{itemize}
-\item 	When opening long position, profit after one candle (this does not mean that position was closed after a single candle) can be calculated as:
+\item 	When opening long position, profit after one candle (this does not mean that position was closed after a~single candle) can be calculated as:
 \begin{equation}
@@
 \end{equation}
-where the $spread = 0$, when opened long position is continued; \\
-and $spread = cost$, when long position was opened after closing or opening a short position in case when there was no open position;\\
-$cost$ is a variable that depends on the particular brokerage platform that was used for testing the strategy; in this case, for the currency pair EURUSD $cost = 0.00016$ was assumed and for the currency pair GBPUSD $cost = 0.00028$.
+where the~$spread = 0$, when opened long position is continued; \\
+and $spread = cost$, when long position was opened after closing or~opening a~short position in case when there was no open position;\\
+$cost$ is a~variable that depends on the~particular brokerage platform that was used for testing the~strategy; in this case, for the~currency pair EURUSD $cost = 0.00016$ was assumed and~for the~currency pair GBPUSD $cost = 0.00028$.
 \item When short position is opened, profit after one candle (it does not mean that position is closed) can be calculated as: 
@@
 \end{equation}
-where the $spread = 0$, when opened short position is continued;\\ 
-and $spread = cost$, when short position was opened after closing or opening a long position in case when there was no open position.
+where the~$spread = 0$, when opened short position is continued;\\ 
+and $spread = cost$, when short position was opened after closing or~opening a~long position in case when there was no open position.
 \end{itemize}
@@
 \begin{itemize}
-\item If as the result of the test the number of red and green candles in the body of the earthworm had not obtained any dominance from the color that would recommend to open defined position (earthworm was white), it is assumed to continue the position, which is open, without any cost of the transaction (with the value of $spread = 0$).
-If at the beginning of the candle, at the time of checking the recommendation, there was no open position then it can be assumed to continue without any position.
-\item Each of the profits calculated above is verified in terms of exceeding the allowable local position drawdown (within one candle).
-This additional risk management is widely used in automated trading and is called limiting losses --- Stop Loss ($SL$).
-In this algorithm, $SL$ was introduced as the fifth parameter of the strategy --- $p5$.
+\item If as the~result of~the~test the~number of~red and~green candles in the~body of~the~earthworm had not obtained any dominance from the~color that would recommend to open defined position (earthworm was white), it is assumed to continue the~position, which is open, without any cost of~the~transaction (with the~value of~$spread = 0$).
+If at the~beginning of~the~candle, at the~time of~checking the~recommendation, there was no open position then it can be assumed to continue without any position.
+\item Each of~the~profits calculated above is verified in terms of~exceeding the~allowable local position drawdown (within one candle).
+This additional risk management is widely used in automated trading and~is called limiting losses --- Stop Loss ($SL$).
+In this algorithm, $SL$ was introduced as the~fifth parameter of~the~strategy --- $p5$.
 \end{itemize}
@@
 \begin{itemize}
-\item in the case of opening at the beginning of the $i-th$ candle or continuation of a long position presented condition did not occur:\\
+\item in the~case of~opening at the~beginning of~the~$i-th$ candle or~continuation of~a~long position presented condition did not occur:\\
 \begin{equation}
@@
 \end{equation}
-where $L_i$ --– the lowest rate value in the $i-th$ candle; $SL$ --– absolute value Stop Loss appearing as $p5$ parameter;
-\item in the case of opening at the beginning of the $i-th$ candle or continuation of a short position presented condition did not occur:
+where $L_i$ --– the~lowest rate value in the~$i-th$ candle; $SL$ --– absolute value Stop Loss appearing as $p5$ parameter;
+\item in the~case of~opening at the~beginning of~the~$i-th$ candle or~continuation of~a~short position presented condition did not occur:
 \begin{equation}
@@
 \end{equation}
-where $H_i$ --– the highest rate value in the $i-th$ candle.
+where $H_i$ --– the~highest rate value in the~$i-th$ candle.
 \end{itemize}
-This way $p5$ parameter was used for securing in strategy the strong local changes in exchange rate within a single candle.\\
-The meaning of $p5$ parameter to the behavior of the earthworm and the occurrence of the closing position is explained in Figure \ref{fig:fig5}.
+This way $p5$ parameter was used for securing in strategy the~strong local changes in exchange rate within a~single candle.\\
+The meaning of~$p5$ parameter to the~behavior of~the~earthworm and~the~occurrence of~the~closing position is explained in Figure \ref{fig:fig5}.
 \begin{figure}[h!]
@@
 \includegraphics[width = 0.5\textwidth]{figures/rys5.png}
-\caption{Method of calculating the profit (here: loss) in the case of necessity to use $p5$ parameter actuating mechanism $SL$ for long positions.}
+\caption{Method of~calculating the~profit (here: loss) in the~case of~necessity to use $p5$ parameter actuating mechanism $SL$ for long positions.}
 \label{fig:fig5}
@@
 \begin{itemize}
-\item To determine the current quality of the strategy and risk management summation of current gains/losses (the accumulation) is performed
+\item To determine the~current quality of~the~strategy and~risk management summation of~current gains/losses (the accumulation) is performed
 \begin{equation}
-Zc_i = sum ( Z_i ) \text{ from } i = 1 \text{ to the current } i \text{ value;}
+Zc_i = sum ( Z_i ) \text{ from } i = 1 \text{ to the~current } i \text{ value;}
 \end{equation}
-\item There is a possible local subsidence $Zc_i$ capital by introducing two additional parameters to manage the risk.\\
-$p3$ --- the number of steps back on the curve of the cumulative profit for the determination of $Zc_i$ --- $p3$ for comparison with the present value of $Zc_i$;
-$p4$ --- maximum value measured in pips of the capital drawdown (eg for the currency pair EURUSD), which if exceeded will trigger the closure position:\\
+\item There is a~possible local subsidence $Zc_i$ capital by~introducing two additional parameters to manage the~risk.\\
+$p3$ --- the~number of~steps back on the~curve of~the~cumulative profit for the~determination of~$Zc_i$ --- $p3$ for comparison with the~present value of~$Zc_i$;
+$p4$ --- maximum value measured in pips of~the~capital drawdown (eg for the~currency pair EURUSD), which if exceeded will trigger the~closure position:\\
 \begin{equation}
-\text{If } ( Zc_i - p3 - Z_i ) <- p4 \text{ and } PositionState \neq 0 \text{ then } PositionState = 0
+\text{If } ( Zc_i - p3 - Z_i ) <- p4 \text{ and~} PositionState \neq 0 \text{ then } PositionState = 0
 \end{equation} 
-where $PositionState$ --- is the type of open position (long or short) and $PositionState$ equal 0 means resignations from the opening position to the beginning of the next candle.
+where $PositionState$ --- is the~type of~open position (long or~short) and~$PositionState$ equal 0 means resignations from the~opening position to the~beginning of~the~next candle.
 \end{itemize}
-So, the above-described algorithm uses 5 parameters and 3 of them are devoted to risk management of the strategy.\\
+So, the~above-described algorithm uses 5 parameters and~3 of~them are devoted to risk management of~the~strategy.\\
 %%PBStart
-The complexity of the algorithm is illustrated in Figure \ref{fig:fig7}, which shows the individual steps and decisions made in the iteration on a single candle in the form of a decision tree.
-This iteration was carried out both in the search for optimal parameters $p1, ..., p5$ and in the process of testing the parameters on data that was not used in the learning period.
+The complexity of~the~algorithm is illustrated in Figure \ref{fig:fig7}, which shows the~individual steps and~decisions made in the~iteration on a~single candle in the~form of~a~decision tree.
+This iteration was carried out both in the~search for optimal parameters $p1, ..., p5$ and~in the~process of~testing the~parameters on data that was not used in the~learning period.
 \begin{figure}[h!]
@@
 \includegraphics[width = \textwidth]{figures/rys7.png}
-\caption{Decision tree for the states and decisions in one step (candle) in the learning and testing phase.}
+\caption{Decision tree for the~states and~decisions in one step (candle) in the~learning and~testing phase.}
 \label{fig:fig7}
@@
 
-The figure shows in a tree form further decisions taken at the beginning of the candle and then reactions to any unacceptable change in course.
-The first step is to examine the state of the position which is taken from the closing of the previous one.
-The next step is to make decisions / recommendations as to the direction of the opening from the set \{long, short, none\}.
-After opening position  the return of the open position is observed --- it can be positive or negative.
+The figure shows in a~tree form further decisions taken at the~beginning of~the~candle and~then reactions to any unacceptable change in course.
+The first step is to examine the~state of~the~position which is taken from the~closing of~the~previous one.
+The next step is to make decisions / recommendations as to the~direction of~the~opening from the~set \{long, short, none\}.
+After opening position  the~return of~the~open position is observed --- it can be positive or~negative.
 If it is positive, no any additional decisions are necessary.
-In the case of a negative return from the position both the level of $SL$ and a condition resulting from the use of parameters ($p3$, $p4$) are checked.
-The state at the end of tree is a beginning of the next candle.
+In the~case of~a~negative return from the~position both the~level of~$SL$ and~a~condition resulting from the~use of~parameters ($p3$, $p4$) are checked.
+The state at the~end of~tree is a~beginning of~the~next candle.
 
-Described algorithm was implemented in MATLAB environment and in Metatrader platform using the MQL4 language.
-The study was conducted both in the historical data (of course with the principles of machine learning --- testing was carried out using data not used in the learning phase) and a real ,,live'' market.
-Between the environments, there are important differences that affect the diversity of simulation results.
+Described algorithm was implemented in MATLAB environment and~in Metatrader platform using the~MQL4 language.
+The study was conducted both in the~historical data (of course with the~principles of~machine learning --- testing was carried out using data not used in the~learning phase) and~a~real ,,live'' market.
+Between the~environments, there are important differences that affect the~diversity of~simulation results.
 
 \section{Strategy studies}
-The study was conducted primarily on the basic currency pair EURUSD at 1h candles.
-This market was chosen because of its popularity, a huge liquidity and also due to the fact that the authors posses many experiences in other machine learning strategies for this particular market such as in \cite{Wilinski2014,Wilinski}.
-These experiments suggested initially, carrying out many tests with a long learning period, about 1000 candles, then 500 candles and testing time windows of 50 to 200 candles.
-All these attempts have proven to be ineffective and led to continuing losses.
-After months of tests in many markets it was noted that over long periods of learning, e.g.
-the order of 1000 candles, variability in parameters was very large.
-Therefore, the tests started with a decidedly shorter periods of learning and testing.\\
+The study was conducted primarily on the~basic currency pair EURUSD at 1h candles.
+This market was chosen because of~its popularity, a~huge liquidity and~also due to the~fact that the~authors posses many experiences in other machine learning strategies for this particular market such as in \cite{Wilinski2014,Wilinski}.
+These experiments suggested initially, carrying out many tests with a~long learning period, about 1000 candles, then 500 candles and~testing time windows of~50 to 200 candles.
+All these attempts have proven to be ineffective and~led to continuing losses.
+After months of~tests in many markets it was noted that over long periods of~learning, e.g.
+the~order of~1000 candles, variability in parameters was very large.
+Therefore, the~tests started with a~decidedly shorter periods of~learning and~testing.\\
 
-Finally, the authors decided to present the results for the two markets --- currency pairs EURUSD and GBPUSD sampled at 1h --- in machine learning with ratios adjusted to the reduced scope of both the learning and testing phase.\\
+Finally, the~authors decided to present the~results for the~two markets --- currency pairs EURUSD and~GBPUSD sampled at 1h --- in machine learning with ratios adjusted to the~reduced scope of~both the~learning and~testing phase.\\
 
@@
 \centering
-\caption{The test results of the algorithm for different configurations of learning and testing periods for a currency pair EURUSD.}
+\caption{The test results of~the~algorithm for different configurations of~learning and~testing periods for a~currency pair EURUSD.}
 \label{tab:tab1}
@@
 \FloatBarrier
-Table \ref{tab:tab1} summarizes the results for different time periods for the first of the currency pairs.
-The study was conducted at approximately constant number of candles in testing period, e.g.
-if the testing period was 10 candles duration, to perform the test on 1300 candles, optimal parameters were calculated 130 times.
-If the testing period was 20 candles long the parameters were changed 65 times, etc..
+Table \ref{tab:tab1} summarizes the~results for different time periods for the~first of~the~currency pairs.
+The study was conducted at approximately constant number of~candles in testing period, e.g.
+if the~testing period was 10 candles duration, to perform the~test on 1300 candles, optimal parameters were calculated 130 times.
+If the~testing period was 20 candles long the~parameters were changed 65 times, etc..
 
-The table shows that the best results were obtained for the learning to testing period ratio of 80/15.
-For this ratio tests were performed on the EURUSD market and shown in the Figure \ref{fig:fig8}.
-For the 800 one hour candles the result 0.2401 (2401 pips) is obtained.
-Chart is showing a growing course with a maximum fall of 600 pips, which gives a very good, according to the authors, the criterion of Calmar (ratio of maximum profit to maximum drawdown) nearly about $4.0$.\\
+The table shows that the~best results were obtained for the~learning to testing period ratio of~80/15.
+For this ratio tests were performed on the~EURUSD market and~shown in the~Figure \ref{fig:fig8}.
+For the~800 one hour candles the~result 0.2401 (2401 pips) is obtained.
+Chart is showing a~growing course with a~maximum fall of~600 pips, which gives a~very good, according to the~authors, the~criterion of~Calmar (ratio of~maximum profit to maximum drawdown) nearly about $4.0$.\\
 
@@
 \includegraphics[width = 0.5\textwidth]{figures/rys8.png}
-\caption{Accumulation of capital for horizon of 800 steps for the currency pair EURUSD 1h.
+\caption{Accumulation of~capital for horizon of~800 steps for the~currency pair EURUSD 1h.
 This horizon was divided into sections with constant parameter values.
-Test sections were preceded by learning sections with a length of 80 steps.}
+Test sections were preceded by~learning sections with a~length of~80 steps.}
 \label{fig:fig8}
@@
 Tests were also made for another great important currency pair GBPUSD sampled every 1h.
-Results for this currency pair are worse than for EURUSD, however, they reaffirm the overall efficiency of the algorithm.\\
+Results for this currency pair are worse than for EURUSD, however, they reaffirm the~overall efficiency of~the~algorithm.\\
 
@@
 
-The best results are obtained in both cases (for both markets) for the learning to testing period ratio of 80/15.
-Result for EURUSD means that the profit higher than 100 pips per month (approximately 550 hours of trading) was achieved.\\
+The best results are obtained in both cases (for both markets) for the~learning to testing period ratio of~80/15.
+Result for EURUSD means that the~profit higher than 100 pips per month (approximately 550 hours of~trading) was achieved.\\
 
-In addition, effectiveness studies were carried out and optimized for different test periods.
-For the purpose of comparison, the results were combined.
-Achieved results were divided by the length of the testing period (number of candles).
+In addition, effectiveness studies were carried out and~optimized for different test periods.
+For the~purpose of~comparison, the~results were combined.
+Achieved results were divided by~the~length of~the~testing period (number of~candles).
 
-Figure \ref{fig:fig10} presents the results for EURUSD currency pair.
-From these results it can be concluded that the strategy is working with a short term duration characteristics.
-The best results were achieved in periods containing 10-20 candles --- unlike in any other strategy presented in \cite{Wilinski2014}, where the best results were achieved for the test periods with a length of 80-100 candles.\\
-All the results presented above refer to simulations conducted in MATLAB.
+Figure \ref{fig:fig10} presents the~results for EURUSD currency pair.
+From these results it can be concluded that the~strategy is working with a~short term duration characteristics.
+The best results were achieved in periods containing 10-20 candles --- unlike in any other strategy presented in \cite{Wilinski2014}, where the~best results were achieved for the~test periods with a~length of~80-100 candles.\\
+All the~results presented above refer to simulations conducted in MATLAB.
 
@@
 \section{Strategy verification using online trading platform}
-From a conceptual point of view implementing automated trading strategies in MATLAB environment is one of proper approaches.
-MATLAB provides a number of features to rapidly prototype such algorithms, e.g.
-built-in computation functions and charting tools.
-What is more, MATLAB enables also intuitive operations on vectors and matrices as well as flexible insight into variables values that are produced by the algorithm which greatly facilitates computing process management.\\
+From a~conceptual point of~view implementing automated trading strategies in MATLAB environment is one of~proper approaches.
+MATLAB provides a~number of~features to rapidly prototype such algorithms, e.g.
+built-in computation functions and~charting tools.
+What is more, MATLAB enables also intuitive operations on vectors and~matrices as well as flexible insight into variables values that are produced by~the~algorithm which greatly facilitates computing process management.\\
 
-However in such approach it is very important to make sure that an algorithm that has been developed in MATLAB could be used also regarding to real market conditions which means a number of rules, validations and limitations which obviously are not natively implemented in MATLAB as it is just an generic computing environment.\\
+However in such approach it is very important to make sure that an algorithm that has been developed in MATLAB could be used also regarding to real market conditions which means a~number of~rules, validations and~limitations which obviously are not natively implemented in MATLAB as it is just an generic computing environment.\\
 
-To make sure that those market conditions are met in the algorithm MATLAB script was converted manually to MQL4 expert advisor for trading platform of MetaTrader 4 which is commonly used to perform the real market operations.\\
+To make sure that those market conditions are met in the~algorithm MATLAB script was converted manually to MQL4 expert advisor for trading platform of~MetaTrader 4 which is commonly used to perform the~real market operations.\\
 
-The main differences between the implementation of the artificial earthworm in MATLAB and in MetaTrader are listed below:
+The main differences between the~implementation of~the~artificial earthworm in MATLAB and~in MetaTrader are listed below:
 \begin{itemize}
@@
 \begin{itemize}
-\item Calculation of balance and other standard market statistics is implemented manually, including also calculation of profit and loss related with opening / closing position;
+\item Calculation of~balance and~other standard market statistics is implemented manually, including also calculation of~profit and~loss related with opening / closing position;
 \item $SL$ handling is implemented manually, including trailing stop;
-\item Lack of built-in market validations for opening / closing position;
+\item Lack of~built-in market validations for opening / closing position;
 \item Calculations are done using only 4 discrete price values for each candle;
-\item Implementation approach from technical point of view is a matter of developer decisions;
+\item Implementation approach from technical point of~view is a~matter of~developer decisions;
 \end{itemize}
@@
 \begin{itemize}
-\item Balance and other standard market statistics are calculated automatically, including also a strictly defined API for opening / closing position;
-\item $SL$ handling is a built-in feature, including trailing stop;
+\item Balance and~other standard market statistics are calculated automatically, including also a~strictly defined API for opening / closing position;
+\item $SL$ handling is a~built-in feature, including trailing stop;
 \item There are built-in market validations for opening / closing position;
 \item Prices are changing smoothly for current candle (not only final fixed OHLC values);
-\item Implementation approach from technical point of view is a not only a matter of developer decisions, but is also enforced by MetaTrader conventions (phases of initialization, candle execution, deinitialization etc.);
+\item Implementation approach from technical point of~view is a~not only a~matter of~developer decisions, but is also enforced by~MetaTrader conventions (phases of~initialization, candle execution, deinitialization etc.);
 \end{itemize}
@@
 
-The elements listed above could cause some variations in the fragmentary as well as the final results of the algorithm execution.\\
+The elements listed above could cause some variations in the~fragmentary as well as the~final results of~the~algorithm execution.\\
 
-In the paper MetaTrader4, implementation for  has covered only the testing part of the algorithm using fixed set of parameters that have been previously computed in MATLAB in the learning part of execution for every test period.
-It is important to note that implementing full algorithm, along with the learning part in MQL4, is obviously possible, however in the article the main objective was to confirm that the artificial earthworm can run on a real market with results similar to those achieved in MATLAB.\\
+In the~paper MetaTrader4, implementation for  has covered only the~testing part of~the~algorithm using fixed set of~parameters that have been previously computed in MATLAB in the~learning part of~execution for every test period.
+It is important to note that implementing full algorithm, along with the~learning part in MQL4, is obviously possible, however in the~article the~main objective was to confirm that the~artificial earthworm can run on a~real market with results similar to those achieved in MATLAB.\\
 
-Below are presented balance comparisons in MATLAB and MetaTrader environments:
+Below are presented balance comparisons in MATLAB and~MetaTrader environments:
 \begin{enumerate}
-\item for EURUSD currency pair using 1h candles values in time period of 2012.01.20 - 2013.01.01 in two different approaches:
+\item for EURUSD currency pair using 1h candles values in time period of~2012.01.20 - 2013.01.01 in two different approaches:
 \begin{itemize}
 \item with fixed parameters: $p1$=34, $p2$=4, $p3$=3, $p4$=-0.0060, $p5$=0.0060.
-Optimal parameters in that case were computed in MATLAB for the first testing period and then were used for all testing periods.
+Optimal parameters in that case were computed in MATLAB for the~first testing period and~then were used for all testing periods.
 \item with dynamic parameters that were changed every testing period, regarding to their values computed in MATLAB that were put to MetaTrader 
@@
 \item initial deposit was 10000 EUR,
-\item size of the opening positions was 1 lot,
+\item size of~the~opening positions was 1 lot,
 \item each testing period lasted 15 candles.
 \end{itemize}
-\item for GBPUSD currency pair using 1h candles values in time period of 2013.01.09 - 2013.12.30 in two different approches:
+\item for GBPUSD currency pair using 1h candles values in time period of~2013.01.09 - 2013.12.30 in two different approches:
 \begin{itemize}
-\item with fixed parameters: $p1$=27, $p2$=4, $p3$=1, $p4$=-0.0060, $p5$=0.0060 (Figure \ref{fig:fig12} and Figure \ref{fig:fig13}).
-Optimal parameters in that case were computed in MATLAB for the first testing period and then were used for all testing periods.
-\item with dynamic parameters that were changed every testing period, regarding to their values computed in MATLAB that were put to MetaTrader (Figure \ref{fig:fig14} and Figure \ref{fig:fig13})
+\item with fixed parameters: $p1$=27, $p2$=4, $p3$=1, $p4$=-0.0060, $p5$=0.0060 (Figure \ref{fig:fig12} and~Figure \ref{fig:fig13}).
+Optimal parameters in that case were computed in MATLAB for the~first testing period and~then were used for all testing periods.
+\item with dynamic parameters that were changed every testing period, regarding to their values computed in MATLAB that were put to MetaTrader (Figure \ref{fig:fig14} and~Figure \ref{fig:fig13})
 \end{itemize}
@@
 \item initial deposit was 50000 EUR,
-\item size of the opening positions was 1 lot,
+\item size of~the~opening positions was 1 lot,
 \item each testing period lasted 15 candles.
@@
 
-Results of the algorithm execution in both environments for both currency pairs are presented in Table \ref{tab:tab5}.
+Results of~the~algorithm execution in both environments for both currency pairs are presented in Table \ref{tab:tab5}.
 \begin{table}[h!]
 \centering
-\caption{Results of the algorithm execution in both environments for both currency pairs and various parameters values.}
+\caption{Results of~the~algorithm execution in both environments for both currency pairs and~various parameters values.}
 \label{tab:tab5}
@@
 \vspace{-1em}
-It is important to note that every first chart from each pair above was done in MATLAB and every second chart was done in MetaTrader.
-In MATLAB chart context, every point of abscissa axis represents testing period, while on ordinate axis there is a result of testing period (relative value), so that it can be assumed that chart was done in time domain.
-On the other hand, every abscissa on MetaTrader chart represents each opening of position, which means that chart is not linear related with time (however in cases presented in the article it is really similar to time domain), so that chart begins with first position opening and it is denoised in comparison to MATLAB chart as every line are determined by opening and closing position, no matter how long this position has lasted.
-Despite those differences, correlation between MATLAB and MetaTrader charts for the artificial earthworm algorithm executions is indisputable.
+It is important to note that every first chart from each pair above was done in MATLAB and~every second chart was done in MetaTrader.
+In MATLAB chart context, every point of~abscissa axis represents testing period, while on ordinate axis there is a~result of~testing period (relative value), so that it can be assumed that chart was done in time domain.
+On the~other hand, every abscissa on MetaTrader chart represents each opening of~position, which means that chart is not linear related with time (however in cases presented in the~article it is really similar to time domain), so that chart begins with first position opening and~it is denoised in comparison to MATLAB chart as every line are determined by~opening and~closing position, no matter how long this position has lasted.
+Despite those differences, correlation between MATLAB and~MetaTrader charts for the~artificial earthworm algorithm executions is indisputable.
 \begin{figure}[h!]
@@
 
-The concept of an innovative investment strategy gave satisfactory results for a certain pair as the result of periods of machine learning.
+The concept of~an innovative investment strategy gave satisfactory results for a~certain pair as the~result of~periods of~machine learning.
 E.g.
-in the studied data for two key market currency pairs sampled every hour, the best value is 80 hours of teaching and 15 hours of testing.
-One can assume that this relationship may change in a different environment (for other markets, for other periods) by becoming a sort of next parameter that optimal values should be sought.
-It should be emphasized that the study was conducted on data not used in the learning phase and for the basic principle of machine learning achieved results that would have satisfied many a practice.
-It should also be noted that outside research conducted in environment completely specified (for constant unchanging data stored in MATLAB) was also performed simulations in terms of actual brokerage platform.
-The results obtained in both environments are similar in the sense of direction changes and logic behavior caused by the user received by the algorithm implemented in the MATLAB and MetaTrader.
+in the~studied data for two key market currency pairs sampled every hour, the~best value is 80 hours of~teaching and~15 hours of~testing.
+One can assume that this relationship may change in a~different environment (for other markets, for other periods) by~becoming a~sort of~next parameter that optimal values should be sought.
+It should be emphasized that the~study was conducted on data not used in the~learning phase and~for the~basic principle of~machine learning achieved results that would have satisfied many a~practice.
+It should also be noted that outside research conducted in environment completely specified (for constant unchanging data stored in MATLAB) was also performed simulations in terms of~actual brokerage platform.
+The results obtained in both environments are similar in the~sense of~direction changes and~logic behavior caused by~the~user received by~the~algorithm implemented in the~MATLAB and~MetaTrader.
 Differences were explained in this work.
-The direction of further research will test the hypothesis that the variability periods to test the learner can improve the quality of prediction.
-This hypothesis seems to be interesting against the background of previous experiences and results, eg for different studied strategies, including \cite{Wilinski2014}\cite{Wilinski}\cite{sinclare}\cite{krutsinger} obtained surprisingly different optimal length of periods of learning and testing.
+The direction of~further research will test the~hypothesis that the~variability periods to test the~learner can improve the~quality of~prediction.
+This hypothesis seems to be interesting against the~background of~previous experiences and~results, eg for different studied strategies, including \cite{Wilinski2014}\cite{Wilinski}\cite{sinclare}\cite{krutsinger} obtained surprisingly different optimal length of~periods of~learning and~testing.
 

### 2014-05-12 Article/Article20140406Granada/LatexArt/article_main.tex
Old title restored

@@
 % first the title is needed
-\title{Investment Strategy Based on Artificial Earthworm Behavior for Algotrading Application}
+\title{The investment strategy based on behavior of artificial earthworm for use in algotrading}
 
 % a short form should be given in case it is too long for the running head
-\titlerunning{Investment Strategy Based on Artificial Earthworm Behavior}
+\titlerunning{The investment strategy based on behavior of artificial earthworm}
 

### 2014-05-12 Article/Article20140406Granada/LatexArt/article_main.tex
layout fixes

@@
 The strategy has been tested in a~number of~simulations on historical data as well as data outside learning periods.
-Tests were performed mainly in the~selected currency markets, including the~primary currency pair of~EURUSD.
+Tests were performed mainly in the~selected currency markets, including the~primary currency pair of~\mbox{EURUSD}.
 Presented approach opens long and~short positions alternately during candle closing events.
@@
 \end{itemize}
-If this condition is fulfilled, then depending on the~current position status $PositionState$ (where $PositionState$ is a~variable which takes values from \{$long, short, none$\}) at the~opening of~the~next candle, a~position is opened or~continued as follows:
+If this condition is fulfilled, then depending on the~current position status \textit{PositionState} (where $PositionState$ is a~variable which takes values from \{$long$, $short$, $none$\}) at the~opening of~the~next candle, a~position is opened or~continued as follows:
 \begin{equation}
@@
 In formulas above there is a~parameter $p2$.
-It is the~second parameter of~the~strategy which is an arbitrarily separated part of~the~earthworm, which depending on size causes the~direction of~investment not to change.
+It is the~second parameter of~the strategy which is an arbitrarily separated part of~the~earthworm, which depending on size causes the~direction of~investment not to change.
 Large $p2$ causes long positions to change into short positions (or vice-versa) rarely.
@@
 $p3$ --- the~number of~steps back on the~curve of~the~cumulative profit for the~determination of~$Zc_i$ --- $p3$ for comparison with the~present value of~$Zc_i$;
-$p4$ --- maximum value measured in pips of~the~capital drawdown (eg for the~currency pair EURUSD), which if exceeded will trigger the~closure position:\\
+$p4$ --- maximum value measured in pips of~the~capital drawdown (e.g. for the~currency pair EURUSD), which if exceeded will trigger the~closure position:\\
 \begin{equation}
@@
 \end{equation} 
-where $PositionState$ --- is the~type of~open position (long or~short) and~$PositionState$ equal 0 means resignations from the~opening position to the~beginning of~the~next candle.
+where $PositionState$ --- is the~type of~open position (long or~short) and $PositionState$ equal 0 means resignations from the~opening position to the~beginning of~the~next candle.
 \end{itemize}
@@
 
-To make sure that those market conditions are met in the~algorithm MATLAB script was converted manually to MQL4 expert advisor for trading platform of~MetaTrader 4 which is commonly used to perform the~real market operations.\\
+To make sure that those market conditions are met in the algorithm \mbox{MATLAB} script was converted manually to MQL4 expert advisor for trading platform of~MetaTrader 4 which is commonly used to perform the~real market operations.\\
 
@@
 The direction of~further research will test the~hypothesis that the~variability periods to test the~learner can improve the~quality of~prediction.
-This hypothesis seems to be interesting against the~background of~previous experiences and~results, eg for different studied strategies, including \cite{Wilinski2014}\cite{Wilinski}\cite{sinclare}\cite{krutsinger} obtained surprisingly different optimal length of~periods of~learning and~testing.
+This hypothesis seems to be interesting against the~background of~previous experiences and~results, e.g.
+for different studied strategies, including \cite{Wilinski2014}\cite{Wilinski}\cite{sinclare}\cite{krutsinger} obtained surprisingly different optimal length of~periods of~learning and~testing.
 
